### 2014-09-02 ants2015.Rmd
ENH: new stuff talk

---
title: <span style="color:red;">How to build a house with<br />Advanced Normalization Tools (*ANTs*)</span>
author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)
bibliography: REFERENCES.bib
logo:    logo.jpg
output:
  pdf_document:
    toc: true
    highlight: zenburn
  beamer_presentation:
    toc: true
    fig_width: 7
    fig_height: 6
  html_document:
    toc: true
    theme: readable
  revealjs_presentation:
    pandoc_args: [ "--slide-level", "2" ]
    incremental: true
    widescreen: true
    smaller: false
    theme: night
    transition: fade
    highlight: zenburn
    center: true
    self_contained: false
  ioslides_presentation:
    css: atk.css
    incremental: false
    widescreen: true
    smaller: false
    fig_width: 5
---

```{r global options, include=FALSE}
library(rmarkdown)
library(knitr)
figpath<-'figures/'
opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
               warning=FALSE, message=FALSE)
```

##

<div align="center"><img src="./logo.png" frameborder="0"></img></div>

This talk is online at [http://stnava.github.io/ANTs2015/](http://stnava.github.io/ANTs2015/) with colored [links](http://stnava.github.io/ANTs2015/) meant to be clicked for more information.

## ANTs & Neuroscience

We need statistical image analysis <br />at several scales in modern neuroscience

* Macro: *in vivo* structural and functional MRI

* Micro:  high-resolution post-mortem MRI links with in vivo MRI

* Nano: neuron reconstruction ...

* Solutions that are consistent across these scales have the potential
to build multi-scale feature sets or templates and provide new
insights into brain structure and function

* E.g. Parcellation constraints based on histology, tractography, function ...

* Statistical definitions of anatomy/pathology?

* Reinvention of these solutions within each lab ... can we mitigate this?

* Reduce, reuse, recycle ...

# *ANTs* optimizes mathematically <br /> well-defined  <br /><span style="color:red;">objective functions</span>  <br />guided by <br /> <span style="color:red;">prior knowledge</span>  ...

# plug *your ideas* <br />into our software: <br /> <span style="color:blue;"> <span style="color:red;">innovation, insight</span> <br />from biomedical data</span> ...

## Diffeomorphisms

<div align="center"><img width="1433" src="./figures/sillyputty.png" frameborder="0"></img></div>

plausible physical modeling of large, invertible deformations

"differentiable map with differentiable inverse"

## ANTs: Beyond Registration

![](./figures/antscapabilities.jpg)

[Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)

## Founding developers

<div align="center"><img width="1433" src="./figures/bant2.png" frameborder="0"></img></div>

## Long-term collaborators

![](./figures/antscollab.jpg)

$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...

## General purpose library for multivariate image registration, segmentation & statistical analysis tools

* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.

* Generic mathematical methods that are tunable for 
application specific domains:  no-free lunch

* Deep testing on multiple platforms ... osx, linux, windows.

* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )

```
    An algorithm must use prior knowledge about a problem 
    to do well on that problem 
```

# <span style="color:red;">Medical Image Registration</span> <br /> Fundamental tool for<br /> morphometry, segmentation,<br /> motion estimation and <br /> <span style="color:blue;">data cleaning</span>

## Definitions

* Registration $=$ estimate an "optimal" geometric mapping between image pairs or image sets (e.g. Affine)

* Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)

* <span style="color:grey;">
Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)  </span>

* Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)

* <span style="color:grey;"> Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>

* Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)

* MALF: multi-atlas label fusion - using anatomical dictionaries to label new data

* Solutions to challenging statistical image processing problems usually need elements from each of the above

## The Technical Framework

![](./figures/designprinciples.png)

... and most of it multivariate.

## [SyN](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC2276735/) for optimization symmetry
![](./figures/fishSyN.png)
Images deform symmetrically along the shape manifold.  This eliminates bias in the
measurement of image differences.

##  [SyN (link)](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC2276735/) Example

<!-- syn example -->

<div align="center"><iframe width="1220" height="730" src="http://www.youtube.com/embed/3I9RcRtpOvw" frameborder="0" allowfullscreen></iframe></div>

[SyN movie](http://www.youtube.com/embed/3I9RcRtpOvw)

## Concatenated transformation $+$ metric stages are necessary in real data

0.  Initialize the mapping ( more on this later )

1.  Start with a *rigid transformation*:  $I(x) \approx J(R(x))$ s.t. negative $MI$ is minimized

2.  Follow by an *affine transformation*:  $I(x) \approx J(R(A(x)))$ s.t. negative $MI$ is minimized with fixed $R$

3.  Finally, a *diffeomorphism*:  $I(x) \approx J(R(A(\phi(x))))$ s.t. $k$-neighborhood correlation $CC_k$ is minimized with fixed $R, A$

4.  Output the *composite transform* $A \circ R$ as a matrix transformation and $\phi$ and $\phi^{-1}$ as deformation fields.

standard in [recommended](http://stnava.github.io/ANTsDoc/) `antsRegistration` application scripts

## Registration benefits from<br /> *optimal sampling strategy*

* sampling for *both* the metric and the transformation

* impacts scalability, memory, optimization accuracy, speed, robustness ...

* could be done optimally *with massive improvements in performance*
    * but needs investment in order to achieve "dream" registration scenario

* important for new schemes that *elect* solutions from **anatomical or transformation** dictionaries

* overall, relatively little translational work on this important problem in biomedical imaging

## Sampling & feature selection: Multi-start

![](./figures/multistart.png)

Theoretical guarantee of global optimum: improves local optimizers.

Default in `antsCorticalThickness` pipeline and `FSL`.

## Sampling & feature selection: Biomedical imagery

![](./figures/slides1.png)

Initial configuration of data

## Sampling & feature selection: Biomedical imagery

![](./figures/slides2.png)

Automatic feature selection

## Sampling & feature selection: Biomedical imagery

![](./figures/slides3.png)

Resampling allows comparison & slide alignment and <br />
validates the feature selection

Dramatic reduction in computation time / memory requirements

## Sampling & feature selection: Lesioned brains

![](./figures/lesionedbrains.jpg)

## Sampling & feature selection: Summary

* we exploit these strategies to:
    - accelerate
    - focus 
    - validate

# Evaluation results

## 
![](./figures/evalhistory.png)

## Anatomical dictionaries
![](./figures/sata2013.png)

we provided the *standard* registration results for $>$ 20,000 image pairs at [SATA 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events)

## [label fusion (link)](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3049832/)
![](./figures/sata2013.jpg)

## Multiple metrics improve performance
![](./figures/multivariateSATA.jpg)

to our knowledge, ANTs is the only freely available system that can solve this problem in a fully multivariate manner.

Hongzhi Wang won the "walk in the park" award for this work ...

# Differentiable maps with<br /> differentiable inverse <br />$+$ *statistics in these spaces*

## Brain templates as *high-dimensional averages*
![](./figures/speciestemplates.png)

## SyGN - templates and averages in deformation space

![](figures/normvsnorm.png)
from [miykael](http://miykael.github.io/nipype-beginner-s-guide/ANTS.html)

[geodesic image averages](http://www.ncbi.nlm.nih.gov/pubmed/15501083)

[optimal templates 2](http://www.ncbi.nlm.nih.gov/pubmed/19818860)

[canine template](http://www.ncbi.nlm.nih.gov/pubmed/23284904)

[chimpanzees](http://www.ncbi.nlm.nih.gov/pubmed/23516289)

## Statistics in deformation space

[AIBS movie](http://www.youtube.com/embed/8GgHG-rApiE)

## Average Republican and Democratic congressmen

<div align="center"><img src="figures/democrat_left_repub_right.png" frameborder="0"></img></div>

[congress](http://ntustison.github.io/CongressionalFaceTemplates/)

# ANTs versus Freesurfer:<br />  Quantifying *life span* brain health

## ANTs versus Freesurfer:<br />  Quantifying *life span* brain health

* Freesurfer is the historical standard for measuring cortical thickness

* instead of using surfaces to measure cortical thickness, we use the image space *DiReCTly*

* [see this section of a different talk](http://stnava.github.io/ANTsTalk/#/putting-it-all-together-can-we-quantify-life-span-brain-health-in-individuals-and-in-populations)

* and this "big data" paper: [Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements](http://www.ncbi.nlm.nih.gov/pubmed/24879923)

* comparison of prediction from automated cortical thickness measurement from 4 public datasets

* $>$ 1200 subjects, age 7 to over 90 years old

* *hint*: ANTs thickness measurements have higher prediction accuracy relative to Freesurfer ( implying we extract more information from the data )

* ANTs methods consistently improve statistical power [eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/24687814), [syn](http://www.ncbi.nlm.nih.gov/pubmed/?term=syn+epstein+avants), [itkv4](http://www.ncbi.nlm.nih.gov/pubmed/24817849) ... also, see [Schwarz CG, et al.](http://www.ncbi.nlm.nih.gov/pubmed/24650605) re: TBSS and related work in fMRI [Miller, PNAS](http://www.ncbi.nlm.nih.gov/pubmed/15980148), [Azab, et al in Hippocampus](http://www.ncbi.nlm.nih.gov/pubmed/24167043).

# Registration & statistics:<br /> Frontiers and innovation

## multivariate statistical fields arise from fused modalities

![images at measurement fields](figures/statisticalfields.png)

*Many opportunities for statistical advancements*

## Scientific Data 2014
![](./figures/ptbp2.png)

## "Network" of predictors for age

...

## ITK+ANTs+R = <span style="color:red;">*ANTsR*</span>

## Agnostic statistics
![](./figures/antsrex.jpg)

[McMillan et al.](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3961542/)

## A Quick <span style="color:grey;">*ANTsR*</span> example
```{r loadantsr,results='hide',echo=FALSE,message=FALSE}
library(ANTsR)
```

This is an executable *ANTsR* code block - *N*-dimensional statistics to go with 
our *N*-dimensional image processing software!
```{r loadimages,message=FALSE,warning=FALSE,results='hide'}
library(ANTsR)
dim<-2
filename<-getANTsRData('r16')
img<-antsImageRead( filename , dim )
filename<-getANTsRData('r64')
img2<-antsImageRead( filename , dim )
mask<-getMask(img,50,max(img),T)
mask2<-getMask(img,150,max(img),T)
nvox<-sum( mask == 1 )
nvox2<-sum( mask2 == 1 )
```
The brain has `r nvox` voxels ...

## A Quick <span style="color:grey;">*ANTsR*</span> example

Simulate a population morphometry study - a "VBM" ...
```{r morph,results='hide'}
simnum<-10
imglist<-list()
imglist2<-list()
for ( i in 1:simnum ) {
  img1sim<-antsImageClone(img)
  img1sim[ mask==1 ]<-rnorm(nvox,mean=0.5)
  img1sim[ mask2==1 ]<-rnorm(nvox2,mean=2.0)
  img2sim<-antsImageClone(img2)
  img2sim[ mask==1 ]<-rnorm(nvox,mean=0.20)
  imglist<-lappend(imglist,img1sim)
  imglist2<-lappend(imglist2,img2sim)
}
imglist<-lappend( imglist, imglist2 )
mat<-imageListToMatrix( imglist, mask )
DX<-factor( c( rep(0,simnum), rep(1,simnum) ) )
mylmresults<-bigLMStats( lm( mat ~ DX ) )
qvals<-p.adjust( mylmresults$pval.model ) 
```
The minimum q-value is `r min(qvals)` ...

## Visualize the histograms of effects
```{r vizmorph,results='hide'}
whichvox<-qvals < 1.e-2
voxdf<-data.frame( volume=c( as.numeric( mat[,whichvox] ) ), DX=DX )
ggplot(voxdf, aes(volume, fill = DX)) + geom_density(alpha = 0.2)
```

## Visualize the anatomical distribution
```{r vizmorph2hide,results='hide',echo=FALSE}
betas<-antsImageClone(mask)
betavec<-abs(mylmresults$beta.t[1,])
betas[mask==1]<-betavec
SmoothImage(dim,betas,1.5,betas)
thresh<-paste(3.0,'x',max(betavec),sep='')
ofn<-paste(figpath,'vizmorph2.jpg',sep='')
```

```{r vizmorph2,results='hide'}
plotANTsImage(img,functional=list(betas),threshold=thresh,
  outname=ofn)
```

![](`r ofn`)

## Network visualization
see `?plotBasicNetwork`
```{r networkfn,results='hide',warning=FALSE,echo=FALSE,message=FALSE}
ofn<-paste(figpath,'network',sep='')
ofnpng<-paste(ofn,'.png',sep='')
```
```{r network,results='hide',warning=FALSE,echo=FALSE,message=FALSE,eval=FALSE}
       mnit<-getANTsRData("mni")
       mnit<-antsImageRead(mnit,3)
       mnia<-getANTsRData("mnia")
       mnia<-antsImageRead(mnia,3)
       ThresholdImage(3,mnit,mnit,1,max(mnit))
       ImageMath(3,mnit,"FillHoles",mnit)
       cnt<-getCentroids( mnia, clustparam = 50 )
       aalcnt<-cnt$centroids[1:90,]
       brain<-renderSurfaceFunction( surfimg =list( mnit ) , alphasurf=0.1 ,smoothsval = 1.5 )
       testweights<-matrix( rep( 0, 90*90 ) ,nrow=90)
       testweights[31,37]<-1  # ant cingulate to hipp
       testweights[31,36]<-2  # ant cingulate to post cingulate
       testweights[11,65]<-3  # broca to angular 
       plotBasicNetwork( centroids = aalcnt , brain , weights=testweights )
       id<-par3d("userMatrix")
       rid<-rotate3d( id , -pi/2, 1, 0, 0 )
       rid2<-rotate3d( id , pi/2, 0, 0, 1 )
       rid3<-rotate3d( id , -pi/2, 0, 0, 1 )
       par3d(userMatrix = id ) 
       dd<-make3ViewPNG(  rid, id, rid2,  ofn )
       par3d(userMatrix = id ) 
```
![](`r ofnpng`)

## The power of *ANTs* $+$ *R* $\rightarrow$<br /> <span style="color:red;">**Reproducible imaging science**</span>

![](./figures/antsgoals.png)

... used in ["Sparse canonical correlation analysis relates network-level atrophy to multivariate cognitive measures in a neurodegenerative population"](http://www.ncbi.nlm.nih.gov/pubmed/24096125) and several upcoming ...

## Can we customize these methods for a challenging multivariate segmentation problem with clinical relevance?

## Automated tumor segmentation from multiple MRI
![](./figures/tumorsegmentation.png)

## General theory tunable to specific domains:  *no-free lunch*
![](./figures/brats.png)

[BRATS 2013 Challenge](http://hal.inria.fr/docs/00/93/56/40/PDF/brats_preprint.pdf) **won** with [*ANTsR*](https://github.com/stnava/ANTsR)

## Can we address subtle questions in brain and cognition via imaging-specific dimensionality reduction?

##  [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/24852460) & [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=avants+SCCAN)

## ANTs*R* $\rightarrow$ new insight <br />via better analytics

Good software should fade into the background ... however ...

<span style="color:red;">
 As is common in science, the first big breakthrough in our understanding ...
 [came from] an improvement in measurement.
</span>

<span style="color:blue;">
> Daniel Kahnemann, *Thinking, Fast and Slow* (2011)
</span>

# Conclusion

## Recap

- Powerful, general-purpose, <span style="color:red;">well-evaluated</span> registration and segmentation.

- Differentiable maps with differentiable inverse <span style="color:red;">$+$ statistics in these spaces</span>

- Evaluated in multiple problem domains</span> via internal studies & open competition

- Borg philosophy: <span style="color:red;">"best of"</span> from I/O, to processing to statistical methods

- Open source, testing, many examples, consistent style, multiple platforms,  active community support ...

- Integration with *R* $+$ novel tools for prediction, decoding, high-to-low dimensional statistics.

- Collaborations with [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...

## Challenges: Computational and Scientific

- Scalability
    - **need to fuse feature selection methods with transformation optimization**
    - **need to leverage existing ITK streaming infrastructure in application level tool**
- Domain expertise: Customizable for specific problems but sometimes not specific enough
- "Plausible physical modeling ..." - this should vary per problem ... but doesn't.
    - a fabulous project would be to resolve this issue at a large-scale e.g. for reconstructing neurons, measuring white matter elaboration ...
    - our prior FEM work is one potential solution
- Rapid development: colleagues still need familiarity with compilation for latest ANTs features
- Latest theoretical advances in registration not yet wrapped for users
- Need more [Documentation](http://stnava.github.io/ANTs/)  & [testing](http://testing.psychiatry.uiowa.edu/CDash/index.php?project=ANTS) ...

## Tools you can use for imaging science

- Core developers:  *B. Avants, N. Tustison, H. J. Johnson, J. T. Duda*

- Many contributors, including users ...

- Multi-platform, multi-threaded C++ [stnava.github.io/ANTs](stnava.github.io/ANTs)

- Developed in conjunction with [http://www.itk.org/](http://www.itk.org/)

- R wrapping and extension [stnava.github.io/ANTsR](stnava.github.io/ANTsR)

- rapid development, regular testing $+$ many eyes $\rightarrow$ bugs are shallow

<img style="float: right" src="figures/penn.png" />
<img style="float: left" src="figures/picsl.jpg" />

# Analysis philosophy and <br /> published opinions

## What is and *is not*<br /> image registration

[*not* registration](http://www.ncbi.nlm.nih.gov/pubmed/23116330)

## Voodoo in voxel-based analysis

[logical circularity VBA](http://www.ncbi.nlm.nih.gov/pubmed/?term=logical+circularity+tustison)

## Instrumentation bias in the use and evaluation of software

[Instrumentation bias in the use and evaluation of software](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3766821/?report=reader)

# References {#reffont}

### 2014-09-02 README.R

@@ -1,0 +1,11 @@
+#!/usr/bin/env Rscript
+#
+# ants wip / future work
+#
+library(ggplot2)
+library(shiny)
+library(ggvis)
+library(rmarkdown)
+srcdir<-"./"
+pre='ants2015'
+render( paste(pre,".Rmd",sep=''), clean=TRUE, "revealjs_presentation", output_file='index.html' ) 

### 2014-09-02 README.R
WIP: regular update

@@ -7,5 +7,10 @@ library(shiny)
 library(ggvis)
 library(rmarkdown)
 srcdir<-"./"
-pre='ants2015'
-render( paste(pre,".Rmd",sep=''), clean=TRUE, "revealjs_presentation", output_file='index.html' ) 
+buildrmd='ants2015build.Rmd'
+rawrmds<-c("ants2015.Rmd","lesions/lesions.Rmd","lastslide.Rmd")
+for ( x in 1:length(rawrmds) ) {
+  if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
+  system(cmd)
+}
+render(buildrmd, clean=TRUE, "revealjs_presentation", output_file='index.html' ) 

### 2014-09-02 README.R
WIP: regular update

@@ -8,7 +8,7 @@ library(ggvis)
 library(rmarkdown)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
-rawrmds<-c("ants2015.Rmd","lesions/lesions.Rmd","lastslide.Rmd")
+rawrmds<-c("ants2015.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","lastslide.Rmd")
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)

### 2014-09-02 lesions/lesions.Rmd
ENH:  Adding lesion stuff.

# Cortical thickness with lesions

## antsCorticalThickness.sh is adaptable!

1. Register subject (or single subject template) to normal template.

2. Transform lesion mask to normal template.

3. Create additional "lesion" prior, i.e. ```SmoothImage 3 ${lesionMask} 1 ${lesionPrior} 1```.

4.  Subtract out lesion prior from all other priors and keep values $\in [0,1]$.

## Modified template spatial priors

![](lesions/figures/lesionPrior.png)

## antsCorticalThickness.sh using lesion prior

![](lesions/figures/lesionSegmentation.png)

Only change to the command call is an additional '-c WM[7]' which means "combine
the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."

### 2014-09-03 README.R
WIP: regular update

@@ -8,7 +8,7 @@ library(ggvis)
 library(rmarkdown)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
-rawrmds<-c("ants2015.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","lastslide.Rmd")
+rawrmds<-c("ants2015.Rmd","background/background1.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","lastslide.Rmd")
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)

### 2014-09-03 ants2015.Rmd
WIP: regular update

@@
 This talk is online at [http://stnava.github.io/ANTs2015/](http://stnava.github.io/ANTs2015/) with colored [links](http://stnava.github.io/ANTs2015/) meant to be clicked for more information.
-
-## ANTs & Neuroscience
-
-We need statistical image analysis <br />at several scales in modern neuroscience
-
-* Macro: *in vivo* structural and functional MRI
-
-* Micro:  high-resolution post-mortem MRI links with in vivo MRI
-
-* Nano: neuron reconstruction ...
-
-* Solutions that are consistent across these scales have the potential
-to build multi-scale feature sets or templates and provide new
-insights into brain structure and function
-
-* E.g. Parcellation constraints based on histology, tractography, function ...
-
-* Statistical definitions of anatomy/pathology?
-
-* Reinvention of these solutions within each lab ... can we mitigate this?
-
-* Reduce, reuse, recycle ...
-
-# *ANTs* optimizes mathematically <br /> well-defined  <br /><span style="color:red;">objective functions</span>  <br />guided by <br /> <span style="color:red;">prior knowledge</span>  ...
-
-# plug *your ideas* <br />into our software: <br /> <span style="color:blue;"> <span style="color:red;">innovation, insight</span> <br />from biomedical data</span> ...
-
-## Diffeomorphisms
-
-<div align="center"><img width="1433" src="./figures/sillyputty.png" frameborder="0"></img></div>
-
-plausible physical modeling of large, invertible deformations
-
-"differentiable map with differentiable inverse"
-
-## ANTs: Beyond Registration
-
-![](./figures/antscapabilities.jpg)
-
-[Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)
-
-## Founding developers
-
-<div align="center"><img width="1433" src="./figures/bant2.png" frameborder="0"></img></div>
-
-## Long-term collaborators
-
-![](./figures/antscollab.jpg)
-
-$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
-
-## General purpose library for multivariate image registration, segmentation & statistical analysis tools
-
-* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.
-
-* Generic mathematical methods that are tunable for 
-application specific domains:  no-free lunch
-
-* Deep testing on multiple platforms ... osx, linux, windows.
-
-* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )
-
-```
-    An algorithm must use prior knowledge about a problem 
-    to do well on that problem 
-```
-
-# <span style="color:red;">Medical Image Registration</span> <br /> Fundamental tool for<br /> morphometry, segmentation,<br /> motion estimation and <br /> <span style="color:blue;">data cleaning</span>
-
-## Definitions
-
-* Registration $=$ estimate an "optimal" geometric mapping between image pairs or image sets (e.g. Affine)
-
-* Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)
-
-* <span style="color:grey;">
-Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)  </span>
-
-* Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)
-
-* <span style="color:grey;"> Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>
-
-* Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)
-
-* MALF: multi-atlas label fusion - using anatomical dictionaries to label new data
-
-* Solutions to challenging statistical image processing problems usually need elements from each of the above
-
-## The Technical Framework
-
-![](./figures/designprinciples.png)
-
-... and most of it multivariate.
-
-## [SyN](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC2276735/) for optimization symmetry
-![](./figures/fishSyN.png)
-Images deform symmetrically along the shape manifold.  This eliminates bias in the
-measurement of image differences.
-
-##  [SyN (link)](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC2276735/) Example
-
-<!-- syn example -->
-
-<div align="center"><iframe width="1220" height="730" src="http://www.youtube.com/embed/3I9RcRtpOvw" frameborder="0" allowfullscreen></iframe></div>
-
-[SyN movie](http://www.youtube.com/embed/3I9RcRtpOvw)
-
-## Concatenated transformation $+$ metric stages are necessary in real data
-
-0.  Initialize the mapping ( more on this later )
-
-1.  Start with a *rigid transformation*:  $I(x) \approx J(R(x))$ s.t. negative $MI$ is minimized
-
-2.  Follow by an *affine transformation*:  $I(x) \approx J(R(A(x)))$ s.t. negative $MI$ is minimized with fixed $R$
-
-3.  Finally, a *diffeomorphism*:  $I(x) \approx J(R(A(\phi(x))))$ s.t. $k$-neighborhood correlation $CC_k$ is minimized with fixed $R, A$
-
-4.  Output the *composite transform* $A \circ R$ as a matrix transformation and $\phi$ and $\phi^{-1}$ as deformation fields.
-
-standard in [recommended](http://stnava.github.io/ANTsDoc/) `antsRegistration` application scripts
-
-## Registration benefits from<br /> *optimal sampling strategy*
-
-* sampling for *both* the metric and the transformation
-
-* impacts scalability, memory, optimization accuracy, speed, robustness ...
-
-* could be done optimally *with massive improvements in performance*
-    * but needs investment in order to achieve "dream" registration scenario
-
-* important for new schemes that *elect* solutions from **anatomical or transformation** dictionaries
-
-* overall, relatively little translational work on this important problem in biomedical imaging
-
-## Sampling & feature selection: Multi-start
-
-![](./figures/multistart.png)
-
-Theoretical guarantee of global optimum: improves local optimizers.
-
-Default in `antsCorticalThickness` pipeline and `FSL`.
-
-## Sampling & feature selection: Biomedical imagery
-
-![](./figures/slides1.png)
-
-Initial configuration of data
-
-## Sampling & feature selection: Biomedical imagery
-
-![](./figures/slides2.png)
-
-Automatic feature selection
-
-## Sampling & feature selection: Biomedical imagery
-
-![](./figures/slides3.png)
-
-Resampling allows comparison & slide alignment and <br />
-validates the feature selection
-
-Dramatic reduction in computation time / memory requirements
-
-## Sampling & feature selection: Lesioned brains
-
-![](./figures/lesionedbrains.jpg)
-
-## Sampling & feature selection: Summary
-
-* we exploit these strategies to:
-    - accelerate
-    - focus 
-    - validate
-
-# Evaluation results
-
-## 
-![](./figures/evalhistory.png)
-
-## Anatomical dictionaries
-![](./figures/sata2013.png)
-
-we provided the *standard* registration results for $>$ 20,000 image pairs at [SATA 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events)
-
-## [label fusion (link)](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3049832/)
-![](./figures/sata2013.jpg)
-
-## Multiple metrics improve performance
-![](./figures/multivariateSATA.jpg)
-
-to our knowledge, ANTs is the only freely available system that can solve this problem in a fully multivariate manner.
-
-Hongzhi Wang won the "walk in the park" award for this work ...
-
-# Differentiable maps with<br /> differentiable inverse <br />$+$ *statistics in these spaces*
-
-## Brain templates as *high-dimensional averages*
-![](./figures/speciestemplates.png)
-
-## SyGN - templates and averages in deformation space
-
-![](figures/normvsnorm.png)
-from [miykael](http://miykael.github.io/nipype-beginner-s-guide/ANTS.html)
-
-[geodesic image averages](http://www.ncbi.nlm.nih.gov/pubmed/15501083)
-
-[optimal templates 2](http://www.ncbi.nlm.nih.gov/pubmed/19818860)
-
-[canine template](http://www.ncbi.nlm.nih.gov/pubmed/23284904)
-
-[chimpanzees](http://www.ncbi.nlm.nih.gov/pubmed/23516289)
-
-## Statistics in deformation space
-
-[AIBS movie](http://www.youtube.com/embed/8GgHG-rApiE)
-
-## Average Republican and Democratic congressmen
-
-<div align="center"><img src="figures/democrat_left_repub_right.png" frameborder="0"></img></div>
-
-[congress](http://ntustison.github.io/CongressionalFaceTemplates/)
-
-# ANTs versus Freesurfer:<br />  Quantifying *life span* brain health
-
-## ANTs versus Freesurfer:<br />  Quantifying *life span* brain health
-
-* Freesurfer is the historical standard for measuring cortical thickness
-
-* instead of using surfaces to measure cortical thickness, we use the image space *DiReCTly*
-
-* [see this section of a different talk](http://stnava.github.io/ANTsTalk/#/putting-it-all-together-can-we-quantify-life-span-brain-health-in-individuals-and-in-populations)
-
-* and this "big data" paper: [Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
-
-* comparison of prediction from automated cortical thickness measurement from 4 public datasets
-
-* $>$ 1200 subjects, age 7 to over 90 years old
-
-* *hint*: ANTs thickness measurements have higher prediction accuracy relative to Freesurfer ( implying we extract more information from the data )
-
-* ANTs methods consistently improve statistical power [eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/24687814), [syn](http://www.ncbi.nlm.nih.gov/pubmed/?term=syn+epstein+avants), [itkv4](http://www.ncbi.nlm.nih.gov/pubmed/24817849) ...
-also, see [Schwarz CG, et al.](http://www.ncbi.nlm.nih.gov/pubmed/24650605) re: TBSS and related work in fMRI [Miller, PNAS](http://www.ncbi.nlm.nih.gov/pubmed/15980148), [Azab, et al in Hippocampus](http://www.ncbi.nlm.nih.gov/pubmed/24167043).
-
-# Registration & statistics:<br /> Frontiers and innovation
-
-## multivariate statistical fields arise from fused modalities
-
-![images at measurement fields](figures/statisticalfields.png)
-
-*Many opportunities for statistical advancements*
-
-## Scientific Data 2014
-![](./figures/ptbp2.png)
-
-## "Network" of predictors for age
-
-...
-
-## ITK+ANTs+R = <span style="color:red;">*ANTsR*</span>
-
-## Agnostic statistics
-![](./figures/antsrex.jpg)
-
-[McMillan et al.](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3961542/)
-
-## A Quick <span style="color:grey;">*ANTsR*</span> example
-```{r loadantsr,results='hide',echo=FALSE,message=FALSE}
-library(ANTsR)
-```
-
-This is an executable *ANTsR* code block - *N*-dimensional statistics to go with 
-our *N*-dimensional image processing software!
-```{r loadimages,message=FALSE,warning=FALSE,results='hide'}
-library(ANTsR)
-dim<-2
-filename<-getANTsRData('r16')
-img<-antsImageRead( filename , dim )
-filename<-getANTsRData('r64')
-img2<-antsImageRead( filename , dim )
-mask<-getMask(img,50,max(img),T)
-mask2<-getMask(img,150,max(img),T)
-nvox<-sum( mask == 1 )
-nvox2<-sum( mask2 == 1 )
-```
-The brain has `r nvox` voxels ...
-
-## A Quick <span style="color:grey;">*ANTsR*</span> example
-
-Simulate a population morphometry study - a "VBM" ...
-```{r morph,results='hide'}
-simnum<-10
-imglist<-list()
-imglist2<-list()
-for ( i in 1:simnum ) {
-  img1sim<-antsImageClone(img)
-  img1sim[ mask==1 ]<-rnorm(nvox,mean=0.5)
-  img1sim[ mask2==1 ]<-rnorm(nvox2,mean=2.0)
-  img2sim<-antsImageClone(img2)
-  img2sim[ mask==1 ]<-rnorm(nvox,mean=0.20)
-  imglist<-lappend(imglist,img1sim)
-  imglist2<-lappend(imglist2,img2sim)
-}
-imglist<-lappend( imglist, imglist2 )
-mat<-imageListToMatrix( imglist, mask )
-DX<-factor( c( rep(0,simnum), rep(1,simnum) ) )
-mylmresults<-bigLMStats( lm( mat ~ DX ) )
-qvals<-p.adjust( mylmresults$pval.model ) 
-```
-The minimum q-value is `r min(qvals)` ...
-
-## Visualize the histograms of effects
-```{r vizmorph,results='hide'}
-whichvox<-qvals < 1.e-2
-voxdf<-data.frame( volume=c( as.numeric( mat[,whichvox] ) ), DX=DX )
-ggplot(voxdf, aes(volume, fill = DX)) + geom_density(alpha = 0.2)
-```
-
-## Visualize the anatomical distribution
-```{r vizmorph2hide,results='hide',echo=FALSE}
-betas<-antsImageClone(mask)
-betavec<-abs(mylmresults$beta.t[1,])
-betas[mask==1]<-betavec
-SmoothImage(dim,betas,1.5,betas)
-thresh<-paste(3.0,'x',max(betavec),sep='')
-ofn<-paste(figpath,'vizmorph2.jpg',sep='')
-```
-
-```{r vizmorph2,results='hide'}
-plotANTsImage(img,functional=list(betas),threshold=thresh,
-  outname=ofn)
-```
-
-![](`r ofn`)
-
-## Network visualization
-see `?plotBasicNetwork`
-```{r networkfn,results='hide',warning=FALSE,echo=FALSE,message=FALSE}
-ofn<-paste(figpath,'network',sep='')
-ofnpng<-paste(ofn,'.png',sep='')
-```
-```{r network,results='hide',warning=FALSE,echo=FALSE,message=FALSE,eval=FALSE}
-       mnit<-getANTsRData("mni")
-       mnit<-antsImageRead(mnit,3)
-       mnia<-getANTsRData("mnia")
-       mnia<-antsImageRead(mnia,3)
-       ThresholdImage(3,mnit,mnit,1,max(mnit))
-       ImageMath(3,mnit,"FillHoles",mnit)
-       cnt<-getCentroids( mnia, clustparam = 50 )
-       aalcnt<-cnt$centroids[1:90,]
-       brain<-renderSurfaceFunction( surfimg =list( mnit ) , alphasurf=0.1 ,smoothsval = 1.5 )
-       testweights<-matrix( rep( 0, 90*90 ) ,nrow=90)
-       testweights[31,37]<-1  # ant cingulate to hipp
-       testweights[31,36]<-2  # ant cingulate to post cingulate
-       testweights[11,65]<-3  # broca to angular 
-       plotBasicNetwork( centroids = aalcnt , brain , weights=testweights )
-       id<-par3d("userMatrix")
-       rid<-rotate3d( id , -pi/2, 1, 0, 0 )
-       rid2<-rotate3d( id , pi/2, 0, 0, 1 )
-       rid3<-rotate3d( id , -pi/2, 0, 0, 1 )
-       par3d(userMatrix = id ) 
-       dd<-make3ViewPNG(  rid, id, rid2,  ofn )
-       par3d(userMatrix = id ) 
-```
-![](`r ofnpng`)
-
-## The power of *ANTs* $+$ *R* $\rightarrow$<br /> <span style="color:red;">**Reproducible imaging science**</span>
-
-![](./figures/antsgoals.png)
-
-...
-used in ["Sparse canonical correlation analysis relates network-level atrophy to multivariate cognitive measures in a neurodegenerative population"](http://www.ncbi.nlm.nih.gov/pubmed/24096125) and several upcoming ...
-
-## Can we customize these methods for a challenging multivariate segmentation problem with clinical relevance?
-
-## Automated tumor segmentation from multiple MRI
-![](./figures/tumorsegmentation.png)
-
-## General theory tunable to specific domains:  *no-free lunch*
-![](./figures/brats.png)
-
-[BRATS 2013 Challenge](http://hal.inria.fr/docs/00/93/56/40/PDF/brats_preprint.pdf) **won** with [*ANTsR*](https://github.com/stnava/ANTsR)
-
-## Can we address subtle questions in brain and cognition via imaging-specific dimensionality reduction?
-
-##  [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/24852460) & [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=avants+SCCAN)
-
-## ANTs*R* $\rightarrow$ new insight <br />via better analytics
-
-Good software should fade into the background ... however ...
-
-<span style="color:red;">
- As is common in science, the first big breakthrough in our understanding ...
- [came from] an improvement in measurement.
-</span>
-
-<span style="color:blue;">
-> Daniel Kahnemann, *Thinking, Fast and Slow* (2011)
-</span>
-
-# Conclusion
-
-## Recap
-
-- Powerful, general-purpose, <span style="color:red;">well-evaluated</span> registration and segmentation.
-
-- Differentiable maps with differentiable inverse <span style="color:red;">$+$ statistics in these spaces</span>
-
-- Evaluated in multiple problem domains</span> via internal studies & open competition
-
-- Borg philosophy: <span style="color:red;">"best of"</span> from I/O, to processing to statistical methods
-
-- Open source, testing, many examples, consistent style, multiple platforms,  active community support ...
-
-- Integration with *R* $+$ novel tools for prediction, decoding, high-to-low dimensional statistics.
-
-- Collaborations with [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
-
-## Challenges: Computational and Scientific
-
-- Scalability
-    - **need to fuse feature selection methods with transformation optimization**
-    - **need to leverage existing ITK streaming infrastructure in application level tool**
-- Domain expertise: Customizable for specific problems but sometimes not specific enough
-- "Plausible physical modeling ..." - this should vary per problem ... but doesn't.
-    - a fabulous project would be to resolve this issue at a large-scale e.g. for reconstructing neurons, measuring white matter elaboration ...
-    - our prior FEM work is one potential solution
-- Rapid development: colleagues still need familiarity with compilation for latest ANTs features
-- Latest theoretical advances in registration not yet wrapped for users
-- Need more [Documentation](http://stnava.github.io/ANTs/)  & [testing](http://testing.psychiatry.uiowa.edu/CDash/index.php?project=ANTS) ...
-
-## Tools you can use for imaging science
-
-- Core developers:  *B. Avants, N. Tustison, H. J. Johnson, J. T. Duda*
-
-- Many contributors, including users ...
-
-- Multi-platform, multi-threaded C++ [stnava.github.io/ANTs](stnava.github.io/ANTs)
-
-- Developed in conjunction with [http://www.itk.org/](http://www.itk.org/)
-
-- R wrapping and extension [stnava.github.io/ANTsR](stnava.github.io/ANTsR)
-
-- rapid development, regular testing $+$ many eyes $\rightarrow$ bugs are shallow
-
-<img style="float: right" src="figures/penn.png" />
-<img style="float: left" src="figures/picsl.jpg" />
-
-# Analysis philosophy and <br /> published opinions
-
-## What is and *is not*<br /> image registration
-
-[*not* registration](http://www.ncbi.nlm.nih.gov/pubmed/23116330)
-
-## Voodoo in voxel-based analysis
-
-[logical circularity VBA](http://www.ncbi.nlm.nih.gov/pubmed/?term=logical+circularity+tustison)
-
-## Instrumentation bias in the use and evaluation of software
-
-[Instrumentation bias in the use and evaluation of software](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3766821/?report=reader)
-
-# References {#reffont}

### 2014-09-03 README.R

@@ -8,7 +8,7 @@ library(ggvis)
 library(rmarkdown)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
-rawrmds<-c("ants2015.Rmd","background/background1.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","lastslide.Rmd")
+rawrmds<-c("ants2015.Rmd","background/background1.Rmd","templates/templates.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","lastslide.Rmd")
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)

### 2014-09-03 ants2015build.Rmd
WIP: regular update

---
title: <span style="color:red;">How to build a house with<br />Advanced Normalization Tools (*ANTs*)</span>
author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)
bibliography: REFERENCES.bib
logo:    logo.jpg
output:
  pdf_document:
    toc: true
    highlight: zenburn
  beamer_presentation:
    toc: true
    fig_width: 7
    fig_height: 6
  html_document:
    toc: true
    theme: readable
  revealjs_presentation:
    pandoc_args: [ "--slide-level", "2" ]
    incremental: true
    widescreen: true
    smaller: false
    theme: night
    transition: fade
    highlight: zenburn
    center: true
    self_contained: false
  ioslides_presentation:
    css: atk.css
    incremental: false
    widescreen: true
    smaller: false
    fig_width: 5
---

```{r global options, include=FALSE}
library(rmarkdown)
library(knitr)
figpath<-'figures/'
opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
               warning=FALSE, message=FALSE)
```

##

<div align="center"><img src="./logo.png" frameborder="0"></img></div>

This talk is online at [http://stnava.github.io/ANTs2015/](http://stnava.github.io/ANTs2015/) with colored [links](http://stnava.github.io/ANTs2015/) meant to be clicked for more information.

# Background

## Founding developers

<div align="center"><img width="1800" src="./figures/bant2.png" frameborder="0"></img></div>

## Long-term collaborators

![](./figures/antscollab.jpg)

$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...

## Definitions

* Registration $=$ estimate an "optimal" geometric mapping between image pairs or image sets (e.g. Affine)

* Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)

* <span style="color:grey;">
Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)  </span>

* Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)

* <span style="color:grey;"> Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>

* Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)

* MALF: multi-atlas label fusion - using anatomical dictionaries to label new data

* Solutions to challenging statistical image processing problems usually need elements from each of the above

## Image mapping & perception: 1878

![](./figures/galton.png)

* Francis Galton: Can we see criminality in the face?

* (maybe he should have used ANTs?)

## Initial scope

![](./figures/ants_initial_scope.png)

## ANTs Lineage

![](./figures/lineage.jpg)

References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012

## Diffeomorphisms

<div align="center"><img width="1433" src="./figures/sillyputty.png" frameborder="0"></img></div>

plausible physical modeling of large, invertible deformations

"differentiable map with differentiable inverse"

## Fine-grained and flexible maps
![](./figures/highresdiffeos.jpg)

## ANTs: Beyond Registration

![](./figures/antscapabilities.jpg)

[Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)

## ANTs & Neuroscience

We need statistical image analysis <br />at several scales in modern neuroscience

* Macro: *in vivo* structural and functional MRI

* Micro:  high-resolution post-mortem MRI links with in vivo MRI

* Nano: neuron reconstruction ...

* Solutions that are consistent across these scales have the potential
to build multi-scale feature sets or templates and provide new
insights into brain structure and function

* E.g. Parcellation constraints based on histology, tractography, function ...

* Statistical definitions of anatomy/pathology?

* Reinvention of these solutions within each lab ... can we mitigate this?

* Reduce, reuse, recycle ...

## Financial impact

* The **high error rate** in software makes testing for quality assurance critically important.

* Bugs exist **Everywhere**: so don't freak out if we admit we have bugs:  we're just being honest ( and not all devs are )

* Virtually every business in the United States now depends on software for development, production, distribution, and after-sales support of products and services.

* A 2002 NIST study estimated the direct costs to the software supply chain due to failure to identify (**successfully test for**) "bugs"

* We are better at this than most ... **not perfect**

* The estimate of direct costs compiled from industry survey data for the U.S. economy was **\$60 billion per year**

* ... this estimate did not include costs to end users such as lost business (for example, the cost of shutting down the New York Mercantile Exchange in 1998 due to a software failure).

## ANTs: Saving society \$\$\$

starting with neuroscience ...

## General purpose library for multivariate image registration, segmentation & statistical analysis tools

* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.

* Generic mathematical methods that are tunable for 
application specific domains:  no-free lunch

* Deep testing on multiple platforms ... osx, linux, windows.

* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )

```
    An algorithm must use prior knowledge about a problem 
    to do well on that problem 
```

## Words of warning

![](figures/handsaw.jpg)

simple and nearly self-explanatory

## Words of warning

![](figures/Chainsaw.jpg)

documentation is important

# Optimal Templates

## "Optimal" templates (?)

* unbiased wrt measurement space

* space is non-linear: reference matters

* encodes prior information: still just averages (usually)

* concept extends across modalities, anatomy, temporality, etc

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.060.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.061.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.062.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.063.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.064.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.065.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.066.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.067.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.068.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.069.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.070.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.071.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.072.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.073.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.074.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.075.jpg)

## Faces, brains, whatever ...

![](templates/figures/WashUJan2011.076.jpg)

## Templates from ANTs Colleagues ( not us )

![](templates/figures/templates_ants_colleagues.png)
## longitudinal

work

# Cortical thickness with lesions

## antsCorticalThickness.sh is adaptable!

1. Register subject (or single subject template) to normal template.

2. Transform lesion mask to normal template.

3. Create additional "lesion" prior, i.e. ```SmoothImage 3 ${lesionMask} 1 ${lesionPrior} 1```.

4.  Subtract out lesion prior from all other priors and keep values $\in [0,1]$.

## Modified template spatial priors

![](lesions/figures/lesionPrior.png)

## antsCorticalThickness.sh using lesion prior

![](lesions/figures/lesionSegmentation.png)

Only change to the command call is an additional '-c WM[7]' which means "combine
the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."

# References

### 2014-09-03 background/background1.Rmd
WIP: regular update

--- 2014-09-03 ants2015build.Rmd
@@
----
-title: <span style="color:red;">How to build a house with<br />Advanced Normalization Tools (*ANTs*)</span>
-author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)
-bibliography: REFERENCES.bib
-logo:    logo.jpg
-output:
-  pdf_document:
-    toc: true
-    highlight: zenburn
-  beamer_presentation:
-    toc: true
-    fig_width: 7
-    fig_height: 6
-  html_document:
-    toc: true
-    theme: readable
-  revealjs_presentation:
-    pandoc_args: [ "--slide-level", "2" ]
-    incremental: true
-    widescreen: true
-    smaller: false
-    theme: night
-    transition: fade
-    highlight: zenburn
-    center: true
-    self_contained: false
-  ioslides_presentation:
-    css: atk.css
-    incremental: false
-    widescreen: true
-    smaller: false
-    fig_width: 5
----
-
-```{r global options, include=FALSE}
-library(rmarkdown)
-library(knitr)
-figpath<-'figures/'
-opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
-               warning=FALSE, message=FALSE)
-```
-
-##
-
-<div align="center"><img src="./logo.png" frameborder="0"></img></div>
-
-This talk is online at [http://stnava.github.io/ANTs2015/](http://stnava.github.io/ANTs2015/) with colored [links](http://stnava.github.io/ANTs2015/) meant to be clicked for more information.
-
 # Background
@@
 documentation is important
-
-# Optimal Templates
-
-## "Optimal" templates (?)
-
-* unbiased wrt measurement space
-
-* space is non-linear: reference matters
-
-* encodes prior information: still just averages (usually)
-
-* concept extends across modalities, anatomy, temporality, etc
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.060.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.061.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.062.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.063.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.064.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.065.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.066.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.067.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.068.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.069.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.070.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.071.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.072.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.073.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.074.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.075.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.076.jpg)
-
-## Templates from ANTs Colleagues ( not us )
-
-![](templates/figures/templates_ants_colleagues.png)
-## longitudinal
-
-work
-
-# Cortical thickness with lesions
-
-## antsCorticalThickness.sh is adaptable!
-
-1. Register subject (or single subject template) to normal template.
-
-2. Transform lesion mask to normal template.
-
-3. Create additional "lesion" prior, i.e. ```SmoothImage 3 ${lesionMask} 1 ${lesionPrior} 1```.
-
-4.  Subtract out lesion prior from all other priors and keep values $\in [0,1]$.
-
-## Modified template spatial priors
-
-![](lesions/figures/lesionPrior.png)
-
-## antsCorticalThickness.sh using lesion prior
-
-![](lesions/figures/lesionSegmentation.png)
-
-Only change to the command call is an additional '-c WM[7]' which means "combine
-the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."
-
-# References

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@
 
-<div align="center"><img src="./logo.png" frameborder="0"></img></div>
+<div align="center"><img src="./figures/brian_and_edie_sedgwick.jpg" frameborder="0"></img></div>
 
@@
 
+BBA & NT
+
 ## Long-term collaborators
@@
 $+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
+
+##
+
+![](./figures/lion.png)
 
@@
 
-## ANTs: Beyond Registration
-
-![](./figures/antscapabilities.jpg)
-
-[Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)
-
-## ANTs & Neuroscience
-
-We need statistical image analysis <br />at several scales in modern neuroscience
-
-* Macro: *in vivo* structural and functional MRI
-
-* Micro:  high-resolution post-mortem MRI links with in vivo MRI
-
-* Nano: neuron reconstruction ...
-
-* Solutions that are consistent across these scales have the potential
-to build multi-scale feature sets or templates and provide new
-insights into brain structure and function
-
-* E.g. Parcellation constraints based on histology, tractography, function ...
-
-* Statistical definitions of anatomy/pathology?
-
-* Reinvention of these solutions within each lab ... can we mitigate this?
-
-* Reduce, reuse, recycle ...
-
-## Financial impact
-
-* The **high error rate** in software makes testing for quality assurance critically important.
-
-* Bugs exist **Everywhere**: so don't freak out if we admit we have bugs:  we're just being honest ( and not all devs are )
-
-* Virtually every business in the United States now depends on software for development, production, distribution, and after-sales support of products and services.
-
-* A 2002 NIST study estimated the direct costs to the software supply chain due to failure to identify (**successfully test for**) "bugs"
-
-* We are better at this than most ... **not perfect**
-
-* The estimate of direct costs compiled from industry survey data for the U.S. economy was **\$60 billion per year**
-
-* ... this estimate did not include costs to end users such as lost business (for example, the cost of shutting down the New York Mercantile Exchange in 1998 due to a software failure).
-
-## ANTs: Saving society \$\$\$
-
-starting with neuroscience ...
+... to correct a misconception about diffeomorphisms ...
 
@@
     to do well on that problem
+
+## ANTs: Beyond Registration
+
+![](./figures/antscapabilities.jpg)
+
+[Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)
+
 ```
 
-## Words of warning
+## On documentation
 
@@
 
-## Words of warning
+## On documentation
 
@@
 documentation is important
+
+## On documentation
+
+![](figures/blindmen.jpg)
 

### 2014-09-03 background/background1.Rmd
WIP: regular update

@@
 documentation is important
+
+## On documentation
+
+![](figures/blindmen.jpg)

### 2014-09-03 impact/impact1.Rmd
WIP: regular update

# ANTs Impact

## ANTs Statistics

![](impact/figures/antsvisitors.png)

## ANTs & Neuroscience

We need statistical image analysis <br />at several scales in modern neuroscience

* Macro: *in vivo* structural and functional MRI

* Micro:  high-resolution post-mortem MRI links with in vivo MRI

* Nano: neuron reconstruction ...

* Solutions that are consistent across these scales have the potential
to build multi-scale feature sets or templates and provide new
insights into brain structure and function

* E.g. Parcellation constraints based on histology, tractography, function ...

* Statistical definitions of anatomy/pathology?

* Reinvention of these solutions within each lab ... can we mitigate this?

* Reduce, reuse, recycle ...

## Financial impact

* The **high error rate** in software makes testing for quality assurance critically important.

* Bugs exist **Everywhere**: so don't freak out if we admit we have bugs:  we're just being honest ( and not all devs are )

* Virtually every business in the United States now depends on software for development, production, distribution, and after-sales support of products and services.

* A 2002 NIST study estimated the direct costs to the software supply chain due to failure to identify (**successfully test for**) "bugs"

* We are better at this than most ... **not perfect**

* The estimate of direct costs compiled from industry survey data for the U.S. economy was **\$60 billion per year**

* ... this estimate did not include costs to end users such as lost business (for example, the cost of shutting down the New York Mercantile Exchange in 1998 due to a software failure).

## ANTs: Saving society \$\$\$

starting with neuroscience ...

### 2014-09-03 ants2015.Rmd
WIP: regular update

@@
 ---
-title: <span style="color:red;">How to build a house with<br />Advanced Normalization Tools (*ANTs*)</span>
+title: <span style="color:red;">Build a house with<br />Advanced Normalization Tools (*ANTs*)</span>
 author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@
 ---
-title: <span style="color:red;">How to build a house with<br />Advanced Normalization Tools (*ANTs*)</span>
+title: <span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>
 author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)
@@
 
+... just do a better registration (tell story) ...
+
 ## ANTs Lineage
@@
     to do well on that problem 
+```
 

### 2014-09-03 background/background1.Rmd
WIP: regular update

@@
 ![](./figures/lion.png)
+
+a pride: common way of doing things
 
@@
 ![](./figures/ants_initial_scope.png)
+
+... just do a better registration (tell story) ...
 
@@
 ![](figures/blindmen.jpg)
+
+... developers can be equally blind to deficiencies
+
+while users are equally blind to what we provide!

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@
 
+... developers can be blind to doc deficiencies
+
+while users are blind to what we provide!
+
 # Optimal Templates
@@
 
+see [ANTs site](stnava.github.io/ANTs) and [ANTs Documentation page](stnava.github.io/ANTsDoc)
+
 ## Templates from ANTs Colleagues ( not us )
@@
 ![](templates/figures/templates_ants_colleagues.png)
+
 ## longitudinal

### 2014-09-03 longitudinal/longitudinal.Rmd
WIP: regular update

--- 2014-09-03 ants2015build.Rmd
@@
----
-title: <span style="color:red;">How to build a house with<br />Advanced Normalization Tools (*ANTs*)</span>
-author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)
-bibliography: REFERENCES.bib
-logo:    logo.jpg
-output:
-  pdf_document:
-    toc: true
-    highlight: zenburn
-  beamer_presentation:
-    toc: true
-    fig_width: 7
-    fig_height: 6
-  html_document:
-    toc: true
-    theme: readable
-  revealjs_presentation:
-    pandoc_args: [ "--slide-level", "2" ]
-    incremental: true
-    widescreen: true
-    smaller: false
-    theme: night
-    transition: fade
-    highlight: zenburn
-    center: true
-    self_contained: false
-  ioslides_presentation:
-    css: atk.css
-    incremental: false
-    widescreen: true
-    smaller: false
-    fig_width: 5
----
+## ANTs longitudinal pipeline
 
-```{r global options, include=FALSE}
-library(rmarkdown)
-library(knitr)
-figpath<-'figures/'
-opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
-               warning=FALSE, message=FALSE)
-```
+![](figures/longpipe.png)
 
-##
+see [link to paper](http://link.springer.com/chapter/10.1007/978-3-642-15705-9_40)
 
-<div align="center"><img src="./figures/brian_and_edie_sedgwick.jpg" frameborder="0"></img></div>
+and [unbiased analysis paper](http://www.ncbi.nlm.nih.gov/pubmed/20005963)
 
-This talk is online at [http://stnava.github.io/ANTs2015/](http://stnava.github.io/ANTs2015/) with colored [links](http://stnava.github.io/ANTs2015/) meant to be clicked for more information.
+plus [longitudinal recommendation paper](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3581852/)
 
-# Background
+## ANTs longitudinal pipeline
 
-## Founding developers
-
-<div align="center"><img width="1800" src="./figures/bant2.png" frameborder="0"></img></div>
-
-BBA & NT
-
-## Long-term collaborators
-
-![](./figures/antscollab.jpg)
-
-$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
-
-##
-
-![](./figures/lion.png)
-
-## Definitions
-
-* Registration $=$ estimate an "optimal" geometric mapping between image pairs or image sets (e.g. Affine)
-
-* Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)
-
-* <span style="color:grey;">
-Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)  </span>
-
-* Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)
-
-* <span style="color:grey;"> Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>
-
-* Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)
-
-* MALF: multi-atlas label fusion - using anatomical dictionaries to label new data
-
-* Solutions to challenging statistical image processing problems usually need elements from each of the above
-
-## Image mapping & perception: 1878
-
-![](./figures/galton.png)
-
-* Francis Galton: Can we see criminality in the face?
-
-* (maybe he should have used ANTs?)
-
-## Initial scope
-
-![](./figures/ants_initial_scope.png)
-
-## ANTs Lineage
-
-![](./figures/lineage.jpg)
-
-References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
-
-## Diffeomorphisms
-
-<div align="center"><img width="1433" src="./figures/sillyputty.png" frameborder="0"></img></div>
-
-plausible physical modeling of large, invertible deformations
-
-"differentiable map with differentiable inverse"
-
-## Fine-grained and flexible maps
-![](./figures/highresdiffeos.jpg)
-
-... to correct a misconception about diffeomorphisms ...
-
-## General purpose library for multivariate image registration, segmentation & statistical analysis tools
-
-* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.
-
-* Generic mathematical methods that are tunable for 
-application specific domains:  no-free lunch
-
-* Deep testing on multiple platforms ... osx, linux, windows.
-
-* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )
-
-```
-    An algorithm must use prior knowledge about a problem 
-    to do well on that problem
-
-## ANTs: Beyond Registration
-
-![](./figures/antscapabilities.jpg)
-
-[Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)
-
-```
-
-## On documentation
-
-![](figures/handsaw.jpg)
-
-simple and nearly self-explanatory
-
-## On documentation
-
-![](figures/Chainsaw.jpg)
-
-documentation is important
-
-## On documentation
-
-![](figures/blindmen.jpg)
-
-# Optimal Templates
-
-## "Optimal" templates (?)
-
-* unbiased wrt measurement space
-
-* space is non-linear: reference matters
-
-* encodes prior information: still just averages (usually)
-
-* concept extends across modalities, anatomy, temporality, etc
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.060.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.061.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.062.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.063.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.064.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.065.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.066.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.067.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.068.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.069.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.070.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.071.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.072.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.073.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.074.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.075.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.076.jpg)
-
-## Templates from ANTs Colleagues ( not us )
-
-![](templates/figures/templates_ants_colleagues.png)
-## longitudinal
-
-work
-
-# Cortical thickness with lesions
-
-## antsCorticalThickness.sh is adaptable!
-
-1. Register subject (or single subject template) to normal template.
-
-2. Transform lesion mask to normal template.
-
-3. Create additional "lesion" prior, i.e. ```SmoothImage 3 ${lesionMask} 1 ${lesionPrior} 1```.
-
-4.  Subtract out lesion prior from all other priors and keep values $\in [0,1]$.
-
-## Modified template spatial priors
-
-![](lesions/figures/lesionPrior.png)
-
-## antsCorticalThickness.sh using lesion prior
-
-![](lesions/figures/lesionSegmentation.png)
-
-Only change to the command call is an additional '-c WM[7]' which means "combine
-the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."
-
-# References
+![](figures/longpipeex.png)

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@
 
+# ANTs Impact
+
+## ANTs Statistics
+
+![](impact/figures/antsvisitors.png)
+
+## ANTs & Neuroscience
+
+We need statistical image analysis <br />at several scales in modern neuroscience
+
+* Macro: *in vivo* structural and functional MRI
+
+* Micro:  high-resolution post-mortem MRI links with in vivo MRI
+
+* Nano: neuron reconstruction ...
+
+* Solutions that are consistent across these scales have the potential
+to build multi-scale feature sets or templates and provide new
+insights into brain structure and function
+
+* E.g. Parcellation constraints based on histology, tractography, function ...
+
+* Statistical definitions of anatomy/pathology?
+
+* Reinvention of these solutions within each lab ... can we mitigate this?
+
+* Reduce, reuse, recycle ...
+
+## Financial impact
+
+* The **high error rate** in software makes testing for quality assurance critically important.
+
+* Bugs exist **Everywhere**: so don't freak out if we admit we have bugs:  we're just being honest ( and not all devs are )
+
+* Virtually every business in the United States now depends on software for development, production, distribution, and after-sales support of products and services.
+
+* A 2002 NIST study estimated the direct costs to the software supply chain due to failure to identify (**successfully test for**) "bugs"
+
+* We are better at this than most ... **not perfect**
+
+* The estimate of direct costs compiled from industry survey data for the U.S. economy was **\$60 billion per year**
+
+* ... this estimate did not include costs to end users such as lost business (for example, the cost of shutting down the New York Mercantile Exchange in 1998 due to a software failure).
+
+## ANTs: Saving society \$\$\$
+
+starting with neuroscience ...
+
 # Optimal Templates
@@
 
-## longitudinal
+# Evaluation
 
-work
+##
+
+![](evaluation/figures/evalhistory.png)
+
+# Longitudinal processing with ANTs
+
+## ANTs longitudinal pipeline
+
+![](longitudinal/figures/longpipe.png)
+
+see [link to paper](http://link.springer.com/chapter/10.1007/978-3-642-15705-9_40)
+
+and [unbiased analysis paper](http://www.ncbi.nlm.nih.gov/pubmed/20005963)
+
+plus [longitudinal recommendation paper](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3581852/)
+
+## ANTs longitudinal pipeline
+
+![](longitudinal/figures/longpipeex.png)
 

### 2014-09-03 README.R

@@ -8,7 +8,7 @@ library(ggvis)
 library(rmarkdown)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
-rawrmds<-c("ants2015.Rmd","background/background1.Rmd","templates/templates.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","lastslide.Rmd")
+rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","lastslide.Rmd")
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@
 
+... in a competitive world ...
+
 ## Definitions
@@
 
-* Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)
+* <span style="color:grey;"> Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)</span>
 
-* <span style="color:grey;">
-Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)  </span>
+* Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)
 
-* Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)
+* <span style="color:grey;">Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)</span>
 
-* <span style="color:grey;"> Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>
+* Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>
 
-* Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)
+* <span style="color:grey;">Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)</span>
 
@@
 
-* Solutions to challenging statistical image processing problems usually need elements from each of the above
+* <span style="color:grey;">Solutions to challenging statistical image processing problems usually need elements from each of the above</span>
 

### 2014-09-03 background/background1.Rmd
WIP: regular update

@@
 
-... developers can be equally blind to deficiencies
+... developers can be blind to doc deficiencies
 
-while users are equally blind to what we provide!
+while users are blind to what we provide!

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@
 
-![](evaluation/figures/evalhistory.png)
+<div align="center"><img width="2500" src="evaluation/figures/evalhistory.png" frameborder="0"></img></div>
 
@@
 
+## Questions driving *ANTs* ($+$ Refs.1)
+
+* how should we geometrically transform anatomical coordinates?
+
+    - [syn paper](http://www.ncbi.nlm.nih.gov/pubmed/17659998) - our geometric transformation model of choice
+    - [recent B-spline alternative/improvement](http://www.ncbi.nlm.nih.gov/pubmed/24409140)
+
+* how should we measure pairwise image similarity?
+
+    - [similarity metric evaluation](http://www.ncbi.nlm.nih.gov/pubmed/20851191) compares functions for computing rigid or affine transformations between images
+
+* what if this pair has rgb/vector/tensor voxels?
+
+    - [dti similarity](http://www.ncbi.nlm.nih.gov/pubmed/18041273)
+
+* how do we extend from pairs to hundreds or thousands of pairs of images?
+
+    - [optimal templates](http://www.ncbi.nlm.nih.gov/pubmed/?term=avants+optimal+template) and [spatial priors](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
+    - species specific templates/priors in [chimps](http://www.ncbi.nlm.nih.gov/pubmed/23516289) and [canines](http://www.ncbi.nlm.nih.gov/pubmed/23284904)
+    - [ants "big data"](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+freesurfer)
+
+* how do we fuse multiple modality images at the subject and population levels?
+
+    - [ants auxiliary modality study](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+logical+circularity)
+
+## Questions driving *ANTs* ($+$ Refs.2)
+
+* can diffeomorphisms [improve cortical thickness measurement](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+freesurfer)?
+
+* how might we efficiently cluster the statistical fields that arise in image analysis?
+
+    - [Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation and [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison)
+    - [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants) for sparse imaging-specific PCA
+
+* how to cluster such fields when we have supervision?
+
+    - [sparse canonical correlation analysis for neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants)
+    - [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460)
+    - [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) - powerful expert systems for segmentation
+
+* how do we implement a fully multivariate *interpretable* brain and behavior study?
+
+    - [SCCAN for imaging & cognition](http://www.ncbi.nlm.nih.gov/pubmed/?term=sccan+avants)
+
+* how do we extend these ideas to functional MRI & decoding?
+
+    - [recent unpublished software](http://stnava.github.io/RKRNS/) 
+    - [recent work with Ben Kandel](..not yet...)
+
+## *ANTs* longitudinal analysis
+
+* Longitudinal image processing issues
+    - [registration induced bias](http://www.ncbi.nlm.nih.gov/pubmed/20005963)
+    - [general & TBI-specific issues in longitudinal analysis](http://www.ncbi.nlm.nih.gov/pubmed/23549059)
+    - [reproducibility of CBF](http://www.ncbi.nlm.nih.gov/pubmed/22517961)
+    - [structure-specific analysis](http://www.ncbi.nlm.nih.gov/pubmed/22306801)
+
+* An early study of longitudinal cortical change in ALS
+    - [ALS atrophy rates](http://www.ncbi.nlm.nih.gov/pubmed/16317254)
+
+* Extension of standard-setting ants cortical thickness pipeline to longitudinal data
+    - [DynANTs (unpublished)](https://github.com/stnava/DynANTs)
+
+## Challenges: Computational and Scientific
+
+- Scalability: **need to fuse feature selection methods with transformation optimization**
+- Scalability: **need to leverage existing ITK streaming infrastructure in application level tool**
+- Domain expertise: Customizable for specific problems but sometimes not specific enough
+- Rapid development: colleagues still need familiarity with compilation for latest ANTs features
+- Latest theoretical advances in registration not yet wrapped for users
+- Need more [Documentation](http://stnava.github.io/ANTs/)  & [testing](http://testing.psychiatry.uiowa.edu/CDash/index.php?project=ANTS) ...
+
+## Recap
+
+- Powerful, general-purpose, <span style="color:red;">well-evaluated</span> registration and segmentation.
+
+- Differentiable maps with differentiable inverse <span style="color:red;">$+$ statistics in these spaces</span>
+
+- Evaluated in multiple problem domains</span> via internal studies & open competition
+
+- Borg philosophy: <span style="color:red;">"best of"</span> from I/O, to processing to statistical methods
+
+- Open source, testing, many examples, consistent style, multiple platforms,  active community support ...
+
+- Integration with *R* $+$ novel tools for prediction, decoding, high-to-low dimensional statistics.
+
+- Collaborations with [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
+
+## Tools you can use for imaging science
+
+- Core developers:  *B. Avants, N. Tustison, H. J. Johnson, J. T. Duda*
+
+- Many contributors, including users ...
+
+- Multi-platform, multi-threaded C++ [stnava.github.io/ANTs](stnava.github.io/ANTs)
+
+- Developed in conjunction with [http://www.itk.org/](http://www.itk.org/)
+
+- R wrapping and extension [stnava.github.io/ANTsR](stnava.github.io/ANTsR)
+
+- rapid development, regular testing $+$ many eyes $\rightarrow$ bugs are shallow
+
+<img style="float: right" src="figures/penn.png" />
+<img style="float: left" src="figures/picsl.jpg" />
+
 # References

### 2014-09-03 conclusion/conclusion.Rmd
WIP: regular update

--- 2014-09-03 ants2015build.Rmd
@@
----
-title: <span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>
-author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)
-bibliography: REFERENCES.bib
-logo:    logo.jpg
-output:
-  pdf_document:
-    toc: true
-    highlight: zenburn
-  beamer_presentation:
-    toc: true
-    fig_width: 7
-    fig_height: 6
-  html_document:
-    toc: true
-    theme: readable
-  revealjs_presentation:
-    pandoc_args: [ "--slide-level", "2" ]
-    incremental: true
-    widescreen: true
-    smaller: false
-    theme: night
-    transition: fade
-    highlight: zenburn
-    center: true
-    self_contained: false
-  ioslides_presentation:
-    css: atk.css
-    incremental: false
-    widescreen: true
-    smaller: false
-    fig_width: 5
----
-
-```{r global options, include=FALSE}
-library(rmarkdown)
-library(knitr)
-figpath<-'figures/'
-opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
-               warning=FALSE, message=FALSE)
-```
-
-##
-
-<div align="center"><img src="./figures/brian_and_edie_sedgwick.jpg" frameborder="0"></img></div>
-
-This talk is online at [http://stnava.github.io/ANTs2015/](http://stnava.github.io/ANTs2015/) with colored [links](http://stnava.github.io/ANTs2015/) meant to be clicked for more information.
-
-# Background
-
-## Founding developers
-
-<div align="center"><img width="1800" src="./figures/bant2.png" frameborder="0"></img></div>
-
-BBA & NT
-
-## Long-term collaborators
-
-![](./figures/antscollab.jpg)
-
-$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
-
-##
-
-![](./figures/lion.png)
-
-a pride: common way of doing things
-
-... in a competitive world ...
-
-## Definitions
-
-* Registration $=$ estimate an "optimal" geometric mapping between image pairs or image sets (e.g. Affine)
-
-* <span style="color:grey;"> Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)</span>
-
-* Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)
-
-* <span style="color:grey;">Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)</span>
-
-* Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>
-
-* <span style="color:grey;">Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)</span>
-
-* MALF: multi-atlas label fusion - using anatomical dictionaries to label new data
-
-* <span style="color:grey;">Solutions to challenging statistical image processing problems usually need elements from each of the above</span>
-
-## Image mapping & perception: 1878
-
-![](./figures/galton.png)
-
-* Francis Galton: Can we see criminality in the face?
-
-* (maybe he should have used ANTs?)
-
-## Initial scope
-
-![](./figures/ants_initial_scope.png)
-
-... just do a better registration (tell story) ...
-
-## ANTs Lineage
-
-![](./figures/lineage.jpg)
-
-References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
-
-## Diffeomorphisms
-
-<div align="center"><img width="1433" src="./figures/sillyputty.png" frameborder="0"></img></div>
-
-plausible physical modeling of large, invertible deformations
-
-"differentiable map with differentiable inverse"
-
-## Fine-grained and flexible maps
-![](./figures/highresdiffeos.jpg)
-
-... to correct a misconception about diffeomorphisms ...
-
-## General purpose library for multivariate image registration, segmentation & statistical analysis tools
-
-* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.
-
-* Generic mathematical methods that are tunable for 
-application specific domains:  no-free lunch
-
-* Deep testing on multiple platforms ... osx, linux, windows.
-
-* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )
-
-```
-    An algorithm must use prior knowledge about a problem 
-    to do well on that problem 
-```
-
-## ANTs: Beyond Registration
-
-![](./figures/antscapabilities.jpg)
-
-[Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)
-
-```
-
-## On documentation
-
-![](figures/handsaw.jpg)
-
-simple and nearly self-explanatory
-
-## On documentation
-
-![](figures/Chainsaw.jpg)
-
-documentation is important
-
-## On documentation
-
-![](figures/blindmen.jpg)
-
-... developers can be blind to doc deficiencies
-
-while users are blind to what we provide!
-
-# ANTs Impact
-
-## ANTs Statistics
-
-![](impact/figures/antsvisitors.png)
-
-## ANTs & Neuroscience
-
-We need statistical image analysis <br />at several scales in modern neuroscience
-
-* Macro: *in vivo* structural and functional MRI
-
-* Micro:  high-resolution post-mortem MRI links with in vivo MRI
-
-* Nano: neuron reconstruction ...
-
-* Solutions that are consistent across these scales have the potential
-to build multi-scale feature sets or templates and provide new
-insights into brain structure and function
-
-* E.g. Parcellation constraints based on histology, tractography, function ...
-
-* Statistical definitions of anatomy/pathology?
-
-* Reinvention of these solutions within each lab ... can we mitigate this?
-
-* Reduce, reuse, recycle ...
-
-## Financial impact
-
-* The **high error rate** in software makes testing for quality assurance critically important.
-
-* Bugs exist **Everywhere**: so don't freak out if we admit we have bugs:  we're just being honest ( and not all devs are )
-
-* Virtually every business in the United States now depends on software for development, production, distribution, and after-sales support of products and services.
-
-* A 2002 NIST study estimated the direct costs to the software supply chain due to failure to identify (**successfully test for**) "bugs"
-
-* We are better at this than most ... **not perfect**
-
-* The estimate of direct costs compiled from industry survey data for the U.S. economy was **\$60 billion per year**
-
-* ... this estimate did not include costs to end users such as lost business (for example, the cost of shutting down the New York Mercantile Exchange in 1998 due to a software failure).
-
-## ANTs: Saving society \$\$\$
-
-starting with neuroscience ...
-
-# Optimal Templates
-
-## "Optimal" templates (?)
-
-* unbiased wrt measurement space
-
-* space is non-linear: reference matters
-
-* encodes prior information: still just averages (usually)
-
-* concept extends across modalities, anatomy, temporality, etc
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.060.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.061.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.062.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.063.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.064.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.065.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.066.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.067.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.068.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.069.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.070.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.071.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.072.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.073.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.074.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.075.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.076.jpg)
-
-see [ANTs site](stnava.github.io/ANTs) and [ANTs Documentation page](stnava.github.io/ANTsDoc)
-
-## Templates from ANTs Colleagues ( not us )
-
-![](templates/figures/templates_ants_colleagues.png)
-
-# Evaluation
-
-##
-
-<div align="center"><img width="2500" src="evaluation/figures/evalhistory.png" frameborder="0"></img></div>
-
-# Longitudinal processing with ANTs
-
-## ANTs longitudinal pipeline
-
-![](longitudinal/figures/longpipe.png)
-
-see [link to paper](http://link.springer.com/chapter/10.1007/978-3-642-15705-9_40)
-
-and [unbiased analysis paper](http://www.ncbi.nlm.nih.gov/pubmed/20005963)
-
-plus [longitudinal recommendation paper](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3581852/)
-
-## ANTs longitudinal pipeline
-
-![](longitudinal/figures/longpipeex.png)
-
-# Cortical thickness with lesions
-
-## antsCorticalThickness.sh is adaptable!
-
-1. Register subject (or single subject template) to normal template.
-
-2. Transform lesion mask to normal template.
-
-3. Create additional "lesion" prior, i.e. ```SmoothImage 3 ${lesionMask} 1 ${lesionPrior} 1```.
-
-4.  Subtract out lesion prior from all other priors and keep values $\in [0,1]$.
-
-## Modified template spatial priors
-
-![](lesions/figures/lesionPrior.png)
-
-## antsCorticalThickness.sh using lesion prior
-
-![](lesions/figures/lesionSegmentation.png)
-
-Only change to the command call is an additional '-c WM[7]' which means "combine
-the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."
-
 ## Questions driving *ANTs* ($+$ Refs.1)
@@
 <img style="float: left" src="figures/picsl.jpg" />
-
-# References

### 2014-09-03 README.R

@@ -8,7 +8,7 @@ library(ggvis)
 library(rmarkdown)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
-rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","lastslide.Rmd")
+rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@
 
-<div align="center"><img width="2500" src="evaluation/figures/evalhistory.png" frameborder="0"></img></div>
+<div align="center"><img width="3500" src="evaluation/figures/evalhistory.png" frameborder="0"></img></div>
 
@@
 the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."
+# Wrap-up & Conclusions
 

### 2014-09-03 evaluation/antsvfreesurfer.Rmd
WIP: regular update

# ANTs versus Freesurfer:<br />  Quantifying *life span* brain health

## "Big data" problem from public resources
![](./figures/lifebrains.jpg)

TOT, NKI, IXI, Oasis, ADNI ... several thousand images

## ANTs versus Freesurfer:<br />  Quantifying *life span* brain health

* Freesurfer is the historical standard for measuring cortical thickness

* instead of using surfaces to measure cortical thickness, we use the image space *DiReCTly*

* [see this section of a different talk](http://stnava.github.io/ANTsTalk/#/putting-it-all-together-can-we-quantify-life-span-brain-health-in-individuals-and-in-populations)

* and this "big data" paper: [Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements](http://www.ncbi.nlm.nih.gov/pubmed/24879923)

* comparison of prediction from automated cortical thickness measurement from 4 public datasets

* $>$ 1200 subjects, age 7 to over 90 years old

* *hint*: ANTs thickness measurements have higher prediction accuracy relative to Freesurfer ( implying we extract more information from the data )

* ANTs methods consistently improve statistical power [eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/24687814), [syn](http://www.ncbi.nlm.nih.gov/pubmed/?term=syn+epstein+avants), [itkv4](http://www.ncbi.nlm.nih.gov/pubmed/24817849) ... also, see [Schwarz CG, et al.](http://www.ncbi.nlm.nih.gov/pubmed/24650605) re: TBSS and related work in fMRI [Miller, PNAS](http://www.ncbi.nlm.nih.gov/pubmed/15980148), [Azab, et al in Hippocampus](http://www.ncbi.nlm.nih.gov/pubmed/24167043).

## ANTS vs Freesurfer

<div align="center"><img height="350" src="./figures/evaluation.png" frameborder="0"></img></div>

## *ANTs* vs Freesurfer 2
![](./figures/antsvfreesurfer2.png)

## *ANTs* MALF Labeling
![](./figures/antsatroposn4malf.png)

## The *ANTs* structural brain mapping pipeline

![](./figures/pipeline.png)

[*Large-scale evaluation of *ANTs* and FreeSurfer cortical thickness measurements*, NeuroImage 2014.*](http://www.ncbi.nlm.nih.gov/pubmed/24879923)

All software components are open source and part of the Advanced Normalization Tools (ANTs) repository.

## Basic components of the pipeline

<div align="center"><img height="350" src="./figures/components.png" frameborder="0"></img></div>

1. template building (offline)
2. brain extraction
3. cortical thickness estimation
4. cortical parcellation

## Template building

*Tailor data to your specific cohort*

<div align="center"><img height="350" src="./figures/templates.png" frameborder="0"></img></div>

* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
* Acquisition and anonymization (e.g. defacing) protocols are often different.

## Template building (cont.)

<div align="center"><img height="350" src="./figures/templatePriors.png" frameborder="0"></img></div>

Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
to produce auxiliary images which are used for brain extraction and brain segmentation.

## Brain extraction

<div align="center"><img height="380" src="./figures/brainExtraction.png" frameborder="0"></img></div>

Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)

## Brain segmentation

<div align="center"><img height="350" src="./figures/brainSegmentation.png" frameborder="0"></img></div>

Randomly selected healthy individuals.  Atropos gets good performance across ages.

## Cortical thickness estimation

<div align="center"><img height="250" src="./figures/corticalThicknessEstimation.png" frameborder="0"></img></div>

In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@
 
+## Templates unlock modalities
+
+![](figures/ptbp2.png)
+
 # Evaluation
@@
 <div align="center"><img width="3500" src="evaluation/figures/evalhistory.png" frameborder="0"></img></div>
+
+# ANTs versus Freesurfer:<br />  Quantifying *life span* brain health
+
+## "Big data" problem from public resources
+![](./figures/lifebrains.jpg)
+
+TOT, NKI, IXI, Oasis, ADNI ... several thousand images
+
+## ANTs versus Freesurfer:<br />  Quantifying *life span* brain health
+
+* Freesurfer is the historical standard for measuring cortical thickness
+
+* instead of using surfaces to measure cortical thickness, we use the image space *DiReCTly*
+
+* [see this section of a different talk](http://stnava.github.io/ANTsTalk/#/putting-it-all-together-can-we-quantify-life-span-brain-health-in-individuals-and-in-populations)
+
+* and this "big data" paper: [Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
+
+* comparison of prediction from automated cortical thickness measurement from 4 public datasets
+
+* $>$ 1200 subjects, age 7 to over 90 years old
+
+* *hint*: ANTs thickness measurements have higher prediction accuracy relative to Freesurfer ( implying we extract more information from the data )
+
+* ANTs methods consistently improve statistical power [eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/24687814), [syn](http://www.ncbi.nlm.nih.gov/pubmed/?term=syn+epstein+avants), [itkv4](http://www.ncbi.nlm.nih.gov/pubmed/24817849) ...
+also, see [Schwarz CG, et al.](http://www.ncbi.nlm.nih.gov/pubmed/24650605) re: TBSS and related work in fMRI [Miller, PNAS](http://www.ncbi.nlm.nih.gov/pubmed/15980148), [Azab, et al in Hippocampus](http://www.ncbi.nlm.nih.gov/pubmed/24167043).
+
+## Cortical thickness estimation
+
+<div align="center"><img height="250" src="./figures/corticalThicknessEstimation.png" frameborder="0"></img></div>
+
+In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
+
+# New work
 
@@
 the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."
+
 # Wrap-up & Conclusions

### 2014-09-03 evaluation/antsvfreesurfer.Rmd
WIP: regular update

@@
 
-## ANTS vs Freesurfer
-
-<div align="center"><img height="350" src="./figures/evaluation.png" frameborder="0"></img></div>
-
-## *ANTs* vs Freesurfer 2
-![](./figures/antsvfreesurfer2.png)
-
-## *ANTs* MALF Labeling
-![](./figures/antsatroposn4malf.png)
-
-## The *ANTs* structural brain mapping pipeline
-
-![](./figures/pipeline.png)
-
-[*Large-scale evaluation of *ANTs* and FreeSurfer cortical thickness measurements*, NeuroImage 2014.*](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
-
-All software components are open source and part of the Advanced Normalization Tools (ANTs) repository.
-
-## Basic components of the pipeline
-
-<div align="center"><img height="350" src="./figures/components.png" frameborder="0"></img></div>
-
-1. template building (offline)
-2. brain extraction
-3. cortical thickness estimation
-4. cortical parcellation
-
-## Template building
-
-*Tailor data to your specific cohort*
-
-<div align="center"><img height="350" src="./figures/templates.png" frameborder="0"></img></div>
-
-* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
-* Acquisition and anonymization (e.g. defacing) protocols are often different.
-
-## Template building (cont.)
-
-<div align="center"><img height="350" src="./figures/templatePriors.png" frameborder="0"></img></div>
-
-Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
-to produce auxiliary images which are used for brain extraction and brain segmentation.
-
-## Brain extraction
-
-<div align="center"><img height="380" src="./figures/brainExtraction.png" frameborder="0"></img></div>
-
-Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
-the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
-
-## Brain segmentation
-
-<div align="center"><img height="350" src="./figures/brainSegmentation.png" frameborder="0"></img></div>
-
-Randomly selected healthy individuals.  Atropos gets good performance across ages.
-
 ## Cortical thickness estimation

### 2014-09-03 README.R

@@ -8,7 +8,7 @@ library(ggvis)
 library(rmarkdown)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
-rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
+rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@
 
+# Registration & statistics:<br /> Frontiers and innovation
+
+## multivariate statistical fields arise from fused modalities
+
+![images at measurement fields](figures/statisticalfields.png)
+
+*Many opportunities for statistical advancements*
+
+## ITK+ANTs+R = <span style="color:red;">*ANTsR*</span>
+
+## Agnostic statistics
+![](./figures/antsrex.jpg)
+
+[McMillan et al.](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3961542/)
+
+## A Quick <span style="color:grey;">*ANTsR*</span> example
+```{r loadantsr,results='hide',echo=FALSE,message=FALSE}
+library(ANTsR)
+```
+
+This is an executable *ANTsR* code block - *N*-dimensional statistics to go with 
+our *N*-dimensional image processing software!
+```{r loadimages,message=FALSE,warning=FALSE,results='hide'}
+library(ANTsR)
+dim<-2
+filename<-getANTsRData('r16')
+img<-antsImageRead( filename , dim )
+filename<-getANTsRData('r64')
+img2<-antsImageRead( filename , dim )
+mask<-getMask(img,50,max(img),T)
+mask2<-getMask(img,150,max(img),T)
+nvox<-sum( mask == 1 )
+nvox2<-sum( mask2 == 1 )
+```
+The brain has `r nvox` voxels ...
+
+## A Quick <span style="color:grey;">*ANTsR*</span> example
+
+Simulate a population morphometry study - a "VBM" ...
+```{r morph,results='hide'}
+simnum<-10
+imglist<-list()
+imglist2<-list()
+for ( i in 1:simnum ) {
+  img1sim<-antsImageClone(img)
+  img1sim[ mask==1 ]<-rnorm(nvox,mean=0.5)
+  img1sim[ mask2==1 ]<-rnorm(nvox2,mean=2.0)
+  img2sim<-antsImageClone(img2)
+  img2sim[ mask==1 ]<-rnorm(nvox,mean=0.20)
+  imglist<-lappend(imglist,img1sim)
+  imglist2<-lappend(imglist2,img2sim)
+}
+imglist<-lappend( imglist, imglist2 )
+mat<-imageListToMatrix( imglist, mask )
+DX<-factor( c( rep(0,simnum), rep(1,simnum) ) )
+mylmresults<-bigLMStats( lm( mat ~ DX ) )
+qvals<-p.adjust( mylmresults$pval.model ) 
+```
+The minimum q-value is `r min(qvals)` ...
+
+## Visualize the histograms of effects
+```{r vizmorph,results='hide'}
+whichvox<-qvals < 1.e-2
+voxdf<-data.frame( volume=c( as.numeric( mat[,whichvox] ) ), DX=DX )
+ggplot(voxdf, aes(volume, fill = DX)) + geom_density(alpha = 0.2)
+```
+
+## Visualize the anatomical distribution
+```{r vizmorph2hide,results='hide',echo=FALSE}
+betas<-antsImageClone(mask)
+betavec<-abs(mylmresults$beta.t[1,])
+betas[mask==1]<-betavec
+SmoothImage(dim,betas,1.5,betas)
+thresh<-paste(3.0,'x',max(betavec),sep='')
+ofn<-paste(figpath,'vizmorph2.jpg',sep='')
+```
+
+```{r vizmorph2,results='hide'}
+plotANTsImage(img,functional=list(betas),threshold=thresh,
+  outname=ofn)
+```
+
+![](`r ofn`)
+
+## Network visualization
+see `?plotBasicNetwork`
+```{r networkfn,results='hide',warning=FALSE,echo=FALSE,message=FALSE}
+ofn<-paste(figpath,'network',sep='')
+ofnpng<-paste(ofn,'.png',sep='')
+```
+```{r network,results='hide',warning=FALSE,echo=FALSE,message=FALSE,eval=T}
+       mnit<-getANTsRData("mni")
+       mnit<-antsImageRead(mnit,3)
+       mnia<-getANTsRData("mnia")
+       mnia<-antsImageRead(mnia,3)
+       ThresholdImage(3,mnit,mnit,1,max(mnit))
+       ImageMath(3,mnit,"FillHoles",mnit)
+       cnt<-getCentroids( mnia, clustparam = 50 )
+       aalcnt<-cnt$centroids[1:90,]
+       brain<-renderSurfaceFunction( surfimg =list( mnit ) , alphasurf=0.1 ,smoothsval = 1.5 )
+       testweights<-matrix( rep( 0, 90*90 ) ,nrow=90)
+       testweights[31,37]<-1  # ant cingulate to hipp
+       testweights[31,36]<-2  # ant cingulate to post cingulate
+       testweights[11,65]<-3  # broca to angular 
+       plotBasicNetwork( centroids = aalcnt , brain , weights=testweights )
+       id<-par3d("userMatrix")
+       rid<-rotate3d( id , -pi/2, 1, 0, 0 )
+       rid2<-rotate3d( id , pi/2, 0, 0, 1 )
+       rid3<-rotate3d( id , -pi/2, 0, 0, 1 )
+       par3d(userMatrix = id ) 
+       dd<-make3ViewPNG(  rid, id, rid2,  ofn )
+       par3d(userMatrix = id ) 
+```
+![](`r ofnpng`)
+
+## The power of *ANTs* $+$ *R* $\rightarrow$<br /> <span style="color:red;">**Reproducible imaging science**</span>
+
+![](./figures/antsgoals.png)
+
+...
+used in ["Sparse canonical correlation analysis relates network-level atrophy to multivariate cognitive measures in a neurodegenerative population"](http://www.ncbi.nlm.nih.gov/pubmed/24096125) and several upcoming ...
+
 # Wrap-up & Conclusions

### 2014-09-03 README.R

@@ -8,7 +8,7 @@ library(ggvis)
 library(rmarkdown)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
-rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
+rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)

### 2014-09-03 antsr/antsrdemo.Rmd
WIP: regular update

--- 2014-09-03 ants2015build.Rmd
@@
----
-title: <span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>
-author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)
-bibliography: REFERENCES.bib
-logo:    logo.jpg
-output:
-  pdf_document:
-    toc: true
-    highlight: zenburn
-  beamer_presentation:
-    toc: true
-    fig_width: 7
-    fig_height: 6
-  html_document:
-    toc: true
-    theme: readable
-  revealjs_presentation:
-    pandoc_args: [ "--slide-level", "2" ]
-    incremental: true
-    widescreen: true
-    smaller: false
-    theme: night
-    transition: fade
-    highlight: zenburn
-    center: true
-    self_contained: false
-  ioslides_presentation:
-    css: atk.css
-    incremental: false
-    widescreen: true
-    smaller: false
-    fig_width: 5
----
-
-```{r global options, include=FALSE}
-library(rmarkdown)
-library(knitr)
-figpath<-'figures/'
-opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
-               warning=FALSE, message=FALSE)
-```
-
-##
-
-<div align="center"><img src="./figures/brian_and_edie_sedgwick.jpg" frameborder="0"></img></div>
-
-This talk is online at [http://stnava.github.io/ANTs2015/](http://stnava.github.io/ANTs2015/) with colored [links](http://stnava.github.io/ANTs2015/) meant to be clicked for more information.
-
-# Background
-
-## Founding developers
-
-<div align="center"><img width="1800" src="./figures/bant2.png" frameborder="0"></img></div>
-
-BBA & NT
-
-## Long-term collaborators
-
-![](./figures/antscollab.jpg)
-
-$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
-
-##
-
-![](./figures/lion.png)
-
-a pride: common way of doing things
-
-... in a competitive world ...
-
-## Definitions
-
-* Registration $=$ estimate an "optimal" geometric mapping between image pairs or image sets (e.g. Affine)
-
-* <span style="color:grey;"> Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)</span>
-
-* Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)
-
-* <span style="color:grey;">Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)</span>
-
-* Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>
-
-* <span style="color:grey;">Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)</span>
-
-* MALF: multi-atlas label fusion - using anatomical dictionaries to label new data
-
-* <span style="color:grey;">Solutions to challenging statistical image processing problems usually need elements from each of the above</span>
-
-## Image mapping & perception: 1878
-
-![](./figures/galton.png)
-
-* Francis Galton: Can we see criminality in the face?
-
-* (maybe he should have used ANTs?)
-
-## Initial scope
-
-![](./figures/ants_initial_scope.png)
-
-... just do a better registration (tell story) ...
-
-## ANTs Lineage
-
-![](./figures/lineage.jpg)
-
-References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
-
-## Diffeomorphisms
-
-<div align="center"><img width="1433" src="./figures/sillyputty.png" frameborder="0"></img></div>
-
-plausible physical modeling of large, invertible deformations
-
-"differentiable map with differentiable inverse"
-
-## Fine-grained and flexible maps
-![](./figures/highresdiffeos.jpg)
-
-... to correct a misconception about diffeomorphisms ...
-
-## General purpose library for multivariate image registration, segmentation & statistical analysis tools
-
-* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.
-
-* Generic mathematical methods that are tunable for 
-application specific domains:  no-free lunch
-
-* Deep testing on multiple platforms ... osx, linux, windows.
-
-* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )
-
-```
-    An algorithm must use prior knowledge about a problem 
-    to do well on that problem 
-```
-
-## ANTs: Beyond Registration
-
-![](./figures/antscapabilities.jpg)
-
-[Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)
-
-```
-
-## On documentation
-
-![](figures/handsaw.jpg)
-
-simple and nearly self-explanatory
-
-## On documentation
-
-![](figures/Chainsaw.jpg)
-
-documentation is important
-
-## On documentation
-
-![](figures/blindmen.jpg)
-
-... developers can be blind to doc deficiencies
-
-while users are blind to what we provide!
-
-# ANTs Impact
-
-## ANTs Statistics
-
-![](impact/figures/antsvisitors.png)
-
-## ANTs & Neuroscience
-
-We need statistical image analysis <br />at several scales in modern neuroscience
-
-* Macro: *in vivo* structural and functional MRI
-
-* Micro:  high-resolution post-mortem MRI links with in vivo MRI
-
-* Nano: neuron reconstruction ...
-
-* Solutions that are consistent across these scales have the potential
-to build multi-scale feature sets or templates and provide new
-insights into brain structure and function
-
-* E.g. Parcellation constraints based on histology, tractography, function ...
-
-* Statistical definitions of anatomy/pathology?
-
-* Reinvention of these solutions within each lab ... can we mitigate this?
-
-* Reduce, reuse, recycle ...
-
-## Financial impact
-
-* The **high error rate** in software makes testing for quality assurance critically important.
-
-* Bugs exist **Everywhere**: so don't freak out if we admit we have bugs:  we're just being honest ( and not all devs are )
-
-* Virtually every business in the United States now depends on software for development, production, distribution, and after-sales support of products and services.
-
-* A 2002 NIST study estimated the direct costs to the software supply chain due to failure to identify (**successfully test for**) "bugs"
-
-* We are better at this than most ... **not perfect**
-
-* The estimate of direct costs compiled from industry survey data for the U.S. economy was **\$60 billion per year**
-
-* ... this estimate did not include costs to end users such as lost business (for example, the cost of shutting down the New York Mercantile Exchange in 1998 due to a software failure).
-
-## ANTs: Saving society \$\$\$
-
-starting with neuroscience ...
-
-# Optimal Templates
-
-## "Optimal" templates (?)
-
-* unbiased wrt measurement space
-
-* space is non-linear: reference matters
-
-* encodes prior information: still just averages (usually)
-
-* concept extends across modalities, anatomy, temporality, etc
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.060.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.061.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.062.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.063.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.064.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.065.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.066.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.067.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.068.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.069.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.070.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.071.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.072.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.073.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.074.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.075.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.076.jpg)
-
-see [ANTs site](stnava.github.io/ANTs) and [ANTs Documentation page](stnava.github.io/ANTsDoc)
-
-## Templates from ANTs Colleagues ( not us )
-
-![](templates/figures/templates_ants_colleagues.png)
-
-## Templates unlock modalities
-
-![](figures/ptbp2.png)
-
-# Evaluation
-
-##
-
-<div align="center"><img width="3500" src="evaluation/figures/evalhistory.png" frameborder="0"></img></div>
-
-# ANTs versus Freesurfer:<br />  Quantifying *life span* brain health
-
-## "Big data" problem from public resources
-![](./figures/lifebrains.jpg)
-
-TOT, NKI, IXI, Oasis, ADNI ... several thousand images
-
-## ANTs versus Freesurfer:<br />  Quantifying *life span* brain health
-
-* Freesurfer is the historical standard for measuring cortical thickness
-
-* instead of using surfaces to measure cortical thickness, we use the image space *DiReCTly*
-
-* [see this section of a different talk](http://stnava.github.io/ANTsTalk/#/putting-it-all-together-can-we-quantify-life-span-brain-health-in-individuals-and-in-populations)
-
-* and this "big data" paper: [Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
-
-* comparison of prediction from automated cortical thickness measurement from 4 public datasets
-
-* $>$ 1200 subjects, age 7 to over 90 years old
-
-* *hint*: ANTs thickness measurements have higher prediction accuracy relative to Freesurfer ( implying we extract more information from the data )
-
-* ANTs methods consistently improve statistical power [eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/24687814), [syn](http://www.ncbi.nlm.nih.gov/pubmed/?term=syn+epstein+avants), [itkv4](http://www.ncbi.nlm.nih.gov/pubmed/24817849) ...
-also, see [Schwarz CG, et al.](http://www.ncbi.nlm.nih.gov/pubmed/24650605) re: TBSS and related work in fMRI [Miller, PNAS](http://www.ncbi.nlm.nih.gov/pubmed/15980148), [Azab, et al in Hippocampus](http://www.ncbi.nlm.nih.gov/pubmed/24167043).
-
-## Cortical thickness estimation
-
-<div align="center"><img height="250" src="./figures/corticalThicknessEstimation.png" frameborder="0"></img></div>
-
-In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
-
-# New work
-
-# Longitudinal processing with ANTs
-
-## ANTs longitudinal pipeline
-
-![](longitudinal/figures/longpipe.png)
-
-see [link to paper](http://link.springer.com/chapter/10.1007/978-3-642-15705-9_40)
-
-and [unbiased analysis paper](http://www.ncbi.nlm.nih.gov/pubmed/20005963)
-
-plus [longitudinal recommendation paper](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3581852/)
-
-## ANTs longitudinal pipeline
-
-![](longitudinal/figures/longpipeex.png)
-
-# Cortical thickness with lesions
-
-## antsCorticalThickness.sh is adaptable!
-
-1. Register subject (or single subject template) to normal template.
-
-2. Transform lesion mask to normal template.
-
-3. Create additional "lesion" prior, i.e. ```SmoothImage 3 ${lesionMask} 1 ${lesionPrior} 1```.
-
-4.  Subtract out lesion prior from all other priors and keep values $\in [0,1]$.
-
-## Modified template spatial priors
-
-![](lesions/figures/lesionPrior.png)
-
-## antsCorticalThickness.sh using lesion prior
-
-![](lesions/figures/lesionSegmentation.png)
-
-Only change to the command call is an additional '-c WM[7]' which means "combine
-the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."
-
 # Registration & statistics:<br /> Frontiers and innovation
@@
 used in ["Sparse canonical correlation analysis relates network-level atrophy to multivariate cognitive measures in a neurodegenerative population"](http://www.ncbi.nlm.nih.gov/pubmed/24096125) and several upcoming ...
-
-# Wrap-up & Conclusions
-
-## Questions driving *ANTs* ($+$ Refs.1)
-
-* how should we geometrically transform anatomical coordinates?
-
-    - [syn paper](http://www.ncbi.nlm.nih.gov/pubmed/17659998) - our geometric transformation model of choice
-    - [recent B-spline alternative/improvement](http://www.ncbi.nlm.nih.gov/pubmed/24409140)
-
-* how should we measure pairwise image similarity?
-
-    - [similarity metric evaluation](http://www.ncbi.nlm.nih.gov/pubmed/20851191) compares functions for computing rigid or affine transformations between images
-
-* what if this pair has rgb/vector/tensor voxels?
-
-    - [dti similarity](http://www.ncbi.nlm.nih.gov/pubmed/18041273)
-
-* how do we extend from pairs to hundreds or thousands of pairs of images?
-
-    - [optimal templates](http://www.ncbi.nlm.nih.gov/pubmed/?term=avants+optimal+template) and [spatial priors](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
-    - species specific templates/priors in [chimps](http://www.ncbi.nlm.nih.gov/pubmed/23516289) and [canines](http://www.ncbi.nlm.nih.gov/pubmed/23284904)
-    - [ants "big data"](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+freesurfer)
-
-* how do we fuse multiple modality images at the subject and population levels?
-
-    - [ants auxiliary modality study](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+logical+circularity)
-
-## Questions driving *ANTs* ($+$ Refs.2)
-
-* can diffeomorphisms [improve cortical thickness measurement](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+freesurfer)?
-
-* how might we efficiently cluster the statistical fields that arise in image analysis?
-
-    - [Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation and [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison)
-    - [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants) for sparse imaging-specific PCA
-
-* how to cluster such fields when we have supervision?
-
-    - [sparse canonical correlation analysis for neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants)
-    - [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460)
-    - [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) - powerful expert systems for segmentation
-
-* how do we implement a fully multivariate *interpretable* brain and behavior study?
-
-    - [SCCAN for imaging & cognition](http://www.ncbi.nlm.nih.gov/pubmed/?term=sccan+avants)
-
-* how do we extend these ideas to functional MRI & decoding?
-
-    - [recent unpublished software](http://stnava.github.io/RKRNS/) 
-    - [recent work with Ben Kandel](..not yet...)
-
-## *ANTs* longitudinal analysis
-
-* Longitudinal image processing issues
-    - [registration induced bias](http://www.ncbi.nlm.nih.gov/pubmed/20005963)
-    - [general & TBI-specific issues in longitudinal analysis](http://www.ncbi.nlm.nih.gov/pubmed/23549059)
-    - [reproducibility of CBF](http://www.ncbi.nlm.nih.gov/pubmed/22517961)
-    - [structure-specific analysis](http://www.ncbi.nlm.nih.gov/pubmed/22306801)
-
-* An early study of longitudinal cortical change in ALS
-    - [ALS atrophy rates](http://www.ncbi.nlm.nih.gov/pubmed/16317254)
-
-* Extension of standard-setting ants cortical thickness pipeline to longitudinal data
-    - [DynANTs (unpublished)](https://github.com/stnava/DynANTs)
-
-## Challenges: Computational and Scientific
-
-- Scalability: **need to fuse feature selection methods with transformation optimization**
-- Scalability: **need to leverage existing ITK streaming infrastructure in application level tool**
-- Domain expertise: Customizable for specific problems but sometimes not specific enough
-- Rapid development: colleagues still need familiarity with compilation for latest ANTs features
-- Latest theoretical advances in registration not yet wrapped for users
-- Need more [Documentation](http://stnava.github.io/ANTs/)  & [testing](http://testing.psychiatry.uiowa.edu/CDash/index.php?project=ANTS) ...
-
-## Recap
-
-- Powerful, general-purpose, <span style="color:red;">well-evaluated</span> registration and segmentation.
-
-- Differentiable maps with differentiable inverse <span style="color:red;">$+$ statistics in these spaces</span>
-
-- Evaluated in multiple problem domains</span> via internal studies & open competition
-
-- Borg philosophy: <span style="color:red;">"best of"</span> from I/O, to processing to statistical methods
-
-- Open source, testing, many examples, consistent style, multiple platforms,  active community support ...
-
-- Integration with *R* $+$ novel tools for prediction, decoding, high-to-low dimensional statistics.
-
-- Collaborations with [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
-
-## Tools you can use for imaging science
-
-- Core developers:  *B. Avants, N. Tustison, H. J. Johnson, J. T. Duda*
-
-- Many contributors, including users ...
-
-- Multi-platform, multi-threaded C++ [stnava.github.io/ANTs](stnava.github.io/ANTs)
-
-- Developed in conjunction with [http://www.itk.org/](http://www.itk.org/)
-
-- R wrapping and extension [stnava.github.io/ANTsR](stnava.github.io/ANTsR)
-
-- rapid development, regular testing $+$ many eyes $\rightarrow$ bugs are shallow
-
-<img style="float: right" src="figures/penn.png" />
-<img style="float: left" src="figures/picsl.jpg" />
-
-# References

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@
 ```
-```{r network,results='hide',warning=FALSE,echo=FALSE,message=FALSE,eval=T}
+```{r network,results='hide',warning=FALSE,echo=FALSE,message=FALSE,eval=F}
        mnit<-getANTsRData("mni")

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@
 
+## Reproducibility
+
+* Consider the recent paper [freesurfer, laplacian, DiReCT thickness in longitudinal stroke](http://ac.els-cdn.com/S2213158214001260/1-s2.0-S2213158214001260-main.pdf?_tid=8e6f5248-335d-11e4-ba4f-00000aab0f02&acdnat=1409743944_6615d59eb5709e6bcb1aca76450f7d93)
+
+* We "pre-wrote" a comment: [Instrumentation bias in the use and evaluation of scientific software](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3766821/?report=reader)
+
+* With these guys:
+
+* ![Luis Ibanez](figures/luis.jpg)
+
+* ![Torsten Rohlfing](figures/torsten.jpg)
+
+## Hired by Google
+
+* ![Luis Ibanez](figures/luis.jpg)
+
+* ![Torsten Rohlfing](figures/torsten.jpg)
+
+* ![Gang Song](figures/gang.jpg)
 # Optimal Templates
@@
 # New work
+
+## RKRNS
+
+[link](stnava.github.io/RKRNS)
+
+What mathematical encoding of language reflects both brain activity and 
+"our" understanding of semantics?
+
+## RIPMMARC: Imputation, strutural networks, etc.
+
+![](figures/ripmmarc_inter.png)
+
+## Big image registration
 

### 2014-09-03 impact/impact1.Rmd
WIP: regular update

@@
 starting with neuroscience ...
+
+## Reproducibility
+
+* Consider the recent paper [freesurfer, laplacian, DiReCT thickness in longitudinal stroke](http://ac.els-cdn.com/S2213158214001260/1-s2.0-S2213158214001260-main.pdf?_tid=8e6f5248-335d-11e4-ba4f-00000aab0f02&acdnat=1409743944_6615d59eb5709e6bcb1aca76450f7d93)
+
+* We "pre-wrote" a comment: [Instrumentation bias in the use and evaluation of scientific software](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3766821/?report=reader)
+
+* With these guys:
+
+* ![Luis Ibanez](figures/luis.jpg)
+
+* ![Torsten Rohlfing](figures/torsten.jpg)
+
+## Hired by Google
+
+* ![Luis Ibanez](figures/luis.jpg)
+
+* ![Torsten Rohlfing](figures/torsten.jpg)
+
+* ![Gang Song](figures/gang.jpg)

### 2014-09-03 ants2015build.Rmd
WIP: regular update

--- 2014-09-03 ants2015build.Rmd
@@
 
-## ANTs: Saving society \$\$\$
+## Reproducibility
 
-starting with neuroscience ...
+* Consider the recent paper: [Freesurfer, laplacian, DiReCT thickness in longitudinal stroke](http://ac.els-cdn.com/S2213158214001260/1-s2.0-S2213158214001260-main.pdf?_tid=8e6f5248-335d-11e4-ba4f-00000aab0f02&acdnat=1409743944_6615d59eb5709e6bcb1aca76450f7d93)
+
+* We "pre-wrote" a comment: [Instrumentation bias in the use and evaluation of scientific software](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3766821/?report=reader)
+
+* With these guys:
+
+* <img src="figures/luis.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right: 3px;"><img src="figures/torsten.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;">
+
+## Hired by Google
+
+<img src="figures/luis.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right: 3px;"><img src="figures/torsten.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;"><img src="figures/gang.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;">
 
@@
 # New work
+
+## RKRNS
+
+[link](stnava.github.io/RKRNS)
+
+What mathematical encoding of language reflects both brain activity and 
+"our" understanding of semantics?
+
+## RIPMARC: Imputation, strutural networks, etc.
+
+![](figures/ripmmarc_inter.png)
+
+MICCAI 2014, Neuroimage 2015
+
+## Big image registration
 

### 2014-09-03 impact/impact1.Rmd
WIP: regular update

--- 2014-09-03 impact/impact1.Rmd
@@
 
-## ANTs: Saving society \$\$\$
+## Reproducibility
 
-starting with neuroscience ...
+* Consider the recent paper: [Freesurfer, laplacian, DiReCT thickness in longitudinal stroke](http://ac.els-cdn.com/S2213158214001260/1-s2.0-S2213158214001260-main.pdf?_tid=8e6f5248-335d-11e4-ba4f-00000aab0f02&acdnat=1409743944_6615d59eb5709e6bcb1aca76450f7d93)
+
+* We "pre-wrote" a comment: [Instrumentation bias in the use and evaluation of scientific software](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3766821/?report=reader)
+
+* With these guys:
+
+* <img src="figures/luis.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right: 3px;"><img src="figures/torsten.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;">
+
+## Hired by Google
+
+<img src="figures/luis.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right: 3px;"><img src="figures/torsten.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;"><img src="figures/gang.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;">

### 2014-10-07 ants2015build.Rmd
WIP: regular update
WIP: for cfn meeting

--- 2014-09-03 ants2015build.Rmd
@@
 
-# Background
+# New work
 
-## Founding developers
+## RKRNS
 
-<div align="center"><img width="1800" src="./figures/bant2.png" frameborder="0"></img></div>
+[link](stnava.github.io/RKRNS)
 
-BBA & NT
+What mathematical encoding of language reflects both brain activity and 
+"our" understanding of semantics?
 
-## Long-term collaborators
+## RIPMARC: Imputation, strutural networks, etc.
 
-![](./figures/antscollab.jpg)
+![](figures/ripmmarc_inter.png)
 
-$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
+MICCAI 2014, Neuroimage 2015
 
-##
-
-![](./figures/lion.png)
-
-a pride: common way of doing things
-
-... in a competitive world ...
-
-## Definitions
-
-* Registration $=$ estimate an "optimal" geometric mapping between image pairs or image sets (e.g. Affine)
-
-* <span style="color:grey;"> Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)</span>
-
-* Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)
-
-* <span style="color:grey;">Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)</span>
-
-* Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>
-
-* <span style="color:grey;">Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)</span>
-
-* MALF: multi-atlas label fusion - using anatomical dictionaries to label new data
-
-* <span style="color:grey;">Solutions to challenging statistical image processing problems usually need elements from each of the above</span>
-
-## Image mapping & perception: 1878
-
-![](./figures/galton.png)
-
-* Francis Galton: Can we see criminality in the face?
-
-* (maybe he should have used ANTs?)
-
-## Initial scope
-
-![](./figures/ants_initial_scope.png)
-
-... just do a better registration (tell story) ...
-
-## ANTs Lineage
-
-![](./figures/lineage.jpg)
-
-References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
-
-## Diffeomorphisms
-
-<div align="center"><img width="1433" src="./figures/sillyputty.png" frameborder="0"></img></div>
-
-plausible physical modeling of large, invertible deformations
-
-"differentiable map with differentiable inverse"
-
-## Fine-grained and flexible maps
-![](./figures/highresdiffeos.jpg)
-
-... to correct a misconception about diffeomorphisms ...
-
-## General purpose library for multivariate image registration, segmentation & statistical analysis tools
-
-* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.
-
-* Generic mathematical methods that are tunable for 
-application specific domains:  no-free lunch
-
-* Deep testing on multiple platforms ... osx, linux, windows.
-
-* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )
-
-```
-    An algorithm must use prior knowledge about a problem 
-    to do well on that problem 
-```
-
-## ANTs: Beyond Registration
-
-![](./figures/antscapabilities.jpg)
-
-[Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)
-
-```
-
-## On documentation
-
-![](figures/handsaw.jpg)
-
-simple and nearly self-explanatory
-
-## On documentation
-
-![](figures/Chainsaw.jpg)
-
-documentation is important
-
-## On documentation
-
-![](figures/blindmen.jpg)
-
-... developers can be blind to doc deficiencies
-
-while users are blind to what we provide!
-
-# ANTs Impact
-
-## ANTs Statistics
-
-![](impact/figures/antsvisitors.png)
-
-## ANTs & Neuroscience
-
-We need statistical image analysis <br />at several scales in modern neuroscience
-
-* Macro: *in vivo* structural and functional MRI
-
-* Micro:  high-resolution post-mortem MRI links with in vivo MRI
-
-* Nano: neuron reconstruction ...
-
-* Solutions that are consistent across these scales have the potential
-to build multi-scale feature sets or templates and provide new
-insights into brain structure and function
-
-* E.g. Parcellation constraints based on histology, tractography, function ...
-
-* Statistical definitions of anatomy/pathology?
-
-* Reinvention of these solutions within each lab ... can we mitigate this?
-
-* Reduce, reuse, recycle ...
-
-## Financial impact
-
-* The **high error rate** in software makes testing for quality assurance critically important.
-
-* Bugs exist **Everywhere**: so don't freak out if we admit we have bugs:  we're just being honest ( and not all devs are )
-
-* Virtually every business in the United States now depends on software for development, production, distribution, and after-sales support of products and services.
-
-* A 2002 NIST study estimated the direct costs to the software supply chain due to failure to identify (**successfully test for**) "bugs"
-
-* We are better at this than most ... **not perfect**
-
-* The estimate of direct costs compiled from industry survey data for the U.S. economy was **\$60 billion per year**
-
-* ... this estimate did not include costs to end users such as lost business (for example, the cost of shutting down the New York Mercantile Exchange in 1998 due to a software failure).
-
-## ANTs: Saving society \$\$\$
-
-starting with neuroscience ...
-
-# Optimal Templates
-
-## "Optimal" templates (?)
-
-* unbiased wrt measurement space
-
-* space is non-linear: reference matters
-
-* encodes prior information: still just averages (usually)
-
-* concept extends across modalities, anatomy, temporality, etc
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.060.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.061.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.062.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.063.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.064.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.065.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.066.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.067.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.068.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.069.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.070.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.071.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.072.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.073.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.074.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.075.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.076.jpg)
-
-see [ANTs site](stnava.github.io/ANTs) and [ANTs Documentation page](stnava.github.io/ANTsDoc)
-
-## Templates from ANTs Colleagues ( not us )
-
-![](templates/figures/templates_ants_colleagues.png)
-
-## Templates unlock modalities
-
-![](figures/ptbp2.png)
-
-# Evaluation
-
-##
-
-<div align="center"><img width="3500" src="evaluation/figures/evalhistory.png" frameborder="0"></img></div>
-
-# ANTs versus Freesurfer:<br />  Quantifying *life span* brain health
-
-## "Big data" problem from public resources
-![](./figures/lifebrains.jpg)
-
-TOT, NKI, IXI, Oasis, ADNI ... several thousand images
-
-## ANTs versus Freesurfer:<br />  Quantifying *life span* brain health
-
-* Freesurfer is the historical standard for measuring cortical thickness
-
-* instead of using surfaces to measure cortical thickness, we use the image space *DiReCTly*
-
-* [see this section of a different talk](http://stnava.github.io/ANTsTalk/#/putting-it-all-together-can-we-quantify-life-span-brain-health-in-individuals-and-in-populations)
-
-* and this "big data" paper: [Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
-
-* comparison of prediction from automated cortical thickness measurement from 4 public datasets
-
-* $>$ 1200 subjects, age 7 to over 90 years old
-
-* *hint*: ANTs thickness measurements have higher prediction accuracy relative to Freesurfer ( implying we extract more information from the data )
-
-* ANTs methods consistently improve statistical power [eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/24687814), [syn](http://www.ncbi.nlm.nih.gov/pubmed/?term=syn+epstein+avants), [itkv4](http://www.ncbi.nlm.nih.gov/pubmed/24817849) ...
-also, see [Schwarz CG, et al.](http://www.ncbi.nlm.nih.gov/pubmed/24650605) re: TBSS and related work in fMRI [Miller, PNAS](http://www.ncbi.nlm.nih.gov/pubmed/15980148), [Azab, et al in Hippocampus](http://www.ncbi.nlm.nih.gov/pubmed/24167043).
-
-## Cortical thickness estimation
-
-<div align="center"><img height="250" src="./figures/corticalThicknessEstimation.png" frameborder="0"></img></div>
-
-In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
-
-# New work
+## Big image registration
 
@@
 ![](longitudinal/figures/longpipeex.png)
+
+## ANTs longitudinal pipeline: TBI
+
+![](longitudinal/figures/long_with_lesions_seg.png)
+
+## ANTs longitudinal pipeline: TBI
+
+![](longitudinal/figures/long_with_lesions_thick.png)
+
+## ANTs longitudinal pipeline
+
+![](longitudinal/figures/babystudy.png)
 

### 2014-10-07 README.R

@@ -9,6 +9,7 @@ library(rmarkdown)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
 rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
+rawrmds<-c("ants2015.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)

### 2014-10-07 README.R
WIP: for cfn meeting

@@ -9,7 +9,7 @@ library(rmarkdown)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
 rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
-rawrmds<-c("ants2015.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
+rawrmds<-c("ants2015.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)

### 2014-10-07 ants2015build.Rmd
WIP: for cfn meeting

@@
 This talk is online at [http://stnava.github.io/ANTs2015/](http://stnava.github.io/ANTs2015/) with colored [links](http://stnava.github.io/ANTs2015/) meant to be clicked for more information.
+
+# ANTs versus Freesurfer:<br />  Quantifying *life span* brain health
+
+## "Big data" problem from public resources
+![](./figures/lifebrains.jpg)
+
+TOT, NKI, IXI, Oasis, ADNI ... several thousand images
+
+## ANTs versus Freesurfer:<br />  Quantifying *life span* brain health
+
+* Freesurfer is the historical standard for measuring cortical thickness
+
+* instead of using surfaces to measure cortical thickness, we use the image space *DiReCTly*
+
+* [see this section of a different talk](http://stnava.github.io/ANTsTalk/#/putting-it-all-together-can-we-quantify-life-span-brain-health-in-individuals-and-in-populations)
+
+* and this "big data" paper: [Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
+
+* comparison of prediction from automated cortical thickness measurement from 4 public datasets
+
+* $>$ 1200 subjects, age 7 to over 90 years old
+
+* *hint*: ANTs thickness measurements have higher prediction accuracy relative to Freesurfer ( implying we extract more information from the data )
+
+* ANTs methods consistently improve statistical power [eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/24687814), [syn](http://www.ncbi.nlm.nih.gov/pubmed/?term=syn+epstein+avants), [itkv4](http://www.ncbi.nlm.nih.gov/pubmed/24817849) ...
+also, see [Schwarz CG, et al.](http://www.ncbi.nlm.nih.gov/pubmed/24650605) re: TBSS and related work in fMRI [Miller, PNAS](http://www.ncbi.nlm.nih.gov/pubmed/15980148), [Azab, et al in Hippocampus](http://www.ncbi.nlm.nih.gov/pubmed/24167043).
+
+## Cortical thickness estimation
+
+<div align="center"><img height="250" src="./figures/corticalThicknessEstimation.png" frameborder="0"></img></div>
+
+In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
 

### 2014-10-15 tools/n4/n4.Rmd
ENH:  Adding tools subfolder.

# N4

## Nonparametric nonuniform intensity normalization (N3)

* Developed at the Montreal Neurological Institute (John Sled, 1998)

* Part of the standard preprocessing protocol in large scale projects such as ADNI

* The traditional de facto standard in MRI bias correction
    + good performance
    + *public availability*

* Public availability --- set of perl scripts coordinating various C++ programs

* "*Let's incorporate N3 into ANTs!*"

## N3 adoption issues

![](./tools/n4/figures/whyN4.png)

<!-- regular html comment

<div align="center"><img src="./tools/n4/figures/whyN4.png" frameborder="0"></img></div>

-->

"*So let's re-implement N3 in ITK for ANTs users.*"

## N3 -> N4<sup>*</sup>

<p align = "middle"><small><sup>*</sup><u>N</u>ick's N3</small></p>

* comparative [evaluation](http://www.ncbi.nlm.nih.gov/pubmed/20378467)

* smaller spline distances (useful for higher magnet strengths)

* multiresolution

* weighted regional mask (used in [`antsAtroposN4.sh`](https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh))

* faster execution times

* less susceptible to noise

* _publicly available_

## N4 example

![](./tools/n4/figures/KKI2009_MPRAGE_slice150.png)

## Command line help

<font size="5", color="lightgrey">
```
$ N4BiasFieldCorrection -h

COMMAND:
     N4BiasFieldCorrection

OPTIONS:
     -d, --image-dimensionality 2/3/4
     -i, --input-image inputImageFilename
     -x, --mask-image maskImageFilename
     -r, --rescale-intensities 0/(1)
     -w, --weight-image weightImageFilename
     -s, --shrink-factor 1/2/3/4/...
     -c, --convergence [<numberOfIterations=50x50x50x50>,<convergenceThreshold=0.0>]
     -b, --bspline-fitting [splineDistance,<splineOrder=3>]
                           [initialMeshResolution,<splineOrder=3>]
     -t, --histogram-sharpening [<FWHM=0.15>,<wienerNoise=0.01>,<numberOfHistogramBins=200>]
     -o, --output correctedImage
                  [correctedImage,<biasField>]
     -h
     --help
```
</font>

### 2014-10-16 ants2015_GE.Rmd
ENH:  GE talk.

---
title: <span style="color:red;">Neuroimaging with<br>ANTs</span>
author:
bibliography: REFERENCES.bib
logo:    logo.jpg
output:
  pdf_document:
    toc: true
    highlight: zenburn
  beamer_presentation:
    toc: true
    fig_width: 7
    fig_height: 6
  html_document:
    toc: true
    theme: readable
  revealjs_presentation:
    pandoc_args: [ "--slide-level", "2" ]
    incremental: true
    widescreen: true
    smaller: false
    theme: night
    transition: fade
    highlight: zenburn
    center: true
    self_contained: false
  ioslides_presentation:
    css: atk.css
    incremental: false
    widescreen: true
    smaller: false
    fig_width: 5
---

```{r global options, include=FALSE}
library(rmarkdown)
library(knitr)
figpath<-'figures/'
opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
               warning=FALSE, message=FALSE)
```

# Background

##

![](./figures/brian_and_nick.png)

## ANTs development philosophy:<br><small>Assimilate the optimal components of other approaches</small>

![](./figures/BorgFirstContact.jpg)

_"We are the Borg. Your biological and technological distinctiveness will be added to our own. Resistance is futile."_

### 2014-10-16 competitions/competitions.Rmd
ENH:  GE talk.

# Competitions

##

![](./evaluation/figures/evalhistory.png)

## <span style="color:green;">BRATS 2013</span> <small>brain tumor segmentation</small>

![](./competitions/figures/brats2013results.png)

_"Optimal symmetric multimodal templates and concatenated random forests for
supervised brain tumor segmentation (simplified) with ANTsR"_

## <span style="color:green;">STACOM 2014</span> <small>cardiac motion estimation</small>

![](./competitions/figures/cardiacBSplineSyN.png)

A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140)

### 2014-10-16 evaluation/antsvfreesurfer2.Rmd
ENH:  GE talk.

# ANTs brain morphology<br><br>[<small>"*Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/24879923)

## Cortical thickness studies:
```{r, results='asis', echo = FALSE}
conditions <- c( "Huntington’s disease", "schizophrenia", "bipolar disorder",
                 "Alzheimer’s disease", "frontotemporal dementia", "Parkinson’s disease",
                 "Williams syndrome", "multiple sclerosis", "autism", "migraines",
                 "chronic smoking", "alcoholism", "cocaine addiction", "Tourette syndrome in children",
                 "scoliosis in female adolescents", "early-onset blindness", "chronic pancreatitis",
                 "obsessive-compulsive disorder", "ADHD", "obesity", "heritable depression",
                 "elderly depression", "age", "gender", "untreated male-to-female transsexuality",
                 "handedness", "intelligence", "athletic ability", "meditative practices", "musical ability",
                 "tendency toward criminality", "childhood sexual abuse in female adolescents",
                 "Tetris-playing ability in female adolescents", "traumatic brain injury" )

conditionsDF <- data.frame( Column1 = conditions[1:floor( 0.5*length(conditions) )], Column2 = conditions[( 1+floor( 0.5*length(conditions) ) ):length(conditions)] )
knitr::kable( conditionsDF )
```

## ANTs-related background

* Sandy, Brian, and <span style="color:red;">DiReCT</span>
  + used other tools such as FMRIB's Automated Segmentation Tool (FAST)
  + `KellySlater.cxx`
  * scripts "adequate for Penn data"
* `KellyKapowski.cxx` and `antsCorticalThickness.sh`
* _"Let's evaluate on open data."_
* and, eventually, _"Let's compare with FreeSurfer."_

## The ANTs structural brain mapping workflow

![](./evaluation/figures/pipeline.png)

## Basic components of the pipeline

<div align="center"><img height="350" src="./evaluation/figures/components.png" frameborder="0"></img></div>

1. template building (offline)
2. brain extraction
3. cortical thickness estimation
4. cortical parcellation

## Template building

*Tailor data to your specific cohort*

<div align="center"><img height="350" src="./evaluation/figures/templates.png" frameborder="0"></img></div>

* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
* Acquisition and anonymization (e.g. defacing) protocols are often different.

## Template building (cont.)

<div align="center"><img height="350" src="./evaluation/figures/templatePriors.png" frameborder="0"></img></div>

Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
to produce auxiliary images which are used for brain extraction and brain segmentation.

## Brain extraction comparison<br>ANTs vs. FreeSurfer

<div align="center"><img height="380" src="./evaluation/figures/brainExtraction.png" frameborder="0"></img></div>

Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)

## Brain segmentation

<div align="center"><img height="350" src="./evaluation/figures/brainSegmentation.png" frameborder="0"></img></div>

Randomly selected healthy individuals.  Atropos gets good performance across ages.

## Cortical thickness estimation

<div align="center"><img height="250" src="./evaluation/figures/corticalThicknessEstimation.png" frameborder="0"></img></div>

In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, ANTs diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.

## _But without ground truth, how does one evaluate the pipeline?_

* Use age and gender (demographic information) in training/prediction paradigm
* Public data sets (IXI, NKI, Oasis, MMRR)
* $>$ 1200 subjects, age 7 to over 90 years old

## Prediction from cortical thickness data:<br>gender and age

<div align="center"><img height="350" src="./evaluation/figures/evaluation.png" frameborder="0"></img></div>

## Regional importance comparison

$AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$

<div align="center"><img height="500" src="./evaluation/figures/antsvfreesurfer_importance.png" frameborder="0"></img></div>

ANTs (left) vs. FreeSurfer (right)

## Regional importance comparison (cont.)

<div align="center"><img height="550" src="./evaluation/figures/antsvfreesurfer_regionalPlots.png" frameborder="0"></img></div>

## All software components are open source and part of the ANTs repository.

# Cortical thickness extensions

### 2014-10-16 longitudinal/longitudinal.Rmd
WIP: regular update
WIP: for cfn meeting
ENH:  GE talk.

@@
+<!--
+# New work
+
+## RKRNS
+
+[link](http://stnava.github.io/RKRNS/)
+
+What mathematical encoding of language reflects both brain activity and
+"our" understanding of semantics?
+
+## RIPMARC: Imputation, strutural networks, etc.
+
+![](figures/ripmmarc_inter.png)
+
+MICCAI 2014, Neuroimage 2015
+
+## Big image registration
+-->
+
+# Longitudinal processing <!--with ANTs>
+
+<!--
 ## ANTs longitudinal pipeline
 
-![](figures/longpipe.png)
+![](longitudinal/figures/longpipe.png)
 
@@
 plus [longitudinal recommendation paper](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3581852/)
+-->
 
+## `antsLongitudinalCorticalThickness.sh`
+
+![](longitudinal/figures/longpipeex.png)
+
+## Longitudinal TBI with lesions (segmentation)
+
+![](longitudinal/figures/long_with_lesions_seg.png)
+
+## Longitudinal TBI with lesions (cortical thickness)
+
+![](longitudinal/figures/long_with_lesions_thick.png)
+
+<!--
 ## ANTs longitudinal pipeline
 
-![](figures/longpipeex.png)
+![](longitudinal/figures/babystudy.png)
+-->

### 2014-10-16 README.R

@@ -10,8 +10,10 @@ srcdir<-"./"
 buildrmd='ants2015build.Rmd'
 rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 rawrmds<-c("ants2015.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
+rawrmds<-c("ants2015_GE.Rmd", "evaluation/antsvfreesurfer2.Rmd", "lesions/lesions.Rmd", "longitudinal/longitudinal.Rmd" )
+rawrmds<-c("ants2015_GE.Rmd", "competitions/competitions.Rmd", "evaluation/antsvfreesurfer2.Rmd", "lesions/lesions.Rmd", "longitudinal/longitudinal.Rmd" )
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)
 }
-render(buildrmd, clean=TRUE, "revealjs_presentation", output_file='index.html' ) 
+render(buildrmd, clean=TRUE, "revealjs_presentation", output_file='index.html' )

### 2014-10-17 ants2015_GE.Rmd
ENH:  Refinements.

@@
 ---
-title: <span style="color:red;">Neuroimaging with<br>ANTs</span>
+title: <span style="color:red;">ANTs</span><br> <small>_power tools for neuroimaging_</small>
 author:
@@
 
+## Built on ITK
+
+* image registration framework
+
+* many other classes such as:
+    + `itkScalarImageToRGBImageFilter`
+    + `itkLabelOverlapMeauresImageFilter`
+    + `itkBSplineScatteredDataPointSetToImageFilter`
+    + `itkStochasticFractalDimensionImageFilter`
+
 ## ANTs development philosophy:<br><small>Assimilate the optimal components of other approaches</small>
@@
 _"We are the Borg. Your biological and technological distinctiveness will be added to our own. Resistance is futile."_
+
+## *The Big 5*
+
+* <span style="color:red">image registration</span> (`antsRegistration.cxx`)
+
+* <span style="color:red">bias correction</span> (`N4BiasFieldCorrection.cxx`)
+
+* multivariate template construction (`antsMultivariateTemplateConstruction.sh`)
+
+* multivariate segmentation (`Atropos.cxx`)
+
+* cortical thickness (`KellyKaposki.cxx` and `antsCorticalThickness.sh`)
+
+## *ANTsR*<br>for statistics and visualization
+
+# *ANTs* optimizes mathematically well-defined <span style="color:red;">objective functions</span> guided by <span style="color:red;">prior knowledge</span>  ...
+
+# ... including that of developers, domain experts and other colleagues ...
+
+# plug *your ideas* into our software to gain insight into biomedical data ...
+
+# our strong <span style="color:red;">mathematical and software engineering</span> foundation leads to near limitless opportunities for innovation in a variety of application domains

### 2014-10-20 ants2015_GE.Rmd
ENH:  Adding circularity section.

@@
 ---
-title: <span style="color:red;">ANTs</span><br> <small>_power tools for neuroimaging_</small>
+title: <span style="color:red;">*ANTs*</span><br> <small>_power tools for neuroimaging_</small>
 author:

### 2014-10-20 ants2015build.Rmd
WIP: for cfn meeting
ENH:  Adding circularity section.

--- 2014-10-07 ants2015build.Rmd
@@
 ---
-title: <span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>
-author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)
+title: <span style="color:red;">*ANTs*</span><br> <small>_power tools for neuroimaging_</small>
+author:
 bibliography: REFERENCES.bib
@@
 
+# Background
+
 ##
 
-<div align="center"><img src="./figures/brian_and_edie_sedgwick.jpg" frameborder="0"></img></div>
+![](./figures/brian_and_nick.png)
 
-This talk is online at [http://stnava.github.io/ANTs2015/](http://stnava.github.io/ANTs2015/) with colored [links](http://stnava.github.io/ANTs2015/) meant to be clicked for more information.
+## Built on ITK
 
-# New work
+* image registration framework
 
-## RKRNS
+* many other classes such as:
+    + `itkScalarImageToRGBImageFilter`
+    + `itkLabelOverlapMeauresImageFilter`
+    + `itkBSplineScatteredDataPointSetToImageFilter`
+    + `itkStochasticFractalDimensionImageFilter`
 
-[link](stnava.github.io/RKRNS)
+## ANTs development philosophy:<br><small>Assimilate the optimal components of other approaches</small>
 
-What mathematical encoding of language reflects both brain activity and 
-"our" understanding of semantics?
+![](./figures/BorgFirstContact.jpg)
 
-## RIPMARC: Imputation, strutural networks, etc.
+_"We are the Borg. Your biological and technological distinctiveness will be added to our own. Resistance is futile."_
 
-![](figures/ripmmarc_inter.png)
+## *The Big 5*
 
-MICCAI 2014, Neuroimage 2015
+* <span style="color:red">image registration</span> (`antsRegistration.cxx`)
 
-## Big image registration
+* <span style="color:red">bias correction</span> (`N4BiasFieldCorrection.cxx`)
 
-# Longitudinal processing with ANTs
+* multivariate template construction (`antsMultivariateTemplateConstruction.sh`)
 
-## ANTs longitudinal pipeline
+* multivariate segmentation (`Atropos.cxx`)
 
-![](longitudinal/figures/longpipe.png)
+* cortical thickness (`KellyKaposki.cxx` and `antsCorticalThickness.sh`)
 
-see [link to paper](http://link.springer.com/chapter/10.1007/978-3-642-15705-9_40)
+## *ANTsR*<br>for statistics and visualization
 
-and [unbiased analysis paper](http://www.ncbi.nlm.nih.gov/pubmed/20005963)
+# *ANTs* optimizes mathematically well-defined <span style="color:red;">objective functions</span> guided by <span style="color:red;">prior knowledge</span>  ...
 
-plus [longitudinal recommendation paper](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3581852/)
+# ... including that of developers, domain experts and other colleagues ...
 
-## ANTs longitudinal pipeline
+# plug *your ideas* into our software to gain insight into biomedical data ...
 
-![](longitudinal/figures/longpipeex.png)
+# our strong <span style="color:red;">mathematical and software engineering</span> foundation leads to near limitless opportunities for innovation in a variety of application domains
 
-## ANTs longitudinal pipeline: TBI
+# *ANTs* and the perils of circularity
 
-![](longitudinal/figures/long_with_lesions_seg.png)
+##
 
-## ANTs longitudinal pipeline: TBI
+![](./philosophy/circularity/figures/escherANTs.png)
 
-![](longitudinal/figures/long_with_lesions_thick.png)
+##
 
-## ANTs longitudinal pipeline
+![](./philosophy/circularity/figures/brianEmail.png)
 
-![](longitudinal/figures/babystudy.png)
+##
 
-# Cortical thickness with lesions
+![](./philosophy/circularity/figures/sleeping0.png)
 
-## antsCorticalThickness.sh is adaptable!
+##
 
-1. Register subject (or single subject template) to normal template.
+![](./philosophy/circularity/figures/sleeping1.png)
 
-2. Transform lesion mask to normal template.
+##
 
-3. Create additional "lesion" prior, i.e. ```SmoothImage 3 ${lesionMask} 1 ${lesionPrior} 1```.
+![](./philosophy/circularity/figures/sleeping2.png)
 
-4.  Subtract out lesion prior from all other priors and keep values $\in [0,1]$.
+##
 
-## Modified template spatial priors
+![](./philosophy/circularity/figures/sleeping0.png)
 
-![](lesions/figures/lesionPrior.png)
+##
 
-## antsCorticalThickness.sh using lesion prior
+![](./philosophy/circularity/figures/sleeping4.png)
 
-![](lesions/figures/lesionSegmentation.png)
+##
 
-Only change to the command call is an additional '-c WM[7]' which means "combine
-the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."
+![](./philosophy/circularity/figures/sleeping5.png)
 
-# Registration & statistics:<br /> Frontiers and innovation
+##
 
-## multivariate statistical fields arise from fused modalities
+![](./philosophy/circularity/figures/sleeping6.png)
 
-![images at measurement fields](figures/statisticalfields.png)
+##
 
-*Many opportunities for statistical advancements*
-
-## ITK+ANTs+R = <span style="color:red;">*ANTsR*</span>
-
-## Agnostic statistics
-![](./figures/antsrex.jpg)
-
-[McMillan et al.](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3961542/)
-
-## A Quick <span style="color:grey;">*ANTsR*</span> example
-```{r loadantsr,results='hide',echo=FALSE,message=FALSE}
-library(ANTsR)
-```
-
-This is an executable *ANTsR* code block - *N*-dimensional statistics to go with 
-our *N*-dimensional image processing software!
-```{r loadimages,message=FALSE,warning=FALSE,results='hide'}
-library(ANTsR)
-dim<-2
-filename<-getANTsRData('r16')
-img<-antsImageRead( filename , dim )
-filename<-getANTsRData('r64')
-img2<-antsImageRead( filename , dim )
-mask<-getMask(img,50,max(img),T)
-mask2<-getMask(img,150,max(img),T)
-nvox<-sum( mask == 1 )
-nvox2<-sum( mask2 == 1 )
-```
-The brain has `r nvox` voxels ...
-
-## A Quick <span style="color:grey;">*ANTsR*</span> example
-
-Simulate a population morphometry study - a "VBM" ...
-```{r morph,results='hide'}
-simnum<-10
-imglist<-list()
-imglist2<-list()
-for ( i in 1:simnum ) {
-  img1sim<-antsImageClone(img)
-  img1sim[ mask==1 ]<-rnorm(nvox,mean=0.5)
-  img1sim[ mask2==1 ]<-rnorm(nvox2,mean=2.0)
-  img2sim<-antsImageClone(img2)
-  img2sim[ mask==1 ]<-rnorm(nvox,mean=0.20)
-  imglist<-lappend(imglist,img1sim)
-  imglist2<-lappend(imglist2,img2sim)
-}
-imglist<-lappend( imglist, imglist2 )
-mat<-imageListToMatrix( imglist, mask )
-DX<-factor( c( rep(0,simnum), rep(1,simnum) ) )
-mylmresults<-bigLMStats( lm( mat ~ DX ) )
-qvals<-p.adjust( mylmresults$pval.model ) 
-```
-The minimum q-value is `r min(qvals)` ...
-
-## Visualize the histograms of effects
-```{r vizmorph,results='hide'}
-whichvox<-qvals < 1.e-2
-voxdf<-data.frame( volume=c( as.numeric( mat[,whichvox] ) ), DX=DX )
-ggplot(voxdf, aes(volume, fill = DX)) + geom_density(alpha = 0.2)
-```
-
-## Visualize the anatomical distribution
-```{r vizmorph2hide,results='hide',echo=FALSE}
-betas<-antsImageClone(mask)
-betavec<-abs(mylmresults$beta.t[1,])
-betas[mask==1]<-betavec
-SmoothImage(dim,betas,1.5,betas)
-thresh<-paste(3.0,'x',max(betavec),sep='')
-ofn<-paste(figpath,'vizmorph2.jpg',sep='')
-```
-
-```{r vizmorph2,results='hide'}
-plotANTsImage(img,functional=list(betas),threshold=thresh,
-  outname=ofn)
-```
-
-![](`r ofn`)
-
-## Network visualization
-see `?plotBasicNetwork`
-```{r networkfn,results='hide',warning=FALSE,echo=FALSE,message=FALSE}
-ofn<-paste(figpath,'network',sep='')
-ofnpng<-paste(ofn,'.png',sep='')
-```
-```{r network,results='hide',warning=FALSE,echo=FALSE,message=FALSE,eval=F}
-       mnit<-getANTsRData("mni")
-       mnit<-antsImageRead(mnit,3)
-       mnia<-getANTsRData("mnia")
-       mnia<-antsImageRead(mnia,3)
-       ThresholdImage(3,mnit,mnit,1,max(mnit))
-       ImageMath(3,mnit,"FillHoles",mnit)
-       cnt<-getCentroids( mnia, clustparam = 50 )
-       aalcnt<-cnt$centroids[1:90,]
-       brain<-renderSurfaceFunction( surfimg =list( mnit ) , alphasurf=0.1 ,smoothsval = 1.5 )
-       testweights<-matrix( rep( 0, 90*90 ) ,nrow=90)
-       testweights[31,37]<-1  # ant cingulate to hipp
-       testweights[31,36]<-2  # ant cingulate to post cingulate
-       testweights[11,65]<-3  # broca to angular 
-       plotBasicNetwork( centroids = aalcnt , brain , weights=testweights )
-       id<-par3d("userMatrix")
-       rid<-rotate3d( id , -pi/2, 1, 0, 0 )
-       rid2<-rotate3d( id , pi/2, 0, 0, 1 )
-       rid3<-rotate3d( id , -pi/2, 0, 0, 1 )
-       par3d(userMatrix = id ) 
-       dd<-make3ViewPNG(  rid, id, rid2,  ofn )
-       par3d(userMatrix = id ) 
-```
-![](`r ofnpng`)
-
-## The power of *ANTs* $+$ *R* $\rightarrow$<br /> <span style="color:red;">**Reproducible imaging science**</span>
-
-![](./figures/antsgoals.png)
-
-...
-used in ["Sparse canonical correlation analysis relates network-level atrophy to multivariate cognitive measures in a neurodegenerative population"](http://www.ncbi.nlm.nih.gov/pubmed/24096125) and several upcoming ...
-
-# Wrap-up & Conclusions
-
-## Questions driving *ANTs* ($+$ Refs.1)
-
-* how should we geometrically transform anatomical coordinates?
-
-    - [syn paper](http://www.ncbi.nlm.nih.gov/pubmed/17659998) - our geometric transformation model of choice
-    - [recent B-spline alternative/improvement](http://www.ncbi.nlm.nih.gov/pubmed/24409140)
-
-* how should we measure pairwise image similarity?
-
-    - [similarity metric evaluation](http://www.ncbi.nlm.nih.gov/pubmed/20851191) compares functions for computing rigid or affine transformations between images
-
-* what if this pair has rgb/vector/tensor voxels?
-
-    - [dti similarity](http://www.ncbi.nlm.nih.gov/pubmed/18041273)
-
-* how do we extend from pairs to hundreds or thousands of pairs of images?
-
-    - [optimal templates](http://www.ncbi.nlm.nih.gov/pubmed/?term=avants+optimal+template) and [spatial priors](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
-    - species specific templates/priors in [chimps](http://www.ncbi.nlm.nih.gov/pubmed/23516289) and [canines](http://www.ncbi.nlm.nih.gov/pubmed/23284904)
-    - [ants "big data"](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+freesurfer)
-
-* how do we fuse multiple modality images at the subject and population levels?
-
-    - [ants auxiliary modality study](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+logical+circularity)
-
-## Questions driving *ANTs* ($+$ Refs.2)
-
-* can diffeomorphisms [improve cortical thickness measurement](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+freesurfer)?
-
-* how might we efficiently cluster the statistical fields that arise in image analysis?
-
-    - [Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation and [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison)
-    - [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants) for sparse imaging-specific PCA
-
-* how to cluster such fields when we have supervision?
-
-    - [sparse canonical correlation analysis for neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants)
-    - [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460)
-    - [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) - powerful expert systems for segmentation
-
-* how do we implement a fully multivariate *interpretable* brain and behavior study?
-
-    - [SCCAN for imaging & cognition](http://www.ncbi.nlm.nih.gov/pubmed/?term=sccan+avants)
-
-* how do we extend these ideas to functional MRI & decoding?
-
-    - [recent unpublished software](http://stnava.github.io/RKRNS/) 
-    - [recent work with Ben Kandel](..not yet...)
-
-## *ANTs* longitudinal analysis
-
-* Longitudinal image processing issues
-    - [registration induced bias](http://www.ncbi.nlm.nih.gov/pubmed/20005963)
-    - [general & TBI-specific issues in longitudinal analysis](http://www.ncbi.nlm.nih.gov/pubmed/23549059)
-    - [reproducibility of CBF](http://www.ncbi.nlm.nih.gov/pubmed/22517961)
-    - [structure-specific analysis](http://www.ncbi.nlm.nih.gov/pubmed/22306801)
-
-* An early study of longitudinal cortical change in ALS
-    - [ALS atrophy rates](http://www.ncbi.nlm.nih.gov/pubmed/16317254)
-
-* Extension of standard-setting ants cortical thickness pipeline to longitudinal data
-    - [DynANTs (unpublished)](https://github.com/stnava/DynANTs)
-
-## Challenges: Computational and Scientific
-
-- Scalability: **need to fuse feature selection methods with transformation optimization**
-- Scalability: **need to leverage existing ITK streaming infrastructure in application level tool**
-- Domain expertise: Customizable for specific problems but sometimes not specific enough
-- Rapid development: colleagues still need familiarity with compilation for latest ANTs features
-- Latest theoretical advances in registration not yet wrapped for users
-- Need more [Documentation](http://stnava.github.io/ANTs/)  & [testing](http://testing.psychiatry.uiowa.edu/CDash/index.php?project=ANTS) ...
-
-## Recap
-
-- Powerful, general-purpose, <span style="color:red;">well-evaluated</span> registration and segmentation.
-
-- Differentiable maps with differentiable inverse <span style="color:red;">$+$ statistics in these spaces</span>
-
-- Evaluated in multiple problem domains</span> via internal studies & open competition
-
-- Borg philosophy: <span style="color:red;">"best of"</span> from I/O, to processing to statistical methods
-
-- Open source, testing, many examples, consistent style, multiple platforms,  active community support ...
-
-- Integration with *R* $+$ novel tools for prediction, decoding, high-to-low dimensional statistics.
-
-- Collaborations with [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
-
-## Tools you can use for imaging science
-
-- Core developers:  *B. Avants, N. Tustison, H. J. Johnson, J. T. Duda*
-
-- Many contributors, including users ...
-
-- Multi-platform, multi-threaded C++ [stnava.github.io/ANTs](stnava.github.io/ANTs)
-
-- Developed in conjunction with [http://www.itk.org/](http://www.itk.org/)
-
-- R wrapping and extension [stnava.github.io/ANTsR](stnava.github.io/ANTsR)
-
-- rapid development, regular testing $+$ many eyes $\rightarrow$ bugs are shallow
-
-<img style="float: right" src="figures/penn.png" />
-<img style="float: left" src="figures/picsl.jpg" />
-
-# References
+![](./philosophy/circularity/figures/sleeping7.png)

### 2014-10-20 evaluation/antsvfreesurfer.Rmd
ENH:  Adding circularity section.

@@
-# ANTs versus Freesurfer:<br />  Quantifying *life span* brain health
+# *ANTs* versus Freesurfer:<br />  Quantifying *life span* brain health
 
@@
 
-## ANTs versus Freesurfer:<br />  Quantifying *life span* brain health
+## *ANTs* versus Freesurfer:<br />  Quantifying *life span* brain health
 
@@
 
-* *hint*: ANTs thickness measurements have higher prediction accuracy relative to Freesurfer ( implying we extract more information from the data )
+* *hint*: *ANTs* thickness measurements have higher prediction accuracy relative to Freesurfer ( implying we extract more information from the data )
 
-* ANTs methods consistently improve statistical power [eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/24687814), [syn](http://www.ncbi.nlm.nih.gov/pubmed/?term=syn+epstein+avants), [itkv4](http://www.ncbi.nlm.nih.gov/pubmed/24817849) ...
+* *ANTs* methods consistently improve statistical power [eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/24687814), [syn](http://www.ncbi.nlm.nih.gov/pubmed/?term=syn+epstein+avants), [itkv4](http://www.ncbi.nlm.nih.gov/pubmed/24817849) ...
 also, see [Schwarz CG, et al.](http://www.ncbi.nlm.nih.gov/pubmed/24650605) re: TBSS and related work in fMRI [Miller, PNAS](http://www.ncbi.nlm.nih.gov/pubmed/15980148), [Azab, et al in Hippocampus](http://www.ncbi.nlm.nih.gov/pubmed/24167043).

### 2014-10-20 evaluation/antsvfreesurfer2.Rmd
ENH:  Refinements.
ENH:  Adding circularity section.

@@
 
-## ANTs-related background
+## *ANTs*-related background
 
@@
 
-## The ANTs structural brain mapping workflow
+## The *ANTs* structural brain mapping workflow
 
@@
 
-## Brain extraction comparison<br>ANTs vs. FreeSurfer
+## Brain extraction comparison<br>*ANTs* vs. FreeSurfer
 
@@
 
-In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, ANTs diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
+In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
 
@@
 
-ANTs (left) vs. FreeSurfer (right)
+*ANTs* (left) vs. FreeSurfer (right)
 
@@
 
-## All software components are open source and part of the ANTs repository.
-
 # Cortical thickness extensions

### 2014-10-20 README.R

@@ -11,7 +11,7 @@ buildrmd='ants2015build.Rmd'
 rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 rawrmds<-c("ants2015.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 rawrmds<-c("ants2015_GE.Rmd", "evaluation/antsvfreesurfer2.Rmd", "lesions/lesions.Rmd", "longitudinal/longitudinal.Rmd" )
-rawrmds<-c("ants2015_GE.Rmd", "competitions/competitions.Rmd", "evaluation/antsvfreesurfer2.Rmd", "lesions/lesions.Rmd", "longitudinal/longitudinal.Rmd" )
+rawrmds<-c("ants2015_GE.Rmd", "philosophy/circularity/circularity.Rmd")
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)

### 2014-10-23 ants2015build.Rmd
ENH:  Add Bookstein review.
ENH:  More Bookstein.
ENH:  Adding more circularity material.

@@
 
-##
+## *ANTs* and the perils of circularity
 
@@
 
-![](./philosophy/circularity/figures/brianEmail.png)
+![](./philosophy/circularity/figures/voodoo.png)
 
@@
 
-![](./philosophy/circularity/figures/sleeping0.png)
+![](./philosophy/circularity/figures/fastForward.png)
+
+##
+
+![](./philosophy/circularity/figures/tbss.png)
+
+##
+
+![](./philosophy/circularity/figures/antsFlavoredTbss1.png)
+
+##
+
+![](./philosophy/circularity/figures/antsFlavoredTbss2.png)
+
+##
+
+![](./philosophy/circularity/figures/antsFlavoredTbss3.png)
+
+##
+
+![](./philosophy/circularity/figures/antsFlavoredTbss4.png)
+
+##
+
+![](./philosophy/circularity/figures/antsFlavoredTbss5.png)
+
+##
+
+![](./philosophy/circularity/figures/brianEmail.png)
 
@@
 ![](./philosophy/circularity/figures/sleeping7.png)
+
+##
+
+![](./philosophy/circularity/figures/benefitsOfOpenScience.png)
+
+## Command line help
+
+<font size="5", color="lightgrey">
+```
+$ CreateDTICohort -h
+
+COMMAND:
+     CreateDTICohort
+
+OPTIONS:
+     -d, --image-dimensionality 2/3
+     -a, --dti-atlas inputDTIAtlasFileName
+     -x, --label-mask-image maskImageFileName
+                            lowerThresholdFunction
+     -n, --noise-sigma <noiseSigma=18>
+     -p, --pathology label[<percentageChangeEig1=-0.05>,<percentageChangeAvgEig2andEig3=0.05>,<numberOfVoxels=all or percentageOfvoxels>]
+     -w, --dwi-parameters [B0Image,directionFile,bvalue]
+                          [B0Image,schemeFile]
+     -r, --registered-population textFileWithFileNames.txt
+     -o, --output [outputDirectory,fileNameSeriesRootName,<numberOfControls=10>,<numberOfExperimentals=10>]
+     -h
+     --help
+```
+</font>
+
+## Which one is not warped?
+
+![](./philosophy/circularity/figures/whichOneIsRegistered.png)
+
+## _Answer_
+
+![](./philosophy/circularity/figures/whichOneIsRegistered2.png)
+
+##
+
+![](./philosophy/circularity/figures/blobs1.png)
+
+##
+
+![](./philosophy/circularity/figures/blobs2.png)
+
+##
+
+![](./philosophy/circularity/figures/BooksteinReview1.png)
+![](./philosophy/circularity/figures/BooksteinReview2.png)
+![](./philosophy/circularity/figures/BooksteinReview3.png)

### 2014-10-23 ants2015_GE.Rmd
ENH:  More edits to the talk.

@@
 
+<!--
+
 ## Built on ITK
@@
 # our strong <span style="color:red;">mathematical and software engineering</span> foundation leads to near limitless opportunities for innovation in a variety of application domains
+-->

### 2014-10-23 ants2015build.Rmd
ENH:  More edits to the talk.

@@
 # our strong <span style="color:red;">mathematical and software engineering</span> foundation leads to near limitless opportunities for innovation in a variety of application domains
+-->
+
+# ANTs brain morphology<br><br>[<small>"*Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
+
+## Cortical thickness studies:
+```{r, results='asis', echo = FALSE}
+conditions <- c( "Huntington’s disease", "schizophrenia", "bipolar disorder",
+                 "Alzheimer’s disease", "frontotemporal dementia", "Parkinson’s disease",
+                 "Williams syndrome", "multiple sclerosis", "autism", "migraines",
+                 "chronic smoking", "alcoholism", "cocaine addiction", "Tourette syndrome in children",
+                 "scoliosis in female adolescents", "early-onset blindness", "chronic pancreatitis",
+                 "obsessive-compulsive disorder", "ADHD", "obesity", "heritable depression",
+                 "elderly depression", "age", "gender", "untreated male-to-female transsexuality",
+                 "handedness", "intelligence", "athletic ability", "meditative practices", "musical ability",
+                 "tendency toward criminality", "childhood sexual abuse in female adolescents",
+                 "Tetris-playing ability in female adolescents", "traumatic brain injury" )
+
+conditionsDF <- data.frame( Column1 = conditions[1:floor( 0.5*length(conditions) )], Column2 = conditions[( 1+floor( 0.5*length(conditions) ) ):length(conditions)] )
+knitr::kable( conditionsDF )
+```
+
+## *ANTs*-related background
+
+* Sandy, Brian, and <span style="color:red;">DiReCT</span>
+  + used other tools such as FMRIB's Automated Segmentation Tool (FAST)
+  + `KellySlater.cxx`
+  * scripts "adequate for Penn data"
+* `KellyKapowski.cxx` and `antsCorticalThickness.sh`
+* _"Let's evaluate on open data."_
+* and, eventually, _"Let's compare with FreeSurfer."_
+
+## The *ANTs* structural brain mapping workflow
+
+![](./evaluation/figures/pipeline.png)
+
+## Basic components of the pipeline
+
+<div align="center"><img height="350" src="./evaluation/figures/components.png" frameborder="0"></img></div>
+
+1. template building (offline)
+2. brain extraction
+3. cortical thickness estimation
+4. cortical parcellation
+
+## Template building
+
+*Tailor data to your specific cohort*
+
+<div align="center"><img height="350" src="./evaluation/figures/templates.png" frameborder="0"></img></div>
+
+* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
+* Acquisition and anonymization (e.g. defacing) protocols are often different.
+
+## Template building (cont.)
+
+<div align="center"><img height="350" src="./evaluation/figures/templatePriors.png" frameborder="0"></img></div>
+
+Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
+to produce auxiliary images which are used for brain extraction and brain segmentation.
+
+## Brain extraction comparison<br>*ANTs* vs. FreeSurfer
+
+<div align="center"><img height="380" src="./evaluation/figures/brainExtraction.png" frameborder="0"></img></div>
+
+Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
+the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
+
+## Brain segmentation
+
+<div align="center"><img height="350" src="./evaluation/figures/brainSegmentation.png" frameborder="0"></img></div>
+
+Randomly selected healthy individuals.  Atropos gets good performance across ages.
+
+## Cortical thickness estimation
+
+<div align="center"><img height="250" src="./evaluation/figures/corticalThicknessEstimation.png" frameborder="0"></img></div>
+
+In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
+
+## _But without ground truth, how does one evaluate the pipeline?_
+
+* Use age and gender (demographic information) in training/prediction paradigm
+* Public data sets (IXI, NKI, Oasis, MMRR)
+* $>$ 1200 subjects, age 7 to over 90 years old
+
+## Prediction from cortical thickness data:<br>gender and age
+
+<div align="center"><img height="350" src="./evaluation/figures/evaluation.png" frameborder="0"></img></div>
+
+## Regional importance comparison
+
+$AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$
+
+<div align="center"><img height="500" src="./evaluation/figures/antsvfreesurfer_importance.png" frameborder="0"></img></div>
+
+*ANTs* (left) vs. FreeSurfer (right)
+
+## Regional importance comparison (cont.)
+
+<div align="center"><img height="550" src="./evaluation/figures/antsvfreesurfer_regionalPlots.png" frameborder="0"></img></div>
+
+## Cortical thickness extensions
 

### 2014-10-23 README.R

@@ -11,7 +11,7 @@ buildrmd='ants2015build.Rmd'
 rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 rawrmds<-c("ants2015.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 rawrmds<-c("ants2015_GE.Rmd", "evaluation/antsvfreesurfer2.Rmd", "lesions/lesions.Rmd", "longitudinal/longitudinal.Rmd" )
-rawrmds<-c("ants2015_GE.Rmd", "philosophy/circularity/circularity.Rmd")
+rawrmds<-c("ants2015_GE.Rmd", "evaluation/antsvfreesurfer2.Rmd", "philosophy/circularity/circularity.Rmd")
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)

### 2014-10-30 ants2015build.Rmd
ENH:  Adding to title slide.
BUG:  Wrong filename.

@@
 
-## Regional importance comparison
+## Regional importance <br>comparison
 
@@
 
-<div align="center"><img height="500" src="./evaluation/figures/antsvfreesurfer_importance.png" frameborder="0"></img></div>
+<div align="center"><img height="500" src="./evaluation/figures/antsvfreesurfer_Importance.png" frameborder="0"></img></div>
 
@@
 
-# *ANTs* and the perils of circularity
+# *ANTs* and the perils of circularity<br><br>[<small>"*Logical circularity in voxel-based analysis: normalization strategy may induce statistical bias*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/23151955)
 

### 2014-10-30 ants2015_GE.Rmd
ENH:  Final changes.

@@
 
-##
+## Founding developers
 
-![](./figures/brian_and_nick.png)
+<div align="center"><img width="1800" src="./figures/brian_and_nick.png" frameborder="0"></img></div>
+
+## Long term collaborators
+
+![](./figures/antscollab.jpg)
+
+## _ANTs_:  General purpose library for multivariate image registration, segmentation & statistical analysis tools
+
+* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.
+
+* Generic mathematical methods that are tunable for
+application specific domains:  no-free lunch
+
+* Deep testing on multiple platforms ... osx, linux, windows.
+
+* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )
+
+```
+    An algorithm must use prior knowledge about a problem
+    to do well on that problem
+```
 

### 2014-10-30 ants2015build.Rmd
ENH:  Final changes.

@@
 -->
-
-# ANTs brain morphology<br><br>[<small>"*Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
-
-## Cortical thickness studies:
-```{r, results='asis', echo = FALSE}
-conditions <- c( "Huntington’s disease", "schizophrenia", "bipolar disorder",
-                 "Alzheimer’s disease", "frontotemporal dementia", "Parkinson’s disease",
-                 "Williams syndrome", "multiple sclerosis", "autism", "migraines",
-                 "chronic smoking", "alcoholism", "cocaine addiction", "Tourette syndrome in children",
-                 "scoliosis in female adolescents", "early-onset blindness", "chronic pancreatitis",
-                 "obsessive-compulsive disorder", "ADHD", "obesity", "heritable depression",
-                 "elderly depression", "age", "gender", "untreated male-to-female transsexuality",
-                 "handedness", "intelligence", "athletic ability", "meditative practices", "musical ability",
-                 "tendency toward criminality", "childhood sexual abuse in female adolescents",
-                 "Tetris-playing ability in female adolescents", "traumatic brain injury" )
-
-conditionsDF <- data.frame( Column1 = conditions[1:floor( 0.5*length(conditions) )], Column2 = conditions[( 1+floor( 0.5*length(conditions) ) ):length(conditions)] )
-knitr::kable( conditionsDF )
-```
-
-## *ANTs*-related background
-
-* Sandy, Brian, and <span style="color:red;">DiReCT</span>
-  + used other tools such as FMRIB's Automated Segmentation Tool (FAST)
-  + `KellySlater.cxx`
-  * scripts "adequate for Penn data"
-* `KellyKapowski.cxx` and `antsCorticalThickness.sh`
-* _"Let's evaluate on open data."_
-* and, eventually, _"Let's compare with FreeSurfer."_
-
-## The *ANTs* structural brain mapping workflow
-
-![](./evaluation/figures/pipeline.png)
-
-## Basic components of the pipeline
-
-<div align="center"><img height="350" src="./evaluation/figures/components.png" frameborder="0"></img></div>
-
-1. template building (offline)
-2. brain extraction
-3. cortical thickness estimation
-4. cortical parcellation
-
-## Template building
-
-*Tailor data to your specific cohort*
-
-<div align="center"><img height="350" src="./evaluation/figures/templates.png" frameborder="0"></img></div>
-
-* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
-* Acquisition and anonymization (e.g. defacing) protocols are often different.
-
-## Template building (cont.)
-
-<div align="center"><img height="350" src="./evaluation/figures/templatePriors.png" frameborder="0"></img></div>
-
-Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
-to produce auxiliary images which are used for brain extraction and brain segmentation.
-
-## Brain extraction comparison<br>*ANTs* vs. FreeSurfer
-
-<div align="center"><img height="380" src="./evaluation/figures/brainExtraction.png" frameborder="0"></img></div>
-
-Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
-the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
-
-## Brain segmentation
-
-<div align="center"><img height="350" src="./evaluation/figures/brainSegmentation.png" frameborder="0"></img></div>
-
-Randomly selected healthy individuals.  Atropos gets good performance across ages.
-
-## Cortical thickness estimation
-
-<div align="center"><img height="250" src="./evaluation/figures/corticalThicknessEstimation.png" frameborder="0"></img></div>
-
-In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
-
-## _But without ground truth, how does one evaluate the pipeline?_
-
-* Use age and gender (demographic information) in training/prediction paradigm
-* Public data sets (IXI, NKI, Oasis, MMRR)
-* $>$ 1200 subjects, age 7 to over 90 years old
-
-## Prediction from cortical thickness data:<br>gender and age
-
-<div align="center"><img height="350" src="./evaluation/figures/evaluation.png" frameborder="0"></img></div>
-
-## Regional importance <br>comparison
-
-$AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$
-
-<div align="center"><img height="500" src="./evaluation/figures/antsvfreesurfer_Importance.png" frameborder="0"></img></div>
-
-*ANTs* (left) vs. FreeSurfer (right)
-
-## Regional importance comparison (cont.)
-
-<div align="center"><img height="550" src="./evaluation/figures/antsvfreesurfer_regionalPlots.png" frameborder="0"></img></div>
-
-## Cortical thickness extensions
 
@@
 ![](./philosophy/circularity/figures/BooksteinReview3.png)
+
+# ANTs brain morphology<br><br>[<small>"*Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
+
+## Cortical thickness studies:
+```{r, results='asis', echo = FALSE}
+conditions <- c( "Huntington’s disease", "schizophrenia", "bipolar disorder",
+                 "Alzheimer’s disease", "frontotemporal dementia", "Parkinson’s disease",
+                 "Williams syndrome", "multiple sclerosis", "autism", "migraines",
+                 "chronic smoking", "alcoholism", "cocaine addiction", "Tourette syndrome in children",
+                 "scoliosis in female adolescents", "early-onset blindness", "chronic pancreatitis",
+                 "obsessive-compulsive disorder", "ADHD", "obesity", "heritable depression",
+                 "elderly depression", "age", "gender", "untreated male-to-female transsexuality",
+                 "handedness", "intelligence", "athletic ability", "meditative practices", "musical ability",
+                 "tendency toward criminality", "childhood sexual abuse in female adolescents",
+                 "Tetris-playing ability in female adolescents", "traumatic brain injury" )
+
+conditionsDF <- data.frame( Column1 = conditions[1:floor( 0.5*length(conditions) )], Column2 = conditions[( 1+floor( 0.5*length(conditions) ) ):length(conditions)] )
+knitr::kable( conditionsDF )
+```
+
+## *ANTs*-related background
+
+* Sandy, Brian, and <span style="color:red;">DiReCT</span>
+  + used other tools such as FMRIB's Automated Segmentation Tool (FAST)
+  + `KellySlater.cxx`
+  * scripts "adequate for Penn data"
+* `KellyKapowski.cxx` and `antsCorticalThickness.sh`
+* _"Let's evaluate on open data."_
+* and, eventually, _"Let's compare with FreeSurfer."_
+
+## The *ANTs* structural brain mapping workflow
+
+![](./evaluation/figures/pipeline.png)
+
+## Basic components of the pipeline
+
+<div align="center"><img height="350" src="./evaluation/figures/components.png" frameborder="0"></img></div>
+
+1. template building (offline)
+2. brain extraction
+3. cortical thickness estimation
+4. cortical parcellation
+
+## Template building
+
+*Tailor data to your specific cohort*
+
+<div align="center"><img height="350" src="./evaluation/figures/templates.png" frameborder="0"></img></div>
+
+* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
+* Acquisition and anonymization (e.g. defacing) protocols are often different.
+
+## Template building (cont.)
+
+<div align="center"><img height="350" src="./evaluation/figures/templatePriors.png" frameborder="0"></img></div>
+
+Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
+to produce auxiliary images which are used for brain extraction and brain segmentation.
+
+## Brain extraction comparison<br>*ANTs* vs. FreeSurfer
+
+<div align="center"><img height="380" src="./evaluation/figures/brainExtraction.png" frameborder="0"></img></div>
+
+Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
+the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
+
+## Brain segmentation
+
+<div align="center"><img height="350" src="./evaluation/figures/brainSegmentation.png" frameborder="0"></img></div>
+
+Randomly selected healthy individuals.  Atropos gets good performance across ages.
+
+## Cortical thickness estimation
+
+<div align="center"><img height="250" src="./evaluation/figures/corticalThicknessEstimation.png" frameborder="0"></img></div>
+
+In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
+
+## _But without ground truth, how does one evaluate the pipeline?_
+
+* Use age and gender (demographic information) in training/prediction paradigm
+* Public data sets (IXI, NKI, Oasis, MMRR)
+* $>$ 1200 subjects, age 7 to over 90 years old
+
+## Prediction from cortical thickness data:<br>gender and age
+
+<div align="center"><img height="350" src="./evaluation/figures/evaluation.png" frameborder="0"></img></div>
+
+## Regional importance <br>comparison
+
+$AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$
+
+<div align="center"><img height="500" src="./evaluation/figures/antsvfreesurfer_Importance.png" frameborder="0"></img></div>
+
+*ANTs* (left) vs. FreeSurfer (right)
+
+## Regional importance comparison (cont.)
+
+<div align="center"><img height="550" src="./evaluation/figures/antsvfreesurfer_regionalPlots.png" frameborder="0"></img></div>
+
+## Cortical thickness extensions

### 2014-10-30 README.R

@@ -11,7 +11,7 @@ buildrmd='ants2015build.Rmd'
 rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 rawrmds<-c("ants2015.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 rawrmds<-c("ants2015_GE.Rmd", "evaluation/antsvfreesurfer2.Rmd", "lesions/lesions.Rmd", "longitudinal/longitudinal.Rmd" )
-rawrmds<-c("ants2015_GE.Rmd", "evaluation/antsvfreesurfer2.Rmd", "philosophy/circularity/circularity.Rmd")
+rawrmds<-c( "ants2015_GE.Rmd", "philosophy/circularity/circularity.Rmd", "evaluation/antsvfreesurfer2.Rmd" )
 for ( x in 1:length(rawrmds) ) {
   if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd<-paste( "cat ",rawrmds[x]," >> ",buildrmd )
   system(cmd)

### 2014-11-11 ants2015build.Rmd
ENH: new reveal style

@@
 ---
-title: <span style="color:red;">*ANTs*</span><br> <small>_power tools for neuroimaging_</small>
-author:
+title: <span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>
+author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)
 bibliography: REFERENCES.bib
@@
 
+##
+
+<div align="center"><img src="./figures/brian_and_edie_sedgwick.jpg" frameborder="0"></img></div>
+
+This talk is online at [http://stnava.github.io/ANTs2015/](http://stnava.github.io/ANTs2015/) with colored [links](http://stnava.github.io/ANTs2015/) meant to be clicked for more information.
+
 # Background
@@
 
-<div align="center"><img width="1800" src="./figures/brian_and_nick.png" frameborder="0"></img></div>
+<div align="center"><img width="1800" src="./figures/bant2.png" frameborder="0"></img></div>
 
-## Long term collaborators
+BBA & NT
+
+## Long-term collaborators
 
@@
 
-## _ANTs_:  General purpose library for multivariate image registration, segmentation & statistical analysis tools
+$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
+
+##
+
+![](./figures/lion.png)
+
+a pride: common way of doing things
+
+... in a competitive world ...
+
+## Definitions
+
+* Registration $=$ estimate an "optimal" geometric mapping between image pairs or image sets (e.g. Affine)
+
+* <span style="color:grey;"> Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)</span>
+
+* Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)
+
+* <span style="color:grey;">Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)</span>
+
+* Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>
+
+* <span style="color:grey;">Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)</span>
+
+* MALF: multi-atlas label fusion - using anatomical dictionaries to label new data
+
+* <span style="color:grey;">Solutions to challenging statistical image processing problems usually need elements from each of the above</span>
+
+## Image mapping & perception: 1878
+
+![](./figures/galton.png)
+
+* Francis Galton: Can we see criminality in the face?
+
+* (maybe he should have used *ANTs*?)
+
+## Image mapping & biology: 1917
+
+![](./figures/dthompson.png)
+
+D'Arcy Thompson
+
+## Initial scope
+
+![](./figures/ants_initial_scope.png)
+
+... just do a better registration (tell story) ...
+
+## *ANTs* Lineage
+
+![](./figures/lineage.jpg)
+
+References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
+
+## Diffeomorphisms
+
+<div align="center"><img width="1433" src="./figures/sillyputty.png" frameborder="0"></img></div>
+
+plausible physical modeling of large, invertible deformations
+
+"differentiable map with differentiable inverse"
+
+## Fine-grained and flexible maps
+![](./figures/highresdiffeos.jpg)
+
+... to correct a misconception about diffeomorphisms ...
+
+## Diffeomorphisms: image parameterization in a metric space
+
+![](./figures/shape_appearance.png)
+
+## General purpose library for multivariate image registration, segmentation & statistical analysis tools
 
@@
 
-<!--
+## *ANTs*: Beyond Registration
 
-## Built on ITK
+![](./figures/antscapabilities.jpg)
 
-* image registration framework
+[Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)
 
-* many other classes such as:
-    + `itkScalarImageToRGBImageFilter`
-    + `itkLabelOverlapMeauresImageFilter`
-    + `itkBSplineScatteredDataPointSetToImageFilter`
-    + `itkStochasticFractalDimensionImageFilter`
+## On documentation
 
-## ANTs development philosophy:<br><small>Assimilate the optimal components of other approaches</small>
+![](figures/Chainsaw.jpg)
 
-![](./figures/BorgFirstContact.jpg)
+documentation is important
 
-_"We are the Borg. Your biological and technological distinctiveness will be added to our own. Resistance is futile."_
+## On documentation
 
-## *The Big 5*
+![](figures/blindmen.jpg)
 
-* <span style="color:red">image registration</span> (`antsRegistration.cxx`)
+... developers can be blind to doc deficiencies
 
-* <span style="color:red">bias correction</span> (`N4BiasFieldCorrection.cxx`)
+while users are blind to what we provide!
+# ANTs Impact
 
-* multivariate template construction (`antsMultivariateTemplateConstruction.sh`)
+## ANTs Statistics
 
-* multivariate segmentation (`Atropos.cxx`)
+![](impact/figures/antsvisitors.png)
 
-* cortical thickness (`KellyKaposki.cxx` and `antsCorticalThickness.sh`)
+## ANTs & Neuroscience
 
-## *ANTsR*<br>for statistics and visualization
+We need statistical image analysis <br />at several scales in modern neuroscience
 
-# *ANTs* optimizes mathematically well-defined <span style="color:red;">objective functions</span> guided by <span style="color:red;">prior knowledge</span>  ...
+* Macro: *in vivo* structural and functional MRI
 
-# ... including that of developers, domain experts and other colleagues ...
+* Micro:  high-resolution post-mortem MRI links with in vivo MRI
 
-# plug *your ideas* into our software to gain insight into biomedical data ...
+* Nano: neuron reconstruction ...
 
-# our strong <span style="color:red;">mathematical and software engineering</span> foundation leads to near limitless opportunities for innovation in a variety of application domains
--->
+* Solutions that are consistent across these scales have the potential
+to build multi-scale feature sets or templates and provide new
+insights into brain structure and function
 
-# *ANTs* and the perils of circularity<br><br>[<small>"*Logical circularity in voxel-based analysis: normalization strategy may induce statistical bias*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/23151955)
+* E.g. Parcellation constraints based on histology, tractography, function ...
 
-## *ANTs* and the perils of circularity
+* Statistical definitions of anatomy/pathology?
 
-![](./philosophy/circularity/figures/escherANTs.png)
+* Reinvention of these solutions within each lab ... can we mitigate this?
+
+* Reduce, reuse, recycle ...
+
+## Financial impact
+
+* The **high error rate** in software makes testing for quality assurance critically important.
+
+* Bugs exist **Everywhere**: so don't freak out if we admit we have bugs:  we're just being honest ( and not all devs are )
+
+* Virtually every business in the United States now depends on software for development, production, distribution, and after-sales support of products and services.
+
+* A 2002 NIST study estimated the direct costs to the software supply chain due to failure to identify (**successfully test for**) "bugs"
+
+* We are better at this than most ... **not perfect**
+
+* The estimate of direct costs compiled from industry survey data for the U.S. economy was **\$60 billion per year**
+
+* ... this estimate did not include costs to end users such as lost business (for example, the cost of shutting down the New York Mercantile Exchange in 1998 due to a software failure).
+
+## Reproducibility
+
+* Consider the recent paper: [Freesurfer, laplacian, DiReCT thickness in longitudinal stroke](http://ac.els-cdn.com/S2213158214001260/1-s2.0-S2213158214001260-main.pdf?_tid=8e6f5248-335d-11e4-ba4f-00000aab0f02&acdnat=1409743944_6615d59eb5709e6bcb1aca76450f7d93)
+
+* We "pre-wrote" a comment: [Instrumentation bias in the use and evaluation of scientific software](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3766821/?report=reader)
+
+* With these guys:
+
+* <img src="figures/luis.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right: 3px;"><img src="figures/torsten.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;">
+
+## Hired by Google
+
+<img src="figures/luis.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right: 3px;"><img src="figures/torsten.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;"><img src="figures/gang.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;">
+
+# Optimal Templates
+
+## "Optimal" templates (?)
+
+* unbiased wrt measurement space
+
+* space is non-linear: reference matters
+
+* encodes prior information: still just averages (usually)
+
+* concept extends across modalities, anatomy, temporality, etc
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.060.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.061.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.062.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.063.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.064.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.065.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.066.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.067.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.068.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.069.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.070.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.071.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.072.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.073.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.074.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.075.jpg)
+
+## Faces, brains, whatever ...
+
+![](templates/figures/WashUJan2011.076.jpg)
+
+see [ANTs site](stnava.github.io/ANTs) and [ANTs Documentation page](stnava.github.io/ANTsDoc)
+
+## Templates from ANTs Colleagues ( not us )
+
+![](templates/figures/templates_ants_colleagues.png)
+
+## Templates unlock modalities
+
+![](figures/ptbp2.png)
+
+# Evaluation
 
@@
 
-![](./philosophy/circularity/figures/voodoo.png)
-
-##
-
-![](./philosophy/circularity/figures/fastForward.png)
-
-##
-
-![](./philosophy/circularity/figures/tbss.png)
-
-##
-
-![](./philosophy/circularity/figures/antsFlavoredTbss1.png)
-
-##
-
-![](./philosophy/circularity/figures/antsFlavoredTbss2.png)
-
-##
-
-![](./philosophy/circularity/figures/antsFlavoredTbss3.png)
-
-##
-
-![](./philosophy/circularity/figures/antsFlavoredTbss4.png)
-
-##
-
-![](./philosophy/circularity/figures/antsFlavoredTbss5.png)
-
-##
-
-![](./philosophy/circularity/figures/brianEmail.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping1.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping2.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping0.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping4.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping5.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping6.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping7.png)
-
-##
-
-![](./philosophy/circularity/figures/benefitsOfOpenScience.png)
-
-## Command line help
-
-<font size="5", color="lightgrey">
-```
-$ CreateDTICohort -h
-
-COMMAND:
-     CreateDTICohort
-
-OPTIONS:
-     -d, --image-dimensionality 2/3
-     -a, --dti-atlas inputDTIAtlasFileName
-     -x, --label-mask-image maskImageFileName
-                            lowerThresholdFunction
-     -n, --noise-sigma <noiseSigma=18>
-     -p, --pathology label[<percentageChangeEig1=-0.05>,<percentageChangeAvgEig2andEig3=0.05>,<numberOfVoxels=all or percentageOfvoxels>]
-     -w, --dwi-parameters [B0Image,directionFile,bvalue]
-                          [B0Image,schemeFile]
-     -r, --registered-population textFileWithFileNames.txt
-     -o, --output [outputDirectory,fileNameSeriesRootName,<numberOfControls=10>,<numberOfExperimentals=10>]
-     -h
-     --help
-```
-</font>
-
-## Which one is not warped?
-
-![](./philosophy/circularity/figures/whichOneIsRegistered.png)
-
-## _Answer_
-
-![](./philosophy/circularity/figures/whichOneIsRegistered2.png)
-
-##
-
-![](./philosophy/circularity/figures/blobs1.png)
-
-##
-
-![](./philosophy/circularity/figures/blobs2.png)
-
-##
-
-![](./philosophy/circularity/figures/BooksteinReview1.png)
-![](./philosophy/circularity/figures/BooksteinReview2.png)
-![](./philosophy/circularity/figures/BooksteinReview3.png)
+<div align="center"><img width="3500" src="evaluation/figures/evalhistory.png" frameborder="0"></img></div>
 
@@
 ## Cortical thickness extensions
+
+<!--
+# New work
+
+## RKRNS
+
+[link](http://stnava.github.io/RKRNS/)
+
+What mathematical encoding of language reflects both brain activity and
+"our" understanding of semantics?
+
+## RIPMARC: Imputation, strutural networks, etc.
+
+![](figures/ripmmarc_inter.png)
+
+MICCAI 2014, Neuroimage 2015
+
+## Big image registration
+-->
+
+# Longitudinal processing <!--with ANTs>
+
+<!--
+## ANTs longitudinal pipeline
+
+![](longitudinal/figures/longpipe.png)
+
+see [link to paper](http://link.springer.com/chapter/10.1007/978-3-642-15705-9_40)
+
+and [unbiased analysis paper](http://www.ncbi.nlm.nih.gov/pubmed/20005963)
+
+plus [longitudinal recommendation paper](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3581852/)
+-->
+
+## `antsLongitudinalCorticalThickness.sh`
+
+![](longitudinal/figures/longpipeex.png)
+
+## Longitudinal TBI with lesions (segmentation)
+
+![](longitudinal/figures/long_with_lesions_seg.png)
+
+## Longitudinal TBI with lesions (cortical thickness)
+
+![](longitudinal/figures/long_with_lesions_thick.png)
+
+<!--
+## ANTs longitudinal pipeline
+
+![](longitudinal/figures/babystudy.png)
+-->
+
+# Cortical thickness with lesions
+
+## antsCorticalThickness.sh is adaptable!
+
+1. Register subject (or single subject template) to normal template.
+
+2. Transform lesion mask to normal template.
+
+3. Create additional "lesion" prior, i.e. ```SmoothImage 3 ${lesionMask} 1 ${lesionPrior} 1```.
+
+4.  Subtract out lesion prior from all other priors and keep values $\in [0,1]$.
+
+## Modified template spatial priors
+
+![](lesions/figures/lesionPrior.png)
+
+## antsCorticalThickness.sh using lesion prior
+
+![](lesions/figures/lesionSegmentation.png)
+
+Only change to the command call is an additional '-c WM[7]' which means "combine
+the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."
+
+# Registration & statistics:<br /> Frontiers and innovation
+
+## multivariate statistical fields arise from fused modalities
+
+![images at measurement fields](figures/statisticalfields.png)
+
+*Many opportunities for statistical advancements*
+
+## ITK+ANTs+R = <span style="color:red;">*ANTsR*</span>
+
+## Agnostic statistics
+![](./figures/antsrex.jpg)
+
+[McMillan et al.](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3961542/)
+
+## A Quick <span style="color:grey;">*ANTsR*</span> example
+```{r loadantsr,results='hide',echo=FALSE,message=FALSE}
+library(ANTsR)
+```
+
+This is an executable *ANTsR* code block - *N*-dimensional statistics to go with 
+our *N*-dimensional image processing software!
+```{r loadimages,message=FALSE,warning=FALSE,results='hide'}
+library(ANTsR)
+dim<-2
+filename<-getANTsRData('r16')
+img<-antsImageRead( filename , dim )
+filename<-getANTsRData('r64')
+img2<-antsImageRead( filename , dim )
+mask<-getMask(img,50,max(img),T)
+mask2<-getMask(img,150,max(img),T)
+nvox<-sum( mask == 1 )
+nvox2<-sum( mask2 == 1 )
+```
+The brain has `r nvox` voxels ...
+
+## A Quick <span style="color:grey;">*ANTsR*</span> example
+
+Simulate a population morphometry study - a "VBM" ...
+```{r morph,results='hide'}
+simnum<-10
+imglist<-list()
+imglist2<-list()
+for ( i in 1:simnum ) {
+  img1sim<-antsImageClone(img)
+  img1sim[ mask==1 ]<-rnorm(nvox,mean=0.5)
+  img1sim[ mask2==1 ]<-rnorm(nvox2,mean=2.0)
+  img2sim<-antsImageClone(img2)
+  img2sim[ mask==1 ]<-rnorm(nvox,mean=0.20)
+  imglist<-lappend(imglist,img1sim)
+  imglist2<-lappend(imglist2,img2sim)
+}
+imglist<-lappend( imglist, imglist2 )
+mat<-imageListToMatrix( imglist, mask )
+DX<-factor( c( rep(0,simnum), rep(1,simnum) ) )
+mylmresults<-bigLMStats( lm( mat ~ DX ) )
+qvals<-p.adjust( mylmresults$pval.model ) 
+```
+The minimum q-value is `r min(qvals)` ...
+
+## Visualize the histograms of effects
+```{r vizmorph,results='hide'}
+whichvox<-qvals < 1.e-2
+voxdf<-data.frame( volume=c( as.numeric( mat[,whichvox] ) ), DX=DX )
+ggplot(voxdf, aes(volume, fill = DX)) + geom_density(alpha = 0.2)
+```
+
+## Visualize the anatomical distribution
+```{r vizmorph2hide,results='hide',echo=FALSE}
+betas<-antsImageClone(mask)
+betavec<-abs(mylmresults$beta.t[1,])
+betas[mask==1]<-betavec
+SmoothImage(dim,betas,1.5,betas)
+thresh<-paste(3.0,'x',max(betavec),sep='')
+ofn<-paste(figpath,'vizmorph2.jpg',sep='')
+```
+
+```{r vizmorph2,results='hide'}
+plotANTsImage(img,functional=list(betas),threshold=thresh,
+  outname=ofn)
+```
+
+![](`r ofn`)
+
+## Network visualization
+see `?plotBasicNetwork`
+```{r networkfn,results='hide',warning=FALSE,echo=FALSE,message=FALSE}
+ofn<-paste(figpath,'network',sep='')
+ofnpng<-paste(ofn,'.png',sep='')
+```
+```{r network,results='hide',warning=FALSE,echo=FALSE,message=FALSE,eval=F}
+       mnit<-getANTsRData("mni")
+       mnit<-antsImageRead(mnit,3)
+       mnia<-getANTsRData("mnia")
+       mnia<-antsImageRead(mnia,3)
+       ThresholdImage(3,mnit,mnit,1,max(mnit))
+       ImageMath(3,mnit,"FillHoles",mnit)
+       cnt<-getCentroids( mnia, clustparam = 50 )
+       aalcnt<-cnt$centroids[1:90,]
+       brain<-renderSurfaceFunction( surfimg =list( mnit ) , alphasurf=0.1 ,smoothsval = 1.5 )
+       testweights<-matrix( rep( 0, 90*90 ) ,nrow=90)
+       testweights[31,37]<-1  # ant cingulate to hipp
+       testweights[31,36]<-2  # ant cingulate to post cingulate
+       testweights[11,65]<-3  # broca to angular 
+       plotBasicNetwork( centroids = aalcnt , brain , weights=testweights )
+       id<-par3d("userMatrix")
+       rid<-rotate3d( id , -pi/2, 1, 0, 0 )
+       rid2<-rotate3d( id , pi/2, 0, 0, 1 )
+       rid3<-rotate3d( id , -pi/2, 0, 0, 1 )
+       par3d(userMatrix = id ) 
+       dd<-make3ViewPNG(  rid, id, rid2,  ofn )
+       par3d(userMatrix = id ) 
+```
+![](`r ofnpng`)
+
+## The power of *ANTs* $+$ *R* $\rightarrow$<br /> <span style="color:red;">**Reproducible imaging science**</span>
+
+![](./figures/antsgoals.png)
+
+...
+used in ["Sparse canonical correlation analysis relates network-level atrophy to multivariate cognitive measures in a neurodegenerative population"](http://www.ncbi.nlm.nih.gov/pubmed/24096125) and several upcoming ...
+
+# Wrap-up & Conclusions
+
+## Questions driving *ANTs* ($+$ Refs.1)
+
+* how should we geometrically transform anatomical coordinates?
+
+    - [syn paper](http://www.ncbi.nlm.nih.gov/pubmed/17659998) - our geometric transformation model of choice
+    - [recent B-spline alternative/improvement](http://www.ncbi.nlm.nih.gov/pubmed/24409140)
+
+* how should we measure pairwise image similarity?
+
+    - [similarity metric evaluation](http://www.ncbi.nlm.nih.gov/pubmed/20851191) compares functions for computing rigid or affine transformations between images
+
+* what if this pair has rgb/vector/tensor voxels?
+
+    - [dti similarity](http://www.ncbi.nlm.nih.gov/pubmed/18041273)
+
+* how do we extend from pairs to hundreds or thousands of pairs of images?
+
+    - [optimal templates](http://www.ncbi.nlm.nih.gov/pubmed/?term=avants+optimal+template) and [spatial priors](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
+    - species specific templates/priors in [chimps](http://www.ncbi.nlm.nih.gov/pubmed/23516289) and [canines](http://www.ncbi.nlm.nih.gov/pubmed/23284904)
+    - [ants "big data"](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+freesurfer)
+
+* how do we fuse multiple modality images at the subject and population levels?
+
+    - [ants auxiliary modality study](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+logical+circularity)
+
+## Questions driving *ANTs* ($+$ Refs.2)
+
+* can diffeomorphisms [improve cortical thickness measurement](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+freesurfer)?
+
+* how might we efficiently cluster the statistical fields that arise in image analysis?
+
+    - [Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation and [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison)
+    - [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants) for sparse imaging-specific PCA
+
+* how to cluster such fields when we have supervision?
+
+    - [sparse canonical correlation analysis for neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants)
+    - [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460)
+    - [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) - powerful expert systems for segmentation
+
+* how do we implement a fully multivariate *interpretable* brain and behavior study?
+
+    - [SCCAN for imaging & cognition](http://www.ncbi.nlm.nih.gov/pubmed/?term=sccan+avants)
+
+* how do we extend these ideas to functional MRI & decoding?
+
+    - [recent unpublished software](http://stnava.github.io/RKRNS/) 
+    - [recent work with Ben Kandel](..not yet...)
+
+## *ANTs* longitudinal analysis
+
+* Longitudinal image processing issues
+    - [registration induced bias](http://www.ncbi.nlm.nih.gov/pubmed/20005963)
+    - [general & TBI-specific issues in longitudinal analysis](http://www.ncbi.nlm.nih.gov/pubmed/23549059)
+    - [reproducibility of CBF](http://www.ncbi.nlm.nih.gov/pubmed/22517961)
+    - [structure-specific analysis](http://www.ncbi.nlm.nih.gov/pubmed/22306801)
+
+* An early study of longitudinal cortical change in ALS
+    - [ALS atrophy rates](http://www.ncbi.nlm.nih.gov/pubmed/16317254)
+
+* Extension of standard-setting ants cortical thickness pipeline to longitudinal data
+    - [DynANTs (unpublished)](https://github.com/stnava/DynANTs)
+
+## Challenges: Computational and Scientific
+
+- Scalability: **need to fuse feature selection methods with transformation optimization**
+- Scalability: **need to leverage existing ITK streaming infrastructure in application level tool**
+- Domain expertise: Customizable for specific problems but sometimes not specific enough
+- Rapid development: colleagues still need familiarity with compilation for latest ANTs features
+- Latest theoretical advances in registration not yet wrapped for users
+- Need more [Documentation](http://stnava.github.io/ANTs/)  & [testing](http://testing.psychiatry.uiowa.edu/CDash/index.php?project=ANTS) ...
+
+## Recap
+
+- Powerful, general-purpose, <span style="color:red;">well-evaluated</span> registration and segmentation.
+
+- Differentiable maps with differentiable inverse <span style="color:red;">$+$ statistics in these spaces</span>
+
+- Evaluated in multiple problem domains</span> via internal studies & open competition
+
+- Borg philosophy: <span style="color:red;">"best of"</span> from I/O, to processing to statistical methods
+
+- Open source, testing, many examples, consistent style, multiple platforms,  active community support ...
+
+- Integration with *R* $+$ novel tools for prediction, decoding, high-to-low dimensional statistics.
+
+- Collaborations with [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
+
+## Tools you can use for imaging science
+
+- Core developers:  *B. Avants, N. Tustison, H. J. Johnson, J. T. Duda*
+
+- Many contributors, including users ...
+
+- Multi-platform, multi-threaded C++ [stnava.github.io/ANTs](stnava.github.io/ANTs)
+
+- Developed in conjunction with [http://www.itk.org/](http://www.itk.org/)
+
+- R wrapping and extension [stnava.github.io/ANTsR](stnava.github.io/ANTsR)
+
+- rapid development, regular testing $+$ many eyes $\rightarrow$ bugs are shallow
+
+<img style="float: right" src="figures/penn.png" />
+<img style="float: left" src="figures/picsl.jpg" />
+
+# References

### 2014-11-11 README.R

@@ -6,14 +6,15 @@ library(ggplot2)
 library(shiny)
 library(ggvis)
 library(rmarkdown)
+library(revealjs)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
-rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
-rawrmds<-c("ants2015.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
-rawrmds<-c("ants2015_GE.Rmd", "evaluation/antsvfreesurfer2.Rmd", "lesions/lesions.Rmd", "longitudinal/longitudinal.Rmd" )
-rawrmds<-c( "ants2015_GE.Rmd", "philosophy/circularity/circularity.Rmd", "evaluation/antsvfreesurfer2.Rmd" )
+rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer2.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
+# rawrmds<-c("ants2015.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
+# rawrmds<-c("ants2015_GE.Rmd", "evaluation/antsvfreesurfer2.Rmd", "lesions/lesions.Rmd", "longitudinal/longitudinal.Rmd" )
+#rawrmds<-c( "ants2015_GE.Rmd", "philosophy/circularity/circularity.Rmd", "evaluation/antsvfreesurfer2.Rmd" )
 for ( x in 1:length(rawrmds) ) {
[…]

### 2015-04-27 ants2015build.Rmd
ENH:  Updating with new ANTsR

@@
 betas[mask==1]<-betavec
-SmoothImage(dim,betas,1.5,betas)
+smoothImage(betas, 1.5)
 thresh<-paste(3.0,'x',max(betavec),sep='')
@@
 ```{r vizmorph2,results='hide'}
-plotANTsImage(img,functional=list(betas),threshold=thresh,
+plot.antsImage(img,functional=list(betas),threshold=thresh,
   outname=ofn)

### 2015-04-27 README.R

@@ -6,7 +6,7 @@ library(ggplot2)
 library(shiny)
 library(ggvis)
 library(rmarkdown)
-library(revealjs)
+# library(revealjs)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
 rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer2.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")

### 2015-04-28 background/background1.Rmd
WIP: regular update
ENH:  Adding circularity section.
ENH:  More slides for compeittion.

@@
 
-<div align="center"><img width="1800" src="./figures/bant2.png" frameborder="0"></img></div>
+<div align="center"><img width="1800" src="./figures/brian_and_nick.png" frameborder="0"></img></div>
 
-BBA & NT
+BBA & NJT
 
@@
 
-* (maybe he should have used ANTs?)
+* (maybe he should have used *ANTs*?)
+
+## Image mapping & biology: 1917
+
+![](./figures/dthompson.png)
+
+D'Arcy Thompson
 
@@
 
-## ANTs Lineage
+## *ANTs* Lineage
 
@@
 
+## Diffeomorphisms: image parameterization in a metric space
+
+![](./figures/shape_appearance.png)
+
 ## General purpose library for multivariate image registration, segmentation & statistical analysis tools
@@
 
-## ANTs: Beyond Registration
+## *ANTs*: Beyond Registration
 
@@
 [Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)
-
-```
-
-## On documentation
-
-![](figures/handsaw.jpg)
-
-simple and nearly self-explanatory
 

### 2015-04-28 competitions/competitions.Rmd
ENH:  More slides for compeittion.

@@
 
-##
+## <span style="color:green;">Competitions</span>
 
-![](./evaluation/figures/evalhistory.png)
+* [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496)
+* [EMPIRE 2010](http://empire10.isi.uu.nl)
+* [Multi-Atlas Label Challenge 2012](https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page)
+* [SATA Challenge 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events)
+* [BRATS 2013](http://martinos.org/qtim/miccai2013/)
+* [STACOM 2014 MoCo Challenge](http://www.cardiacatlas.org/web/stacom2014/moco-introduction)
+
+<!--- ![](./evaluation/figures/evalhistory.png) -->
+
+## <span style="color:green;">Klein 2009</span> <small>brain image registration</small>
+
+![](./competitions/figures/nihms-130679-f0001.jpg)
+
+* 14 algorithms
+* publicly available data
+* unbiased evaluation
+
+## <span style="color:green;">Klein 2009</span> <small>results</small>
+
+![](./competitions/figures/KleinResults2009.png)
+
+_"One of the most significant findings of this study is that the relative performances of
+the registration methods under comparison appear to be little affected by the choice of
+subject population, labeling protocol, and type of overlap measure....  ART, SyN, IRTK, and
+SPM's DARTEL Toolbox gave the best results according to overlap and distance measures,
+with ART and SyN delivering the most consistently high accuracy across subjects and label sets."_
+
+## <span style="color:green;">EMPIRE 2010</span> <small>lung image registration</small>
+
+## <span style="color:green;">Multi-Atlas Label Challenge 2012</span> <small>atlas label fusion</small>
+
+## <span style="color:green;">SATA Challenge 2012</span> <small>multi-modal/multi application label fusion</small>
 
@@
 
-_"Optimal symmetric multimodal templates and concatenated random forests for
-supervised brain tumor segmentation (simplified) with ANTsR"_
+_Optimal symmetric multimodal templates and concatenated random forests for
+supervised brain tumor segmentation (simplified) with ANTsR_
 

### 2015-04-29 competitions/competitions.Rmd
ENH:  More comp. stuff.

@@
 
-## <span style="color:green;">Klein 2009</span> <small>brain image registration</small>
+## <span style="color:green;">Klein 2009</span>
 
@@
 * publicly available data
-* unbiased evaluation
+* different labeling protocols
+* developers tune their own algorithms
 
-## <span style="color:green;">Klein 2009</span> <small>results</small>
+## <span style="color:green;">Results</span>
 
@@
 
-## <span style="color:green;">EMPIRE 2010</span> <small>lung image registration</small>
+## <span style="color:green;">EMPIRE 2010</span>
 
-## <span style="color:green;">Multi-Atlas Label Challenge 2012</span> <small>atlas label fusion</small>
+![](./competitions/figures/EMPIRE10criteria.png)
 
-## <span style="color:green;">SATA Challenge 2012</span> <small>multi-modal/multi application label fusion</small>
+* Alignment of lung boundaries,
+* major fissures,
+* annotated landmark pairs, and
+* topology of displacement field.
 
-## <span style="color:green;">BRATS 2013</span> <small>brain tumor segmentation</small>
+## <span style="color:green;"> Results</span>
+
+![](./competitions/figures/EMPIRE10Results.png)
+
+## <span style="color:green;">Multi-Atlas 2012</span>
+
+![](./competitions/figures/NKI30_MALF.png)
+
+## <span style="color:green;">Results</span>
+
+![](./competitions/figures/MALF2012.png)
+
+## <span style="color:green;">SATA 2013</span>
+
+## <span style="color:green;">BRATS 2013</span>
 
@@
 
-## <span style="color:green;">STACOM 2014</span> <small>cardiac motion estimation</small>
+## <span style="color:green;">STACOM 2014</span>
 

### 2015-04-29 README.R

@@ -9,7 +9,8 @@ library(rmarkdown)
 # library(revealjs)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
-rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer2.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
+# rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer2.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
+rawrmds<-c("ants2015.Rmd","competitions/competitions.Rmd")
 # rawrmds<-c("ants2015.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 # rawrmds<-c("ants2015_GE.Rmd", "evaluation/antsvfreesurfer2.Rmd", "lesions/lesions.Rmd", "longitudinal/longitudinal.Rmd" )
 #rawrmds<-c( "ants2015_GE.Rmd", "philosophy/circularity/circularity.Rmd", "evaluation/antsvfreesurfer2.Rmd" )

### 2015-04-29 competitions/competitions.Rmd
ENH:  Finish up competition slides.

@@
 
+![](./competitions/figures/SATA_data.png)
+
 ## <span style="color:green;">BRATS 2013</span>
 
-![](./competitions/figures/brats2013results.png)
+![](./competitions/figures/brats2013results1.png)
 
-_Optimal symmetric multimodal templates and concatenated random forests for
-supervised brain tumor segmentation (simplified) with ANTsR_
+## <span style="color:green;">Results</span>
+
+![](./competitions/figures/brats2013results2.png)
+
+Optimal symmetric multimodal templates and concatenated random forests for
+supervised brain tumor segmentation (simplified) with ANTsR, _Neuroinformatics_.
 
@@
 
-![](./competitions/figures/cardiacBSplineSyN.png)
+![](./competitions/figures/image_gallery.gif)
 
-A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140)
+<!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->

### 2015-05-08 installation/ants_installation.Rmd
ENH:  Installation and initial testing.

# ANTs installation

##

ANTs is a <span style="color:red;">_dynamic_</span> toolkit so,

![](./installation/figures/coder2.png)

for the willing, we recommend compiling from source.

## Requirements for source installation

* [CMake](http://www.cmake.org) -- build system
* [git](http://git-scm.com/downloads) -- version control system
* C++ compiler
* ITK/VTK dependencies are handled by CMake magic

##

https://github.com/stnava/ANTs

* README.md

    * "Is the current code building without compilation errors?"
    * More information about ANTs.

* Where to report [issues](https://github.com/stnava/ANTs/issues)

* or [contribute](https://github.com/stnava/ANTs/pulls).

## From the terminal...

~~~~~~~~~~~~~~~~~~
$ cd ${WHICH_PATH}
$ git clone https://github.com/stnava/ANTs.git
$ cd ANTs
$ mkdir bin
$ cd bin
$ ccmake ..
$ make
$ echo "export ANTSPATH=/${WHICH_PATH}/ANTs/bin/bin/" >> ~/.profile
$ echo "export ITK_GLOBAL_DEFAULT_NUMBER_OF_THREADS=4" >> ~/.profile
$ source ~/.profile
~~~~~~~~~~~~~~~~~~

##

<span style="color:blue;">__Some cmake considerations:__</span>

* Installation location?  (default = /usr/local/bin)
* Enable external applications (only ```jointFusion```)
* Type of build (a debug build produces __slow__ programs)

## Now test installation

##

Try calling the <span style="color:blue;">```KellyKapowski```</span> short help menu.

~~~~~~~~~~~~~~~~~~
$ KellyKapowski -h

COMMAND:
     KellyKapowski

OPTIONS:
     -d, --image-dimensionality 2/3
     -s, --segmentation-image imageFilename
                              [imageFilename,<grayMatterLabel=2>,<whiteMatterLabel=3>]
     -g, --gray-matter-probability-image imageFilename
     -w, --white-matter-probability-image imageFilename
     -c, --convergence [<numberOfIterations=50>,<convergenceThreshold=0.001>,<convergenceWindowSize=10>]
     -t, --thickness-prior-estimate thicknessPriorEstimate
     -a, --thickness-prior-image thicknessPriorFileName
     -r, --gradient-step stepSize
     -l, --smoothing-variance variance
     -m, --smoothing-velocity-field-parameter variance
                                              isotropicMeshSpacing
     -b, --use-bspline-smoothing 1/(0)
     -n, --number-of-integration-points numberOfPoints
     -p, --maximum-number-of-invert-displacement-field-iterations numberOfIterations
     -o, --output imageFileName
                  [imageFileName,warpedWhiteMatterImageFileName]
     -v, --verbose (0)/1
     -h
     --help
~~~~~~~~~~~~~~~~~~

##

or the <span style="color:blue;">```antsRegistration```</span> long help menu.

~~~~~~~~~~~~~~~~~~
$ antsRegistration --help

COMMAND:
     antsRegistration
          This program is a user-level registration application meant to utilize
          ITKv4-only classes. The user can specify any number of "stages" where a stage
          consists of a transform; an image metric; and iterations, shrink factors, and
          smoothing sigmas for each level.Note that dimensionality, metric, transform,
          output, convergence, shrink-factors and smoothing-sigmas parameters are
          mandatory.

OPTIONS:
     --version
          Get Version Information.

     -d, --dimensionality 2/3
          This option forces the image to be treated as a specified-dimensional image. If
          not specified, we try to infer the dimensionality from the input image.

     -o, --output outputTransformPrefix
                  [outputTransformPrefix,<outputWarpedImage>,<outputInverseWarpedImage>]
          Specify the output transform prefix (output format is .nii.gz ). Optionally, one
          can choose to warp the moving image to the fixed space and, if the inverse
          transform exists, one can also output the warped fixed image. Note that only the
          images specified in the first metric call are warped. Use antsApplyTransforms to
          warp other images using the resultant transform(s).

     -j, --save-state saveSateAsTransform
          Specify the output file for the current state of the registration. The state
          file is written to an hdf5 composite file. It is specially usefull if we want to
          save the current state of a SyN registration to the disk, so we can load and
          restore that later to continue the next registration process directly started
          from the last saved state. The output file of this flag is the same as the
          write-composite-transform, unless the last transform is a SyN transform. In that
          case, the inverse displacement field of the SyN transform is also added to the
          output composite transform. Again notice that this file cannot be treated as a
          transform, and restore-state option must be used to load the written file by
          this flag.

     -k, --restore-state restoreStateAsATransform
          Specify the initial state of the registration which get immediately used to
          directly initialize the registration process. The flag is mutually exclusive
          with other intialization flags.If this flag is used, none of the
          initial-moving-transform and initial-fixed-transform cannot be used.

     -a, --write-composite-transform 1/(0)
          Boolean specifying whether or not the composite transform (and its inverse, if
          it exists) should be written to an hdf5 composite file. This is false by default
          so that only the transform for each stage is written to file.
          <VALUES>: 0

     -p, --print-similarity-measure-interval <unsignedIntegerValue>
          Prints out the CC similarity metric measure between the full-size input fixed
          and the transformed moving images at each iteration a value of 0 (the default)
          indicates that the full scale computation should not take placeany value greater
          than 0 represents the interval of full scale metric computation.
          <VALUES>: 0

     -v, --write-interval-volumes <unsignedIntegerValue>
          Writes out the output volume at each iteration. It helps to present the
          registration process as a short movie a value of 0 (the default) indicates that
          this option should not take placeany value greater than 0 represents the
          interval between the iterations which outputs are written to the disk.
          <VALUES>: 0

     -z, --collapse-output-transforms (1)/0
          Collapse output transforms. Specifically, enabling this option combines all
          adjacent transforms wherepossible. All adjacent linear transforms are written to
          disk in the forman itk affine transform (called xxxGenericAffine.mat).
          Similarly, all adjacent displacement field transforms are combined when written
          to disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available)).Also, an
          output composite transform including the collapsed transforms is written to the
          disk (called outputCollapsed(Inverse)Composite).
          <VALUES>: 1

     -i, --initialize-transforms-per-stage (1)/0
          Initialize linear transforms from the previous stage. By enabling this option,
          the current linear stage transform is directly intialized from the previous
          stages linear transform; this allows multiple linear stages to be run where
          each stage directly updates the estimated linear transform from the previous
          stage. (e.g. Translation -> Rigid -> Affine).
          <VALUES>: 0

     -n, --interpolation Linear
                         NearestNeighbor
                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]
                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]
                         BSpline[<order=3>]
                         CosineWindowedSinc
                         WelchWindowedSinc
                         HammingWindowedSinc
                         LanczosWindowedSinc
          Several interpolation options are available in ITK. These have all been made
          available. Currently the interpolator choice is only used to warp (and possibly
          inverse warp) the final output image(s).

     -g, --restrict-deformation PxQxR
          This option allows the user to restrict the optimization of the displacement
          field, translation, rigid or affine transform on a per-component basis. For
          example, if one wants to limit the deformation or rotation of 3-D volume to the
          first two dimensions, this is possible by specifying a weight vector of '1x1x0'
          for a deformation field or '1x1x0x1x1x0' for a rigid
          transformation.Low-dimensional restriction only works if there are no preceding
          transformations.

     -q, --initial-fixed-transform initialTransform
                                   [initialTransform,<useInverse>]
                                   [fixedImage,movingImage,initializationFeature]
          Specify the initial fixed transform(s) which get immediately incorporated into
          the composite transform. The order of the transforms is stack-esque in that the
          last transform specified on the command line is the first to be applied. In
          addition to initialization with ITK transforms, the user can perform an initial
          translation alignment by specifying the fixed and moving images and selecting an
          initialization feature. These features include using the geometric center of the
          images (=0), the image intensities (=1), or the origin of the images (=2).

     -r, --initial-moving-transform initialTransform
                                    [initialTransform,<useInverse>]
                                    [fixedImage,movingImage,initializationFeature]
          Specify the initial moving transform(s) which get immediately incorporated into
          the composite transform. The order of the transforms is stack-esque in that the
          last transform specified on the command line is the first to be applied. In
          addition to initialization with ITK transforms, the user can perform an initial
          translation alignment by specifying the fixed and moving images and selecting an
          initialization feature. These features include using the geometric center of the
          images (=0), the image intensities (=1), or the origin of the images (=2).

     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]
                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]
                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]
                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]
          These image metrics are available--- CC: ANTS neighborhood cross correlation,
          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global
          Correlation. The "metricWeight" variable is used to modulate the per stage
          weighting of the metrics. The metrics can also employ a sampling strategy
          defined by a sampling percentage. The sampling strategy defaults to 'None' (aka
          a dense sampling of one sample per voxel), otherwise it defines a point set over
          which to optimize the metric. The point set can be on a regular lattice or a
          random lattice of points slightly perturbed to minimize aliasing artifacts.
          samplingPercentage defines the fraction of points to select from the domain. In
          addition, three point set metrics are available: Euclidean (ICP), Point-set
          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).

     -t, --transform Rigid[gradientStep]
                     Affine[gradientStep]
                     CompositeAffine[gradientStep]
                     Similarity[gradientStep]
                     Translation[gradientStep]
                     BSpline[gradientStep,meshSizeAtBaseLevel]
                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]
                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]
                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]
                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]
          Several transform options are available. The gradientStep or learningRate
          characterizes the gradient descent optimization and is scaled appropriately for
          each transform using the shift scales estimator. Subsequent parameters are
          transform-specific and can be determined from the usage. For the B-spline
          transforms one can also specify the smoothing in terms of spline distance (i.e.
          knot spacing).

     -c, --convergence MxNxO
                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]
          Convergence is determined from the number of iterations per level and is
          determined by fitting a line to the normalized energy profile of the last N
          iterations (where N is specified by the window size) and determining the slope
          which is then compared with the convergence threshold.

     -s, --smoothing-sigmas MxNxO...
          Specify the sigma of gaussian smoothing at each level. Units are given in terms
          of voxels ('vox') or physical spacing ('mm'). Example usage is '4x2x1mm' and
          '4x2x1vox' where no units implies voxel spacing.

     -f, --shrink-factors MxNxO...
          Specify the shrink factor for the virtual domain (typically the fixed image) at
          each level.

     -u, --use-histogram-matching
          Histogram match the images before registration.

     -l, --use-estimate-learning-rate-once
          turn on the option that lets you estimate the learning rate step size only at
          the beginning of each level. * useful as a second stage of fine-scale
          registration.

     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]
          Winsorize data based on specified quantiles.

     -x, --masks [fixedImageMask,movingImageMask]
          Image masks to limit voxels considered by the metric.

     --float
          Use 'float' instead of 'double' for computations.
          <VALUES>: 0

     -v, --verbose (0)/1
          Verbose output.

     -h
          Print the help menu (short version).

     --help
          Print the help menu. Will also print values used on the current command line
          call.
          <VALUES>: 1
~~~~~~~~~~~~~~~~~~

## However,

[binaries are available](https://github.com/stnava/ANTs/releases).

![](./installation/figures/binaries.png)

## Steps for binary installation

1. Download appropriate binaries (~350 MB) from ANTs [website](https://github.com/stnava/ANTs/releases).

2. De-archive downloaded file to desired directory.

3. <a href="#/from-the-terminal">export</a> the ```ANTSPATH``` to the .profile or .bashrc file.

4. <a href="#/now-test-installation">Test</a> the installation by calling an ANTs program help menu.

### 2015-05-08 installation/antsr_installation.Rmd
ENH:  Installation and initial testing.

# _ANTsR_ installation

## R

http://www.r-project.org

## Requirements for source installation

* [CMake](http://www.cmake.org) -- build system
* [git](http://git-scm.com/downloads) -- version control system
* C++ compiler

##

Install _ANTsR_ dependencies

~~~~~~~~~~~~~~~~~
$ R

R version 3.2.0 (2015-04-16) -- "Full of Ingredients"
Copyright (C) 2015 The R Foundation for Statistical Computing
Platform: x86_64-apple-darwin13.4.0 (64-bit)

R is free software and comes with ABSOLUTELY NO WARRANTY.
You are welcome to redistribute it under certain conditions.
Type 'license()' or 'licence()' for distribution details.

  Natural language support but running in an English locale

R is a collaborative project with many contributors.
Type 'contributors()' for more information and
'citation()' on how to cite R or R packages in publications.

Type 'demo()' for some demos, 'help()' for on-line help, or
'help.start()' for an HTML browser interface to help.
Type 'q()' to quit R.

> antsrDependencies <- c( "Rcpp", "tools", "methods", "magrittr" )
> install.packages( pkgs = antsrDependencies, dependencies = TRUE )
~~~~~~~~~~~~~~~~~~

## Command line install

~~~~~~~~~~~~~~~~~
$ cd ${WHICH_PATH}
$ git clone https://github.com/stnava/ITKR.git
$ git clone https://github.com/stnava/ANTsR.git
~~~~~~~~~~~~~~~~~

## Install ITK and ANTsR

~~~~~~~~~~~~~~~~~
$ R CMD INSTALL ITKR
$ R CMD INSTALL ANTsR
~~~~~~~~~~~~~~~~~

## ANTsR updates?

~~~~~~~~~~~~~~~~~
$ cd ${WHICH_PATH}/ITKR
$ git pull
$ cd ${WHICH_PATH}/ANTsR
$ git pull
$ R CMD INSTALL ITKR
$ R CMD INSTALL ANTsR
~~~~~~~~~~~~~~~~~

## However,

[binaries are available](https://github.com/stnava/ANTsR/releases).

![](./installation/figures/antsrBinaries.png)

## Steps for binary installation

* Download [archive](https://github.com/stnava/ANTsR/releases) to the desired location
* install using R

~~~~~~~~~~~~~~~~~~~~~~~~~~
$ R CMD INSTALL ANTsR*gz
~~~~~~~~~~~~~~~~~~~~~~~~~~

## Test installation

~~~~~~~~~~~~~~~~~~~~~~~~~~
$ R
.
.
.
> library( ANTsR )
~~~~~~~~~~~~~~~~~~~~~~~~~~

_if no error message, then done!_

##

Let's do something simple:

1. Fetch MNI template.

2. Read in antsImage

3. Perform N3* bias correction

##

_Cross your fingers..._

~~~~~~~~~~~~~~~~~~~~~~~~~~
$ R
.
.
.
> library( ANTsR )
> mniTemplateFileName <- getANTsRData( "mni" )
trying URL 'http://placid.nlm.nih.gov/download?items=10785'
Content type 'application/octet-stream' length 3219212 bytes (3.1 MB)
==================================================
downloaded 3.1 MB
> image <- antsImageRead( mniTemplateFileName )
> imageN3 <- n3BiasFieldCorrection( image, 4 )
~~~~~~~~~~~~~~~~~~~~~~~~~~

## RStudio

(add more here)

### 2015-05-08 installation/snap_installation.Rmd
ENH:  Installation and initial testing.

# ITK-SNAP installation

##

![](./installation/figures/snaplogo3.png)

## MacOS

1. [Download](http://www.itksnap.org/pmwiki/pmwiki.php?n=Downloads.SNAP3)

2. Drag the ```ITK-SNAP.app``` icon to the Applications folder

3. Drag the ```itksnap``` icon to the ```usr_local_bin``` folder

## Linux

1. [Download](http://www.itksnap.org/pmwiki/pmwiki.php?n=Downloads.SNAP3)

2. Open terminal.

3. Uncompress the downloaded file and copy the archive directory to ```/usr/local/```.

~~~~~~~~~~~~~~~~~~~~~~~
$ tar -zxvf itksnap-3.2.0-rc2-20140919-Linux_x86_64.tar.gz
$ sudo cp itksnap-3.2.0-rc2-20140919-Linux_x86_64/ /usr/local/
$ itksnap
~~~~~~~~~~~~~~~~~~~~~~~

## Thanks Paul!

and [others](http://www.itksnap.org/pmwiki/pmwiki.php?n=Main.Credits)

### 2015-05-08 README.R

@@ -11,6 +11,9 @@ srcdir<-"./"
 buildrmd='ants2015build.Rmd'
 # rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer2.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 rawrmds<-c("ants2015.Rmd","competitions/competitions.Rmd")
+
+rawrmds<-c("ants2015.Rmd","installation/ants_installation.Rmd","installation/antsr_installation.Rmd","installation/snap_installation.Rmd")
+
 # rawrmds<-c("ants2015.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 # rawrmds<-c("ants2015_GE.Rmd", "evaluation/antsvfreesurfer2.Rmd", "lesions/lesions.Rmd", "longitudinal/longitudinal.Rmd" )
 #rawrmds<-c( "ants2015_GE.Rmd", "philosophy/circularity/circularity.Rmd", "evaluation/antsvfreesurfer2.Rmd" )

### 2015-05-09 evaluation/antsvfreesurfer2.Rmd
ENH:  More edits to the talk.
BUG:  Wrong filename.
ENH:  More stuff.

@@
-# ANTs brain morphology<br><br>[<small>"*Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
+# ANTs brain morphology<br>[<small>"*Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
 
-## Cortical thickness studies:
+##
+
+__Cortical thickness studies__
+
 ```{r, results='asis', echo = FALSE}
@@
 
-## *ANTs*-related background
+##
+
+__ANTs-related background__
 
 * Sandy, Brian, and <span style="color:red;">DiReCT</span>
-  + used other tools such as FMRIB's Automated Segmentation Tool (FAST)
+    + used other tools such as FMRIB Automated Segmentation Tool (FAST)
     + `KellySlater.cxx`
-  * scripts "adequate for Penn data"
+* pipedream scripts "adequate for Penn data."
 * `KellyKapowski.cxx` and `antsCorticalThickness.sh`
@@
 
-## The *ANTs* structural brain mapping workflow
+##
+
+__The ANTs structural brain mapping workflow__
 
@@
 
-## Basic components of the pipeline
+##
+
+__Basic components of the pipeline__
 
@@
 
-## Template building
+##
+
+__Template building__
 
@@
 
-## Template building (cont.)
+##
+
+__Template building__ (cont.)
 
@@
 
-## Brain extraction comparison<br>*ANTs* vs. FreeSurfer
+##
+
+__Brain extraction comparison ANTs vs. FreeSurfer__
 
@@
 
-## Brain segmentation
+##
+
+__Brain segmentation__
 
@@
 
-Randomly selected healthy individuals.  Atropos gets good performance across ages.
+Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.
 
-## Cortical thickness estimation
+##
+
+__Cortical thickness estimation__
 
@@
 
-## _But without ground truth, how does one evaluate the pipeline?_
+## <span style="color:red;">_But without ground truth, how does one evaluate the pipeline?_</span>
+
+##
+
+<div align="center"><img height="400" src="./evaluation/figures/ageDistribution.png" frameborder="0"></img></div>
 
 * Use age and gender (demographic information) in training/prediction paradigm
-* Public data sets (IXI, NKI, Oasis, MMRR)
-* $>$ 1200 subjects, age 7 to over 90 years old
+* Public data sets (IXI, NKI, OASIS, MMRR)
+* $>$ 1200 subjects, age 4 to over 94 years old
 
-## Prediction from cortical thickness data:<br>gender and age
+##
+
+__Prediction from cortical thickness data:<br>gender and age__
 
@@
 
-## Regional importance comparison
+##
+
+__Age prediction per site__
+
+<div align="center"><img height="350" src="./evaluation/figures/agePredictionPerSite.png" frameborder="0"></img></div>
+
+##
+
+__Regional importance comparison__
 
@@
 
-## Regional importance comparison (cont.)
+##
 
+__Regional measurements__
 <div align="center"><img height="550" src="./evaluation/figures/antsvfreesurfer_regionalPlots.png" frameborder="0"></img></div>
-
-# Cortical thickness extensions

### 2015-05-09 evaluation/antsvfreesurfer2_extra.Rmd
ENH:  More stuff.

# But, wait, there's more!

##

[__Data availability__](https://github.com/ntustison/KapowskiChronicles)

*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"  <span style="color:blue;">Sure, why not?</span>

*  "_I was wondering if you would make available the CT in each ROI for each subject..._" <span style="color:blue;">Sure, why not?  Would you also like the surface areas and volumes?</span>

*  "_Can I have one or more of the templates that you used for your study?_"  <span style="color:blue;">Would you like the priors as well?</span>

*  "_Hey Nick, can we hire you to do an [EZ-MAP]-type study?_" <span style="color:blue;">What about something better?</span>

##  What about using both the T1 & T2?

##

__ANTs tools are multivariate__

<div align="center"><img height="450" src="./evaluation/figures/rfRmse0.5ANTsT1T2.png" frameborder="0"></img></div>

##

__Arno-thick-in-the-head (ATITH)__

<br><br>
<span style="color:blue;">_What if we made a crude estimate of the cortical thickness?_</span>
<br><br>

$thickness_{ROI} = \frac{volume_{ROI}}{area_{ROI}}$

##

<span style="color:blue;">Make sure you estimate the [surface area](http://www.insight-journal.org/browse/publication/852) correctly!</span>

![](./evaluation/figures/LabelThickness.png)

## So how does ATITH compare with ANTs, FS?

##

__Prediction from cortical thickness data:<br>gender and age__

<div align="center"><img height="350" src="./evaluation/figures/atith.png" frameborder="0"></img></div>

##

![](./evaluation/figures/brainConstellationMaps.png)

# But the best part is ...

## it is absolutely free!

~~~~~~~~~~~~~~~~~~~~~~~
${ANTSPATH}/antsCorticalThickness.sh \
  -a IXI/T1/IXI002-Guys-0828-T1.nii.gz \
  -e IXI/template/T_template0.nii.gz \
  -m IXI/template/T_template0ProbabilityMask.nii.gz \
  -f IXI/template/T_template0ExtractionMask.nii.gz \
  -p IXI/template/Priors/priors%d.nii.gz \
  -o IXI/ANTsResults/IXI002-Guys-0828-
~~~~~~~~~~~~~~~~~~~~~~~

_(as in speech, not beer)_

## Don't worry,

we'll run a 2-D example this afternoon.
<BR><BR>

https://github.com/ntustison/antsCorticalThicknessExample

# Extensions

### 2015-05-09 installation/antsr_installation.Rmd
ENH:  More stuff.

@@
 > install.packages( pkgs = antsrDependencies, dependencies = TRUE )
+> moreAntsrDependencies <- c( "igraph", "randomForest", "misc3d", "rgl", "mFilter", "fastICA", "fpc", "knitr", "rmarkdown", "pixmap", "png", "signal", "visreg" )
+> install.packages( moreAntsrDependencies )
+
 ~~~~~~~~~~~~~~~~~~

### 2015-05-09 lesions/lesions.Rmd
ENH:  More stuff.

@@
 
-## antsCorticalThickness.sh is adaptable!
+##
+```antsCorticalThickness.sh``` is adaptable!
 
-1. Register subject (or single subject template) to normal template.
+1. Register subject (or single subject template) to normal template with priors.
 
@@
 
-3. Create additional "lesion" prior, i.e. ```SmoothImage 3 ${lesionMask} 1 ${lesionPrior} 1```.
+3. Create additional "lesion" prior, i.e.
+
+~~~~~~~~~~~~~~~~~~~~~~~
+SmoothImage 3 ${lesionMask} 1 ${lesionPrior} 1
+~~~~~~~~~~~~~~~~~~~~~~~
 
@@
 
-## Modified template spatial priors
+##
 
-![](lesions/figures/lesionPrior.png)
+__Modified template spatial priors__
 
-## antsCorticalThickness.sh using lesion prior
+<div align="center"><img height="450" src="lesions/figures/lesionPrior.png" frameborder="0"></img></div>
 
-![](lesions/figures/lesionSegmentation.png)
+##
 
+```antsCorticalThickness.sh``` using lesion prior
+
+<div align="center"><img height="450" src="lesions/figures/lesionSegmentation.png" frameborder="0"></img></div>
+
+<!--
 Only change to the command call is an additional '-c WM[7]' which means "combine
 the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."
+-->

### 2015-05-09 longitudinal/longitudinal2.Rmd
ENH:  More stuff.

# Longitudinal processing

##

![](./longitudinal/figures/unbiasedPapers.png)

##

![](./longitudinal/figures/longitudinalPipeline.png)

### 2015-05-09 README.R

@@ -9,14 +9,31 @@ library(rmarkdown)
 # library(revealjs)
 srcdir<-"./"
 buildrmd='ants2015build.Rmd'
+
+####################
+#
+#             May 19
+#
+####################
+
+########   Morning    ##########
+
+# Retrospective
+rawrmds <- c( "antsMni.Rmd", "background/background1.Rmd", "competitions/competitions.Rmd", "philosophy/circularity/circularity.Rmd" )
+
+# Research talk
+# rawrmds <- c( "evaluation/antsvfreesurfer2.Rmd", "evaluation/antsvfreesurfer2_extra.Rmd", "lesions/lesions.Rmd", "longitudinal/longitudinal2.Rmd" )
+
+########   Afternoon    ##########
+# rawrmds <- c( "ants2015.Rmd", "installation/ants_installation.Rmd", "installation/antsr_installation.Rmd", "installation/snap_installation.Rmd" )
+
+
+
+
 # rawrmds<-c("ants2015.Rmd","background/background1.Rmd","impact/impact1.Rmd","templates/templates.Rmd","evaluation/evaluation1.Rmd","evaluation/antsvfreesurfer2.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
-rawrmds<-c("ants2015.Rmd","competitions/competitions.Rmd")
-
-rawrmds<-c("ants2015.Rmd","installation/ants_installation.Rmd","installation/antsr_installation.Rmd","installation/snap_installation.Rmd")
-
 # rawrmds<-c("ants2015.Rmd","evaluation/antsvfreesurfer.Rmd","longitudinal/longitudinal.Rmd","lesions/lesions.Rmd","antsr/antsrdemo.Rmd","conclusion/conclusion.Rmd","lastslide.Rmd")
 # rawrmds<-c("ants2015_GE.Rmd", "evaluation/antsvfreesurfer2.Rmd", "lesions/lesions.Rmd", "longitudinal/longitudinal.Rmd" )
-#rawrmds<-c( "ants2015_GE.Rmd", "philosophy/circularity/circularity.Rmd", "evaluation/antsvfreesurfer2.Rmd" )
[…]

### 2015-05-10 ANTsScience.Rmd
WIP: science ants section

---
title: "ANTs in science"
author: "Brian B. Avants et al."
date: "May 9, 2015"
output: pdf_document
---

# Introduction

Advanced Normalization Tools (ANTs, originating at [sourceforge.net](sourceforge.net) on 2008-06-26 and now residing at [http://stnava.github.io/ANTs/](http://stnava.github.io/ANTs/) is a systematic framework for quantitative biological image analysis based on the Insight ToolKit [www.itk.org](www.itk.org).  ANTs was first created to rapidly disseminate our latest research to the community of scientists who depend on imaging analytics and to allow them to study different organ systems, species or modalities with the same sound foundation.  While originally focused on diffeomorphic image registration, ANTs now incorporates novel and cutting-edge methods for segmentation, feature extraction and, more recently, complete statistical pipelines via ANTsR [http://stnava.github.io/ANTsR/](http://stnava.github.io/ANTsR/).  In 2014, there were nearly 2,000 citations to ANTs and the software is cloned, downloaded or otherwise accessed over 100-200 times per week, on average.  Though ANTsR is relatively new, this software is cloned (via github) on average 50 times per week---a substantial number that suggests the value of the software.

# Novelty

ANTs and ANTsR support imaging analysis in two, three and four dimensions.  The framework is also designed explicitly for multivariate analyses.  Nearly every tool within ANTs/R that can be multivariate is multivariate.  For example, the ANTs registration tool is capable of combining several metrics each with its own weight function.  Complementary metrics might measure a different imaging modality (e.g. T1 and T2) or might include a different feature (landmarks) or type of similarity (mutual information and correlation) in addition to the core metric.  ANTs registration is also optimized for fast computation of high-dimensional diffeomorphic transformations with regularization over space or over space and time simultaneously, the latter being appropriate for longitudinal studies or studies of cardiac dynamics.  The Atropos segmentation tool also incorporates multiple modalities via parametric models (Mahalanobis distance) or non-parametric models (products of joint probabilities).  More recently, we implemented, in ANTsR, the challenge-winning MRVNRFS algorithm which won the BRATS2013 tumor segmentation challenge.

# Technical solutions

* Accurate high-dimensional and flexible digital diffeomorphisms with multivariate similarity

* Multiple modality template building in the digital diffeomorphic space

* Prior-based multivariate / multiple modality segmentation in the public domain

* Volumetric sub-voxel accurate thickness, evaluated against Freesurfer

* Joint intensity and joint label fusion

* Broad distribution channels: ITK, Slicer, Neurodebian, BrainsFit, etc

* Eigenanatomy and a parameter-free version

* SCCAN

* Automated template construction with priors based on SyGN, JIF and Atropos ... with probability modifiers.

* RIPMMARC

* A highly-customizable adaptive processing pipeline for cerebral blood flow calculation

* Joint intensity and landmark-based registration

* Broad testing across organ systems and species, deep testing of registration and segmentation and detection power capabilities

* Multi-start optimization

* Standardization of registration architecture and transformations through our work on ITK version 4+.

* MRV-NRF ...

# Clinical and neuroscience solutions

* mouse

* chimp, rhesus

* lung

* heart

# Future

* Sparse transformations

* Sparse registration

* ICDM - framework for sparse image and pointset/curve/surface matching

* More fully reproducible studies based on ANTsR ...

.....

system to analyze a multiple modality neuroimaging dataset derived from the freely available Pediatric Template of Brain Perfusion (http://www.nature.com/articles/sdata20153).

### 2015-05-17 background/background.Rmd
ENH:  More material.

# ANTs lineage

##

__Image mapping & perception: 1877-8__
<BR><BR>
Francis Galton: _Can we see criminality in the face?_

![](./figures/galton.png)

<!--
Notes:
* Use of "composite portraiture" and what he called "eugenics"
* Can we see criminality, mental illness, syphilis, and others in facial features?
* Despite the obvious prejudices driving his research, he was a pioneer.
-->

##

<!--
![](./background/figures/FrancisGalton2.jpg)
-->

<!--
Notes:
* Another example where he has manually categorized facial features and try to combine them
* Did not find much---composite tends to blend away to normality.
-->

##

Speaking of criminality...<BR>
_Can we say anything about the U.S. Congress?_

![](./background/figures/congressPersons.png)
__Maybe he should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__

<!--
Notes:
-->

##

__Image mapping & biology: 1917__
<BR><BR>
D''Arcy Thompson: _Comparison of related forms_

![](./figures/dthompson.png)

<!--
Notes:
* Book: On Growth and Form
* Descriptive not susceptible to hypothesis testing
* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
-->

##

__Image mapping & biology: Current__
<BR><BR>
_Look where we are now!_
<BR><BR>
![](./background/figures/r16xr85.png)

<!--
Notes:
* Book: On Growth and Form
* Descriptive not susceptible to hypothesis testing
* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
-->

##

__ANTs family tree__

![](./figures/lineage.jpg)

<!--
References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
-->

##

__Initial scope__

![](./figures/ants_initial_scope.png)

<!--
Notes:
* Brian work with Murray Grossman
* First registration paper
  - WBIR submission
  - FEM registraiton using B-spline basis functions.
  - "yeah, that registration is not that good---Jim would not like it."
-->

##

__Diffeomorphisms__:plausible physical modeling

<div align="center"><img src="./figures/sillyputty.png" frameborder="0"></img></div>

"differentiable map with differentiable inverse"

##

__Fine-grained and flexible maps__

![](./figures/highresdiffeos.jpg)

<!--
... to correct a misconception about diffeomorphisms ...
-->

##

 __Diffeomorphisms__: image parameterization in a metric space

![](./figures/shape_appearance.png)

##

__General purpose library for multivariate image registration, segmentation & statistical analysis tools__

* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.

* Generic mathematical methods that are tunable for
application specific domains.

* <span style="color:red;">no free lunch</span>: <span style="color:black;">_An algorithm must use prior knowledge about a problem to do well on that problem._</span>

<!--
* Deep testing on multiple platforms ... osx, linux, windows.

* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )
-->

## Still quite a bit to do

##

__On documentation__

![](figures/Chainsaw.jpg)

<!--
Notes:
* ANTs documentation is only slightly better than what is shown here.
-->

##

Developers can be blind to doc deficiencies while users are blind to what we provide!

![](figures/blindmen.jpg)

### 2015-05-17 background/people.Rmd
ENH:  More material.

# Founding developers

##

![](./figures/brian_and_edie_sedgwick.jpg)

<!--
Notes:
* Where is this from?
* Brain--visionary,brilliant.
* New college in Florida --- degree in Physics and Literature(?)
* Went to Siemens and got kicked out, fortunately, by ???  "You need to get a doctorate."
* Jim Gee first graduate student
* Jim wanted to work on FEM registration
  - side tangent:  Jim''s notebooks of FEM registration code
-->

##

![](./background/figures/brucelee.png)

<!--
NOtes:
* Not much to say
  - did graduate work at the University of Virginia (hyper. gas lungs)
  - Washington University in St. Louis (cardiac)
  - actually bombed interview with Siemens
  - 2004: Jim offered a job without an interview (long term collaboration)
  - wrote graph cuts for ITK in a month
-->

##
<BR><BR>

<div align="center"><img width="1800" src="./figures/brian_and_nick.png" frameborder="0"></img></div>

<!--
NOtes:
* Worked together for almost 10 years
* have learned tons
* have written quite a bit of code together
-->

##

![](./figures/antscollab.jpg)

$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...

<!--
NOtes:
* However, it is not just us
* Other people have done quite a bit
* and others who are not shown such as Arman
-->

### 2015-05-17 competitions/competitions.Rmd
ENH:  More material.

@@
 
-## <span style="color:green;">Competitions</span>
+##
+
+<span style="color:green;">__Competitions__</span>
 
@@
 
-## <span style="color:green;">Klein 2009</span>
+##
+
+<span style="color:green;">__Klein 2009__</span>
 
@@
 
-## <span style="color:green;"> Results</span>
+##
+
+<span style="color:green;">__Results__</span>
 
@@
 
-## <span style="color:green;">Multi-Atlas 2012</span>
+##
+
+<span style="color:green;">__Multi-Atlas 2012__</span>
 
@@
 
-## <span style="color:green;">Results</span>
+##
+
+<span style="color:green;">__Results__</span>
 
@@
 
-## <span style="color:green;">SATA 2013</span>
+##
+
+<span style="color:green;">SATA 2013</span>
 
@@
 
-## <span style="color:green;">BRATS 2013</span>
+##
+
+<span style="color:green;">__BRATS 2013__</span>
 
@@
 
-## <span style="color:green;">STACOM 2014</span>
+##
+
+<span style="color:green;">__STACOM 2014__</span>
 

### 2015-05-17 evaluation/antsvfreesurfer2_extra.Rmd
ENH:  More material.

@@
 
+## And currently brewing on the UVa cluster...
+
+_Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_
+
+##
+
+* ``itkAdaptiveNonLocalMeansDenoisingImageFilter.h``
+
+* ``itkAdaptiveNonLocalMeansDenoisingImageFilter.hxx``
+
+~~~~~~~~~~~~~~~~~~~~~~
+$ DenoiseImage
+
+COMMAND:
+     DenoiseImage
+          Denoise an image using a spatially adaptive filter originally described in J. V.
+          Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive
+          Non-Local Means Denoising of MR Images With Spatially Varying Noise Levels,
+          Journal of Magnetic Resonance Imaging, 31:192-203, June 2010.
+
+OPTIONS:
+     -d, --image-dimensionality 2/3/4
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, the program tries to infer the dimensionality from the input
+          image.
+
+     -i, --input-image inputImageFilename
+          A scalar image is expected as input for noise correction.
+
+     -n, --noise-model (Rician)/Gaussian
+          Employ a Rician or Gaussian noise model.
+
+     -s, --shrink-factor (1)/2/3/...
+          Running noise correction on large images can be time consuming. To lessen
+          computation time, the input image can be resampled. The shrink factor, specified
+          as a single integer, describes this resampling. Shrink factor = 1 is the
+          default.
+
+     -o, --output correctedImage
+                  [correctedImage,<noiseImage>]
+          The output consists of the noise corrected version of the input image.
+          Optionally, one can also output the estimated noise image.
+
+     --version
+          Get Version Information.
+
+     -v, --verbose (0)/1
+          Verbose output.
+
+     -h
+          Print the help menu (short version).
+
+     --help
+          Print the help menu.
+~~~~~~~~~~~~~~~~~~~~~~
+
 # But the best part is ...

### 2015-05-17 longitudinal/longitudinal2.Rmd
ENH:  More material.

@@
 ![](./longitudinal/figures/longitudinalPipeline.png)
+
+##
+
+``antsLongitudinalCorticalThickness.sh``
+
+~~~~~~~~~~~~~~~~~~~~
+$ antsLongitudinalCorticalThickness.sh
+
+antsLongitudinalCorticalThickness.sh performs a longitudinal cortical thickness estimation.  The following steps
+are performed:
+  1. Create a single-subject template (SST) from all the data
+  2. Create priors for the SST
+     a. Run the SST through the individual cortical thickness pipeline.
+     b. The brain extraction SST prior is created by smoothing the brain extraction
+        mask created during 2a.
+     c. If labeled atlases are not provided, we smooth the posteriors from 2a to create
+        the SST segmentation priors, otherwise we use antsMalfLabeling to create a set of
+        posteriors (https://github.com/ntustison/antsCookTemplatePriorsExample).
+  3. Using the SST + priors, we run each subject through the antsCorticalThickness
+     pipeline.
+
+Usage:
+
+antsLongitudinalCorticalThickness.sh -d imageDimension
+              -e brainTemplate
+              -m brainExtractionProbabilityMask
+              -p brainSegmentationPriors
+              <OPTARGS>
+              -o outputPrefix
+              ${anatomicalImages[@]}
+
+Example:
+
+  bash /Users/ntustison/Pkg/ANTs/bin/bin/antsLongitudinalCorticalThickness.sh -d 3 -e brainWithSkullTemplate.nii.gz -m brainPrior.nii.gz -p segmentationPriors%d.nii.gz -o output ${anatomicalImages[@]}
+
+Required arguments:
+
+     -d:  Image dimension                       2 or 3 (for 2- or 3-dimensional image)
+     -e:  Brain template                        Anatomical *intensity* template (possibly created using a population
+                                                data set with buildtemplateparallel.sh in ANTs).  This template is
+                                                *not* skull-stripped.
+     -m:  Brain extraction probability mask     Brain *probability* mask created using e.g. LPBA40 labels which
+                                                have brain masks defined, and warped to anatomical template and
+                                                averaged resulting in a probability image.
+     -p:  Brain segmentation priors             Tissue *probability* priors corresponding to the image specified
+                                                with the -e option.  Specified using c-style formatting, e.g.
+                                                -p labelsPriors%02d.nii.gz.  We assume that the first four priors
+                                                are ordered as follows
+                                                  1:  csf
+                                                  2:  cortical gm
+                                                  3:  wm
+                                                  4:  deep gm
+     -o:  Output prefix                         The following subdirectory and images are created for the single
+                                                subject template
+                                                  * ${OUTPUT_PREFIX}SingleSubjectTemplate/
+                                                  * ${OUTPUT_PREFIX}SingleSubjectTemplate/T_template*.nii.gz
+
+     anatomical images                          Set of multimodal input data assumed to be specified ordered as
+                                                follows:
+                                                  ${time1_modality1} ${time1_modality2} ... ${time1_modalityN} \
+                                                  ${time2_modality1} ${time2_modality2} ...
+                                                  .
+                                                  .
+                                                  .
+                                                  ${timeN_modality1} ...
+
+						A single modality is expected by default, in which case the input images
+						are simply ordered by time:
+
+						  ${time1_modality1} ${time2_modality1} ... ${timeN_modality1}
+
+						If there are multiple modalities, use the -k option to specify how many.
+
+Optional arguments:
+
+     -s:  image file suffix                     Any of the standard ITK IO formats e.g. nrrd, nii.gz (default), mhd
+     -c:  control type                          Control for parallel computation (default 0):
+                                                  0 = run serially
+                                                  1 = SGE qsub
+                                                  2 = use PEXEC (localhost)
+                                                  3 = Apple XGrid
+                                                  4 = PBS qsub
+     -t:  template for t1 registration          Anatomical *intensity* template (assumed to be skull-stripped).  A common
+                                                use case would be where this would be the same template as specified in the
+                                                -e option which is not skull stripped.
+     -a:                                        Atlases (assumed to be skull-stripped) used to cook template priors.  If atlases
+                                                aren't used then we simply smooth the single-subject template posteriors after
+                                                passing through antsCorticalThickness.sh. Example:
+
+ 						  -a atlas1.nii.gz -a atlas2.nii.gz ... -a atlasN.nii.gz
+
+     -l:                                        Labels associated with each atlas, in the same order as they are specified
+						with the -a option. The number of labels in each image is assumed to be equal
+                                                to the number of priors.
+     -f:  extraction registration mask          Mask (defined in the template space) used during registration
+                                                for brain extraction.
+     -j:  number of cpu cores                   Number of cpu cores to use locally for pexec option (default 2; requires "-c 2")
+     -k:  number of modalities                  Number of modalities used to construct the template (default 1):  For example,
+                                                if one wanted to use multiple modalities consisting of T1, T2, and FA
+                                                components ("-k 3").
+     -n:  use SST cortical thickness prior      If set to '1', the cortical thickness map from the single-subject template is used
+                                                as a prior constraint for each of the individual calls to antsCorticalThickness.sh
+                                                (default = 0).
+     -g:  use floating-point precision          Use floating point precision in registrations (default = 0)
+     -v:  Atropos segmentation weight (SST)     Atropos spatial prior *probability* weight for the segmentation for the single
+                                                subject template (default = 0.25)
+     -w:  Atropos segmentation weight (Indiv.)  Atropos spatial prior *probability* weight for the segmentation for the individual
+                                                time points (default = 0.5)
+     -q:  Use quick registration parameters     If = 1, use antsRegistrationSyNQuick.sh as the basis for registration
+                                                during brain extraction, brain segmentation, and (optional) normalization
+                                                to a template.  Otherwise use antsRegistrationSyN.sh (default = 0).
+     -r:  rigid alignment to SST                This option dictates if the individual subjects are registered to the single
+                                                subject template before running through antsCorticalThickness.  This potentially
+                                                reduces bias caused by subject orientation and voxel spacing (default = 0).
+     -z:  Test / debug mode                     If > 0, runs a faster version of the script. Only for testing. Implies -u 0.
+                                                Requires single thread computation for complete reproducibility.
+~~~~~~~~~~~~~~~~~~~~

### 2015-05-17 papers/papers.Rmd
ENH:  More material.

# Major papers

##

<BR><BR>
<span style="color:red;">_"Papers are just advertisements for the science."_</red>
<BR>

##

__Symmetric Normalization:__  (_SyN_)

$\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt$

$+ \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2$

![](./papers/figures/fishes.png)

<!--
NOtes:
* Previously discussed Brians work
* The variant most widely used
-->

##

__Beyond original SyN__

![](./papers/figures/Frontiers_ITK.png)

![](./papers/figures/Frontiers_BSplineSyN.png)

##

```antsRegistration```
<BR><BR>

~~~~~~~~~~~~~~~~~~~~~~~
$ antsRegistration --help

COMMAND:
     antsRegistration
          This program is a user-level registration application meant to utilize
          ITKv4-only classes. The user can specify any number of "stages" where a stage
          consists of a transform; an image metric; and iterations, shrink factors, and
          smoothing sigmas for each level.Note that dimensionality, metric, transform,
          output, convergence, shrink-factors and smoothing-sigmas parameters are
          mandatory.

OPTIONS:
     --version
          Get Version Information.

     -d, --dimensionality 2/3
          This option forces the image to be treated as a specified-dimensional image. If
          not specified, we try to infer the dimensionality from the input image.

     -o, --output outputTransformPrefix
                  [outputTransformPrefix,<outputWarpedImage>,<outputInverseWarpedImage>]
          Specify the output transform prefix (output format is .nii.gz ). Optionally, one
          can choose to warp the moving image to the fixed space and, if the inverse
          transform exists, one can also output the warped fixed image. Note that only the
          images specified in the first metric call are warped. Use antsApplyTransforms to
          warp other images using the resultant transform(s).

     -j, --save-state saveSateAsTransform
          Specify the output file for the current state of the registration. The state
          file is written to an hdf5 composite file. It is specially usefull if we want to
          save the current state of a SyN registration to the disk, so we can load and
          restore that later to continue the next registration process directly started
          from the last saved state. The output file of this flag is the same as the
          write-composite-transform, unless the last transform is a SyN transform. In that
          case, the inverse displacement field of the SyN transform is also added to the
          output composite transform. Again notice that this file cannot be treated as a
          transform, and restore-state option must be used to load the written file by
          this flag.

     -k, --restore-state restoreStateAsATransform
          Specify the initial state of the registration which get immediately used to
          directly initialize the registration process. The flag is mutually exclusive
          with other intialization flags.If this flag is used, none of the
          initial-moving-transform and initial-fixed-transform cannot be used.

     -a, --write-composite-transform 1/(0)
          Boolean specifying whether or not the composite transform (and its inverse, if
          it exists) should be written to an hdf5 composite file. This is false by default
          so that only the transform for each stage is written to file.
          <VALUES>: 0

     -p, --print-similarity-measure-interval <unsignedIntegerValue>
          Prints out the CC similarity metric measure between the full-size input fixed
          and the transformed moving images at each iteration a value of 0 (the default)
          indicates that the full scale computation should not take placeany value greater
          than 0 represents the interval of full scale metric computation.
          <VALUES>: 0

     -v, --write-interval-volumes <unsignedIntegerValue>
          Writes out the output volume at each iteration. It helps to present the
          registration process as a short movie a value of 0 (the default) indicates that
          this option should not take placeany value greater than 0 represents the
          interval between the iterations which outputs are written to the disk.
          <VALUES>: 0

     -z, --collapse-output-transforms (1)/0
          Collapse output transforms. Specifically, enabling this option combines all
          adjacent transforms wherepossible. All adjacent linear transforms are written to
          disk in the forman itk affine transform (called xxxGenericAffine.mat).
          Similarly, all adjacent displacement field transforms are combined when written
          to disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available)).Also, an
          output composite transform including the collapsed transforms is written to the
          disk (called outputCollapsed(Inverse)Composite).
          <VALUES>: 1

     -i, --initialize-transforms-per-stage (1)/0
          Initialize linear transforms from the previous stage. By enabling this option,
          the current linear stage transform is directly intialized from the previous
          stage's linear transform; this allows multiple linear stages to be run where
          each stage directly updates the estimated linear transform from the previous
          stage. (e.g. Translation -> Rigid -> Affine).
          <VALUES>: 0

     -n, --interpolation Linear
                         NearestNeighbor
                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]
                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]
                         BSpline[<order=3>]
                         CosineWindowedSinc
                         WelchWindowedSinc
                         HammingWindowedSinc
                         LanczosWindowedSinc
          Several interpolation options are available in ITK. These have all been made
          available. Currently the interpolator choice is only used to warp (and possibly
          inverse warp) the final output image(s).

     -g, --restrict-deformation PxQxR
          This option allows the user to restrict the optimization of the displacement
          field, translation, rigid or affine transform on a per-component basis. For
          example, if one wants to limit the deformation or rotation of 3-D volume to the
          first two dimensions, this is possible by specifying a weight vector of '1x1x0'
          for a deformation field or '1x1x0x1x1x0' for a rigid
          transformation.Low-dimensional restriction only works if there are no preceding
          transformations.

     -q, --initial-fixed-transform initialTransform
                                   [initialTransform,<useInverse>]
                                   [fixedImage,movingImage,initializationFeature]
          Specify the initial fixed transform(s) which get immediately incorporated into
          the composite transform. The order of the transforms is stack-esque in that the
          last transform specified on the command line is the first to be applied. In
          addition to initialization with ITK transforms, the user can perform an initial
          translation alignment by specifying the fixed and moving images and selecting an
          initialization feature. These features include using the geometric center of the
          images (=0), the image intensities (=1), or the origin of the images (=2).

     -r, --initial-moving-transform initialTransform
                                    [initialTransform,<useInverse>]
                                    [fixedImage,movingImage,initializationFeature]
          Specify the initial moving transform(s) which get immediately incorporated into
          the composite transform. The order of the transforms is stack-esque in that the
          last transform specified on the command line is the first to be applied. In
          addition to initialization with ITK transforms, the user can perform an initial
          translation alignment by specifying the fixed and moving images and selecting an
          initialization feature. These features include using the geometric center of the
          images (=0), the image intensities (=1), or the origin of the images (=2).

     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]
                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]
                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]
                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]
          These image metrics are available--- CC: ANTS neighborhood cross correlation,
          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global
          Correlation. The "metricWeight" variable is used to modulate the per stage
          weighting of the metrics. The metrics can also employ a sampling strategy
          defined by a sampling percentage. The sampling strategy defaults to 'None' (aka
          a dense sampling of one sample per voxel), otherwise it defines a point set over
          which to optimize the metric. The point set can be on a regular lattice or a
          random lattice of points slightly perturbed to minimize aliasing artifacts.
          samplingPercentage defines the fraction of points to select from the domain. In
          addition, three point set metrics are available: Euclidean (ICP), Point-set
          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).

     -t, --transform Rigid[gradientStep]
                     Affine[gradientStep]
                     CompositeAffine[gradientStep]
                     Similarity[gradientStep]
                     Translation[gradientStep]
                     BSpline[gradientStep,meshSizeAtBaseLevel]
                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]
                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]
                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]
                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]
          Several transform options are available. The gradientStep or learningRate
          characterizes the gradient descent optimization and is scaled appropriately for
          each transform using the shift scales estimator. Subsequent parameters are
          transform-specific and can be determined from the usage. For the B-spline
          transforms one can also specify the smoothing in terms of spline distance (i.e.
          knot spacing).

     -c, --convergence MxNxO
                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]
          Convergence is determined from the number of iterations per level and is
          determined by fitting a line to the normalized energy profile of the last N
          iterations (where N is specified by the window size) and determining the slope
          which is then compared with the convergence threshold.

     -s, --smoothing-sigmas MxNxO...
          Specify the sigma of gaussian smoothing at each level. Units are given in terms
          of voxels ('vox') or physical spacing ('mm'). Example usage is '4x2x1mm' and
          '4x2x1vox' where no units implies voxel spacing.

     -f, --shrink-factors MxNxO...
          Specify the shrink factor for the virtual domain (typically the fixed image) at
          each level.

     -u, --use-histogram-matching
          Histogram match the images before registration.

     -l, --use-estimate-learning-rate-once
          turn on the option that lets you estimate the learning rate step size only at
          the beginning of each level. * useful as a second stage of fine-scale
          registration.

     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]
          Winsorize data based on specified quantiles.

     -x, --masks [fixedImageMask,movingImageMask]
          Image masks to limit voxels considered by the metric.

     --float
          Use 'float' instead of 'double' for computations.
          <VALUES>: 0

     -v, --verbose (0)/1
          Verbose output.

     -h
          Print the help menu (short version).

     --help
          Print the help menu. Will also print values used on the current command line
          call.
~~~~~~~~~~~~~~~~~~~~~~~

##

__Template building__

##

![](./papers/figures/template0.jpg)

##

![](./papers/figures/template1.jpg)

##

![](./papers/figures/template3.jpg)

##

![](./papers/figures/template4.jpg)

##

![](./papers/figures/template5.jpg)

##

```antsMultivariateTemplateConstruction2.sh```

<BR>

~~~~~~~~~~~~~~~~~~~~~~
$ antsMultivariateTemplateConstruction2.sh

Usage:

antsMultivariateTemplateConstruction2.sh -d ImageDimension -o OutputPrefix <other options> <images>

Compulsory arguments (minimal command line requires SGE/PBS cluster, otherwise use -c and
  -j options):

     -d:  ImageDimension: 2 or 3 (for 2 or 3 dimensional registration of single volume)
   ImageDimension: 4 (for template generation of time-series data)

     -o:  OutputPrefix; A prefix that is prepended to all output files.

<images>  List of images in the current directory, eg *_t1.nii.gz. Should be at the end
          of the command.  Optionally, one can specify a .csv or .txt file where each
          line is the location of the input image.  One can also specify more than
          one file for each image for multi-modal template construction (e.g. t1 and t2).
          For the multi-modal case, the templates will be consecutively numbered (e.g.
          template0.nii.gz, template1.nii.gz, ...).

NB: All images to be added to the template should be in the same directory, and this
    script should be invoked from that directory.

Optional arguments:

     -a   image statistic used to summarize images (default 1)
          0 = mean
          1 = mean of normalized intensities
          2 = median

     -b:  Backup images and results from all iterations (default = 0):  Boolean to save
          the transform files, bias corrected, and warped images for each iteration.

     -c:  Control for parallel computation (default 0):
          0 = run serially
          1 = SGE qsub
          2 = use PEXEC (localhost)
          3 = Apple XGrid
          4 = PBS qsub

     -e   use single precision ( default 1 )

     -g:  Gradient step size (default 0.25): smaller in magnitude results in more
          cautious steps.

     -i:  Iteration limit (default 4): iterations of the template construction
          (Iteration limit)*NumImages registrations.

     -j:  Number of cpu cores to use locally for pexec option (default 2; requires "-c 2")

     -k:  Number of modalities used to construct the template (default 1):  For example,
          if one wanted to create a multimodal template consisting of T1,T2,and FA
          components ("-k 3").

     -w:  Modality weights used in the similarity metric (default = 1): specified as
          e.g. 1x0.5x0.75.

     -q:  Max iterations for each pairwise registration (default = 100x100x70x20):
          specified in the form ...xJxKxL where
            J = max iterations at coarsest resolution (here, reduced by power of 2^2)
            K = middle resolution iterations (here, reduced by power of 2)
            L = fine resolution iteratioxns (here, full resolution).
          Finer resolutions take much more time per iteration than coarser resolutions.

     -f:  Shrink factors (default = 6x4x2x1):  Also in the same form as -q max iterations.  
          Needs to have the same number of components.

     -s:  Smoothing factors (default = 3x2x1x0):  Also in the same form as -q max
          iterations.  Needs to have the same number of components.

     -n:  N4BiasFieldCorrection of moving image: 0 == off, 1 == on (default 1).

     -p:  Commands to prepend to job scripts (e.g., change into appropriate directory, set
          paths, etc)

     -r:  Do rigid-body registration of inputs before creating template (default 0):
          0 == off 1 == on. Only useful when you do not have an initial template

     -l:  Use linear image registration stages during the pairwise (template/subject)
          deformable registration.  Otherwise, registration is limited to SyN or
          B-spline SyN (see '-t' option).  This is '1' by default.

     -m:  Type of similarity metric used for registration (default = CC):  Options are
            CC = cross-correlation
            MI = mutual information
            MSQ = mean square difference
            DEMONS = demon's metric
          A similarity metric per modality can be specified.  If the CC metric is chosen,
          one can also specify the radius in brackets, e.g. '-m CC[4]'.

     -t:  Type of transformation model used for registration (default = SyN):  Options are
            SyN = Greedy SyN
            BSplineSyN = Greedy B-spline SyN
            TimeVaryingVelocityField = Time-varying velocity field
            TimeVaryingBSplineVelocityField = Time-varying B-spline velocity field

     -u:  Walltime (default = 20:00:00):  Option for PBS qsub specifying requested time
          per pairwise registration.

     -v:  Memory limit (default = 8gb):  Option for PBS qsub specifying requested memory
          per pairwise registration.

     -x:  XGrid arguments (e.g., -x "-p password -h controlhost")

     -y:  Update the template with the full affine transform (default 1). If 0, the rigid
          component of the affine transform will not be used to update the template. If your
          template drifts in translation or orientation try -y 0.

     -z:  Use this this volume as the target of all inputs. When not used, the script
          will create an unbiased starting point by averaging all inputs. Use the full
          path.
          For multiple modalities, specify -z modality1.nii.gz -z modality2.nii.gz ...
          in the same modality order as the input images.

Example:

antsMultivariateTemplateConstruction2.sh -d 3 -i 3 -k 1 -f 4x2x1 -s 2x1x0vox -q 30x20x4 -t SyN  -m CC -c 0 -o MY sub*avg.nii.gz

Multimodal example:

antsMultivariateTemplateConstruction2.sh -d 3 -i 3 -k 2 -f 4x2x1 -s 2x1x0vox -q 30x20x4 -t SyN -z t1.nii.gz -z t2.nii.gz  -m CC -c 0 -o MY templateInput.csv

where templateInput.csv contains

subjectA_t1.nii.gz,subjectA_t2.nii.gz
subjectB_t1.nii.gz,subjectB_t2.nii.gz
...

--------------------------------------------------------------------------------------
ANTS was created by:
--------------------------------------------------------------------------------------
Brian B. Avants, Nick Tustison and Gang Song
Penn Image Computing And Science Laboratory
University of Pennsylvania

Please reference http://www.ncbi.nlm.nih.gov/pubmed/20851191 when employing this script
in your studies. A reproducible evaluation of ANTs similarity metric performance in
brain image registration:

* Avants BB, Tustison NJ, Song G, Cook PA, Klein A, Gee JC. Neuroimage, 2011.

Also see http://www.ncbi.nlm.nih.gov/pubmed/19818860 for more details.

The script has been updated and improved since this publication.

--------------------------------------------------------------------------------------
Script by Nick Tustison
--------------------------------------------------------------------------------------
Apple XGrid support by Craig Stark
--------------------------------------------------------------------------------------
~~~~~~~~~~~~~~~~~~~~~~

##

__Nonparametric nonuniform intensity normalization (N3)__

* Developed at the Montreal Neurological Institute (John Sled, 1998)

* Part of the standard preprocessing protocol in large scale projects such as ADNI

* The traditional de facto standard in MRI bias correction
    + good performance
    + *public availability*

* Public availability --- set of perl scripts coordinating various C++ programs

* "*Let's incorporate N3 into ANTs!*"

##

__N3 adoption issues__

![](./tools/n4/figures/whyN4.png)

<!-- regular html comment

<div align="center"><img src="./tools/n4/figures/whyN4.png" frameborder="0"></img></div>

-->

##

<!--
__N3 $\rightarrow$ N4<sup>*</sup>__

<p align = "middle"><small><sup>*</sup><u>N</u>ick's N3</small></p>
-->

__N4__

* comparative [evaluation](http://www.ncbi.nlm.nih.gov/pubmed/20378467)

* smaller spline distances (useful for higher magnet strengths)

* multiresolution

* weighted regional mask (used in [`antsAtroposN4.sh`](https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh))

* faster execution times

* _publicly available_

##

```N4BiasFieldCorrection```

<BR>

~~~~~~~~~~~~~~~~~~~~~~~~~~~
$ N4BiasFieldCorrection --help

COMMAND:
     N4BiasFieldCorrection
          N4 is a variant of the popular N3 (nonparameteric nonuniform normalization)
          retrospective bias correction algorithm. Based on the assumption that the
          corruption of the low frequency bias field can be modeled as a convolution of
          the intensity histogram by a Gaussian, the basic algorithmic protocol is to
          iterate between deconvolving the intensity histogram by a Gaussian, remapping
          the intensities, and then spatially smoothing this result by a B-spline modeling
          of the bias field itself. The modifications from and improvements obtained over
          the original N3 algorithm are described in the following paper: N. Tustison et
          al., N4ITK: Improved N3 Bias Correction, IEEE Transactions on Medical Imaging,
          29(6):1310-1320, June 2010.

OPTIONS:
     -d, --image-dimensionality 2/3/4
          This option forces the image to be treated as a specified-dimensional image. If
          not specified, N4 tries to infer the dimensionality from the input image.

     -i, --input-image inputImageFilename
          A scalar image is expected as input for bias correction. Since N4 log transforms
          the intensities, negative values or values close to zero should be processed
          prior to correction.

     -x, --mask-image maskImageFilename
          If a mask image is specified, the final bias correction is only performed in the
          mask region. If a weight image is not specified, only intensity values inside
          the masked region are used during the execution of the algorithm. If a weight
          image is specified, only the non-zero weights are used in the execution of the
          algorithm although the mask region defines where bias correction is performed in
          the final output. Otherwise bias correction occurs over the entire image domain.
          See also the option description for the weight image.

     -r, --rescale-intensities 0/(1)
          At each iteration, a new intensity mapping is calculated and applied but there
          is nothing which constrains the new intensity range to be within certain values.
          The result is that the range can "drift" from the original at each iteration.
          This option rescales to the [min,max] range of the original image intensities
          within the user-specified mask.

     -w, --weight-image weightImageFilename
          The weight image allows the user to perform a relative weighting of specific
          voxels during the B-spline fitting. For example, some studies have shown that N3
          performed on white matter segmentations improves performance. If one has a
          spatial probability map of the white matter, one can use this map to weight the
          b-spline fitting towards those voxels which are more probabilistically
          classified as white matter. See also the option description for the mask image.

     -s, --shrink-factor 1/2/3/4/...
          Running N4 on large images can be time consuming. To lessen computation time,
          the input image can be resampled. The shrink factor, specified as a single
          integer, describes this resampling. Shrink factors <= 4 are commonly used.

     -c, --convergence [<numberOfIterations=50x50x50x50>,<convergenceThreshold=0.0>]
          Convergence is determined by calculating the coefficient of variation between
          subsequent iterations. When this value is less than the specified threshold from
          the previous iteration or the maximum number of iterations is exceeded the
          program terminates. Multiple resolutions can be specified by using 'x' between
          the number of iterations at each resolution, e.g. 100x50x50.

     -b, --bspline-fitting [splineDistance,<splineOrder=3>]
                           [initialMeshResolution,<splineOrder=3>]
          These options describe the b-spline fitting parameters. The initial b-spline
          mesh at the coarsest resolution is specified either as the number of elements in
          each dimension, e.g. 2x2x3 for 3-D images, or it can be specified as a single
          scalar parameter which describes the isotropic sizing of the mesh elements. The
          latter option is typically preferred. For each subsequent level, the spline
          distance decreases in half, or equivalently, the number of mesh elements doubles
          Cubic splines (order = 3) are typically used.

     -t, --histogram-sharpening [<FWHM=0.15>,<wienerNoise=0.01>,<numberOfHistogramBins=200>]
          These options describe the histogram sharpening parameters, i.e. the
          deconvolution step parameters described in the original N3 algorithm. The
          default values have been shown to work fairly well.

     -o, --output correctedImage
                  [correctedImage,<biasField>]
          The output consists of the bias corrected version of the input image.
          Optionally, one can also output the estimated bias field.

     --version
          Get Version Information.

     -v, --verbose (0)/1
          Verbose output.

     -h
          Print the help menu (short version).

     --help
          Print the help menu.
          <VALUES>: 1
~~~~~~~~~~~~~~~~~~~~~~~~~~~

##

![](./papers/figures/Atropos_deGoya.jpg)

"20+ years of development.  <br>_Show me the code!_"

<p align = "right"><small>Brian, MICCAI workshop</small></p>

<!--
Notes:
* Can we use Suyash's code?
* What about graph cuts?
-->

##

__Atropos__

![](./tools/atropos/figures/atropos.png)

<!-- regular html comment

<div align="center"><img src="./tools/n4/figures/whyN4.png" frameborder="0"></img></div>

-->

##

__Algorithmic workflow__<br>(Atropos + N4 $\rightarrow$ `antsAtroposN4.sh`)

![](./tools/atropos/figures/atroposFlow.png)

##

```Atropos```

<BR>

~~~~~~~~~~~~~~~~~~~~~~~~~~~
$ Atropos --help

COMMAND:
     Atropos
          A finite mixture modeling (FMM) segmentation approach with possibilities for
          specifying prior constraints. These prior constraints include the specification
          of a prior label image, prior probability images (one for each class), and/or an
          MRF prior to enforce spatial smoothing of the labels. Similar algorithms include
          FAST and SPM. Reference: Avants BB, Tustison NJ, Wu J, Cook PA, Gee JC. An open
          source multivariate framework for n-tissue segmentation with evaluation on
          public data. Neuroinformatics. 2011 Dec;9(4):381-400.

OPTIONS:
     -d, --image-dimensionality 2/3/4
          This option forces the image to be treated as a specified-dimensional image. If
          not specified, Atropos tries to infer the dimensionality from the first input
          image.

     -a, --intensity-image [intensityImage,<adaptiveSmoothingWeight>]
          One or more scalar images is specified for segmentation using the
          -a/--intensity-image option. For segmentation scenarios with no prior
          information, the first scalar image encountered on the command line is used to
          order labelings such that the class with the smallest intensity signature is
          class '1' through class 'N' which represents the voxels with the largest
          intensity values. The optional adaptive smoothing weight parameter is applicable
          only when using prior label or probability images. This scalar parameter is to
          be specified between [0,1] which smooths each labeled region separately and
          modulates the intensity measurement at each voxel in each intensity image
          between the original intensity and its smoothed counterpart. The smoothness
          parameters are governed by the -b/--bspline option.

     -b, --bspline [<numberOfLevels=6>,<initialMeshResolution=1x1x...>,<splineOrder=3>]
          If the adaptive smoothing weights are > 0, the intensity images are smoothed in
          calculating the likelihood values. This is to account for subtle intensity
          differences across the same tissue regions.

     -i, --initialization Random[numberOfClasses]
                          Otsu[numberOfTissueClasses]
                          KMeans[numberOfTissueClasses,<clusterCenters(in ascending order and for first intensity image only)>]
                          PriorProbabilityImages[numberOfTissueClasses,fileSeriesFormat(index=1 to numberOfClasses) or vectorImage,priorWeighting,<priorProbabilityThreshold>]
                          PriorLabelImage[numberOfTissueClasses,labelImage,priorWeighting]
          To initialize the FMM parameters, one of the following options must be
          specified. If one does not have prior label or probability images we recommend
          using kmeans as it is typically faster than otsu and can be used with
          multivariate initialization. However, since a Euclidean distance on the inter
          cluster distances is used, one might have to appropriately scale the additional
          input images. Random initialization is meant purely for intellectual curiosity.
          The prior weighting (specified in the range [0,1]) is used to modulate the
          calculation of the posterior probabilities between the likelihood*mrfprior and
          the likelihood*mrfprior*prior. For specifying many prior probability images for
          a multi-label segmentation, we offer a minimize usage option (see -m). With that
          option one can specify a prior probability threshold in which only those pixels
          exceeding that threshold are stored in memory.

     -s, --partial-volume-label-set label1xlabel2xlabel3
          The partial volume estimation option allows one to modelmixtures of classes
          within single voxels. Atropos currently allows the user to model two class
          mixtures per partial volume class. The user specifies a set of class labels per
          partial volume class requested. For example, suppose the user was performing a
          classic 3-tissue segmentation (csf, gm, wm) using kmeans initialization. Suppose
          the user also wanted to model the partial voluming effects between csf/gm and
          gm/wm. The user would specify it using -i kmeans[3] and -s 1x2 -s 2x3. So, for
          this example, there would be 3 tissue classes and 2 partial volume classes.
          Optionally,the user can limit partial volume handling to mrf considerations only
          whereby the output would only be the three tissues.

     --use-partial-volume-likelihoods 1/(0)
                                      true/(false)
          The user can specify whether or not to use the partial volume likelihoods, in
          which case the partial volume class is considered separate from the tissue
          classes. Alternatively, one can use the MRF only to handle partial volume in
          which case, partial volume voxels are not considered as separate classes.

     -p, --posterior-formulation Socrates[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
                                 Plato[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
                                 Aristotle[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
                                 Sigmoid[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]]
          Different posterior probability formulations are possible as are different
          update options. To guarantee theoretical convergence properties, a proper
          formulation of the well-known iterated conditional modes (ICM) uses an
          asynchronous update step modulated by a specified annealing temperature. If one
          sets the AnnealingTemperature > 1 in the posterior formulation a traditional
          code set for a proper ICM update will be created. Otherwise, a synchronous
          update step will take place at each iteration. The annealing temperature, T,
          converts the posteriorProbability to posteriorProbability^(1/T) over the course
          of optimization.

     -x, --mask-image maskImageFilename
          The image mask (which is required) defines the region which is to be labeled by
          the Atropos algorithm.

     -c, --convergence numberOfIterations
                       [<numberOfIterations=5>,<convergenceThreshold=0.001>]
          Convergence is determined by calculating the mean maximum posterior probability
          over the region of interest at each iteration. When this value decreases or
          increases less than the specified threshold from the previous iteration or the
          maximum number of iterations is exceeded the program terminates.

     -k, --likelihood-model Gaussian
                            HistogramParzenWindows[<sigma=1.0>,<numberOfBins=32>]
                            ManifoldParzenWindows[<pointSetSigma=1.0>,<evaluationKNeighborhood=50>,<CovarianceKNeighborhood=0>,<kernelSigma=0>]
                            JointShapeAndOrientationProbability[<shapeSigma=1.0>,<numberOfShapeBins=64>, <orientationSigma=1.0>, <numberOfOrientationBins=32>]
                            LogEuclideanGaussian
          Both parametric and non-parametric options exist in Atropos. The Gaussian
          parametric option is commonly used (e.g. SPM & FAST) where the mean and standard
          deviation for the Gaussian of each class is calculated at each iteration. Other
          groups use non-parametric approaches exemplified by option 2. We recommend using
          options 1 or 2 as they are fairly standard and the default parameters work
          adequately.

     -m, --mrf [<smoothingFactor=0.3>,<radius=1x1x...>]
               [<mrfCoefficientImage>,<radius=1x1x...>]
          Markov random field (MRF) theory provides a general framework for enforcing
          spatially contextual constraints on the segmentation solution. The default
          smoothing factor of 0.3 provides a moderate amount of smoothing. Increasing this
          number causes more smoothing whereas decreasing the number lessens the
          smoothing. The radius parameter specifies the mrf neighborhood. Different update
          schemes are possible but only the asynchronous updating has theoretical
          convergence properties.

     -g, --icm [<useAsynchronousUpdate=1>,<maximumNumberOfICMIterations=1>,<icmCodeImage=''>]
          Asynchronous updating requires the construction of an ICM code image which is a
          label image (with labels in the range {1,..,MaximumICMCode}) constructed such
          that no MRF neighborhood has duplicate ICM code labels. Thus, to update the
          voxel class labels we iterate through the code labels and, for each code label,
          we iterate through the image and update the voxel class label that has the
          corresponding ICM code label. One can print out the ICM code image by specifying
          an ITK-compatible image filename.

     -r, --use-random-seed 0/(1)
          Initialize internal random number generator with a random seed. Otherwise,
          initialize with a constant seed number.

     -o, --output [classifiedImage,<posteriorProbabilityImageFileNameFormat>]
          The output consists of a labeled image where each voxel in the masked region is
          assigned a label from 1, 2, ..., N. Optionally, one can also output the
          posterior probability images specified in the same format as the prior
          probability images, e.g. posterior%02d.nii.gz (C-style file name formatting).

     -u, --minimize-memory-usage (0)/1
          By default, memory usage is not minimized, however, if this is needed, the
          various probability and distance images are calculated on the fly instead of
          being stored in memory at each iteration. Also, if prior probability images are
          used, only the non-negligible pixel values are stored in memory.
          <VALUES>: 0

     -w, --winsorize-outliers BoxPlot[<lowerPercentile=0.25>,<upperPercentile=0.75>,<whiskerLength=1.5>]
                              GrubbsRosner[<significanceLevel=0.05>,<winsorizingLevel=0.10>]
          To remove the effects of outliers in calculating the weighted mean and weighted
          covariance, the user can opt to remove the outliers through the options
          specified below.

     -e, --use-euclidean-distance (0)/1
          Given prior label or probability images, the labels are propagated throughout
          the masked region so that every voxel in the mask is labeled. Propagation is
          done by using a signed distance transform of the label. Alternatively,
          propagation of the labels with the fast marching filter respects the distance
          along the shape of the mask (e.g. the sinuous sulci and gyri of the cortex.
          <VALUES>: 0

     -l, --label-propagation whichLabel[lambda=0.0,<boundaryProbability=1.0>]
          The propagation of each prior label can be controlled by the lambda and boundary
          probability parameters. The latter parameter is the probability (in the range
          [0,1]) of the label on the boundary which increases linearly to a maximum value
          of 1.0 in the interior of the labeled region. The former parameter dictates the
          exponential decay of probability propagation outside the labeled region from the
          boundary probability, i.e. boundaryProbability*exp( -lambda * distance ).

     -v, --verbose (0)/1
          Verbose output.

     -h
          Print the help menu (short version).

     --help
          Print the help menu.
          <VALUES>: 1
~~~~~~~~~~~~~~~~~~~~~~~~~~~

### 2015-05-17 retrospective/neuroimage_fmri.Rmd
ENH:  More material.

# Retrospective

##

![](./retrospective/figures/retrospective.jpg)

<!--
Notes:
* No equations, just kind of a look back at where ANTs came from.
* Manuscripts are a bit deceptive in that they often present a linear development
  whereas science is messy (e.g. Popper, Carnap, and others).  Review from Fred Bookstein
  said the same thing---more on that later.
-->

##

![](./retrospective/figures/juicyDetails.png)

<!--
Notes:
* NeuroImage 26(2)  "20 years of fmri"
* FreeSurfer, Bruce Fischl "only manuscript where the reviewer requested more juicy details of the history of the development of a set of ideas."
* Yearly course with FSL, 2003 in Santa Monica "Where's the free surfer course, Dude?"
* As a quasi-relevant tangent, not a surfer, decade long playful argument with significant other
-->

##

![](./retrospective/figures/logos.png)

<!--
Notes:
* Additional interesting bits of information
* Logos
* Why a fish skeleton?
* "FOSSIL vs EFF ESS ELL"
* What is the ice cream cone for and what does it have to do with British humour?
-->

##

<BR>
<BR>
<BR>
<span style="color:red;">_"Contingency.
<BR>
AFNI is one result of unexpected events.
<BR>
I met a woman and fell in love."_</span>
<BR>

<!--
Notes:
* Love this!
* Perhaps not in the realm of "It was the best of times it was the worst of times" or "Call me Ishmael."
but, in our field, that's as close as we're going to get!
* His love interest was faculty at the University of Milwaukee.
* I certainly do not expect these stories or discussions to be retained in memory
but I hope they point to the fact that Brian and I love what we do, we love reproducible
science and enjoy helping other people, and that ANTs is a set of tools that might be
worth investigating.
-->

## <span style="color:red;">ANTs--_begotten in SyN_</red

<!--
Notes:
* In somewhat playful antithetical terms, ANTs was beggotten in SyN.
-->

### 2015-05-17 retrospective/retrospective.Rmd
ENH:  More material.

---
title: <span style="color:red;">ANTs:</span><br />A retrospective
author: Brian (<span style="color:blue;">PENN</span>) and <br />Nick (<span style="color:orange;">UVA</span>)
bibliography: REFERENCES.bib
logo:    logo.jpg
output:
  pdf_document:
    toc: true
    highlight: zenburn
  beamer_presentation:
    toc: true
    fig_width: 7
    fig_height: 6
  html_document:
    toc: true
    theme: readable
  revealjs_presentation:
    pandoc_args: [ "--slide-level", "2" ]
    incremental: true
    widescreen: true
    smaller: false
    theme: night
    transition: fade
    highlight: zenburn
    center: true
    self_contained: false
  ioslides_presentation:
    css: atk.css
    incremental: false
    widescreen: true
    smaller: false
    fig_width: 5
---

```{r global options, include=FALSE}
library(rmarkdown)
library(knitr)
figpath<-'figures/'
opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
               warning=FALSE, message=FALSE)
```

<!--
Notes:
* Acknowledgments
* Honor to be here
-->

This talk is online at [http://stnava.github.io/ANTs2015/](http://stnava.github.io/ANTs2015/) with colored [links](http://stnava.github.io/ANTs2015/) meant to be clicked for more information.

<!--
Notes:
* Format:  we chose this particular format as it gives us quite a bit of flexibility
  in reusability, public availability, and linking to additional online information
  - Apologize if it doesn't conform to your sense of aesthetics.  We empathize but...
-->

### 2015-05-20 background/background.Rmd
ENH:  Adding mni tutorial stuff.

@@
 
-##
+## Image mapping and perception: 1877
 
-__Image mapping & perception: 1877-8__
-<BR><BR>
 Francis Galton: _Can we see criminality in the face?_
@@
 ![](./figures/galton.png)
+
+_What about syphilis, mental illness?_
 
@@
 
+<!--
+
 ##
 
-<!--
 ![](./background/figures/FrancisGalton2.jpg)
@@
 
-##
+##  Speaking of criminality...
 
-Speaking of criminality...<BR>
 _Can we say anything about the U.S. Congress?_
@@
 ![](./background/figures/congressPersons.png)
+
 __Maybe he should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__
@@
 
-##
+##  Image mapping & biology:  1917
 
-__Image mapping & biology: 1917__
-<BR><BR>
-D''Arcy Thompson: _Comparison of related forms_
+D'Arcy Thompson: _Comparison of related forms_
 
@@
 
-##
-
-__Image mapping & biology: Current__
+## Image mapping & biology: Current
 <BR><BR>
@@
 
-##
-
-__ANTs family tree__
+## ANTs family tree
 
@@
 
-##
-
-__Initial scope__
+## Initial scope
 
@@
 
-##
+## Diffeomorphisms:  Occam's razor modeling
 
-__Diffeomorphisms__:plausible physical modeling
+![](./figures/sillyputty.png)
 
-<div align="center"><img src="./figures/sillyputty.png" frameborder="0"></img></div>
+_differentiable map with differentiable inverse_
 
-"differentiable map with differentiable inverse"
-
-##
-
-__Fine-grained and flexible maps__
+## Diffeomoprhisms:  fine-grained and flexible maps
 
@@
 
-##
-
- __Diffeomorphisms__: image parameterization in a metric space
+## Diffeomorphisms: image parameterization in a metric space
 
 ![](./figures/shape_appearance.png)
-
-##
-
-__General purpose library for multivariate image registration, segmentation & statistical analysis tools__
-
-* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.
-
-* Generic mathematical methods that are tunable for
-application specific domains.
-
-* <span style="color:red;">no free lunch</span>: <span style="color:black;">_An algorithm must use prior knowledge about a problem to do well on that problem._</span>
-
-<!--
-* Deep testing on multiple platforms ... osx, linux, windows.
-
-* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )
--->
-
-## Still quite a bit to do
-
-##
-
-__On documentation__
-
-![](figures/Chainsaw.jpg)
-
-<!--
-Notes:
-* ANTs documentation is only slightly better than what is shown here.
--->
-
-##
-
-Developers can be blind to doc deficiencies while users are blind to what we provide!
-
-![](figures/blindmen.jpg)

### 2015-05-20 competitions/competitions.Rmd
ENH:  Adding mni tutorial stuff.

@@
 
-##
+## Algorithmic fight club
 
-<span style="color:green;">__Competitions__</span>
+![](./competitions/figures/fightclub.jpg)
+
+## International competitions
 
@@
 
-##
-
-<span style="color:green;">__Klein 2009__</span>
+## Klein, NeuroImage 2009
 
@@
 
+<!--
 * 14 algorithms
@@
 * developers tune their own algorithms
+-->
 
-## <span style="color:green;">Results</span>
+## Klein results
 
 ![](./competitions/figures/KleinResults2009.png)
+
+## Take-away message
 
@@
 
-## <span style="color:green;">EMPIRE 2010</span>
+## EMPIRE 2010
 
@@
 * Alignment of lung boundaries,
+
 * major fissures,
+
 * annotated landmark pairs, and
+
 * topology of displacement field.
 
-##
-
-<span style="color:green;">__Results__</span>
+## EMPIRE 2010 results
 
@@
 
-##
-
-<span style="color:green;">__Multi-Atlas 2012__</span>
+## Multi-atlas 2012
 
@@
 
-##
-
-<span style="color:green;">__Results__</span>
+## Multi-atlas 2012 results
 
@@
 
-##
+## SATA 2013
 
-<span style="color:green;">SATA 2013</span>
+Three very different problem domains
 
@@
 
-##
-
-<span style="color:green;">__BRATS 2013__</span>
+## BRATS 2013
 
@@
 
-##
+## BRATS 2013 results
 
@@
 
-##
+## STACOM 2014
 
-<span style="color:green;">__STACOM 2014__</span>
-
-![](./competitions/figures/image_gallery.gif)
+![](./competitions/figures/image_gallery.jpg)
 

### 2015-05-20 evaluation/antsvfreesurfer2.Rmd
ENH:  Adding mni tutorial stuff.

--- 2014-10-16 evaluation/antsvfreesurfer2.Rmd
@@
-# ANTs brain morphology<br><br>[<small>"*Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
+---
+title: ANTs brain morphology
+author: Nick (UVa) and Brian (Penn)
+bibliography: REFERENCES.bib
+logo:    figures/antsLogoBase.png
+output:
+  beamer_presentation:
+    colortheme: dolphin
+    fonttheme:  structurebold
+    highlight: tango
+    incremental: yes
+    theme:  AnnArbor
+    includes:
+      in_header: mystyle.tex
+    toc: yes
+  pdf_document:
+    toc: true
+    highlight: zenburn
+  html_document:
+    toc: true
+    theme: readable
+  revealjs_presentation:
+    pandoc_args: [ "--slide-level", "2" ]
+    incremental: true
+    widescreen: true
+    smaller: false
+    theme: night
+    transition: fade
+    highlight: zenburn
+    center: true
+    self_contained: false
+  ioslides_presentation:
+    css: atk.css
+    incremental: false
+    widescreen: true
+    smaller: false
+    fig_width: 5
+---
 
-## Cortical thickness studies:
+```{r global options, include=FALSE}
+library(rmarkdown)
+library(knitr)
+figpath<-'figures/'
+opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
+               warning=FALSE, message=FALSE)
+```
+
+## Cortical thickness studies
+
 ```{r, results='asis', echo = FALSE}
-conditions <- c( "Huntington’s disease", "schizophrenia", "bipolar disorder",
+conditions <- c( "Tetris-playing ability", "Huntington’s disease", "schizophrenia", "bipolar disorder",
                  "Alzheimer’s disease", "frontotemporal dementia", "Parkinson’s disease",
@@
                  "obsessive-compulsive disorder", "ADHD", "obesity", "heritable depression",
-                 "elderly depression", "age", "gender", "untreated male-to-female transsexuality",
+                 "elderly depression", "age", "gender",
                  "handedness", "intelligence", "athletic ability", "meditative practices", "musical ability",
                  "tendency toward criminality", "childhood sexual abuse in female adolescents",
-                 "Tetris-playing ability in female adolescents", "traumatic brain injury" )
+                  "traumatic brain injury", "untreated male-to-female transsexuality" )
 
@@
 * Sandy, Brian, and <span style="color:red;">DiReCT</span>
-  + used other tools such as FMRIB's Automated Segmentation Tool (FAST)
+    + used other tools such as FMRIB Automated Segmentation Tool (FAST)
     + `KellySlater.cxx`
-  * scripts "adequate for Penn data"
+* pipedream scripts "adequate for Penn data."
 * `KellyKapowski.cxx` and `antsCorticalThickness.sh`
@@
 
-## The ANTs structural brain mapping workflow
-
-![](./evaluation/figures/pipeline.png)
-
 ## Basic components of the pipeline
-
-<div align="center"><img height="350" src="./evaluation/figures/components.png" frameborder="0"></img></div>
 
@@
 
+## Sample results
+
+![](./evaluation/figures/components.png)
+
+## The ANTs structural brain mapping workflow
+
+![](./evaluation/figures/pipeline.png)
+
 ## Template building
@@
 
-<div align="center"><img height="350" src="./evaluation/figures/templates.png" frameborder="0"></img></div>
+![](./evaluation/figures/templates.png)
 
+<!--
 * Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
 * Acquisition and anonymization (e.g. defacing) protocols are often different.
+-->
 
-## Template building (cont.)
+## Template priors
 
-<div align="center"><img height="350" src="./evaluation/figures/templatePriors.png" frameborder="0"></img></div>
+![](./evaluation/figures/templatePriors.png)
 
+<!--
 Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
 to produce auxiliary images which are used for brain extraction and brain segmentation.
+-->
 
-## Brain extraction comparison<br>ANTs vs. FreeSurfer
+## Brain extraction comparison
 
-<div align="center"><img height="380" src="./evaluation/figures/brainExtraction.png" frameborder="0"></img></div>
+![](./evaluation/figures/brainExtraction.png)
 
+<!--
 Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
 the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
+-->
 
@@
 
-<div align="center"><img height="350" src="./evaluation/figures/brainSegmentation.png" frameborder="0"></img></div>
+![](./evaluation/figures/brainSegmentation.png)
 
-Randomly selected healthy individuals.  Atropos gets good performance across ages.
+<!--
+Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.
+-->
 
@@
 
-<div align="center"><img height="250" src="./evaluation/figures/corticalThicknessEstimation.png" frameborder="0"></img></div>
+![](./evaluation/figures/corticalThicknessEstimation.png)
 
-In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, ANTs diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
+<!--
+In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
+-->
 
@@
 
-* Use age and gender (demographic information) in training/prediction paradigm
-* Public data sets (IXI, NKI, Oasis, MMRR)
-* $>$ 1200 subjects, age 7 to over 90 years old
+## Predict age and gender
 
-## Prediction from cortical thickness data:<br>gender and age
+$AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$
 
-<div align="center"><img height="350" src="./evaluation/figures/evaluation.png" frameborder="0"></img></div>
+## Open science prinicples
+
+![](./evaluation/figures/ageDistribution.png)
+
+<!--
+* Public data sets (IXI, NKI, OASIS, MMRR)
+* $>$ 1200 subjects, age 4 to over 94 years old
+-->
+
+## Prediction from cortical thickness data
+
+![](./evaluation/figures/evaluation.png)
+
+## Age prediction per site
+
+![](./evaluation/figures/agePredictionPerSite.png)
 
@@
 
-$AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$
-
-<div align="center"><img height="500" src="./evaluation/figures/antsvfreesurfer_importance.png" frameborder="0"></img></div>
+![](./evaluation/figures/antsvfreesurfer_Importance.png)
 
@@
 
-## Regional importance comparison (cont.)
+## Regional measurements
 
-<div align="center"><img height="550" src="./evaluation/figures/antsvfreesurfer_regionalPlots.png" frameborder="0"></img></div>
-
-## All software components are open source and part of the ANTs repository.
-
-# Cortical thickness extensions
+![](./evaluation/figures/antsvfreesurfer_regionalPlots.png)

### 2015-05-20 papers/papers.Rmd
ENH:  Adding mni tutorial stuff.

@@
 
-##
+## Donoho?
 
@@
 
-##
+## Symmetric Normalization (SyN)
 
-__Symmetric Normalization:__  (_SyN_)
-
-$\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt$
-
-$+ \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2$
+$\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt + \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2$
 
@@
 
-##
+## Beyond original SyN
 
-__Beyond original SyN__
+\small
 
@@
 
-##
-
-```antsRegistration```
+## ```antsRegistration```
 <BR><BR>
 
-~~~~~~~~~~~~~~~~~~~~~~~
+```bash
 $ antsRegistration --help
@@
           call.
-~~~~~~~~~~~~~~~~~~~~~~~
+```
 
-##
-
-__Template building__
-
-##
+## Template building:  creating the average Joe
 
@@
 
-##
+## "Attractiveness" $\rightarrow$ mental processing?
 
@@
 
-##
+##  What about brains?
 
@@
 
-##
+## Templates facilitate computation
 
@@
 
-##
+## Gender discernibility?
 
@@
 
-##
+## ```antsMultivariateTemplateConstruction2.sh```
 
-```antsMultivariateTemplateConstruction2.sh```
-
-<BR>
-
-~~~~~~~~~~~~~~~~~~~~~~
+```bash
 $ antsMultivariateTemplateConstruction2.sh
@@
 --------------------------------------------------------------------------------------
-~~~~~~~~~~~~~~~~~~~~~~
+```
 
-##
-
-__Nonparametric nonuniform intensity normalization (N3)__
+## Nonparametric nonuniform intensity normalization (N3)
 
@@
 
-##
-
-__N3 adoption issues__
+## N3 adoption issues
 
@@
 
-##
-
-<!--
-__N3 $\rightarrow$ N4<sup>*</sup>__
-
-<p align = "middle"><small><sup>*</sup><u>N</u>ick's N3</small></p>
--->
-
-__N4__
+## N4
 
@@
 
-* smaller spline distances (useful for higher magnet strengths)
+* small spline distances (useful for higher magnet strengths)
 
@@
 
-* faster execution times
+* fast execution times
 
@@
 
-##
+* tested nightly within the ITK dashboard system
 
-```N4BiasFieldCorrection```
+## ```N4BiasFieldCorrection```
 
-<BR>
-
-~~~~~~~~~~~~~~~~~~~~~~~~~~~
+```bash
 $ N4BiasFieldCorrection --help
@@
           <VALUES>: 1
-~~~~~~~~~~~~~~~~~~~~~~~~~~~
+```
 
-##
+##  Atropos -- cutting the threads of fate
 
@@
 "20+ years of development.  <br>_Show me the code!_"
-
-<p align = "right"><small>Brian, MICCAI workshop</small></p>
 
@@
 
-##
-
-__Atropos__
+## Atropos:  flexible code base
 
@@
 
-<!-- regular html comment
+## ```Atropos```
 
-<div align="center"><img src="./tools/n4/figures/whyN4.png" frameborder="0"></img></div>
-
--->
-
-##
-
-__Algorithmic workflow__<br>(Atropos + N4 $\rightarrow$ `antsAtroposN4.sh`)
-
-![](./tools/atropos/figures/atroposFlow.png)
-
-##
-
-```Atropos```
-
-<BR>
-
-~~~~~~~~~~~~~~~~~~~~~~~~~~~
+```bash
 $ Atropos --help
@@
           <VALUES>: 1
-~~~~~~~~~~~~~~~~~~~~~~~~~~~
+```
+
+## Atropos + N4 $\rightarrow$ `antsAtroposN4.sh`
+
+![](./tools/atropos/figures/atroposFlow.png)

### 2015-05-20 retrospective/neuroimage_fmri.Rmd
ENH:  Adding mni tutorial stuff.

@@
 ##
+
+## ANTs evolution
 
@@
 
-##
+## FreeSurfer, Bruce Fischl
 
@@
 
-##
+<!--
+
+## Other juicy bits
 
@@
 
-<!--
 Notes:
@@
 
-##
+## NeuroImaging research as literature
 
-<BR>
-<BR>
-<BR>
-<span style="color:red;">_"Contingency.
-<BR>
+"Contingency.
 AFNI is one result of unexpected events.
-<BR>
-I met a woman and fell in love."_</span>
-<BR>
+I met a woman and fell in love."
 
@@
 
-## <span style="color:red;">ANTs--_begotten in SyN_</red
+## ANTs--_begotten in SyN_
+
+![](./retrospective/figures/Welcometotherealm.jpg)
 

### 2015-05-20 retrospective/retrospective.Rmd
ENH:  Adding mni tutorial stuff.

@@
 ---
-title: <span style="color:red;">ANTs:</span><br />A retrospective
-author: Brian (<span style="color:blue;">PENN</span>) and <br />Nick (<span style="color:orange;">UVA</span>)
+title: <span style="color:red;">ANTs:</span><br /> A retrospective
+author: Brian (Penn) and Nick (UVa)
 bibliography: REFERENCES.bib
-logo:    logo.jpg
+logo:    figures/antsLogoBase.png
 output:
+  beamer_presentation:
+    colortheme: dolphin
+    fonttheme:  structurebold
+    highlight: tango
+    incremental: yes
+    theme:  AnnArbor
+    includes:
+      in_header: mystyle.tex
+    toc: yes
   pdf_document:
@@
     highlight: zenburn
-  beamer_presentation:
-    toc: true
-    fig_width: 7
-    fig_height: 6
   html_document:

### 2015-05-20 ANTsScience.Rmd
ENH: first complete draft

@@
 author: "Brian B. Avants et al."
-date: "May 9, 2015"
+date: "`r Sys.Date()`"
 output: pdf_document
@@
 
-Advanced Normalization Tools (ANTs, originating at [sourceforge.net](sourceforge.net) on 2008-06-26 and now residing at [http://stnava.github.io/ANTs/](http://stnava.github.io/ANTs/) is a systematic framework for quantitative biological image analysis based on the Insight ToolKit [www.itk.org](www.itk.org).
+Advanced Normalization Tools (ANTs, originating at [sourceforge.net](sourceforge.net) on 2008-06-26 and now residing at [http://stnava.github.io/ANTs/](http://stnava.github.io/ANTs/) ) is a systematic framework for quantitative biological image analysis based on the Insight ToolKit [www.itk.org](www.itk.org).
 ANTs was first created to rapidly disseminate our latest research to the community of scientists who depend on imaging analytics and to allow them to study different organ systems, species or modalities with the same sound foundation.
 While originally focused on diffeomorphic image registration, ANTs now incorporates novel and cutting-edge methods for segmentation, feature extraction and, more recently, complete statistical pipelines via ANTsR [http://stnava.github.io/ANTsR/](http://stnava.github.io/ANTsR/).
-In 2014, there were nearly 2,000 citations to ANTs and the software is cloned, downloaded or otherwise accessed over 100-200 times per week, on average.
-Though ANTsR is relatively new, this software is cloned (via github) on average 50 times per week---a substantial number that suggests the value of the software.
+In 2014, there were nearly 2,000 citations to ANTs and the software is cloned, downloaded or otherwise accessed over 100-200 times per week, on average at github.
+The sourceforge site hosts a similar number of visits and downloads.
+ANTsR is accessed on average 50 times per week---a substantial number for a new software.
+There are also over 500 discussion topics on the ANTs sourceforge community site, nearly 100 topics on the github site and over 50 help-focused emails to the personal addresses of developers.
+Generally, response time to requests for help is within a few hours with rare occasions taking up to a day or two.
 
@@
 The framework is also designed explicitly for multivariate analyses.
-Nearly every tool within ANTs/R that can be multivariate is multivariate.
+Nearly every tool within ANTs/R is multivariate.
 For example, the ANTs registration tool is capable of combining several metrics each with its own weight function.
@@
 The Atropos segmentation tool also incorporates multiple modalities via parametric models (Mahalanobis distance) or non-parametric models (products of joint probabilities).
-More recently, we implemented, in ANTsR, the challenge-winning MRVNRFS algorithm which won the BRATS2013 tumor segmentation challenge.
+More recently, we implemented, in ANTsR, the challenge-winning multi-resolution voxel-wise neighborhood random forest (MRVNRF) prediction algorithm which won the BRATS2013 tumor segmentation challenge.
 
-# Technical solutions
+# ANTs solutions in science
 
-* Accurate high-dimensional and flexible digital diffeomorphisms with multivariate similarity
+* Accurate high-dimensional and flexible digital diffeomorphisms with multivariate similarity: ANTs implements transformation models that are robust to noise and yet are able to exploit high resolution detail available in modern neuroimaging.
 
-* Multiple modality template building in the digital diffeomorphic space
+* Multiple modality template building in the digital diffeomorphic space: We exploit the fact that diffeomorphisms encode a high-dimensional metric space to compute shape and appearance averages of organs and organ systems based on multiple modality medical imaging.
+The recent Pediatric Template of Brain Perfusion, for instance, distributes a dictionary of normal variability in cortical structure, diffusion tensor metrics, resting bold connectivity and cerebral blood flow during adolescence.
+We also relate these modalities to demographic metrics such as IQ, age and socioeconomic factors.
 
-* Prior-based multivariate / multiple modality segmentation in the public domain
+* Prior-based multivariate/multiple modality segmentation in the public domain: ANTs distributes Atropos as a multi-channel segmentation tool that leverages tunable spatial priors.
+Atropos is able to segment large numbers of regions from multiple imaging modalities while maintaining the integrity of expert-based prior knowledge.
+This work is valuable to both human brain mapping and non-human mammalian imaging FIXME REF-CHIMP REF-MOUSE.
 
-* Volumetric sub-voxel accurate thickness, evaluated against Freesurfer
+* Volumetric sub-voxel accurate thickness, evaluated against Freesurfer: We contributed the first large-scale comparison of voxel-based, volumetric thickness versus the standard Freesurfer surface-based thickness in terms of prediction power in a large lifespan T1 dataset.
+The ANTs-based cortical thickness measure improved prediction of both age and gender relative to Freesurfer in a pure training and testing evaluation framework.
+FIXME REF.
 
-* Joint intensity and joint label fusion
+* Joint intensity and joint label fusion: The ANTs toolkit distributes Joint Label Fusion (JLF) for multiple modality segmentation based on large datasets of expert annotated medical images, e.g.
+neuroanatomical regions defined in T1 MRI or major tracts defined in DTI.
+JLF has won several international anatomical segmentation challenges in medical imaging FIXME-REF.
 
-* Broad distribution channels: ITK, Slicer, Neurodebian, BrainsFit, etc
+* Broad distribution channels:  ANTs technology is distributed through the Insight ToolKit (ITK), the Slicer toolkit, Neurodebian, BrainsFit and in SimpleITK.
+Thus, the impact of ANTs is beyond what we can directly measure from references in publications or direct software downloads.
+Furthermore, our liberal distribution policies for ANTs software cannot enforce specific referencing practices - many papers, for instance, only reference neurodebian or one of the ANTs websites in publication.
 
-* Eigenanatomy and a parameter-free version
+* Eigenanatomy is a parameter-free tool for generating data-driven regions of interest:  Our recent paper defined a novel approach to computing an optimal set of regions of interest from population neuroimaging data.
+This is one of the only data-driven image decomposition methods with *in vivo* findings that have been validated post-mortem FIXME-REF.
+Indeed, regions of the white matter implicated by Eigenanatomy in a neuroimaging study led to verified pathology in a classification analysis of tau and TDP frontotemporal lobar degeneration FIXME-REF.
 
-* SCCAN
+* Sparse canonical correlation analysis (SCCAN): ANTs and ANTsR also enable a "supervised" version of Eigenanatomy based on a modernized sparse and geometrically regularized update to Hotelling's classic canonical correlation analysis.
+This tool has been used to focus testing for imaging genomics studies, to relate multiple imaging modalities to each other and to map structural networks that underlie cognitive performance.
+FIXME REFS.
 
-* Automated template construction with priors based on SyGN, JIF and Atropos ... with probability modifiers.
+* Automated template construction with priors based on symmetric normalization (SyN, 800+ references to the original paper), JIF and Atropos: An anatomical or functional template is more than just an average image - it is also the set of probabilistic priors and spatial maps of anatomy that accompany the image.
+In the last several years, we have established a system for generating new templates based on existing priors.
+This leverages our prior work on template construction, multi-atlas labeling and tissue segmentation to generate probabilistic templates that are ready to use on new problems.
+Such templates form the basis of our large-scale multiple modality analysis framework.  FIXME-REF chimp, waxholm, lung etc.
 
-* RIPMMARC
+* Learning one imaging modality from another to understand modality redundancy and structure-function relationships:  We recently developed the RIPMMARC algorithm to show that nearly 50\% of the variability in ASL-based cerebral blood flow images can be predicted from T1 neuroimaging.
+However, we also established that there is valuable signal in the CBF images that cannot be predicted from the T1 data.
+That is, the residual CBF signal (the putative "functional signal") is related to demographic variables as is the structural component.
+This tool has value, yet to be explored, for performing imputation and can be extended to other modalities, species or organ systems.
+FIXME-REF.
 
-* A highly-customizable adaptive processing pipeline for cerebral blood flow calculation
+* A highly-customizable adaptive processing pipeline for cerebral blood flow calculation from ASL: ANTsR has enabled us to implement a large-scale evaluation of cerebral blood flow calculation from arterial spin labeling.
+This pipeline was used in adolescent and neurodegenerative subjects FIXME-REFS but is undergoing further evaluation in a lifespan population and comparison with PET.
 
-* Joint intensity and landmark-based registration
+* Joint intensity and landmark-based registration:  Purely image-driven registration can be improved in terms of accuracy and consistency by using anatomical labels or landmarks to guide a registration.
+ANTs is one of the only currently available tools that allows scientists to jointly optimize, in a weighted fashion, the registration of images and anatomy.
+This functionality is frequently employed for guided registration with hippocampal subfields or for registration based on structure plus tractography.
 
-* Broad testing across organ systems and species, deep testing of registration and segmentation and detection power capabilities
+* ANTs is founded on deep software testing and practical evaluation across organ systems and species, deep testing of registration and segmentation and detection power capabilities.
+Several papers have established the value of our methods for improving the reproducibility of prediction models based on ANTs image processing and statistical methods: FIXME REFS.
+We have also won several challenges e.g.
+in heart [http://www.cardiacatlas.org/web/stacom2014/home](http://www.cardiacatlas.org/web/stacom2014/home), [lung](lung), [brain](brain)  and [other organ systems](www).
 
-* Multi-start optimization
+* Multi-start optimization and feature selection/masking:  ANTs has several powerful but under-utilized registration tools that include global optimization and feature selection.
+These tools can be used to improve robustness of registration in large datasets, in challenging datasets or in datasets with only partial structure (lesions, masking, cropped images, images with missing data etc.) FIXME-REF-LESION MAPPING.
 
 * Standardization of registration architecture and transformations through our work on ITK version 4+.
+We are part of the ITK development team and have worked with the community over the last 15 years to evaluate and improve the standardized transformation frameworks that are used throughout our own and several related software infrastructures FIXME cite elastix etc.
 
-* MRV-NRF ...
+* ANTsR implements and distributes novel MRV-NRF and other prediction algorithms that improve machine learning via image-specific regularization.   FIXME-BRATS-PAPERS, SCCAN, Eanat ...
 
-# Clinical and neuroscience solutions
+* Subject-specific denoising solutions for functional MRI data, specifically arterial spin labeling (ASL), have the potential to revolutionize the applicability of cerebral blood flow to new populations with high variability (neurodegeneration, TBI, etc).
+Detection power is also likely to improve when these new methods are combined with our latest registration techniques even in control populations, in non-human mammals or in MRI beyond the brain, e.g.
+cardiac ASL FIXME-REFS.
 
-* mouse
+* Our ANTs and ITK methods are instrumental to several recent non-human mammal studies including developing the Waxholm template space, the Allen Brain Atlas, the Possum template space and a chimpanzee template.
+These methods have been widely adopted and applied to studies published in high-impact journals such as Nature, PNAS, etc.
 
-* chimp, rhesus
+* We have implemented complete "scanner to study" tutorials that show how to employ ITK, ANTs and ANTsR to transform raw data into a complete and reproducible study.
+These studies include ....
+We also provide the ANTs Neurobattery **FIXME** a documented/distributable system to analyze multiple modality neuroimaging datasets.
+The framework was developed from and is regularly tested on the freely available Pediatric Template of Brain Perfusion (http://www.nature.com/articles/sdata20153).
 
-* lung
+* **FIXME** say something about lung ....
 
-* heart
+* **FIXME** say something about heart ...
 
@@
 
-* Sparse transformations
-
-* Sparse registration
-
-* ICDM - framework for sparse image and pointset/curve/surface matching
-
-* More fully reproducible studies based on ANTsR ...
-
-.....
-
-system to analyze a multiple modality neuroimaging dataset derived from the freely available Pediatric Template of Brain Perfusion (http://www.nature.com/articles/sdata20153).
+* We have ongoing work in Advanced Normalization Tools that is devoted to the development of sparse image, transformation and metric representations.
+Additional mathematical and software effort is needed to exploit the advantages that these innovative solutions enable.
+Specifically, our iterative closest data mapping (ICDM for sparse image and pointset/curve/surface matching) framework has the potential to massively reduce computation time as well as the memory footprint of both low and high-dimensional image registration within ANTs.
+However, to achieve this goal and reach full potential, both the sparse sampling theory for diffeomorphisms and metric spaces must be resolved to enable a proper software implementation to reach full potential.
+With additional effort, we will be able to address emerging needs for sparse and dense registration (with optimal sampling) of massive datasets being collected with the laboratories of collaborators:  Betzig, Seung, Deisseroth, AJohnson, A Badea and more **FIXME**

### 2015-05-20 evaluation/antsvfreesurfer2_extra.Rmd

@@
 
-*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"  <span style="color:blue;">Sure, why not?</span>
+*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"  Sure, why not?
 
-*  "_I was wondering if you would make available the CT in each ROI for each subject..._" <span style="color:blue;">Sure, why not?  Would you also like the surface areas and volumes?</span>
+*  "_I was wondering if you would make available the CT in each ROI for each subject..._" Sure, why not?  Would you also like the surface areas and volumes?
 
-*  "_Can I have one or more of the templates that you used for your study?_"  <span style="color:blue;">Would you like the priors as well?</span>
-
-*  "_Hey Nick, can we hire you to do an [EZ-MAP]-type study?_" <span style="color:blue;">What about something better?</span>
+*  "_Can I have one or more of the templates that you used for your study?_" Would you like the priors as well?
 
@@
 
-##
+## ANTs tools are multivariate
 
-__ANTs tools are multivariate__
+![](./evaluation/figures/rfRmse05ANTsT1T2.png)
 
-<div align="center"><img height="450" src="./evaluation/figures/rfRmse0.5ANTsT1T2.png" frameborder="0"></img></div>
+## Arno-thick-in-the-head (ATITH)
 
-##
+_What if we made a crude estimate of the cortical thickness?_
 
-__Arno-thick-in-the-head (ATITH)__
+$$thickness_{ROI} = \frac{volume_{ROI}}{area_{ROI}}$$
 
-<br><br>
-<span style="color:blue;">_What if we made a crude estimate of the cortical thickness?_</span>
-<br><br>
-
-$thickness_{ROI} = \frac{volume_{ROI}}{area_{ROI}}$
-
-##
-
-<span style="color:blue;">Make sure you estimate the [surface area](http://www.insight-journal.org/browse/publication/852) correctly!</span>
+## Make sure you estimate the [surface area](http://www.insight-journal.org/browse/publication/852) correctly!
 
@@
 
-##
+## Prediction from cortical thickness data
 
-__Prediction from cortical thickness data:<br>gender and age__
+![](./evaluation/figures/atith.png)
 
-<div align="center"><img height="350" src="./evaluation/figures/atith.png" frameborder="0"></img></div>
-
-##
+## Brain constellation maps
 
@@
 
-##
+## Contribution from Jose
 
@@
 
-~~~~~~~~~~~~~~~~~~~~~~
+```bash
 $ DenoiseImage
@@
           Print the help menu.
-~~~~~~~~~~~~~~~~~~~~~~
+```
 
@@
 
-~~~~~~~~~~~~~~~~~~~~~~~
+```bash
 ${ANTSPATH}/antsCorticalThickness.sh \
@@
   -o IXI/ANTsResults/IXI002-Guys-0828-
-~~~~~~~~~~~~~~~~~~~~~~~
+```
 
@@
 
-## Don't worry,
-
-we'll run a 2-D example this afternoon.
-<BR><BR>
+## We'll discuss more this afternoon
 
 https://github.com/ntustison/antsCorticalThicknessExample
-
-# Extensions

### 2015-05-20 installation/ants_installation.Rmd
ENH:  More material.

@@
 
-##
-
-ANTs is a <span style="color:red;">_dynamic_</span> toolkit so,
+## ANTs is a _dynamic_ toolkit
 
@@
 
-for the willing, we recommend compiling from source.
+so we generally recommend compiling from source.
+
+Current modifications: ``antsAI`` and ``CreateTieldMosaic``.
 
@@
 
-##
+## First source for documentation
 
@@
 
-~~~~~~~~~~~~~~~~~~
+```bash
 $ cd ${WHICH_PATH}
@@
 $ echo "export ANTSPATH=/${WHICH_PATH}/ANTs/bin/bin/" >> ~/.profile
-$ echo "export ITK_GLOBAL_DEFAULT_NUMBER_OF_THREADS=4" >> ~/.profile
+$ echo "export ITK_GLOBAL_DEFAULT_NUMBER_OF_THREADS=1" >> ~/.profile
 $ source ~/.profile
-~~~~~~~~~~~~~~~~~~
+```
 
-##
-
-<span style="color:blue;">__Some cmake considerations:__</span>
+## Some cmake considerations
 
@@
 
-##
+## Try calling the ```KellyKapowski``` short help menu.
 
-Try calling the <span style="color:blue;">```KellyKapowski```</span> short help menu.
-
-~~~~~~~~~~~~~~~~~~
+```bash
 $ KellyKapowski -h
@@
      --help
-~~~~~~~~~~~~~~~~~~
+```
 
-##
-
-or the <span style="color:blue;">```antsRegistration```</span> long help menu.
+## ```antsRegistration``` long help menu.
 

### 2015-05-20 installation/snap_installation.Rmd

@@
 
-~~~~~~~~~~~~~~~~~~~~~~~
+## Linux (command line)
+
+```bash
 $ tar -zxvf itksnap-3.2.0-rc2-20140919-Linux_x86_64.tar.gz
@@
 $ itksnap
-~~~~~~~~~~~~~~~~~~~~~~~
+```
 
-## Thanks Paul!
-
-and [others](http://www.itksnap.org/pmwiki/pmwiki.php?n=Main.Credits)
+## Ready to go!

### 2015-05-20 mystyle.tex

\pgfdeclareimage[height=0.1cm, width=1cm]{logo}{}
\logo{\pgfuseimage{logo}}
\institute{}
\definecolor{links}{HTML}{2A1B81}
\definecolor{mypink2}{RGB}{219, 48, 122}
\hypersetup{colorlinks,linkcolor=links,urlcolor=mypink2}
\usefonttheme{professionalfonts}
\setbeamerfont{note page}{family*=pplx,size=\footnotesize} % Palatino for notes
\usepackage{helvet}
\useinnertheme{rectangles}

### 2015-05-20 summary/summary.Rmd

# ANTs:  in summary

## Show me the code!

__General purpose library for multivariate image registration, segmentation & statistical analysis tools__

* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.

* Generic mathematical methods that are tunable for
application specific domains.

* <span style="color:red;">no free lunch</span>: <span style="color:black;">_An algorithm must use prior knowledge about a problem to do well on that problem._</span>

<!--
* Deep testing on multiple platforms ... osx, linux, windows.

* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )
-->

## Still quite a bit to do

## On documentation

![](figures/Chainsaw.jpg)

<!--
Notes:
* ANTs documentation is only slightly better than what is shown here.
-->

## We are blind to deficiencies.  Users blind to features.

![](figures/blindmen.jpg)

### 2016-07-13 antsr/antsrdemo.Rmd
ENH: quick demo of some features

@@
+---
+title: "Mapping and matrix decomposition for biomedical images"
+author: "Brian B. Avants"
+date: "July 11, 2016"
+output: ioslides_presentation
+---
+
 # Registration & statistics:<br /> Frontiers and innovation
@@
 
-![images at measurement fields](figures/statisticalfields.png)
+```{r, out.width = 800, fig.retina = NULL, echo=FALSE}
+knitr::include_graphics("~/data/antsExamples/ANTs2015/figures/statisticalfields.png")
+```
 
@@
 ## Agnostic statistics
-![](./figures/antsrex.jpg)
+
+```{r, out.width = 800, fig.retina = NULL, echo=FALSE}
+knitr::include_graphics("/Users/bavants/data/antsExamples/ANTs2015/figures/antsrex.jpg")
+```
 
@@
 ```{r loadimages,message=FALSE,warning=FALSE,results='hide'}
-library(ANTsR)
-dim<-2
+library( ANTsR )
+library( ggplot2 )
 filename<-getANTsRData('r16')
-img<-antsImageRead( filename , dim )
-filename<-getANTsRData('r64')
-img2<-antsImageRead( filename , dim )
-mask<-getMask(img,50,max(img),T)
-mask2<-getMask(img,150,max(img),T)
+img<-antsImageRead( filename )
+filename2<-getANTsRData('r16')
+img2<-antsImageRead( filename2 )
+mask<-getMask( img,  50, max(img), cleanup = 5 )
+mask2<-getMask( img, 150, max(img), cleanup = 5 )
 nvox<-sum( mask == 1 )
 nvox2<-sum( mask2 == 1 )
+img3<-antsImageRead( getANTsRData('r27') )
+mask3<-getMask( img3,  200, max(img3), cleanup = 5 )
+nvox3 = sum( mask3 == 1 )
 ```
 The brain has `r nvox` voxels ...
+
+## Run a diffeomorphic mapping
+
+```{r qreg,message=FALSE,warning=FALSE,results='hide'}
+plot( img )
+img64 = antsImageRead( getANTsRData( 'r64' ) )
+plot( img64 )
+areg = antsRegistration( img, img64, typeofTransform = 'Affine' )
+plot( areg$warpedmov )
+sreg = antsRegistration( img, img64, typeofTransform = 'SyN' )
+plot( sreg$warpedmov )
+jacobian = createJacobianDeterminantImage( img, sreg$fwdtransforms[[1]], 1 )
+plot( jacobian )
+plot( img, jacobian * -1 , window.overlay = c(0.2,1) )
+plot( img, sreg$warpedmovout  %>% iMath("Canny", 5, 0.1, 1) )
+```
+
+## Run a population diffeomorphic mapping
+
+```{r qregpop,message=FALSE,warning=FALSE,results='hide'}
+ilist = list( 
+  antsImageRead( getANTsRData( 'r27') ),
+  antsImageRead( getANTsRData( 'r30') ),
+  antsImageRead( getANTsRData( 'r62') ),
+  antsImageRead( getANTsRData( 'r64') ),
+  antsImageRead( getANTsRData( 'r85') ) )
+rlist = list( )
+for ( i in 1:length( ilist ) ) {
+  temp = antsRegistration( img, ilist[[i]], typeofTransform = "SyN" )
+  jacobian = createJacobianDeterminantImage( img, temp$fwdtransforms[[1]], 1)
+  rlist[[ i ]] = jacobian }
+imask = getMask( img )
+mat   = imageListToMatrix( rlist, imask )
+eanat = eanatDef( scale( mat ), nvecs = esel, mask = mask,
+  positivity = TRUE, smoother = 0.5, cthresh = 200 )
+```
+
+## Run a population eigenanatomy
+
+```{r qreanat,message=FALSE,warning=FALSE,results='hide'}
+eanat = eanatDef( scale( mat ), nvecs = 4, mask = imask,
+  positivity = TRUE, smoother = 0.5, cthresh = 2200 )
+eilist = matrixToImages( eanat, imask )
+eseg = eigSeg( imask, eilist )
+plot( img, eseg )
+```
 
@@
   img1sim<-antsImageClone(img)
-  img1sim[ mask==1 ]<-rnorm(nvox,mean=0.5)
-  img1sim[ mask2==1 ]<-rnorm(nvox2,mean=2.0)
-  img2sim<-antsImageClone(img2)
-  img2sim[ mask==1 ]<-rnorm(nvox,mean=0.20)
-  imglist<-lappend(imglist,img1sim)
-  imglist2<-lappend(imglist2,img2sim)
+  img1sim[ mask==1 ]  = rnorm(  nvox, mean=1.0 )
+  img1sim[ mask2==1 ] = rnorm( nvox2, mean=1.5 )
+  img2sim = antsImageClone(img2)
+  img2sim[ mask==1 ] = rnorm( nvox, mean=1.0)
+  img2sim[ mask3==1 ] = rnorm( nvox3, mean=0.0)
+  imglist<-lappend(  imglist ,  img1sim %>% smoothImage( 5 ) )
+  imglist2<-lappend( imglist2,  img2sim %>% smoothImage( 5 ) )
 }
 imglist<-lappend( imglist, imglist2 )
+```
+
+## A Quick <span style="color:grey;">*ANTsR*</span> example
+
+Simulate a population morphometry study - a "VBM" ...
+```{r morph2,results='hide'}
 mat<-imageListToMatrix( imglist, mask )
-DX<-factor( c( rep(0,simnum), rep(1,simnum) ) )
+DX<-factor( c( rep(1,simnum), rep(0,simnum) ) )
 mylmresults<-bigLMStats( lm( mat ~ DX ) )
@@
 betas<-antsImageClone(mask)
-betavec<-abs(mylmresults$beta.t[1,])
+betavec<-( mylmresults$beta.t[1,] )
 betas[mask==1]<-betavec
-smoothImage(betas, 1.5)
-thresh<-paste(3.0,'x',max(betavec),sep='')
-ofn<-paste(figpath,'vizmorph2.jpg',sep='')
+thresh<-c( 5.0, max(betavec) )
+plot( img, betas, window.overlay=thresh )
 ```
 
-```{r vizmorph2,results='hide'}
-plot.antsImage(img,functional=list(betas),threshold=thresh,
-  outname=ofn)
+## Eigenanatomy: Run it
+
+```{r eanat}
+esel = eanatSelect( scale( mat ), mask, 200, 0.5, maxNEvec = 10 )
+eanat = eanatDef( scale( mat ), nvecs = esel, mask = mask,
+  positivity = TRUE, smoother = 0.5, cthresh = 200 )
 ```
 
-![](`r ofn`)
+## Eigenanatomy: Display it
+
+```{r eanatd}
+mm = makeImage( mask, eanat[1,] ) %>% iMath("Normalize")
+plot( img, mm, window.overlay=c(0.1,1) )
+```
+
+## Test the eigenanatomy components
+
+The first component should relate to a "group difference."
+
+Let's just use linear regression.
+
+```{r eanatregression}
+dx = factor( c( rep(1, (nrow(mat)/2) ), rep(0, (nrow(mat)/2) )   ) )
+# make the low-dimensional representation
+proj = mat %*% t( eanat )
+eanatDataFrame = data.frame( dx = dx, eanat = proj )
+mdl = lm( eanat.1 ~ dx , data = eanatDataFrame )
+print( knitr::kable( coefficients( summary( mdl ) ) ) )
+mdl = lm( eanat.5 ~ dx , data = eanatDataFrame )
+print( knitr::kable( coefficients( summary( mdl ) ) ) )
+```
+
+## A "real study"
 
@@
 ```{r networkfn,results='hide',warning=FALSE,echo=FALSE,message=FALSE}
-ofn<-paste(figpath,'network',sep='')
+ofn<-paste('/Users/bavants/data/antsExamples/ANTs2015/figures/network',sep='')
 ofnpng<-paste(ofn,'.png',sep='')
 ```
+
 ```{r network,results='hide',warning=FALSE,echo=FALSE,message=FALSE,eval=F}
@@
 ```
-![](`r ofnpng`)
+
+```{r, out.width = 800, fig.retina = NULL, echo=FALSE}
+knitr::include_graphics( ofnpng )
+```
 
@@
 
-![](./figures/antsgoals.png)
+```{r, out.width = 800, fig.retina = NULL, echo=FALSE}
+knitr::include_graphics("~/data/antsExamples/ANTs2015/figures/antsgoals.png")
+```
 

### 2016-07-17 ants2015build.Rmd
ENH:  IBM presentation.

--- 2014-10-30 ants2015build.Rmd
@@
 ---
-title: <span style="color:red;">*ANTs*</span><br> <small>_power tools for neuroimaging_</small>
-author:
+title: <span style="color:red;">ANTs:</span><br /> A brief retrospective
+author: Nick Tustison
 bibliography: REFERENCES.bib
-logo:    logo.jpg
+logo:    figures/antsLogoBase.png
 output:
+  beamer_presentation:
+    colortheme: dolphin
+    fonttheme:  structurebold
+    highlight: tango
+    incremental: yes
+    theme:  AnnArbor
+    includes:
+      in_header: mystyle.tex
+    toc: yes
   pdf_document:
@@
 ---
+# Founding developers
 
-```{r global options, include=FALSE}
-library(rmarkdown)
-library(knitr)
-figpath<-'figures/'
-opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
-               warning=FALSE, message=FALSE)
-```
+##  Brian and Nick
 
-# Background
+<BR><BR>
 
-## Founding developers
+![](./figures/brian_and_nick.png)
 
-<div align="center"><img width="1800" src="./figures/brian_and_nick.png" frameborder="0"></img></div>
+<!--
+NOtes:
+* Worked together for almost 10 years
+* have learned tons
+* have written quite a bit of code together
+-->
 
-## Long term collaborators
+## ANTs long term collaborators
 
@@
 
-## _ANTs_:  General purpose library for multivariate image registration, segmentation & statistical analysis tools
+$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
 
-* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.
+<!--
+NOtes:
+* However, it is not just us
+* Other people have done quite a bit
+* and others who are not shown such as Arman
+-->
+# ANTs lineage
 
-* Generic mathematical methods that are tunable for
-application specific domains:  no-free lunch
+## Image mapping and perception: 1877
 
-* Deep testing on multiple platforms ... osx, linux, windows.
+Francis Galton: _Can we see criminality in the face?_
 
-* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )
+![](./figures/galton.png)
 
+_What about syphilis, mental illness?_
+
+<!--
+Notes:
+* Use of "composite portraiture" and what he called "eugenics"
+* Can we see criminality, mental illness, syphilis, and others in facial features?
+* Despite the obvious prejudices driving his research, he was a pioneer.
+-->
+
+<!--
+
+##
+
+![](./background/figures/FrancisGalton2.jpg)
+-->
+
+<!--
+Notes:
+* Another example where he has manually categorized facial features and try to combine them
+* Did not find much---composite tends to blend away to normality.
+-->
+
+##  Speaking of criminality...
+
+_Can we say anything about the U.S. Congress?_
+
+![](./background/figures/congressPersons.png)
+
+__Maybe they should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__
+
+<!--
+Notes:
+-->
+
+##  Image mapping & biology:  1917
+
+D'Arcy Thompson: _Comparison of related forms_
+
+![](./figures/dthompson.png)
+-->
+
+<!--
+Notes:
+* Book: On Growth and Form
+* Descriptive not susceptible to hypothesis testing
+* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
+-->
+
+## Image mapping & biology: Current
+<BR><BR>
+_Look where we are now!_
+<BR><BR>
+![](./background/figures/r16xr85.png)
+
+## ANTs family tree
+
+![](./figures/lineage.jpg)
+
+<!--
+References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
+-->
+
+## Initial scope
+
+![](./figures/ants_initial_scope.png)
+
+<!--
+Notes:
+* Brian work with Murray Grossman
+* First registration paper
+  - WBIR submission
+  - FEM registraiton using B-spline basis functions.
+  - "yeah, that registration is not that good---Jim would not like it."
+-->
+
+# Major tools
+
+## Donoho?
+
+<BR><BR>
+<span style="color:red;">_"Papers are just advertisements for the science."_</red>
+<BR>
+
+<!--
+
+## Symmetric Normalization (SyN)
+
+$\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt + \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2$
+
+![](./papers/figures/fishes.png)
+
+NOtes:
+* Previously discussed Brians work
+* The variant most widely used
+-->
+
+## Diffeomorphisms:  Occam's razor modeling
+
+![](./figures/sillyputty.png)
+
+_differentiable map with differentiable inverse_
+
+## Diffeomoprhisms:  fine-grained and flexible maps
+
+![](./figures/highresdiffeos.jpg)
+
+<!--
+
+## Diffeomorphisms: image parameterization in a metric space
+
+![](./figures/shape_appearance.png)
+-->
+
+## Beyond original SyN
+
+\small
+
+![](./papers/figures/Frontiers_ITK.png)
+
+![](./papers/figures/Frontiers_BSplineSyN.png)
+
+## ```antsRegistration```
+<BR><BR>
+
+```bash
+$ antsRegistration --help
+
+COMMAND:
+     antsRegistration
+          This program is a user-level registration application meant to utilize
+          ITKv4-only classes. The user can specify any number of "stages" where a stage
+          consists of a transform; an image metric; and iterations, shrink factors, and
+          smoothing sigmas for each level.Note that dimensionality, metric, transform,
+          output, convergence, shrink-factors and smoothing-sigmas parameters are
+          mandatory.
+
+OPTIONS:
+     --version
+          Get Version Information.
+
+     -d, --dimensionality 2/3
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, we try to infer the dimensionality from the input image.
+
+     -o, --output outputTransformPrefix
+                  [outputTransformPrefix,<outputWarpedImage>,<outputInverseWarpedImage>]
+          Specify the output transform prefix (output format is .nii.gz ). Optionally, one
+          can choose to warp the moving image to the fixed space and, if the inverse
+          transform exists, one can also output the warped fixed image. Note that only the
+          images specified in the first metric call are warped. Use antsApplyTransforms to
+          warp other images using the resultant transform(s).
+
+     -j, --save-state saveSateAsTransform
+          Specify the output file for the current state of the registration. The state
+          file is written to an hdf5 composite file. It is specially usefull if we want to
+          save the current state of a SyN registration to the disk, so we can load and
+          restore that later to continue the next registration process directly started
+          from the last saved state. The output file of this flag is the same as the
+          write-composite-transform, unless the last transform is a SyN transform. In that
+          case, the inverse displacement field of the SyN transform is also added to the
+          output composite transform. Again notice that this file cannot be treated as a
+          transform, and restore-state option must be used to load the written file by
+          this flag.
+
+     -k, --restore-state restoreStateAsATransform
+          Specify the initial state of the registration which get immediately used to
+          directly initialize the registration process. The flag is mutually exclusive
+          with other intialization flags.If this flag is used, none of the
+          initial-moving-transform and initial-fixed-transform cannot be used.
+
+     -a, --write-composite-transform 1/(0)
+          Boolean specifying whether or not the composite transform (and its inverse, if
+          it exists) should be written to an hdf5 composite file. This is false by default
+          so that only the transform for each stage is written to file.
+          <VALUES>: 0
+
+     -p, --print-similarity-measure-interval <unsignedIntegerValue>
+          Prints out the CC similarity metric measure between the full-size input fixed
+          and the transformed moving images at each iteration a value of 0 (the default)
+          indicates that the full scale computation should not take placeany value greater
+          than 0 represents the interval of full scale metric computation.
+          <VALUES>: 0
+
+     -v, --write-interval-volumes <unsignedIntegerValue>
+          Writes out the output volume at each iteration. It helps to present the
+          registration process as a short movie a value of 0 (the default) indicates that
+          this option should not take placeany value greater than 0 represents the
+          interval between the iterations which outputs are written to the disk.
+          <VALUES>: 0
+
+     -z, --collapse-output-transforms (1)/0
+          Collapse output transforms. Specifically, enabling this option combines all
+          adjacent transforms wherepossible. All adjacent linear transforms are written to
+          disk in the forman itk affine transform (called xxxGenericAffine.mat).
+          Similarly, all adjacent displacement field transforms are combined when written
+          to disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available)).Also, an
+          output composite transform including the collapsed transforms is written to the
+          disk (called outputCollapsed(Inverse)Composite).
+          <VALUES>: 1
+
+     -i, --initialize-transforms-per-stage (1)/0
+          Initialize linear transforms from the previous stage. By enabling this option,
+          the current linear stage transform is directly intialized from the previous
+          stage's linear transform; this allows multiple linear stages to be run where
+          each stage directly updates the estimated linear transform from the previous
+          stage. (e.g. Translation -> Rigid -> Affine).
+          <VALUES>: 0
+
+     -n, --interpolation Linear
+                         NearestNeighbor
+                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]
+                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]
+                         BSpline[<order=3>]
+                         CosineWindowedSinc
+                         WelchWindowedSinc
+                         HammingWindowedSinc
+                         LanczosWindowedSinc
+          Several interpolation options are available in ITK. These have all been made
+          available. Currently the interpolator choice is only used to warp (and possibly
+          inverse warp) the final output image(s).
+
+     -g, --restrict-deformation PxQxR
+          This option allows the user to restrict the optimization of the displacement
+          field, translation, rigid or affine transform on a per-component basis. For
+          example, if one wants to limit the deformation or rotation of 3-D volume to the
+          first two dimensions, this is possible by specifying a weight vector of '1x1x0'
+          for a deformation field or '1x1x0x1x1x0' for a rigid
+          transformation.Low-dimensional restriction only works if there are no preceding
+          transformations.
+
+     -q, --initial-fixed-transform initialTransform
+                                   [initialTransform,<useInverse>]
+                                   [fixedImage,movingImage,initializationFeature]
+          Specify the initial fixed transform(s) which get immediately incorporated into
+          the composite transform. The order of the transforms is stack-esque in that the
+          last transform specified on the command line is the first to be applied. In
+          addition to initialization with ITK transforms, the user can perform an initial
+          translation alignment by specifying the fixed and moving images and selecting an
+          initialization feature. These features include using the geometric center of the
+          images (=0), the image intensities (=1), or the origin of the images (=2).
+
+     -r, --initial-moving-transform initialTransform
+                                    [initialTransform,<useInverse>]
+                                    [fixedImage,movingImage,initializationFeature]
+          Specify the initial moving transform(s) which get immediately incorporated into
+          the composite transform. The order of the transforms is stack-esque in that the
+          last transform specified on the command line is the first to be applied. In
+          addition to initialization with ITK transforms, the user can perform an initial
+          translation alignment by specifying the fixed and moving images and selecting an
+          initialization feature. These features include using the geometric center of the
+          images (=0), the image intensities (=1), or the origin of the images (=2).
+
+     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
+                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
+                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
+                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
+                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
+                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
+                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]
+                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]
+                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]
+                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]
+          These image metrics are available--- CC: ANTS neighborhood cross correlation,
+          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global
+          Correlation. The "metricWeight" variable is used to modulate the per stage
+          weighting of the metrics. The metrics can also employ a sampling strategy
+          defined by a sampling percentage. The sampling strategy defaults to 'None' (aka
+          a dense sampling of one sample per voxel), otherwise it defines a point set over
+          which to optimize the metric. The point set can be on a regular lattice or a
+          random lattice of points slightly perturbed to minimize aliasing artifacts.
+          samplingPercentage defines the fraction of points to select from the domain. In
+          addition, three point set metrics are available: Euclidean (ICP), Point-set
+          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).
+
+     -t, --transform Rigid[gradientStep]
+                     Affine[gradientStep]
+                     CompositeAffine[gradientStep]
+                     Similarity[gradientStep]
+                     Translation[gradientStep]
+                     BSpline[gradientStep,meshSizeAtBaseLevel]
+                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
+                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
+                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]
+                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]
+                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
+                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
+                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]
+                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]
+          Several transform options are available. The gradientStep or learningRate
+          characterizes the gradient descent optimization and is scaled appropriately for
+          each transform using the shift scales estimator. Subsequent parameters are
+          transform-specific and can be determined from the usage. For the B-spline
+          transforms one can also specify the smoothing in terms of spline distance (i.e.
+          knot spacing).
+
+     -c, --convergence MxNxO
+                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]
+          Convergence is determined from the number of iterations per level and is
+          determined by fitting a line to the normalized energy profile of the last N
+          iterations (where N is specified by the window size) and determining the slope
+          which is then compared with the convergence threshold.
+
+     -s, --smoothing-sigmas MxNxO...
+          Specify the sigma of gaussian smoothing at each level. Units are given in terms
+          of voxels ('vox') or physical spacing ('mm'). Example usage is '4x2x1mm' and
+          '4x2x1vox' where no units implies voxel spacing.
+
+     -f, --shrink-factors MxNxO...
+          Specify the shrink factor for the virtual domain (typically the fixed image) at
+          each level.
+
+     -u, --use-histogram-matching
+          Histogram match the images before registration.
+
+     -l, --use-estimate-learning-rate-once
+          turn on the option that lets you estimate the learning rate step size only at
+          the beginning of each level. * useful as a second stage of fine-scale
+          registration.
+
+     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]
+          Winsorize data based on specified quantiles.
+
+     -x, --masks [fixedImageMask,movingImageMask]
+          Image masks to limit voxels considered by the metric.
+
+     --float
+          Use 'float' instead of 'double' for computations.
+          <VALUES>: 0
+
+     -v, --verbose (0)/1
+          Verbose output.
+
+     -h
+          Print the help menu (short version).
+
+     --help
+          Print the help menu. Will also print values used on the current command line
+          call.
 ```
-    An algorithm must use prior knowledge about a problem
-    to do well on that problem
+
+## Template building:  creating the average Joe
+
+![](./papers/figures/template0.jpg)
+
+## "Attractiveness" $\rightarrow$ mental processing?
+
+![](./papers/figures/template1.jpg)
+
+##  What about brains?
+
+![](./papers/figures/template3.jpg)
+
+## Templates facilitate computation
+
+![](./papers/figures/template4.jpg)
+
+## Gender discernibility?
+
+![](./papers/figures/template5.jpg)
+
+## ```antsMultivariateTemplateConstruction2.sh```
+
+```bash
+$ antsMultivariateTemplateConstruction2.sh
+
+Usage:
+
+antsMultivariateTemplateConstruction2.sh -d ImageDimension -o OutputPrefix <other options> <images>
+
+Compulsory arguments (minimal command line requires SGE/PBS cluster, otherwise use -c and
+  -j options):
+
+     -d:  ImageDimension: 2 or 3 (for 2 or 3 dimensional registration of single volume)
+   ImageDimension: 4 (for template generation of time-series data)
+
+     -o:  OutputPrefix; A prefix that is prepended to all output files.
+
+<images>  List of images in the current directory, eg *_t1.nii.gz. Should be at the end
+          of the command.  Optionally, one can specify a .csv or .txt file where each
+          line is the location of the input image.  One can also specify more than
+          one file for each image for multi-modal template construction (e.g. t1 and t2).
+          For the multi-modal case, the templates will be consecutively numbered (e.g.
+          template0.nii.gz, template1.nii.gz, ...).
+
+NB: All images to be added to the template should be in the same directory, and this
+    script should be invoked from that directory.
+
+Optional arguments:
+
+     -a   image statistic used to summarize images (default 1)
+          0 = mean
+          1 = mean of normalized intensities
+          2 = median
+
+     -b:  Backup images and results from all iterations (default = 0):  Boolean to save
+          the transform files, bias corrected, and warped images for each iteration.
+
+     -c:  Control for parallel computation (default 0):
+          0 = run serially
+          1 = SGE qsub
+          2 = use PEXEC (localhost)
+          3 = Apple XGrid
+          4 = PBS qsub
+
+     -e   use single precision ( default 1 )
+
+     -g:  Gradient step size (default 0.25): smaller in magnitude results in more
+          cautious steps.
+
+     -i:  Iteration limit (default 4): iterations of the template construction
+          (Iteration limit)*NumImages registrations.
+
+     -j:  Number of cpu cores to use locally for pexec option (default 2; requires "-c 2")
+
+     -k:  Number of modalities used to construct the template (default 1):  For example,
+          if one wanted to create a multimodal template consisting of T1,T2,and FA
+          components ("-k 3").
+
+     -w:  Modality weights used in the similarity metric (default = 1): specified as
+          e.g. 1x0.5x0.75.
+
+     -q:  Max iterations for each pairwise registration (default = 100x100x70x20):
+          specified in the form ...xJxKxL where
+            J = max iterations at coarsest resolution (here, reduced by power of 2^2)
+            K = middle resolution iterations (here, reduced by power of 2)
+            L = fine resolution iteratioxns (here, full resolution).
+          Finer resolutions take much more time per iteration than coarser resolutions.
+
+     -f:  Shrink factors (default = 6x4x2x1):  Also in the same form as -q max iterations.
+          Needs to have the same number of components.
+
+     -s:  Smoothing factors (default = 3x2x1x0):  Also in the same form as -q max
+          iterations.  Needs to have the same number of components.
+
+     -n:  N4BiasFieldCorrection of moving image: 0 == off, 1 == on (default 1).
+
+     -p:  Commands to prepend to job scripts (e.g., change into appropriate directory, set
+          paths, etc)
+
+     -r:  Do rigid-body registration of inputs before creating template (default 0):
+          0 == off 1 == on. Only useful when you do not have an initial template
+
+     -l:  Use linear image registration stages during the pairwise (template/subject)
+          deformable registration.  Otherwise, registration is limited to SyN or
+          B-spline SyN (see '-t' option).  This is '1' by default.
+
+     -m:  Type of similarity metric used for registration (default = CC):  Options are
+            CC = cross-correlation
+            MI = mutual information
+            MSQ = mean square difference
+            DEMONS = demon's metric
+          A similarity metric per modality can be specified.  If the CC metric is chosen,
+          one can also specify the radius in brackets, e.g. '-m CC[4]'.
+
+     -t:  Type of transformation model used for registration (default = SyN):  Options are
+            SyN = Greedy SyN
+            BSplineSyN = Greedy B-spline SyN
+            TimeVaryingVelocityField = Time-varying velocity field
+            TimeVaryingBSplineVelocityField = Time-varying B-spline velocity field
+
+     -u:  Walltime (default = 20:00:00):  Option for PBS qsub specifying requested time
+          per pairwise registration.
+
+     -v:  Memory limit (default = 8gb):  Option for PBS qsub specifying requested memory
+          per pairwise registration.
+
+     -x:  XGrid arguments (e.g., -x "-p password -h controlhost")
+
+     -y:  Update the template with the full affine transform (default 1). If 0, the rigid
+          component of the affine transform will not be used to update the template. If your
+          template drifts in translation or orientation try -y 0.
+
+     -z:  Use this this volume as the target of all inputs. When not used, the script
+          will create an unbiased starting point by averaging all inputs. Use the full
+          path.
+          For multiple modalities, specify -z modality1.nii.gz -z modality2.nii.gz ...
+          in the same modality order as the input images.
+
+Example:
+
+antsMultivariateTemplateConstruction2.sh -d 3 -i 3 -k 1 -f 4x2x1 -s 2x1x0vox -q 30x20x4 -t SyN  -m CC -c 0 -o MY sub*avg.nii.gz
+
+Multimodal example:
+
+antsMultivariateTemplateConstruction2.sh -d 3 -i 3 -k 2 -f 4x2x1 -s 2x1x0vox -q 30x20x4 -t SyN -z t1.nii.gz -z t2.nii.gz  -m CC -c 0 -o MY templateInput.csv
+
+where templateInput.csv contains
+
+subjectA_t1.nii.gz,subjectA_t2.nii.gz
+subjectB_t1.nii.gz,subjectB_t2.nii.gz
+...
+
+--------------------------------------------------------------------------------------
+ANTS was created by:
+--------------------------------------------------------------------------------------
+Brian B. Avants, Nick Tustison and Gang Song
+Penn Image Computing And Science Laboratory
+University of Pennsylvania
+
+Please reference http://www.ncbi.nlm.nih.gov/pubmed/20851191 when employing this script
+in your studies. A reproducible evaluation of ANTs similarity metric performance in
+brain image registration:
+
+* Avants BB, Tustison NJ, Song G, Cook PA, Klein A, Gee JC. Neuroimage, 2011.
+
+Also see http://www.ncbi.nlm.nih.gov/pubmed/19818860 for more details.
+
+The script has been updated and improved since this publication.
+
+--------------------------------------------------------------------------------------
+Script by Nick Tustison
+--------------------------------------------------------------------------------------
+Apple XGrid support by Craig Stark
+--------------------------------------------------------------------------------------
 ```
@@
 
-## Built on ITK
+## Nonparametric nonuniform intensity normalization (N3)
 
-* image registration framework
+* Developed at the Montreal Neurological Institute (John Sled, 1998)
 
-* many other classes such as:
-    + `itkScalarImageToRGBImageFilter`
-    + `itkLabelOverlapMeauresImageFilter`
-    + `itkBSplineScatteredDataPointSetToImageFilter`
-    + `itkStochasticFractalDimensionImageFilter`
+* Part of the standard preprocessing protocol in large scale projects such as ADNI
 
-## ANTs development philosophy:<br><small>Assimilate the optimal components of other approaches</small>
+* The traditional de facto standard in MRI bias correction
+    + good performance
+    + *public availability*
 
-![](./figures/BorgFirstContact.jpg)
+* Public availability --- set of perl scripts coordinating various C++ programs
 
-_"We are the Borg. Your biological and technological distinctiveness will be added to our own. Resistance is futile."_
-
-## *The Big 5*
-
-* <span style="color:red">image registration</span> (`antsRegistration.cxx`)
-
-* <span style="color:red">bias correction</span> (`N4BiasFieldCorrection.cxx`)
-
-* multivariate template construction (`antsMultivariateTemplateConstruction.sh`)
-
-* multivariate segmentation (`Atropos.cxx`)
-
-* cortical thickness (`KellyKaposki.cxx` and `antsCorticalThickness.sh`)
-
-## *ANTsR*<br>for statistics and visualization
-
-# *ANTs* optimizes mathematically well-defined <span style="color:red;">objective functions</span> guided by <span style="color:red;">prior knowledge</span>  ...
-
-# ... including that of developers, domain experts and other colleagues ...
-
-# plug *your ideas* into our software to gain insight into biomedical data ...
-
-# our strong <span style="color:red;">mathematical and software engineering</span> foundation leads to near limitless opportunities for innovation in a variety of application domains
+* "*Let's incorporate N3 into ANTs!*"
 -->
 
-# *ANTs* and the perils of circularity<br><br>[<small>"*Logical circularity in voxel-based analysis: normalization strategy may induce statistical bias*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/23151955)
+## N3 adoption issues
 
-## *ANTs* and the perils of circularity
+![](./tools/n4/figures/whyN4.png)
 
-![](./philosophy/circularity/figures/escherANTs.png)
+<div align="center"><img src="./tools/n4/figures/whyN4.png" frameborder="0"></img></div>
 
-##
+<!--
 
-![](./philosophy/circularity/figures/voodoo.png)
+## N4
 
-##
+* comparative [evaluation](http://www.ncbi.nlm.nih.gov/pubmed/20378467)
 
-![](./philosophy/circularity/figures/fastForward.png)
+* small spline distances (useful for higher magnet strengths)
 
-##
+* multiresolution
 
-![](./philosophy/circularity/figures/tbss.png)
+* weighted regional mask (used in [`antsAtroposN4.sh`](https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh))
 
-##
+* fast execution times
 
-![](./philosophy/circularity/figures/antsFlavoredTbss1.png)
+* _publicly available_
 
-##
+* tested nightly within the ITK dashboard system
+-->
 
-![](./philosophy/circularity/figures/antsFlavoredTbss2.png)
+## ```N4BiasFieldCorrection```
 
-##
-
-![](./philosophy/circularity/figures/antsFlavoredTbss3.png)
-
-##
-
-![](./philosophy/circularity/figures/antsFlavoredTbss4.png)
-
-##
-
-![](./philosophy/circularity/figures/antsFlavoredTbss5.png)
-
-##
-
-![](./philosophy/circularity/figures/brianEmail.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping1.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping2.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping0.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping4.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping5.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping6.png)
-
-##
-
-![](./philosophy/circularity/figures/sleeping7.png)
-
-##
-
-![](./philosophy/circularity/figures/benefitsOfOpenScience.png)
-
-## Command line help
-
-<font size="5", color="lightgrey">
-```
-$ CreateDTICohort -h
+```bash
+$ N4BiasFieldCorrection --help
 
 COMMAND:
-     CreateDTICohort
+     N4BiasFieldCorrection
+          N4 is a variant of the popular N3 (nonparameteric nonuniform normalization)
+          retrospective bias correction algorithm. Based on the assumption that the
+          corruption of the low frequency bias field can be modeled as a convolution of
+          the intensity histogram by a Gaussian, the basic algorithmic protocol is to
+          iterate between deconvolving the intensity histogram by a Gaussian, remapping
+          the intensities, and then spatially smoothing this result by a B-spline modeling
+          of the bias field itself. The modifications from and improvements obtained over
+          the original N3 algorithm are described in the following paper: N. Tustison et
+          al., N4ITK: Improved N3 Bias Correction, IEEE Transactions on Medical Imaging,
+          29(6):1310-1320, June 2010.
 
 OPTIONS:
-     -d, --image-dimensionality 2/3
-     -a, --dti-atlas inputDTIAtlasFileName
-     -x, --label-mask-image maskImageFileName
-                            lowerThresholdFunction
-     -n, --noise-sigma <noiseSigma=18>
-     -p, --pathology label[<percentageChangeEig1=-0.05>,<percentageChangeAvgEig2andEig3=0.05>,<numberOfVoxels=all or percentageOfvoxels>]
-     -w, --dwi-parameters [B0Image,directionFile,bvalue]
-                          [B0Image,schemeFile]
-     -r, --registered-population textFileWithFileNames.txt
-     -o, --output [outputDirectory,fileNameSeriesRootName,<numberOfControls=10>,<numberOfExperimentals=10>]
+     -d, --image-dimensionality 2/3/4
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, N4 tries to infer the dimensionality from the input image.
+
+     -i, --input-image inputImageFilename
+          A scalar image is expected as input for bias correction. Since N4 log transforms
+          the intensities, negative values or values close to zero should be processed
+          prior to correction.
+
+     -x, --mask-image maskImageFilename
+          If a mask image is specified, the final bias correction is only performed in the
+          mask region. If a weight image is not specified, only intensity values inside
+          the masked region are used during the execution of the algorithm. If a weight
+          image is specified, only the non-zero weights are used in the execution of the
+          algorithm although the mask region defines where bias correction is performed in
+          the final output. Otherwise bias correction occurs over the entire image domain.
+          See also the option description for the weight image.
+
+     -r, --rescale-intensities 0/(1)
+          At each iteration, a new intensity mapping is calculated and applied but there
+          is nothing which constrains the new intensity range to be within certain values.
+          The result is that the range can "drift" from the original at each iteration.
+          This option rescales to the [min,max] range of the original image intensities
+          within the user-specified mask.
+
+     -w, --weight-image weightImageFilename
+          The weight image allows the user to perform a relative weighting of specific
+          voxels during the B-spline fitting. For example, some studies have shown that N3
+          performed on white matter segmentations improves performance. If one has a
+          spatial probability map of the white matter, one can use this map to weight the
+          b-spline fitting towards those voxels which are more probabilistically
+          classified as white matter. See also the option description for the mask image.
+
+     -s, --shrink-factor 1/2/3/4/...
+          Running N4 on large images can be time consuming. To lessen computation time,
+          the input image can be resampled. The shrink factor, specified as a single
+          integer, describes this resampling. Shrink factors <= 4 are commonly used.
+
+     -c, --convergence [<numberOfIterations=50x50x50x50>,<convergenceThreshold=0.0>]
+          Convergence is determined by calculating the coefficient of variation between
+          subsequent iterations. When this value is less than the specified threshold from
+          the previous iteration or the maximum number of iterations is exceeded the
+          program terminates. Multiple resolutions can be specified by using 'x' between
+          the number of iterations at each resolution, e.g. 100x50x50.
+
+     -b, --bspline-fitting [splineDistance,<splineOrder=3>]
+                           [initialMeshResolution,<splineOrder=3>]
+          These options describe the b-spline fitting parameters. The initial b-spline
+          mesh at the coarsest resolution is specified either as the number of elements in
+          each dimension, e.g. 2x2x3 for 3-D images, or it can be specified as a single
+          scalar parameter which describes the isotropic sizing of the mesh elements. The
+          latter option is typically preferred. For each subsequent level, the spline
+          distance decreases in half, or equivalently, the number of mesh elements doubles
+          Cubic splines (order = 3) are typically used.
+
+     -t, --histogram-sharpening [<FWHM=0.15>,<wienerNoise=0.01>,<numberOfHistogramBins=200>]
+          These options describe the histogram sharpening parameters, i.e. the
+          deconvolution step parameters described in the original N3 algorithm. The
+          default values have been shown to work fairly well.
+
+     -o, --output correctedImage
+                  [correctedImage,<biasField>]
+          The output consists of the bias corrected version of the input image.
+          Optionally, one can also output the estimated bias field.
+
+     --version
+          Get Version Information.
+
+     -v, --verbose (0)/1
+          Verbose output.
+
      -h
+          Print the help menu (short version).
+
      --help
+          Print the help menu.
+          <VALUES>: 1
 ```
-</font>
 
-## Which one is not warped?
+<--
+##  Atropos -- cutting the threads of fate
 
-![](./philosophy/circularity/figures/whichOneIsRegistered.png)
+![](./papers/figures/Atropos_deGoya.jpg)
+-->
 
-## _Answer_
+<!--
+Notes:
+* Can we use Suyash's code?
+* What about graph cuts?
+-->
 
-![](./philosophy/circularity/figures/whichOneIsRegistered2.png)
+## Atropos:  flexible code base
 
-##
+"20+ years of development.  <br>_Show me the code!_"
 
-![](./philosophy/circularity/figures/blobs1.png)
+![](./tools/atropos/figures/atropos.png)
 
-##
+## ```Atropos```
 
-![](./philosophy/circularity/figures/blobs2.png)
+```bash
+$ Atropos --help
 
-##
+COMMAND:
+     Atropos
+          A finite mixture modeling (FMM) segmentation approach with possibilities for
+          specifying prior constraints. These prior constraints include the specification
+          of a prior label image, prior probability images (one for each class), and/or an
+          MRF prior to enforce spatial smoothing of the labels. Similar algorithms include
+          FAST and SPM. Reference: Avants BB, Tustison NJ, Wu J, Cook PA, Gee JC. An open
+          source multivariate framework for n-tissue segmentation with evaluation on
+          public data. Neuroinformatics. 2011 Dec;9(4):381-400.
 
-![](./philosophy/circularity/figures/BooksteinReview1.png)
-![](./philosophy/circularity/figures/BooksteinReview2.png)
-![](./philosophy/circularity/figures/BooksteinReview3.png)
+OPTIONS:
+     -d, --image-dimensionality 2/3/4
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, Atropos tries to infer the dimensionality from the first input
+          image.
 
-# ANTs brain morphology<br><br>[<small>"*Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
+     -a, --intensity-image [intensityImage,<adaptiveSmoothingWeight>]
+          One or more scalar images is specified for segmentation using the
+          -a/--intensity-image option. For segmentation scenarios with no prior
+          information, the first scalar image encountered on the command line is used to
+          order labelings such that the class with the smallest intensity signature is
+          class '1' through class 'N' which represents the voxels with the largest
+          intensity values. The optional adaptive smoothing weight parameter is applicable
+          only when using prior label or probability images. This scalar parameter is to
+          be specified between [0,1] which smooths each labeled region separately and
+          modulates the intensity measurement at each voxel in each intensity image
+          between the original intensity and its smoothed counterpart. The smoothness
+          parameters are governed by the -b/--bspline option.
 
-## Cortical thickness studies:
+     -b, --bspline [<numberOfLevels=6>,<initialMeshResolution=1x1x...>,<splineOrder=3>]
+          If the adaptive smoothing weights are > 0, the intensity images are smoothed in
+          calculating the likelihood values. This is to account for subtle intensity
+          differences across the same tissue regions.
+
+     -i, --initialization Random[numberOfClasses]
+                          Otsu[numberOfTissueClasses]
+                          KMeans[numberOfTissueClasses,<clusterCenters(in ascending order and for first intensity image only)>]
+                          PriorProbabilityImages[numberOfTissueClasses,fileSeriesFormat(index=1 to numberOfClasses) or vectorImage,priorWeighting,<priorProbabilityThreshold>]
+                          PriorLabelImage[numberOfTissueClasses,labelImage,priorWeighting]
+          To initialize the FMM parameters, one of the following options must be
+          specified. If one does not have prior label or probability images we recommend
+          using kmeans as it is typically faster than otsu and can be used with
+          multivariate initialization. However, since a Euclidean distance on the inter
+          cluster distances is used, one might have to appropriately scale the additional
+          input images. Random initialization is meant purely for intellectual curiosity.
+          The prior weighting (specified in the range [0,1]) is used to modulate the
+          calculation of the posterior probabilities between the likelihood*mrfprior and
+          the likelihood*mrfprior*prior. For specifying many prior probability images for
+          a multi-label segmentation, we offer a minimize usage option (see -m). With that
+          option one can specify a prior probability threshold in which only those pixels
+          exceeding that threshold are stored in memory.
+
+     -s, --partial-volume-label-set label1xlabel2xlabel3
+          The partial volume estimation option allows one to modelmixtures of classes
+          within single voxels. Atropos currently allows the user to model two class
+          mixtures per partial volume class. The user specifies a set of class labels per
+          partial volume class requested. For example, suppose the user was performing a
+          classic 3-tissue segmentation (csf, gm, wm) using kmeans initialization. Suppose
+          the user also wanted to model the partial voluming effects between csf/gm and
+          gm/wm. The user would specify it using -i kmeans[3] and -s 1x2 -s 2x3. So, for
+          this example, there would be 3 tissue classes and 2 partial volume classes.
+          Optionally,the user can limit partial volume handling to mrf considerations only
+          whereby the output would only be the three tissues.
+
+     --use-partial-volume-likelihoods 1/(0)
+                                      true/(false)
+          The user can specify whether or not to use the partial volume likelihoods, in
+          which case the partial volume class is considered separate from the tissue
+          classes. Alternatively, one can use the MRF only to handle partial volume in
+          which case, partial volume voxels are not considered as separate classes.
+
+     -p, --posterior-formulation Socrates[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
+                                 Plato[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
+                                 Aristotle[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
+                                 Sigmoid[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]]
+          Different posterior probability formulations are possible as are different
+          update options. To guarantee theoretical convergence properties, a proper
+          formulation of the well-known iterated conditional modes (ICM) uses an
+          asynchronous update step modulated by a specified annealing temperature. If one
+          sets the AnnealingTemperature > 1 in the posterior formulation a traditional
+          code set for a proper ICM update will be created. Otherwise, a synchronous
+          update step will take place at each iteration. The annealing temperature, T,
+          converts the posteriorProbability to posteriorProbability^(1/T) over the course
+          of optimization.
+
+     -x, --mask-image maskImageFilename
+          The image mask (which is required) defines the region which is to be labeled by
+          the Atropos algorithm.
+
+     -c, --convergence numberOfIterations
+                       [<numberOfIterations=5>,<convergenceThreshold=0.001>]
+          Convergence is determined by calculating the mean maximum posterior probability
+          over the region of interest at each iteration. When this value decreases or
+          increases less than the specified threshold from the previous iteration or the
+          maximum number of iterations is exceeded the program terminates.
+
+     -k, --likelihood-model Gaussian
+                            HistogramParzenWindows[<sigma=1.0>,<numberOfBins=32>]
+                            ManifoldParzenWindows[<pointSetSigma=1.0>,<evaluationKNeighborhood=50>,<CovarianceKNeighborhood=0>,<kernelSigma=0>]
+                            JointShapeAndOrientationProbability[<shapeSigma=1.0>,<numberOfShapeBins=64>, <orientationSigma=1.0>, <numberOfOrientationBins=32>]
+                            LogEuclideanGaussian
+          Both parametric and non-parametric options exist in Atropos. The Gaussian
+          parametric option is commonly used (e.g. SPM & FAST) where the mean and standard
+          deviation for the Gaussian of each class is calculated at each iteration. Other
+          groups use non-parametric approaches exemplified by option 2. We recommend using
+          options 1 or 2 as they are fairly standard and the default parameters work
+          adequately.
+
+     -m, --mrf [<smoothingFactor=0.3>,<radius=1x1x...>]
+               [<mrfCoefficientImage>,<radius=1x1x...>]
+          Markov random field (MRF) theory provides a general framework for enforcing
+          spatially contextual constraints on the segmentation solution. The default
+          smoothing factor of 0.3 provides a moderate amount of smoothing. Increasing this
+          number causes more smoothing whereas decreasing the number lessens the
+          smoothing. The radius parameter specifies the mrf neighborhood. Different update
+          schemes are possible but only the asynchronous updating has theoretical
+          convergence properties.
+
+     -g, --icm [<useAsynchronousUpdate=1>,<maximumNumberOfICMIterations=1>,<icmCodeImage=''>]
+          Asynchronous updating requires the construction of an ICM code image which is a
+          label image (with labels in the range {1,..,MaximumICMCode}) constructed such
+          that no MRF neighborhood has duplicate ICM code labels. Thus, to update the
+          voxel class labels we iterate through the code labels and, for each code label,
+          we iterate through the image and update the voxel class label that has the
+          corresponding ICM code label. One can print out the ICM code image by specifying
+          an ITK-compatible image filename.
+
+     -r, --use-random-seed 0/(1)
+          Initialize internal random number generator with a random seed. Otherwise,
+          initialize with a constant seed number.
+
+     -o, --output [classifiedImage,<posteriorProbabilityImageFileNameFormat>]
+          The output consists of a labeled image where each voxel in the masked region is
+          assigned a label from 1, 2, ..., N. Optionally, one can also output the
+          posterior probability images specified in the same format as the prior
+          probability images, e.g. posterior%02d.nii.gz (C-style file name formatting).
+
+     -u, --minimize-memory-usage (0)/1
+          By default, memory usage is not minimized, however, if this is needed, the
+          various probability and distance images are calculated on the fly instead of
+          being stored in memory at each iteration. Also, if prior probability images are
+          used, only the non-negligible pixel values are stored in memory.
+          <VALUES>: 0
+
+     -w, --winsorize-outliers BoxPlot[<lowerPercentile=0.25>,<upperPercentile=0.75>,<whiskerLength=1.5>]
+                              GrubbsRosner[<significanceLevel=0.05>,<winsorizingLevel=0.10>]
+          To remove the effects of outliers in calculating the weighted mean and weighted
+          covariance, the user can opt to remove the outliers through the options
+          specified below.
+
+     -e, --use-euclidean-distance (0)/1
+          Given prior label or probability images, the labels are propagated throughout
+          the masked region so that every voxel in the mask is labeled. Propagation is
+          done by using a signed distance transform of the label. Alternatively,
+          propagation of the labels with the fast marching filter respects the distance
+          along the shape of the mask (e.g. the sinuous sulci and gyri of the cortex.
+          <VALUES>: 0
+
+     -l, --label-propagation whichLabel[lambda=0.0,<boundaryProbability=1.0>]
+          The propagation of each prior label can be controlled by the lambda and boundary
+          probability parameters. The latter parameter is the probability (in the range
+          [0,1]) of the label on the boundary which increases linearly to a maximum value
+          of 1.0 in the interior of the labeled region. The former parameter dictates the
+          exponential decay of probability propagation outside the labeled region from the
+          boundary probability, i.e. boundaryProbability*exp( -lambda * distance ).
+
+     -v, --verbose (0)/1
+          Verbose output.
+
+     -h
+          Print the help menu (short version).
+
+     --help
+          Print the help menu.
+          <VALUES>: 1
+```
+
+<!--
+
+## Atropos + N4 $\rightarrow$ `antsAtroposN4.sh`
+
+![](./tools/atropos/figures/atroposFlow.png)
+-->
+
+# Putting it all together---the ANTs cortical thickness pipeline
+
+## Cortical thickness studies
+
 ```{r, results='asis', echo = FALSE}
-conditions <- c( "Huntington’s disease", "schizophrenia", "bipolar disorder",
+conditions <- c( "Tetris-playing ability", "Huntington’s disease", "schizophrenia", "bipolar disorder",
                  "Alzheimer’s disease", "frontotemporal dementia", "Parkinson’s disease",
@@
 
-## *ANTs*-related background
+<!--
+
+## ANTs-related background
 
 * Sandy, Brian, and <span style="color:red;">DiReCT</span>
-  + used other tools such as FMRIB's Automated Segmentation Tool (FAST)
+    + used other tools such as FMRIB Automated Segmentation Tool (FAST)
     + `KellySlater.cxx`
-  * scripts "adequate for Penn data"
+* pipedream scripts "adequate for Penn data."
 * `KellyKapowski.cxx` and `antsCorticalThickness.sh`
@@
 * and, eventually, _"Let's compare with FreeSurfer."_
-
-## The *ANTs* structural brain mapping workflow
-
-![](./evaluation/figures/pipeline.png)
+-->
 
 ## Basic components of the pipeline
-
-<div align="center"><img height="350" src="./evaluation/figures/components.png" frameborder="0"></img></div>
 
@@
 
-<div align="center"><img height="350" src="./evaluation/figures/templates.png" frameborder="0"></img></div>
+![](./evaluation/figures/templates.png)
 
+<!--
 * Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
 * Acquisition and anonymization (e.g. defacing) protocols are often different.
+-->
 
-## Template building (cont.)
+## Template priors
 
-<div align="center"><img height="350" src="./evaluation/figures/templatePriors.png" frameborder="0"></img></div>
+![](./evaluation/figures/templatePriors.png)
 
+<!--
 Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
 to produce auxiliary images which are used for brain extraction and brain segmentation.
+-->
 
-## Brain extraction comparison<br>*ANTs* vs. FreeSurfer
+<!--
 
-<div align="center"><img height="380" src="./evaluation/figures/brainExtraction.png" frameborder="0"></img></div>
+## Brain extraction comparison
+
+![](./evaluation/figures/brainExtraction.png)
 
@@
 the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
+-->
+
+<!--
 
@@
 
-<div align="center"><img height="350" src="./evaluation/figures/brainSegmentation.png" frameborder="0"></img></div>
+![](./evaluation/figures/brainSegmentation.png)
 
-Randomly selected healthy individuals.  Atropos gets good performance across ages.
+Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.
+-->
 
@@
 
-<div align="center"><img height="250" src="./evaluation/figures/corticalThicknessEstimation.png" frameborder="0"></img></div>
+![](./evaluation/figures/corticalThicknessEstimation.png)
 
+<!--
 In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
+-->
 
@@
 
-* Use age and gender (demographic information) in training/prediction paradigm
-* Public data sets (IXI, NKI, Oasis, MMRR)
-* $>$ 1200 subjects, age 7 to over 90 years old
-
-## Prediction from cortical thickness data:<br>gender and age
-
-<div align="center"><img height="350" src="./evaluation/figures/evaluation.png" frameborder="0"></img></div>
-
-## Regional importance <br>comparison
+## Predict age and gender
 
@@
 
-<div align="center"><img height="500" src="./evaluation/figures/antsvfreesurfer_Importance.png" frameborder="0"></img></div>
+## Open science principles
 
-*ANTs* (left) vs. FreeSurfer (right)
+![](./evaluation/figures/ageDistribution.png)
 
-## Regional importance comparison (cont.)
+<!--
+* Public data sets (IXI, NKI, OASIS, MMRR)
+* $>$ 1200 subjects, age 4 to over 94 years old
+-->
 
-<div align="center"><img height="550" src="./evaluation/figures/antsvfreesurfer_regionalPlots.png" frameborder="0"></img></div>
+## Prediction from cortical thickness data
 
-## Cortical thickness extensions
+![](./evaluation/figures/evaluation.png)
+
+## Age prediction per site
+
+![](./evaluation/figures/agePredictionPerSite.png)
+
+## Regional importance comparison
+
+![](./evaluation/figures/antsvfreesurfer_Importance.png)
+
+ANTs (left) vs. FreeSurfer (right)
+
+## Regional measurements
+
+![](./evaluation/figures/antsvfreesurfer_regionalPlots.png)
+
+# But, wait, there's more!
+
+##
+
+[__Data availability__](https://github.com/ntustison/KapowskiChronicles)
+
+*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"  Sure, why not?
+
+*  "_I was wondering if you would make available the CT in each ROI for each subject..._" Sure, why not?  Would you also like the surface areas and volumes?
+
+*  "_Can I have one or more of the templates that you used for your study?_" Would you like the priors as well?
+
+##  What about using both the T1 & T2?
+
+## ANTs tools are multivariate
+
+![](./evaluation/figures/rfRmse05ANTsT1T2.png)
+
+## Arno-thick-in-the-head (ATITH)
+
+_What if we made a crude estimate of the cortical thickness?_
+
+$$thickness_{ROI} = \frac{volume_{ROI}}{area_{ROI}}$$
+
+## Make sure you estimate the [surface area](http://www.insight-journal.org/browse/publication/852) correctly!
+
+![](./evaluation/figures/LabelThickness.png)
+
+## So how does ATITH compare with ANTs, FS?
+
+## Prediction from cortical thickness data
+
+![](./evaluation/figures/atith.png)
+
+## Brain constellation maps
+
+![](./evaluation/figures/brainConstellationMaps.png)
+
+## _Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_
+
+## Contribution from Jose
+
+```bash
+$ DenoiseImage
+
+COMMAND:
+     DenoiseImage
+          Denoise an image using a spatially adaptive filter originally described in J. V.
+          Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive
+          Non-Local Means Denoising of MR Images With Spatially Varying Noise Levels,
+          Journal of Magnetic Resonance Imaging, 31:192-203, June 2010.
+
+OPTIONS:
+     -d, --image-dimensionality 2/3/4
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, the program tries to infer the dimensionality from the input
+          image.
+
+     -i, --input-image inputImageFilename
+          A scalar image is expected as input for noise correction.
+
+     -n, --noise-model (Rician)/Gaussian
+          Employ a Rician or Gaussian noise model.
+
+     -s, --shrink-factor (1)/2/3/...
+          Running noise correction on large images can be time consuming. To lessen
+          computation time, the input image can be resampled. The shrink factor, specified
+          as a single integer, describes this resampling. Shrink factor = 1 is the
+          default.
+
+     -o, --output correctedImage
+                  [correctedImage,<noiseImage>]
+          The output consists of the noise corrected version of the input image.
+          Optionally, one can also output the estimated noise image.
+
+     --version
+          Get Version Information.
+
+     -v, --verbose (0)/1
+          Verbose output.
+
+     -h
+          Print the help menu (short version).
+
+     --help
+          Print the help menu.
+```
+
+## _Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_
+
+![](./evaluation/figures/rfRmseDenoise05.png)
+
+# But the best part is ...
+
+## it is absolutely free!
+
+```bash
+${ANTSPATH}/antsCorticalThickness.sh \
+  -a IXI/T1/IXI002-Guys-0828-T1.nii.gz \
+  -e IXI/template/T_template0.nii.gz \
+  -m IXI/template/T_template0ProbabilityMask.nii.gz \
+  -f IXI/template/T_template0ExtractionMask.nii.gz \
+  -p IXI/template/Priors/priors%d.nii.gz \
+  -o IXI/ANTsResults/IXI002-Guys-0828-
+```
+
+# Joint label/intensity fusion
+
+## Multi-atlas labeling
+
+![](./competitions/figures/NKI30_MALF.png)
+
+## Multi-atlas segmentation
+
+![](./tools/jointfusion/figures/jointLabelFusion.png)
+
+## Multi-atlas 2012 results
+
+![](./competitions/figures/MALF2012.png)
+
+## New work:  joint intensity fusion
+
+![](./tools/jointfusion/figures/jointIntensityFusion.png)
+
+<!--
+
+## Possible uses
+
+* ``Correct'' images
+    * motion correction
+    * lesions
+* Project atlas set intensity signature
+-->

### 2016-07-17 antsr/antsr.Rmd
ENH:  IBM presentation.

# Current work and Advanced Normalization Tools in R (ANTsR)

## Multimodal Brain Tumor Segmentation (BRATS 2013)

![](./competitions/figures/brats2013results2.png)

[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)

## White matter hyperintensities in TBI

![](./wmhs/figures/wmhPipeline.png)

## Social behavior and immunity dysfunction in mice

![](./antsr/figures/filiano_rsfmri.png)

## Other ANTsR work

* [Pediatric template of brain perfusion](http://www.nature.com/articles/sdata20153)

* [Automated segmentation of chronic stroke lesions using LINDA: Lesion identification with neighborhood data analysis](http://www.ncbi.nlm.nih.gov/pubmed/26756101)

* [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/25448483)

* Corrective learning for segmentation refinement

### 2016-07-17 background/background.Rmd
ENH:  IBM presentation.

@@
 
-__Maybe he should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__
+__Maybe they should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__
 
@@
 ![](./figures/dthompson.png)
+-->
 
@@
 * Book: On Growth and Form
-* Descriptive not susceptible to hypothesis testing
+* Descriptive
 * "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
@@
 <!--
-Notes:
-* Book: On Growth and Form
-* Descriptive not susceptible to hypothesis testing
-* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
--->
-
 ## ANTs family tree
@@
 ![](./figures/lineage.jpg)
+-->
 
@@
 
+<!--
 ## Initial scope
@@
 ![](./figures/ants_initial_scope.png)
+-->
 
@@
 -->
-
-## Diffeomorphisms:  Occam's razor modeling
-
-![](./figures/sillyputty.png)
-
-_differentiable map with differentiable inverse_
-
-## Diffeomoprhisms:  fine-grained and flexible maps
-
-![](./figures/highresdiffeos.jpg)
-
-<!--
-... to correct a misconception about diffeomorphisms ...
--->
-
-## Diffeomorphisms: image parameterization in a metric space
-
-![](./figures/shape_appearance.png)

### 2016-07-17 background/people2.Rmd
ENH:  IBM presentation.

--- 2015-05-17 background/people.Rmd
@@
-# Founding developers
+# Developers and collaborators
 
-##
+##  Founders:  Brian and Nick
 
-![](./figures/brian_and_edie_sedgwick.jpg)
-
-<!--
-Notes:
-* Where is this from?
-* Brain--visionary,brilliant.
-* New college in Florida --- degree in Physics and Literature(?)
-* Went to Siemens and got kicked out, fortunately, by ???  "You need to get a doctorate."
-* Jim Gee first graduate student
-* Jim wanted to work on FEM registration
-  - side tangent:  Jim''s notebooks of FEM registration code
--->
-
-##
-
-![](./background/figures/brucelee.png)
-
-<!--
-NOtes:
-* Not much to say
-  - did graduate work at the University of Virginia (hyper. gas lungs)
-  - Washington University in St. Louis (cardiac)
-  - actually bombed interview with Siemens
-  - 2004: Jim offered a job without an interview (long term collaboration)
-  - wrote graph cuts for ITK in a month
--->
-
-##
-<BR><BR>
-
-<div align="center"><img width="1800" src="./figures/brian_and_nick.png" frameborder="0"></img></div>
+![](./figures/brian_and_nick.png)
 
@@
 
-##
+----
 
-![](./figures/antscollab.jpg)
+![](./figures/antsCollaborators2.png)
 

### 2016-07-17 competitions/competitions.Rmd
ENH:  IBM presentation.

@@
+<!--
 # Competitions
+-->
+
+<!--
 
@@
 
+-->
+
 ## International competitions
 
-* [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496)
-* [EMPIRE 2010](http://empire10.isi.uu.nl)
-* [Multi-Atlas Label Challenge 2012](https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page)
-* [SATA Challenge 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events)
-* [BRATS 2013](http://martinos.org/qtim/miccai2013/)
-* [STACOM 2014 MoCo Challenge](http://www.cardiacatlas.org/web/stacom2014/moco-introduction)
+* [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496): MRI brain registration
+
+* [EMPIRE 2010](http://empire10.isi.uu.nl):  CT lung registration
+
+* [Multi-Atlas Label Challenge 2012](https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page):  MRI brain registration and segmentation
+
+* [SATA Challenge 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events): MRI cardiac and canine hind leg registration
+
+* [BRATS 2013](http://martinos.org/qtim/miccai2013/): Multi-modal MRI brain segmentation
+
+* [STACOM 2014 MoCo Challenge](http://www.cardiacatlas.org/web/stacom2014/moco-introduction):  MRI cardiac motion estimation
 
 <!--- ![](./evaluation/figures/evalhistory.png) -->
+
+<!--
 
@@
 
-<!--
 * 14 algorithms
@@
 * developers tune their own algorithms
--->
 
@@
 
-<span style="color:green;">__Results__</span>
-
 ![](./competitions/figures/brats2013results2.png)
 
-Optimal symmetric multimodal templates and concatenated random forests for
-supervised brain tumor segmentation (simplified) with ANTsR, _Neuroinformatics_.
+[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
+supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)
 
@@
 
+-->
+
 <!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->

### 2016-07-17 evaluation/antsvfreesurfer2.Rmd
ENH:  IBM presentation.

@@
----
-title: ANTs brain morphology
-author: Nick (UVa) and Brian (Penn)
-bibliography: REFERENCES.bib
-logo:    figures/antsLogoBase.png
-output:
-  beamer_presentation:
-    colortheme: dolphin
-    fonttheme:  structurebold
-    highlight: tango
-    incremental: yes
-    theme:  AnnArbor
-    includes:
-      in_header: mystyle.tex
-    toc: yes
-  pdf_document:
-    toc: true
-    highlight: zenburn
-  html_document:
-    toc: true
-    theme: readable
-  revealjs_presentation:
-    pandoc_args: [ "--slide-level", "2" ]
-    incremental: true
-    widescreen: true
-    smaller: false
-    theme: night
-    transition: fade
-    highlight: zenburn
-    center: true
-    self_contained: false
-  ioslides_presentation:
-    css: atk.css
-    incremental: false
-    widescreen: true
-    smaller: false
-    fig_width: 5
----
-
-```{r global options, include=FALSE}
-library(rmarkdown)
-library(knitr)
-figpath<-'figures/'
-opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
-               warning=FALSE, message=FALSE)
-```
+# Putting it all together---the ANTs cortical thickness pipeline
 
@@
 
+<!--
+
 ## ANTs-related background
@@
 * and, eventually, _"Let's compare with FreeSurfer."_
+-->
 
@@
 
+<!--
+
 ## Brain extraction comparison
@@
 
-<!--
 Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
@@
 -->
+
+<!--
 
@@
 
-<!--
 Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.
@@
 
-## Cortical thickness estimation
+## Cortical thickness maps
 
@@
 
-<!--
-In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
--->
+In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter,
+*ANTs* diffeomorphically registers the white matter to the combined gray/white matters
+while simultaneously estimating thickness.
 
-## _But without ground truth, how does one evaluate the pipeline?_
+----
+
+_But without ground truth, how does one evaluate the pipeline?_
 
@@
 
-## Open science prinicples
+## Open science principles
 

### 2016-07-17 evaluation/antsvfreesurfer2_extra.Rmd
ENH:  IBM presentation.

@@
 
-##
-
-[__Data availability__](https://github.com/ntustison/KapowskiChronicles)
-
-*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"  Sure, why not?
-
-*  "_I was wondering if you would make available the CT in each ROI for each subject..._" Sure, why not?  Would you also like the surface areas and volumes?
-
-*  "_Can I have one or more of the templates that you used for your study?_" Would you like the priors as well?
-
+<!--
 ##  What about using both the T1 & T2?
+-->
 
@@
 
+<!--
+
 ## Make sure you estimate the [surface area](http://www.insight-journal.org/browse/publication/852) correctly!
@@
 
-## So how does ATITH compare with ANTs, FS?
+-->
 
+<!--
+----
+
+_So how does ATITH compare with ANTs, FS?_
+-->
 ## Prediction from cortical thickness data
@@
 ![](./evaluation/figures/atith.png)
+
+<!--
 
@@
 
-## And currently brewing on the UVa cluster...
-
-_Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_
+## _Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_
 
 ## Contribution from Jose
-
-* ``itkAdaptiveNonLocalMeansDenoisingImageFilter.h``
-
-* ``itkAdaptiveNonLocalMeansDenoisingImageFilter.hxx``
 
@@
 
+## _Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_
+
+![](./evaluation/figures/rfRmseDenoise05.png)
+
+-->
+
+## Longitudinal processing
+
+![](./longitudinal/figures/longitudinalPipeline.png)
+
 # But the best part is ...
 
-## it is absolutely free!
+## it is absolutely ``free''!
 
@@
 
-_(as in speech, not beer)_
+----
 
-## We'll discuss more this afternoon
+[__Data availability__](https://github.com/ntustison/KapowskiChronicles)
 
-https://github.com/ntustison/antsCorticalThicknessExample
+*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"
+Sure, why not?---[Hasan, et al., J Neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/26565394)
+
+*  "_Can I have one or more of the templates that you used for your study?_" Would you like the priors as well?

### 2016-07-17 ibm.Rmd
ENH:  IBM presentation.

--- 2016-07-17 ants2015build.Rmd
@@
 ---
-title: <span style="color:red;">ANTs:</span><br /> A brief retrospective
+title: \`\`Dr. Tustison (UVA) presentation\'\'
+subtitle:
 author: Nick Tustison
 bibliography: REFERENCES.bib
-logo:    figures/antsLogoBase.png
 output:
@@
     colortheme: dolphin
-    fonttheme:  structurebold
+    fonttheme:  professionalfonts
     highlight: tango
-    incremental: yes
+    incremental: false
     theme:  AnnArbor
@@
       in_header: mystyle.tex
-    toc: yes
-  pdf_document:
-    toc: true
-    highlight: zenburn
-  html_document:
-    toc: true
-    theme: readable
-  revealjs_presentation:
-    pandoc_args: [ "--slide-level", "2" ]
-    incremental: true
-    widescreen: true
-    smaller: false
-    theme: night
-    transition: fade
-    highlight: zenburn
-    center: true
-    self_contained: false
-  ioslides_presentation:
-    css: atk.css
-    incremental: false
-    widescreen: true
-    smaller: false
-    fig_width: 5
+ #   toc: yes
+    keep_tex: yes
+    slide_level: 2
 ---
-# Founding developers
-
-##  Brian and Nick
-
-<BR><BR>
+
+# Developers and collaborators
+
+##  Founders:  Brian and Nick
 
@@
 
-## ANTs long term collaborators
-
-![](./figures/antscollab.jpg)
+----
+
+![](./figures/antsCollaborators2.png)
 
@@
 -->
+
+# Why would you care?
+
+<!--
+
+## \`\`Free beer\'\'
+
+![](./licenses/figures/freebeerfreespeech.jpg)
+
+-->
+
+## Software for medical image analysis
+
+* [FSL](http://fsl.fmrib.ox.ac.uk/fsldownloads/)
+
+* [SPM](http://www.fil.ion.ucl.ac.uk/spm/software/)
+
+* [FreeSurfer](http://www.fil.ion.ucl.ac.uk/spm/software/)
+
+* [MIPAV](http://mipav.cit.nih.gov)
+
+* [AFNI](https://afni.nimh.nih.gov/afni)
+
+* Slicer, Elastix, SimpleITK, ANTs $\longleftrightarrow$ [Insight Toolkit](http://www.itk.org)
+
+* Many more at [idoimaging.com](http://idoimaging.com)
+
+<!--
+
+## [FSL](http://fsl.fmrib.ox.ac.uk/fsldownloads/)
+
+> No part of the Software may be reproduced, modified, transmitted or
+> transferred in any form or by any means, electronic or mechanical,
+> without the express permission of the University. The permission of
+> the University is not required if the said reproduction, modification,
+> transmission or transference is done without financial return, ...
+> You may be held legally responsible for any copyright infringement
+> that is caused or encouraged by your failure to abide by these terms
+> and conditions.
+>
+> __You are not permitted under this Licence to use this Software
+> commercially.__
+
+## [SPM](http://www.fil.ion.ucl.ac.uk/spm/software/)
+
+> SPM is free but copyright software, distributed under the terms of
+> the GNU General Public Licence as published by the Free Software
+> Foundation (either version 2, as given in file spm_LICENCE.man,
+> or at your option, any later version). Further details on "copyleft"
+> can be found at http://www.gnu.org/copyleft/. In particular, SPM is
+> supplied as is. No formal support or maintenance is provided or implied.
+
+> "Copyleft" says that anyone who redistributes the software, with or
+> without changes, must pass along the freedom to further copy and change
+> it. Copyleft guarantees that every user has freedom... __it is illegal to
+> distribute the improved version except as free software__...
+
+## [FreeSurfer](http://www.fil.ion.ucl.ac.uk/spm/software/)
+
+> The license granted in this Software License includes without limitation
+> the right to (i) incorporate the Software into proprietary programs
+> (subject to any restrictions applicable to such programs), (ii) add
+> your own copyright statement to your modifications of the Software, and
+> (iii) provide additional or different license terms and conditions in your
+> sublicenses of modifications of the Software; provided that in each case your
+> use, reproduction or distribution of such modifications otherwise complies
+> with the conditions stated in this Software License.
+
+## [ANTs](https://github.com/stnava/ANTs/blob/master/ANTSCopyright.txt)
+
+> Redistribution and use in source and binary forms, with or without
+> modification, are permitted provided that the following conditions
+> are met:
+> 1. _Redistributions of source code must retain the above copyright
+>   notice, this list of conditions and the following disclaimer._
+> 2. _Redistributions in binary form must reproduce the above copyright
+>   notice, this list of conditions and the following disclaimer in the
+>   documentation and/or other materials provided with the distribution._
+> 3. _Neither the name of the consortium nor the names of its contributors
+>  may be used to endorse or promote products derived from this software
+>  without specific prior written permission._
+
+## [ITK](https://itk.org/ITK/project/licenseversion1.html)
+
+> The license of the Insight Toolkit is an open-source Apache 2.0 license. It
+> allows unrestricted use, including use in commercial products.
+> Starting with ITK 4.0, The Insight Toolkit is distributed under the Apache 2.0
+> license approved by the Open Source Initiative (OSI).
+
+-->
+
+<!--
+# Competitions
+-->
+
+<!--
+
+## Algorithmic fight club
+
+![](./competitions/figures/fightclub.jpg)
+
+-->
+
+## International competitions
+
+* [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496): MRI brain registration
+
+* [EMPIRE 2010](http://empire10.isi.uu.nl):  CT lung registration
+
+* [Multi-Atlas Label Challenge 2012](https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page):  MRI brain registration and segmentation
+
+* [SATA Challenge 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events): MRI cardiac and canine hind leg registration
+
+* [BRATS 2013](http://martinos.org/qtim/miccai2013/): Multi-modal MRI brain segmentation
+
+* [STACOM 2014 MoCo Challenge](http://www.cardiacatlas.org/web/stacom2014/moco-introduction):  MRI cardiac motion estimation
+
+<!--- ![](./evaluation/figures/evalhistory.png) -->
+
+<!--
+
+## Klein, NeuroImage 2009
+
+![](./competitions/figures/nihms-130679-f0001.jpg)
+
+* 14 algorithms
+* publicly available data
+* different labeling protocols
+* developers tune their own algorithms
+
+## Klein results
+
+![](./competitions/figures/KleinResults2009.png)
+
+## Take-away message
+
+_"One of the most significant findings of this study is that the relative performances of
+the registration methods under comparison appear to be little affected by the choice of
+subject population, labeling protocol, and type of overlap measure....  ART, SyN, IRTK, and
+SPM's DARTEL Toolbox gave the best results according to overlap and distance measures,
+with ART and SyN delivering the most consistently high accuracy across subjects and label sets."_
+
+## EMPIRE 2010
+
+![](./competitions/figures/EMPIRE10criteria.png)
+
+* Alignment of lung boundaries,
+
+* major fissures,
+
+* annotated landmark pairs, and
+
+* topology of displacement field.
+
+## EMPIRE 2010 results
+
+![](./competitions/figures/EMPIRE10Results.png)
+
+## Multi-atlas 2012
+
+![](./competitions/figures/NKI30_MALF.png)
+
+## Multi-atlas 2012 results
+
+![](./competitions/figures/MALF2012.png)
+
+## SATA 2013
+
+Three very different problem domains
+
+![](./competitions/figures/SATA_data.png)
+
+## BRATS 2013
+
+![](./competitions/figures/brats2013results1.png)
+
+## BRATS 2013 results
+
+![](./competitions/figures/brats2013results2.png)
+
+[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
+supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)
+
+## STACOM 2014
+
+![](./competitions/figures/image_gallery.jpg)
+
+-->
+
+<!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->
 # ANTs lineage
@@
 
+<!--
 ## ANTs family tree
@@
 
-# Major tools
+# Major ANTs utilities
 
@@
 <BR><BR>
-<span style="color:red;">_"Papers are just advertisements for the science."_</red>
+_\`\`Papers are just advertisements for the science.\'\'_
 <BR>
+
+## Neuro tools
+
+![](./tools/figures/coreANtsToolsNeuro.png)
+
+## Pulmonary tools
+
+![](./tools/figures/coreANtsToolsLung.png)
 
@@
 
+<!--
+
 ## Diffeomorphisms:  Occam's razor modeling
@@
 
-## Diffeomoprhisms:  fine-grained and flexible maps
+-->
+
+## Diffeomoprhisms:  differentiable map with diff. inverse
 
@@
 
-## ```antsMultivariateTemplateConstruction2.sh```
+## ```antsMultivariateTemplateConstruction.sh```
 
 ```bash
-$ antsMultivariateTemplateConstruction2.sh
+$ antsMultivariateTemplateConstruction.sh
 
@@
 
-antsMultivariateTemplateConstruction2.sh -d ImageDimension -o OutputPrefix <other options> <images>
-
-Compulsory arguments (minimal command line requires SGE/PBS cluster, otherwise use -c and
-  -j options):
+antsMultivariateTemplateConstruction.sh -d ImageDimension -o OUTPREFIX <other options> <images>
+
+Compulsory arguments (minimal command line requires SGE cluster, otherwise use -c & -j options):
 
@@
 
-     -o:  OutputPrefix; A prefix that is prepended to all output files.
+     -o:  OUTPREFIX; A prefix that is prepended to all output files.
 
@@
 
-NB: All images to be added to the template should be in the same directory, and this
-    script should be invoked from that directory.
+NB: All images to be added to the template should be in the same directory, and this script
+should be invoked from that directory.
 
@@
 
-     -a   image statistic used to summarize images (default 1)
-          0 = mean
-          1 = mean of normalized intensities
-          2 = median
-
-     -b:  Backup images and results from all iterations (default = 0):  Boolean to save
-          the transform files, bias corrected, and warped images for each iteration.
-
-     -c:  Control for parallel computation (default 0):
-          0 = run serially
-          1 = SGE qsub
-          2 = use PEXEC (localhost)
-          3 = Apple XGrid
-          4 = PBS qsub
-
-     -e   use single precision ( default 1 )
-
-     -g:  Gradient step size (default 0.25): smaller in magnitude results in more
-          cautious steps.
-
-     -i:  Iteration limit (default 4): iterations of the template construction
-          (Iteration limit)*NumImages registrations.
-
-     -j:  Number of cpu cores to use locally for pexec option (default 2; requires "-c 2")
-
-     -k:  Number of modalities used to construct the template (default 1):  For example,
-          if one wanted to create a multimodal template consisting of T1,T2,and FA
-          components ("-k 3").
-
-     -w:  Modality weights used in the similarity metric (default = 1): specified as
-          e.g. 1x0.5x0.75.
-
-     -q:  Max iterations for each pairwise registration (default = 100x100x70x20):
-          specified in the form ...xJxKxL where
-            J = max iterations at coarsest resolution (here, reduced by power of 2^2)
-            K = middle resolution iterations (here, reduced by power of 2)
-            L = fine resolution iteratioxns (here, full resolution).
-          Finer resolutions take much more time per iteration than coarser resolutions.
-
-     -f:  Shrink factors (default = 6x4x2x1):  Also in the same form as -q max iterations.
-          Needs to have the same number of components.
-
-     -s:  Smoothing factors (default = 3x2x1x0):  Also in the same form as -q max
-          iterations.  Needs to have the same number of components.
-
-     -n:  N4BiasFieldCorrection of moving image: 0 == off, 1 == on (default 1).
-
-     -p:  Commands to prepend to job scripts (e.g., change into appropriate directory, set
-          paths, etc)
-
-     -r:  Do rigid-body registration of inputs before creating template (default 0):
-          0 == off 1 == on. Only useful when you do not have an initial template
-
-     -l:  Use linear image registration stages during the pairwise (template/subject)
-          deformable registration.  Otherwise, registration is limited to SyN or
-          B-spline SyN (see '-t' option).  This is '1' by default.
-
-     -m:  Type of similarity metric used for registration (default = CC):  Options are
-            CC = cross-correlation
-            MI = mutual information
-            MSQ = mean square difference
-            DEMONS = demon's metric
-          A similarity metric per modality can be specified.  If the CC metric is chosen,
-          one can also specify the radius in brackets, e.g. '-m CC[4]'.
-
-     -t:  Type of transformation model used for registration (default = SyN):  Options are
-            SyN = Greedy SyN
-            BSplineSyN = Greedy B-spline SyN
-            TimeVaryingVelocityField = Time-varying velocity field
-            TimeVaryingBSplineVelocityField = Time-varying B-spline velocity field
-
-     -u:  Walltime (default = 20:00:00):  Option for PBS qsub specifying requested time
-          per pairwise registration.
-
-     -v:  Memory limit (default = 8gb):  Option for PBS qsub specifying requested memory
-          per pairwise registration.
+     -c:  Control for parallel computation (default 1) -- 0 == run serially,  1 == SGE qsub,
+          2 == use PEXEC (localhost), 3 == Apple XGrid, 4 == PBS qsub, 5 == SLURM
+
+     -g:  Gradient step size (default 0.25) -- smaller in magnitude results in more cautious steps
+
+     -i:  Iteration limit (default 4) -- iterations of the template construction (Iteration limit)*NumImages registrations.
+
+     -j:  Number of cpu cores to use (default 2; -- requires "-c 2")
+
+     -k:  Number of modalities used to construct the template (default 1)
+
+     -w:  Modality weights used in the similarity metric (default = 1) --- specified as e.g. 1x0.5x0.75
+
+     -m:  Max-iterations in each registration
+
+     -n:  N4BiasFieldCorrection of moving image (default 1) -- 0 == off, 1 == on
+
+     -p:  Commands to prepend to job scripts (e.g., change into appropriate directory, set paths, etc)
+
+     -r:  Do rigid-body registration of inputs before creating template (default 0) -- 0 == off 1 == on. Only useful when
+          you do not have an initial template
+
+     -s:  Type of similarity metric used for registration.
+
+     -t:  Type of transformation model used for registration.
 
@@
      -z:  Use this this volume as the target of all inputs. When not used, the script
-          will create an unbiased starting point by averaging all inputs. Use the full
-          path.
-          For multiple modalities, specify -z modality1.nii.gz -z modality2.nii.gz ...
-          in the same modality order as the input images.
+          will create an unbiased starting point by averaging all inputs. Use the full path!
+
+     -b:  Boolean for saving iteration output to directories (default = 0).
 
@@
 
-antsMultivariateTemplateConstruction2.sh -d 3 -i 3 -k 1 -f 4x2x1 -s 2x1x0vox -q 30x20x4 -t SyN  -m CC -c 0 -o MY sub*avg.nii.gz
-
-Multimodal example:
-
-antsMultivariateTemplateConstruction2.sh -d 3 -i 3 -k 2 -f 4x2x1 -s 2x1x0vox -q 30x20x4 -t SyN -z t1.nii.gz -z t2.nii.gz  -m CC -c 0 -o MY templateInput.csv
-
-where templateInput.csv contains
-
-subjectA_t1.nii.gz,subjectA_t2.nii.gz
-subjectB_t1.nii.gz,subjectB_t2.nii.gz
-...
+antsMultivariateTemplateConstruction.sh -d 3 -m 30x50x20 -t GR -s CC -c 1 -o MY -z InitialTemplate.nii.gz  *RF*T1x.nii.gz
+
+- In this example 30x50x20 iterations per registration are used for template creation (that is the default)
+- Greedy-SyN and CC are the metrics to guide the mapping.
+- Output is prepended with MY and the initial template is InitialTemplate.nii.gz (optional).
+- The -c option is set to 1, which will result in using the Sun Grid Engine (SGE) to distribute the computation.
+- if you do not have SGE, read the help for multi-core computation on the local machine, or Apple X-grid options.
 
@@
 --------------------------------------------------------------------------------------
-Script by Nick Tustison
+script adapted by N.M. van Strien, http://www.mri-tutorial.com | NTNU MR-Center
+multivariate template adaption by Nick Tustison
 --------------------------------------------------------------------------------------
@@
 
+## ```DenoiseImage``` --- contribution from Jose Manjon
+
+```bash
+$ DenoiseImage --help
+
+COMMAND:
+     DenoiseImage
+          Denoise an image using a spatially adaptive filter originally described in J. V.
+          Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive
+          Non-Local Means Denoising of MR Images With Spatially Varying Noise Levels,
+          Journal of Magnetic Resonance Imaging, 31:192-203, June 2010.
+
+OPTIONS:
+     -d, --image-dimensionality 2/3/4
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, the program tries to infer the dimensionality from the input
+          image.
+
+     -i, --input-image inputImageFilename
+          A scalar image is expected as input for noise correction.
+
+     -n, --noise-model Rician/(Gaussian)
+          Employ a Rician or Gaussian noise model.
+
+     -x, --mask-image maskImageFilename
+          If a mask image is specified, denoising is only performed in the mask region.
+
+     -s, --shrink-factor (1)/2/3/...
+          Running noise correction on large images can be time consuming. To lessen
+          computation time, the input image can be resampled. The shrink factor, specified
+          as a single integer, describes this resampling. Shrink factor = 1 is the
+          default.
+
+     -p, --patch-radius 1
+                        1x1x1
+          Patch radius. Default = 1x1x1
+
+     -r, --search-radius 3
+                         3x3x3
+          Search radius. Default = 3x3x3.
+
+     -o, --output correctedImage
+                  [correctedImage,<noiseImage>]
+          The output consists of the noise corrected version of the input image.
+          Optionally, one can also output the estimated noise image.
+
+     --version
+          Get Version Information.
+
+     -v, --verbose (0)/1
+          Verbose output.
+
+     -h
+          Print the help menu (short version).
+
+     --help
+          Print the help menu.
+          <VALUES>: 1
+
+```
+
+## Multi-atlas segmentation
+
+![](./tools/jointfusion/figures/jointLabelFusion.png)
+
+## New work:  joint intensity fusion
+
+![](./tools/jointfusion/figures/jointIntensityFusion.png)
+
+## Possible uses
+
+* ``Correct'' images
+
+    * motion correction
+
+    * ``remove'' lesions
+
+* Project atlas set intensity signature
+
+* Use in ``corrective learning''
+
+## ```antsJointFusion``` --- contribution from Hongzhi Wang (with some added features)
+
+```bash
+$ antsJointFusion --help
+
+COMMAND:
+     antsJointFusion
+          antsJointFusion is an image fusion algorithm developed by Hongzhi Wang and Paul
+          Yushkevich which won segmentation challenges at MICCAI 2012 and MICCAI 2013. The
+          original label fusion framework was extended to accommodate intensities by Brian
+          Avants. This implementation is based on Paul's original ITK-style implementation
+          and Brian's ANTsR implementation. References include 1) H. Wang, J. W. Suh, S.
+          Das, J. Pluta, C. Craige, P. Yushkevich, Multi-atlas segmentation with joint
+          label fusion IEEE Trans. on Pattern Analysis and Machine Intelligence, 35(3),
+          611-623, 2013. and 2) H. Wang and P. A. Yushkevich, Multi-atlas segmentation
+          with joint label fusion and corrective learning--an open source implementation,
+          Front. Neuroinform., 2013.
+
+OPTIONS:
+     -d, --image-dimensionality 2/3/4
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, the program tries to infer the dimensionality from the input
+          image.
+
+     -t, --target-image targetImage
+                        [targetImageModality0,targetImageModality1,...,targetImageModalityN]
+          The target image (or multimodal target images) assumed to be aligned to a common
+          image domain.
+
+     -g, --atlas-image atlasImage
+                       [atlasImageModality0,atlasImageModality1,...,atlasImageModalityN]
+          The atlas image (or multimodal atlas images) assumed to be aligned to a common
+          image domain.
+
+     -l, --atlas-segmentation atlasSegmentation
+          The atlas segmentation images. For performing label fusion the number of
+          specified segmentations should be identical to the number of atlas image sets.
+
+     -a, --alpha 0.1
+          Regularization term added to matrix Mx for calculating the inverse. Default =
+          0.1
+
+     -b, --beta 2.0
+          Exponent for mapping intensity difference to the joint error. Default = 2.0
+
+     -r, --retain-label-posterior-images (0)/1
+          Retain label posterior probability images. Requires atlas segmentations to be
+          specified. Default = false
+
+     -f, --retain-atlas-voting-images (0)/1
+          Retain atlas voting images. Default = false
+
+     -c, --constrain-nonnegative (0)/1
+          Constrain solution to non-negative weights.
+
+     -p, --patch-radius 2
+                        2x2x2
+          Patch radius for similarity measures. Default = 2x2x2
+
+     -m, --patch-metric (PC)/MSQ
+          Metric to be used in determining the most similar neighborhood patch. Options
+          include Pearson's correlation (PC) and mean squares (MSQ). Default = PC (Pearson
+          correlation).
+
+     -s, --search-radius 3
+                         3x3x3
+                         searchRadiusMap.nii.gz
+          Search radius for similarity measures. Default = 3x3x3. One can also specify an
+          image where the value at the voxel specifies the isotropic search radius at that
+          voxel.
+
+     -e, --exclusion-image label[exclusionImage]
+          Specify an exclusion region for the given label.
+
+     -x, --mask-image maskImageFilename
+          If a mask image is specified, fusion is only performed in the mask region.
+
+     -o, --output labelFusionImage
+                  intensityFusionImageFileNameFormat
+                  [labelFusionImage,intensityFusionImageFileNameFormat,<labelPosteriorProbabilityImageFileNameFormat>,<atlasVotingWeightImageFileNameFormat>]
+          The output is the intensity and/or label fusion image. Additional optional
+          outputs include the label posterior probability images and the atlas voting
+          weight images.
+
+     --version
+          Get version information.
+
+     -v, --verbose (0)/1
+          Verbose output.
+
+     -h
+          Print the help menu (short version).
+
+     --help
+          Print the help menu.
+          <VALUES>: 1
+
+```
+
 # Putting it all together---the ANTs cortical thickness pipeline
@@
 
-<!--
-In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
--->
-
-## _But without ground truth, how does one evaluate the pipeline?_
+In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter,
+*ANTs* diffeomorphically registers the white matter to the combined gray/white matters
+while simultaneously estimating thickness.
+
+----
+
+_But without ground truth, how does one evaluate the pipeline?_
 
@@
 
-## So how does ATITH compare with ANTs, FS?
-
+-->
+
+<!--
+----
+
+_So how does ATITH compare with ANTs, FS?_
+-->
 ## Prediction from cortical thickness data
@@
 
+-->
+
+## Longitudinal processing
+
+![](./longitudinal/figures/longitudinalPipeline.png)
+
 # But the best part is ...
 
-## it is absolutely free!
+## it is absolutely ``free''!
 
@@
 
-# Joint label/intensity fusion
-
-## Multi-atlas labeling
-
-![](./competitions/figures/NKI30_MALF.png)
-
-## Multi-atlas segmentation
-
-![](./tools/jointfusion/figures/jointLabelFusion.png)
-
-## Multi-atlas 2012 results
-
-![](./competitions/figures/MALF2012.png)
-
-## New work:  joint intensity fusion
-
-![](./tools/jointfusion/figures/jointIntensityFusion.png)
-
-<!--
-
-## Possible uses
-
-* ``Correct'' images
-    * motion correction
-    * lesions
-* Project atlas set intensity signature
--->
+----
+
+[__Data availability__](https://github.com/ntustison/KapowskiChronicles)
+
+*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"
+Sure, why not?---[Hasan, et al., J Neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/26565394)
+
+*  "_Can I have one or more of the templates that you used for your study?_" Would you like the priors as well?
+
+# Current work and Advanced Normalization Tools in R (ANTsR)
+
+## Multimodal Brain Tumor Segmentation (BRATS 2013)
+
+![](./competitions/figures/brats2013results2.png)
+
+[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
+supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)
+
+## White matter hyperintensities in TBI
+
+![](./wmhs/figures/wmhPipeline.png)
+
+## Social behavior and immunity dysfunction in mice
+
+![](./antsr/figures/filiano_rsfmri.png)
+
+## Other ANTsR work
+
+* [Pediatric template of brain perfusion](http://www.nature.com/articles/sdata20153)
+
+* [Automated segmentation of chronic stroke lesions using LINDA: Lesion identification with neighborhood data analysis](http://www.ncbi.nlm.nih.gov/pubmed/26756101)
+
+* [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/25448483)
+
+* Corrective learning for segmentation refinement

### 2016-07-17 ibm.tex
ENH:  IBM presentation.

\documentclass[ignorenonframetext,]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usetheme{AnnArbor}
\usecolortheme{dolphin}
\usefonttheme{professionalfonts}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\newif\ifbibliography
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\ImportTok}[1]{{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{{#1}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{{#1}}}}
\newcommand{\BuiltInTok}[1]{{#1}}
\newcommand{\ExtensionTok}[1]{{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}
\usepackage{longtable,booktabs}
\usepackage{caption}
% These lines are needed to make table captions work with longtable:
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight0.8\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

% Prevent slide breaks in the middle of a paragraph:
\widowpenalties 1 10000
\raggedbottom

\AtBeginPart{
  \let\insertpartnumber\relax
  \let\partname\relax
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \let\insertsectionnumber\relax
    \let\sectionname\relax
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \let\insertsubsectionnumber\relax
  \let\subsectionname\relax
  \frame{\subsectionpage}
}

\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% \pgfdeclareimage[width=1cm]{logo}{./figures/monkeyTypewriter.png}
%\logo{\pgfuseimage{logo}}

\institute{University of Virginia}
\definecolor{links}{RGB}{42, 27, 129}
\definecolor{mypink2}{RGB}{219, 48, 122}
%\hypersetup{colorlinks,linkcolor=links,urlcolor=mypink2}
\usefonttheme{professionalfonts}

% \setbeamerfont{note page}{family*=pplx,size=\footnotesize} % Palatino for notes

\setbeamerfont{subtitle}{size=\small}

\definecolor{uvablue}{RGB}{0,85,150}
\definecolor{uvalibraryorange}{RGB}{252,175,23}
\definecolor{uvacream}{RGB}{241,229,199}
\definecolor{uvalightblue}{RGB}{163,220,230}

\setbeamercolor{block body}{bg=green,fg=green}
\setbeamercolor{block body alerted}{bg=green,fg=green}
\setbeamercolor{block body example}{bg=green,fg=green}

\setbeamercolor{caption name}{fg=uvablue}

\setbeamercolor{headline}{fg=uvacream,bg=uvacream}
\setbeamercolor{section}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{frametitle}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{palette primary}{bg=uvalibraryorange,fg=uvablue}
\setbeamercolor{palette secondary}{bg=uvablue,fg=uvablue}
\setbeamercolor{palette tertiary}{bg=uvalibraryorange,fg=uvablue}
\setbeamercolor{palette quarternary}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{palette sidebar primary}{bg=uvalibraryorange,fg=uvablue}
\setbeamercolor{palette sidebar secondary}{fg=uvablue,bg=uvablue}
\setbeamercolor{palette sidebar tertiary}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{palette sidebar quarternary}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{structure}{bg=uvablue}

\useinnertheme{rectangles}

\titlegraphic{\vspace{-7.5mm}\includegraphics[width=0.45\paperwidth]{./figures/monkeyTypewriter.png}}

\title{``Dr.~Tustison (UVA) presentation''}
\author{Nick Tustison}
\date{}

\begin{document}
\frame{\titlepage}

\section{Developers and
collaborators}\label{developers-and-collaborators}

\begin{frame}{Founders: Brian and Nick}

\includegraphics{./figures/brian_and_nick.png}

\end{frame}

\begin{frame}

\includegraphics{./figures/antsCollaborators2.png}

\(+\) \href{http://neuro.debian.net/pkgs/ants.html}{neurodebian},
\href{http://www.slicer.org/}{slicer},
\href{https://github.com/BRAINSia/BRAINSTools}{brainsfit},
\href{http://nipy.sourceforge.net/nipype/}{nipype},
\href{http://www.itk.org}{itk} and more \ldots{}

\end{frame}

\section{Why would you care?}\label{why-would-you-care}

\begin{frame}{Software for medical image analysis}

\begin{itemize}
\item
  \href{http://fsl.fmrib.ox.ac.uk/fsldownloads/}{FSL}
\item
  \href{http://www.fil.ion.ucl.ac.uk/spm/software/}{SPM}
\item
  \href{http://www.fil.ion.ucl.ac.uk/spm/software/}{FreeSurfer}
\item
  \href{http://mipav.cit.nih.gov}{MIPAV}
\item
  \href{https://afni.nimh.nih.gov/afni}{AFNI}
\item
  Slicer, Elastix, SimpleITK, ANTs \(\longleftrightarrow\)
  \href{http://www.itk.org}{Insight Toolkit}
\item
  Many more at \href{http://idoimaging.com}{idoimaging.com}
\end{itemize}

\end{frame}

\begin{frame}{International competitions}

\begin{itemize}
\item
  \href{http://www.ncbi.nlm.nih.gov/pubmed/19195496}{Klein 2009}: MRI
  brain registration
\item
  \href{http://empire10.isi.uu.nl}{EMPIRE 2010}: CT lung registration
\item
  \href{https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page}{Multi-Atlas
  Label Challenge 2012}: MRI brain registration and segmentation
\item
  \href{https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events}{SATA
  Challenge 2013}: MRI cardiac and canine hind leg registration
\item
  \href{http://martinos.org/qtim/miccai2013/}{BRATS 2013}: Multi-modal
  MRI brain segmentation
\item
  \href{http://www.cardiacatlas.org/web/stacom2014/moco-introduction}{STACOM
  2014 MoCo Challenge}: MRI cardiac motion estimation
\end{itemize}

\end{frame}

\section{ANTs lineage}\label{ants-lineage}

\begin{frame}{Image mapping and perception: 1877}

Francis Galton: \emph{Can we see criminality in the face?}

\includegraphics{./figures/galton.png}

\emph{What about syphilis, mental illness?}

\end{frame}

\begin{frame}{Speaking of criminality\ldots{}}

\emph{Can we say anything about the U.S. Congress?}

\includegraphics{./background/figures/congressPersons.png}

\textbf{Maybe they should have used
\href{https://github.com/ntustison/CongressionalFaceTemplates}{ANTs}?}

\end{frame}

\begin{frame}{Image mapping \& biology: 1917}

D'Arcy Thompson: \emph{Comparison of related forms}

\includegraphics{./figures/dthompson.png} --\textgreater{}

\end{frame}

\begin{frame}{Image mapping \& biology: Current}

 \emph{Look where we are now!}
\includegraphics{./background/figures/r16xr85.png}

\end{frame}

\section{Major ANTs utilities}\label{major-ants-utilities}

\begin{frame}{Donoho?}

 \emph{``Papers are just advertisements for the science.''}

\end{frame}

\begin{frame}{Neuro tools}

\includegraphics{./tools/figures/coreANtsToolsNeuro.png}

\end{frame}

\begin{frame}{Pulmonary tools}

\includegraphics{./tools/figures/coreANtsToolsLung.png}

\end{frame}

\begin{frame}{Diffeomoprhisms: differentiable map with diff. inverse}

\includegraphics{./figures/highresdiffeos.jpg}

\end{frame}

\begin{frame}{Beyond original SyN}

\small

\includegraphics{./papers/figures/Frontiers_ITK.png}

\includegraphics{./papers/figures/Frontiers_BSplineSyN.png}

\end{frame}

\begin{frame}[fragile]{\texttt{antsRegistration}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{antsRegistration} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{antsRegistration}
          \KeywordTok{This} \NormalTok{program is a user-level registration application meant to utilize}
          \KeywordTok{ITKv4-only} \NormalTok{classes. The user can specify any number of }\StringTok{"stages"} \NormalTok{where a stage}
          \KeywordTok{consists} \NormalTok{of a transform}\KeywordTok{;} \KeywordTok{an} \NormalTok{image metric}\KeywordTok{;} \KeywordTok{and} \NormalTok{iterations, shrink factors, and}
          \KeywordTok{smoothing} \NormalTok{sigmas for each level.Note that dimensionality, metric, transform,}
          \KeywordTok{output}\NormalTok{, convergence, shrink-factors and smoothing-sigmas parameters are}
          \KeywordTok{mandatory.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{--version}
          \KeywordTok{Get} \NormalTok{Version Information.}

     \KeywordTok{-d}\NormalTok{, --dimensionality 2/3}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, we try to infer the dimensionality from the input image.}

     \KeywordTok{-o}\NormalTok{, --output outputTransformPrefix}
                  \NormalTok{[}\KeywordTok{outputTransformPrefix}\NormalTok{,}\KeywordTok{<}\NormalTok{outputWarpedImage}\KeywordTok{>}\NormalTok{,}\KeywordTok{<}\NormalTok{outputInverseWarpedImage}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{Specify} \NormalTok{the output transform prefix (output format is .nii.gz )}\KeywordTok{.} \KeywordTok{Optionally}\NormalTok{, one}
          \KeywordTok{can} \NormalTok{choose to warp the moving image to the fixed space and, if the inverse}
          \KeywordTok{transform} \NormalTok{exists, one can also output the warped fixed image. Note that only the}
          \KeywordTok{images} \NormalTok{specified in the first metric call are warped. Use antsApplyTransforms to}
          \KeywordTok{warp} \NormalTok{other images using the resultant transform(s)}\KeywordTok{.}

     \KeywordTok{-j}\NormalTok{, --save-state saveSateAsTransform}
          \KeywordTok{Specify} \NormalTok{the output file for the current state of the registration. The state}
          \KeywordTok{file} \NormalTok{is written to an hdf5 composite file. It is specially usefull if we want to}
          \KeywordTok{save} \NormalTok{the current state of a SyN registration to the disk, so we can load and}
          \KeywordTok{restore} \NormalTok{that later to continue the next registration process directly started}
          \KeywordTok{from} \NormalTok{the last saved state. The output file of this flag is the same as the}
          \KeywordTok{write-composite-transform}\NormalTok{, unless the last transform is a SyN transform. In that}
          \KeywordTok{case}\NormalTok{, the inverse displacement field of the SyN transform is also added to the}
          \NormalTok{output composite transform. Again notice that this file cannot be treated as a}
          \NormalTok{transform, and restore-state option must be used to load the written file by}
          \NormalTok{this flag.}

     \NormalTok{-k, --restore-state restoreStateAsATransform}
          \NormalTok{Specify the initial state of the registration which get immediately used to}
          \NormalTok{directly initialize the registration process. The flag is mutually exclusive}
          \NormalTok{with other intialization flags.If this flag is used, none of the}
          \NormalTok{initial-moving-transform and initial-fixed-transform cannot be used.}

     \NormalTok{-a, --write-composite-transform 1/(0)}
          \NormalTok{Boolean specifying whether or not the composite transform (and its inverse, if}
          \NormalTok{it exists) should be written to an hdf5 composite file. This is false by default}
          \NormalTok{so that only the transform for each stage is written to file.}
          \NormalTok{<VALUES>: 0}

     \NormalTok{-p, --print-similarity-measure-interval <unsignedIntegerValue>}
          \NormalTok{Prints out the CC similarity metric measure between the full-size input fixed}
          \NormalTok{and the transformed moving images at each iteration a value of 0 (the default)}
          \NormalTok{indicates that the full scale computation should not take placeany value greater}
          \NormalTok{than 0 represents the interval of full scale metric computation.}
          \NormalTok{<VALUES>: 0}

     \NormalTok{-v, --write-interval-volumes <unsignedIntegerValue>}
          \NormalTok{Writes out the output volume at each iteration. It helps to present the}
          \NormalTok{registration process as a short movie a value of 0 (the default) indicates that}
          \NormalTok{this option should not take placeany value greater than 0 represents the}
          \NormalTok{interval between the iterations which outputs are written to the disk.}
          \NormalTok{<VALUES>: 0}

     \NormalTok{-z, --collapse-output-transforms (1)/0}
          \NormalTok{Collapse output transforms. Specifically, enabling this option combines all}
          \NormalTok{adjacent transforms wherepossible. All adjacent linear transforms are written to}
          \NormalTok{disk}\KeywordTok{ in} \NormalTok{the forman itk affine transform }\KeywordTok{(}\NormalTok{called xxxGenericAffine.mat}\KeywordTok{).}
          \KeywordTok{Similarly}\NormalTok{, all adjacent displacement field transforms are combined when written}
          \KeywordTok{to} \NormalTok{disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available))}\KeywordTok{.Also}\NormalTok{, an}
          \KeywordTok{output} \NormalTok{composite transform including the collapsed transforms is written to the}
          \KeywordTok{disk} \NormalTok{(called outputCollapsed(Inverse)}\KeywordTok{Composite}\NormalTok{)}\KeywordTok{.}
          \KeywordTok{<VALUES>}\NormalTok{: 1}

     \KeywordTok{-i}\NormalTok{, --initialize-transforms-per-stage (1)}\KeywordTok{/0}
          \KeywordTok{Initialize} \NormalTok{linear transforms from the previous stage. By enabling this option,}
          \KeywordTok{the} \NormalTok{current linear stage transform is directly intialized from the previous}
          \KeywordTok{stage}\StringTok{'s linear transform; this allows multiple linear stages to be run where}
\StringTok{          each stage directly updates the estimated linear transform from the previous}
\StringTok{          stage. (e.g. Translation -> Rigid -> Affine).}
\StringTok{          <VALUES>: 0}

\StringTok{     -n, --interpolation Linear}
\StringTok{                         NearestNeighbor}
\StringTok{                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]}
\StringTok{                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]}
\StringTok{                         BSpline[<order=3>]}
\StringTok{                         CosineWindowedSinc}
\StringTok{                         WelchWindowedSinc}
\StringTok{                         HammingWindowedSinc}
\StringTok{                         LanczosWindowedSinc}
\StringTok{          Several interpolation options are available in ITK. These have all been made}
\StringTok{          available. Currently the interpolator choice is only used to warp (and possibly}
\StringTok{          inverse warp) the final output image(s).}

\StringTok{     -g, --restrict-deformation PxQxR}
\StringTok{          This option allows the user to restrict the optimization of the displacement}
\StringTok{          field, translation, rigid or affine transform on a per-component basis. For}
\StringTok{          example, if one wants to limit the deformation or rotation of 3-D volume to the}
\StringTok{          first two dimensions, this is possible by specifying a weight vector of '}\NormalTok{1x1x0}\StringTok{'}
\StringTok{          for a deformation field or '}\NormalTok{1x1x0x1x1x0}\StringTok{' for a rigid}
\StringTok{          transformation.Low-dimensional restriction only works if there are no preceding}
\StringTok{          transformations.}

\StringTok{     -q, --initial-fixed-transform initialTransform}
\StringTok{                                   [initialTransform,<useInverse>]}
\StringTok{                                   [fixedImage,movingImage,initializationFeature]}
\StringTok{          Specify the initial fixed transform(s) which get immediately incorporated into}
\StringTok{          the composite transform. The order of the transforms is stack-esque in that the}
\StringTok{          last transform specified on the command line is the first to be applied. In}
\StringTok{          addition to initialization with ITK transforms, the user can perform an initial}
\StringTok{          translation alignment by specifying the fixed and moving images and selecting an}
\StringTok{          initialization feature. These features include using the geometric center of the}
\StringTok{          images (=0), the image intensities (=1), or the origin of the images (=2).}

\StringTok{     -r, --initial-moving-transform initialTransform}
\StringTok{                                    [initialTransform,<useInverse>]}
\StringTok{                                    [fixedImage,movingImage,initializationFeature]}
\StringTok{          Specify the initial moving transform(s) which get immediately incorporated into}
\StringTok{          the composite transform. The order of the transforms is stack-esque in that the}
\StringTok{          last transform specified on the command line is the first to be applied. In}
\StringTok{          addition to initialization with ITK transforms, the user can perform an initial}
\StringTok{          translation alignment by specifying the fixed and moving images and selecting an}
\StringTok{          initialization feature. These features include using the geometric center of the}
\StringTok{          images (=0), the image intensities (=1), or the origin of the images (=2).}

\StringTok{     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]}
\StringTok{                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]}
\StringTok{                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]}
\StringTok{                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]}
\StringTok{          These image metrics are available--- CC: ANTS neighborhood cross correlation,}
\StringTok{          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global}
\StringTok{          Correlation. The "metricWeight" variable is used to modulate the per stage}
\StringTok{          weighting of the metrics. The metrics can also employ a sampling strategy}
\StringTok{          defined by a sampling percentage. The sampling strategy defaults to '}\NormalTok{None}\StringTok{' (aka}
\StringTok{          a dense sampling of one sample per voxel), otherwise it defines a point set over}
\StringTok{          which to optimize the metric. The point set can be on a regular lattice or a}
\StringTok{          random lattice of points slightly perturbed to minimize aliasing artifacts.}
\StringTok{          samplingPercentage defines the fraction of points to select from the domain. In}
\StringTok{          addition, three point set metrics are available: Euclidean (ICP), Point-set}
\StringTok{          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).}

\StringTok{     -t, --transform Rigid[gradientStep]}
\StringTok{                     Affine[gradientStep]}
\StringTok{                     CompositeAffine[gradientStep]}
\StringTok{                     Similarity[gradientStep]}
\StringTok{                     Translation[gradientStep]}
\StringTok{                     BSpline[gradientStep,meshSizeAtBaseLevel]}
\StringTok{                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]}
\StringTok{                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]}
\StringTok{                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]}
\StringTok{                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]}
\StringTok{                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]}
\StringTok{                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]}
\StringTok{                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]}
\StringTok{                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]}
\StringTok{          Several transform options are available. The gradientStep or learningRate}
\StringTok{          characterizes the gradient descent optimization and is scaled appropriately for}
\StringTok{          each transform using the shift scales estimator. Subsequent parameters are}
\StringTok{          transform-specific and can be determined from the usage. For the B-spline}
\StringTok{          transforms one can also specify the smoothing in terms of spline distance (i.e.}
\StringTok{          knot spacing).}

\StringTok{     -c, --convergence MxNxO}
\StringTok{                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]}
\StringTok{          Convergence is determined from the number of iterations per level and is}
\StringTok{          determined by fitting a line to the normalized energy profile of the last N}
\StringTok{          iterations (where N is specified by the window size) and determining the slope}
\StringTok{          which is then compared with the convergence threshold.}

\StringTok{     -s, --smoothing-sigmas MxNxO...}
\StringTok{          Specify the sigma of gaussian smoothing at each level. Units are given in terms}
\StringTok{          of voxels ('}\NormalTok{vox}\StringTok{') or physical spacing ('}\NormalTok{mm}\StringTok{'). Example usage is '}\NormalTok{4x2x1mm}\StringTok{' and}
\StringTok{          '}\NormalTok{4x2x1vox}\StringTok{' where no units implies voxel spacing.}

\StringTok{     -f, --shrink-factors MxNxO...}
\StringTok{          Specify the shrink factor for the virtual domain (typically the fixed image) at}
\StringTok{          each level.}

\StringTok{     -u, --use-histogram-matching}
\StringTok{          Histogram match the images before registration.}

\StringTok{     -l, --use-estimate-learning-rate-once}
\StringTok{          turn on the option that lets you estimate the learning rate step size only at}
\StringTok{          the beginning of each level. * useful as a second stage of fine-scale}
\StringTok{          registration.}

\StringTok{     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]}
\StringTok{          Winsorize data based on specified quantiles.}

\StringTok{     -x, --masks [fixedImageMask,movingImageMask]}
\StringTok{          Image masks to limit voxels considered by the metric.}

\StringTok{     --float}
\StringTok{          Use '}\NormalTok{float}\StringTok{' instead of '}\NormalTok{double}\StringTok{' for computations.}
\StringTok{          <VALUES>: 0}

\StringTok{     -v, --verbose (0)/1}
\StringTok{          Verbose output.}

\StringTok{     -h}
\StringTok{          Print the help menu (short version).}

\StringTok{     --help}
\StringTok{          Print the help menu. Will also print values used on the current command line}
\StringTok{          call.}
\end{Highlighting}
\end{Shaded}

\end{frame}

\begin{frame}{Template building: creating the average Joe}

\includegraphics{./papers/figures/template0.jpg}

\end{frame}

\begin{frame}{``Attractiveness'' \(\rightarrow\) mental processing?}

\includegraphics{./papers/figures/template1.jpg}

\end{frame}

\begin{frame}{What about brains?}

\includegraphics{./papers/figures/template3.jpg}

\end{frame}

\begin{frame}{Templates facilitate computation}

\includegraphics{./papers/figures/template4.jpg}

\end{frame}

\begin{frame}{Gender discernibility?}

\includegraphics{./papers/figures/template5.jpg}

\end{frame}

\begin{frame}[fragile]{\texttt{antsMultivariateTemplateConstruction.sh}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{antsMultivariateTemplateConstruction.sh}

\KeywordTok{Usage}\NormalTok{:}

\KeywordTok{antsMultivariateTemplateConstruction.sh} \NormalTok{-d ImageDimension -o OUTPREFIX }\KeywordTok{<}\NormalTok{other options}\KeywordTok{>} \KeywordTok{<}\NormalTok{images}\KeywordTok{>}

\KeywordTok{Compulsory} \NormalTok{arguments (minimal command line requires SGE cluster, otherwise use -c }\KeywordTok{&} \KeywordTok{-j} \NormalTok{options)}\KeywordTok{:}

     \KeywordTok{-d}\NormalTok{:  ImageDimension: 2 or 3 (for 2 or 3 dimensional registration of single volume)}
   \KeywordTok{ImageDimension}\NormalTok{: 4 (for template generation of time-series data)}

     \KeywordTok{-o}\NormalTok{:  OUTPREFIX}\KeywordTok{;} \KeywordTok{A} \NormalTok{prefix that is prepended to all output files.}

\KeywordTok{<images>}  \NormalTok{List of images in the current directory, eg *_t1.nii.gz. Should be at the end}
          \KeywordTok{of} \NormalTok{the command.  Optionally, one can specify a .csv or .txt file where each}
          \KeywordTok{line} \NormalTok{is the location of the input image.  One can also specify more than}
          \KeywordTok{one} \NormalTok{file for each image for multi-modal template construction (e.g. t1 and t2)}\KeywordTok{.}
          \KeywordTok{For} \NormalTok{the multi-modal case, the templates will be consecutively numbered (e.g.}
          \KeywordTok{template0.nii.gz}\NormalTok{, template1.nii.gz, ...)}\KeywordTok{.}

\KeywordTok{NB}\NormalTok{: All images to be added to the template should be in the same directory, and this script}
\KeywordTok{should} \NormalTok{be invoked from that directory.}

\KeywordTok{Optional} \NormalTok{arguments:}

     \KeywordTok{-c}\NormalTok{:  Control for parallel computation (default 1) }\KeywordTok{--} \NormalTok{0 == run serially,  1 == SGE qsub,}
          \KeywordTok{2} \NormalTok{== use PEXEC (localhost), }\KeywordTok{3} \NormalTok{== Apple XGrid, 4 == PBS qsub, 5 == SLURM}

     \KeywordTok{-g}\NormalTok{:  Gradient step size (default 0.25) }\KeywordTok{--} \NormalTok{smaller in magnitude results in more cautious steps}

     \KeywordTok{-i}\NormalTok{:  Iteration limit (default 4) }\KeywordTok{--} \NormalTok{iterations of the template construction (Iteration limit)}\KeywordTok{*NumImages} \NormalTok{registrations.}

     \KeywordTok{-j}\NormalTok{:  Number of cpu cores to use (default 2}\KeywordTok{;} \KeywordTok{--} \NormalTok{requires }\StringTok{"-c 2"}\NormalTok{)}

     \KeywordTok{-k}\NormalTok{:  Number of modalities used to construct the template (default 1)}

     \KeywordTok{-w}\NormalTok{:  Modality weights used in the similarity metric (default = 1) }\KeywordTok{---} \NormalTok{specified as e.g. 1x0.5x0.75}

     \KeywordTok{-m}\NormalTok{:  Max-iterations in each registration}

     \KeywordTok{-n}\NormalTok{:  N4BiasFieldCorrection of moving image (default 1) }\KeywordTok{--} \NormalTok{0 == off, 1 == on}

     \KeywordTok{-p}\NormalTok{:  Commands to prepend to job scripts (e.g., change into appropriate directory, set paths, etc)}

     \KeywordTok{-r}\NormalTok{:  Do rigid-body registration of inputs before creating template (default 0) }\KeywordTok{--} \NormalTok{0 == off 1 == on. Only useful when}
          \KeywordTok{you} \NormalTok{do not have an initial template}

     \KeywordTok{-s}\NormalTok{:  Type of similarity metric used for registration.}

     \KeywordTok{-t}\NormalTok{:  Type of transformation model used for registration.}

     \KeywordTok{-x}\NormalTok{:  XGrid arguments (e.g., -x }\StringTok{"-p password -h controlhost"}\NormalTok{)}

     \KeywordTok{-y}\NormalTok{:  Update the template with the full affine transform (default 1)}\KeywordTok{.} \KeywordTok{If} \NormalTok{0, the rigid}
          \KeywordTok{component} \NormalTok{of the affine transform will not be used to update the template. If your}
          \KeywordTok{template} \NormalTok{drifts in translation or orientation try -y 0.}

     \KeywordTok{-z}\NormalTok{:  Use this this volume as the target of all inputs. When not used, the script}
          \KeywordTok{will} \NormalTok{create an unbiased starting point by averaging all inputs. Use the full path!}

     \KeywordTok{-b}\NormalTok{:  Boolean for saving iteration output to directories (default = 0)}\KeywordTok{.}

\KeywordTok{Example}\NormalTok{:}

\KeywordTok{antsMultivariateTemplateConstruction.sh} \NormalTok{-d 3 -m 30x50x20 -t GR -s CC -c 1 -o MY -z InitialTemplate.nii.gz  *RF*T1x.nii.gz}

\KeywordTok{-} \NormalTok{In this example 30x50x20 iterations per registration are used for template creation (that is the default)}
\KeywordTok{-} \NormalTok{Greedy-SyN and CC are the metrics to guide the mapping.}
\KeywordTok{-} \NormalTok{Output is prepended with MY and the initial template is InitialTemplate.nii.gz (optional)}\KeywordTok{.}
\KeywordTok{-} \NormalTok{The -c option is set to 1, which will result in using the Sun Grid Engine (SGE) }\KeywordTok{to} \NormalTok{distribute the computation.}
\KeywordTok{-} \NormalTok{if you do not have SGE, read the help for multi-core computation on the local machine, or Apple X-grid options.}

\KeywordTok{--------------------------------------------------------------------------------------}
\KeywordTok{ANTS} \NormalTok{was created by:}
\KeywordTok{--------------------------------------------------------------------------------------}
\KeywordTok{Brian} \NormalTok{B. Avants, Nick Tustison and Gang Song}
\KeywordTok{Penn} \NormalTok{Image Computing And Science Laboratory}
\KeywordTok{University} \NormalTok{of Pennsylvania}

\KeywordTok{Please} \NormalTok{reference http://www.ncbi.nlm.nih.gov/pubmed/20851191 when employing this script}
\KeywordTok{in} \KeywordTok{your} \NormalTok{studies. A reproducible evaluation of ANTs similarity metric performance in}
\KeywordTok{brain} \NormalTok{image registration:}

\KeywordTok{*} \NormalTok{Avants BB, Tustison NJ, Song G, Cook PA, Klein A, Gee JC. Neuroimage, 2011.}

\KeywordTok{Also} \NormalTok{see http://www.ncbi.nlm.nih.gov/pubmed/19818860 for more details.}

\KeywordTok{The} \NormalTok{script has been updated and improved since this publication.}

\KeywordTok{--------------------------------------------------------------------------------------}
\KeywordTok{script} \NormalTok{adapted by N.M. van Strien, http://www.mri-tutorial.com }\KeywordTok{|} \KeywordTok{NTNU} \NormalTok{MR-Center}
\KeywordTok{multivariate} \NormalTok{template adaption by Nick Tustison}
\KeywordTok{--------------------------------------------------------------------------------------}
\KeywordTok{Apple} \NormalTok{XGrid support by Craig Stark}
\KeywordTok{--------------------------------------------------------------------------------------}
\end{Highlighting}
\end{Shaded}

\end{frame}

\begin{frame}{N3 adoption issues}

\includegraphics{./tools/n4/figures/whyN4.png}

\end{frame}

\begin{frame}[fragile]{\texttt{N4BiasFieldCorrection}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{N4BiasFieldCorrection} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{N4BiasFieldCorrection}
          \KeywordTok{N4} \NormalTok{is a variant of the popular N3 (nonparameteric nonuniform normalization)}
          \KeywordTok{retrospective} \NormalTok{bias correction algorithm. Based on the assumption that the}
          \KeywordTok{corruption} \NormalTok{of the low frequency bias field can be modeled as a convolution of}
          \KeywordTok{the} \NormalTok{intensity histogram by a Gaussian, the basic algorithmic protocol is to}
          \KeywordTok{iterate} \NormalTok{between deconvolving the intensity histogram by a Gaussian, remapping}
          \KeywordTok{the} \NormalTok{intensities, and then spatially smoothing this result by a B-spline modeling}
          \KeywordTok{of} \NormalTok{the bias field itself. The modifications from and improvements obtained over}
          \KeywordTok{the} \NormalTok{original N3 algorithm are described in the following paper: N. Tustison et}
          \KeywordTok{al.}\NormalTok{, N4ITK: Improved N3 Bias Correction, IEEE Transactions on Medical Imaging,}
          \KeywordTok{29}\NormalTok{(6):}\KeywordTok{1310-1320}\NormalTok{, June 2010.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, N4 tries to infer the dimensionality from the input image.}

     \KeywordTok{-i}\NormalTok{, --input-image inputImageFilename}
          \KeywordTok{A} \NormalTok{scalar image is expected as input for bias correction. Since N4 log transforms}
          \KeywordTok{the} \NormalTok{intensities, negative values or values close to zero should be processed}
          \KeywordTok{prior} \NormalTok{to correction.}

     \KeywordTok{-x}\NormalTok{, --mask-image maskImageFilename}
          \KeywordTok{If} \NormalTok{a mask image is specified, the final bias correction is only performed in the}
          \KeywordTok{mask} \NormalTok{region. If a weight image is not specified, only intensity values inside}
          \KeywordTok{the} \NormalTok{masked region are used during the execution of the algorithm. If a weight}
          \KeywordTok{image} \NormalTok{is specified, only the non-zero weights are used in the execution of the}
          \KeywordTok{algorithm} \NormalTok{although the mask region defines where bias correction is performed in}
          \KeywordTok{the} \NormalTok{final output. Otherwise bias correction occurs over the entire image domain.}
          \KeywordTok{See} \NormalTok{also the option description for the weight image.}

     \KeywordTok{-r}\NormalTok{, --rescale-intensities 0/(1)}
          \KeywordTok{At} \NormalTok{each iteration, a new intensity mapping is calculated and applied but there}
          \KeywordTok{is} \NormalTok{nothing which constrains the new intensity range to be within certain values.}
          \KeywordTok{The} \NormalTok{result is that the range can }\StringTok{"drift"} \NormalTok{from the original at each iteration.}
          \KeywordTok{This} \NormalTok{option rescales to the [min,max] range of the original image intensities}
          \KeywordTok{within} \NormalTok{the user-specified mask.}

     \KeywordTok{-w}\NormalTok{, --weight-image weightImageFilename}
          \KeywordTok{The} \NormalTok{weight image allows the user to perform a relative weighting of specific}
          \KeywordTok{voxels} \NormalTok{during the B-spline fitting. For example, some studies have shown that N3}
          \KeywordTok{performed} \NormalTok{on white matter segmentations improves performance. If one has a}
          \KeywordTok{spatial} \NormalTok{probability map of the white matter, one can use this map to weight the}
          \KeywordTok{b-spline} \NormalTok{fitting towards those voxels which are more probabilistically}
          \KeywordTok{classified} \NormalTok{as white matter. See also the option description for the mask image.}

     \KeywordTok{-s}\NormalTok{, --shrink-factor 1/2/3/4/...}
          \KeywordTok{Running} \NormalTok{N4 on large images can be time consuming. To lessen computation time,}
          \KeywordTok{the} \NormalTok{input image can be resampled. The shrink factor, specified as a single}
          \KeywordTok{integer}\NormalTok{, describes this resampling. Shrink factors }\KeywordTok{<}\NormalTok{= 4 are commonly used.}

     \KeywordTok{-c}\NormalTok{, --convergence [}\KeywordTok{<}\NormalTok{numberOfIterations=50x50x50x}\KeywordTok{50>}\NormalTok{,}\KeywordTok{<}\NormalTok{convergenceThreshold=0.}\KeywordTok{0>}\NormalTok{]}
          \KeywordTok{Convergence} \NormalTok{is determined by calculating the coefficient of variation between}
          \KeywordTok{subsequent} \NormalTok{iterations. When this value is less than the specified threshold from}
          \KeywordTok{the} \NormalTok{previous iteration or the maximum number of iterations is exceeded the}
          \KeywordTok{program} \NormalTok{terminates. Multiple resolutions can be specified by using }\StringTok{'x'} \NormalTok{between}
          \KeywordTok{the} \NormalTok{number of iterations at each resolution, e.g. 100x50x50.}

     \KeywordTok{-b}\NormalTok{, --bspline-fitting [splineDistance,}\KeywordTok{<}\NormalTok{splineOrder=}\KeywordTok{3>}\NormalTok{]}
                           \NormalTok{[}\KeywordTok{initialMeshResolution}\NormalTok{,}\KeywordTok{<}\NormalTok{splineOrder=}\KeywordTok{3>}\NormalTok{]}
          \KeywordTok{These} \NormalTok{options describe the b-spline fitting parameters. The initial b-spline}
          \KeywordTok{mesh} \NormalTok{at the coarsest resolution is specified either as the number of elements in}
          \KeywordTok{each} \NormalTok{dimension, e.g. 2x2x3 for 3-D images, or it can be specified as a single}
          \KeywordTok{scalar} \NormalTok{parameter which describes the isotropic sizing of the mesh elements. The}
          \KeywordTok{latter} \NormalTok{option is typically preferred. For each subsequent level, the spline}
          \KeywordTok{distance} \NormalTok{decreases in half, or equivalently, the number of mesh elements doubles}
          \KeywordTok{Cubic} \NormalTok{splines (order = 3) }\KeywordTok{are} \NormalTok{typically used.}

     \KeywordTok{-t}\NormalTok{, --histogram-sharpening [}\KeywordTok{<}\NormalTok{FWHM=0.}\KeywordTok{15>}\NormalTok{,}\KeywordTok{<}\NormalTok{wienerNoise=0.}\KeywordTok{01>}\NormalTok{,}\KeywordTok{<}\NormalTok{numberOfHistogramBins=}\KeywordTok{200>}\NormalTok{]}
          \KeywordTok{These} \NormalTok{options describe the histogram sharpening parameters, i.e. the}
          \KeywordTok{deconvolution} \NormalTok{step parameters described in the original N3 algorithm. The}
          \KeywordTok{default} \NormalTok{values have been shown to work fairly well.}

     \KeywordTok{-o}\NormalTok{, --output correctedImage}
                  \NormalTok{[}\KeywordTok{correctedImage}\NormalTok{,}\KeywordTok{<}\NormalTok{biasField}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{The} \NormalTok{output consists of the bias corrected version of the input image.}
          \KeywordTok{Optionally}\NormalTok{, one can also output the estimated bias field.}

     \KeywordTok{--version}
          \KeywordTok{Get} \NormalTok{Version Information.}

     \KeywordTok{-v}\NormalTok{, --verbose (0)}\KeywordTok{/1}
          \KeywordTok{Verbose} \NormalTok{output.}

     \KeywordTok{-h}
          \KeywordTok{Print} \NormalTok{the help menu (short version)}\KeywordTok{.}

     \KeywordTok{--help}
          \KeywordTok{Print} \NormalTok{the help menu.}
          \KeywordTok{<VALUES>}\NormalTok{: 1}
\end{Highlighting}
\end{Shaded}

\textless{}-- \#\# Atropos -- cutting the threads of fate

\includegraphics{./papers/figures/Atropos_deGoya.jpg} --\textgreater{}

\end{frame}

\begin{frame}{Atropos: flexible code base}

``20+ years of development. \emph{Show me the code!}''

\includegraphics{./tools/atropos/figures/atropos.png}

\end{frame}

\begin{frame}[fragile]{\texttt{Atropos}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{Atropos} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{Atropos}
          \KeywordTok{A} \NormalTok{finite mixture modeling (FMM) }\KeywordTok{segmentation} \NormalTok{approach with possibilities for}
          \KeywordTok{specifying} \NormalTok{prior constraints. These prior constraints include the specification}
          \KeywordTok{of} \NormalTok{a prior label image, prior probability images (one for each class), }\KeywordTok{and/or} \NormalTok{an}
          \KeywordTok{MRF} \NormalTok{prior to enforce spatial smoothing of the labels. Similar algorithms include}
          \KeywordTok{FAST} \NormalTok{and SPM. Reference: Avants BB, Tustison NJ, Wu J, Cook PA, Gee JC. An open}
          \KeywordTok{source} \NormalTok{multivariate framework for n-tissue segmentation with evaluation on}
          \KeywordTok{public} \NormalTok{data. Neuroinformatics. 2011 Dec}\KeywordTok{;9}\NormalTok{(4):}\KeywordTok{381-400.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, Atropos tries to infer the dimensionality from the first input}
          \KeywordTok{image.}

     \KeywordTok{-a}\NormalTok{, --intensity-image [intensityImage,}\KeywordTok{<}\NormalTok{adaptiveSmoothingWeight}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{One} \NormalTok{or more scalar images is specified for segmentation using the}
          \KeywordTok{-a/--intensity-image} \NormalTok{option. For segmentation scenarios with no prior}
          \KeywordTok{information}\NormalTok{, the first scalar image encountered on the command line is used to}
          \KeywordTok{order} \NormalTok{labelings such that the class with the smallest intensity signature is}
          \KeywordTok{class} \StringTok{'1'} \NormalTok{through class }\StringTok{'N'} \NormalTok{which represents the voxels with the largest}
          \KeywordTok{intensity} \NormalTok{values. The optional adaptive smoothing weight parameter is applicable}
          \KeywordTok{only} \NormalTok{when using prior label or probability images. This scalar parameter is to}
          \KeywordTok{be} \NormalTok{specified between [0,1] which smooths each labeled region separately and}
          \KeywordTok{modulates} \NormalTok{the intensity measurement at each voxel in each intensity image}
          \KeywordTok{between} \NormalTok{the original intensity and its smoothed counterpart. The smoothness}
          \KeywordTok{parameters} \NormalTok{are governed by the -b/--bspline option.}

     \KeywordTok{-b}\NormalTok{, --bspline [}\KeywordTok{<}\NormalTok{numberOfLevels=}\KeywordTok{6>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialMeshResolution=1x1x...}\KeywordTok{>}\NormalTok{,}\KeywordTok{<}\NormalTok{splineOrder=}\KeywordTok{3>}\NormalTok{]}
          \KeywordTok{If} \NormalTok{the adaptive smoothing weights are }\KeywordTok{>} \NormalTok{0, the intensity images are smoothed in}
          \KeywordTok{calculating} \NormalTok{the likelihood values. This is to account for subtle intensity}
          \KeywordTok{differences} \NormalTok{across the same tissue regions.}

     \KeywordTok{-i}\NormalTok{, --initialization Random[numberOfClasses]}
                          \KeywordTok{Otsu}\NormalTok{[numberOfTissueClasses]}
                          \KeywordTok{KMeans}\NormalTok{[numberOfTissueClasses,}\KeywordTok{<}\NormalTok{clusterCenters(in ascending order and for first intensity image only)}\KeywordTok{>}\NormalTok{]}
                          \KeywordTok{PriorProbabilityImages}\NormalTok{[numberOfTissueClasses,fileSeriesFormat(index=1 to numberOfClasses) }\KeywordTok{or} \NormalTok{vectorImage,priorWeighting,}\KeywordTok{<}\NormalTok{priorProbabilityThreshold}\KeywordTok{>}\NormalTok{]}
                          \KeywordTok{PriorLabelImage}\NormalTok{[numberOfTissueClasses,labelImage,priorWeighting]}
          \KeywordTok{To} \NormalTok{initialize the FMM parameters, one of the following options must be}
          \KeywordTok{specified.} \NormalTok{If one does not have prior label or probability images we recommend}
          \KeywordTok{using} \NormalTok{kmeans as it is typically faster than otsu and can be used with}
          \KeywordTok{multivariate} \NormalTok{initialization. However, since a Euclidean distance on the inter}
          \KeywordTok{cluster} \NormalTok{distances is used, one might have to appropriately scale the additional}
          \KeywordTok{input} \NormalTok{images. Random initialization is meant purely for intellectual curiosity.}
          \KeywordTok{The} \NormalTok{prior weighting (specified in the range [0,1]) }\KeywordTok{is} \NormalTok{used to modulate the}
          \KeywordTok{calculation} \NormalTok{of the posterior probabilities between the likelihood*mrfprior and}
          \KeywordTok{the} \NormalTok{likelihood*mrfprior*prior. For specifying many prior probability images for}
          \KeywordTok{a} \NormalTok{multi-label segmentation, we offer a minimize usage option (see -m)}\KeywordTok{.} \KeywordTok{With} \NormalTok{that}
          \KeywordTok{option} \NormalTok{one can specify a prior probability threshold in which only those pixels}
          \KeywordTok{exceeding} \NormalTok{that threshold are stored in memory.}

     \KeywordTok{-s}\NormalTok{, --partial-volume-label-set label1xlabel2xlabel3}
          \KeywordTok{The} \NormalTok{partial volume estimation option allows one to modelmixtures of classes}
          \KeywordTok{within} \NormalTok{single voxels. Atropos currently allows the user to model two class}
          \KeywordTok{mixtures} \NormalTok{per partial volume class. The user specifies a set of class labels per}
          \KeywordTok{partial} \NormalTok{volume class requested. For example, suppose the user was performing a}
          \KeywordTok{classic} \NormalTok{3-tissue segmentation (csf, gm, wm) }\KeywordTok{using} \NormalTok{kmeans initialization. Suppose}
          \KeywordTok{the} \NormalTok{user also wanted to model the partial voluming effects between csf/gm and}
          \KeywordTok{gm/wm.} \NormalTok{The user would specify it using -i kmeans[3] and -s 1x2 -s 2x3. So, for}
          \KeywordTok{this} \NormalTok{example, there would be 3 tissue classes and 2 partial volume classes.}
          \KeywordTok{Optionally}\NormalTok{,the user can limit partial volume handling to mrf considerations only}
          \KeywordTok{whereby} \NormalTok{the output would only be the three tissues.}

     \KeywordTok{--use-partial-volume-likelihoods} \NormalTok{1/(0)}
                                      \KeywordTok{true}\NormalTok{/}\KeywordTok{(false)}
          \KeywordTok{The} \NormalTok{user can specify whether or not to use the partial volume likelihoods, in}
          \KeywordTok{which} \NormalTok{case the partial volume class is considered separate from the tissue}
          \KeywordTok{classes.} \NormalTok{Alternatively, one can use the MRF only to handle partial volume in}
          \KeywordTok{which} \NormalTok{case, partial volume voxels are not considered as separate classes.}

     \KeywordTok{-p}\NormalTok{, --posterior-formulation Socrates[}\KeywordTok{<}\NormalTok{useMixtureModelProportions=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialAnnealingTemperature=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{annealingRate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{minimumTemperature=0.}\KeywordTok{1>}\NormalTok{]}
                                 \KeywordTok{Plato}\NormalTok{[}\KeywordTok{<}\NormalTok{useMixtureModelProportions=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialAnnealingTemperature=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{annealingRate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{minimumTemperature=0.}\KeywordTok{1>}\NormalTok{]}
                                 \KeywordTok{Aristotle}\NormalTok{[}\KeywordTok{<}\NormalTok{useMixtureModelProportions=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialAnnealingTemperature=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{annealingRate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{minimumTemperature=0.}\KeywordTok{1>}\NormalTok{]}
                                 \KeywordTok{Sigmoid}\NormalTok{[}\KeywordTok{<}\NormalTok{useMixtureModelProportions=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialAnnealingTemperature=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{annealingRate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{minimumTemperature=0.}\KeywordTok{1>}\NormalTok{]]}
          \KeywordTok{Different} \NormalTok{posterior probability formulations are possible as are different}
          \KeywordTok{update} \NormalTok{options. To guarantee theoretical convergence properties, a proper}
          \KeywordTok{formulation} \NormalTok{of the well-known iterated conditional modes (ICM) }\KeywordTok{uses} \NormalTok{an}
          \KeywordTok{asynchronous} \NormalTok{update step modulated by a specified annealing temperature. If one}
          \KeywordTok{sets} \NormalTok{the AnnealingTemperature }\KeywordTok{>} \NormalTok{1 in the posterior formulation a traditional}
          \KeywordTok{code} \NormalTok{set for a proper ICM update will be created. Otherwise, a synchronous}
          \KeywordTok{update} \NormalTok{step will take place at each iteration. The annealing temperature, T,}
          \KeywordTok{converts} \NormalTok{the posteriorProbability to posteriorProbability^(1/T) }\KeywordTok{over} \NormalTok{the course}
          \KeywordTok{of} \NormalTok{optimization.}

     \KeywordTok{-x}\NormalTok{, --mask-image maskImageFilename}
          \KeywordTok{The} \NormalTok{image mask (which is required) }\KeywordTok{defines} \NormalTok{the region which is to be labeled by}
          \KeywordTok{the} \NormalTok{Atropos algorithm.}

     \KeywordTok{-c}\NormalTok{, --convergence numberOfIterations}
                       \NormalTok{[}\KeywordTok{<}\OtherTok{numberOfIterations=}\NormalTok{5}\KeywordTok{>}\NormalTok{,}\KeywordTok{<}\OtherTok{convergenceThreshold=}\NormalTok{0.001}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{Convergence} \NormalTok{is determined by calculating the mean maximum posterior probability}
          \KeywordTok{over} \NormalTok{the region of interest at each iteration. When this value decreases or}
          \KeywordTok{increases} \NormalTok{less than the specified threshold from the previous iteration or the}
          \KeywordTok{maximum} \NormalTok{number of iterations is exceeded the program terminates.}

     \KeywordTok{-k}\NormalTok{, --likelihood-model Gaussian}
                            \KeywordTok{HistogramParzenWindows}\NormalTok{[}\KeywordTok{<}\NormalTok{sigma=1.}\KeywordTok{0>}\NormalTok{,}\KeywordTok{<}\NormalTok{numberOfBins=}\KeywordTok{32>}\NormalTok{]}
                            \KeywordTok{ManifoldParzenWindows}\NormalTok{[}\KeywordTok{<}\NormalTok{pointSetSigma=1.}\KeywordTok{0>}\NormalTok{,}\KeywordTok{<}\NormalTok{evaluationKNeighborhood=}\KeywordTok{50>}\NormalTok{,}\KeywordTok{<}\NormalTok{CovarianceKNeighborhood=}\KeywordTok{0>}\NormalTok{,}\KeywordTok{<}\NormalTok{kernelSigma=}\KeywordTok{0>}\NormalTok{]}
                            \KeywordTok{JointShapeAndOrientationProbability}\NormalTok{[}\KeywordTok{<}\NormalTok{shapeSigma=1.}\KeywordTok{0>}\NormalTok{,}\KeywordTok{<}\NormalTok{numberOfShapeBins=}\KeywordTok{64>}\NormalTok{, }\KeywordTok{<}\NormalTok{orientationSigma=1.}\KeywordTok{0>}\NormalTok{, }\KeywordTok{<}\NormalTok{numberOfOrientationBins=}\KeywordTok{32>}\NormalTok{]}
                            \KeywordTok{LogEuclideanGaussian}
          \KeywordTok{Both} \NormalTok{parametric and non-parametric options exist in Atropos. The Gaussian}
          \KeywordTok{parametric} \NormalTok{option is commonly used (e.g. SPM }\KeywordTok{&} \KeywordTok{FAST}\NormalTok{) }\KeywordTok{where} \NormalTok{the mean and standard}
          \KeywordTok{deviation} \NormalTok{for the Gaussian of each class is calculated at each iteration. Other}
          \KeywordTok{groups} \NormalTok{use non-parametric approaches exemplified by option 2. We recommend using}
          \KeywordTok{options} \NormalTok{1 or 2 as they are fairly standard and the default parameters work}
          \KeywordTok{adequately.}

     \KeywordTok{-m}\NormalTok{, --mrf [}\KeywordTok{<}\NormalTok{smoothingFactor=0.}\KeywordTok{3>}\NormalTok{,}\KeywordTok{<}\NormalTok{radius=1x1x...}\KeywordTok{>}\NormalTok{]}
               \NormalTok{[}\KeywordTok{<mrfCoefficientImage>}\NormalTok{,}\KeywordTok{<}\NormalTok{radius=1x1x...}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{Markov} \NormalTok{random field (MRF) }\KeywordTok{theory} \NormalTok{provides a general framework for enforcing}
          \KeywordTok{spatially} \NormalTok{contextual constraints on the segmentation solution. The default}
          \KeywordTok{smoothing} \NormalTok{factor of 0.3 provides a moderate amount of smoothing. Increasing this}
          \KeywordTok{number} \NormalTok{causes more smoothing whereas decreasing the number lessens the}
          \KeywordTok{smoothing.} \NormalTok{The radius parameter specifies the mrf neighborhood. Different update}
          \KeywordTok{schemes} \NormalTok{are possible but only the asynchronous updating has theoretical}
          \KeywordTok{convergence} \NormalTok{properties.}

     \KeywordTok{-g}\NormalTok{, --icm [}\KeywordTok{<}\NormalTok{useAsynchronousUpdate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{maximumNumberOfICMIterations=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{icmCodeImage=}\StringTok{''}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{Asynchronous} \NormalTok{updating requires the construction of an ICM code image which is a}
          \KeywordTok{label} \NormalTok{image (with labels in the range }\DataTypeTok{\{1,..,MaximumICMCode\}}\NormalTok{) }\KeywordTok{constructed} \NormalTok{such}
          \KeywordTok{that} \NormalTok{no MRF neighborhood has duplicate ICM code labels. Thus, to update the}
          \KeywordTok{voxel} \NormalTok{class labels we iterate through the code labels and, for each code label,}
          \KeywordTok{we} \NormalTok{iterate through the image and update the voxel class label that has the}
          \KeywordTok{corresponding} \NormalTok{ICM code label. One can print out the ICM code image by specifying}
          \KeywordTok{an} \NormalTok{ITK-compatible image filename.}

     \KeywordTok{-r}\NormalTok{, --use-random-seed 0/(1)}
          \KeywordTok{Initialize} \NormalTok{internal random number generator with a random seed. Otherwise,}
          \KeywordTok{initialize} \NormalTok{with a constant seed number.}

     \KeywordTok{-o}\NormalTok{, --output [classifiedImage,}\KeywordTok{<}\NormalTok{posteriorProbabilityImageFileNameFormat}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{The} \NormalTok{output consists of a labeled image where each voxel in the masked region is}
          \KeywordTok{assigned} \NormalTok{a label from 1, 2, ..., N. Optionally, one can also output the}
          \KeywordTok{posterior} \NormalTok{probability images specified in the same format as the prior}
          \KeywordTok{probability} \NormalTok{images, e.g. posterior%02d.nii.gz (C-style file name formatting)}\KeywordTok{.}

     \KeywordTok{-u}\NormalTok{, --minimize-memory-usage (0)}\KeywordTok{/1}
          \KeywordTok{By} \NormalTok{default, memory usage is not minimized, however, if this is needed, the}
          \KeywordTok{various} \NormalTok{probability and distance images are calculated on the fly instead of}
          \KeywordTok{being} \NormalTok{stored in memory at each iteration. Also, if prior probability images are}
          \KeywordTok{used}\NormalTok{, only the non-negligible pixel values are stored in memory.}
          \KeywordTok{<VALUES>}\NormalTok{: 0}

     \KeywordTok{-w}\NormalTok{, --winsorize-outliers BoxPlot[}\KeywordTok{<}\NormalTok{lowerPercentile=0.}\KeywordTok{25>}\NormalTok{,}\KeywordTok{<}\NormalTok{upperPercentile=0.}\KeywordTok{75>}\NormalTok{,}\KeywordTok{<}\NormalTok{whiskerLength=1.}\KeywordTok{5>}\NormalTok{]}
                              \KeywordTok{GrubbsRosner}\NormalTok{[}\KeywordTok{<}\NormalTok{significanceLevel=0.}\KeywordTok{05>}\NormalTok{,}\KeywordTok{<}\NormalTok{winsorizingLevel=0.}\KeywordTok{10>}\NormalTok{]}
          \KeywordTok{To} \NormalTok{remove the effects of outliers in calculating the weighted mean and weighted}
          \KeywordTok{covariance}\NormalTok{, the user can opt to remove the outliers through the options}
          \KeywordTok{specified} \NormalTok{below.}

     \KeywordTok{-e}\NormalTok{, --use-euclidean-distance (0)}\KeywordTok{/1}
          \KeywordTok{Given} \NormalTok{prior label or probability images, the labels are propagated throughout}
          \KeywordTok{the} \NormalTok{masked region so that every voxel in the mask is labeled. Propagation is}
          \KeywordTok{done} \KeywordTok{by} \NormalTok{using a signed distance transform of the label. Alternatively,}
          \KeywordTok{propagation} \NormalTok{of the labels with the fast marching filter respects the distance}
          \KeywordTok{along} \NormalTok{the shape of the mask (e.g. the sinuous sulci and gyri of the cortex.}
          \KeywordTok{<VALUES>}\NormalTok{: 0}

     \KeywordTok{-l}\NormalTok{, --label-propagation whichLabel[lambda=0.0,}\KeywordTok{<}\NormalTok{boundaryProbability=1.}\KeywordTok{0>}\NormalTok{]}
          \KeywordTok{The} \NormalTok{propagation of each prior label can be controlled by the lambda and boundary}
          \KeywordTok{probability} \NormalTok{parameters. The latter parameter is the probability (in the range}
          \NormalTok{[}\KeywordTok{0}\NormalTok{,1]) }\KeywordTok{of} \NormalTok{the label on the boundary which increases linearly to a maximum value}
          \KeywordTok{of} \NormalTok{1.0 in the interior of the labeled region. The former parameter dictates the}
          \KeywordTok{exponential} \NormalTok{decay of probability propagation outside the labeled region from the}
          \KeywordTok{boundary} \NormalTok{probability, i.e. boundaryProbability*exp( -lambda * distance )}\KeywordTok{.}

     \KeywordTok{-v}\NormalTok{, --verbose (0)}\KeywordTok{/1}
          \KeywordTok{Verbose} \NormalTok{output.}

     \KeywordTok{-h}
          \KeywordTok{Print} \NormalTok{the help menu (short version)}\KeywordTok{.}

     \KeywordTok{--help}
          \KeywordTok{Print} \NormalTok{the help menu.}
          \KeywordTok{<VALUES>}\NormalTok{: 1}
\end{Highlighting}
\end{Shaded}

\end{frame}

\begin{frame}[fragile]{\texttt{DenoiseImage} --- contribution from Jose
Manjon}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{DenoiseImage} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{DenoiseImage}
          \KeywordTok{Denoise} \NormalTok{an image using a spatially adaptive filter originally described in J. V.}
          \KeywordTok{Manjon}\NormalTok{, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive}
          \KeywordTok{Non-Local} \NormalTok{Means Denoising of MR Images With Spatially Varying Noise Levels,}
          \KeywordTok{Journal} \NormalTok{of Magnetic Resonance Imaging, 31:192-203, June 2010.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, the program tries to infer the dimensionality from the input}
          \KeywordTok{image.}

     \KeywordTok{-i}\NormalTok{, --input-image inputImageFilename}
          \KeywordTok{A} \NormalTok{scalar image is expected as input for noise correction.}

     \KeywordTok{-n}\NormalTok{, --noise-model Rician/(Gaussian)}
          \KeywordTok{Employ} \NormalTok{a Rician or Gaussian noise model.}

     \KeywordTok{-x}\NormalTok{, --mask-image maskImageFilename}
          \KeywordTok{If} \NormalTok{a mask image is specified, denoising is only performed in the mask region.}

     \KeywordTok{-s}\NormalTok{, --shrink-factor (1)}\KeywordTok{/2/3/...}
          \KeywordTok{Running} \NormalTok{noise correction on large images can be time consuming. To lessen}
          \KeywordTok{computation} \NormalTok{time, the input image can be resampled. The shrink factor, specified}
          \KeywordTok{as} \NormalTok{a single integer, describes this resampling. Shrink factor = 1 is the}
          \KeywordTok{default.}

     \KeywordTok{-p}\NormalTok{, --patch-radius 1}
                        \KeywordTok{1x1x1}
          \KeywordTok{Patch} \NormalTok{radius. Default = 1x1x1}

     \KeywordTok{-r}\NormalTok{, --search-radius 3}
                         \KeywordTok{3x3x3}
          \KeywordTok{Search} \NormalTok{radius. Default = 3x3x3.}

     \KeywordTok{-o}\NormalTok{, --output correctedImage}
                  \NormalTok{[}\KeywordTok{correctedImage}\NormalTok{,}\KeywordTok{<}\NormalTok{noiseImage}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{The} \NormalTok{output consists of the noise corrected version of the input image.}
          \KeywordTok{Optionally}\NormalTok{, one can also output the estimated noise image.}

     \KeywordTok{--version}
          \KeywordTok{Get} \NormalTok{Version Information.}

     \KeywordTok{-v}\NormalTok{, --verbose (0)}\KeywordTok{/1}
          \KeywordTok{Verbose} \NormalTok{output.}

     \KeywordTok{-h}
          \KeywordTok{Print} \NormalTok{the help menu (short version)}\KeywordTok{.}

     \KeywordTok{--help}
          \KeywordTok{Print} \NormalTok{the help menu.}
          \KeywordTok{<VALUES>}\NormalTok{: 1}
\end{Highlighting}
\end{Shaded}

\end{frame}

\begin{frame}{Multi-atlas segmentation}

\includegraphics{./tools/jointfusion/figures/jointLabelFusion.png}

\end{frame}

\begin{frame}{New work: joint intensity fusion}

\includegraphics{./tools/jointfusion/figures/jointIntensityFusion.png}

\end{frame}

\begin{frame}{Possible uses}

\begin{itemize}
\item
  ``Correct'' images

  \begin{itemize}
  \item
    motion correction
  \item
    ``remove'' lesions
  \end{itemize}
\item
  Project atlas set intensity signature
\item
  Use in ``corrective learning''
\end{itemize}

\end{frame}

\begin{frame}[fragile]{\texttt{antsJointFusion} --- contribution from
Hongzhi Wang (with some added features)}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{antsJointFusion} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{antsJointFusion}
          \KeywordTok{antsJointFusion} \NormalTok{is an image fusion algorithm developed by Hongzhi Wang and Paul}
          \KeywordTok{Yushkevich} \NormalTok{which won segmentation challenges at MICCAI 2012 and MICCAI 2013. The}
          \KeywordTok{original} \NormalTok{label fusion framework was extended to accommodate intensities by Brian}
          \KeywordTok{Avants.} \NormalTok{This implementation is based on Paul}\StringTok{'s original ITK-style implementation}
\StringTok{          and Brian'}\NormalTok{s ANTsR implementation. References include 1) }\KeywordTok{H.} \NormalTok{Wang, J. W. Suh, S.}
          \KeywordTok{Das}\NormalTok{, J. Pluta, C. Craige, P. Yushkevich, Multi-atlas segmentation with joint}
          \KeywordTok{label} \NormalTok{fusion IEEE Trans. on Pattern Analysis and Machine Intelligence, 35(3),}
          \KeywordTok{611-623}\NormalTok{, 2013. and 2) }\KeywordTok{H.} \NormalTok{Wang and P. A. Yushkevich, Multi-atlas segmentation}
          \KeywordTok{with} \NormalTok{joint label fusion and corrective learning--an open source implementation,}
          \KeywordTok{Front.} \NormalTok{Neuroinform., 2013.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, the program tries to infer the dimensionality from the input}
          \KeywordTok{image.}

     \KeywordTok{-t}\NormalTok{, --target-image targetImage}
                        \NormalTok{[}\KeywordTok{targetImageModality0}\NormalTok{,targetImageModality1,...,targetImageModalityN]}
          \KeywordTok{The} \NormalTok{target image (or multimodal target images) }\KeywordTok{assumed} \NormalTok{to be aligned to a common}
          \KeywordTok{image} \NormalTok{domain.}

     \KeywordTok{-g}\NormalTok{, --atlas-image atlasImage}
                       \NormalTok{[}\KeywordTok{atlasImageModality0}\NormalTok{,atlasImageModality1,...,atlasImageModalityN]}
          \KeywordTok{The} \NormalTok{atlas image (or multimodal atlas images) }\KeywordTok{assumed} \NormalTok{to be aligned to a common}
          \KeywordTok{image} \NormalTok{domain.}

     \KeywordTok{-l}\NormalTok{, --atlas-segmentation atlasSegmentation}
          \KeywordTok{The} \NormalTok{atlas segmentation images. For performing label fusion the number of}
          \KeywordTok{specified} \NormalTok{segmentations should be identical to the number of atlas image sets.}

     \KeywordTok{-a}\NormalTok{, --alpha 0.1}
          \KeywordTok{Regularization} \NormalTok{term added to matrix Mx for calculating the inverse. Default =}
          \KeywordTok{0.1}

     \KeywordTok{-b}\NormalTok{, --beta 2.0}
          \KeywordTok{Exponent} \NormalTok{for mapping intensity difference to the joint error. Default = 2.0}

     \KeywordTok{-r}\NormalTok{, --retain-label-posterior-images (0)}\KeywordTok{/1}
          \KeywordTok{Retain} \NormalTok{label posterior probability images. Requires atlas segmentations to be}
          \KeywordTok{specified.} \NormalTok{Default = false}

     \KeywordTok{-f}\NormalTok{, --retain-atlas-voting-images (0)}\KeywordTok{/1}
          \KeywordTok{Retain} \NormalTok{atlas voting images. Default = false}

     \KeywordTok{-c}\NormalTok{, --constrain-nonnegative (0)}\KeywordTok{/1}
          \KeywordTok{Constrain} \NormalTok{solution to non-negative weights.}

     \KeywordTok{-p}\NormalTok{, --patch-radius 2}
                        \KeywordTok{2x2x2}
          \KeywordTok{Patch} \NormalTok{radius for similarity measures. Default = 2x2x2}

     \KeywordTok{-m}\NormalTok{, --patch-metric (PC)}\KeywordTok{/MSQ}
          \KeywordTok{Metric} \NormalTok{to be used in determining the most similar neighborhood patch. Options}
          \KeywordTok{include} \NormalTok{Pearson}\StringTok{'s correlation (PC) and mean squares (MSQ). Default = PC (Pearson}
\StringTok{          correlation).}

\StringTok{     -s, --search-radius 3}
\StringTok{                         3x3x3}
\StringTok{                         searchRadiusMap.nii.gz}
\StringTok{          Search radius for similarity measures. Default = 3x3x3. One can also specify an}
\StringTok{          image where the value at the voxel specifies the isotropic search radius at that}
\StringTok{          voxel.}

\StringTok{     -e, --exclusion-image label[exclusionImage]}
\StringTok{          Specify an exclusion region for the given label.}

\StringTok{     -x, --mask-image maskImageFilename}
\StringTok{          If a mask image is specified, fusion is only performed in the mask region.}

\StringTok{     -o, --output labelFusionImage}
\StringTok{                  intensityFusionImageFileNameFormat}
\StringTok{                  [labelFusionImage,intensityFusionImageFileNameFormat,<labelPosteriorProbabilityImageFileNameFormat>,<atlasVotingWeightImageFileNameFormat>]}
\StringTok{          The output is the intensity and/or label fusion image. Additional optional}
\StringTok{          outputs include the label posterior probability images and the atlas voting}
\StringTok{          weight images.}

\StringTok{     --version}
\StringTok{          Get version information.}

\StringTok{     -v, --verbose (0)/1}
\StringTok{          Verbose output.}

\StringTok{     -h}
\StringTok{          Print the help menu (short version).}

\StringTok{     --help}
\StringTok{          Print the help menu.}
\StringTok{          <VALUES>: 1}
\end{Highlighting}
\end{Shaded}

\end{frame}

\section{Putting it all together---the ANTs cortical thickness
pipeline}\label{putting-it-all-togetherthe-ants-cortical-thickness-pipeline}

\begin{frame}{Cortical thickness studies}

\begin{longtable}[c]{@{}ll@{}}
\toprule
Column1 & Column2\tabularnewline
\midrule
\endhead
Tetris-playing ability & chronic pancreatitis\tabularnewline
Huntington's disease & obsessive-compulsive disorder\tabularnewline
schizophrenia & ADHD\tabularnewline
bipolar disorder & obesity\tabularnewline
Alzheimer's disease & heritable depression\tabularnewline
frontotemporal dementia & elderly depression\tabularnewline
Parkinson's disease & age\tabularnewline
Williams syndrome & gender\tabularnewline
multiple sclerosis & handedness\tabularnewline
autism & intelligence\tabularnewline
migraines & athletic ability\tabularnewline
chronic smoking & meditative practices\tabularnewline
alcoholism & musical ability\tabularnewline
cocaine addiction & tendency toward criminality\tabularnewline
Tourette syndrome in children & childhood sexual abuse in female
adolescents\tabularnewline
scoliosis in female adolescents & traumatic brain injury\tabularnewline
early-onset blindness & untreated male-to-female
transsexuality\tabularnewline
\bottomrule
\end{longtable}

\end{frame}

\begin{frame}{Basic components of the pipeline}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  template building (offline)
\item
  brain extraction
\item
  cortical thickness estimation
\item
  cortical parcellation
\end{enumerate}

\end{frame}

\begin{frame}{Sample results}

\includegraphics{./evaluation/figures/components.png}

\end{frame}

\begin{frame}{The ANTs structural brain mapping workflow}

\includegraphics{./evaluation/figures/pipeline.png}

\end{frame}

\begin{frame}{Template building}

\emph{Tailor data to your specific cohort}

\includegraphics{./evaluation/figures/templates.png}

\end{frame}

\begin{frame}{Template priors}

\includegraphics{./evaluation/figures/templatePriors.png}

\end{frame}

\begin{frame}{Cortical thickness maps}

\includegraphics{./evaluation/figures/corticalThicknessEstimation.png}

In contrast to FreeSurfer which warps coupled surface meshes to segment
the gray matter, \emph{ANTs} diffeomorphically registers the white
matter to the combined gray/white matters while simultaneously
estimating thickness.

\end{frame}

\begin{frame}

\emph{But without ground truth, how does one evaluate the pipeline?}

\end{frame}

\begin{frame}{Predict age and gender}

\(AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)\)

\end{frame}

\begin{frame}{Open science principles}

\includegraphics{./evaluation/figures/ageDistribution.png}

\end{frame}

\begin{frame}{Prediction from cortical thickness data}

\includegraphics{./evaluation/figures/evaluation.png}

\end{frame}

\begin{frame}{Age prediction per site}

\includegraphics{./evaluation/figures/agePredictionPerSite.png}

\end{frame}

\begin{frame}{Regional importance comparison}

\includegraphics{./evaluation/figures/antsvfreesurfer_Importance.png}

ANTs (left) vs.~FreeSurfer (right)

\end{frame}

\begin{frame}{Regional measurements}

\includegraphics{./evaluation/figures/antsvfreesurfer_regionalPlots.png}

\end{frame}

\section{But, wait, there's more!}\label{but-wait-theres-more}

\begin{frame}{ANTs tools are multivariate}

\includegraphics{./evaluation/figures/rfRmse05ANTsT1T2.png}

\end{frame}

\begin{frame}{Arno-thick-in-the-head (ATITH)}

\emph{What if we made a crude estimate of the cortical thickness?}

\[thickness_{ROI} = \frac{volume_{ROI}}{area_{ROI}}\]

\end{frame}

\begin{frame}{Prediction from cortical thickness data}

\includegraphics{./evaluation/figures/atith.png}

\end{frame}

\begin{frame}{Longitudinal processing}

\includegraphics{./longitudinal/figures/longitudinalPipeline.png}

\end{frame}

\section{But the best part is \ldots{}}\label{but-the-best-part-is}

\begin{frame}[fragile]{it is absolutely ``free''!}

\begin{Shaded}
\begin{Highlighting}[]
\OtherTok{$\{ANTSPATH\}}\KeywordTok{/antsCorticalThickness.sh} \NormalTok{\textbackslash{}}
  \NormalTok{-a IXI/T1/IXI002-Guys-0828-T1.nii.gz \textbackslash{}}
  \NormalTok{-e IXI/template/T_template0.nii.gz \textbackslash{}}
  \NormalTok{-m IXI/template/T_template0ProbabilityMask.nii.gz \textbackslash{}}
  \NormalTok{-f IXI/template/T_template0ExtractionMask.nii.gz \textbackslash{}}
  \NormalTok{-p IXI/template/Priors/priors%d.nii.gz \textbackslash{}}
  \NormalTok{-o IXI/ANTsResults/IXI002-Guys-0828-}
\end{Highlighting}
\end{Shaded}

\end{frame}

\begin{frame}

\href{https://github.com/ntustison/KapowskiChronicles}{\textbf{Data
availability}}

\begin{itemize}
\item
  ``\emph{Hey, can I have the FreeSurfer measurements for the entorhinal
  cortex?}'' Sure, why
  not?---\href{http://www.ncbi.nlm.nih.gov/pubmed/26565394}{Hasan, et
  al., J Neuroimaging}
\item
  ``\emph{Can I have one or more of the templates that you used for your
  study?}'' Would you like the priors as well?
\end{itemize}

\end{frame}

\section{Current work and Advanced Normalization Tools in R
(ANTsR)}\label{current-work-and-advanced-normalization-tools-in-r-antsr}

\begin{frame}{Multimodal Brain Tumor Segmentation (BRATS 2013)}

\includegraphics{./competitions/figures/brats2013results2.png}

\href{http://www.ncbi.nlm.nih.gov/pubmed/25433513}{Tustison, et al.,
Optimal symmetric multimodal templates and concatenated random forests
for supervised brain tumor segmentation (simplified) with \emph{ANTsR},
\emph{Neuroinformatics}.}

\end{frame}

\begin{frame}{White matter hyperintensities in TBI}

\includegraphics{./wmhs/figures/wmhPipeline.png}

\end{frame}

\begin{frame}{Social behavior and immunity dysfunction in mice}

\includegraphics{./antsr/figures/filiano_rsfmri.png}

\end{frame}

\begin{frame}{Other ANTsR work}

\begin{itemize}
\item
  \href{http://www.nature.com/articles/sdata20153}{Pediatric template of
  brain perfusion}
\item
  \href{http://www.ncbi.nlm.nih.gov/pubmed/26756101}{Automated
  segmentation of chronic stroke lesions using LINDA: Lesion
  identification with neighborhood data analysis}
\item
  \href{http://www.ncbi.nlm.nih.gov/pubmed/25448483}{Eigenanatomy}
\item
  Corrective learning for segmentation refinement
\end{itemize}

\hypertarget{refs}{}

\end{frame}

\end{document}

### 2016-07-17 licenses/licenses.Rmd
ENH:  IBM presentation.

--- 2015-04-27 ants2015build.Rmd
@@
----
-title: <span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>
-author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)
-bibliography: REFERENCES.bib
-logo:    logo.jpg
-output:
-  pdf_document:
-    toc: true
-    highlight: zenburn
-  beamer_presentation:
-    toc: true
-    fig_width: 7
-    fig_height: 6
-  html_document:
-    toc: true
-    theme: readable
-  revealjs_presentation:
-    pandoc_args: [ "--slide-level", "2" ]
-    incremental: true
-    widescreen: true
-    smaller: false
-    theme: night
-    transition: fade
-    highlight: zenburn
-    center: true
-    self_contained: false
-  ioslides_presentation:
-    css: atk.css
-    incremental: false
-    widescreen: true
-    smaller: false
-    fig_width: 5
----
-
-```{r global options, include=FALSE}
-library(rmarkdown)
-library(knitr)
-figpath<-'figures/'
-opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
-               warning=FALSE, message=FALSE)
-```
-
-##
-
-<div align="center"><img src="./figures/brian_and_edie_sedgwick.jpg" frameborder="0"></img></div>
-
-This talk is online at [http://stnava.github.io/ANTs2015/](http://stnava.github.io/ANTs2015/) with colored [links](http://stnava.github.io/ANTs2015/) meant to be clicked for more information.
-
-# Background
-
-## Founding developers
-
-<div align="center"><img width="1800" src="./figures/bant2.png" frameborder="0"></img></div>
-
-BBA & NT
-
-## Long-term collaborators
-
-![](./figures/antscollab.jpg)
-
-$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
-
-##
-
-![](./figures/lion.png)
-
-a pride: common way of doing things
-
-... in a competitive world ...
-
-## Definitions
-
-* Registration $=$ estimate an "optimal" geometric mapping between image pairs or image sets (e.g. Affine)
-
-* <span style="color:grey;"> Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)</span>
-
-* Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)
-
-* <span style="color:grey;">Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)</span>
-
-* Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>
-
-* <span style="color:grey;">Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)</span>
-
-* MALF: multi-atlas label fusion - using anatomical dictionaries to label new data
-
-* <span style="color:grey;">Solutions to challenging statistical image processing problems usually need elements from each of the above</span>
-
-## Image mapping & perception: 1878
-
-![](./figures/galton.png)
-
-* Francis Galton: Can we see criminality in the face?
-
-* (maybe he should have used *ANTs*?)
-
-## Image mapping & biology: 1917
-
-![](./figures/dthompson.png)
-
-D'Arcy Thompson
-
-## Initial scope
-
-![](./figures/ants_initial_scope.png)
-
-... just do a better registration (tell story) ...
-
-## *ANTs* Lineage
-
-![](./figures/lineage.jpg)
-
-References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
-
-## Diffeomorphisms
-
-<div align="center"><img width="1433" src="./figures/sillyputty.png" frameborder="0"></img></div>
-
-plausible physical modeling of large, invertible deformations
-
-"differentiable map with differentiable inverse"
-
-## Fine-grained and flexible maps
-![](./figures/highresdiffeos.jpg)
-
-... to correct a misconception about diffeomorphisms ...
-
-## Diffeomorphisms: image parameterization in a metric space
-
-![](./figures/shape_appearance.png)
-
-## General purpose library for multivariate image registration, segmentation & statistical analysis tools
-
-* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.
-
-* Generic mathematical methods that are tunable for
-application specific domains:  no-free lunch
-
-* Deep testing on multiple platforms ... osx, linux, windows.
-
-* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )
-
-```
-    An algorithm must use prior knowledge about a problem
-    to do well on that problem
-```
-
-## *ANTs*: Beyond Registration
-
-![](./figures/antscapabilities.jpg)
-
-[Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)
-
-## On documentation
-
-![](figures/Chainsaw.jpg)
-
-documentation is important
-
-## On documentation
-
-![](figures/blindmen.jpg)
-
-... developers can be blind to doc deficiencies
-
-while users are blind to what we provide!
-# ANTs Impact
-
-## ANTs Statistics
-
-![](impact/figures/antsvisitors.png)
-
-## ANTs & Neuroscience
-
-We need statistical image analysis <br />at several scales in modern neuroscience
-
-* Macro: *in vivo* structural and functional MRI
-
-* Micro:  high-resolution post-mortem MRI links with in vivo MRI
-
-* Nano: neuron reconstruction ...
-
-* Solutions that are consistent across these scales have the potential
-to build multi-scale feature sets or templates and provide new
-insights into brain structure and function
-
-* E.g. Parcellation constraints based on histology, tractography, function ...
-
-* Statistical definitions of anatomy/pathology?
-
-* Reinvention of these solutions within each lab ... can we mitigate this?
-
-* Reduce, reuse, recycle ...
-
-## Financial impact
-
-* The **high error rate** in software makes testing for quality assurance critically important.
-
-* Bugs exist **Everywhere**: so don't freak out if we admit we have bugs:  we're just being honest ( and not all devs are )
-
-* Virtually every business in the United States now depends on software for development, production, distribution, and after-sales support of products and services.
-
-* A 2002 NIST study estimated the direct costs to the software supply chain due to failure to identify (**successfully test for**) "bugs"
-
-* We are better at this than most ... **not perfect**
-
-* The estimate of direct costs compiled from industry survey data for the U.S. economy was **\$60 billion per year**
-
-* ... this estimate did not include costs to end users such as lost business (for example, the cost of shutting down the New York Mercantile Exchange in 1998 due to a software failure).
-
-## Reproducibility
-
-* Consider the recent paper: [Freesurfer, laplacian, DiReCT thickness in longitudinal stroke](http://ac.els-cdn.com/S2213158214001260/1-s2.0-S2213158214001260-main.pdf?_tid=8e6f5248-335d-11e4-ba4f-00000aab0f02&acdnat=1409743944_6615d59eb5709e6bcb1aca76450f7d93)
-
-* We "pre-wrote" a comment: [Instrumentation bias in the use and evaluation of scientific software](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3766821/?report=reader)
-
-* With these guys:
-
-* <img src="figures/luis.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right: 3px;"><img src="figures/torsten.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;">
-
-## Hired by Google
-
-<img src="figures/luis.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right: 3px;"><img src="figures/torsten.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;"><img src="figures/gang.jpg" style="height: 256px; float: middle; margin-bottom: 15px; margin-right:3px;">
-
-# Optimal Templates
-
-## "Optimal" templates (?)
-
-* unbiased wrt measurement space
-
-* space is non-linear: reference matters
-
-* encodes prior information: still just averages (usually)
-
-* concept extends across modalities, anatomy, temporality, etc
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.060.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.061.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.062.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.063.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.064.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.065.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.066.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.067.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.068.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.069.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.070.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.071.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.072.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.073.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.074.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.075.jpg)
-
-## Faces, brains, whatever ...
-
-![](templates/figures/WashUJan2011.076.jpg)
-
-see [ANTs site](stnava.github.io/ANTs) and [ANTs Documentation page](stnava.github.io/ANTsDoc)
-
-## Templates from ANTs Colleagues ( not us )
-
-![](templates/figures/templates_ants_colleagues.png)
-
-## Templates unlock modalities
-
-![](figures/ptbp2.png)
-
-# Evaluation
-
-##
-
-<div align="center"><img width="3500" src="evaluation/figures/evalhistory.png" frameborder="0"></img></div>
-
-# ANTs brain morphology<br><br>[<small>"*Large-scale evaluation of ANTs and FreeSurfer cortical thickness measurements*"</small>](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
-
-## Cortical thickness studies:
-```{r, results='asis', echo = FALSE}
-conditions <- c( "Huntington’s disease", "schizophrenia", "bipolar disorder",
-                 "Alzheimer’s disease", "frontotemporal dementia", "Parkinson’s disease",
-                 "Williams syndrome", "multiple sclerosis", "autism", "migraines",
-                 "chronic smoking", "alcoholism", "cocaine addiction", "Tourette syndrome in children",
-                 "scoliosis in female adolescents", "early-onset blindness", "chronic pancreatitis",
-                 "obsessive-compulsive disorder", "ADHD", "obesity", "heritable depression",
-                 "elderly depression", "age", "gender", "untreated male-to-female transsexuality",
-                 "handedness", "intelligence", "athletic ability", "meditative practices", "musical ability",
-                 "tendency toward criminality", "childhood sexual abuse in female adolescents",
-                 "Tetris-playing ability in female adolescents", "traumatic brain injury" )
-
-conditionsDF <- data.frame( Column1 = conditions[1:floor( 0.5*length(conditions) )], Column2 = conditions[( 1+floor( 0.5*length(conditions) ) ):length(conditions)] )
-knitr::kable( conditionsDF )
-```
-
-## *ANTs*-related background
-
-* Sandy, Brian, and <span style="color:red;">DiReCT</span>
-  + used other tools such as FMRIB's Automated Segmentation Tool (FAST)
-  + `KellySlater.cxx`
-  * scripts "adequate for Penn data"
-* `KellyKapowski.cxx` and `antsCorticalThickness.sh`
-* _"Let's evaluate on open data."_
-* and, eventually, _"Let's compare with FreeSurfer."_
-
-## The *ANTs* structural brain mapping workflow
-
-![](./evaluation/figures/pipeline.png)
-
-## Basic components of the pipeline
-
-<div align="center"><img height="350" src="./evaluation/figures/components.png" frameborder="0"></img></div>
-
-1. template building (offline)
-2. brain extraction
-3. cortical thickness estimation
-4. cortical parcellation
-
-## Template building
-
-*Tailor data to your specific cohort*
-
-<div align="center"><img height="350" src="./evaluation/figures/templates.png" frameborder="0"></img></div>
-
-* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
-* Acquisition and anonymization (e.g. defacing) protocols are often different.
-
-## Template building (cont.)
-
-<div align="center"><img height="350" src="./evaluation/figures/templatePriors.png" frameborder="0"></img></div>
-
-Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
-to produce auxiliary images which are used for brain extraction and brain segmentation.
-
-## Brain extraction comparison<br>*ANTs* vs. FreeSurfer
-
-<div align="center"><img height="380" src="./evaluation/figures/brainExtraction.png" frameborder="0"></img></div>
-
-Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
-the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
-
-## Brain segmentation
-
-<div align="center"><img height="350" src="./evaluation/figures/brainSegmentation.png" frameborder="0"></img></div>
-
-Randomly selected healthy individuals.  Atropos gets good performance across ages.
-
-## Cortical thickness estimation
-
-<div align="center"><img height="250" src="./evaluation/figures/corticalThicknessEstimation.png" frameborder="0"></img></div>
-
-In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
-
-## _But without ground truth, how does one evaluate the pipeline?_
-
-* Use age and gender (demographic information) in training/prediction paradigm
-* Public data sets (IXI, NKI, Oasis, MMRR)
-* $>$ 1200 subjects, age 7 to over 90 years old
-
-## Prediction from cortical thickness data:<br>gender and age
-
-<div align="center"><img height="350" src="./evaluation/figures/evaluation.png" frameborder="0"></img></div>
-
-## Regional importance <br>comparison
-
-$AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$
-
-<div align="center"><img height="500" src="./evaluation/figures/antsvfreesurfer_Importance.png" frameborder="0"></img></div>
-
-*ANTs* (left) vs. FreeSurfer (right)
-
-## Regional importance comparison (cont.)
-
-<div align="center"><img height="550" src="./evaluation/figures/antsvfreesurfer_regionalPlots.png" frameborder="0"></img></div>
-
-## Cortical thickness extensions
+# Why would you care?
 
 <!--
-# New work
 
-## RKRNS
+## \`\`Free beer\'\'
 
-[link](http://stnava.github.io/RKRNS/)
+![](./licenses/figures/freebeerfreespeech.jpg)
 
-What mathematical encoding of language reflects both brain activity and
-"our" understanding of semantics?
-
-## RIPMARC: Imputation, strutural networks, etc.
-
-![](figures/ripmmarc_inter.png)
-
-MICCAI 2014, Neuroimage 2015
-
-## Big image registration
 -->
 
-# Longitudinal processing <!--with ANTs>
+## Software for medical image analysis
+
+* [FSL](http://fsl.fmrib.ox.ac.uk/fsldownloads/)
+
+* [SPM](http://www.fil.ion.ucl.ac.uk/spm/software/)
+
+* [FreeSurfer](http://www.fil.ion.ucl.ac.uk/spm/software/)
+
+* [MIPAV](http://mipav.cit.nih.gov)
+
+* [AFNI](https://afni.nimh.nih.gov/afni)
+
+* Slicer, Elastix, SimpleITK, ANTs $\longleftrightarrow$ [Insight Toolkit](http://www.itk.org)
+
+* Many more at [idoimaging.com](http://idoimaging.com)
 
 <!--
-## ANTs longitudinal pipeline
 
-![](longitudinal/figures/longpipe.png)
+## [FSL](http://fsl.fmrib.ox.ac.uk/fsldownloads/)
 
-see [link to paper](http://link.springer.com/chapter/10.1007/978-3-642-15705-9_40)
+> No part of the Software may be reproduced, modified, transmitted or
+> transferred in any form or by any means, electronic or mechanical,
+> without the express permission of the University. The permission of
+> the University is not required if the said reproduction, modification,
+> transmission or transference is done without financial return, ...
+> You may be held legally responsible for any copyright infringement
+> that is caused or encouraged by your failure to abide by these terms
+> and conditions.
+>
+> __You are not permitted under this Licence to use this Software
+> commercially.__
 
-and [unbiased analysis paper](http://www.ncbi.nlm.nih.gov/pubmed/20005963)
+## [SPM](http://www.fil.ion.ucl.ac.uk/spm/software/)
 
-plus [longitudinal recommendation paper](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3581852/)
+> SPM is free but copyright software, distributed under the terms of
+> the GNU General Public Licence as published by the Free Software
+> Foundation (either version 2, as given in file spm_LICENCE.man,
+> or at your option, any later version). Further details on "copyleft"
+> can be found at http://www.gnu.org/copyleft/. In particular, SPM is
+> supplied as is. No formal support or maintenance is provided or implied.
+
+> "Copyleft" says that anyone who redistributes the software, with or
+> without changes, must pass along the freedom to further copy and change
+> it. Copyleft guarantees that every user has freedom... __it is illegal to
+> distribute the improved version except as free software__...
+
+## [FreeSurfer](http://www.fil.ion.ucl.ac.uk/spm/software/)
+
+> The license granted in this Software License includes without limitation
+> the right to (i) incorporate the Software into proprietary programs
+> (subject to any restrictions applicable to such programs), (ii) add
+> your own copyright statement to your modifications of the Software, and
+> (iii) provide additional or different license terms and conditions in your
+> sublicenses of modifications of the Software; provided that in each case your
+> use, reproduction or distribution of such modifications otherwise complies
+> with the conditions stated in this Software License.
+
+## [ANTs](https://github.com/stnava/ANTs/blob/master/ANTSCopyright.txt)
+
+> Redistribution and use in source and binary forms, with or without
+> modification, are permitted provided that the following conditions
+> are met:
+> 1. _Redistributions of source code must retain the above copyright
+>   notice, this list of conditions and the following disclaimer._
+> 2. _Redistributions in binary form must reproduce the above copyright
+>   notice, this list of conditions and the following disclaimer in the
+>   documentation and/or other materials provided with the distribution._
+> 3. _Neither the name of the consortium nor the names of its contributors
+>  may be used to endorse or promote products derived from this software
+>  without specific prior written permission._
+
+## [ITK](https://itk.org/ITK/project/licenseversion1.html)
+
+> The license of the Insight Toolkit is an open-source Apache 2.0 license. It
+> allows unrestricted use, including use in commercial products.
+> Starting with ITK 4.0, The Insight Toolkit is distributed under the Apache 2.0
+> license approved by the Open Source Initiative (OSI).
+
 -->
-
-## `antsLongitudinalCorticalThickness.sh`
-
-![](longitudinal/figures/longpipeex.png)
-
-## Longitudinal TBI with lesions (segmentation)
-
-![](longitudinal/figures/long_with_lesions_seg.png)
-
-## Longitudinal TBI with lesions (cortical thickness)
-
-![](longitudinal/figures/long_with_lesions_thick.png)
-
-<!--
-## ANTs longitudinal pipeline
-
-![](longitudinal/figures/babystudy.png)
--->
-
-# Cortical thickness with lesions
-
-## antsCorticalThickness.sh is adaptable!
-
-1. Register subject (or single subject template) to normal template.
-
-2. Transform lesion mask to normal template.
-
-3. Create additional "lesion" prior, i.e. ```SmoothImage 3 ${lesionMask} 1 ${lesionPrior} 1```.
-
-4.  Subtract out lesion prior from all other priors and keep values $\in [0,1]$.
-
-## Modified template spatial priors
-
-![](lesions/figures/lesionPrior.png)
-
-## antsCorticalThickness.sh using lesion prior
-
-![](lesions/figures/lesionSegmentation.png)
-
-Only change to the command call is an additional '-c WM[7]' which means "combine
-the 7<sup>th</sup> prior, i.e. lesion, to the white matter for cortical thickness calculation."
-
-# Registration & statistics:<br /> Frontiers and innovation
-
-## multivariate statistical fields arise from fused modalities
-
-![images at measurement fields](figures/statisticalfields.png)
-
-*Many opportunities for statistical advancements*
-
-## ITK+ANTs+R = <span style="color:red;">*ANTsR*</span>
-
-## Agnostic statistics
-![](./figures/antsrex.jpg)
-
-[McMillan et al.](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3961542/)
-
-## A Quick <span style="color:grey;">*ANTsR*</span> example
-```{r loadantsr,results='hide',echo=FALSE,message=FALSE}
-library(ANTsR)
-```
-
-This is an executable *ANTsR* code block - *N*-dimensional statistics to go with
-our *N*-dimensional image processing software!
-```{r loadimages,message=FALSE,warning=FALSE,results='hide'}
-library(ANTsR)
-dim<-2
-filename<-getANTsRData('r16')
-img<-antsImageRead( filename , dim )
-filename<-getANTsRData('r64')
-img2<-antsImageRead( filename , dim )
-mask<-getMask(img,50,max(img),T)
-mask2<-getMask(img,150,max(img),T)
-nvox<-sum( mask == 1 )
-nvox2<-sum( mask2 == 1 )
-```
-The brain has `r nvox` voxels ...
-
-## A Quick <span style="color:grey;">*ANTsR*</span> example
-
-Simulate a population morphometry study - a "VBM" ...
-```{r morph,results='hide'}
-simnum<-10
-imglist<-list()
-imglist2<-list()
-for ( i in 1:simnum ) {
-  img1sim<-antsImageClone(img)
-  img1sim[ mask==1 ]<-rnorm(nvox,mean=0.5)
-  img1sim[ mask2==1 ]<-rnorm(nvox2,mean=2.0)
-  img2sim<-antsImageClone(img2)
-  img2sim[ mask==1 ]<-rnorm(nvox,mean=0.20)
-  imglist<-lappend(imglist,img1sim)
-  imglist2<-lappend(imglist2,img2sim)
-}
-imglist<-lappend( imglist, imglist2 )
-mat<-imageListToMatrix( imglist, mask )
-DX<-factor( c( rep(0,simnum), rep(1,simnum) ) )
-mylmresults<-bigLMStats( lm( mat ~ DX ) )
-qvals<-p.adjust( mylmresults$pval.model )
-```
-The minimum q-value is `r min(qvals)` ...
-
-## Visualize the histograms of effects
-```{r vizmorph,results='hide'}
-whichvox<-qvals < 1.e-2
-voxdf<-data.frame( volume=c( as.numeric( mat[,whichvox] ) ), DX=DX )
-ggplot(voxdf, aes(volume, fill = DX)) + geom_density(alpha = 0.2)
-```
-
-## Visualize the anatomical distribution
-```{r vizmorph2hide,results='hide',echo=FALSE}
-betas<-antsImageClone(mask)
-betavec<-abs(mylmresults$beta.t[1,])
-betas[mask==1]<-betavec
-smoothImage(betas, 1.5)
-thresh<-paste(3.0,'x',max(betavec),sep='')
-ofn<-paste(figpath,'vizmorph2.jpg',sep='')
-```
-
-```{r vizmorph2,results='hide'}
-plot.antsImage(img,functional=list(betas),threshold=thresh,
-  outname=ofn)
-```
-
-![](`r ofn`)
-
-## Network visualization
-see `?plotBasicNetwork`
-```{r networkfn,results='hide',warning=FALSE,echo=FALSE,message=FALSE}
-ofn<-paste(figpath,'network',sep='')
-ofnpng<-paste(ofn,'.png',sep='')
-```
-```{r network,results='hide',warning=FALSE,echo=FALSE,message=FALSE,eval=F}
-       mnit<-getANTsRData("mni")
-       mnit<-antsImageRead(mnit,3)
-       mnia<-getANTsRData("mnia")
-       mnia<-antsImageRead(mnia,3)
-       ThresholdImage(3,mnit,mnit,1,max(mnit))
-       ImageMath(3,mnit,"FillHoles",mnit)
-       cnt<-getCentroids( mnia, clustparam = 50 )
-       aalcnt<-cnt$centroids[1:90,]
-       brain<-renderSurfaceFunction( surfimg =list( mnit ) , alphasurf=0.1 ,smoothsval = 1.5 )
-       testweights<-matrix( rep( 0, 90*90 ) ,nrow=90)
-       testweights[31,37]<-1  # ant cingulate to hipp
-       testweights[31,36]<-2  # ant cingulate to post cingulate
-       testweights[11,65]<-3  # broca to angular
-       plotBasicNetwork( centroids = aalcnt , brain , weights=testweights )
-       id<-par3d("userMatrix")
-       rid<-rotate3d( id , -pi/2, 1, 0, 0 )
-       rid2<-rotate3d( id , pi/2, 0, 0, 1 )
-       rid3<-rotate3d( id , -pi/2, 0, 0, 1 )
-       par3d(userMatrix = id )
-       dd<-make3ViewPNG(  rid, id, rid2,  ofn )
-       par3d(userMatrix = id )
-```
-![](`r ofnpng`)
-
-## The power of *ANTs* $+$ *R* $\rightarrow$<br /> <span style="color:red;">**Reproducible imaging science**</span>
-
-![](./figures/antsgoals.png)
-
-...
-used in ["Sparse canonical correlation analysis relates network-level atrophy to multivariate cognitive measures in a neurodegenerative population"](http://www.ncbi.nlm.nih.gov/pubmed/24096125) and several upcoming ...
-
-# Wrap-up & Conclusions
-
-## Questions driving *ANTs* ($+$ Refs.1)
-
-* how should we geometrically transform anatomical coordinates?
-
-    - [syn paper](http://www.ncbi.nlm.nih.gov/pubmed/17659998) - our geometric transformation model of choice
-    - [recent B-spline alternative/improvement](http://www.ncbi.nlm.nih.gov/pubmed/24409140)
-
-* how should we measure pairwise image similarity?
-
-    - [similarity metric evaluation](http://www.ncbi.nlm.nih.gov/pubmed/20851191) compares functions for computing rigid or affine transformations between images
-
-* what if this pair has rgb/vector/tensor voxels?
-
-    - [dti similarity](http://www.ncbi.nlm.nih.gov/pubmed/18041273)
-
-* how do we extend from pairs to hundreds or thousands of pairs of images?
-
-    - [optimal templates](http://www.ncbi.nlm.nih.gov/pubmed/?term=avants+optimal+template) and [spatial priors](http://www.ncbi.nlm.nih.gov/pubmed/24879923)
-    - species specific templates/priors in [chimps](http://www.ncbi.nlm.nih.gov/pubmed/23516289) and [canines](http://www.ncbi.nlm.nih.gov/pubmed/23284904)
-    - [ants "big data"](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+freesurfer)
-
-* how do we fuse multiple modality images at the subject and population levels?
-
-    - [ants auxiliary modality study](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+logical+circularity)
-
-## Questions driving *ANTs* ($+$ Refs.2)
-
-* can diffeomorphisms [improve cortical thickness measurement](http://www.ncbi.nlm.nih.gov/pubmed/?term=tustison+freesurfer)?
-
-* how might we efficiently cluster the statistical fields that arise in image analysis?
-
-    - [Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation and [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison)
-    - [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants) for sparse imaging-specific PCA
-
-* how to cluster such fields when we have supervision?
-
-    - [sparse canonical correlation analysis for neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants)
-    - [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460)
-    - [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) - powerful expert systems for segmentation
-
-* how do we implement a fully multivariate *interpretable* brain and behavior study?
-
-    - [SCCAN for imaging & cognition](http://www.ncbi.nlm.nih.gov/pubmed/?term=sccan+avants)
-
-* how do we extend these ideas to functional MRI & decoding?
-
-    - [recent unpublished software](http://stnava.github.io/RKRNS/) 
-    - [recent work with Ben Kandel](..not yet...)
-
-## *ANTs* longitudinal analysis
-
-* Longitudinal image processing issues
-    - [registration induced bias](http://www.ncbi.nlm.nih.gov/pubmed/20005963)
-    - [general & TBI-specific issues in longitudinal analysis](http://www.ncbi.nlm.nih.gov/pubmed/23549059)
-    - [reproducibility of CBF](http://www.ncbi.nlm.nih.gov/pubmed/22517961)
-    - [structure-specific analysis](http://www.ncbi.nlm.nih.gov/pubmed/22306801)
-
-* An early study of longitudinal cortical change in ALS
-    - [ALS atrophy rates](http://www.ncbi.nlm.nih.gov/pubmed/16317254)
-
-* Extension of standard-setting ants cortical thickness pipeline to longitudinal data
-    - [DynANTs (unpublished)](https://github.com/stnava/DynANTs)
-
-## Challenges: Computational and Scientific
-
-- Scalability: **need to fuse feature selection methods with transformation optimization**
-- Scalability: **need to leverage existing ITK streaming infrastructure in application level tool**
-- Domain expertise: Customizable for specific problems but sometimes not specific enough
-- Rapid development: colleagues still need familiarity with compilation for latest ANTs features
-- Latest theoretical advances in registration not yet wrapped for users
-- Need more [Documentation](http://stnava.github.io/ANTs/)  & [testing](http://testing.psychiatry.uiowa.edu/CDash/index.php?project=ANTS) ...
-
-## Recap
-
-- Powerful, general-purpose, <span style="color:red;">well-evaluated</span> registration and segmentation.
-
-- Differentiable maps with differentiable inverse <span style="color:red;">$+$ statistics in these spaces</span>
-
-- Evaluated in multiple problem domains</span> via internal studies & open competition
-
-- Borg philosophy: <span style="color:red;">"best of"</span> from I/O, to processing to statistical methods
-
-- Open source, testing, many examples, consistent style, multiple platforms,  active community support ...
-
-- Integration with *R* $+$ novel tools for prediction, decoding, high-to-low dimensional statistics.
-
-- Collaborations with [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
-
-## Tools you can use for imaging science
-
-- Core developers:  *B. Avants, N. Tustison, H. J. Johnson, J. T. Duda*
-
-- Many contributors, including users ...
-
-- Multi-platform, multi-threaded C++ [stnava.github.io/ANTs](stnava.github.io/ANTs)
-
-- Developed in conjunction with [http://www.itk.org/](http://www.itk.org/)
-
-- R wrapping and extension [stnava.github.io/ANTsR](stnava.github.io/ANTsR)
-
-- rapid development, regular testing $+$ many eyes $\rightarrow$ bugs are shallow
-
-<img style="float: right" src="figures/penn.png" />
-<img style="float: left" src="figures/picsl.jpg" />
-
-# References

### 2016-07-17 mystyle.tex
ENH:  IBM presentation.

@@
-\pgfdeclareimage[height=0.1cm, width=1cm]{logo}{}
-\logo{\pgfuseimage{logo}}
-\institute{}
-\definecolor{links}{HTML}{2A1B81}
+% \pgfdeclareimage[width=1cm]{logo}{./figures/monkeyTypewriter.png}
+%\logo{\pgfuseimage{logo}}
+
+\institute{University of Virginia}
+\definecolor{links}{RGB}{42, 27, 129}
 \definecolor{mypink2}{RGB}{219, 48, 122}
-\hypersetup{colorlinks,linkcolor=links,urlcolor=mypink2}
+%\hypersetup{colorlinks,linkcolor=links,urlcolor=mypink2}
 \usefonttheme{professionalfonts}
-\setbeamerfont{note page}{family*=pplx,size=\footnotesize} % Palatino for notes
-\usepackage{helvet}
+
+% \setbeamerfont{note page}{family*=pplx,size=\footnotesize} % Palatino for notes
+
+\setbeamerfont{subtitle}{size=\small}
+
+\definecolor{uvablue}{RGB}{0,85,150}
+\definecolor{uvalibraryorange}{RGB}{252,175,23}
+\definecolor{uvacream}{RGB}{241,229,199}
+\definecolor{uvalightblue}{RGB}{163,220,230}
+
+\setbeamercolor{block body}{bg=green,fg=green}
+\setbeamercolor{block body alerted}{bg=green,fg=green}
+\setbeamercolor{block body example}{bg=green,fg=green}
+
+\setbeamercolor{caption name}{fg=uvablue}
+
+\setbeamercolor{headline}{fg=uvacream,bg=uvacream}
+\setbeamercolor{section}{fg=uvalibraryorange,bg=uvablue}
+\setbeamercolor{frametitle}{fg=uvalibraryorange,bg=uvablue}
+\setbeamercolor{palette primary}{bg=uvalibraryorange,fg=uvablue}
+\setbeamercolor{palette secondary}{bg=uvablue,fg=uvablue}
+\setbeamercolor{palette tertiary}{bg=uvalibraryorange,fg=uvablue}
+\setbeamercolor{palette quarternary}{fg=uvalibraryorange,bg=uvablue}
+\setbeamercolor{palette sidebar primary}{bg=uvalibraryorange,fg=uvablue}
+\setbeamercolor{palette sidebar secondary}{fg=uvablue,bg=uvablue}
+\setbeamercolor{palette sidebar tertiary}{fg=uvalibraryorange,bg=uvablue}
+\setbeamercolor{palette sidebar quarternary}{fg=uvalibraryorange,bg=uvablue}
+\setbeamercolor{structure}{bg=uvablue}
+
 \useinnertheme{rectangles}
+
+\titlegraphic{\vspace{-7.5mm}\includegraphics[width=0.45\paperwidth]{./figures/monkeyTypewriter.png}}

### 2016-07-17 papers/papers.Rmd
ENH:  IBM presentation.

@@
-# Major papers
+# Major ANTs utilities
 
@@
 <BR><BR>
-<span style="color:red;">_"Papers are just advertisements for the science."_</red>
+_\`\`Papers are just advertisements for the science.\'\'_
 <BR>
+
+## Neuro tools
+
+![](./tools/figures/coreANtsToolsNeuro.png)
+
+## Pulmonary tools
+
+![](./tools/figures/coreANtsToolsLung.png)
+
+<!--
 
@@
 
-<!--
 NOtes:
@@
 * The variant most widely used
+-->
+
+<!--
+
+## Diffeomorphisms:  Occam's razor modeling
+
+![](./figures/sillyputty.png)
+
+_differentiable map with differentiable inverse_
+
+-->
+
+## Diffeomoprhisms:  differentiable map with diff. inverse
+
+![](./figures/highresdiffeos.jpg)
+
+<!--
+
+## Diffeomorphisms: image parameterization in a metric space
+
+![](./figures/shape_appearance.png)
 -->
@@
 
-antsMultivariateTemplateConstruction2.sh -d ImageDimension -o OutputPrefix <other options> <images>
+antsMultivariateTemplateConstruction.sh -d ImageDimension -o OUTPREFIX <other options> <images>
 
-Compulsory arguments (minimal command line requires SGE/PBS cluster, otherwise use -c and
-  -j options):
+Compulsory arguments (minimal command line requires SGE cluster, otherwise use -c & -j options):
 
@@
 
-     -a   image statistic used to summarize images (default 1)
-          0 = mean
-          1 = mean of normalized intensities
-          2 = median
+     -c:  Control for parallel computation (default 1) -- 0 == run serially,  1 == SGE qsub,
+          2 == use PEXEC (localhost), 3 == Apple XGrid, 4 == PBS qsub, 5 == SLURM
 
-     -b:  Backup images and results from all iterations (default = 0):  Boolean to save
-          the transform files, bias corrected, and warped images for each iteration.
+     -g:  Gradient step size (default 0.25) -- smaller in magnitude results in more cautious steps
 
-     -c:  Control for parallel computation (default 0):
-          0 = run serially
-          1 = SGE qsub
-          2 = use PEXEC (localhost)
-          3 = Apple XGrid
-          4 = PBS qsub
+     -i:  Iteration limit (default 4) -- iterations of the template construction (Iteration limit)*NumImages registrations.
 
-     -e   use single precision ( default 1 )
+     -j:  Number of cpu cores to use (default 2; -- requires "-c 2")
 
-     -g:  Gradient step size (default 0.25): smaller in magnitude results in more
-          cautious steps.
+     -k:  Number of modalities used to construct the template (default 1)
 
-     -i:  Iteration limit (default 4): iterations of the template construction
-          (Iteration limit)*NumImages registrations.
+     -w:  Modality weights used in the similarity metric (default = 1) --- specified as e.g. 1x0.5x0.75
 
-     -j:  Number of cpu cores to use locally for pexec option (default 2; requires "-c 2")
+     -m:  Max-iterations in each registration
 
-     -k:  Number of modalities used to construct the template (default 1):  For example,
-          if one wanted to create a multimodal template consisting of T1,T2,and FA
-          components ("-k 3").
+     -n:  N4BiasFieldCorrection of moving image (default 1) -- 0 == off, 1 == on
 
-     -w:  Modality weights used in the similarity metric (default = 1): specified as
-          e.g. 1x0.5x0.75.
+     -p:  Commands to prepend to job scripts (e.g., change into appropriate directory, set paths, etc)
 
-     -q:  Max iterations for each pairwise registration (default = 100x100x70x20):
-          specified in the form ...xJxKxL where
-            J = max iterations at coarsest resolution (here, reduced by power of 2^2)
-            K = middle resolution iterations (here, reduced by power of 2)
-            L = fine resolution iteratioxns (here, full resolution).
-          Finer resolutions take much more time per iteration than coarser resolutions.
+     -r:  Do rigid-body registration of inputs before creating template (default 0) -- 0 == off 1 == on. Only useful when
+          you do not have an initial template
 
-     -f:  Shrink factors (default = 6x4x2x1):  Also in the same form as -q max iterations.
-          Needs to have the same number of components.
+     -s:  Type of similarity metric used for registration.
 
-     -s:  Smoothing factors (default = 3x2x1x0):  Also in the same form as -q max
-          iterations.  Needs to have the same number of components.
-
-     -n:  N4BiasFieldCorrection of moving image: 0 == off, 1 == on (default 1).
-
-     -p:  Commands to prepend to job scripts (e.g., change into appropriate directory, set
-          paths, etc)
-
-     -r:  Do rigid-body registration of inputs before creating template (default 0):
-          0 == off 1 == on. Only useful when you do not have an initial template
-
-     -l:  Use linear image registration stages during the pairwise (template/subject)
-          deformable registration.  Otherwise, registration is limited to SyN or
-          B-spline SyN (see '-t' option).  This is '1' by default.
-
-     -m:  Type of similarity metric used for registration (default = CC):  Options are
-            CC = cross-correlation
-            MI = mutual information
-            MSQ = mean square difference
-            DEMONS = demon's metric
-          A similarity metric per modality can be specified.  If the CC metric is chosen,
-          one can also specify the radius in brackets, e.g. '-m CC[4]'.
-
-     -t:  Type of transformation model used for registration (default = SyN):  Options are
-            SyN = Greedy SyN
-            BSplineSyN = Greedy B-spline SyN
-            TimeVaryingVelocityField = Time-varying velocity field
-            TimeVaryingBSplineVelocityField = Time-varying B-spline velocity field
-
-     -u:  Walltime (default = 20:00:00):  Option for PBS qsub specifying requested time
-          per pairwise registration.
-
-     -v:  Memory limit (default = 8gb):  Option for PBS qsub specifying requested memory
-          per pairwise registration.
+     -t:  Type of transformation model used for registration.
 
@@
 
-antsMultivariateTemplateConstruction2.sh -d 3 -i 3 -k 1 -f 4x2x1 -s 2x1x0vox -q 30x20x4 -t SyN  -m CC -c 0 -o MY sub*avg.nii.gz
+antsMultivariateTemplateConstruction.sh -d 3 -m 30x50x20 -t GR -s CC -c 1 -o MY -z InitialTemplate.nii.gz  *RF*T1x.nii.gz
 
-Multimodal example:
-
-antsMultivariateTemplateConstruction2.sh -d 3 -i 3 -k 2 -f 4x2x1 -s 2x1x0vox -q 30x20x4 -t SyN -z t1.nii.gz -z t2.nii.gz  -m CC -c 0 -o MY templateInput.csv
-
-where templateInput.csv contains
-
-subjectA_t1.nii.gz,subjectA_t2.nii.gz
-subjectB_t1.nii.gz,subjectB_t2.nii.gz
-...
+- In this example 30x50x20 iterations per registration are used for template creation (that is the default)
+- Greedy-SyN and CC are the metrics to guide the mapping.
+- Output is prepended with MY and the initial template is InitialTemplate.nii.gz (optional).
+- The -c option is set to 1, which will result in using the Sun Grid Engine (SGE) to distribute the computation.
+- if you do not have SGE, read the help for multi-core computation on the local machine, or Apple X-grid options.
 
@@
 ```
+
+<!--
 
@@
 * "*Let's incorporate N3 into ANTs!*"
+-->
 
@@
 
-<!-- regular html comment
-
 <div align="center"><img src="./tools/n4/figures/whyN4.png" frameborder="0"></img></div>
 
--->
+<!--
 
@@
 * tested nightly within the ITK dashboard system
+-->
 
@@
 
+<--
 ##  Atropos -- cutting the threads of fate
@@
 ![](./papers/figures/Atropos_deGoya.jpg)
-
-"20+ years of development.  <br>_Show me the code!_"
+-->
 
@@
 ## Atropos:  flexible code base
+
+"20+ years of development.  <br>_Show me the code!_"
 
@@
 
+<!--
+
 ## Atropos + N4 $\rightarrow$ `antsAtroposN4.sh`
@@
 ![](./tools/atropos/figures/atroposFlow.png)
+-->
+
+## ```DenoiseImage``` --- contribution from Jose Manjon
+
+```bash
+$ DenoiseImage --help
+
+COMMAND:
+     DenoiseImage
+          Denoise an image using a spatially adaptive filter originally described in J. V.
+          Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive
+          Non-Local Means Denoising of MR Images With Spatially Varying Noise Levels,
+          Journal of Magnetic Resonance Imaging, 31:192-203, June 2010.
+
+OPTIONS:
+     -d, --image-dimensionality 2/3/4
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, the program tries to infer the dimensionality from the input
+          image.
+
+     -i, --input-image inputImageFilename
+          A scalar image is expected as input for noise correction.
+
+     -n, --noise-model Rician/(Gaussian)
+          Employ a Rician or Gaussian noise model.
+
+     -x, --mask-image maskImageFilename
+          If a mask image is specified, denoising is only performed in the mask region.
+
+     -s, --shrink-factor (1)/2/3/...
+          Running noise correction on large images can be time consuming. To lessen
+          computation time, the input image can be resampled. The shrink factor, specified
+          as a single integer, describes this resampling. Shrink factor = 1 is the
+          default.
+
+     -p, --patch-radius 1
+                        1x1x1
+          Patch radius. Default = 1x1x1
+
+     -r, --search-radius 3
+                         3x3x3
+          Search radius. Default = 3x3x3.
+
+     -o, --output correctedImage
+                  [correctedImage,<noiseImage>]
+          The output consists of the noise corrected version of the input image.
+          Optionally, one can also output the estimated noise image.
+
+     --version
+          Get Version Information.
+
+     -v, --verbose (0)/1
+          Verbose output.
+
+     -h
+          Print the help menu (short version).
+
+     --help
+          Print the help menu.
+          <VALUES>: 1
+
+```
+
+## Multi-atlas segmentation
+
+![](./tools/jointfusion/figures/jointLabelFusion.png)
+
+## New work:  joint intensity fusion
+
+![](./tools/jointfusion/figures/jointIntensityFusion.png)
+
+## Possible uses
+
+* ``Correct'' images
+
+    * motion correction
+
+    * ``remove'' lesions
+
+* Project atlas set intensity signature
+
+* Use in ``corrective learning''
+
+## ```antsJointFusion``` --- contribution from Hongzhi Wang (with some added features)
+
+```bash
+$ antsJointFusion --help
+
+COMMAND:
+     antsJointFusion
+          antsJointFusion is an image fusion algorithm developed by Hongzhi Wang and Paul
+          Yushkevich which won segmentation challenges at MICCAI 2012 and MICCAI 2013. The
+          original label fusion framework was extended to accommodate intensities by Brian
+          Avants. This implementation is based on Paul's original ITK-style implementation
+          and Brian's ANTsR implementation. References include 1) H. Wang, J. W. Suh, S.
+          Das, J. Pluta, C. Craige, P. Yushkevich, Multi-atlas segmentation with joint
+          label fusion IEEE Trans. on Pattern Analysis and Machine Intelligence, 35(3),
+          611-623, 2013. and 2) H. Wang and P. A. Yushkevich, Multi-atlas segmentation
+          with joint label fusion and corrective learning--an open source implementation,
+          Front. Neuroinform., 2013.
+
+OPTIONS:
+     -d, --image-dimensionality 2/3/4
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, the program tries to infer the dimensionality from the input
+          image.
+
+     -t, --target-image targetImage
+                        [targetImageModality0,targetImageModality1,...,targetImageModalityN]
+          The target image (or multimodal target images) assumed to be aligned to a common
+          image domain.
+
+     -g, --atlas-image atlasImage
+                       [atlasImageModality0,atlasImageModality1,...,atlasImageModalityN]
+          The atlas image (or multimodal atlas images) assumed to be aligned to a common
+          image domain.
+
+     -l, --atlas-segmentation atlasSegmentation
+          The atlas segmentation images. For performing label fusion the number of
+          specified segmentations should be identical to the number of atlas image sets.
+
+     -a, --alpha 0.1
+          Regularization term added to matrix Mx for calculating the inverse. Default =
+          0.1
+
+     -b, --beta 2.0
+          Exponent for mapping intensity difference to the joint error. Default = 2.0
+
+     -r, --retain-label-posterior-images (0)/1
+          Retain label posterior probability images. Requires atlas segmentations to be
+          specified. Default = false
+
+     -f, --retain-atlas-voting-images (0)/1
+          Retain atlas voting images. Default = false
+
+     -c, --constrain-nonnegative (0)/1
+          Constrain solution to non-negative weights.
+
+     -p, --patch-radius 2
+                        2x2x2
+          Patch radius for similarity measures. Default = 2x2x2
+
+     -m, --patch-metric (PC)/MSQ
+          Metric to be used in determining the most similar neighborhood patch. Options
+          include Pearson's correlation (PC) and mean squares (MSQ). Default = PC (Pearson
+          correlation).
+
+     -s, --search-radius 3
+                         3x3x3
+                         searchRadiusMap.nii.gz
+          Search radius for similarity measures. Default = 3x3x3. One can also specify an
+          image where the value at the voxel specifies the isotropic search radius at that
+          voxel.
+
+     -e, --exclusion-image label[exclusionImage]
+          Specify an exclusion region for the given label.
+
+     -x, --mask-image maskImageFilename
+          If a mask image is specified, fusion is only performed in the mask region.
+
+     -o, --output labelFusionImage
+                  intensityFusionImageFileNameFormat
+                  [labelFusionImage,intensityFusionImageFileNameFormat,<labelPosteriorProbabilityImageFileNameFormat>,<atlasVotingWeightImageFileNameFormat>]
+          The output is the intensity and/or label fusion image. Additional optional
+          outputs include the label posterior probability images and the atlas voting
+          weight images.
+
+     --version
+          Get version information.
+
+     -v, --verbose (0)/1
+          Verbose output.
+
+     -h
+          Print the help menu (short version).
+
+     --help
+          Print the help menu.
+          <VALUES>: 1
+
+```

### 2016-07-17 simpleItkTalk.Rmd
ENH:  IBM presentation.

--- 2016-07-17 ants2015build.Rmd
@@
 ---
-title: <span style="color:red;">ANTs:</span><br /> A brief retrospective
-author: Nick Tustison
+title: The ITKv4 registration framework
+author: Nick Tustison and Brian Avants
 bibliography: REFERENCES.bib
@@
     highlight: tango
-    incremental: yes
+    incremental: false
     theme:  AnnArbor
@@
 ---
-# Founding developers
-
-##  Brian and Nick
-
-<BR><BR>
-
-![](./figures/brian_and_nick.png)
-
-<!--
-NOtes:
-* Worked together for almost 10 years
-* have learned tons
-* have written quite a bit of code together
--->
-
-## ANTs long term collaborators
-
-![](./figures/antscollab.jpg)
-
-$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
-
-<!--
-NOtes:
-* However, it is not just us
-* Other people have done quite a bit
-* and others who are not shown such as Arman
--->
-# ANTs lineage
+# Brief image registration history
 
@@
 
-## Image mapping & biology: Current
+## Image mapping & biology: current
 <BR><BR>
@@
 
-## ANTs family tree
+## Family tree
 
@@
 
-## Initial scope
+# ITKv3 $\longrightarrow$ ITKv4
 
-![](./figures/ants_initial_scope.png)
+## Extensions of ITKv3
 
-<!--
-Notes:
-* Brian work with Murray Grossman
-* First registration paper
-  - WBIR submission
-  - FEM registraiton using B-spline basis functions.
-  - "yeah, that registration is not that good---Jim would not like it."
--->
+* [Elastix](http://elastix.isi.uu.nl)
+* [Diffeomorphic Demons](http://www.insight-journal.org/browse/publication/154)
+* [BrainsFit](http://www.insight-journal.org/browse/publication/180)
+* [Advanced Normalization Tools (ANTs)](http://www.insight-journal.org/browse/publication/681)
 
-# Major tools
+## Basic components
 
-## Donoho?
+* Optimizers (v4)
+* Metrics (v4)
+* Transforms
+* Image registration methods (v4)
 
-<BR><BR>
-<span style="color:red;">_"Papers are just advertisements for the science."_</red>
-<BR>
+## Optimizers (v4) and scales estimators
 
-<!--
+* Scales estimator
+
+## Metrics (v4)
+
+* Intensity metrics
+    * mean squares
+    * mutual information (Mattes and joint histogram)
+    * neighborhood cross-correlation
+    * demons
+    * global correlation
+* Point-set metrics
+    * iterative closest point
+    * point-set expectation
+    * Jensen-Havrda-Charvat-Tsallis
+* Multi-metrics
+
+## Transforms
+
+* Linear (translation, rigid, \ldots)
+* B-spline
+* Displacement field (Gaussian, B-spline, SyN)
+* Velocity field (exponential, time-varying)
+* Composite
+
+## Image registration methods (v4)
+
+* $\rightarrow$ Input:
+    * Fixed image and initial fixed transform
+    * Moving image and initial moving transform
+    * metric(s)
+* $\leftarrow$ Output:
+    * Optimized moving transform
+* Special methods for SyN and velocity field transforms
+
+## Beyond original SyN
+
+\small
+
+![](./papers/figures/Frontiers_ITK.png)
+
+![](./papers/figures/Frontiers_BSplineSyN.png)
+
+# Brief ANTs introduction
 
@@
 -->
-
-## Beyond original SyN
-
-\small
-
-![](./papers/figures/Frontiers_ITK.png)
-
-![](./papers/figures/Frontiers_BSplineSyN.png)
 
@@
 
-## Template building:  creating the average Joe
+## Easy-to-use scripts
 
-![](./papers/figures/template0.jpg)
-
-## "Attractiveness" $\rightarrow$ mental processing?
-
-![](./papers/figures/template1.jpg)
-
-##  What about brains?
-
-![](./papers/figures/template3.jpg)
-
-## Templates facilitate computation
-
-![](./papers/figures/template4.jpg)
-
-## Gender discernibility?
-
-![](./papers/figures/template5.jpg)
-
-## ```antsMultivariateTemplateConstruction2.sh```
+* ``antsRegistrationSyN.sh``
+* ``antsRegistrationSyNQuick.sh``
 
 ```bash
-$ antsMultivariateTemplateConstruction2.sh
-
-Usage:
-
-antsMultivariateTemplateConstruction2.sh -d ImageDimension -o OutputPrefix <other options> <images>
-
-Compulsory arguments (minimal command line requires SGE/PBS cluster, otherwise use -c and
-  -j options):
-
-     -d:  ImageDimension: 2 or 3 (for 2 or 3 dimensional registration of single volume)
-   ImageDimension: 4 (for template generation of time-series data)
-
-     -o:  OutputPrefix; A prefix that is prepended to all output files.
-
-<images>  List of images in the current directory, eg *_t1.nii.gz. Should be at the end
-          of the command.  Optionally, one can specify a .csv or .txt file where each
-          line is the location of the input image.  One can also specify more than
-          one file for each image for multi-modal template construction (e.g. t1 and t2).
-          For the multi-modal case, the templates will be consecutively numbered (e.g.
-          template0.nii.gz, template1.nii.gz, ...).
-
-NB: All images to be added to the template should be in the same directory, and this
-    script should be invoked from that directory.
-
-Optional arguments:
-
-     -a   image statistic used to summarize images (default 1)
-          0 = mean
-          1 = mean of normalized intensities
-          2 = median
-
-     -b:  Backup images and results from all iterations (default = 0):  Boolean to save
-          the transform files, bias corrected, and warped images for each iteration.
-
-     -c:  Control for parallel computation (default 0):
-          0 = run serially
-          1 = SGE qsub
-          2 = use PEXEC (localhost)
-          3 = Apple XGrid
-          4 = PBS qsub
-
-     -e   use single precision ( default 1 )
-
-     -g:  Gradient step size (default 0.25): smaller in magnitude results in more
-          cautious steps.
-
-     -i:  Iteration limit (default 4): iterations of the template construction
-          (Iteration limit)*NumImages registrations.
-
-     -j:  Number of cpu cores to use locally for pexec option (default 2; requires "-c 2")
-
-     -k:  Number of modalities used to construct the template (default 1):  For example,
-          if one wanted to create a multimodal template consisting of T1,T2,and FA
-          components ("-k 3").
-
-     -w:  Modality weights used in the similarity metric (default = 1): specified as
-          e.g. 1x0.5x0.75.
-
-     -q:  Max iterations for each pairwise registration (default = 100x100x70x20):
-          specified in the form ...xJxKxL where
-            J = max iterations at coarsest resolution (here, reduced by power of 2^2)
-            K = middle resolution iterations (here, reduced by power of 2)
-            L = fine resolution iteratioxns (here, full resolution).
-          Finer resolutions take much more time per iteration than coarser resolutions.
-
-     -f:  Shrink factors (default = 6x4x2x1):  Also in the same form as -q max iterations.
-          Needs to have the same number of components.
-
-     -s:  Smoothing factors (default = 3x2x1x0):  Also in the same form as -q max
-          iterations.  Needs to have the same number of components.
-
-     -n:  N4BiasFieldCorrection of moving image: 0 == off, 1 == on (default 1).
-
-     -p:  Commands to prepend to job scripts (e.g., change into appropriate directory, set
-          paths, etc)
-
-     -r:  Do rigid-body registration of inputs before creating template (default 0):
-          0 == off 1 == on. Only useful when you do not have an initial template
-
-     -l:  Use linear image registration stages during the pairwise (template/subject)
-          deformable registration.  Otherwise, registration is limited to SyN or
-          B-spline SyN (see '-t' option).  This is '1' by default.
-
-     -m:  Type of similarity metric used for registration (default = CC):  Options are
-            CC = cross-correlation
-            MI = mutual information
-            MSQ = mean square difference
-            DEMONS = demon's metric
-          A similarity metric per modality can be specified.  If the CC metric is chosen,
-          one can also specify the radius in brackets, e.g. '-m CC[4]'.
-
-     -t:  Type of transformation model used for registration (default = SyN):  Options are
-            SyN = Greedy SyN
-            BSplineSyN = Greedy B-spline SyN
-            TimeVaryingVelocityField = Time-varying velocity field
-            TimeVaryingBSplineVelocityField = Time-varying B-spline velocity field
-
-     -u:  Walltime (default = 20:00:00):  Option for PBS qsub specifying requested time
-          per pairwise registration.
-
-     -v:  Memory limit (default = 8gb):  Option for PBS qsub specifying requested memory
-          per pairwise registration.
-
-     -x:  XGrid arguments (e.g., -x "-p password -h controlhost")
-
-     -y:  Update the template with the full affine transform (default 1). If 0, the rigid
-          component of the affine transform will not be used to update the template. If your
-          template drifts in translation or orientation try -y 0.
-
-     -z:  Use this this volume as the target of all inputs. When not used, the script
-          will create an unbiased starting point by averaging all inputs. Use the full
-          path.
-          For multiple modalities, specify -z modality1.nii.gz -z modality2.nii.gz ...
-          in the same modality order as the input images.
-
-Example:
-
-antsMultivariateTemplateConstruction2.sh -d 3 -i 3 -k 1 -f 4x2x1 -s 2x1x0vox -q 30x20x4 -t SyN  -m CC -c 0 -o MY sub*avg.nii.gz
-
-Multimodal example:
-
-antsMultivariateTemplateConstruction2.sh -d 3 -i 3 -k 2 -f 4x2x1 -s 2x1x0vox -q 30x20x4 -t SyN -z t1.nii.gz -z t2.nii.gz  -m CC -c 0 -o MY templateInput.csv
-
-where templateInput.csv contains
-
-subjectA_t1.nii.gz,subjectA_t2.nii.gz
-subjectB_t1.nii.gz,subjectB_t2.nii.gz
-...
-
---------------------------------------------------------------------------------------
-ANTS was created by:
---------------------------------------------------------------------------------------
-Brian B. Avants, Nick Tustison and Gang Song
-Penn Image Computing And Science Laboratory
-University of Pennsylvania
-
-Please reference http://www.ncbi.nlm.nih.gov/pubmed/20851191 when employing this script
-in your studies. A reproducible evaluation of ANTs similarity metric performance in
-brain image registration:
-
-* Avants BB, Tustison NJ, Song G, Cook PA, Klein A, Gee JC. Neuroimage, 2011.
-
-Also see http://www.ncbi.nlm.nih.gov/pubmed/19818860 for more details.
-
-The script has been updated and improved since this publication.
-
---------------------------------------------------------------------------------------
-Script by Nick Tustison
---------------------------------------------------------------------------------------
-Apple XGrid support by Craig Stark
---------------------------------------------------------------------------------------
+$ antsRegistrationSyN.sh -d 3 \
+                         -f fixed.nii.gz \
+                         -m moving.nii.gz \
+                         -o output
 ```
-
-<!--
-
-## Nonparametric nonuniform intensity normalization (N3)
-
-* Developed at the Montreal Neurological Institute (John Sled, 1998)
-
-* Part of the standard preprocessing protocol in large scale projects such as ADNI
-
-* The traditional de facto standard in MRI bias correction
-    + good performance
-    + *public availability*
-
-* Public availability --- set of perl scripts coordinating various C++ programs
-
-* "*Let's incorporate N3 into ANTs!*"
--->
-
-## N3 adoption issues
-
-![](./tools/n4/figures/whyN4.png)
-
-<div align="center"><img src="./tools/n4/figures/whyN4.png" frameborder="0"></img></div>
-
-<!--
-
-## N4
-
-* comparative [evaluation](http://www.ncbi.nlm.nih.gov/pubmed/20378467)
-
-* small spline distances (useful for higher magnet strengths)
-
-* multiresolution
-
-* weighted regional mask (used in [`antsAtroposN4.sh`](https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh))
-
-* fast execution times
-
-* _publicly available_
-
-* tested nightly within the ITK dashboard system
--->
-
-## ```N4BiasFieldCorrection```
-
-```bash
-$ N4BiasFieldCorrection --help
-
-COMMAND:
-     N4BiasFieldCorrection
-          N4 is a variant of the popular N3 (nonparameteric nonuniform normalization)
-          retrospective bias correction algorithm. Based on the assumption that the
-          corruption of the low frequency bias field can be modeled as a convolution of
-          the intensity histogram by a Gaussian, the basic algorithmic protocol is to
-          iterate between deconvolving the intensity histogram by a Gaussian, remapping
-          the intensities, and then spatially smoothing this result by a B-spline modeling
-          of the bias field itself. The modifications from and improvements obtained over
-          the original N3 algorithm are described in the following paper: N. Tustison et
-          al., N4ITK: Improved N3 Bias Correction, IEEE Transactions on Medical Imaging,
-          29(6):1310-1320, June 2010.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, N4 tries to infer the dimensionality from the input image.
-
-     -i, --input-image inputImageFilename
-          A scalar image is expected as input for bias correction. Since N4 log transforms
-          the intensities, negative values or values close to zero should be processed
-          prior to correction.
-
-     -x, --mask-image maskImageFilename
-          If a mask image is specified, the final bias correction is only performed in the
-          mask region. If a weight image is not specified, only intensity values inside
-          the masked region are used during the execution of the algorithm. If a weight
-          image is specified, only the non-zero weights are used in the execution of the
-          algorithm although the mask region defines where bias correction is performed in
-          the final output. Otherwise bias correction occurs over the entire image domain.
-          See also the option description for the weight image.
-
-     -r, --rescale-intensities 0/(1)
-          At each iteration, a new intensity mapping is calculated and applied but there
-          is nothing which constrains the new intensity range to be within certain values.
-          The result is that the range can "drift" from the original at each iteration.
-          This option rescales to the [min,max] range of the original image intensities
-          within the user-specified mask.
-
-     -w, --weight-image weightImageFilename
-          The weight image allows the user to perform a relative weighting of specific
-          voxels during the B-spline fitting. For example, some studies have shown that N3
-          performed on white matter segmentations improves performance. If one has a
-          spatial probability map of the white matter, one can use this map to weight the
-          b-spline fitting towards those voxels which are more probabilistically
-          classified as white matter. See also the option description for the mask image.
-
-     -s, --shrink-factor 1/2/3/4/...
-          Running N4 on large images can be time consuming. To lessen computation time,
-          the input image can be resampled. The shrink factor, specified as a single
-          integer, describes this resampling. Shrink factors <= 4 are commonly used.
-
-     -c, --convergence [<numberOfIterations=50x50x50x50>,<convergenceThreshold=0.0>]
-          Convergence is determined by calculating the coefficient of variation between
-          subsequent iterations. When this value is less than the specified threshold from
-          the previous iteration or the maximum number of iterations is exceeded the
-          program terminates. Multiple resolutions can be specified by using 'x' between
-          the number of iterations at each resolution, e.g. 100x50x50.
-
-     -b, --bspline-fitting [splineDistance,<splineOrder=3>]
-                           [initialMeshResolution,<splineOrder=3>]
-          These options describe the b-spline fitting parameters. The initial b-spline
-          mesh at the coarsest resolution is specified either as the number of elements in
-          each dimension, e.g. 2x2x3 for 3-D images, or it can be specified as a single
-          scalar parameter which describes the isotropic sizing of the mesh elements. The
-          latter option is typically preferred. For each subsequent level, the spline
-          distance decreases in half, or equivalently, the number of mesh elements doubles
-          Cubic splines (order = 3) are typically used.
-
-     -t, --histogram-sharpening [<FWHM=0.15>,<wienerNoise=0.01>,<numberOfHistogramBins=200>]
-          These options describe the histogram sharpening parameters, i.e. the
-          deconvolution step parameters described in the original N3 algorithm. The
-          default values have been shown to work fairly well.
-
-     -o, --output correctedImage
-                  [correctedImage,<biasField>]
-          The output consists of the bias corrected version of the input image.
-          Optionally, one can also output the estimated bias field.
-
-     --version
-          Get Version Information.
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-```
-
-<--
-##  Atropos -- cutting the threads of fate
-
-![](./papers/figures/Atropos_deGoya.jpg)
--->
-
-<!--
-Notes:
-* Can we use Suyash's code?
-* What about graph cuts?
--->
-
-## Atropos:  flexible code base
-
-"20+ years of development.  <br>_Show me the code!_"
-
-![](./tools/atropos/figures/atropos.png)
-
-## ```Atropos```
-
-```bash
-$ Atropos --help
-
-COMMAND:
-     Atropos
-          A finite mixture modeling (FMM) segmentation approach with possibilities for
-          specifying prior constraints. These prior constraints include the specification
-          of a prior label image, prior probability images (one for each class), and/or an
-          MRF prior to enforce spatial smoothing of the labels. Similar algorithms include
-          FAST and SPM. Reference: Avants BB, Tustison NJ, Wu J, Cook PA, Gee JC. An open
-          source multivariate framework for n-tissue segmentation with evaluation on
-          public data. Neuroinformatics. 2011 Dec;9(4):381-400.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, Atropos tries to infer the dimensionality from the first input
-          image.
-
-     -a, --intensity-image [intensityImage,<adaptiveSmoothingWeight>]
-          One or more scalar images is specified for segmentation using the
-          -a/--intensity-image option. For segmentation scenarios with no prior
-          information, the first scalar image encountered on the command line is used to
-          order labelings such that the class with the smallest intensity signature is
-          class '1' through class 'N' which represents the voxels with the largest
-          intensity values. The optional adaptive smoothing weight parameter is applicable
-          only when using prior label or probability images. This scalar parameter is to
-          be specified between [0,1] which smooths each labeled region separately and
-          modulates the intensity measurement at each voxel in each intensity image
-          between the original intensity and its smoothed counterpart. The smoothness
-          parameters are governed by the -b/--bspline option.
-
-     -b, --bspline [<numberOfLevels=6>,<initialMeshResolution=1x1x...>,<splineOrder=3>]
-          If the adaptive smoothing weights are > 0, the intensity images are smoothed in
-          calculating the likelihood values. This is to account for subtle intensity
-          differences across the same tissue regions.
-
-     -i, --initialization Random[numberOfClasses]
-                          Otsu[numberOfTissueClasses]
-                          KMeans[numberOfTissueClasses,<clusterCenters(in ascending order and for first intensity image only)>]
-                          PriorProbabilityImages[numberOfTissueClasses,fileSeriesFormat(index=1 to numberOfClasses) or vectorImage,priorWeighting,<priorProbabilityThreshold>]
-                          PriorLabelImage[numberOfTissueClasses,labelImage,priorWeighting]
-          To initialize the FMM parameters, one of the following options must be
-          specified. If one does not have prior label or probability images we recommend
-          using kmeans as it is typically faster than otsu and can be used with
-          multivariate initialization. However, since a Euclidean distance on the inter
-          cluster distances is used, one might have to appropriately scale the additional
-          input images. Random initialization is meant purely for intellectual curiosity.
-          The prior weighting (specified in the range [0,1]) is used to modulate the
-          calculation of the posterior probabilities between the likelihood*mrfprior and
-          the likelihood*mrfprior*prior. For specifying many prior probability images for
-          a multi-label segmentation, we offer a minimize usage option (see -m). With that
-          option one can specify a prior probability threshold in which only those pixels
-          exceeding that threshold are stored in memory.
-
-     -s, --partial-volume-label-set label1xlabel2xlabel3
-          The partial volume estimation option allows one to modelmixtures of classes
-          within single voxels. Atropos currently allows the user to model two class
-          mixtures per partial volume class. The user specifies a set of class labels per
-          partial volume class requested. For example, suppose the user was performing a
-          classic 3-tissue segmentation (csf, gm, wm) using kmeans initialization. Suppose
-          the user also wanted to model the partial voluming effects between csf/gm and
-          gm/wm. The user would specify it using -i kmeans[3] and -s 1x2 -s 2x3. So, for
-          this example, there would be 3 tissue classes and 2 partial volume classes.
-          Optionally,the user can limit partial volume handling to mrf considerations only
-          whereby the output would only be the three tissues.
-
-     --use-partial-volume-likelihoods 1/(0)
-                                      true/(false)
-          The user can specify whether or not to use the partial volume likelihoods, in
-          which case the partial volume class is considered separate from the tissue
-          classes. Alternatively, one can use the MRF only to handle partial volume in
-          which case, partial volume voxels are not considered as separate classes.
-
-     -p, --posterior-formulation Socrates[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
-                                 Plato[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
-                                 Aristotle[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
-                                 Sigmoid[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]]
-          Different posterior probability formulations are possible as are different
-          update options. To guarantee theoretical convergence properties, a proper
-          formulation of the well-known iterated conditional modes (ICM) uses an
-          asynchronous update step modulated by a specified annealing temperature. If one
-          sets the AnnealingTemperature > 1 in the posterior formulation a traditional
-          code set for a proper ICM update will be created. Otherwise, a synchronous
-          update step will take place at each iteration. The annealing temperature, T,
-          converts the posteriorProbability to posteriorProbability^(1/T) over the course
-          of optimization.
-
-     -x, --mask-image maskImageFilename
-          The image mask (which is required) defines the region which is to be labeled by
-          the Atropos algorithm.
-
-     -c, --convergence numberOfIterations
-                       [<numberOfIterations=5>,<convergenceThreshold=0.001>]
-          Convergence is determined by calculating the mean maximum posterior probability
-          over the region of interest at each iteration. When this value decreases or
-          increases less than the specified threshold from the previous iteration or the
-          maximum number of iterations is exceeded the program terminates.
-
-     -k, --likelihood-model Gaussian
-                            HistogramParzenWindows[<sigma=1.0>,<numberOfBins=32>]
-                            ManifoldParzenWindows[<pointSetSigma=1.0>,<evaluationKNeighborhood=50>,<CovarianceKNeighborhood=0>,<kernelSigma=0>]
-                            JointShapeAndOrientationProbability[<shapeSigma=1.0>,<numberOfShapeBins=64>, <orientationSigma=1.0>, <numberOfOrientationBins=32>]
-                            LogEuclideanGaussian
-          Both parametric and non-parametric options exist in Atropos. The Gaussian
-          parametric option is commonly used (e.g. SPM & FAST) where the mean and standard
-          deviation for the Gaussian of each class is calculated at each iteration. Other
-          groups use non-parametric approaches exemplified by option 2. We recommend using
-          options 1 or 2 as they are fairly standard and the default parameters work
-          adequately.
-
-     -m, --mrf [<smoothingFactor=0.3>,<radius=1x1x...>]
-               [<mrfCoefficientImage>,<radius=1x1x...>]
-          Markov random field (MRF) theory provides a general framework for enforcing
-          spatially contextual constraints on the segmentation solution. The default
-          smoothing factor of 0.3 provides a moderate amount of smoothing. Increasing this
-          number causes more smoothing whereas decreasing the number lessens the
-          smoothing. The radius parameter specifies the mrf neighborhood. Different update
-          schemes are possible but only the asynchronous updating has theoretical
-          convergence properties.
-
-     -g, --icm [<useAsynchronousUpdate=1>,<maximumNumberOfICMIterations=1>,<icmCodeImage=''>]
-          Asynchronous updating requires the construction of an ICM code image which is a
-          label image (with labels in the range {1,..,MaximumICMCode}) constructed such
-          that no MRF neighborhood has duplicate ICM code labels. Thus, to update the
-          voxel class labels we iterate through the code labels and, for each code label,
-          we iterate through the image and update the voxel class label that has the
-          corresponding ICM code label. One can print out the ICM code image by specifying
-          an ITK-compatible image filename.
-
-     -r, --use-random-seed 0/(1)
-          Initialize internal random number generator with a random seed. Otherwise,
-          initialize with a constant seed number.
-
-     -o, --output [classifiedImage,<posteriorProbabilityImageFileNameFormat>]
-          The output consists of a labeled image where each voxel in the masked region is
-          assigned a label from 1, 2, ..., N. Optionally, one can also output the
-          posterior probability images specified in the same format as the prior
-          probability images, e.g. posterior%02d.nii.gz (C-style file name formatting).
-
-     -u, --minimize-memory-usage (0)/1
-          By default, memory usage is not minimized, however, if this is needed, the
-          various probability and distance images are calculated on the fly instead of
-          being stored in memory at each iteration. Also, if prior probability images are
-          used, only the non-negligible pixel values are stored in memory.
-          <VALUES>: 0
-
-     -w, --winsorize-outliers BoxPlot[<lowerPercentile=0.25>,<upperPercentile=0.75>,<whiskerLength=1.5>]
-                              GrubbsRosner[<significanceLevel=0.05>,<winsorizingLevel=0.10>]
-          To remove the effects of outliers in calculating the weighted mean and weighted
-          covariance, the user can opt to remove the outliers through the options
-          specified below.
-
-     -e, --use-euclidean-distance (0)/1
-          Given prior label or probability images, the labels are propagated throughout
-          the masked region so that every voxel in the mask is labeled. Propagation is
-          done by using a signed distance transform of the label. Alternatively,
-          propagation of the labels with the fast marching filter respects the distance
-          along the shape of the mask (e.g. the sinuous sulci and gyri of the cortex.
-          <VALUES>: 0
-
-     -l, --label-propagation whichLabel[lambda=0.0,<boundaryProbability=1.0>]
-          The propagation of each prior label can be controlled by the lambda and boundary
-          probability parameters. The latter parameter is the probability (in the range
-          [0,1]) of the label on the boundary which increases linearly to a maximum value
-          of 1.0 in the interior of the labeled region. The former parameter dictates the
-          exponential decay of probability propagation outside the labeled region from the
-          boundary probability, i.e. boundaryProbability*exp( -lambda * distance ).
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-```
-
-<!--
-
-## Atropos + N4 $\rightarrow$ `antsAtroposN4.sh`
-
-![](./tools/atropos/figures/atroposFlow.png)
--->
-
-# Putting it all together---the ANTs cortical thickness pipeline
-
-## Cortical thickness studies
-
-```{r, results='asis', echo = FALSE}
-conditions <- c( "Tetris-playing ability", "Huntington’s disease", "schizophrenia", "bipolar disorder",
-                 "Alzheimer’s disease", "frontotemporal dementia", "Parkinson’s disease",
-                 "Williams syndrome", "multiple sclerosis", "autism", "migraines",
-                 "chronic smoking", "alcoholism", "cocaine addiction", "Tourette syndrome in children",
-                 "scoliosis in female adolescents", "early-onset blindness", "chronic pancreatitis",
-                 "obsessive-compulsive disorder", "ADHD", "obesity", "heritable depression",
-                 "elderly depression", "age", "gender",
-                 "handedness", "intelligence", "athletic ability", "meditative practices", "musical ability",
-                 "tendency toward criminality", "childhood sexual abuse in female adolescents",
-                  "traumatic brain injury", "untreated male-to-female transsexuality" )
-
-conditionsDF <- data.frame( Column1 = conditions[1:floor( 0.5*length(conditions) )], Column2 = conditions[( 1+floor( 0.5*length(conditions) ) ):length(conditions)] )
-knitr::kable( conditionsDF )
-```
-
-<!--
-
-## ANTs-related background
-
-* Sandy, Brian, and <span style="color:red;">DiReCT</span>
-    + used other tools such as FMRIB Automated Segmentation Tool (FAST)
-    + `KellySlater.cxx`
-* pipedream scripts "adequate for Penn data."
-* `KellyKapowski.cxx` and `antsCorticalThickness.sh`
-* _"Let's evaluate on open data."_
-* and, eventually, _"Let's compare with FreeSurfer."_
--->
-
-## Basic components of the pipeline
-
-1. template building (offline)
-2. brain extraction
-3. cortical thickness estimation
-4. cortical parcellation
-
-## Sample results
-
-![](./evaluation/figures/components.png)
-
-## The ANTs structural brain mapping workflow
-
-![](./evaluation/figures/pipeline.png)
-
-## Template building
-
-*Tailor data to your specific cohort*
-
-![](./evaluation/figures/templates.png)
-
-<!--
-* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
-* Acquisition and anonymization (e.g. defacing) protocols are often different.
--->
-
-## Template priors
-
-![](./evaluation/figures/templatePriors.png)
-
-<!--
-Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
-to produce auxiliary images which are used for brain extraction and brain segmentation.
--->
-
-<!--
-
-## Brain extraction comparison
-
-![](./evaluation/figures/brainExtraction.png)
-
-Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
-the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
--->
-
-<!--
-
-## Brain segmentation
-
-![](./evaluation/figures/brainSegmentation.png)
-
-Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.
--->
-
-## Cortical thickness estimation
-
-![](./evaluation/figures/corticalThicknessEstimation.png)
-
-<!--
-In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
--->
-
-## _But without ground truth, how does one evaluate the pipeline?_
-
-## Predict age and gender
-
-$AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$
-
-## Open science principles
-
-![](./evaluation/figures/ageDistribution.png)
-
-<!--
-* Public data sets (IXI, NKI, OASIS, MMRR)
-* $>$ 1200 subjects, age 4 to over 94 years old
--->
-
-## Prediction from cortical thickness data
-
-![](./evaluation/figures/evaluation.png)
-
-## Age prediction per site
-
-![](./evaluation/figures/agePredictionPerSite.png)
-
-## Regional importance comparison
-
-![](./evaluation/figures/antsvfreesurfer_Importance.png)
-
-ANTs (left) vs. FreeSurfer (right)
-
-## Regional measurements
-
-![](./evaluation/figures/antsvfreesurfer_regionalPlots.png)
-
-# But, wait, there's more!
-
-##
-
-[__Data availability__](https://github.com/ntustison/KapowskiChronicles)
-
-*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"  Sure, why not?
-
-*  "_I was wondering if you would make available the CT in each ROI for each subject..._" Sure, why not?  Would you also like the surface areas and volumes?
-
-*  "_Can I have one or more of the templates that you used for your study?_" Would you like the priors as well?
-
-##  What about using both the T1 & T2?
-
-## ANTs tools are multivariate
-
-![](./evaluation/figures/rfRmse05ANTsT1T2.png)
-
-## Arno-thick-in-the-head (ATITH)
-
-_What if we made a crude estimate of the cortical thickness?_
-
-$$thickness_{ROI} = \frac{volume_{ROI}}{area_{ROI}}$$
-
-## Make sure you estimate the [surface area](http://www.insight-journal.org/browse/publication/852) correctly!
-
-![](./evaluation/figures/LabelThickness.png)
-
-## So how does ATITH compare with ANTs, FS?
-
-## Prediction from cortical thickness data
-
-![](./evaluation/figures/atith.png)
-
-## Brain constellation maps
-
-![](./evaluation/figures/brainConstellationMaps.png)
-
-## _Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_
-
-## Contribution from Jose
-
-```bash
-$ DenoiseImage
-
-COMMAND:
-     DenoiseImage
-          Denoise an image using a spatially adaptive filter originally described in J. V.
-          Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive
-          Non-Local Means Denoising of MR Images With Spatially Varying Noise Levels,
-          Journal of Magnetic Resonance Imaging, 31:192-203, June 2010.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, the program tries to infer the dimensionality from the input
-          image.
-
-     -i, --input-image inputImageFilename
-          A scalar image is expected as input for noise correction.
-
-     -n, --noise-model (Rician)/Gaussian
-          Employ a Rician or Gaussian noise model.
-
-     -s, --shrink-factor (1)/2/3/...
-          Running noise correction on large images can be time consuming. To lessen
-          computation time, the input image can be resampled. The shrink factor, specified
-          as a single integer, describes this resampling. Shrink factor = 1 is the
-          default.
-
-     -o, --output correctedImage
-                  [correctedImage,<noiseImage>]
-          The output consists of the noise corrected version of the input image.
-          Optionally, one can also output the estimated noise image.
-
-     --version
-          Get Version Information.
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-```
-
-## _Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_
-
-![](./evaluation/figures/rfRmseDenoise05.png)
-
-# But the best part is ...
-
-## it is absolutely free!
-
-```bash
-${ANTSPATH}/antsCorticalThickness.sh \
-  -a IXI/T1/IXI002-Guys-0828-T1.nii.gz \
-  -e IXI/template/T_template0.nii.gz \
-  -m IXI/template/T_template0ProbabilityMask.nii.gz \
-  -f IXI/template/T_template0ExtractionMask.nii.gz \
-  -p IXI/template/Priors/priors%d.nii.gz \
-  -o IXI/ANTsResults/IXI002-Guys-0828-
-```
-
-# Joint label/intensity fusion
-
-## Multi-atlas labeling
-
-![](./competitions/figures/NKI30_MALF.png)
-
-## Multi-atlas segmentation
-
-![](./tools/jointfusion/figures/jointLabelFusion.png)
-
-## Multi-atlas 2012 results
-
-![](./competitions/figures/MALF2012.png)
-
-## New work:  joint intensity fusion
-
-![](./tools/jointfusion/figures/jointIntensityFusion.png)
-
-<!--
-
-## Possible uses
-
-* ``Correct'' images
-    * motion correction
-    * lesions
-* Project atlas set intensity signature
--->

### 2016-07-17 simpleItkTalk/antsBrief.Rmd
ENH:  IBM presentation.

--- 2016-07-17 simpleItkTalk.Rmd
@@
----
-title: The ITKv4 registration framework
-author: Nick Tustison and Brian Avants
-bibliography: REFERENCES.bib
-logo:    figures/antsLogoBase.png
-output:
-  beamer_presentation:
-    colortheme: dolphin
-    fonttheme:  structurebold
-    highlight: tango
-    incremental: false
-    theme:  AnnArbor
-    includes:
-      in_header: mystyle.tex
-    toc: yes
-  pdf_document:
-    toc: true
-    highlight: zenburn
-  html_document:
-    toc: true
-    theme: readable
-  revealjs_presentation:
-    pandoc_args: [ "--slide-level", "2" ]
-    incremental: true
-    widescreen: true
-    smaller: false
-    theme: night
-    transition: fade
-    highlight: zenburn
-    center: true
-    self_contained: false
-  ioslides_presentation:
-    css: atk.css
-    incremental: false
-    widescreen: true
-    smaller: false
-    fig_width: 5
----
-# Brief image registration history
-
-## Image mapping and perception: 1877
-
-Francis Galton: _Can we see criminality in the face?_
-
-![](./figures/galton.png)
-
-_What about syphilis, mental illness?_
-
-<!--
-Notes:
-* Use of "composite portraiture" and what he called "eugenics"
-* Can we see criminality, mental illness, syphilis, and others in facial features?
-* Despite the obvious prejudices driving his research, he was a pioneer.
--->
-
-<!--
-
-##
-
-![](./background/figures/FrancisGalton2.jpg)
--->
-
-<!--
-Notes:
-* Another example where he has manually categorized facial features and try to combine them
-* Did not find much---composite tends to blend away to normality.
--->
-
-##  Speaking of criminality...
-
-_Can we say anything about the U.S. Congress?_
-
-![](./background/figures/congressPersons.png)
-
-__Maybe they should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__
-
-<!--
-Notes:
--->
-
-##  Image mapping & biology:  1917
-
-D'Arcy Thompson: _Comparison of related forms_
-
-![](./figures/dthompson.png)
--->
-
-<!--
-Notes:
-* Book: On Growth and Form
-* Descriptive not susceptible to hypothesis testing
-* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
--->
-
-## Image mapping & biology: current
-<BR><BR>
-_Look where we are now!_
-<BR><BR>
-![](./background/figures/r16xr85.png)
-
-## Family tree
-
-![](./figures/lineage.jpg)
-
-<!--
-References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
--->
-
-# ITKv3 $\longrightarrow$ ITKv4
-
-## Extensions of ITKv3
-
-* [Elastix](http://elastix.isi.uu.nl)
-* [Diffeomorphic Demons](http://www.insight-journal.org/browse/publication/154)
-* [BrainsFit](http://www.insight-journal.org/browse/publication/180)
-* [Advanced Normalization Tools (ANTs)](http://www.insight-journal.org/browse/publication/681)
-
-## Basic components
-
-* Optimizers (v4)
-* Metrics (v4)
-* Transforms
-* Image registration methods (v4)
-
-## Optimizers (v4) and scales estimators
-
-* Scales estimator
-
-## Metrics (v4)
-
-* Intensity metrics
-    * mean squares
-    * mutual information (Mattes and joint histogram)
-    * neighborhood cross-correlation
-    * demons
-    * global correlation
-* Point-set metrics
-    * iterative closest point
-    * point-set expectation
-    * Jensen-Havrda-Charvat-Tsallis
-* Multi-metrics
-
-## Transforms
-
-* Linear (translation, rigid, \ldots)
-* B-spline
-* Displacement field (Gaussian, B-spline, SyN)
-* Velocity field (exponential, time-varying)
-* Composite
-
-## Image registration methods (v4)
-
-* $\rightarrow$ Input:
-    * Fixed image and initial fixed transform
-    * Moving image and initial moving transform
-    * metric(s)
-* $\leftarrow$ Output:
-    * Optimized moving transform
-* Special methods for SyN and velocity field transforms
-
-## Beyond original SyN
-
-\small
-
-![](./papers/figures/Frontiers_ITK.png)
-
-![](./papers/figures/Frontiers_BSplineSyN.png)
-
 # Brief ANTs introduction

### 2016-07-17 simpleItkTalk/background.Rmd
ENH:  IBM presentation.

--- 2016-07-17 simpleItkTalk.Rmd
@@
----
-title: The ITKv4 registration framework
-author: Nick Tustison and Brian Avants
-bibliography: REFERENCES.bib
-logo:    figures/antsLogoBase.png
-output:
-  beamer_presentation:
-    colortheme: dolphin
-    fonttheme:  structurebold
-    highlight: tango
-    incremental: false
-    theme:  AnnArbor
-    includes:
-      in_header: mystyle.tex
-    toc: yes
-  pdf_document:
-    toc: true
-    highlight: zenburn
-  html_document:
-    toc: true
-    theme: readable
-  revealjs_presentation:
-    pandoc_args: [ "--slide-level", "2" ]
-    incremental: true
-    widescreen: true
-    smaller: false
-    theme: night
-    transition: fade
-    highlight: zenburn
-    center: true
-    self_contained: false
-  ioslides_presentation:
-    css: atk.css
-    incremental: false
-    widescreen: true
-    smaller: false
-    fig_width: 5
----
 # Brief image registration history
@@
 -->
-
-# ITKv3 $\longrightarrow$ ITKv4
-
-## Extensions of ITKv3
-
-* [Elastix](http://elastix.isi.uu.nl)
-* [Diffeomorphic Demons](http://www.insight-journal.org/browse/publication/154)
-* [BrainsFit](http://www.insight-journal.org/browse/publication/180)
-* [Advanced Normalization Tools (ANTs)](http://www.insight-journal.org/browse/publication/681)
-
-## Basic components
-
-* Optimizers (v4)
-* Metrics (v4)
-* Transforms
-* Image registration methods (v4)
-
-## Optimizers (v4) and scales estimators
-
-* Scales estimator
-
-## Metrics (v4)
-
-* Intensity metrics
-    * mean squares
-    * mutual information (Mattes and joint histogram)
-    * neighborhood cross-correlation
-    * demons
-    * global correlation
-* Point-set metrics
-    * iterative closest point
-    * point-set expectation
-    * Jensen-Havrda-Charvat-Tsallis
-* Multi-metrics
-
-## Transforms
-
-* Linear (translation, rigid, \ldots)
-* B-spline
-* Displacement field (Gaussian, B-spline, SyN)
-* Velocity field (exponential, time-varying)
-* Composite
-
-## Image registration methods (v4)
-
-* $\rightarrow$ Input:
-    * Fixed image and initial fixed transform
-    * Moving image and initial moving transform
-    * metric(s)
-* $\leftarrow$ Output:
-    * Optimized moving transform
-* Special methods for SyN and velocity field transforms
-
-## Beyond original SyN
-
-\small
-
-![](./papers/figures/Frontiers_ITK.png)
-
-![](./papers/figures/Frontiers_BSplineSyN.png)
-
-# Brief ANTs introduction
-
-## Symmetric Normalization (SyN)
-
-$\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt + \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2$
-
-![](./papers/figures/fishes.png)
-
-NOtes:
-* Previously discussed Brians work
-* The variant most widely used
--->
-
-## Diffeomorphisms:  Occam's razor modeling
-
-![](./figures/sillyputty.png)
-
-_differentiable map with differentiable inverse_
-
-## Diffeomoprhisms:  fine-grained and flexible maps
-
-![](./figures/highresdiffeos.jpg)
-
-<!--
-
-## Diffeomorphisms: image parameterization in a metric space
-
-![](./figures/shape_appearance.png)
--->
-
-## ```antsRegistration```
-<BR><BR>
-
-```bash
-$ antsRegistration --help
-
-COMMAND:
-     antsRegistration
-          This program is a user-level registration application meant to utilize
-          ITKv4-only classes. The user can specify any number of "stages" where a stage
-          consists of a transform; an image metric; and iterations, shrink factors, and
-          smoothing sigmas for each level.Note that dimensionality, metric, transform,
-          output, convergence, shrink-factors and smoothing-sigmas parameters are
-          mandatory.
-
-OPTIONS:
-     --version
-          Get Version Information.
-
-     -d, --dimensionality 2/3
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, we try to infer the dimensionality from the input image.
-
-     -o, --output outputTransformPrefix
-                  [outputTransformPrefix,<outputWarpedImage>,<outputInverseWarpedImage>]
-          Specify the output transform prefix (output format is .nii.gz ). Optionally, one
-          can choose to warp the moving image to the fixed space and, if the inverse
-          transform exists, one can also output the warped fixed image. Note that only the
-          images specified in the first metric call are warped. Use antsApplyTransforms to
-          warp other images using the resultant transform(s).
-
-     -j, --save-state saveSateAsTransform
-          Specify the output file for the current state of the registration. The state
-          file is written to an hdf5 composite file. It is specially usefull if we want to
-          save the current state of a SyN registration to the disk, so we can load and
-          restore that later to continue the next registration process directly started
-          from the last saved state. The output file of this flag is the same as the
-          write-composite-transform, unless the last transform is a SyN transform. In that
-          case, the inverse displacement field of the SyN transform is also added to the
-          output composite transform. Again notice that this file cannot be treated as a
-          transform, and restore-state option must be used to load the written file by
-          this flag.
-
-     -k, --restore-state restoreStateAsATransform
-          Specify the initial state of the registration which get immediately used to
-          directly initialize the registration process. The flag is mutually exclusive
-          with other intialization flags.If this flag is used, none of the
-          initial-moving-transform and initial-fixed-transform cannot be used.
-
-     -a, --write-composite-transform 1/(0)
-          Boolean specifying whether or not the composite transform (and its inverse, if
-          it exists) should be written to an hdf5 composite file. This is false by default
-          so that only the transform for each stage is written to file.
-          <VALUES>: 0
-
-     -p, --print-similarity-measure-interval <unsignedIntegerValue>
-          Prints out the CC similarity metric measure between the full-size input fixed
-          and the transformed moving images at each iteration a value of 0 (the default)
-          indicates that the full scale computation should not take placeany value greater
-          than 0 represents the interval of full scale metric computation.
-          <VALUES>: 0
-
-     -v, --write-interval-volumes <unsignedIntegerValue>
-          Writes out the output volume at each iteration. It helps to present the
-          registration process as a short movie a value of 0 (the default) indicates that
-          this option should not take placeany value greater than 0 represents the
-          interval between the iterations which outputs are written to the disk.
-          <VALUES>: 0
-
-     -z, --collapse-output-transforms (1)/0
-          Collapse output transforms. Specifically, enabling this option combines all
-          adjacent transforms wherepossible. All adjacent linear transforms are written to
-          disk in the forman itk affine transform (called xxxGenericAffine.mat).
-          Similarly, all adjacent displacement field transforms are combined when written
-          to disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available)).Also, an
-          output composite transform including the collapsed transforms is written to the
-          disk (called outputCollapsed(Inverse)Composite).
-          <VALUES>: 1
-
-     -i, --initialize-transforms-per-stage (1)/0
-          Initialize linear transforms from the previous stage. By enabling this option,
-          the current linear stage transform is directly intialized from the previous
-          stage's linear transform; this allows multiple linear stages to be run where
-          each stage directly updates the estimated linear transform from the previous
-          stage. (e.g. Translation -> Rigid -> Affine).
-          <VALUES>: 0
-
-     -n, --interpolation Linear
-                         NearestNeighbor
-                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]
-                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]
-                         BSpline[<order=3>]
-                         CosineWindowedSinc
-                         WelchWindowedSinc
-                         HammingWindowedSinc
-                         LanczosWindowedSinc
-          Several interpolation options are available in ITK. These have all been made
-          available. Currently the interpolator choice is only used to warp (and possibly
-          inverse warp) the final output image(s).
-
-     -g, --restrict-deformation PxQxR
-          This option allows the user to restrict the optimization of the displacement
-          field, translation, rigid or affine transform on a per-component basis. For
-          example, if one wants to limit the deformation or rotation of 3-D volume to the
-          first two dimensions, this is possible by specifying a weight vector of '1x1x0'
-          for a deformation field or '1x1x0x1x1x0' for a rigid
-          transformation.Low-dimensional restriction only works if there are no preceding
-          transformations.
-
-     -q, --initial-fixed-transform initialTransform
-                                   [initialTransform,<useInverse>]
-                                   [fixedImage,movingImage,initializationFeature]
-          Specify the initial fixed transform(s) which get immediately incorporated into
-          the composite transform. The order of the transforms is stack-esque in that the
-          last transform specified on the command line is the first to be applied. In
-          addition to initialization with ITK transforms, the user can perform an initial
-          translation alignment by specifying the fixed and moving images and selecting an
-          initialization feature. These features include using the geometric center of the
-          images (=0), the image intensities (=1), or the origin of the images (=2).
-
-     -r, --initial-moving-transform initialTransform
-                                    [initialTransform,<useInverse>]
-                                    [fixedImage,movingImage,initializationFeature]
-          Specify the initial moving transform(s) which get immediately incorporated into
-          the composite transform. The order of the transforms is stack-esque in that the
-          last transform specified on the command line is the first to be applied. In
-          addition to initialization with ITK transforms, the user can perform an initial
-          translation alignment by specifying the fixed and moving images and selecting an
-          initialization feature. These features include using the geometric center of the
-          images (=0), the image intensities (=1), or the origin of the images (=2).
-
-     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]
-                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]
-                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]
-                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]
-          These image metrics are available--- CC: ANTS neighborhood cross correlation,
-          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global
-          Correlation. The "metricWeight" variable is used to modulate the per stage
-          weighting of the metrics. The metrics can also employ a sampling strategy
-          defined by a sampling percentage. The sampling strategy defaults to 'None' (aka
-          a dense sampling of one sample per voxel), otherwise it defines a point set over
-          which to optimize the metric. The point set can be on a regular lattice or a
-          random lattice of points slightly perturbed to minimize aliasing artifacts.
-          samplingPercentage defines the fraction of points to select from the domain. In
-          addition, three point set metrics are available: Euclidean (ICP), Point-set
-          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).
-
-     -t, --transform Rigid[gradientStep]
-                     Affine[gradientStep]
-                     CompositeAffine[gradientStep]
-                     Similarity[gradientStep]
-                     Translation[gradientStep]
-                     BSpline[gradientStep,meshSizeAtBaseLevel]
-                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
-                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
-                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]
-                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]
-                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
-                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
-                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]
-                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]
-          Several transform options are available. The gradientStep or learningRate
-          characterizes the gradient descent optimization and is scaled appropriately for
-          each transform using the shift scales estimator. Subsequent parameters are
-          transform-specific and can be determined from the usage. For the B-spline
-          transforms one can also specify the smoothing in terms of spline distance (i.e.
-          knot spacing).
-
-     -c, --convergence MxNxO
-                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]
-          Convergence is determined from the number of iterations per level and is
-          determined by fitting a line to the normalized energy profile of the last N
-          iterations (where N is specified by the window size) and determining the slope
-          which is then compared with the convergence threshold.
-
-     -s, --smoothing-sigmas MxNxO...
-          Specify the sigma of gaussian smoothing at each level. Units are given in terms
-          of voxels ('vox') or physical spacing ('mm'). Example usage is '4x2x1mm' and
-          '4x2x1vox' where no units implies voxel spacing.
-
-     -f, --shrink-factors MxNxO...
-          Specify the shrink factor for the virtual domain (typically the fixed image) at
-          each level.
-
-     -u, --use-histogram-matching
-          Histogram match the images before registration.
-
-     -l, --use-estimate-learning-rate-once
-          turn on the option that lets you estimate the learning rate step size only at
-          the beginning of each level. * useful as a second stage of fine-scale
-          registration.
-
-     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]
-          Winsorize data based on specified quantiles.
-
-     -x, --masks [fixedImageMask,movingImageMask]
-          Image masks to limit voxels considered by the metric.
-
-     --float
-          Use 'float' instead of 'double' for computations.
-          <VALUES>: 0
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu. Will also print values used on the current command line
-          call.
-```
-
-## Easy-to-use scripts
-
-* ``antsRegistrationSyN.sh``
-* ``antsRegistrationSyNQuick.sh``
-
-```bash
-$ antsRegistrationSyN.sh -d 3 \
-                         -f fixed.nii.gz \
-                         -m moving.nii.gz \
-                         -o output
-```

### 2016-07-17 simpleItkTalk/itkv4.Rmd
ENH:  IBM presentation.

--- 2016-07-17 simpleItkTalk.Rmd
@@
----
-title: The ITKv4 registration framework
-author: Nick Tustison and Brian Avants
-bibliography: REFERENCES.bib
-logo:    figures/antsLogoBase.png
-output:
-  beamer_presentation:
-    colortheme: dolphin
-    fonttheme:  structurebold
-    highlight: tango
-    incremental: false
-    theme:  AnnArbor
-    includes:
-      in_header: mystyle.tex
-    toc: yes
-  pdf_document:
-    toc: true
-    highlight: zenburn
-  html_document:
-    toc: true
-    theme: readable
-  revealjs_presentation:
-    pandoc_args: [ "--slide-level", "2" ]
-    incremental: true
-    widescreen: true
-    smaller: false
-    theme: night
-    transition: fade
-    highlight: zenburn
-    center: true
-    self_contained: false
-  ioslides_presentation:
-    css: atk.css
-    incremental: false
-    widescreen: true
-    smaller: false
-    fig_width: 5
----
-# Brief image registration history
-
-## Image mapping and perception: 1877
-
-Francis Galton: _Can we see criminality in the face?_
-
-![](./figures/galton.png)
-
-_What about syphilis, mental illness?_
-
-<!--
-Notes:
-* Use of "composite portraiture" and what he called "eugenics"
-* Can we see criminality, mental illness, syphilis, and others in facial features?
-* Despite the obvious prejudices driving his research, he was a pioneer.
--->
-
-<!--
-
-##
-
-![](./background/figures/FrancisGalton2.jpg)
--->
-
-<!--
-Notes:
-* Another example where he has manually categorized facial features and try to combine them
-* Did not find much---composite tends to blend away to normality.
--->
-
-##  Speaking of criminality...
-
-_Can we say anything about the U.S. Congress?_
-
-![](./background/figures/congressPersons.png)
-
-__Maybe they should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__
-
-<!--
-Notes:
--->
-
-##  Image mapping & biology:  1917
-
-D'Arcy Thompson: _Comparison of related forms_
-
-![](./figures/dthompson.png)
--->
-
-<!--
-Notes:
-* Book: On Growth and Form
-* Descriptive not susceptible to hypothesis testing
-* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
--->
-
-## Image mapping & biology: current
-<BR><BR>
-_Look where we are now!_
-<BR><BR>
-![](./background/figures/r16xr85.png)
-
-## Family tree
-
-![](./figures/lineage.jpg)
-
-<!--
-References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
--->
-
 # ITKv3 $\longrightarrow$ ITKv4
@@
 ![](./papers/figures/Frontiers_BSplineSyN.png)
-
-# Brief ANTs introduction
-
-## Symmetric Normalization (SyN)
-
-$\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt + \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2$
-
-![](./papers/figures/fishes.png)
-
-NOtes:
-* Previously discussed Brians work
-* The variant most widely used
--->
-
-## Diffeomorphisms:  Occam's razor modeling
-
-![](./figures/sillyputty.png)
-
-_differentiable map with differentiable inverse_
-
-## Diffeomoprhisms:  fine-grained and flexible maps
-
-![](./figures/highresdiffeos.jpg)
-
-<!--
-
-## Diffeomorphisms: image parameterization in a metric space
-
-![](./figures/shape_appearance.png)
--->
-
-## ```antsRegistration```
-<BR><BR>
-
-```bash
-$ antsRegistration --help
-
-COMMAND:
-     antsRegistration
-          This program is a user-level registration application meant to utilize
-          ITKv4-only classes. The user can specify any number of "stages" where a stage
-          consists of a transform; an image metric; and iterations, shrink factors, and
-          smoothing sigmas for each level.Note that dimensionality, metric, transform,
-          output, convergence, shrink-factors and smoothing-sigmas parameters are
-          mandatory.
-
-OPTIONS:
-     --version
-          Get Version Information.
-
-     -d, --dimensionality 2/3
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, we try to infer the dimensionality from the input image.
-
-     -o, --output outputTransformPrefix
-                  [outputTransformPrefix,<outputWarpedImage>,<outputInverseWarpedImage>]
-          Specify the output transform prefix (output format is .nii.gz ). Optionally, one
-          can choose to warp the moving image to the fixed space and, if the inverse
-          transform exists, one can also output the warped fixed image. Note that only the
-          images specified in the first metric call are warped. Use antsApplyTransforms to
-          warp other images using the resultant transform(s).
-
-     -j, --save-state saveSateAsTransform
-          Specify the output file for the current state of the registration. The state
-          file is written to an hdf5 composite file. It is specially usefull if we want to
-          save the current state of a SyN registration to the disk, so we can load and
-          restore that later to continue the next registration process directly started
-          from the last saved state. The output file of this flag is the same as the
-          write-composite-transform, unless the last transform is a SyN transform. In that
-          case, the inverse displacement field of the SyN transform is also added to the
-          output composite transform. Again notice that this file cannot be treated as a
-          transform, and restore-state option must be used to load the written file by
-          this flag.
-
-     -k, --restore-state restoreStateAsATransform
-          Specify the initial state of the registration which get immediately used to
-          directly initialize the registration process. The flag is mutually exclusive
-          with other intialization flags.If this flag is used, none of the
-          initial-moving-transform and initial-fixed-transform cannot be used.
-
-     -a, --write-composite-transform 1/(0)
-          Boolean specifying whether or not the composite transform (and its inverse, if
-          it exists) should be written to an hdf5 composite file. This is false by default
-          so that only the transform for each stage is written to file.
-          <VALUES>: 0
-
-     -p, --print-similarity-measure-interval <unsignedIntegerValue>
-          Prints out the CC similarity metric measure between the full-size input fixed
-          and the transformed moving images at each iteration a value of 0 (the default)
-          indicates that the full scale computation should not take placeany value greater
-          than 0 represents the interval of full scale metric computation.
-          <VALUES>: 0
-
-     -v, --write-interval-volumes <unsignedIntegerValue>
-          Writes out the output volume at each iteration. It helps to present the
-          registration process as a short movie a value of 0 (the default) indicates that
-          this option should not take placeany value greater than 0 represents the
-          interval between the iterations which outputs are written to the disk.
-          <VALUES>: 0
-
-     -z, --collapse-output-transforms (1)/0
-          Collapse output transforms. Specifically, enabling this option combines all
-          adjacent transforms wherepossible. All adjacent linear transforms are written to
-          disk in the forman itk affine transform (called xxxGenericAffine.mat).
-          Similarly, all adjacent displacement field transforms are combined when written
-          to disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available)).Also, an
-          output composite transform including the collapsed transforms is written to the
-          disk (called outputCollapsed(Inverse)Composite).
-          <VALUES>: 1
-
-     -i, --initialize-transforms-per-stage (1)/0
-          Initialize linear transforms from the previous stage. By enabling this option,
-          the current linear stage transform is directly intialized from the previous
-          stage's linear transform; this allows multiple linear stages to be run where
-          each stage directly updates the estimated linear transform from the previous
-          stage. (e.g. Translation -> Rigid -> Affine).
-          <VALUES>: 0
-
-     -n, --interpolation Linear
-                         NearestNeighbor
-                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]
-                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]
-                         BSpline[<order=3>]
-                         CosineWindowedSinc
-                         WelchWindowedSinc
-                         HammingWindowedSinc
-                         LanczosWindowedSinc
-          Several interpolation options are available in ITK. These have all been made
-          available. Currently the interpolator choice is only used to warp (and possibly
-          inverse warp) the final output image(s).
-
-     -g, --restrict-deformation PxQxR
-          This option allows the user to restrict the optimization of the displacement
-          field, translation, rigid or affine transform on a per-component basis. For
-          example, if one wants to limit the deformation or rotation of 3-D volume to the
-          first two dimensions, this is possible by specifying a weight vector of '1x1x0'
-          for a deformation field or '1x1x0x1x1x0' for a rigid
-          transformation.Low-dimensional restriction only works if there are no preceding
-          transformations.
-
-     -q, --initial-fixed-transform initialTransform
-                                   [initialTransform,<useInverse>]
-                                   [fixedImage,movingImage,initializationFeature]
-          Specify the initial fixed transform(s) which get immediately incorporated into
-          the composite transform. The order of the transforms is stack-esque in that the
-          last transform specified on the command line is the first to be applied. In
-          addition to initialization with ITK transforms, the user can perform an initial
-          translation alignment by specifying the fixed and moving images and selecting an
-          initialization feature. These features include using the geometric center of the
-          images (=0), the image intensities (=1), or the origin of the images (=2).
-
-     -r, --initial-moving-transform initialTransform
-                                    [initialTransform,<useInverse>]
-                                    [fixedImage,movingImage,initializationFeature]
-          Specify the initial moving transform(s) which get immediately incorporated into
-          the composite transform. The order of the transforms is stack-esque in that the
-          last transform specified on the command line is the first to be applied. In
-          addition to initialization with ITK transforms, the user can perform an initial
-          translation alignment by specifying the fixed and moving images and selecting an
-          initialization feature. These features include using the geometric center of the
-          images (=0), the image intensities (=1), or the origin of the images (=2).
-
-     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]
-                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]
-                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]
-                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]
-          These image metrics are available--- CC: ANTS neighborhood cross correlation,
-          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global
-          Correlation. The "metricWeight" variable is used to modulate the per stage
-          weighting of the metrics. The metrics can also employ a sampling strategy
-          defined by a sampling percentage. The sampling strategy defaults to 'None' (aka
-          a dense sampling of one sample per voxel), otherwise it defines a point set over
-          which to optimize the metric. The point set can be on a regular lattice or a
-          random lattice of points slightly perturbed to minimize aliasing artifacts.
-          samplingPercentage defines the fraction of points to select from the domain. In
-          addition, three point set metrics are available: Euclidean (ICP), Point-set
-          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).
-
-     -t, --transform Rigid[gradientStep]
-                     Affine[gradientStep]
-                     CompositeAffine[gradientStep]
-                     Similarity[gradientStep]
-                     Translation[gradientStep]
-                     BSpline[gradientStep,meshSizeAtBaseLevel]
-                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
-                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
-                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]
-                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]
-                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
-                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
-                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]
-                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]
-          Several transform options are available. The gradientStep or learningRate
-          characterizes the gradient descent optimization and is scaled appropriately for
-          each transform using the shift scales estimator. Subsequent parameters are
-          transform-specific and can be determined from the usage. For the B-spline
-          transforms one can also specify the smoothing in terms of spline distance (i.e.
-          knot spacing).
-
-     -c, --convergence MxNxO
-                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]
-          Convergence is determined from the number of iterations per level and is
-          determined by fitting a line to the normalized energy profile of the last N
-          iterations (where N is specified by the window size) and determining the slope
-          which is then compared with the convergence threshold.
-
-     -s, --smoothing-sigmas MxNxO...
-          Specify the sigma of gaussian smoothing at each level. Units are given in terms
-          of voxels ('vox') or physical spacing ('mm'). Example usage is '4x2x1mm' and
-          '4x2x1vox' where no units implies voxel spacing.
-
-     -f, --shrink-factors MxNxO...
-          Specify the shrink factor for the virtual domain (typically the fixed image) at
-          each level.
-
-     -u, --use-histogram-matching
-          Histogram match the images before registration.
-
-     -l, --use-estimate-learning-rate-once
-          turn on the option that lets you estimate the learning rate step size only at
-          the beginning of each level. * useful as a second stage of fine-scale
-          registration.
-
-     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]
-          Winsorize data based on specified quantiles.
-
-     -x, --masks [fixedImageMask,movingImageMask]
-          Image masks to limit voxels considered by the metric.
-
-     --float
-          Use 'float' instead of 'double' for computations.
-          <VALUES>: 0
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu. Will also print values used on the current command line
-          call.
-```
-
-## Easy-to-use scripts
-
-* ``antsRegistrationSyN.sh``
-* ``antsRegistrationSyNQuick.sh``
-
-```bash
-$ antsRegistrationSyN.sh -d 3 \
-                         -f fixed.nii.gz \
-                         -m moving.nii.gz \
-                         -o output
-```

### 2016-07-17 README.R

@@ -19,13 +19,14 @@ buildrmd='ants2015build.Rmd'
 ########   Morning    ##########
 
 # Retrospective
-rawrmds <- c( "retrospective/retrospective.Rmd", "retrospective/neuroimage_fmri.Rmd",
-              "background/people.Rmd", "background/background.Rmd",
+rawrmds <- c( "format.Rmd",
+              "background/people2.Rmd",
+              "background/background.Rmd",
               "papers/papers.Rmd",
-              "philosophy/circularity/circularity.Rmd",
-              "competitions/competitions.Rmd",
-              "summary/summary.Rmd"
-                )
+              "evaluation/antsvfreesurfer2.Rmd",
+              "evaluation/antsvfreesurfer2_extra.Rmd",
+              "tools/jointfusion/jointfusion.Rmd"
+               )
 
 # Research talk
 # rawrmds <- c( "evaluation/antsvfreesurfer2.Rmd",

### 2016-07-17 makePresentationIBM.R

@@ -1,0 +1,43 @@
+#!/usr/bin/env Rscript
+
+####################
+#
+#   July 19, 2016
+#
+#
+#
+#
+#####################
+
+library( ggplot2 )
+library( rmarkdown )
+
+srcDir <- "./"
+buildrmd <- 'ibm.Rmd'
+
+########   Morning    ##########
+
+# Retrospective
+
+rawrmds <- c( "format.Rmd",
+              "background/people2.Rmd",
+              "licenses/licenses.Rmd",
+              "competitions/competitions.Rmd",
+              "background/background.Rmd",
+              "papers/papers.Rmd",
+              "evaluation/antsvfreesurfer2.Rmd",
+              "evaluation/antsvfreesurfer2_extra.Rmd",
+              "antsr/antsr.Rmd"
+               )
+
+for ( x in 1:length(rawrmds) ) {
+  if ( x == 1 )
+    {
+    cmd<-paste( "cat ", rawrmds[x], " > ", buildrmd )
+    } else {
+      cmd<-paste( "cat ", rawrmds[x], " >> ", buildrmd )
+    }
+  system( cmd )
+  }
+
+render( buildrmd, clean = TRUE )

### 2016-07-17 simpleItkTalk.R

@@ -1,0 +1,27 @@
+#!/usr/bin/env Rscript
+
+library( ggplot2 )
+library( shiny )
+library( ggvis )
+library( rmarkdown )
+
+buildrmd <- 'simpleItkTalk.Rmd'
+
+####################
+#
+#         * http://www.itk.org/Wiki/SimpleITK/Tutorials/MICCAI2015
+#         * May 5, 2015
+#
+####################
+
+rawrmds <- c( "format.Rmd",
+              "simpleItkTalk/background.Rmd",
+              "simpleItkTalk/itkv4.Rmd",
+              "simpleItkTalk/antsBrief.Rmd"
+               )
+
+for ( x in 1:length( rawrmds ) ) {
+  if ( x == 1 )  cmd<-paste( "cat ",rawrmds[x]," > ",buildrmd ) else cmd <- paste( "cat ", rawrmds[x], " >> ", buildrmd )
+  system( cmd )
+}
+render( buildrmd, clean=TRUE )

### 2016-07-17 evaluation/antsvfreesurfer2.Rmd
ENH:  Remove slides.

@@
 * and, eventually, _"Let's compare with FreeSurfer."_
--->
 
@@
 ![](./evaluation/figures/components.png)
+
+-->
 
@@
 
+<!--
+
 ## Open science principles
@@
 
-<!--
 * Public data sets (IXI, NKI, OASIS, MMRR)

### 2016-07-17 ibm.Rmd
ENH:  Remove slides.

@@
 <!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->
-# ANTs lineage
-
-## Image mapping and perception: 1877
-
-Francis Galton: _Can we see criminality in the face?_
-
-![](./figures/galton.png)
-
-_What about syphilis, mental illness?_
-
-<!--
-Notes:
-* Use of "composite portraiture" and what he called "eugenics"
-* Can we see criminality, mental illness, syphilis, and others in facial features?
-* Despite the obvious prejudices driving his research, he was a pioneer.
--->
-
-<!--
-
-##
-
-![](./background/figures/FrancisGalton2.jpg)
--->
-
-<!--
-Notes:
-* Another example where he has manually categorized facial features and try to combine them
-* Did not find much---composite tends to blend away to normality.
--->
-
-##  Speaking of criminality...
-
-_Can we say anything about the U.S. Congress?_
-
-![](./background/figures/congressPersons.png)
-
-__Maybe they should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__
-
-<!--
-Notes:
--->
-
-##  Image mapping & biology:  1917
-
-D'Arcy Thompson: _Comparison of related forms_
-
-![](./figures/dthompson.png)
--->
-
-<!--
-Notes:
-* Book: On Growth and Form
-* Descriptive
-* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
--->
-
-## Image mapping & biology: Current
-<BR><BR>
-_Look where we are now!_
-<BR><BR>
-![](./background/figures/r16xr85.png)
-
-<!--
-## ANTs family tree
-
-![](./figures/lineage.jpg)
--->
-
-<!--
-References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
--->
-
-<!--
-## Initial scope
-
-![](./figures/ants_initial_scope.png)
--->
-
-<!--
-Notes:
-* Brian work with Murray Grossman
-* First registration paper
-  - WBIR submission
-  - FEM registraiton using B-spline basis functions.
-  - "yeah, that registration is not that good---Jim would not like it."
--->
 
@@
 
+<!--
+
 ## Neuro tools
@@
 ![](./tools/figures/coreANtsToolsLung.png)
+
+-->
 
@@
 
--->
-
 ## Diffeomoprhisms:  differentiable map with diff. inverse
@@
 ![](./figures/highresdiffeos.jpg)
+
+-->
 
@@
 
+-->
+
 ## The ANTs structural brain mapping workflow
@@
 
+<!--
+
 ## Arno-thick-in-the-head (ATITH)
@@
 
-<!--
-
 ## Make sure you estimate the [surface area](http://www.insight-journal.org/browse/publication/852) correctly!
@@
 _So how does ATITH compare with ANTs, FS?_
--->
+
 ## Prediction from cortical thickness data
@@
 ![](./evaluation/figures/atith.png)
-
-<!--
 
@@
 ![](./longitudinal/figures/longitudinalPipeline.png)
+
+<!--
 
@@
 
+-->
+
 # Current work and Advanced Normalization Tools in R (ANTsR)

### 2016-07-17 ibm.tex
ENH:  Remove slides.

@@
 
-\section{ANTs lineage}\label{ants-lineage}
-
-\begin{frame}{Image mapping and perception: 1877}
-
-Francis Galton: \emph{Can we see criminality in the face?}
-
-\includegraphics{./figures/galton.png}
-
-\emph{What about syphilis, mental illness?}
-
-\end{frame}
-
-\begin{frame}{Speaking of criminality\ldots{}}
-
-\emph{Can we say anything about the U.S. Congress?}
-
-\includegraphics{./background/figures/congressPersons.png}
-
-\textbf{Maybe they should have used
-\href{https://github.com/ntustison/CongressionalFaceTemplates}{ANTs}?}
-
-\end{frame}
-
-\begin{frame}{Image mapping \& biology: 1917}
-
-D'Arcy Thompson: \emph{Comparison of related forms}
-
-\includegraphics{./figures/dthompson.png} --\textgreater{}
-
-\end{frame}
-
-\begin{frame}{Image mapping \& biology: Current}
-
- \emph{Look where we are now!}
-\includegraphics{./background/figures/r16xr85.png}
-
-\end{frame}
-
 \section{Major ANTs utilities}\label{major-ants-utilities}
@@
  \emph{``Papers are just advertisements for the science.''}
-
-\end{frame}
-
-\begin{frame}{Neuro tools}
-
-\includegraphics{./tools/figures/coreANtsToolsNeuro.png}
-
-\end{frame}
-
-\begin{frame}{Pulmonary tools}
-
-\includegraphics{./tools/figures/coreANtsToolsLung.png}
-
-\end{frame}
-
-\begin{frame}{Diffeomoprhisms: differentiable map with diff. inverse}
-
-\includegraphics{./figures/highresdiffeos.jpg}
 
@@
 
-\begin{frame}{Basic components of the pipeline}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  template building (offline)
-\item
-  brain extraction
-\item
-  cortical thickness estimation
-\item
-  cortical parcellation
-\end{enumerate}
-
-\end{frame}
-
-\begin{frame}{Sample results}
-
-\includegraphics{./evaluation/figures/components.png}
-
-\end{frame}
-
 \begin{frame}{The ANTs structural brain mapping workflow}
@@
 
-\begin{frame}{Open science principles}
-
-\includegraphics{./evaluation/figures/ageDistribution.png}
-
-\end{frame}
-
 \begin{frame}{Prediction from cortical thickness data}
@@
 
-\begin{frame}{Arno-thick-in-the-head (ATITH)}
-
-\emph{What if we made a crude estimate of the cortical thickness?}
-
-\[thickness_{ROI} = \frac{volume_{ROI}}{area_{ROI}}\]
-
-\end{frame}
-
-\begin{frame}{Prediction from cortical thickness data}
-
-\includegraphics{./evaluation/figures/atith.png}
-
-\end{frame}
-
 \begin{frame}{Longitudinal processing}
@@
 \includegraphics{./longitudinal/figures/longitudinalPipeline.png}
-
-\end{frame}
-
-\section{But the best part is \ldots{}}\label{but-the-best-part-is}
-
-\begin{frame}[fragile]{it is absolutely ``free''!}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\OtherTok{$\{ANTSPATH\}}\KeywordTok{/antsCorticalThickness.sh} \NormalTok{\textbackslash{}}
-  \NormalTok{-a IXI/T1/IXI002-Guys-0828-T1.nii.gz \textbackslash{}}
-  \NormalTok{-e IXI/template/T_template0.nii.gz \textbackslash{}}
-  \NormalTok{-m IXI/template/T_template0ProbabilityMask.nii.gz \textbackslash{}}
-  \NormalTok{-f IXI/template/T_template0ExtractionMask.nii.gz \textbackslash{}}
-  \NormalTok{-p IXI/template/Priors/priors%d.nii.gz \textbackslash{}}
-  \NormalTok{-o IXI/ANTsResults/IXI002-Guys-0828-}
-\end{Highlighting}
-\end{Shaded}
-
-\end{frame}
-
-\begin{frame}
-
-\href{https://github.com/ntustison/KapowskiChronicles}{\textbf{Data
-availability}}
-
-\begin{itemize}
-\item
-  ``\emph{Hey, can I have the FreeSurfer measurements for the entorhinal
-  cortex?}'' Sure, why
-  not?---\href{http://www.ncbi.nlm.nih.gov/pubmed/26565394}{Hasan, et
-  al., J Neuroimaging}
-\item
-  ``\emph{Can I have one or more of the templates that you used for your
-  study?}'' Would you like the priors as well?
-\end{itemize}
 

### 2016-07-17 makePresentationIBM.R

@@ -23,7 +23,6 @@ rawrmds <- c( "format.Rmd",
               "background/people2.Rmd",
               "licenses/licenses.Rmd",
               "competitions/competitions.Rmd",
-              "background/background.Rmd",
               "papers/papers.Rmd",
               "evaluation/antsvfreesurfer2.Rmd",
               "evaluation/antsvfreesurfer2_extra.Rmd",

### 2016-07-17 ibm.tex
ENH:  Last minute refinements.

@@
 
-\begin{frame}[fragile]{\texttt{antsMultivariateTemplateConstruction.sh}}
+\begin{frame}{Nonparametric nonuniform intensity normalization (N3)}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{$ }\KeywordTok{antsMultivariateTemplateConstruction.sh}
+\begin{itemize}
+\item
+  Developed at the Montreal Neurological Institute (John Sled, 1998)
+\item
+  Part of the standard preprocessing protocol in large scale projects
+  such as ADNI
+\item
+  The traditional de facto standard in MRI bias correction
 
-\KeywordTok{Usage}\NormalTok{:}
-
-\KeywordTok{antsMultivariateTemplateConstruction.sh} \NormalTok{-d ImageDimension -o OUTPREFIX }\KeywordTok{<}\NormalTok{other options}\KeywordTok{>} \KeywordTok{<}\NormalTok{images}\KeywordTok{>}
-
-\KeywordTok{Compulsory} \NormalTok{arguments (minimal command line requires SGE cluster, otherwise use -c }\KeywordTok{&} \KeywordTok{-j} \NormalTok{options)}\KeywordTok{:}
-
-     \KeywordTok{-d}\NormalTok{:  ImageDimension: 2 or 3 (for 2 or 3 dimensional registration of single volume)}
-   \KeywordTok{ImageDimension}\NormalTok{: 4 (for template generation of time-series data)}
-
-     \KeywordTok{-o}\NormalTok{:  OUTPREFIX}\KeywordTok{;} \KeywordTok{A} \NormalTok{prefix that is prepended to all output files.}
-
-\KeywordTok{<images>}  \NormalTok{List of images in the current directory, eg *_t1.nii.gz. Should be at the end}
-          \KeywordTok{of} \NormalTok{the command.  Optionally, one can specify a .csv or .txt file where each}
-          \KeywordTok{line} \NormalTok{is the location of the input image.  One can also specify more than}
-          \KeywordTok{one} \NormalTok{file for each image for multi-modal template construction (e.g. t1 and t2)}\KeywordTok{.}
-          \KeywordTok{For} \NormalTok{the multi-modal case, the templates will be consecutively numbered (e.g.}
-          \KeywordTok{template0.nii.gz}\NormalTok{, template1.nii.gz, ...)}\KeywordTok{.}
-
-\KeywordTok{NB}\NormalTok{: All images to be added to the template should be in the same directory, and this script}
-\KeywordTok{should} \NormalTok{be invoked from that directory.}
-
-\KeywordTok{Optional} \NormalTok{arguments:}
-
-     \KeywordTok{-c}\NormalTok{:  Control for parallel computation (default 1) }\KeywordTok{--} \NormalTok{0 == run serially,  1 == SGE qsub,}
-          \KeywordTok{2} \NormalTok{== use PEXEC (localhost), }\KeywordTok{3} \NormalTok{== Apple XGrid, 4 == PBS qsub, 5 == SLURM}
-
-     \KeywordTok{-g}\NormalTok{:  Gradient step size (default 0.25) }\KeywordTok{--} \NormalTok{smaller in magnitude results in more cautious steps}
-
-     \KeywordTok{-i}\NormalTok{:  Iteration limit (default 4) }\KeywordTok{--} \NormalTok{iterations of the template construction (Iteration limit)}\KeywordTok{*NumImages} \NormalTok{registrations.}
-
-     \KeywordTok{-j}\NormalTok{:  Number of cpu cores to use (default 2}\KeywordTok{;} \KeywordTok{--} \NormalTok{requires }\StringTok{"-c 2"}\NormalTok{)}
-
-     \KeywordTok{-k}\NormalTok{:  Number of modalities used to construct the template (default 1)}
-
-     \KeywordTok{-w}\NormalTok{:  Modality weights used in the similarity metric (default = 1) }\KeywordTok{---} \NormalTok{specified as e.g. 1x0.5x0.75}
-
-     \KeywordTok{-m}\NormalTok{:  Max-iterations in each registration}
-
-     \KeywordTok{-n}\NormalTok{:  N4BiasFieldCorrection of moving image (default 1) }\KeywordTok{--} \NormalTok{0 == off, 1 == on}
-
-     \KeywordTok{-p}\NormalTok{:  Commands to prepend to job scripts (e.g., change into appropriate directory, set paths, etc)}
-
-     \KeywordTok{-r}\NormalTok{:  Do rigid-body registration of inputs before creating template (default 0) }\KeywordTok{--} \NormalTok{0 == off 1 == on. Only useful when}
-          \KeywordTok{you} \NormalTok{do not have an initial template}
-
-     \KeywordTok{-s}\NormalTok{:  Type of similarity metric used for registration.}
-
-     \KeywordTok{-t}\NormalTok{:  Type of transformation model used for registration.}
-
-     \KeywordTok{-x}\NormalTok{:  XGrid arguments (e.g., -x }\StringTok{"-p password -h controlhost"}\NormalTok{)}
-
-     \KeywordTok{-y}\NormalTok{:  Update the template with the full affine transform (default 1)}\KeywordTok{.} \KeywordTok{If} \NormalTok{0, the rigid}
-          \KeywordTok{component} \NormalTok{of the affine transform will not be used to update the template. If your}
-          \KeywordTok{template} \NormalTok{drifts in translation or orientation try -y 0.}
-
-     \KeywordTok{-z}\NormalTok{:  Use this this volume as the target of all inputs. When not used, the script}
-          \KeywordTok{will} \NormalTok{create an unbiased starting point by averaging all inputs. Use the full path!}
-
-     \KeywordTok{-b}\NormalTok{:  Boolean for saving iteration output to directories (default = 0)}\KeywordTok{.}
-
-\KeywordTok{Example}\NormalTok{:}
-
-\KeywordTok{antsMultivariateTemplateConstruction.sh} \NormalTok{-d 3 -m 30x50x20 -t GR -s CC -c 1 -o MY -z InitialTemplate.nii.gz  *RF*T1x.nii.gz}
-
-\KeywordTok{-} \NormalTok{In this example 30x50x20 iterations per registration are used for template creation (that is the default)}
-\KeywordTok{-} \NormalTok{Greedy-SyN and CC are the metrics to guide the mapping.}
-\KeywordTok{-} \NormalTok{Output is prepended with MY and the initial template is InitialTemplate.nii.gz (optional)}\KeywordTok{.}
-\KeywordTok{-} \NormalTok{The -c option is set to 1, which will result in using the Sun Grid Engine (SGE) }\KeywordTok{to} \NormalTok{distribute the computation.}
-\KeywordTok{-} \NormalTok{if you do not have SGE, read the help for multi-core computation on the local machine, or Apple X-grid options.}
-
-\KeywordTok{--------------------------------------------------------------------------------------}
-\KeywordTok{ANTS} \NormalTok{was created by:}
-\KeywordTok{--------------------------------------------------------------------------------------}
-\KeywordTok{Brian} \NormalTok{B. Avants, Nick Tustison and Gang Song}
-\KeywordTok{Penn} \NormalTok{Image Computing And Science Laboratory}
-\KeywordTok{University} \NormalTok{of Pennsylvania}
-
-\KeywordTok{Please} \NormalTok{reference http://www.ncbi.nlm.nih.gov/pubmed/20851191 when employing this script}
-\KeywordTok{in} \KeywordTok{your} \NormalTok{studies. A reproducible evaluation of ANTs similarity metric performance in}
-\KeywordTok{brain} \NormalTok{image registration:}
-
-\KeywordTok{*} \NormalTok{Avants BB, Tustison NJ, Song G, Cook PA, Klein A, Gee JC. Neuroimage, 2011.}
-
-\KeywordTok{Also} \NormalTok{see http://www.ncbi.nlm.nih.gov/pubmed/19818860 for more details.}
-
-\KeywordTok{The} \NormalTok{script has been updated and improved since this publication.}
-
-\KeywordTok{--------------------------------------------------------------------------------------}
-\KeywordTok{script} \NormalTok{adapted by N.M. van Strien, http://www.mri-tutorial.com }\KeywordTok{|} \KeywordTok{NTNU} \NormalTok{MR-Center}
-\KeywordTok{multivariate} \NormalTok{template adaption by Nick Tustison}
-\KeywordTok{--------------------------------------------------------------------------------------}
-\KeywordTok{Apple} \NormalTok{XGrid support by Craig Stark}
-\KeywordTok{--------------------------------------------------------------------------------------}
-\end{Highlighting}
-\end{Shaded}
+  \begin{itemize}
+  \tightlist
+  \item
+    good performance
+  \item
+    \emph{public availability}
+  \end{itemize}
+\item
+  Public availability --- set of perl scripts coordinating various C++
+  programs
+\item
+  ``\emph{Let's incorporate N3 into ANTs!}''
+\end{itemize}
 
@@
 \includegraphics{./tools/n4/figures/whyN4.png}
-
-\end{frame}
-
-\begin{frame}[fragile]{\texttt{N4BiasFieldCorrection}}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{$ }\KeywordTok{N4BiasFieldCorrection} \NormalTok{--help}
-
-\KeywordTok{COMMAND}\NormalTok{:}
-     \KeywordTok{N4BiasFieldCorrection}
-          \KeywordTok{N4} \NormalTok{is a variant of the popular N3 (nonparameteric nonuniform normalization)}
-          \KeywordTok{retrospective} \NormalTok{bias correction algorithm. Based on the assumption that the}
-          \KeywordTok{corruption} \NormalTok{of the low frequency bias field can be modeled as a convolution of}
-          \KeywordTok{the} \NormalTok{intensity histogram by a Gaussian, the basic algorithmic protocol is to}
-          \KeywordTok{iterate} \NormalTok{between deconvolving the intensity histogram by a Gaussian, remapping}
-          \KeywordTok{the} \NormalTok{intensities, and then spatially smoothing this result by a B-spline modeling}
-          \KeywordTok{of} \NormalTok{the bias field itself. The modifications from and improvements obtained over}
-          \KeywordTok{the} \NormalTok{original N3 algorithm are described in the following paper: N. Tustison et}
-          \KeywordTok{al.}\NormalTok{, N4ITK: Improved N3 Bias Correction, IEEE Transactions on Medical Imaging,}
-          \KeywordTok{29}\NormalTok{(6):}\KeywordTok{1310-1320}\NormalTok{, June 2010.}
-
-\KeywordTok{OPTIONS}\NormalTok{:}
-     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
-          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
-          \KeywordTok{not} \NormalTok{specified, N4 tries to infer the dimensionality from the input image.}
-
-     \KeywordTok{-i}\NormalTok{, --input-image inputImageFilename}
-          \KeywordTok{A} \NormalTok{scalar image is expected as input for bias correction. Since N4 log transforms}
-          \KeywordTok{the} \NormalTok{intensities, negative values or values close to zero should be processed}
-          \KeywordTok{prior} \NormalTok{to correction.}
-
-     \KeywordTok{-x}\NormalTok{, --mask-image maskImageFilename}
-          \KeywordTok{If} \NormalTok{a mask image is specified, the final bias correction is only performed in the}
-          \KeywordTok{mask} \NormalTok{region. If a weight image is not specified, only intensity values inside}
-          \KeywordTok{the} \NormalTok{masked region are used during the execution of the algorithm. If a weight}
-          \KeywordTok{image} \NormalTok{is specified, only the non-zero weights are used in the execution of the}
-          \KeywordTok{algorithm} \NormalTok{although the mask region defines where bias correction is performed in}
-          \KeywordTok{the} \NormalTok{final output. Otherwise bias correction occurs over the entire image domain.}
-          \KeywordTok{See} \NormalTok{also the option description for the weight image.}
-
-     \KeywordTok{-r}\NormalTok{, --rescale-intensities 0/(1)}
-          \KeywordTok{At} \NormalTok{each iteration, a new intensity mapping is calculated and applied but there}
-          \KeywordTok{is} \NormalTok{nothing which constrains the new intensity range to be within certain values.}
-          \KeywordTok{The} \NormalTok{result is that the range can }\StringTok{"drift"} \NormalTok{from the original at each iteration.}
-          \KeywordTok{This} \NormalTok{option rescales to the [min,max] range of the original image intensities}
-          \KeywordTok{within} \NormalTok{the user-specified mask.}
-
-     \KeywordTok{-w}\NormalTok{, --weight-image weightImageFilename}
-          \KeywordTok{The} \NormalTok{weight image allows the user to perform a relative weighting of specific}
-          \KeywordTok{voxels} \NormalTok{during the B-spline fitting. For example, some studies have shown that N3}
-          \KeywordTok{performed} \NormalTok{on white matter segmentations improves performance. If one has a}
-          \KeywordTok{spatial} \NormalTok{probability map of the white matter, one can use this map to weight the}
-          \KeywordTok{b-spline} \NormalTok{fitting towards those voxels which are more probabilistically}
-          \KeywordTok{classified} \NormalTok{as white matter. See also the option description for the mask image.}
-
-     \KeywordTok{-s}\NormalTok{, --shrink-factor 1/2/3/4/...}
-          \KeywordTok{Running} \NormalTok{N4 on large images can be time consuming. To lessen computation time,}
-          \KeywordTok{the} \NormalTok{input image can be resampled. The shrink factor, specified as a single}
-          \KeywordTok{integer}\NormalTok{, describes this resampling. Shrink factors }\KeywordTok{<}\NormalTok{= 4 are commonly used.}
-
-     \KeywordTok{-c}\NormalTok{, --convergence [}\KeywordTok{<}\NormalTok{numberOfIterations=50x50x50x}\KeywordTok{50>}\NormalTok{,}\KeywordTok{<}\NormalTok{convergenceThreshold=0.}\KeywordTok{0>}\NormalTok{]}
-          \KeywordTok{Convergence} \NormalTok{is determined by calculating the coefficient of variation between}
-          \KeywordTok{subsequent} \NormalTok{iterations. When this value is less than the specified threshold from}
-          \KeywordTok{the} \NormalTok{previous iteration or the maximum number of iterations is exceeded the}
-          \KeywordTok{program} \NormalTok{terminates. Multiple resolutions can be specified by using }\StringTok{'x'} \NormalTok{between}
-          \KeywordTok{the} \NormalTok{number of iterations at each resolution, e.g. 100x50x50.}
-
-     \KeywordTok{-b}\NormalTok{, --bspline-fitting [splineDistance,}\KeywordTok{<}\NormalTok{splineOrder=}\KeywordTok{3>}\NormalTok{]}
-                           \NormalTok{[}\KeywordTok{initialMeshResolution}\NormalTok{,}\KeywordTok{<}\NormalTok{splineOrder=}\KeywordTok{3>}\NormalTok{]}
-          \KeywordTok{These} \NormalTok{options describe the b-spline fitting parameters. The initial b-spline}
-          \KeywordTok{mesh} \NormalTok{at the coarsest resolution is specified either as the number of elements in}
-          \KeywordTok{each} \NormalTok{dimension, e.g. 2x2x3 for 3-D images, or it can be specified as a single}
-          \KeywordTok{scalar} \NormalTok{parameter which describes the isotropic sizing of the mesh elements. The}
-          \KeywordTok{latter} \NormalTok{option is typically preferred. For each subsequent level, the spline}
-          \KeywordTok{distance} \NormalTok{decreases in half, or equivalently, the number of mesh elements doubles}
-          \KeywordTok{Cubic} \NormalTok{splines (order = 3) }\KeywordTok{are} \NormalTok{typically used.}
-
-     \KeywordTok{-t}\NormalTok{, --histogram-sharpening [}\KeywordTok{<}\NormalTok{FWHM=0.}\KeywordTok{15>}\NormalTok{,}\KeywordTok{<}\NormalTok{wienerNoise=0.}\KeywordTok{01>}\NormalTok{,}\KeywordTok{<}\NormalTok{numberOfHistogramBins=}\KeywordTok{200>}\NormalTok{]}
-          \KeywordTok{These} \NormalTok{options describe the histogram sharpening parameters, i.e. the}
-          \KeywordTok{deconvolution} \NormalTok{step parameters described in the original N3 algorithm. The}
-          \KeywordTok{default} \NormalTok{values have been shown to work fairly well.}
-
-     \KeywordTok{-o}\NormalTok{, --output correctedImage}
-                  \NormalTok{[}\KeywordTok{correctedImage}\NormalTok{,}\KeywordTok{<}\NormalTok{biasField}\KeywordTok{>}\NormalTok{]}
-          \KeywordTok{The} \NormalTok{output consists of the bias corrected version of the input image.}
-          \KeywordTok{Optionally}\NormalTok{, one can also output the estimated bias field.}
-
-     \KeywordTok{--version}
-          \KeywordTok{Get} \NormalTok{Version Information.}
-
-     \KeywordTok{-v}\NormalTok{, --verbose (0)}\KeywordTok{/1}
-          \KeywordTok{Verbose} \NormalTok{output.}
-
-     \KeywordTok{-h}
-          \KeywordTok{Print} \NormalTok{the help menu (short version)}\KeywordTok{.}
-
-     \KeywordTok{--help}
-          \KeywordTok{Print} \NormalTok{the help menu.}
-          \KeywordTok{<VALUES>}\NormalTok{: 1}
-\end{Highlighting}
-\end{Shaded}
-
-\textless{}-- \#\# Atropos -- cutting the threads of fate
-
-\includegraphics{./papers/figures/Atropos_deGoya.jpg} --\textgreater{}
 
@@
 
-\begin{frame}[fragile]{\texttt{Atropos}}
+\begin{frame}{Atropos + N4 \(\rightarrow\) \texttt{antsAtroposN4.sh}}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{$ }\KeywordTok{Atropos} \NormalTok{--help}
-
-\KeywordTok{COMMAND}\NormalTok{:}
-     \KeywordTok{Atropos}
-          \KeywordTok{A} \NormalTok{finite mixture modeling (FMM) }\KeywordTok{segmentation} \NormalTok{approach with possibilities for}
-          \KeywordTok{specifying} \NormalTok{prior constraints. These prior constraints include the specification}
-          \KeywordTok{of} \NormalTok{a prior label image, prior probability images (one for each class), }\KeywordTok{and/or} \NormalTok{an}
-          \KeywordTok{MRF} \NormalTok{prior to enforce spatial smoothing of the labels. Similar algorithms include}
-          \KeywordTok{FAST} \NormalTok{and SPM. Reference: Avants BB, Tustison NJ, Wu J, Cook PA, Gee JC. An open}
-          \KeywordTok{source} \NormalTok{multivariate framework for n-tissue segmentation with evaluation on}
-          \KeywordTok{public} \NormalTok{data. Neuroinformatics. 2011 Dec}\KeywordTok{;9}\NormalTok{(4):}\KeywordTok{381-400.}
-
-\KeywordTok{OPTIONS}\NormalTok{:}
-     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
-          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
-          \KeywordTok{not} \NormalTok{specified, Atropos tries to infer the dimensionality from the first input}
-          \KeywordTok{image.}
-
-     \KeywordTok{-a}\NormalTok{, --intensity-image [intensityImage,}\KeywordTok{<}\NormalTok{adaptiveSmoothingWeight}\KeywordTok{>}\NormalTok{]}
-          \KeywordTok{One} \NormalTok{or more scalar images is specified for segmentation using the}
-          \KeywordTok{-a/--intensity-image} \NormalTok{option. For segmentation scenarios with no prior}
-          \KeywordTok{information}\NormalTok{, the first scalar image encountered on the command line is used to}
-          \KeywordTok{order} \NormalTok{labelings such that the class with the smallest intensity signature is}
-          \KeywordTok{class} \StringTok{'1'} \NormalTok{through class }\StringTok{'N'} \NormalTok{which represents the voxels with the largest}
-          \KeywordTok{intensity} \NormalTok{values. The optional adaptive smoothing weight parameter is applicable}
-          \KeywordTok{only} \NormalTok{when using prior label or probability images. This scalar parameter is to}
-          \KeywordTok{be} \NormalTok{specified between [0,1] which smooths each labeled region separately and}
-          \KeywordTok{modulates} \NormalTok{the intensity measurement at each voxel in each intensity image}
-          \KeywordTok{between} \NormalTok{the original intensity and its smoothed counterpart. The smoothness}
-          \KeywordTok{parameters} \NormalTok{are governed by the -b/--bspline option.}
-
-     \KeywordTok{-b}\NormalTok{, --bspline [}\KeywordTok{<}\NormalTok{numberOfLevels=}\KeywordTok{6>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialMeshResolution=1x1x...}\KeywordTok{>}\NormalTok{,}\KeywordTok{<}\NormalTok{splineOrder=}\KeywordTok{3>}\NormalTok{]}
-          \KeywordTok{If} \NormalTok{the adaptive smoothing weights are }\KeywordTok{>} \NormalTok{0, the intensity images are smoothed in}
-          \KeywordTok{calculating} \NormalTok{the likelihood values. This is to account for subtle intensity}
-          \KeywordTok{differences} \NormalTok{across the same tissue regions.}
-
-     \KeywordTok{-i}\NormalTok{, --initialization Random[numberOfClasses]}
-                          \KeywordTok{Otsu}\NormalTok{[numberOfTissueClasses]}
-                          \KeywordTok{KMeans}\NormalTok{[numberOfTissueClasses,}\KeywordTok{<}\NormalTok{clusterCenters(in ascending order and for first intensity image only)}\KeywordTok{>}\NormalTok{]}
-                          \KeywordTok{PriorProbabilityImages}\NormalTok{[numberOfTissueClasses,fileSeriesFormat(index=1 to numberOfClasses) }\KeywordTok{or} \NormalTok{vectorImage,priorWeighting,}\KeywordTok{<}\NormalTok{priorProbabilityThreshold}\KeywordTok{>}\NormalTok{]}
-                          \KeywordTok{PriorLabelImage}\NormalTok{[numberOfTissueClasses,labelImage,priorWeighting]}
-          \KeywordTok{To} \NormalTok{initialize the FMM parameters, one of the following options must be}
-          \KeywordTok{specified.} \NormalTok{If one does not have prior label or probability images we recommend}
-          \KeywordTok{using} \NormalTok{kmeans as it is typically faster than otsu and can be used with}
-          \KeywordTok{multivariate} \NormalTok{initialization. However, since a Euclidean distance on the inter}
-          \KeywordTok{cluster} \NormalTok{distances is used, one might have to appropriately scale the additional}
-          \KeywordTok{input} \NormalTok{images. Random initialization is meant purely for intellectual curiosity.}
-          \KeywordTok{The} \NormalTok{prior weighting (specified in the range [0,1]) }\KeywordTok{is} \NormalTok{used to modulate the}
-          \KeywordTok{calculation} \NormalTok{of the posterior probabilities between the likelihood*mrfprior and}
-          \KeywordTok{the} \NormalTok{likelihood*mrfprior*prior. For specifying many prior probability images for}
-          \KeywordTok{a} \NormalTok{multi-label segmentation, we offer a minimize usage option (see -m)}\KeywordTok{.} \KeywordTok{With} \NormalTok{that}
-          \KeywordTok{option} \NormalTok{one can specify a prior probability threshold in which only those pixels}
-          \KeywordTok{exceeding} \NormalTok{that threshold are stored in memory.}
-
-     \KeywordTok{-s}\NormalTok{, --partial-volume-label-set label1xlabel2xlabel3}
-          \KeywordTok{The} \NormalTok{partial volume estimation option allows one to modelmixtures of classes}
-          \KeywordTok{within} \NormalTok{single voxels. Atropos currently allows the user to model two class}
-          \KeywordTok{mixtures} \NormalTok{per partial volume class. The user specifies a set of class labels per}
-          \KeywordTok{partial} \NormalTok{volume class requested. For example, suppose the user was performing a}
-          \KeywordTok{classic} \NormalTok{3-tissue segmentation (csf, gm, wm) }\KeywordTok{using} \NormalTok{kmeans initialization. Suppose}
-          \KeywordTok{the} \NormalTok{user also wanted to model the partial voluming effects between csf/gm and}
-          \KeywordTok{gm/wm.} \NormalTok{The user would specify it using -i kmeans[3] and -s 1x2 -s 2x3. So, for}
-          \KeywordTok{this} \NormalTok{example, there would be 3 tissue classes and 2 partial volume classes.}
-          \KeywordTok{Optionally}\NormalTok{,the user can limit partial volume handling to mrf considerations only}
-          \KeywordTok{whereby} \NormalTok{the output would only be the three tissues.}
-
-     \KeywordTok{--use-partial-volume-likelihoods} \NormalTok{1/(0)}
-                                      \KeywordTok{true}\NormalTok{/}\KeywordTok{(false)}
-          \KeywordTok{The} \NormalTok{user can specify whether or not to use the partial volume likelihoods, in}
-          \KeywordTok{which} \NormalTok{case the partial volume class is considered separate from the tissue}
-          \KeywordTok{classes.} \NormalTok{Alternatively, one can use the MRF only to handle partial volume in}
-          \KeywordTok{which} \NormalTok{case, partial volume voxels are not considered as separate classes.}
-
-     \KeywordTok{-p}\NormalTok{, --posterior-formulation Socrates[}\KeywordTok{<}\NormalTok{useMixtureModelProportions=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialAnnealingTemperature=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{annealingRate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{minimumTemperature=0.}\KeywordTok{1>}\NormalTok{]}
-                                 \KeywordTok{Plato}\NormalTok{[}\KeywordTok{<}\NormalTok{useMixtureModelProportions=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialAnnealingTemperature=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{annealingRate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{minimumTemperature=0.}\KeywordTok{1>}\NormalTok{]}
-                                 \KeywordTok{Aristotle}\NormalTok{[}\KeywordTok{<}\NormalTok{useMixtureModelProportions=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialAnnealingTemperature=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{annealingRate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{minimumTemperature=0.}\KeywordTok{1>}\NormalTok{]}
-                                 \KeywordTok{Sigmoid}\NormalTok{[}\KeywordTok{<}\NormalTok{useMixtureModelProportions=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{initialAnnealingTemperature=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{annealingRate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{minimumTemperature=0.}\KeywordTok{1>}\NormalTok{]]}
-          \KeywordTok{Different} \NormalTok{posterior probability formulations are possible as are different}
-          \KeywordTok{update} \NormalTok{options. To guarantee theoretical convergence properties, a proper}
-          \KeywordTok{formulation} \NormalTok{of the well-known iterated conditional modes (ICM) }\KeywordTok{uses} \NormalTok{an}
-          \KeywordTok{asynchronous} \NormalTok{update step modulated by a specified annealing temperature. If one}
-          \KeywordTok{sets} \NormalTok{the AnnealingTemperature }\KeywordTok{>} \NormalTok{1 in the posterior formulation a traditional}
-          \KeywordTok{code} \NormalTok{set for a proper ICM update will be created. Otherwise, a synchronous}
-          \KeywordTok{update} \NormalTok{step will take place at each iteration. The annealing temperature, T,}
-          \KeywordTok{converts} \NormalTok{the posteriorProbability to posteriorProbability^(1/T) }\KeywordTok{over} \NormalTok{the course}
-          \KeywordTok{of} \NormalTok{optimization.}
-
-     \KeywordTok{-x}\NormalTok{, --mask-image maskImageFilename}
-          \KeywordTok{The} \NormalTok{image mask (which is required) }\KeywordTok{defines} \NormalTok{the region which is to be labeled by}
-          \KeywordTok{the} \NormalTok{Atropos algorithm.}
-
-     \KeywordTok{-c}\NormalTok{, --convergence numberOfIterations}
-                       \NormalTok{[}\KeywordTok{<}\OtherTok{numberOfIterations=}\NormalTok{5}\KeywordTok{>}\NormalTok{,}\KeywordTok{<}\OtherTok{convergenceThreshold=}\NormalTok{0.001}\KeywordTok{>}\NormalTok{]}
-          \KeywordTok{Convergence} \NormalTok{is determined by calculating the mean maximum posterior probability}
-          \KeywordTok{over} \NormalTok{the region of interest at each iteration. When this value decreases or}
-          \KeywordTok{increases} \NormalTok{less than the specified threshold from the previous iteration or the}
-          \KeywordTok{maximum} \NormalTok{number of iterations is exceeded the program terminates.}
-
-     \KeywordTok{-k}\NormalTok{, --likelihood-model Gaussian}
-                            \KeywordTok{HistogramParzenWindows}\NormalTok{[}\KeywordTok{<}\NormalTok{sigma=1.}\KeywordTok{0>}\NormalTok{,}\KeywordTok{<}\NormalTok{numberOfBins=}\KeywordTok{32>}\NormalTok{]}
-                            \KeywordTok{ManifoldParzenWindows}\NormalTok{[}\KeywordTok{<}\NormalTok{pointSetSigma=1.}\KeywordTok{0>}\NormalTok{,}\KeywordTok{<}\NormalTok{evaluationKNeighborhood=}\KeywordTok{50>}\NormalTok{,}\KeywordTok{<}\NormalTok{CovarianceKNeighborhood=}\KeywordTok{0>}\NormalTok{,}\KeywordTok{<}\NormalTok{kernelSigma=}\KeywordTok{0>}\NormalTok{]}
-                            \KeywordTok{JointShapeAndOrientationProbability}\NormalTok{[}\KeywordTok{<}\NormalTok{shapeSigma=1.}\KeywordTok{0>}\NormalTok{,}\KeywordTok{<}\NormalTok{numberOfShapeBins=}\KeywordTok{64>}\NormalTok{, }\KeywordTok{<}\NormalTok{orientationSigma=1.}\KeywordTok{0>}\NormalTok{, }\KeywordTok{<}\NormalTok{numberOfOrientationBins=}\KeywordTok{32>}\NormalTok{]}
-                            \KeywordTok{LogEuclideanGaussian}
-          \KeywordTok{Both} \NormalTok{parametric and non-parametric options exist in Atropos. The Gaussian}
-          \KeywordTok{parametric} \NormalTok{option is commonly used (e.g. SPM }\KeywordTok{&} \KeywordTok{FAST}\NormalTok{) }\KeywordTok{where} \NormalTok{the mean and standard}
-          \KeywordTok{deviation} \NormalTok{for the Gaussian of each class is calculated at each iteration. Other}
-          \KeywordTok{groups} \NormalTok{use non-parametric approaches exemplified by option 2. We recommend using}
-          \KeywordTok{options} \NormalTok{1 or 2 as they are fairly standard and the default parameters work}
-          \KeywordTok{adequately.}
-
-     \KeywordTok{-m}\NormalTok{, --mrf [}\KeywordTok{<}\NormalTok{smoothingFactor=0.}\KeywordTok{3>}\NormalTok{,}\KeywordTok{<}\NormalTok{radius=1x1x...}\KeywordTok{>}\NormalTok{]}
-               \NormalTok{[}\KeywordTok{<mrfCoefficientImage>}\NormalTok{,}\KeywordTok{<}\NormalTok{radius=1x1x...}\KeywordTok{>}\NormalTok{]}
-          \KeywordTok{Markov} \NormalTok{random field (MRF) }\KeywordTok{theory} \NormalTok{provides a general framework for enforcing}
-          \KeywordTok{spatially} \NormalTok{contextual constraints on the segmentation solution. The default}
-          \KeywordTok{smoothing} \NormalTok{factor of 0.3 provides a moderate amount of smoothing. Increasing this}
-          \KeywordTok{number} \NormalTok{causes more smoothing whereas decreasing the number lessens the}
-          \KeywordTok{smoothing.} \NormalTok{The radius parameter specifies the mrf neighborhood. Different update}
-          \KeywordTok{schemes} \NormalTok{are possible but only the asynchronous updating has theoretical}
-          \KeywordTok{convergence} \NormalTok{properties.}
-
-     \KeywordTok{-g}\NormalTok{, --icm [}\KeywordTok{<}\NormalTok{useAsynchronousUpdate=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{maximumNumberOfICMIterations=}\KeywordTok{1>}\NormalTok{,}\KeywordTok{<}\NormalTok{icmCodeImage=}\StringTok{''}\KeywordTok{>}\NormalTok{]}
-          \KeywordTok{Asynchronous} \NormalTok{updating requires the construction of an ICM code image which is a}
-          \KeywordTok{label} \NormalTok{image (with labels in the range }\DataTypeTok{\{1,..,MaximumICMCode\}}\NormalTok{) }\KeywordTok{constructed} \NormalTok{such}
-          \KeywordTok{that} \NormalTok{no MRF neighborhood has duplicate ICM code labels. Thus, to update the}
-          \KeywordTok{voxel} \NormalTok{class labels we iterate through the code labels and, for each code label,}
-          \KeywordTok{we} \NormalTok{iterate through the image and update the voxel class label that has the}
-          \KeywordTok{corresponding} \NormalTok{ICM code label. One can print out the ICM code image by specifying}
-          \KeywordTok{an} \NormalTok{ITK-compatible image filename.}
-
-     \KeywordTok{-r}\NormalTok{, --use-random-seed 0/(1)}
-          \KeywordTok{Initialize} \NormalTok{internal random number generator with a random seed. Otherwise,}
-          \KeywordTok{initialize} \NormalTok{with a constant seed number.}
-
-     \KeywordTok{-o}\NormalTok{, --output [classifiedImage,}\KeywordTok{<}\NormalTok{posteriorProbabilityImageFileNameFormat}\KeywordTok{>}\NormalTok{]}
-          \KeywordTok{The} \NormalTok{output consists of a labeled image where each voxel in the masked region is}
-          \KeywordTok{assigned} \NormalTok{a label from 1, 2, ..., N. Optionally, one can also output the}
-          \KeywordTok{posterior} \NormalTok{probability images specified in the same format as the prior}
-          \KeywordTok{probability} \NormalTok{images, e.g. posterior%02d.nii.gz (C-style file name formatting)}\KeywordTok{.}
-
-     \KeywordTok{-u}\NormalTok{, --minimize-memory-usage (0)}\KeywordTok{/1}
-          \KeywordTok{By} \NormalTok{default, memory usage is not minimized, however, if this is needed, the}
-          \KeywordTok{various} \NormalTok{probability and distance images are calculated on the fly instead of}
-          \KeywordTok{being} \NormalTok{stored in memory at each iteration. Also, if prior probability images are}
-          \KeywordTok{used}\NormalTok{, only the non-negligible pixel values are stored in memory.}
-          \KeywordTok{<VALUES>}\NormalTok{: 0}
-
-     \KeywordTok{-w}\NormalTok{, --winsorize-outliers BoxPlot[}\KeywordTok{<}\NormalTok{lowerPercentile=0.}\KeywordTok{25>}\NormalTok{,}\KeywordTok{<}\NormalTok{upperPercentile=0.}\KeywordTok{75>}\NormalTok{,}\KeywordTok{<}\NormalTok{whiskerLength=1.}\KeywordTok{5>}\NormalTok{]}
-                              \KeywordTok{GrubbsRosner}\NormalTok{[}\KeywordTok{<}\NormalTok{significanceLevel=0.}\KeywordTok{05>}\NormalTok{,}\KeywordTok{<}\NormalTok{winsorizingLevel=0.}\KeywordTok{10>}\NormalTok{]}
-          \KeywordTok{To} \NormalTok{remove the effects of outliers in calculating the weighted mean and weighted}
-          \KeywordTok{covariance}\NormalTok{, the user can opt to remove the outliers through the options}
-          \KeywordTok{specified} \NormalTok{below.}
-
-     \KeywordTok{-e}\NormalTok{, --use-euclidean-distance (0)}\KeywordTok{/1}
-          \KeywordTok{Given} \NormalTok{prior label or probability images, the labels are propagated throughout}
-          \KeywordTok{the} \NormalTok{masked region so that every voxel in the mask is labeled. Propagation is}
-          \KeywordTok{done} \KeywordTok{by} \NormalTok{using a signed distance transform of the label. Alternatively,}
-          \KeywordTok{propagation} \NormalTok{of the labels with the fast marching filter respects the distance}
-          \KeywordTok{along} \NormalTok{the shape of the mask (e.g. the sinuous sulci and gyri of the cortex.}
-          \KeywordTok{<VALUES>}\NormalTok{: 0}
-
-     \KeywordTok{-l}\NormalTok{, --label-propagation whichLabel[lambda=0.0,}\KeywordTok{<}\NormalTok{boundaryProbability=1.}\KeywordTok{0>}\NormalTok{]}
-          \KeywordTok{The} \NormalTok{propagation of each prior label can be controlled by the lambda and boundary}
-          \KeywordTok{probability} \NormalTok{parameters. The latter parameter is the probability (in the range}
-          \NormalTok{[}\KeywordTok{0}\NormalTok{,1]) }\KeywordTok{of} \NormalTok{the label on the boundary which increases linearly to a maximum value}
-          \KeywordTok{of} \NormalTok{1.0 in the interior of the labeled region. The former parameter dictates the}
-          \KeywordTok{exponential} \NormalTok{decay of probability propagation outside the labeled region from the}
-          \KeywordTok{boundary} \NormalTok{probability, i.e. boundaryProbability*exp( -lambda * distance )}\KeywordTok{.}
-
-     \KeywordTok{-v}\NormalTok{, --verbose (0)}\KeywordTok{/1}
-          \KeywordTok{Verbose} \NormalTok{output.}
-
-     \KeywordTok{-h}
-          \KeywordTok{Print} \NormalTok{the help menu (short version)}\KeywordTok{.}
-
-     \KeywordTok{--help}
-          \KeywordTok{Print} \NormalTok{the help menu.}
-          \KeywordTok{<VALUES>}\NormalTok{: 1}
-\end{Highlighting}
-\end{Shaded}
+\includegraphics{./tools/atropos/figures/atroposFlow.png}
 
@@
 
-\begin{frame}[fragile]{\texttt{DenoiseImage} --- contribution from Jose
-Manjon}
+\begin{frame}{\texttt{DenoiseImage} --- contribution from Jose Manjon}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{$ }\KeywordTok{DenoiseImage} \NormalTok{--help}
-
-\KeywordTok{COMMAND}\NormalTok{:}
-     \KeywordTok{DenoiseImage}
-          \KeywordTok{Denoise} \NormalTok{an image using a spatially adaptive filter originally described in J. V.}
-          \KeywordTok{Manjon}\NormalTok{, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive}
-          \KeywordTok{Non-Local} \NormalTok{Means Denoising of MR Images With Spatially Varying Noise Levels,}
-          \KeywordTok{Journal} \NormalTok{of Magnetic Resonance Imaging, 31:192-203, June 2010.}
-
-\KeywordTok{OPTIONS}\NormalTok{:}
-     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
-          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
-          \KeywordTok{not} \NormalTok{specified, the program tries to infer the dimensionality from the input}
-          \KeywordTok{image.}
-
-     \KeywordTok{-i}\NormalTok{, --input-image inputImageFilename}
-          \KeywordTok{A} \NormalTok{scalar image is expected as input for noise correction.}
-
-     \KeywordTok{-n}\NormalTok{, --noise-model Rician/(Gaussian)}
-          \KeywordTok{Employ} \NormalTok{a Rician or Gaussian noise model.}
-
-     \KeywordTok{-x}\NormalTok{, --mask-image maskImageFilename}
-          \KeywordTok{If} \NormalTok{a mask image is specified, denoising is only performed in the mask region.}
-
-     \KeywordTok{-s}\NormalTok{, --shrink-factor (1)}\KeywordTok{/2/3/...}
-          \KeywordTok{Running} \NormalTok{noise correction on large images can be time consuming. To lessen}
-          \KeywordTok{computation} \NormalTok{time, the input image can be resampled. The shrink factor, specified}
-          \KeywordTok{as} \NormalTok{a single integer, describes this resampling. Shrink factor = 1 is the}
-          \KeywordTok{default.}
-
-     \KeywordTok{-p}\NormalTok{, --patch-radius 1}
-                        \KeywordTok{1x1x1}
-          \KeywordTok{Patch} \NormalTok{radius. Default = 1x1x1}
-
-     \KeywordTok{-r}\NormalTok{, --search-radius 3}
-                         \KeywordTok{3x3x3}
-          \KeywordTok{Search} \NormalTok{radius. Default = 3x3x3.}
-
-     \KeywordTok{-o}\NormalTok{, --output correctedImage}
-                  \NormalTok{[}\KeywordTok{correctedImage}\NormalTok{,}\KeywordTok{<}\NormalTok{noiseImage}\KeywordTok{>}\NormalTok{]}
-          \KeywordTok{The} \NormalTok{output consists of the noise corrected version of the input image.}
-          \KeywordTok{Optionally}\NormalTok{, one can also output the estimated noise image.}
-
-     \KeywordTok{--version}
-          \KeywordTok{Get} \NormalTok{Version Information.}
-
-     \KeywordTok{-v}\NormalTok{, --verbose (0)}\KeywordTok{/1}
-          \KeywordTok{Verbose} \NormalTok{output.}
-
-     \KeywordTok{-h}
-          \KeywordTok{Print} \NormalTok{the help menu (short version)}\KeywordTok{.}
-
-     \KeywordTok{--help}
-          \KeywordTok{Print} \NormalTok{the help menu.}
-          \KeywordTok{<VALUES>}\NormalTok{: 1}
-\end{Highlighting}
-\end{Shaded}
+\includegraphics{./tools/figures/denoising.png}
 
@@
 \end{itemize}
-
-\end{frame}
-
-\begin{frame}[fragile]{\texttt{antsJointFusion} --- contribution from
-Hongzhi Wang (with some added features)}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{$ }\KeywordTok{antsJointFusion} \NormalTok{--help}
-
-\KeywordTok{COMMAND}\NormalTok{:}
-     \KeywordTok{antsJointFusion}
-          \KeywordTok{antsJointFusion} \NormalTok{is an image fusion algorithm developed by Hongzhi Wang and Paul}
-          \KeywordTok{Yushkevich} \NormalTok{which won segmentation challenges at MICCAI 2012 and MICCAI 2013. The}
-          \KeywordTok{original} \NormalTok{label fusion framework was extended to accommodate intensities by Brian}
-          \KeywordTok{Avants.} \NormalTok{This implementation is based on Paul}\StringTok{'s original ITK-style implementation}
-\StringTok{          and Brian'}\NormalTok{s ANTsR implementation. References include 1) }\KeywordTok{H.} \NormalTok{Wang, J. W. Suh, S.}
-          \KeywordTok{Das}\NormalTok{, J. Pluta, C. Craige, P. Yushkevich, Multi-atlas segmentation with joint}
-          \KeywordTok{label} \NormalTok{fusion IEEE Trans. on Pattern Analysis and Machine Intelligence, 35(3),}
-          \KeywordTok{611-623}\NormalTok{, 2013. and 2) }\KeywordTok{H.} \NormalTok{Wang and P. A. Yushkevich, Multi-atlas segmentation}
-          \KeywordTok{with} \NormalTok{joint label fusion and corrective learning--an open source implementation,}
-          \KeywordTok{Front.} \NormalTok{Neuroinform., 2013.}
-
-\KeywordTok{OPTIONS}\NormalTok{:}
-     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
-          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
-          \KeywordTok{not} \NormalTok{specified, the program tries to infer the dimensionality from the input}
-          \KeywordTok{image.}
-
-     \KeywordTok{-t}\NormalTok{, --target-image targetImage}
-                        \NormalTok{[}\KeywordTok{targetImageModality0}\NormalTok{,targetImageModality1,...,targetImageModalityN]}
-          \KeywordTok{The} \NormalTok{target image (or multimodal target images) }\KeywordTok{assumed} \NormalTok{to be aligned to a common}
-          \KeywordTok{image} \NormalTok{domain.}
-
-     \KeywordTok{-g}\NormalTok{, --atlas-image atlasImage}
-                       \NormalTok{[}\KeywordTok{atlasImageModality0}\NormalTok{,atlasImageModality1,...,atlasImageModalityN]}
-          \KeywordTok{The} \NormalTok{atlas image (or multimodal atlas images) }\KeywordTok{assumed} \NormalTok{to be aligned to a common}
-          \KeywordTok{image} \NormalTok{domain.}
-
-     \KeywordTok{-l}\NormalTok{, --atlas-segmentation atlasSegmentation}
-          \KeywordTok{The} \NormalTok{atlas segmentation images. For performing label fusion the number of}
-          \KeywordTok{specified} \NormalTok{segmentations should be identical to the number of atlas image sets.}
-
-     \KeywordTok{-a}\NormalTok{, --alpha 0.1}
-          \KeywordTok{Regularization} \NormalTok{term added to matrix Mx for calculating the inverse. Default =}
-          \KeywordTok{0.1}
-
-     \KeywordTok{-b}\NormalTok{, --beta 2.0}
-          \KeywordTok{Exponent} \NormalTok{for mapping intensity difference to the joint error. Default = 2.0}
-
-     \KeywordTok{-r}\NormalTok{, --retain-label-posterior-images (0)}\KeywordTok{/1}
-          \KeywordTok{Retain} \NormalTok{label posterior probability images. Requires atlas segmentations to be}
-          \KeywordTok{specified.} \NormalTok{Default = false}
-
-     \KeywordTok{-f}\NormalTok{, --retain-atlas-voting-images (0)}\KeywordTok{/1}
-          \KeywordTok{Retain} \NormalTok{atlas voting images. Default = false}
-
-     \KeywordTok{-c}\NormalTok{, --constrain-nonnegative (0)}\KeywordTok{/1}
-          \KeywordTok{Constrain} \NormalTok{solution to non-negative weights.}
-
-     \KeywordTok{-p}\NormalTok{, --patch-radius 2}
-                        \KeywordTok{2x2x2}
-          \KeywordTok{Patch} \NormalTok{radius for similarity measures. Default = 2x2x2}
-
-     \KeywordTok{-m}\NormalTok{, --patch-metric (PC)}\KeywordTok{/MSQ}
-          \KeywordTok{Metric} \NormalTok{to be used in determining the most similar neighborhood patch. Options}
-          \KeywordTok{include} \NormalTok{Pearson}\StringTok{'s correlation (PC) and mean squares (MSQ). Default = PC (Pearson}
-\StringTok{          correlation).}
-
-\StringTok{     -s, --search-radius 3}
-\StringTok{                         3x3x3}
-\StringTok{                         searchRadiusMap.nii.gz}
-\StringTok{          Search radius for similarity measures. Default = 3x3x3. One can also specify an}
-\StringTok{          image where the value at the voxel specifies the isotropic search radius at that}
-\StringTok{          voxel.}
-
-\StringTok{     -e, --exclusion-image label[exclusionImage]}
-\StringTok{          Specify an exclusion region for the given label.}
-
-\StringTok{     -x, --mask-image maskImageFilename}
-\StringTok{          If a mask image is specified, fusion is only performed in the mask region.}
-
-\StringTok{     -o, --output labelFusionImage}
-\StringTok{                  intensityFusionImageFileNameFormat}
-\StringTok{                  [labelFusionImage,intensityFusionImageFileNameFormat,<labelPosteriorProbabilityImageFileNameFormat>,<atlasVotingWeightImageFileNameFormat>]}
-\StringTok{          The output is the intensity and/or label fusion image. Additional optional}
-\StringTok{          outputs include the label posterior probability images and the atlas voting}
-\StringTok{          weight images.}
-
-\StringTok{     --version}
-\StringTok{          Get version information.}
-
-\StringTok{     -v, --verbose (0)/1}
-\StringTok{          Verbose output.}
-
-\StringTok{     -h}
-\StringTok{          Print the help menu (short version).}
-
-\StringTok{     --help}
-\StringTok{          Print the help menu.}
-\StringTok{          <VALUES>: 1}
-\end{Highlighting}
-\end{Shaded}
 

### 2016-07-18 background/people2.Rmd
ENH:  Final commit.

@@
 
+<!--
 ##  Founders:  Brian and Nick
+-->
 
@@
 
+<!--
 $+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
+-->
 

### 2016-07-18 ibm.Rmd
ENH:  Last minute refinements.
ENH:  Final commit.

@@
 ![](./papers/figures/Frontiers_BSplineSyN.png)
+
+<!--
 
@@
 
+-->
+
 ## Template building:  creating the average Joe
@@
 
-## Gender discernibility?
+<!--
+
+## Gender?
 
 ![](./papers/figures/template5.jpg)
+
+-->
+
+<!--
 
@@
 
-<!--
+-->
 
@@
 * "*Let's incorporate N3 into ANTs!*"
--->
-
-## N3 adoption issues
+
+<!--
+## Nonparametric nonuniform intensity normalization (N3)
 
@@
 
-<!--
-
-## N4
+-->
+
+## N4 ("Nick's N3")
 
@@
 * tested nightly within the ITK dashboard system
--->
+
+<!--
 
@@
 ```
-
-<--
+-->
+
+<!--
 ##  Atropos -- cutting the threads of fate
@@
 
+<!--
+
 ## Atropos:  flexible code base
@@
 ![](./tools/atropos/figures/atropos.png)
+
+-->
+
+<!--
 
@@
 
+-->
+
 <!--
@@
 ![](./tools/atropos/figures/atroposFlow.png)
--->
 
@@
 
+![](./tools/figures/denoising.png)
+
+-->
+
+<!--
 ```bash
@@
 ```
+-->
 
@@
 * Use in ``corrective learning''
+
+<!--
 
@@
 
+-->
+
 # Putting it all together---the ANTs cortical thickness pipeline
@@
 
+<!--
+
 ## Age prediction per site
@@
 
-# But, wait, there's more!
-
-<!--
-##  What about using both the T1 & T2?
--->
-
-## ANTs tools are multivariate
-
-![](./evaluation/figures/rfRmse05ANTsT1T2.png)
-
-<!--
-
-## Arno-thick-in-the-head (ATITH)
-
-_What if we made a crude estimate of the cortical thickness?_
-
-$$thickness_{ROI} = \frac{volume_{ROI}}{area_{ROI}}$$
-
-## Make sure you estimate the [surface area](http://www.insight-journal.org/browse/publication/852) correctly!
-
-![](./evaluation/figures/LabelThickness.png)
-
--->
-
-<!--
-----
-
-_So how does ATITH compare with ANTs, FS?_
-
-## Prediction from cortical thickness data
-
-![](./evaluation/figures/atith.png)
-
-## Brain constellation maps
-
-![](./evaluation/figures/brainConstellationMaps.png)
-
-## _Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_
-
-## Contribution from Jose
-
-```bash
-$ DenoiseImage
-
-COMMAND:
-     DenoiseImage
-          Denoise an image using a spatially adaptive filter originally described in J. V.
-          Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive
-          Non-Local Means Denoising of MR Images With Spatially Varying Noise Levels,
-          Journal of Magnetic Resonance Imaging, 31:192-203, June 2010.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, the program tries to infer the dimensionality from the input
-          image.
-
-     -i, --input-image inputImageFilename
-          A scalar image is expected as input for noise correction.
-
-     -n, --noise-model (Rician)/Gaussian
-          Employ a Rician or Gaussian noise model.
-
-     -s, --shrink-factor (1)/2/3/...
-          Running noise correction on large images can be time consuming. To lessen
-          computation time, the input image can be resampled. The shrink factor, specified
-          as a single integer, describes this resampling. Shrink factor = 1 is the
-          default.
-
-     -o, --output correctedImage
-                  [correctedImage,<noiseImage>]
-          The output consists of the noise corrected version of the input image.
-          Optionally, one can also output the estimated noise image.
-
-     --version
-          Get Version Information.
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-```
-
-## _Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_
-
-![](./evaluation/figures/rfRmseDenoise05.png)
-
--->
-
-## Longitudinal processing
-
-![](./longitudinal/figures/longitudinalPipeline.png)
-
-<!--
-
-# But the best part is ...
-
-## it is absolutely ``free''!
-
-```bash
-${ANTSPATH}/antsCorticalThickness.sh \
-  -a IXI/T1/IXI002-Guys-0828-T1.nii.gz \
-  -e IXI/template/T_template0.nii.gz \
-  -m IXI/template/T_template0ProbabilityMask.nii.gz \
-  -f IXI/template/T_template0ExtractionMask.nii.gz \
-  -p IXI/template/Priors/priors%d.nii.gz \
-  -o IXI/ANTsResults/IXI002-Guys-0828-
-```
-
-----
-
-[__Data availability__](https://github.com/ntustison/KapowskiChronicles)
-
-*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"
-Sure, why not?---[Hasan, et al., J Neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/26565394)
-
-*  "_Can I have one or more of the templates that you used for your study?_" Would you like the priors as well?
-
 -->
@@
 
-![](./competitions/figures/brats2013results2.png)
+![](./competitions/figures/brats2013results1.png)
 
@@
 
+<!--
+
 ## Other ANTsR work
@@
 * Corrective learning for segmentation refinement
+
+-->

### 2016-07-18 ibm.tex
ENH:  Final commit.

@@
 \newif\ifbibliography
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{{#1}}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
-\newcommand{\ImportTok}[1]{{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{{#1}}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{{#1}}}}
-\newcommand{\BuiltInTok}[1]{{#1}}
-\newcommand{\ExtensionTok}[1]{{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{{#1}}}
-\newcommand{\RegionMarkerTok}[1]{{#1}}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{{#1}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{{#1}}}}
-\newcommand{\NormalTok}[1]{{#1}}
 \usepackage{longtable,booktabs}
@@
 
-\begin{frame}{Founders: Brian and Nick}
-
 \includegraphics{./figures/brian_and_nick.png}
-
-\end{frame}
 
@@
 \includegraphics{./figures/antsCollaborators2.png}
-
-\(+\) \href{http://neuro.debian.net/pkgs/ants.html}{neurodebian},
-\href{http://www.slicer.org/}{slicer},
-\href{https://github.com/BRAINSia/BRAINSTools}{brainsfit},
-\href{http://nipy.sourceforge.net/nipype/}{nipype},
-\href{http://www.itk.org}{itk} and more \ldots{}
 
@@
 
-\begin{frame}[fragile]{\texttt{antsRegistration}}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{$ }\KeywordTok{antsRegistration} \NormalTok{--help}
-
-\KeywordTok{COMMAND}\NormalTok{:}
-     \KeywordTok{antsRegistration}
-          \KeywordTok{This} \NormalTok{program is a user-level registration application meant to utilize}
-          \KeywordTok{ITKv4-only} \NormalTok{classes. The user can specify any number of }\StringTok{"stages"} \NormalTok{where a stage}
-          \KeywordTok{consists} \NormalTok{of a transform}\KeywordTok{;} \KeywordTok{an} \NormalTok{image metric}\KeywordTok{;} \KeywordTok{and} \NormalTok{iterations, shrink factors, and}
-          \KeywordTok{smoothing} \NormalTok{sigmas for each level.Note that dimensionality, metric, transform,}
-          \KeywordTok{output}\NormalTok{, convergence, shrink-factors and smoothing-sigmas parameters are}
-          \KeywordTok{mandatory.}
-
-\KeywordTok{OPTIONS}\NormalTok{:}
-     \KeywordTok{--version}
-          \KeywordTok{Get} \NormalTok{Version Information.}
-
-     \KeywordTok{-d}\NormalTok{, --dimensionality 2/3}
-          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
-          \KeywordTok{not} \NormalTok{specified, we try to infer the dimensionality from the input image.}
-
-     \KeywordTok{-o}\NormalTok{, --output outputTransformPrefix}
-                  \NormalTok{[}\KeywordTok{outputTransformPrefix}\NormalTok{,}\KeywordTok{<}\NormalTok{outputWarpedImage}\KeywordTok{>}\NormalTok{,}\KeywordTok{<}\NormalTok{outputInverseWarpedImage}\KeywordTok{>}\NormalTok{]}
-          \KeywordTok{Specify} \NormalTok{the output transform prefix (output format is .nii.gz )}\KeywordTok{.} \KeywordTok{Optionally}\NormalTok{, one}
-          \KeywordTok{can} \NormalTok{choose to warp the moving image to the fixed space and, if the inverse}
-          \KeywordTok{transform} \NormalTok{exists, one can also output the warped fixed image. Note that only the}
-          \KeywordTok{images} \NormalTok{specified in the first metric call are warped. Use antsApplyTransforms to}
-          \KeywordTok{warp} \NormalTok{other images using the resultant transform(s)}\KeywordTok{.}
-
-     \KeywordTok{-j}\NormalTok{, --save-state saveSateAsTransform}
-          \KeywordTok{Specify} \NormalTok{the output file for the current state of the registration. The state}
-          \KeywordTok{file} \NormalTok{is written to an hdf5 composite file. It is specially usefull if we want to}
-          \KeywordTok{save} \NormalTok{the current state of a SyN registration to the disk, so we can load and}
-          \KeywordTok{restore} \NormalTok{that later to continue the next registration process directly started}
-          \KeywordTok{from} \NormalTok{the last saved state. The output file of this flag is the same as the}
-          \KeywordTok{write-composite-transform}\NormalTok{, unless the last transform is a SyN transform. In that}
-          \KeywordTok{case}\NormalTok{, the inverse displacement field of the SyN transform is also added to the}
-          \NormalTok{output composite transform. Again notice that this file cannot be treated as a}
-          \NormalTok{transform, and restore-state option must be used to load the written file by}
-          \NormalTok{this flag.}
-
-     \NormalTok{-k, --restore-state restoreStateAsATransform}
-          \NormalTok{Specify the initial state of the registration which get immediately used to}
-          \NormalTok{directly initialize the registration process. The flag is mutually exclusive}
-          \NormalTok{with other intialization flags.If this flag is used, none of the}
-          \NormalTok{initial-moving-transform and initial-fixed-transform cannot be used.}
-
-     \NormalTok{-a, --write-composite-transform 1/(0)}
-          \NormalTok{Boolean specifying whether or not the composite transform (and its inverse, if}
-          \NormalTok{it exists) should be written to an hdf5 composite file. This is false by default}
-          \NormalTok{so that only the transform for each stage is written to file.}
-          \NormalTok{<VALUES>: 0}
-
-     \NormalTok{-p, --print-similarity-measure-interval <unsignedIntegerValue>}
-          \NormalTok{Prints out the CC similarity metric measure between the full-size input fixed}
-          \NormalTok{and the transformed moving images at each iteration a value of 0 (the default)}
-          \NormalTok{indicates that the full scale computation should not take placeany value greater}
-          \NormalTok{than 0 represents the interval of full scale metric computation.}
-          \NormalTok{<VALUES>: 0}
-
-     \NormalTok{-v, --write-interval-volumes <unsignedIntegerValue>}
-          \NormalTok{Writes out the output volume at each iteration. It helps to present the}
-          \NormalTok{registration process as a short movie a value of 0 (the default) indicates that}
-          \NormalTok{this option should not take placeany value greater than 0 represents the}
-          \NormalTok{interval between the iterations which outputs are written to the disk.}
-          \NormalTok{<VALUES>: 0}
-
-     \NormalTok{-z, --collapse-output-transforms (1)/0}
-          \NormalTok{Collapse output transforms. Specifically, enabling this option combines all}
-          \NormalTok{adjacent transforms wherepossible. All adjacent linear transforms are written to}
-          \NormalTok{disk}\KeywordTok{ in} \NormalTok{the forman itk affine transform }\KeywordTok{(}\NormalTok{called xxxGenericAffine.mat}\KeywordTok{).}
-          \KeywordTok{Similarly}\NormalTok{, all adjacent displacement field transforms are combined when written}
-          \KeywordTok{to} \NormalTok{disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available))}\KeywordTok{.Also}\NormalTok{, an}
-          \KeywordTok{output} \NormalTok{composite transform including the collapsed transforms is written to the}
-          \KeywordTok{disk} \NormalTok{(called outputCollapsed(Inverse)}\KeywordTok{Composite}\NormalTok{)}\KeywordTok{.}
-          \KeywordTok{<VALUES>}\NormalTok{: 1}
-
-     \KeywordTok{-i}\NormalTok{, --initialize-transforms-per-stage (1)}\KeywordTok{/0}
-          \KeywordTok{Initialize} \NormalTok{linear transforms from the previous stage. By enabling this option,}
-          \KeywordTok{the} \NormalTok{current linear stage transform is directly intialized from the previous}
-          \KeywordTok{stage}\StringTok{'s linear transform; this allows multiple linear stages to be run where}
-\StringTok{          each stage directly updates the estimated linear transform from the previous}
-\StringTok{          stage. (e.g. Translation -> Rigid -> Affine).}
-\StringTok{          <VALUES>: 0}
-
-\StringTok{     -n, --interpolation Linear}
-\StringTok{                         NearestNeighbor}
-\StringTok{                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]}
-\StringTok{                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]}
-\StringTok{                         BSpline[<order=3>]}
-\StringTok{                         CosineWindowedSinc}
-\StringTok{                         WelchWindowedSinc}
-\StringTok{                         HammingWindowedSinc}
-\StringTok{                         LanczosWindowedSinc}
-\StringTok{          Several interpolation options are available in ITK. These have all been made}
-\StringTok{          available. Currently the interpolator choice is only used to warp (and possibly}
-\StringTok{          inverse warp) the final output image(s).}
-
-\StringTok{     -g, --restrict-deformation PxQxR}
-\StringTok{          This option allows the user to restrict the optimization of the displacement}
-\StringTok{          field, translation, rigid or affine transform on a per-component basis. For}
-\StringTok{          example, if one wants to limit the deformation or rotation of 3-D volume to the}
-\StringTok{          first two dimensions, this is possible by specifying a weight vector of '}\NormalTok{1x1x0}\StringTok{'}
-\StringTok{          for a deformation field or '}\NormalTok{1x1x0x1x1x0}\StringTok{' for a rigid}
-\StringTok{          transformation.Low-dimensional restriction only works if there are no preceding}
-\StringTok{          transformations.}
-
-\StringTok{     -q, --initial-fixed-transform initialTransform}
-\StringTok{                                   [initialTransform,<useInverse>]}
-\StringTok{                                   [fixedImage,movingImage,initializationFeature]}
-\StringTok{          Specify the initial fixed transform(s) which get immediately incorporated into}
-\StringTok{          the composite transform. The order of the transforms is stack-esque in that the}
-\StringTok{          last transform specified on the command line is the first to be applied. In}
-\StringTok{          addition to initialization with ITK transforms, the user can perform an initial}
-\StringTok{          translation alignment by specifying the fixed and moving images and selecting an}
-\StringTok{          initialization feature. These features include using the geometric center of the}
-\StringTok{          images (=0), the image intensities (=1), or the origin of the images (=2).}
-
-\StringTok{     -r, --initial-moving-transform initialTransform}
-\StringTok{                                    [initialTransform,<useInverse>]}
-\StringTok{                                    [fixedImage,movingImage,initializationFeature]}
-\StringTok{          Specify the initial moving transform(s) which get immediately incorporated into}
-\StringTok{          the composite transform. The order of the transforms is stack-esque in that the}
-\StringTok{          last transform specified on the command line is the first to be applied. In}
-\StringTok{          addition to initialization with ITK transforms, the user can perform an initial}
-\StringTok{          translation alignment by specifying the fixed and moving images and selecting an}
-\StringTok{          initialization feature. These features include using the geometric center of the}
-\StringTok{          images (=0), the image intensities (=1), or the origin of the images (=2).}
-
-\StringTok{     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
-\StringTok{                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
-\StringTok{                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
-\StringTok{                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
-\StringTok{                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
-\StringTok{                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
-\StringTok{                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]}
-\StringTok{                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]}
-\StringTok{                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]}
-\StringTok{                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]}
-\StringTok{          These image metrics are available--- CC: ANTS neighborhood cross correlation,}
-\StringTok{          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global}
-\StringTok{          Correlation. The "metricWeight" variable is used to modulate the per stage}
-\StringTok{          weighting of the metrics. The metrics can also employ a sampling strategy}
-\StringTok{          defined by a sampling percentage. The sampling strategy defaults to '}\NormalTok{None}\StringTok{' (aka}
-\StringTok{          a dense sampling of one sample per voxel), otherwise it defines a point set over}
-\StringTok{          which to optimize the metric. The point set can be on a regular lattice or a}
-\StringTok{          random lattice of points slightly perturbed to minimize aliasing artifacts.}
-\StringTok{          samplingPercentage defines the fraction of points to select from the domain. In}
-\StringTok{          addition, three point set metrics are available: Euclidean (ICP), Point-set}
-\StringTok{          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).}
-
-\StringTok{     -t, --transform Rigid[gradientStep]}
-\StringTok{                     Affine[gradientStep]}
-\StringTok{                     CompositeAffine[gradientStep]}
-\StringTok{                     Similarity[gradientStep]}
-\StringTok{                     Translation[gradientStep]}
-\StringTok{                     BSpline[gradientStep,meshSizeAtBaseLevel]}
-\StringTok{                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]}
-\StringTok{                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]}
-\StringTok{                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]}
-\StringTok{                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]}
-\StringTok{                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]}
-\StringTok{                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]}
-\StringTok{                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]}
-\StringTok{                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]}
-\StringTok{          Several transform options are available. The gradientStep or learningRate}
-\StringTok{          characterizes the gradient descent optimization and is scaled appropriately for}
-\StringTok{          each transform using the shift scales estimator. Subsequent parameters are}
-\StringTok{          transform-specific and can be determined from the usage. For the B-spline}
-\StringTok{          transforms one can also specify the smoothing in terms of spline distance (i.e.}
-\StringTok{          knot spacing).}
-
-\StringTok{     -c, --convergence MxNxO}
-\StringTok{                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]}
-\StringTok{          Convergence is determined from the number of iterations per level and is}
-\StringTok{          determined by fitting a line to the normalized energy profile of the last N}
-\StringTok{          iterations (where N is specified by the window size) and determining the slope}
-\StringTok{          which is then compared with the convergence threshold.}
-
-\StringTok{     -s, --smoothing-sigmas MxNxO...}
-\StringTok{          Specify the sigma of gaussian smoothing at each level. Units are given in terms}
-\StringTok{          of voxels ('}\NormalTok{vox}\StringTok{') or physical spacing ('}\NormalTok{mm}\StringTok{'). Example usage is '}\NormalTok{4x2x1mm}\StringTok{' and}
-\StringTok{          '}\NormalTok{4x2x1vox}\StringTok{' where no units implies voxel spacing.}
-
-\StringTok{     -f, --shrink-factors MxNxO...}
-\StringTok{          Specify the shrink factor for the virtual domain (typically the fixed image) at}
-\StringTok{          each level.}
-
-\StringTok{     -u, --use-histogram-matching}
-\StringTok{          Histogram match the images before registration.}
-
-\StringTok{     -l, --use-estimate-learning-rate-once}
-\StringTok{          turn on the option that lets you estimate the learning rate step size only at}
-\StringTok{          the beginning of each level. * useful as a second stage of fine-scale}
-\StringTok{          registration.}
-
-\StringTok{     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]}
-\StringTok{          Winsorize data based on specified quantiles.}
-
-\StringTok{     -x, --masks [fixedImageMask,movingImageMask]}
-\StringTok{          Image masks to limit voxels considered by the metric.}
-
-\StringTok{     --float}
-\StringTok{          Use '}\NormalTok{float}\StringTok{' instead of '}\NormalTok{double}\StringTok{' for computations.}
-\StringTok{          <VALUES>: 0}
-
-\StringTok{     -v, --verbose (0)/1}
-\StringTok{          Verbose output.}
-
-\StringTok{     -h}
-\StringTok{          Print the help menu (short version).}
-
-\StringTok{     --help}
-\StringTok{          Print the help menu. Will also print values used on the current command line}
-\StringTok{          call.}
-\end{Highlighting}
-\end{Shaded}
-
-\end{frame}
-
 \begin{frame}{Template building: creating the average Joe}
@@
 \includegraphics{./papers/figures/template4.jpg}
-
-\end{frame}
-
-\begin{frame}{Gender discernibility?}
-
-\includegraphics{./papers/figures/template5.jpg}
 
@@
 
-\begin{frame}{N3 adoption issues}
+\begin{frame}[fragile]{N4 (``Nick's N3'')}
 
-\includegraphics{./tools/n4/figures/whyN4.png}
-
-\end{frame}
-
-\begin{frame}{Atropos: flexible code base}
-
-``20+ years of development. \emph{Show me the code!}''
-
-\includegraphics{./tools/atropos/figures/atropos.png}
-
-\end{frame}
-
-\begin{frame}{Atropos + N4 \(\rightarrow\) \texttt{antsAtroposN4.sh}}
-
-\includegraphics{./tools/atropos/figures/atroposFlow.png}
-
-\end{frame}
-
-\begin{frame}{\texttt{DenoiseImage} --- contribution from Jose Manjon}
-
-\includegraphics{./tools/figures/denoising.png}
+\begin{itemize}
+\item
+  comparative
+  \href{http://www.ncbi.nlm.nih.gov/pubmed/20378467}{evaluation}
+\item
+  small spline distances (useful for higher magnet strengths)
+\item
+  multiresolution
+\item
+  weighted regional mask (used in
+  \href{https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh}{\texttt{antsAtroposN4.sh}})
+\item
+  fast execution times
+\item
+  \emph{publicly available}
+\item
+  tested nightly within the ITK dashboard system
+\end{itemize}
 
@@
 
-\begin{frame}{Age prediction per site}
-
-\includegraphics{./evaluation/figures/agePredictionPerSite.png}
-
-\end{frame}
-
-\begin{frame}{Regional importance comparison}
-
-\includegraphics{./evaluation/figures/antsvfreesurfer_Importance.png}
-
-ANTs (left) vs.~FreeSurfer (right)
-
-\end{frame}
-
-\begin{frame}{Regional measurements}
-
-\includegraphics{./evaluation/figures/antsvfreesurfer_regionalPlots.png}
-
-\end{frame}
-
-\section{But, wait, there's more!}\label{but-wait-theres-more}
-
-\begin{frame}{ANTs tools are multivariate}
-
-\includegraphics{./evaluation/figures/rfRmse05ANTsT1T2.png}
-
-\end{frame}
-
-\begin{frame}{Longitudinal processing}
-
-\includegraphics{./longitudinal/figures/longitudinalPipeline.png}
-
-\end{frame}
-
 \section{Current work and Advanced Normalization Tools in R
@@
 
-\includegraphics{./competitions/figures/brats2013results2.png}
+\includegraphics{./competitions/figures/brats2013results1.png}
 
@@
 
-\end{frame}
-
-\begin{frame}{Other ANTsR work}
-
-\begin{itemize}
-\item
-  \href{http://www.nature.com/articles/sdata20153}{Pediatric template of
-  brain perfusion}
-\item
-  \href{http://www.ncbi.nlm.nih.gov/pubmed/26756101}{Automated
-  segmentation of chronic stroke lesions using LINDA: Lesion
-  identification with neighborhood data analysis}
-\item
-  \href{http://www.ncbi.nlm.nih.gov/pubmed/25448483}{Eigenanatomy}
-\item
-  Corrective learning for segmentation refinement
-\end{itemize}
-
 \hypertarget{refs}{}

### 2016-07-18 makePresentationIBM.R

@@ -25,7 +25,6 @@ rawrmds <- c( "format.Rmd",
               "competitions/competitions.Rmd",
               "papers/papers.Rmd",
               "evaluation/antsvfreesurfer2.Rmd",
-              "evaluation/antsvfreesurfer2_extra.Rmd",
               "antsr/antsr.Rmd"
                )
 

### 2016-08-04 ants2015build.Rmd
ENH:  More.

@@
 <BR><BR>
-<span style="color:red;">_"Papers are just advertisements for the science."_</red>
+_\`\`Papers are just advertisements for the science.\'\'_
 <BR>
 
-<!--
+## Neuro tools
+
+![](./tools/figures/coreANtsToolsNeuro.png)
+
+## Pulmonary tools
+
+![](./tools/figures/coreANtsToolsLung.png)
 
@@
 ![](./papers/figures/fishes.png)
+
+-->
 
@@
 
-<!--
-
 ## Diffeomorphisms: image parameterization in a metric space
@@
 ![](./figures/shape_appearance.png)
--->
 
@@
 
-## Gender discernibility?
+## Gender?
 
@@
 
-## ```antsMultivariateTemplateConstruction2.sh```
+<!--
+
+## ```antsMultivariateTemplateConstruction.sh```
 
 ```bash
-$ antsMultivariateTemplateConstruction2.sh
+$ antsMultivariateTemplateConstruction.sh
 
@@
 * "*Let's incorporate N3 into ANTs!*"
--->
-
-## N3 adoption issues
+
+## Nonparametric nonuniform intensity normalization (N3)
 
@@
 
-<!--
-
-## N4
+## N4 ("Nick's N3")
 
@@
 ![](./tools/atropos/figures/atropos.png)
+
+<!--
 
@@
 ![](./tools/atropos/figures/atroposFlow.png)
+
+## ```DenoiseImage``` --- contribution from Jose Manjon
+
+![](./tools/figures/denoising.png)
+
+```bash
+$ DenoiseImage --help
+
+COMMAND:
+     DenoiseImage
+          Denoise an image using a spatially adaptive filter originally described in J. V.
+          Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive
+          Non-Local Means Denoising of MR Images With Spatially Varying Noise Levels,
+          Journal of Magnetic Resonance Imaging, 31:192-203, June 2010.
+
+OPTIONS:
+     -d, --image-dimensionality 2/3/4
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, the program tries to infer the dimensionality from the input
+          image.
+
+     -i, --input-image inputImageFilename
+          A scalar image is expected as input for noise correction.
+
+     -n, --noise-model Rician/(Gaussian)
+          Employ a Rician or Gaussian noise model.
+
+     -x, --mask-image maskImageFilename
+          If a mask image is specified, denoising is only performed in the mask region.
+
+     -s, --shrink-factor (1)/2/3/...
+          Running noise correction on large images can be time consuming. To lessen
+          computation time, the input image can be resampled. The shrink factor, specified
+          as a single integer, describes this resampling. Shrink factor = 1 is the
+          default.
+
+     -p, --patch-radius 1
+                        1x1x1
+          Patch radius. Default = 1x1x1
+
+     -r, --search-radius 3
+                         3x3x3
+          Search radius. Default = 3x3x3.
+
+     -o, --output correctedImage
+                  [correctedImage,<noiseImage>]
+          The output consists of the noise corrected version of the input image.
+          Optionally, one can also output the estimated noise image.
+
+     --version
+          Get Version Information.
+
+     -v, --verbose (0)/1
+          Verbose output.
+
+     -h
+          Print the help menu (short version).
+
+     --help
+          Print the help menu.
+          <VALUES>: 1
+
+```
+
+## Multi-atlas segmentation
+
+![](./tools/jointfusion/figures/jointLabelFusion.png)
+
+## New work:  joint intensity fusion
+
+![](./tools/jointfusion/figures/jointIntensityFusion.png)
+
+## Possible uses
+
+* ``Correct'' images
+
+    * motion correction
+
+    * ``remove'' lesions
+
+* Project atlas set intensity signature
+
+* Use in ``corrective learning''
+
+<!--
+
+## ```antsJointFusion``` --- contribution from Hongzhi Wang (with some added features)
+
+```bash
+$ antsJointFusion --help
+
+COMMAND:
+     antsJointFusion
+          antsJointFusion is an image fusion algorithm developed by Hongzhi Wang and Paul
+          Yushkevich which won segmentation challenges at MICCAI 2012 and MICCAI 2013. The
+          original label fusion framework was extended to accommodate intensities by Brian
+          Avants. This implementation is based on Paul's original ITK-style implementation
+          and Brian's ANTsR implementation. References include 1) H. Wang, J. W. Suh, S.
+          Das, J. Pluta, C. Craige, P. Yushkevich, Multi-atlas segmentation with joint
+          label fusion IEEE Trans. on Pattern Analysis and Machine Intelligence, 35(3),
+          611-623, 2013. and 2) H. Wang and P. A. Yushkevich, Multi-atlas segmentation
+          with joint label fusion and corrective learning--an open source implementation,
+          Front. Neuroinform., 2013.
+
+OPTIONS:
+     -d, --image-dimensionality 2/3/4
+          This option forces the image to be treated as a specified-dimensional image. If
+          not specified, the program tries to infer the dimensionality from the input
+          image.
+
+     -t, --target-image targetImage
+                        [targetImageModality0,targetImageModality1,...,targetImageModalityN]
+          The target image (or multimodal target images) assumed to be aligned to a common
+          image domain.
+
+     -g, --atlas-image atlasImage
+                       [atlasImageModality0,atlasImageModality1,...,atlasImageModalityN]
+          The atlas image (or multimodal atlas images) assumed to be aligned to a common
+          image domain.
+
+     -l, --atlas-segmentation atlasSegmentation
+          The atlas segmentation images. For performing label fusion the number of
+          specified segmentations should be identical to the number of atlas image sets.
+
+     -a, --alpha 0.1
+          Regularization term added to matrix Mx for calculating the inverse. Default =
+          0.1
+
+     -b, --beta 2.0
+          Exponent for mapping intensity difference to the joint error. Default = 2.0
+
+     -r, --retain-label-posterior-images (0)/1
+          Retain label posterior probability images. Requires atlas segmentations to be
+          specified. Default = false
+
+     -f, --retain-atlas-voting-images (0)/1
+          Retain atlas voting images. Default = false
+
+     -c, --constrain-nonnegative (0)/1
+          Constrain solution to non-negative weights.
+
+     -p, --patch-radius 2
+                        2x2x2
+          Patch radius for similarity measures. Default = 2x2x2
+
+     -m, --patch-metric (PC)/MSQ
+          Metric to be used in determining the most similar neighborhood patch. Options
+          include Pearson's correlation (PC) and mean squares (MSQ). Default = PC (Pearson
+          correlation).
+
+     -s, --search-radius 3
+                         3x3x3
+                         searchRadiusMap.nii.gz
+          Search radius for similarity measures. Default = 3x3x3. One can also specify an
+          image where the value at the voxel specifies the isotropic search radius at that
+          voxel.
+
+     -e, --exclusion-image label[exclusionImage]
+          Specify an exclusion region for the given label.
+
+     -x, --mask-image maskImageFilename
+          If a mask image is specified, fusion is only performed in the mask region.
+
+     -o, --output labelFusionImage
+                  intensityFusionImageFileNameFormat
+                  [labelFusionImage,intensityFusionImageFileNameFormat,<labelPosteriorProbabilityImageFileNameFormat>,<atlasVotingWeightImageFileNameFormat>]
+          The output is the intensity and/or label fusion image. Additional optional
+          outputs include the label posterior probability images and the atlas voting
+          weight images.
+
+     --version
+          Get version information.
+
+     -v, --verbose (0)/1
+          Verbose output.
+
+     -h
+          Print the help menu (short version).
+
+     --help
+          Print the help menu.
+          <VALUES>: 1
+
+```
+
 -->
@@
 
+-->
+
 # But, wait, there's more!
 
-##
-
-[__Data availability__](https://github.com/ntustison/KapowskiChronicles)
-
-*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"  Sure, why not?
-
-*  "_I was wondering if you would make available the CT in each ROI for each subject..._" Sure, why not?  Would you also like the surface areas and volumes?
-
-*  "_Can I have one or more of the templates that you used for your study?_" Would you like the priors as well?
-
+<!--
 ##  What about using both the T1 & T2?
+-->
 
@@
 
-## So how does ATITH compare with ANTs, FS?
+-->
+
+<!--
+----
+
+_So how does ATITH compare with ANTs, FS?_
 
@@
 
+-->
+
+## Longitudinal processing
+
+![](./longitudinal/figures/longitudinalPipeline.png)
+
+<!--
+
 # But the best part is ...
 
-## it is absolutely free!
+## it is absolutely ``free''!
 
@@
 
+----
+
+[__Data availability__](https://github.com/ntustison/KapowskiChronicles)
+
+*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"
+Sure, why not?---[Hasan, et al., J Neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/26565394)
+
+*  "_Can I have one or more of the templates that you used for your study?_" Would you like the priors as well?
+
+-->
+
 # Joint label/intensity fusion

### 2016-08-04 ants2015build.tex
ENH:  More.

\documentclass[ignorenonframetext,]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usetheme{AnnArbor}
\usecolortheme{dolphin}
\usefonttheme{professionalfonts}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\newif\ifbibliography
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{{#1}}}
\newcommand{\ImportTok}[1]{{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{{#1}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{{#1}}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{{#1}}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{{#1}}}}
\newcommand{\BuiltInTok}[1]{{#1}}
\newcommand{\ExtensionTok}[1]{{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{{#1}}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}
\usepackage{longtable,booktabs}
\usepackage{caption}
% These lines are needed to make table captions work with longtable:
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight0.8\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

% Prevent slide breaks in the middle of a paragraph:
\widowpenalties 1 10000
\raggedbottom

\AtBeginPart{
  \let\insertpartnumber\relax
  \let\partname\relax
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \let\insertsectionnumber\relax
    \let\sectionname\relax
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \let\insertsubsectionnumber\relax
  \let\subsectionname\relax
  \frame{\subsectionpage}
}

\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% \pgfdeclareimage[width=1cm]{logo}{./figures/monkeyTypewriter.png}
%\logo{\pgfuseimage{logo}}

\institute{University of Virginia}
\definecolor{links}{RGB}{42, 27, 129}
\definecolor{mypink2}{RGB}{219, 48, 122}
%\hypersetup{colorlinks,linkcolor=links,urlcolor=mypink2}
\usefonttheme{professionalfonts}

% \setbeamerfont{note page}{family*=pplx,size=\footnotesize} % Palatino for notes

\setbeamerfont{subtitle}{size=\small}

\definecolor{uvablue}{RGB}{0,85,150}
\definecolor{uvalibraryorange}{RGB}{252,175,23}
\definecolor{uvacream}{RGB}{241,229,199}
\definecolor{uvalightblue}{RGB}{163,220,230}

\setbeamercolor{block body}{bg=green,fg=green}
\setbeamercolor{block body alerted}{bg=green,fg=green}
\setbeamercolor{block body example}{bg=green,fg=green}

\setbeamercolor{caption name}{fg=uvablue}

\setbeamercolor{headline}{fg=uvacream,bg=uvacream}
\setbeamercolor{section}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{frametitle}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{palette primary}{bg=uvalibraryorange,fg=uvablue}
\setbeamercolor{palette secondary}{bg=uvablue,fg=uvablue}
\setbeamercolor{palette tertiary}{bg=uvalibraryorange,fg=uvablue}
\setbeamercolor{palette quarternary}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{palette sidebar primary}{bg=uvalibraryorange,fg=uvablue}
\setbeamercolor{palette sidebar secondary}{fg=uvablue,bg=uvablue}
\setbeamercolor{palette sidebar tertiary}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{palette sidebar quarternary}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{structure}{bg=uvablue}

\useinnertheme{rectangles}

\titlegraphic{\vspace{-7.5mm}\includegraphics[width=0.45\paperwidth]{./figures/monkeyTypewriter.png}}

\title{``Dr.~Tustison (UVA) presentation''}
\author{Nick Tustison}
\date{}

\begin{document}
\frame{\titlepage}

\section{Developers and
collaborators}\label{developers-and-collaborators}

\begin{frame}{Founders: Brian and Nick}

\includegraphics{./figures/brian_and_nick.png}

\end{frame}

\begin{frame}

\includegraphics{./figures/antsCollaborators2.png}

\(+\) \href{http://neuro.debian.net/pkgs/ants.html}{neurodebian},
\href{http://www.slicer.org/}{slicer},
\href{https://github.com/BRAINSia/BRAINSTools}{brainsfit},
\href{http://nipy.sourceforge.net/nipype/}{nipype},
\href{http://www.itk.org}{itk} and more \ldots{}

\end{frame}

\section{ANTs lineage}\label{ants-lineage}

\begin{frame}{Image mapping and perception: 1877}

Francis Galton: \emph{Can we see criminality in the face?}

\includegraphics{./figures/galton.png}

\emph{What about syphilis, mental illness?}

\end{frame}

\begin{frame}{Speaking of criminality\ldots{}}

\emph{Can we say anything about the U.S. Congress?}

\includegraphics{./background/figures/congressPersons.png}

\textbf{Maybe they should have used
\href{https://github.com/ntustison/CongressionalFaceTemplates}{ANTs}?}

\end{frame}

\begin{frame}{Image mapping \& biology: 1917}

D'Arcy Thompson: \emph{Comparison of related forms}

\includegraphics{./figures/dthompson.png} --\textgreater{}

\end{frame}

\begin{frame}{Image mapping \& biology: Current}

 \emph{Look where we are now!}
\includegraphics{./background/figures/r16xr85.png}

\end{frame}

\section{Major ANTs utilities}\label{major-ants-utilities}

\begin{frame}{Donoho?}

 \emph{``Papers are just advertisements for the science.''}

\end{frame}

\begin{frame}{Neuro tools}

\includegraphics{./tools/figures/coreANtsToolsNeuro.png}

\end{frame}

\begin{frame}{Pulmonary tools}

\includegraphics{./tools/figures/coreANtsToolsLung.png}

\end{frame}

\begin{frame}{Symmetric Normalization (SyN)}

\(\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt + \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2\)

\includegraphics{./papers/figures/fishes.png}

--\textgreater{}

NOtes: * Previously discussed Brians work * The variant most widely used
--\textgreater{}

\end{frame}

\begin{frame}{Diffeomoprhisms: differentiable map with diff. inverse}

\includegraphics{./figures/highresdiffeos.jpg}

\end{frame}

\begin{frame}{Diffeomorphisms: image parameterization in a metric space}

\includegraphics{./figures/shape_appearance.png}

\end{frame}

\begin{frame}{Beyond original SyN}

\small

\includegraphics{./papers/figures/Frontiers_ITK.png}

\includegraphics{./papers/figures/Frontiers_BSplineSyN.png}

\end{frame}

\begin{frame}[fragile]{\texttt{antsRegistration}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{antsRegistration} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{antsRegistration}
          \KeywordTok{This} \NormalTok{program is a user-level registration application meant to utilize}
          \KeywordTok{ITKv4-only} \NormalTok{classes. The user can specify any number of }\StringTok{"stages"} \NormalTok{where a stage}
          \KeywordTok{consists} \NormalTok{of a transform}\KeywordTok{;} \KeywordTok{an} \NormalTok{image metric}\KeywordTok{;} \KeywordTok{and} \NormalTok{iterations, shrink factors, and}
          \KeywordTok{smoothing} \NormalTok{sigmas for each level.Note that dimensionality, metric, transform,}
          \KeywordTok{output}\NormalTok{, convergence, shrink-factors and smoothing-sigmas parameters are}
          \KeywordTok{mandatory.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{--version}
          \KeywordTok{Get} \NormalTok{Version Information.}

     \KeywordTok{-d}\NormalTok{, --dimensionality 2/3}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, we try to infer the dimensionality from the input image.}

     \KeywordTok{-o}\NormalTok{, --output outputTransformPrefix}
                  \NormalTok{[}\KeywordTok{outputTransformPrefix}\NormalTok{,}\KeywordTok{<}\NormalTok{outputWarpedImage}\KeywordTok{>}\NormalTok{,}\KeywordTok{<}\NormalTok{outputInverseWarpedImage}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{Specify} \NormalTok{the output transform prefix (output format is .nii.gz )}\KeywordTok{.} \KeywordTok{Optionally}\NormalTok{, one}
          \KeywordTok{can} \NormalTok{choose to warp the moving image to the fixed space and, if the inverse}
          \KeywordTok{transform} \NormalTok{exists, one can also output the warped fixed image. Note that only the}
          \KeywordTok{images} \NormalTok{specified in the first metric call are warped. Use antsApplyTransforms to}
          \KeywordTok{warp} \NormalTok{other images using the resultant transform(s)}\KeywordTok{.}

     \KeywordTok{-j}\NormalTok{, --save-state saveSateAsTransform}
          \KeywordTok{Specify} \NormalTok{the output file for the current state of the registration. The state}
          \KeywordTok{file} \NormalTok{is written to an hdf5 composite file. It is specially usefull if we want to}
          \KeywordTok{save} \NormalTok{the current state of a SyN registration to the disk, so we can load and}
          \KeywordTok{restore} \NormalTok{that later to continue the next registration process directly started}
          \KeywordTok{from} \NormalTok{the last saved state. The output file of this flag is the same as the}
          \KeywordTok{write-composite-transform}\NormalTok{, unless the last transform is a SyN transform. In that}
          \KeywordTok{case}\NormalTok{, the inverse displacement field of the SyN transform is also added to the}
          \NormalTok{output composite transform. Again notice that this file cannot be treated as a}
          \NormalTok{transform, and restore-state option must be used to load the written file by}
          \NormalTok{this flag.}

     \NormalTok{-k, --restore-state restoreStateAsATransform}
          \NormalTok{Specify the initial state of the registration which get immediately used to}
          \NormalTok{directly initialize the registration process. The flag is mutually exclusive}
          \NormalTok{with other intialization flags.If this flag is used, none of the}
          \NormalTok{initial-moving-transform and initial-fixed-transform cannot be used.}

     \NormalTok{-a, --write-composite-transform 1/(0)}
          \NormalTok{Boolean specifying whether or not the composite transform (and its inverse, if}
          \NormalTok{it exists) should be written to an hdf5 composite file. This is false by default}
          \NormalTok{so that only the transform for each stage is written to file.}
          \NormalTok{<VALUES>: 0}

     \NormalTok{-p, --print-similarity-measure-interval <unsignedIntegerValue>}
          \NormalTok{Prints out the CC similarity metric measure between the full-size input fixed}
          \NormalTok{and the transformed moving images at each iteration a value of 0 (the default)}
          \NormalTok{indicates that the full scale computation should not take placeany value greater}
          \NormalTok{than 0 represents the interval of full scale metric computation.}
          \NormalTok{<VALUES>: 0}

     \NormalTok{-v, --write-interval-volumes <unsignedIntegerValue>}
          \NormalTok{Writes out the output volume at each iteration. It helps to present the}
          \NormalTok{registration process as a short movie a value of 0 (the default) indicates that}
          \NormalTok{this option should not take placeany value greater than 0 represents the}
          \NormalTok{interval between the iterations which outputs are written to the disk.}
          \NormalTok{<VALUES>: 0}

     \NormalTok{-z, --collapse-output-transforms (1)/0}
          \NormalTok{Collapse output transforms. Specifically, enabling this option combines all}
          \NormalTok{adjacent transforms wherepossible. All adjacent linear transforms are written to}
          \NormalTok{disk}\KeywordTok{ in} \NormalTok{the forman itk affine transform }\KeywordTok{(}\NormalTok{called xxxGenericAffine.mat}\KeywordTok{).}
          \KeywordTok{Similarly}\NormalTok{, all adjacent displacement field transforms are combined when written}
          \KeywordTok{to} \NormalTok{disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available))}\KeywordTok{.Also}\NormalTok{, an}
          \KeywordTok{output} \NormalTok{composite transform including the collapsed transforms is written to the}
          \KeywordTok{disk} \NormalTok{(called outputCollapsed(Inverse)}\KeywordTok{Composite}\NormalTok{)}\KeywordTok{.}
          \KeywordTok{<VALUES>}\NormalTok{: 1}

     \KeywordTok{-i}\NormalTok{, --initialize-transforms-per-stage (1)}\KeywordTok{/0}
          \KeywordTok{Initialize} \NormalTok{linear transforms from the previous stage. By enabling this option,}
          \KeywordTok{the} \NormalTok{current linear stage transform is directly intialized from the previous}
          \KeywordTok{stage}\StringTok{'s linear transform; this allows multiple linear stages to be run where}
\StringTok{          each stage directly updates the estimated linear transform from the previous}
\StringTok{          stage. (e.g. Translation -> Rigid -> Affine).}
\StringTok{          <VALUES>: 0}

\StringTok{     -n, --interpolation Linear}
\StringTok{                         NearestNeighbor}
\StringTok{                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]}
\StringTok{                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]}
\StringTok{                         BSpline[<order=3>]}
\StringTok{                         CosineWindowedSinc}
\StringTok{                         WelchWindowedSinc}
\StringTok{                         HammingWindowedSinc}
\StringTok{                         LanczosWindowedSinc}
\StringTok{          Several interpolation options are available in ITK. These have all been made}
\StringTok{          available. Currently the interpolator choice is only used to warp (and possibly}
\StringTok{          inverse warp) the final output image(s).}

\StringTok{     -g, --restrict-deformation PxQxR}
\StringTok{          This option allows the user to restrict the optimization of the displacement}
\StringTok{          field, translation, rigid or affine transform on a per-component basis. For}
\StringTok{          example, if one wants to limit the deformation or rotation of 3-D volume to the}
\StringTok{          first two dimensions, this is possible by specifying a weight vector of '}\NormalTok{1x1x0}\StringTok{'}
\StringTok{          for a deformation field or '}\NormalTok{1x1x0x1x1x0}\StringTok{' for a rigid}
\StringTok{          transformation.Low-dimensional restriction only works if there are no preceding}
\StringTok{          transformations.}

\StringTok{     -q, --initial-fixed-transform initialTransform}
\StringTok{                                   [initialTransform,<useInverse>]}
\StringTok{                                   [fixedImage,movingImage,initializationFeature]}
\StringTok{          Specify the initial fixed transform(s) which get immediately incorporated into}
\StringTok{          the composite transform. The order of the transforms is stack-esque in that the}
\StringTok{          last transform specified on the command line is the first to be applied. In}
\StringTok{          addition to initialization with ITK transforms, the user can perform an initial}
\StringTok{          translation alignment by specifying the fixed and moving images and selecting an}
\StringTok{          initialization feature. These features include using the geometric center of the}
\StringTok{          images (=0), the image intensities (=1), or the origin of the images (=2).}

\StringTok{     -r, --initial-moving-transform initialTransform}
\StringTok{                                    [initialTransform,<useInverse>]}
\StringTok{                                    [fixedImage,movingImage,initializationFeature]}
\StringTok{          Specify the initial moving transform(s) which get immediately incorporated into}
\StringTok{          the composite transform. The order of the transforms is stack-esque in that the}
\StringTok{          last transform specified on the command line is the first to be applied. In}
\StringTok{          addition to initialization with ITK transforms, the user can perform an initial}
\StringTok{          translation alignment by specifying the fixed and moving images and selecting an}
\StringTok{          initialization feature. These features include using the geometric center of the}
\StringTok{          images (=0), the image intensities (=1), or the origin of the images (=2).}

\StringTok{     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy=\{None,Regular,Random\}>,<samplingPercentage=[0,1]>]}
\StringTok{                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]}
\StringTok{                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]}
\StringTok{                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]}
\StringTok{                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]}
\StringTok{          These image metrics are available--- CC: ANTS neighborhood cross correlation,}
\StringTok{          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global}
\StringTok{          Correlation. The "metricWeight" variable is used to modulate the per stage}
\StringTok{          weighting of the metrics. The metrics can also employ a sampling strategy}
\StringTok{          defined by a sampling percentage. The sampling strategy defaults to '}\NormalTok{None}\StringTok{' (aka}
\StringTok{          a dense sampling of one sample per voxel), otherwise it defines a point set over}
\StringTok{          which to optimize the metric. The point set can be on a regular lattice or a}
\StringTok{          random lattice of points slightly perturbed to minimize aliasing artifacts.}
\StringTok{          samplingPercentage defines the fraction of points to select from the domain. In}
\StringTok{          addition, three point set metrics are available: Euclidean (ICP), Point-set}
\StringTok{          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).}

\StringTok{     -t, --transform Rigid[gradientStep]}
\StringTok{                     Affine[gradientStep]}
\StringTok{                     CompositeAffine[gradientStep]}
\StringTok{                     Similarity[gradientStep]}
\StringTok{                     Translation[gradientStep]}
\StringTok{                     BSpline[gradientStep,meshSizeAtBaseLevel]}
\StringTok{                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]}
\StringTok{                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]}
\StringTok{                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]}
\StringTok{                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]}
\StringTok{                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]}
\StringTok{                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]}
\StringTok{                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]}
\StringTok{                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]}
\StringTok{          Several transform options are available. The gradientStep or learningRate}
\StringTok{          characterizes the gradient descent optimization and is scaled appropriately for}
\StringTok{          each transform using the shift scales estimator. Subsequent parameters are}
\StringTok{          transform-specific and can be determined from the usage. For the B-spline}
\StringTok{          transforms one can also specify the smoothing in terms of spline distance (i.e.}
\StringTok{          knot spacing).}

\StringTok{     -c, --convergence MxNxO}
\StringTok{                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]}
\StringTok{          Convergence is determined from the number of iterations per level and is}
\StringTok{          determined by fitting a line to the normalized energy profile of the last N}
\StringTok{          iterations (where N is specified by the window size) and determining the slope}
\StringTok{          which is then compared with the convergence threshold.}

\StringTok{     -s, --smoothing-sigmas MxNxO...}
\StringTok{          Specify the sigma of gaussian smoothing at each level. Units are given in terms}
\StringTok{          of voxels ('}\NormalTok{vox}\StringTok{') or physical spacing ('}\NormalTok{mm}\StringTok{'). Example usage is '}\NormalTok{4x2x1mm}\StringTok{' and}
\StringTok{          '}\NormalTok{4x2x1vox}\StringTok{' where no units implies voxel spacing.}

\StringTok{     -f, --shrink-factors MxNxO...}
\StringTok{          Specify the shrink factor for the virtual domain (typically the fixed image) at}
\StringTok{          each level.}

\StringTok{     -u, --use-histogram-matching}
\StringTok{          Histogram match the images before registration.}

\StringTok{     -l, --use-estimate-learning-rate-once}
\StringTok{          turn on the option that lets you estimate the learning rate step size only at}
\StringTok{          the beginning of each level. * useful as a second stage of fine-scale}
\StringTok{          registration.}

\StringTok{     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]}
\StringTok{          Winsorize data based on specified quantiles.}

\StringTok{     -x, --masks [fixedImageMask,movingImageMask]}
\StringTok{          Image masks to limit voxels considered by the metric.}

\StringTok{     --float}
\StringTok{          Use '}\NormalTok{float}\StringTok{' instead of '}\NormalTok{double}\StringTok{' for computations.}
\StringTok{          <VALUES>: 0}

\StringTok{     -v, --verbose (0)/1}
\StringTok{          Verbose output.}

\StringTok{     -h}
\StringTok{          Print the help menu (short version).}

\StringTok{     --help}
\StringTok{          Print the help menu. Will also print values used on the current command line}
\StringTok{          call.}
\end{Highlighting}
\end{Shaded}

\end{frame}

\begin{frame}{Template building: creating the average Joe}

\includegraphics{./papers/figures/template0.jpg}

\end{frame}

\begin{frame}{``Attractiveness'' \(\rightarrow\) mental processing?}

\includegraphics{./papers/figures/template1.jpg}

\end{frame}

\begin{frame}{What about brains?}

\includegraphics{./papers/figures/template3.jpg}

\end{frame}

\begin{frame}{Templates facilitate computation}

\includegraphics{./papers/figures/template4.jpg}

\end{frame}

\begin{frame}{Gender?}

\includegraphics{./papers/figures/template5.jpg}

\end{frame}

\begin{frame}{Nonparametric nonuniform intensity normalization (N3)}

\begin{itemize}
\item
  Developed at the Montreal Neurological Institute (John Sled, 1998)
\item
  Part of the standard preprocessing protocol in large scale projects
  such as ADNI
\item
  The traditional de facto standard in MRI bias correction

  \begin{itemize}
  \tightlist
  \item
    good performance
  \item
    \emph{public availability}
  \end{itemize}
\item
  Public availability --- set of perl scripts coordinating various C++
  programs
\item
  ``\emph{Let's incorporate N3 into ANTs!}''
\end{itemize}

\end{frame}

\begin{frame}{Nonparametric nonuniform intensity normalization (N3)}

\includegraphics{./tools/n4/figures/whyN4.png}

\end{frame}

\begin{frame}[fragile]{N4 (``Nick's N3'')}

\begin{itemize}
\item
  comparative
  \href{http://www.ncbi.nlm.nih.gov/pubmed/20378467}{evaluation}
\item
  small spline distances (useful for higher magnet strengths)
\item
  multiresolution
\item
  weighted regional mask (used in
  \href{https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh}{\texttt{antsAtroposN4.sh}})
\item
  fast execution times
\item
  \emph{publicly available}
\item
  tested nightly within the ITK dashboard system
\end{itemize}

\end{frame}

\begin{frame}{Atropos: flexible code base}

``20+ years of development. \emph{Show me the code!}''

\includegraphics{./tools/atropos/figures/atropos.png}

\end{frame}

\begin{frame}{Atropos + N4 \(\rightarrow\) \texttt{antsAtroposN4.sh}}

\includegraphics{./tools/atropos/figures/atroposFlow.png}

\end{frame}

\begin{frame}[fragile]{\texttt{DenoiseImage} --- contribution from Jose
Manjon}

\includegraphics{./tools/figures/denoising.png}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{DenoiseImage} \NormalTok{--help}

\KeywordTok{COMMAND}\NormalTok{:}
     \KeywordTok{DenoiseImage}
          \KeywordTok{Denoise} \NormalTok{an image using a spatially adaptive filter originally described in J. V.}
          \KeywordTok{Manjon}\NormalTok{, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive}
          \KeywordTok{Non-Local} \NormalTok{Means Denoising of MR Images With Spatially Varying Noise Levels,}
          \KeywordTok{Journal} \NormalTok{of Magnetic Resonance Imaging, 31:192-203, June 2010.}

\KeywordTok{OPTIONS}\NormalTok{:}
     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
          \KeywordTok{not} \NormalTok{specified, the program tries to infer the dimensionality from the input}
          \KeywordTok{image.}

     \KeywordTok{-i}\NormalTok{, --input-image inputImageFilename}
          \KeywordTok{A} \NormalTok{scalar image is expected as input for noise correction.}

     \KeywordTok{-n}\NormalTok{, --noise-model Rician/(Gaussian)}
          \KeywordTok{Employ} \NormalTok{a Rician or Gaussian noise model.}

     \KeywordTok{-x}\NormalTok{, --mask-image maskImageFilename}
          \KeywordTok{If} \NormalTok{a mask image is specified, denoising is only performed in the mask region.}

     \KeywordTok{-s}\NormalTok{, --shrink-factor (1)}\KeywordTok{/2/3/...}
          \KeywordTok{Running} \NormalTok{noise correction on large images can be time consuming. To lessen}
          \KeywordTok{computation} \NormalTok{time, the input image can be resampled. The shrink factor, specified}
          \KeywordTok{as} \NormalTok{a single integer, describes this resampling. Shrink factor = 1 is the}
          \KeywordTok{default.}

     \KeywordTok{-p}\NormalTok{, --patch-radius 1}
                        \KeywordTok{1x1x1}
          \KeywordTok{Patch} \NormalTok{radius. Default = 1x1x1}

     \KeywordTok{-r}\NormalTok{, --search-radius 3}
                         \KeywordTok{3x3x3}
          \KeywordTok{Search} \NormalTok{radius. Default = 3x3x3.}

     \KeywordTok{-o}\NormalTok{, --output correctedImage}
                  \NormalTok{[}\KeywordTok{correctedImage}\NormalTok{,}\KeywordTok{<}\NormalTok{noiseImage}\KeywordTok{>}\NormalTok{]}
          \KeywordTok{The} \NormalTok{output consists of the noise corrected version of the input image.}
          \KeywordTok{Optionally}\NormalTok{, one can also output the estimated noise image.}

     \KeywordTok{--version}
          \KeywordTok{Get} \NormalTok{Version Information.}

     \KeywordTok{-v}\NormalTok{, --verbose (0)}\KeywordTok{/1}
          \KeywordTok{Verbose} \NormalTok{output.}

     \KeywordTok{-h}
          \KeywordTok{Print} \NormalTok{the help menu (short version)}\KeywordTok{.}

     \KeywordTok{--help}
          \KeywordTok{Print} \NormalTok{the help menu.}
          \KeywordTok{<VALUES>}\NormalTok{: 1}
\end{Highlighting}
\end{Shaded}

\end{frame}

\begin{frame}{Multi-atlas segmentation}

\includegraphics{./tools/jointfusion/figures/jointLabelFusion.png}

\end{frame}

\begin{frame}{New work: joint intensity fusion}

\includegraphics{./tools/jointfusion/figures/jointIntensityFusion.png}

\end{frame}

\begin{frame}{Possible uses}

\begin{itemize}
\item
  ``Correct'' images

  \begin{itemize}
  \item
    motion correction
  \item
    ``remove'' lesions
  \end{itemize}
\item
  Project atlas set intensity signature
\item
  Use in ``corrective learning''
\end{itemize}

\end{frame}

\section{Putting it all together---the ANTs cortical thickness
pipeline}\label{putting-it-all-togetherthe-ants-cortical-thickness-pipeline}

\begin{frame}{Cortical thickness studies}

\begin{longtable}[c]{@{}ll@{}}
\toprule
Column1 & Column2\tabularnewline
\midrule
\endhead
Tetris-playing ability & chronic pancreatitis\tabularnewline
Huntington's disease & obsessive-compulsive disorder\tabularnewline
schizophrenia & ADHD\tabularnewline
bipolar disorder & obesity\tabularnewline
Alzheimer's disease & heritable depression\tabularnewline
frontotemporal dementia & elderly depression\tabularnewline
Parkinson's disease & age\tabularnewline
Williams syndrome & gender\tabularnewline
multiple sclerosis & handedness\tabularnewline
autism & intelligence\tabularnewline
migraines & athletic ability\tabularnewline
chronic smoking & meditative practices\tabularnewline
alcoholism & musical ability\tabularnewline
cocaine addiction & tendency toward criminality\tabularnewline
Tourette syndrome in children & childhood sexual abuse in female
adolescents\tabularnewline
scoliosis in female adolescents & traumatic brain injury\tabularnewline
early-onset blindness & untreated male-to-female
transsexuality\tabularnewline
\bottomrule
\end{longtable}

\end{frame}

\begin{frame}{The ANTs structural brain mapping workflow}

\includegraphics{./evaluation/figures/pipeline.png}

\end{frame}

\begin{frame}{Template building}

\emph{Tailor data to your specific cohort}

\includegraphics{./evaluation/figures/templates.png}

\end{frame}

\begin{frame}{Template priors}

\includegraphics{./evaluation/figures/templatePriors.png}

\end{frame}

\begin{frame}{Cortical thickness maps}

\includegraphics{./evaluation/figures/corticalThicknessEstimation.png}

In contrast to FreeSurfer which warps coupled surface meshes to segment
the gray matter, \emph{ANTs} diffeomorphically registers the white
matter to the combined gray/white matters while simultaneously
estimating thickness.

\end{frame}

\begin{frame}

\emph{But without ground truth, how does one evaluate the pipeline?}

\end{frame}

\begin{frame}{Predict age and gender}

\(AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)\)

\end{frame}

\begin{frame}{Prediction from cortical thickness data}

\includegraphics{./evaluation/figures/evaluation.png}

\end{frame}

\section{But, wait, there's more!}\label{but-wait-theres-more}

\begin{frame}{ANTs tools are multivariate}

\includegraphics{./evaluation/figures/rfRmse05ANTsT1T2.png}

\end{frame}

\begin{frame}{Longitudinal processing}

\includegraphics{./longitudinal/figures/longitudinalPipeline.png}

\end{frame}

\section{Joint label/intensity
fusion}\label{joint-labelintensity-fusion}

\begin{frame}{Multi-atlas labeling}

\includegraphics{./competitions/figures/NKI30_MALF.png}

\end{frame}

\begin{frame}{Multi-atlas segmentation}

\includegraphics{./tools/jointfusion/figures/jointLabelFusion.png}

\end{frame}

\begin{frame}{Multi-atlas 2012 results}

\includegraphics{./competitions/figures/MALF2012.png}

\end{frame}

\begin{frame}{New work: joint intensity fusion}

\includegraphics{./tools/jointfusion/figures/jointIntensityFusion.png}

\hypertarget{refs}{}

\end{frame}

\end{document}

### 2016-08-04 evaluation/antsvfreesurfer2.Rmd
ENH:  Final commit.
ENH:  More.

@@
 
-<!--
-* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
+* Templates representing the average mean shape and intensity are built directly from the
+* cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
 * Acquisition and anonymization (e.g. defacing) protocols are often different.
--->
 
@@
 
-<!--
 Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
 to produce auxiliary images which are used for brain extraction and brain segmentation.
--->
-
-<!--
 
@@
 the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
--->
-
-<!--
 
@@
 Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.
--->
 
@@
 
-<!--
-
 ## Open science principles
@@
 * $>$ 1200 subjects, age 4 to over 94 years old
--->
 

### 2016-08-04 ibm.Rmd
ENH:  More.

@@
 
-<!--
 ##  Founders:  Brian and Nick
--->
 
@@
 
-<!--
 $+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
--->
 
@@
 
-<!--
-
 ## \`\`Free beer\'\'
@@
 ![](./licenses/figures/freebeerfreespeech.jpg)
-
--->
 
@@
 
-<!--
+# ANTs lineage
+
+## Image mapping and perception: 1877
+
+Francis Galton: _Can we see criminality in the face?_
+
+![](./figures/galton.png)
+
+_What about syphilis, mental illness?_
+
+<!--
+Notes:
+* Use of "composite portraiture" and what he called "eugenics"
+* Can we see criminality, mental illness, syphilis, and others in facial features?
+* Despite the obvious prejudices driving his research, he was a pioneer.
+-->
+
+<!--
+
+##
+
+![](./background/figures/FrancisGalton2.jpg)
+-->
+
+<!--
+Notes:
+* Another example where he has manually categorized facial features and try to combine them
+* Did not find much---composite tends to blend away to normality.
+-->
+
+##  Speaking of criminality...
+
+_Can we say anything about the U.S. Congress?_
+
+![](./background/figures/congressPersons.png)
+
+__Maybe they should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__
+
+<!--
+Notes:
+-->
+
+##  Image mapping & biology:  1917
+
+D'Arcy Thompson: _Comparison of related forms_
+
+![](./figures/dthompson.png)
+-->
+
+<!--
+Notes:
+* Book: On Growth and Form
+* Descriptive
+* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
+-->
+
+## Image mapping & biology: Current
+<BR><BR>
+_Look where we are now!_
+<BR><BR>
+![](./background/figures/r16xr85.png)
+
+<!--
+## ANTs family tree
+
+![](./figures/lineage.jpg)
+-->
+
+<!--
+References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
+-->
+
+<!--
+## Initial scope
+
+![](./figures/ants_initial_scope.png)
+-->
+
+<!--
+Notes:
+* Brian work with Murray Grossman
+* First registration paper
+  - WBIR submission
+  - FEM registraiton using B-spline basis functions.
+  - "yeah, that registration is not that good---Jim would not like it."
+-->
+
 # Competitions
--->
-
-<!--
 
@@
 ![](./competitions/figures/fightclub.jpg)
-
--->
 
@@
 
-<!--
-
 ## Neuro tools
@@
 
--->
-
-<!--
-
 ## Symmetric Normalization (SyN)
@@
 
+-->
+
 ## Diffeomoprhisms:  differentiable map with diff. inverse
@@
 
--->
-
-<!--
-
 ## Diffeomorphisms: image parameterization in a metric space
@@
 ![](./papers/figures/Frontiers_BSplineSyN.png)
-
-<!--
 
@@
 
--->
-
 ## Template building:  creating the average Joe
@@
 
-<!--
-
 ## Gender?
@@
 ![](./papers/figures/template5.jpg)
-
--->
 
@@
 
-<!--
 ## Nonparametric nonuniform intensity normalization (N3)
@@
 <div align="center"><img src="./tools/n4/figures/whyN4.png" frameborder="0"></img></div>
-
--->
 
@@
 
-<!--
-
 ## Atropos:  flexible code base
@@
 ![](./tools/atropos/figures/atropos.png)
-
--->
 
@@
 
-<!--
-
 ## Atropos + N4 $\rightarrow$ `antsAtroposN4.sh`
@@
 
--->
-
-<!--
 ```bash
@@
 ```
--->
 
@@
 
-<!--
-
 ## Age prediction per site
@@
 ![](./evaluation/figures/antsvfreesurfer_regionalPlots.png)
-
--->
 

### 2016-08-04 ibm.tex
ENH:  More.

--- 2016-07-17 ibm.tex
@@
 
+\begin{frame}{``Free beer''}
+
+\includegraphics{./licenses/figures/freebeerfreespeech.jpg}
+
+\end{frame}
+
 \begin{frame}{Software for medical image analysis}
@@
 \end{itemize}
+
+\end{frame}
+
+\section{ANTs lineage}\label{ants-lineage}
+
+\begin{frame}{Image mapping and perception: 1877}
+
+Francis Galton: \emph{Can we see criminality in the face?}
+
+\includegraphics{./figures/galton.png}
+
+\emph{What about syphilis, mental illness?}
+
+\end{frame}
+
+\begin{frame}{Speaking of criminality\ldots{}}
+
+\emph{Can we say anything about the U.S. Congress?}
+
+\includegraphics{./background/figures/congressPersons.png}
+
+\textbf{Maybe they should have used
+\href{https://github.com/ntustison/CongressionalFaceTemplates}{ANTs}?}
+
+\end{frame}
+
+\begin{frame}{Image mapping \& biology: 1917}
+
+D'Arcy Thompson: \emph{Comparison of related forms}
+
+\includegraphics{./figures/dthompson.png} --\textgreater{}
+
+\end{frame}
+
+\begin{frame}{Image mapping \& biology: Current}
+
+ \emph{Look where we are now!}
+\includegraphics{./background/figures/r16xr85.png}
+
+\end{frame}
+
+\section{Competitions}\label{competitions}
+
+\begin{frame}{Algorithmic fight club}
+
+\includegraphics{./competitions/figures/fightclub.jpg}
 
@@
  \emph{``Papers are just advertisements for the science.''}
+
+\end{frame}
+
+\begin{frame}{Neuro tools}
+
+\includegraphics{./tools/figures/coreANtsToolsNeuro.png}
+
+\end{frame}
+
+\begin{frame}{Pulmonary tools}
+
+\includegraphics{./tools/figures/coreANtsToolsLung.png}
+
+\end{frame}
+
+\begin{frame}{Symmetric Normalization (SyN)}
+
+\(\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt + \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2\)
+
+\includegraphics{./papers/figures/fishes.png}
+
+--\textgreater{}
+
+NOtes: * Previously discussed Brians work * The variant most widely used
+--\textgreater{}
+
+\end{frame}
+
+\begin{frame}{Diffeomoprhisms: differentiable map with diff. inverse}
+
+\includegraphics{./figures/highresdiffeos.jpg}
+
+\end{frame}
+
+\begin{frame}{Diffeomorphisms: image parameterization in a metric space}
+
+\includegraphics{./figures/shape_appearance.png}
 
@@
 
-\begin{frame}{Gender discernibility?}
+\begin{frame}{Gender?}
 
@@
 
-\begin{frame}{N3 adoption issues}
+\begin{frame}{Nonparametric nonuniform intensity normalization (N3)}
 
 \includegraphics{./tools/n4/figures/whyN4.png}
+
+\end{frame}
+
+\begin{frame}[fragile]{N4 (``Nick's N3'')}
+
+\begin{itemize}
+\item
+  comparative
+  \href{http://www.ncbi.nlm.nih.gov/pubmed/20378467}{evaluation}
+\item
+  small spline distances (useful for higher magnet strengths)
+\item
+  multiresolution
+\item
+  weighted regional mask (used in
+  \href{https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh}{\texttt{antsAtroposN4.sh}})
+\item
+  fast execution times
+\item
+  \emph{publicly available}
+\item
+  tested nightly within the ITK dashboard system
+\end{itemize}
 
@@
 
-\begin{frame}{\texttt{DenoiseImage} --- contribution from Jose Manjon}
+\begin{frame}[fragile]{\texttt{DenoiseImage} --- contribution from Jose
+Manjon}
 
 \includegraphics{./tools/figures/denoising.png}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{$ }\KeywordTok{DenoiseImage} \NormalTok{--help}
+
+\KeywordTok{COMMAND}\NormalTok{:}
+     \KeywordTok{DenoiseImage}
+          \KeywordTok{Denoise} \NormalTok{an image using a spatially adaptive filter originally described in J. V.}
+          \KeywordTok{Manjon}\NormalTok{, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive}
+          \KeywordTok{Non-Local} \NormalTok{Means Denoising of MR Images With Spatially Varying Noise Levels,}
+          \KeywordTok{Journal} \NormalTok{of Magnetic Resonance Imaging, 31:192-203, June 2010.}
+
+\KeywordTok{OPTIONS}\NormalTok{:}
+     \KeywordTok{-d}\NormalTok{, --image-dimensionality 2/3/4}
+          \KeywordTok{This} \NormalTok{option forces the image to be treated as a specified-dimensional image. If}
+          \KeywordTok{not} \NormalTok{specified, the program tries to infer the dimensionality from the input}
+          \KeywordTok{image.}
+
+     \KeywordTok{-i}\NormalTok{, --input-image inputImageFilename}
+          \KeywordTok{A} \NormalTok{scalar image is expected as input for noise correction.}
+
+     \KeywordTok{-n}\NormalTok{, --noise-model Rician/(Gaussian)}
+          \KeywordTok{Employ} \NormalTok{a Rician or Gaussian noise model.}
+
+     \KeywordTok{-x}\NormalTok{, --mask-image maskImageFilename}
+          \KeywordTok{If} \NormalTok{a mask image is specified, denoising is only performed in the mask region.}
+
+     \KeywordTok{-s}\NormalTok{, --shrink-factor (1)}\KeywordTok{/2/3/...}
+          \KeywordTok{Running} \NormalTok{noise correction on large images can be time consuming. To lessen}
+          \KeywordTok{computation} \NormalTok{time, the input image can be resampled. The shrink factor, specified}
+          \KeywordTok{as} \NormalTok{a single integer, describes this resampling. Shrink factor = 1 is the}
+          \KeywordTok{default.}
+
+     \KeywordTok{-p}\NormalTok{, --patch-radius 1}
+                        \KeywordTok{1x1x1}
+          \KeywordTok{Patch} \NormalTok{radius. Default = 1x1x1}
+
+     \KeywordTok{-r}\NormalTok{, --search-radius 3}
+                         \KeywordTok{3x3x3}
+          \KeywordTok{Search} \NormalTok{radius. Default = 3x3x3.}
+
+     \KeywordTok{-o}\NormalTok{, --output correctedImage}
+                  \NormalTok{[}\KeywordTok{correctedImage}\NormalTok{,}\KeywordTok{<}\NormalTok{noiseImage}\KeywordTok{>}\NormalTok{]}
+          \KeywordTok{The} \NormalTok{output consists of the noise corrected version of the input image.}
+          \KeywordTok{Optionally}\NormalTok{, one can also output the estimated noise image.}
+
+     \KeywordTok{--version}
+          \KeywordTok{Get} \NormalTok{Version Information.}
+
+     \KeywordTok{-v}\NormalTok{, --verbose (0)}\KeywordTok{/1}
+          \KeywordTok{Verbose} \NormalTok{output.}
+
+     \KeywordTok{-h}
+          \KeywordTok{Print} \NormalTok{the help menu (short version)}\KeywordTok{.}
+
+     \KeywordTok{--help}
+          \KeywordTok{Print} \NormalTok{the help menu.}
+          \KeywordTok{<VALUES>}\NormalTok{: 1}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
+\begin{itemize}
+\tightlist
+\item
+  Templates representing the average mean shape and intensity are built
+  directly from the
+\item
+  cohort to be analyzed, e.g.~pediatric vs.~middle-aged brains.
+\item
+  Acquisition and anonymization (e.g.~defacing) protocols are often
+  different.
+\end{itemize}
+
 \end{frame}
@@
 \includegraphics{./evaluation/figures/templatePriors.png}
+
+Each template is
+\href{https://github.com/ntustison/antsCookTemplatePriorsExample}{processed}
+to produce auxiliary images which are used for brain extraction and
+brain segmentation.
+
+\end{frame}
+
+\begin{frame}{Brain extraction comparison}
+
+\includegraphics{./evaluation/figures/brainExtraction.png}
+
+Comparison with de facto standard FreeSurfer package. Note the
+difference in separation of the gray matter from the surrounding CSF. (0
+failures out of 1205 scans)
+
+\end{frame}
+
+\begin{frame}[fragile]{Brain segmentation}
+
+\includegraphics{./evaluation/figures/brainSegmentation.png}
+
+Randomly selected healthy individuals. \texttt{Atropos} gets good
+performance across ages.
 
@@
 \(AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)\)
+
+\end{frame}
+
+\begin{frame}{Open science principles}
+
+\includegraphics{./evaluation/figures/ageDistribution.png}
+
+\begin{itemize}
+\tightlist
+\item
+  Public data sets (IXI, NKI, OASIS, MMRR)
+\item
+  \(>\) 1200 subjects, age 4 to over 94 years old
+\end{itemize}
 
@@
 
-\section{But, wait, there's more!}\label{but-wait-theres-more}
-
-\begin{frame}{ANTs tools are multivariate}
-
-\includegraphics{./evaluation/figures/rfRmse05ANTsT1T2.png}
-
-\end{frame}
-
-\begin{frame}{Longitudinal processing}
-
-\includegraphics{./longitudinal/figures/longitudinalPipeline.png}
-
-\end{frame}
-
 \section{Current work and Advanced Normalization Tools in R

### 2016-08-04 makePresentationIBM.R

@@ -22,6 +22,7 @@ buildrmd <- 'ibm.Rmd'
 rawrmds <- c( "format.Rmd",
               "background/people2.Rmd",
               "licenses/licenses.Rmd",
+              "background/background.Rmd",
               "competitions/competitions.Rmd",
               "papers/papers.Rmd",
               "evaluation/antsvfreesurfer2.Rmd",

### 2016-08-11 mdAnderson.Rmd
ENH:  mdAnderson August 11 morning talk.

--- 2016-08-04 ibm.Rmd
@@
 ---
-title: \`\`Dr. Tustison (UVA) presentation\'\'
+title: ANTs Overview
 subtitle:
-author: Nick Tustison
+author: Brian Avants and Nick Tustison
 bibliography: REFERENCES.bib
@@
 -->
-
-# Why would you care?
-
-## \`\`Free beer\'\'
-
-![](./licenses/figures/freebeerfreespeech.jpg)
-
-## Software for medical image analysis
-
-* [FSL](http://fsl.fmrib.ox.ac.uk/fsldownloads/)
-
-* [SPM](http://www.fil.ion.ucl.ac.uk/spm/software/)
-
-* [FreeSurfer](http://www.fil.ion.ucl.ac.uk/spm/software/)
-
-* [MIPAV](http://mipav.cit.nih.gov)
-
-* [AFNI](https://afni.nimh.nih.gov/afni)
-
-* Slicer, Elastix, SimpleITK, ANTs $\longleftrightarrow$ [Insight Toolkit](http://www.itk.org)
-
-* Many more at [idoimaging.com](http://idoimaging.com)
-
-<!--
-
-## [FSL](http://fsl.fmrib.ox.ac.uk/fsldownloads/)
-
-> No part of the Software may be reproduced, modified, transmitted or
-> transferred in any form or by any means, electronic or mechanical,
-> without the express permission of the University. The permission of
-> the University is not required if the said reproduction, modification,
-> transmission or transference is done without financial return, ...
-> You may be held legally responsible for any copyright infringement
-> that is caused or encouraged by your failure to abide by these terms
-> and conditions.
->
-> __You are not permitted under this Licence to use this Software
-> commercially.__
-
-## [SPM](http://www.fil.ion.ucl.ac.uk/spm/software/)
-
-> SPM is free but copyright software, distributed under the terms of
-> the GNU General Public Licence as published by the Free Software
-> Foundation (either version 2, as given in file spm_LICENCE.man,
-> or at your option, any later version). Further details on "copyleft"
-> can be found at http://www.gnu.org/copyleft/. In particular, SPM is
-> supplied as is. No formal support or maintenance is provided or implied.
-
-> "Copyleft" says that anyone who redistributes the software, with or
-> without changes, must pass along the freedom to further copy and change
-> it. Copyleft guarantees that every user has freedom... __it is illegal to
-> distribute the improved version except as free software__...
-
-## [FreeSurfer](http://www.fil.ion.ucl.ac.uk/spm/software/)
-
-> The license granted in this Software License includes without limitation
-> the right to (i) incorporate the Software into proprietary programs
-> (subject to any restrictions applicable to such programs), (ii) add
-> your own copyright statement to your modifications of the Software, and
-> (iii) provide additional or different license terms and conditions in your
-> sublicenses of modifications of the Software; provided that in each case your
-> use, reproduction or distribution of such modifications otherwise complies
-> with the conditions stated in this Software License.
-
-## [ANTs](https://github.com/stnava/ANTs/blob/master/ANTSCopyright.txt)
-
-> Redistribution and use in source and binary forms, with or without
-> modification, are permitted provided that the following conditions
-> are met:
-> 1. _Redistributions of source code must retain the above copyright
->   notice, this list of conditions and the following disclaimer._
-> 2. _Redistributions in binary form must reproduce the above copyright
->   notice, this list of conditions and the following disclaimer in the
->   documentation and/or other materials provided with the distribution._
-> 3. _Neither the name of the consortium nor the names of its contributors
->  may be used to endorse or promote products derived from this software
->  without specific prior written permission._
-
-## [ITK](https://itk.org/ITK/project/licenseversion1.html)
-
-> The license of the Insight Toolkit is an open-source Apache 2.0 license. It
-> allows unrestricted use, including use in commercial products.
-> Starting with ITK 4.0, The Insight Toolkit is distributed under the Apache 2.0
-> license approved by the Open Source Initiative (OSI).
-
--->
-
 # ANTs lineage
 
+<!--
+
 ## Image mapping and perception: 1877
@@
 _What about syphilis, mental illness?_
+
+-->
 
@@
 
+<!--
 ##  Speaking of criminality...
@@
 
+<!--
 ##  Image mapping & biology:  1917
@@
 
+<!--
 ## Image mapping & biology: Current
@@
 ![](./background/figures/r16xr85.png)
+-->
 
@@
 
-<!--
 ## Initial scope
@@
 ![](./figures/ants_initial_scope.png)
--->
 
@@
 
-# Competitions
-
-## Algorithmic fight club
-
-![](./competitions/figures/fightclub.jpg)
-
-## International competitions
-
-* [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496): MRI brain registration
-
-* [EMPIRE 2010](http://empire10.isi.uu.nl):  CT lung registration
-
-* [Multi-Atlas Label Challenge 2012](https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page):  MRI brain registration and segmentation
-
-* [SATA Challenge 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events): MRI cardiac and canine hind leg registration
-
-* [BRATS 2013](http://martinos.org/qtim/miccai2013/): Multi-modal MRI brain segmentation
-
-* [STACOM 2014 MoCo Challenge](http://www.cardiacatlas.org/web/stacom2014/moco-introduction):  MRI cardiac motion estimation
-
-<!--- ![](./evaluation/figures/evalhistory.png) -->
-
-<!--
-
-## Klein, NeuroImage 2009
-
-![](./competitions/figures/nihms-130679-f0001.jpg)
-
-* 14 algorithms
-* publicly available data
-* different labeling protocols
-* developers tune their own algorithms
-
-## Klein results
-
-![](./competitions/figures/KleinResults2009.png)
-
-## Take-away message
-
-_"One of the most significant findings of this study is that the relative performances of
-the registration methods under comparison appear to be little affected by the choice of
-subject population, labeling protocol, and type of overlap measure....  ART, SyN, IRTK, and
-SPM's DARTEL Toolbox gave the best results according to overlap and distance measures,
-with ART and SyN delivering the most consistently high accuracy across subjects and label sets."_
-
-## EMPIRE 2010
-
-![](./competitions/figures/EMPIRE10criteria.png)
-
-* Alignment of lung boundaries,
-
-* major fissures,
-
-* annotated landmark pairs, and
-
-* topology of displacement field.
-
-## EMPIRE 2010 results
-
-![](./competitions/figures/EMPIRE10Results.png)
-
-## Multi-atlas 2012
-
-![](./competitions/figures/NKI30_MALF.png)
-
-## Multi-atlas 2012 results
-
-![](./competitions/figures/MALF2012.png)
-
-## SATA 2013
-
-Three very different problem domains
-
-![](./competitions/figures/SATA_data.png)
-
-## BRATS 2013
-
-![](./competitions/figures/brats2013results1.png)
-
-## BRATS 2013 results
-
-![](./competitions/figures/brats2013results2.png)
-
-[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
-supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)
-
-## STACOM 2014
-
-![](./competitions/figures/image_gallery.jpg)
-
--->
-
-<!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->
-
 # Major ANTs utilities
@@
 
+<!--
+
 ## Diffeomoprhisms:  differentiable map with diff. inverse
@@
 
+-->
+
 ## Beyond original SyN
@@
 
+-->
+
+<!--
 ## Template building:  creating the average Joe
@@
 ![](./papers/figures/template5.jpg)
+
+-->
 
@@
 
+<!--
+
 ## N4 ("Nick's N3")
@@
 * tested nightly within the ITK dashboard system
+
+-->
 
@@
 
+<!--
+
+##
+
 ```bash
@@
 
+<!--
 ## Possible uses
@@
 * Use in ``corrective learning''
+
+-->
 
@@
 ![](./evaluation/figures/antsvfreesurfer_regionalPlots.png)
-
-# Current work and Advanced Normalization Tools in R (ANTsR)
-
-## Multimodal Brain Tumor Segmentation (BRATS 2013)
-
-![](./competitions/figures/brats2013results1.png)
-
-[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
-supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)
-
-## White matter hyperintensities in TBI
-
-![](./wmhs/figures/wmhPipeline.png)
-
-## Social behavior and immunity dysfunction in mice
-
-![](./antsr/figures/filiano_rsfmri.png)
-
-<!--
-
-## Other ANTsR work
-
-* [Pediatric template of brain perfusion](http://www.nature.com/articles/sdata20153)
-
-* [Automated segmentation of chronic stroke lesions using LINDA: Lesion identification with neighborhood data analysis](http://www.ncbi.nlm.nih.gov/pubmed/26756101)
-
-* [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/25448483)
-
-* Corrective learning for segmentation refinement
-
--->

### 2016-08-11 mdAnderson.tex
ENH:  mdAnderson August 11 morning talk.

--- 2016-07-18 ibm.tex
@@
 
-\title{``Dr.~Tustison (UVA) presentation''}
-\author{Nick Tustison}
+\title{ANTs Overview}
+\author{Brian Avants and Nick Tustison}
 \date{}
@@
 
+\begin{frame}{Founders: Brian and Nick}
+
 \includegraphics{./figures/brian_and_nick.png}
+
+\end{frame}
 
@@
 
-\end{frame}
-
-\section{Why would you care?}\label{why-would-you-care}
-
-\begin{frame}{Software for medical image analysis}
-
-\begin{itemize}
-\item
-  \href{http://fsl.fmrib.ox.ac.uk/fsldownloads/}{FSL}
-\item
-  \href{http://www.fil.ion.ucl.ac.uk/spm/software/}{SPM}
-\item
-  \href{http://www.fil.ion.ucl.ac.uk/spm/software/}{FreeSurfer}
-\item
-  \href{http://mipav.cit.nih.gov}{MIPAV}
-\item
-  \href{https://afni.nimh.nih.gov/afni}{AFNI}
-\item
-  Slicer, Elastix, SimpleITK, ANTs \(\longleftrightarrow\)
-  \href{http://www.itk.org}{Insight Toolkit}
-\item
-  Many more at \href{http://idoimaging.com}{idoimaging.com}
-\end{itemize}
+\(+\) \href{http://neuro.debian.net/pkgs/ants.html}{neurodebian},
+\href{http://www.slicer.org/}{slicer},
+\href{https://github.com/BRAINSia/BRAINSTools}{brainsfit},
+\href{http://nipy.sourceforge.net/nipype/}{nipype},
+\href{http://www.itk.org}{itk} and more \ldots{}
 
@@
 
-\begin{frame}{International competitions}
+\section{ANTs lineage}\label{ants-lineage}
 
-\begin{itemize}
-\item
-  \href{http://www.ncbi.nlm.nih.gov/pubmed/19195496}{Klein 2009}: MRI
-  brain registration
-\item
-  \href{http://empire10.isi.uu.nl}{EMPIRE 2010}: CT lung registration
-\item
-  \href{https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page}{Multi-Atlas
-  Label Challenge 2012}: MRI brain registration and segmentation
-\item
-  \href{https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events}{SATA
-  Challenge 2013}: MRI cardiac and canine hind leg registration
-\item
-  \href{http://martinos.org/qtim/miccai2013/}{BRATS 2013}: Multi-modal
-  MRI brain segmentation
-\item
-  \href{http://www.cardiacatlas.org/web/stacom2014/moco-introduction}{STACOM
-  2014 MoCo Challenge}: MRI cardiac motion estimation
-\end{itemize}
+\begin{frame}{Initial scope}
+
+\includegraphics{./figures/ants_initial_scope.png}
 
@@
 
+\begin{frame}{Neuro tools}
+
+\includegraphics{./tools/figures/coreANtsToolsNeuro.png}
+
+\end{frame}
+
+\begin{frame}{Pulmonary tools}
+
+\includegraphics{./tools/figures/coreANtsToolsLung.png}
+
+\end{frame}
+
+\begin{frame}{Symmetric Normalization (SyN)}
+
+\(\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt + \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2\)
+
+\includegraphics{./papers/figures/fishes.png}
+
+--\textgreater{}
+
+NOtes: * Previously discussed Brians work * The variant most widely used
+--\textgreater{}
+
+\end{frame}
+
 \begin{frame}{Beyond original SyN}
@@
 \includegraphics{./papers/figures/Frontiers_BSplineSyN.png}
-
-\end{frame}
-
-\begin{frame}{Template building: creating the average Joe}
-
-\includegraphics{./papers/figures/template0.jpg}
-
-\end{frame}
-
-\begin{frame}{``Attractiveness'' \(\rightarrow\) mental processing?}
-
-\includegraphics{./papers/figures/template1.jpg}
-
-\end{frame}
-
-\begin{frame}{What about brains?}
-
-\includegraphics{./papers/figures/template3.jpg}
-
-\end{frame}
-
-\begin{frame}{Templates facilitate computation}
-
-\includegraphics{./papers/figures/template4.jpg}
 
@@
 
-\begin{frame}[fragile]{N4 (``Nick's N3'')}
+\begin{frame}{Nonparametric nonuniform intensity normalization (N3)}
 
-\begin{itemize}
-\item
-  comparative
-  \href{http://www.ncbi.nlm.nih.gov/pubmed/20378467}{evaluation}
-\item
-  small spline distances (useful for higher magnet strengths)
-\item
-  multiresolution
-\item
-  weighted regional mask (used in
-  \href{https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh}{\texttt{antsAtroposN4.sh}})
-\item
-  fast execution times
-\item
-  \emph{publicly available}
-\item
-  tested nightly within the ITK dashboard system
-\end{itemize}
+\includegraphics{./tools/n4/figures/whyN4.png}
+
+\end{frame}
+
+\begin{frame}{Atropos: flexible code base}
+
+``20+ years of development. \emph{Show me the code!}''
+
+\includegraphics{./tools/atropos/figures/atropos.png}
+
+\end{frame}
+
+\begin{frame}{Atropos + N4 \(\rightarrow\) \texttt{antsAtroposN4.sh}}
+
+\includegraphics{./tools/atropos/figures/atroposFlow.png}
+
+\end{frame}
+
+\begin{frame}{\texttt{DenoiseImage} --- contribution from Jose Manjon}
+
+\includegraphics{./tools/figures/denoising.png}
 
@@
 \includegraphics{./tools/jointfusion/figures/jointIntensityFusion.png}
-
-\end{frame}
-
-\begin{frame}{Possible uses}
-
-\begin{itemize}
-\item
-  ``Correct'' images
-
-  \begin{itemize}
-  \item
-    motion correction
-  \item
-    ``remove'' lesions
-  \end{itemize}
-\item
-  Project atlas set intensity signature
-\item
-  Use in ``corrective learning''
-\end{itemize}
 
@@
 
+\begin{frame}{Open science principles}
+
+\includegraphics{./evaluation/figures/ageDistribution.png}
+
+\begin{itemize}
+\tightlist
+\item
+  Public data sets (IXI, NKI, OASIS, MMRR)
+\item
+  \(>\) 1200 subjects, age 4 to over 94 years old
+\end{itemize}
+
+\end{frame}
+
 \begin{frame}{Prediction from cortical thickness data}
@@
 
-\section{Current work and Advanced Normalization Tools in R
-(ANTsR)}\label{current-work-and-advanced-normalization-tools-in-r-antsr}
+\begin{frame}{Age prediction per site}
 
-\begin{frame}{Multimodal Brain Tumor Segmentation (BRATS 2013)}
-
-\includegraphics{./competitions/figures/brats2013results1.png}
-
-\href{http://www.ncbi.nlm.nih.gov/pubmed/25433513}{Tustison, et al.,
-Optimal symmetric multimodal templates and concatenated random forests
-for supervised brain tumor segmentation (simplified) with \emph{ANTsR},
-\emph{Neuroinformatics}.}
+\includegraphics{./evaluation/figures/agePredictionPerSite.png}
 
@@
 
-\begin{frame}{White matter hyperintensities in TBI}
+\begin{frame}{Regional importance comparison}
 
-\includegraphics{./wmhs/figures/wmhPipeline.png}
+\includegraphics{./evaluation/figures/antsvfreesurfer_Importance.png}
+
+ANTs (left) vs.~FreeSurfer (right)
 
@@
 
-\begin{frame}{Social behavior and immunity dysfunction in mice}
+\begin{frame}{Regional measurements}
 
-\includegraphics{./antsr/figures/filiano_rsfmri.png}
+\includegraphics{./evaluation/figures/antsvfreesurfer_regionalPlots.png}
 

### 2016-08-11 makePresentationMdAnderson.R

@@ -1,0 +1,42 @@
+#!/usr/bin/env Rscript
+
+####################
+#
+#   August 11, 2016
+#
+#
+#
+#
+#####################
+
+library( ggplot2 )
+library( rmarkdown )
+
+srcDir <- "./"
+buildrmd <- 'mdAnderson.Rmd'
+
+########   Morning    ##########
+
+# Retrospective
+
+rawrmds <- c( "format.Rmd",
+              "background/people2.Rmd",
+#               "licenses/licenses.Rmd",
+              "background/background.Rmd",
+#               "competitions/competitions.Rmd",
+              "papers/papers.Rmd",
+              "evaluation/antsvfreesurfer2.Rmd"
+#               "antsr/antsr.Rmd"
+               )
+
+for ( x in 1:length(rawrmds) ) {
+  if ( x == 1 )
+    {
+    cmd<-paste( "cat ", rawrmds[x], " > ", buildrmd )
+    } else {
+      cmd<-paste( "cat ", rawrmds[x], " >> ", buildrmd )
+    }
+  system( cmd )
+  }
+
+render( buildrmd, clean = TRUE )

### 2017-04-24 asnr2017.Rmd
ENH:  ASNR 2017

--- 2016-07-18 ibm.Rmd
@@
 ---
-title: \`\`Dr. Tustison (UVA) presentation\'\'
+title: Quantitative neuroimaging with ANTs
 subtitle:
@@
     slide_level: 2
+    fig_width: 6
+    fig_height: 4.5
+    fig_caption: false
 ---
 
-# Developers and collaborators
+---
 
-<!--
-##  Founders:  Brian and Nick
--->
+# What is ANTs?
 
-![](./figures/brian_and_nick.png)
+## NLM's The Visible Human Project and The Insight Toolkit
 
-<!--
-NOtes:
-* Worked together for almost 10 years
-* have learned tons
-* have written quite a bit of code together
--->
+\begin{center}
 
-----
+\includegraphics[width=4.75in]{./figures/VisibleHumanProject_ITK.pdf}
 
-![](./figures/antsCollaborators2.png)
+\end{center}
 
-<!--
-$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
--->
+## ANTs _began with a clinical research need._
 
-<!--
-NOtes:
-* However, it is not just us
-* Other people have done quite a bit
-* and others who are not shown such as Arman
--->
+\begin{center}
 
-# Why would you care?
+\includegraphics[width=4.75in]{./figures/ANTsEvolutionarySummary.pdf}
+
+\end{center}
+
+## Advanced Normalization Tools
+
+\begin{center}
+
+\includegraphics[width=4.75in]{./tools/figures/coreANtsToolsNeuro.png}
+
+\end{center}
+
+## Advanced Normalization Tools $\rightarrow$ ``ITK-Lung''
+
+\begin{center}
+
+\includegraphics[width=4.75in]{./tools/figures/coreANtsToolsLung.png}
+
+\end{center}
 
@@
 
-## \`\`Free beer\'\'
-
-![](./licenses/figures/freebeerfreespeech.jpg)
-
--->
-
-## Software for medical image analysis
-
-* [FSL](http://fsl.fmrib.ox.ac.uk/fsldownloads/)
-
-* [SPM](http://www.fil.ion.ucl.ac.uk/spm/software/)
-
-* [FreeSurfer](http://www.fil.ion.ucl.ac.uk/spm/software/)
-
-* [MIPAV](http://mipav.cit.nih.gov)
-
-* [AFNI](https://afni.nimh.nih.gov/afni)
-
-* Slicer, Elastix, SimpleITK, ANTs $\longleftrightarrow$ [Insight Toolkit](http://www.itk.org)
-
-* Many more at [idoimaging.com](http://idoimaging.com)
-
-<!--
-
-## [FSL](http://fsl.fmrib.ox.ac.uk/fsldownloads/)
-
-> No part of the Software may be reproduced, modified, transmitted or
-> transferred in any form or by any means, electronic or mechanical,
-> without the express permission of the University. The permission of
-> the University is not required if the said reproduction, modification,
-> transmission or transference is done without financial return, ...
-> You may be held legally responsible for any copyright infringement
-> that is caused or encouraged by your failure to abide by these terms
-> and conditions.
->
-> __You are not permitted under this Licence to use this Software
-> commercially.__
-
-## [SPM](http://www.fil.ion.ucl.ac.uk/spm/software/)
-
-> SPM is free but copyright software, distributed under the terms of
-> the GNU General Public Licence as published by the Free Software
-> Foundation (either version 2, as given in file spm_LICENCE.man,
-> or at your option, any later version). Further details on "copyleft"
-> can be found at http://www.gnu.org/copyleft/. In particular, SPM is
-> supplied as is. No formal support or maintenance is provided or implied.
-
-> "Copyleft" says that anyone who redistributes the software, with or
-> without changes, must pass along the freedom to further copy and change
-> it. Copyleft guarantees that every user has freedom... __it is illegal to
-> distribute the improved version except as free software__...
-
-## [FreeSurfer](http://www.fil.ion.ucl.ac.uk/spm/software/)
-
-> The license granted in this Software License includes without limitation
-> the right to (i) incorporate the Software into proprietary programs
-> (subject to any restrictions applicable to such programs), (ii) add
-> your own copyright statement to your modifications of the Software, and
-> (iii) provide additional or different license terms and conditions in your
-> sublicenses of modifications of the Software; provided that in each case your
-> use, reproduction or distribution of such modifications otherwise complies
-> with the conditions stated in this Software License.
-
-## [ANTs](https://github.com/stnava/ANTs/blob/master/ANTSCopyright.txt)
-
-> Redistribution and use in source and binary forms, with or without
-> modification, are permitted provided that the following conditions
-> are met:
-> 1. _Redistributions of source code must retain the above copyright
->   notice, this list of conditions and the following disclaimer._
-> 2. _Redistributions in binary form must reproduce the above copyright
->   notice, this list of conditions and the following disclaimer in the
->   documentation and/or other materials provided with the distribution._
-> 3. _Neither the name of the consortium nor the names of its contributors
->  may be used to endorse or promote products derived from this software
->  without specific prior written permission._
-
-## [ITK](https://itk.org/ITK/project/licenseversion1.html)
-
-> The license of the Insight Toolkit is an open-source Apache 2.0 license. It
-> allows unrestricted use, including use in commercial products.
-> Starting with ITK 4.0, The Insight Toolkit is distributed under the Apache 2.0
-> license approved by the Open Source Initiative (OSI).
-
--->
-
-<!--
 # Competitions
--->
-
-<!--
 
@@
 
-# Major ANTs utilities
-
-## Donoho?
-
-<BR><BR>
-_\`\`Papers are just advertisements for the science.\'\'_
-<BR>
-
-<!--
-
-## Neuro tools
-
-![](./tools/figures/coreANtsToolsNeuro.png)
-
-## Pulmonary tools
-
-![](./tools/figures/coreANtsToolsLung.png)
-
--->
-
-<!--
-
-## Symmetric Normalization (SyN)
-
-$\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt + \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2$
-
-![](./papers/figures/fishes.png)
-
-NOtes:
-* Previously discussed Brians work
-* The variant most widely used
--->
-
-<!--
-
-## Diffeomorphisms:  Occam's razor modeling
-
-![](./figures/sillyputty.png)
-
-_differentiable map with differentiable inverse_
-
-## Diffeomoprhisms:  differentiable map with diff. inverse
-
-![](./figures/highresdiffeos.jpg)
-
--->
-
-<!--
-
-## Diffeomorphisms: image parameterization in a metric space
-
-![](./figures/shape_appearance.png)
--->
-
-## Beyond original SyN
-
-\small
-
-![](./papers/figures/Frontiers_ITK.png)
-
-![](./papers/figures/Frontiers_BSplineSyN.png)
-
-<!--
-
-## ```antsRegistration```
-<BR><BR>
-
-```bash
-$ antsRegistration --help
-
-COMMAND:
-     antsRegistration
-          This program is a user-level registration application meant to utilize
-          ITKv4-only classes. The user can specify any number of "stages" where a stage
-          consists of a transform; an image metric; and iterations, shrink factors, and
-          smoothing sigmas for each level.Note that dimensionality, metric, transform,
-          output, convergence, shrink-factors and smoothing-sigmas parameters are
-          mandatory.
-
-OPTIONS:
-     --version
-          Get Version Information.
-
-     -d, --dimensionality 2/3
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, we try to infer the dimensionality from the input image.
-
-     -o, --output outputTransformPrefix
-                  [outputTransformPrefix,<outputWarpedImage>,<outputInverseWarpedImage>]
-          Specify the output transform prefix (output format is .nii.gz ). Optionally, one
-          can choose to warp the moving image to the fixed space and, if the inverse
-          transform exists, one can also output the warped fixed image. Note that only the
-          images specified in the first metric call are warped. Use antsApplyTransforms to
-          warp other images using the resultant transform(s).
-
-     -j, --save-state saveSateAsTransform
-          Specify the output file for the current state of the registration. The state
-          file is written to an hdf5 composite file. It is specially usefull if we want to
-          save the current state of a SyN registration to the disk, so we can load and
-          restore that later to continue the next registration process directly started
-          from the last saved state. The output file of this flag is the same as the
-          write-composite-transform, unless the last transform is a SyN transform. In that
-          case, the inverse displacement field of the SyN transform is also added to the
-          output composite transform. Again notice that this file cannot be treated as a
-          transform, and restore-state option must be used to load the written file by
-          this flag.
-
-     -k, --restore-state restoreStateAsATransform
-          Specify the initial state of the registration which get immediately used to
-          directly initialize the registration process. The flag is mutually exclusive
-          with other intialization flags.If this flag is used, none of the
-          initial-moving-transform and initial-fixed-transform cannot be used.
-
-     -a, --write-composite-transform 1/(0)
-          Boolean specifying whether or not the composite transform (and its inverse, if
-          it exists) should be written to an hdf5 composite file. This is false by default
-          so that only the transform for each stage is written to file.
-          <VALUES>: 0
-
-     -p, --print-similarity-measure-interval <unsignedIntegerValue>
-          Prints out the CC similarity metric measure between the full-size input fixed
-          and the transformed moving images at each iteration a value of 0 (the default)
-          indicates that the full scale computation should not take placeany value greater
-          than 0 represents the interval of full scale metric computation.
-          <VALUES>: 0
-
-     -v, --write-interval-volumes <unsignedIntegerValue>
-          Writes out the output volume at each iteration. It helps to present the
-          registration process as a short movie a value of 0 (the default) indicates that
-          this option should not take placeany value greater than 0 represents the
-          interval between the iterations which outputs are written to the disk.
-          <VALUES>: 0
-
-     -z, --collapse-output-transforms (1)/0
-          Collapse output transforms. Specifically, enabling this option combines all
-          adjacent transforms wherepossible. All adjacent linear transforms are written to
-          disk in the forman itk affine transform (called xxxGenericAffine.mat).
-          Similarly, all adjacent displacement field transforms are combined when written
-          to disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available)).Also, an
-          output composite transform including the collapsed transforms is written to the
-          disk (called outputCollapsed(Inverse)Composite).
-          <VALUES>: 1
-
-     -i, --initialize-transforms-per-stage (1)/0
-          Initialize linear transforms from the previous stage. By enabling this option,
-          the current linear stage transform is directly intialized from the previous
-          stage's linear transform; this allows multiple linear stages to be run where
-          each stage directly updates the estimated linear transform from the previous
-          stage. (e.g. Translation -> Rigid -> Affine).
-          <VALUES>: 0
-
-     -n, --interpolation Linear
-                         NearestNeighbor
-                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]
-                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]
-                         BSpline[<order=3>]
-                         CosineWindowedSinc
-                         WelchWindowedSinc
-                         HammingWindowedSinc
-                         LanczosWindowedSinc
-          Several interpolation options are available in ITK. These have all been made
-          available. Currently the interpolator choice is only used to warp (and possibly
-          inverse warp) the final output image(s).
-
-     -g, --restrict-deformation PxQxR
-          This option allows the user to restrict the optimization of the displacement
-          field, translation, rigid or affine transform on a per-component basis. For
-          example, if one wants to limit the deformation or rotation of 3-D volume to the
-          first two dimensions, this is possible by specifying a weight vector of '1x1x0'
-          for a deformation field or '1x1x0x1x1x0' for a rigid
-          transformation.Low-dimensional restriction only works if there are no preceding
-          transformations.
-
-     -q, --initial-fixed-transform initialTransform
-                                   [initialTransform,<useInverse>]
-                                   [fixedImage,movingImage,initializationFeature]
-          Specify the initial fixed transform(s) which get immediately incorporated into
-          the composite transform. The order of the transforms is stack-esque in that the
-          last transform specified on the command line is the first to be applied. In
-          addition to initialization with ITK transforms, the user can perform an initial
-          translation alignment by specifying the fixed and moving images and selecting an
-          initialization feature. These features include using the geometric center of the
-          images (=0), the image intensities (=1), or the origin of the images (=2).
-
-     -r, --initial-moving-transform initialTransform
-                                    [initialTransform,<useInverse>]
-                                    [fixedImage,movingImage,initializationFeature]
-          Specify the initial moving transform(s) which get immediately incorporated into
-          the composite transform. The order of the transforms is stack-esque in that the
-          last transform specified on the command line is the first to be applied. In
-          addition to initialization with ITK transforms, the user can perform an initial
-          translation alignment by specifying the fixed and moving images and selecting an
-          initialization feature. These features include using the geometric center of the
-          images (=0), the image intensities (=1), or the origin of the images (=2).
-
-     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]
-                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]
-                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]
-                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]
-          These image metrics are available--- CC: ANTS neighborhood cross correlation,
-          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global
-          Correlation. The "metricWeight" variable is used to modulate the per stage
-          weighting of the metrics. The metrics can also employ a sampling strategy
-          defined by a sampling percentage. The sampling strategy defaults to 'None' (aka
-          a dense sampling of one sample per voxel), otherwise it defines a point set over
-          which to optimize the metric. The point set can be on a regular lattice or a
-          random lattice of points slightly perturbed to minimize aliasing artifacts.
-          samplingPercentage defines the fraction of points to select from the domain. In
-          addition, three point set metrics are available: Euclidean (ICP), Point-set
-          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).
-
-     -t, --transform Rigid[gradientStep]
-                     Affine[gradientStep]
-                     CompositeAffine[gradientStep]
-                     Similarity[gradientStep]
-                     Translation[gradientStep]
-                     BSpline[gradientStep,meshSizeAtBaseLevel]
-                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
-                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
-                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]
-                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]
-                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
-                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
-                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]
-                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]
-          Several transform options are available. The gradientStep or learningRate
-          characterizes the gradient descent optimization and is scaled appropriately for
-          each transform using the shift scales estimator. Subsequent parameters are
-          transform-specific and can be determined from the usage. For the B-spline
-          transforms one can also specify the smoothing in terms of spline distance (i.e.
-          knot spacing).
-
-     -c, --convergence MxNxO
-                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]
-          Convergence is determined from the number of iterations per level and is
-          determined by fitting a line to the normalized energy profile of the last N
-          iterations (where N is specified by the window size) and determining the slope
-          which is then compared with the convergence threshold.
-
-     -s, --smoothing-sigmas MxNxO...
-          Specify the sigma of gaussian smoothing at each level. Units are given in terms
-          of voxels ('vox') or physical spacing ('mm'). Example usage is '4x2x1mm' and
-          '4x2x1vox' where no units implies voxel spacing.
-
-     -f, --shrink-factors MxNxO...
-          Specify the shrink factor for the virtual domain (typically the fixed image) at
-          each level.
-
-     -u, --use-histogram-matching
-          Histogram match the images before registration.
-
-     -l, --use-estimate-learning-rate-once
-          turn on the option that lets you estimate the learning rate step size only at
-          the beginning of each level. * useful as a second stage of fine-scale
-          registration.
-
-     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]
-          Winsorize data based on specified quantiles.
-
-     -x, --masks [fixedImageMask,movingImageMask]
-          Image masks to limit voxels considered by the metric.
-
-     --float
-          Use 'float' instead of 'double' for computations.
-          <VALUES>: 0
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu. Will also print values used on the current command line
-          call.
-```
-
--->
-
-## Template building:  creating the average Joe
-
-![](./papers/figures/template0.jpg)
-
-## "Attractiveness" $\rightarrow$ mental processing?
-
-![](./papers/figures/template1.jpg)
-
-##  What about brains?
-
-![](./papers/figures/template3.jpg)
-
-## Templates facilitate computation
-
-![](./papers/figures/template4.jpg)
-
-<!--
-
-## Gender?
-
-![](./papers/figures/template5.jpg)
-
--->
-
-<!--
-
-## ```antsMultivariateTemplateConstruction.sh```
-
-```bash
-$ antsMultivariateTemplateConstruction.sh
-
-Usage:
-
-antsMultivariateTemplateConstruction.sh -d ImageDimension -o OUTPREFIX <other options> <images>
-
-Compulsory arguments (minimal command line requires SGE cluster, otherwise use -c & -j options):
-
-     -d:  ImageDimension: 2 or 3 (for 2 or 3 dimensional registration of single volume)
-   ImageDimension: 4 (for template generation of time-series data)
-
-     -o:  OUTPREFIX; A prefix that is prepended to all output files.
-
-<images>  List of images in the current directory, eg *_t1.nii.gz. Should be at the end
-          of the command.  Optionally, one can specify a .csv or .txt file where each
-          line is the location of the input image.  One can also specify more than
-          one file for each image for multi-modal template construction (e.g. t1 and t2).
-          For the multi-modal case, the templates will be consecutively numbered (e.g.
-          template0.nii.gz, template1.nii.gz, ...).
-
-NB: All images to be added to the template should be in the same directory, and this script
-should be invoked from that directory.
-
-Optional arguments:
-
-     -c:  Control for parallel computation (default 1) -- 0 == run serially,  1 == SGE qsub,
-          2 == use PEXEC (localhost), 3 == Apple XGrid, 4 == PBS qsub, 5 == SLURM
-
-     -g:  Gradient step size (default 0.25) -- smaller in magnitude results in more cautious steps
-
-     -i:  Iteration limit (default 4) -- iterations of the template construction (Iteration limit)*NumImages registrations.
-
-     -j:  Number of cpu cores to use (default 2; -- requires "-c 2")
-
-     -k:  Number of modalities used to construct the template (default 1)
-
-     -w:  Modality weights used in the similarity metric (default = 1) --- specified as e.g. 1x0.5x0.75
-
-     -m:  Max-iterations in each registration
-
-     -n:  N4BiasFieldCorrection of moving image (default 1) -- 0 == off, 1 == on
-
-     -p:  Commands to prepend to job scripts (e.g., change into appropriate directory, set paths, etc)
-
-     -r:  Do rigid-body registration of inputs before creating template (default 0) -- 0 == off 1 == on. Only useful when
-          you do not have an initial template
-
-     -s:  Type of similarity metric used for registration.
-
-     -t:  Type of transformation model used for registration.
-
-     -x:  XGrid arguments (e.g., -x "-p password -h controlhost")
-
-     -y:  Update the template with the full affine transform (default 1). If 0, the rigid
-          component of the affine transform will not be used to update the template. If your
-          template drifts in translation or orientation try -y 0.
-
-     -z:  Use this this volume as the target of all inputs. When not used, the script
-          will create an unbiased starting point by averaging all inputs. Use the full path!
-
-     -b:  Boolean for saving iteration output to directories (default = 0).
-
-Example:
-
-antsMultivariateTemplateConstruction.sh -d 3 -m 30x50x20 -t GR -s CC -c 1 -o MY -z InitialTemplate.nii.gz  *RF*T1x.nii.gz
-
-- In this example 30x50x20 iterations per registration are used for template creation (that is the default)
-- Greedy-SyN and CC are the metrics to guide the mapping.
-- Output is prepended with MY and the initial template is InitialTemplate.nii.gz (optional).
-- The -c option is set to 1, which will result in using the Sun Grid Engine (SGE) to distribute the computation.
-- if you do not have SGE, read the help for multi-core computation on the local machine, or Apple X-grid options.
-
---------------------------------------------------------------------------------------
-ANTS was created by:
---------------------------------------------------------------------------------------
-Brian B. Avants, Nick Tustison and Gang Song
-Penn Image Computing And Science Laboratory
-University of Pennsylvania
-
-Please reference http://www.ncbi.nlm.nih.gov/pubmed/20851191 when employing this script
-in your studies. A reproducible evaluation of ANTs similarity metric performance in
-brain image registration:
-
-* Avants BB, Tustison NJ, Song G, Cook PA, Klein A, Gee JC. Neuroimage, 2011.
-
-Also see http://www.ncbi.nlm.nih.gov/pubmed/19818860 for more details.
-
-The script has been updated and improved since this publication.
-
---------------------------------------------------------------------------------------
-script adapted by N.M. van Strien, http://www.mri-tutorial.com | NTNU MR-Center
-multivariate template adaption by Nick Tustison
---------------------------------------------------------------------------------------
-Apple XGrid support by Craig Stark
---------------------------------------------------------------------------------------
-```
-
--->
-
-## Nonparametric nonuniform intensity normalization (N3)
-
-* Developed at the Montreal Neurological Institute (John Sled, 1998)
-
-* Part of the standard preprocessing protocol in large scale projects such as ADNI
-
-* The traditional de facto standard in MRI bias correction
-    + good performance
-    + *public availability*
-
-* Public availability --- set of perl scripts coordinating various C++ programs
-
-* "*Let's incorporate N3 into ANTs!*"
-
-<!--
-## Nonparametric nonuniform intensity normalization (N3)
-
-![](./tools/n4/figures/whyN4.png)
-
-<div align="center"><img src="./tools/n4/figures/whyN4.png" frameborder="0"></img></div>
-
--->
-
-## N4 ("Nick's N3")
-
-* comparative [evaluation](http://www.ncbi.nlm.nih.gov/pubmed/20378467)
-
-* small spline distances (useful for higher magnet strengths)
-
-* multiresolution
-
-* weighted regional mask (used in [`antsAtroposN4.sh`](https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh))
-
-* fast execution times
-
-* _publicly available_
-
-* tested nightly within the ITK dashboard system
-
-<!--
-
-## ```N4BiasFieldCorrection```
-
-```bash
-$ N4BiasFieldCorrection --help
-
-COMMAND:
-     N4BiasFieldCorrection
-          N4 is a variant of the popular N3 (nonparameteric nonuniform normalization)
-          retrospective bias correction algorithm. Based on the assumption that the
-          corruption of the low frequency bias field can be modeled as a convolution of
-          the intensity histogram by a Gaussian, the basic algorithmic protocol is to
-          iterate between deconvolving the intensity histogram by a Gaussian, remapping
-          the intensities, and then spatially smoothing this result by a B-spline modeling
-          of the bias field itself. The modifications from and improvements obtained over
-          the original N3 algorithm are described in the following paper: N. Tustison et
-          al., N4ITK: Improved N3 Bias Correction, IEEE Transactions on Medical Imaging,
-          29(6):1310-1320, June 2010.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, N4 tries to infer the dimensionality from the input image.
-
-     -i, --input-image inputImageFilename
-          A scalar image is expected as input for bias correction. Since N4 log transforms
-          the intensities, negative values or values close to zero should be processed
-          prior to correction.
-
-     -x, --mask-image maskImageFilename
-          If a mask image is specified, the final bias correction is only performed in the
-          mask region. If a weight image is not specified, only intensity values inside
-          the masked region are used during the execution of the algorithm. If a weight
-          image is specified, only the non-zero weights are used in the execution of the
-          algorithm although the mask region defines where bias correction is performed in
-          the final output. Otherwise bias correction occurs over the entire image domain.
-          See also the option description for the weight image.
-
-     -r, --rescale-intensities 0/(1)
-          At each iteration, a new intensity mapping is calculated and applied but there
-          is nothing which constrains the new intensity range to be within certain values.
-          The result is that the range can "drift" from the original at each iteration.
-          This option rescales to the [min,max] range of the original image intensities
-          within the user-specified mask.
-
-     -w, --weight-image weightImageFilename
-          The weight image allows the user to perform a relative weighting of specific
-          voxels during the B-spline fitting. For example, some studies have shown that N3
-          performed on white matter segmentations improves performance. If one has a
-          spatial probability map of the white matter, one can use this map to weight the
-          b-spline fitting towards those voxels which are more probabilistically
-          classified as white matter. See also the option description for the mask image.
-
-     -s, --shrink-factor 1/2/3/4/...
-          Running N4 on large images can be time consuming. To lessen computation time,
-          the input image can be resampled. The shrink factor, specified as a single
-          integer, describes this resampling. Shrink factors <= 4 are commonly used.
-
-     -c, --convergence [<numberOfIterations=50x50x50x50>,<convergenceThreshold=0.0>]
-          Convergence is determined by calculating the coefficient of variation between
-          subsequent iterations. When this value is less than the specified threshold from
-          the previous iteration or the maximum number of iterations is exceeded the
-          program terminates. Multiple resolutions can be specified by using 'x' between
-          the number of iterations at each resolution, e.g. 100x50x50.
-
-     -b, --bspline-fitting [splineDistance,<splineOrder=3>]
-                           [initialMeshResolution,<splineOrder=3>]
-          These options describe the b-spline fitting parameters. The initial b-spline
-          mesh at the coarsest resolution is specified either as the number of elements in
-          each dimension, e.g. 2x2x3 for 3-D images, or it can be specified as a single
-          scalar parameter which describes the isotropic sizing of the mesh elements. The
-          latter option is typically preferred. For each subsequent level, the spline
-          distance decreases in half, or equivalently, the number of mesh elements doubles
-          Cubic splines (order = 3) are typically used.
-
-     -t, --histogram-sharpening [<FWHM=0.15>,<wienerNoise=0.01>,<numberOfHistogramBins=200>]
-          These options describe the histogram sharpening parameters, i.e. the
-          deconvolution step parameters described in the original N3 algorithm. The
-          default values have been shown to work fairly well.
-
-     -o, --output correctedImage
-                  [correctedImage,<biasField>]
-          The output consists of the bias corrected version of the input image.
-          Optionally, one can also output the estimated bias field.
-
-     --version
-          Get Version Information.
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-```
--->
-
-<!--
-##  Atropos -- cutting the threads of fate
-
-![](./papers/figures/Atropos_deGoya.jpg)
--->
-
-<!--
-Notes:
-* Can we use Suyash's code?
-* What about graph cuts?
--->
-
-<!--
-
-## Atropos:  flexible code base
-
-"20+ years of development.  <br>_Show me the code!_"
-
-![](./tools/atropos/figures/atropos.png)
-
--->
-
-<!--
-
-## ```Atropos```
-
-```bash
-$ Atropos --help
-
-COMMAND:
-     Atropos
-          A finite mixture modeling (FMM) segmentation approach with possibilities for
-          specifying prior constraints. These prior constraints include the specification
-          of a prior label image, prior probability images (one for each class), and/or an
-          MRF prior to enforce spatial smoothing of the labels. Similar algorithms include
-          FAST and SPM. Reference: Avants BB, Tustison NJ, Wu J, Cook PA, Gee JC. An open
-          source multivariate framework for n-tissue segmentation with evaluation on
-          public data. Neuroinformatics. 2011 Dec;9(4):381-400.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, Atropos tries to infer the dimensionality from the first input
-          image.
-
-     -a, --intensity-image [intensityImage,<adaptiveSmoothingWeight>]
-          One or more scalar images is specified for segmentation using the
-          -a/--intensity-image option. For segmentation scenarios with no prior
-          information, the first scalar image encountered on the command line is used to
-          order labelings such that the class with the smallest intensity signature is
-          class '1' through class 'N' which represents the voxels with the largest
-          intensity values. The optional adaptive smoothing weight parameter is applicable
-          only when using prior label or probability images. This scalar parameter is to
-          be specified between [0,1] which smooths each labeled region separately and
-          modulates the intensity measurement at each voxel in each intensity image
-          between the original intensity and its smoothed counterpart. The smoothness
-          parameters are governed by the -b/--bspline option.
-
-     -b, --bspline [<numberOfLevels=6>,<initialMeshResolution=1x1x...>,<splineOrder=3>]
-          If the adaptive smoothing weights are > 0, the intensity images are smoothed in
-          calculating the likelihood values. This is to account for subtle intensity
-          differences across the same tissue regions.
-
-     -i, --initialization Random[numberOfClasses]
-                          Otsu[numberOfTissueClasses]
-                          KMeans[numberOfTissueClasses,<clusterCenters(in ascending order and for first intensity image only)>]
-                          PriorProbabilityImages[numberOfTissueClasses,fileSeriesFormat(index=1 to numberOfClasses) or vectorImage,priorWeighting,<priorProbabilityThreshold>]
-                          PriorLabelImage[numberOfTissueClasses,labelImage,priorWeighting]
-          To initialize the FMM parameters, one of the following options must be
-          specified. If one does not have prior label or probability images we recommend
-          using kmeans as it is typically faster than otsu and can be used with
-          multivariate initialization. However, since a Euclidean distance on the inter
-          cluster distances is used, one might have to appropriately scale the additional
-          input images. Random initialization is meant purely for intellectual curiosity.
-          The prior weighting (specified in the range [0,1]) is used to modulate the
-          calculation of the posterior probabilities between the likelihood*mrfprior and
-          the likelihood*mrfprior*prior. For specifying many prior probability images for
-          a multi-label segmentation, we offer a minimize usage option (see -m). With that
-          option one can specify a prior probability threshold in which only those pixels
-          exceeding that threshold are stored in memory.
-
-     -s, --partial-volume-label-set label1xlabel2xlabel3
-          The partial volume estimation option allows one to modelmixtures of classes
-          within single voxels. Atropos currently allows the user to model two class
-          mixtures per partial volume class. The user specifies a set of class labels per
-          partial volume class requested. For example, suppose the user was performing a
-          classic 3-tissue segmentation (csf, gm, wm) using kmeans initialization. Suppose
-          the user also wanted to model the partial voluming effects between csf/gm and
-          gm/wm. The user would specify it using -i kmeans[3] and -s 1x2 -s 2x3. So, for
-          this example, there would be 3 tissue classes and 2 partial volume classes.
-          Optionally,the user can limit partial volume handling to mrf considerations only
-          whereby the output would only be the three tissues.
-
-     --use-partial-volume-likelihoods 1/(0)
-                                      true/(false)
-          The user can specify whether or not to use the partial volume likelihoods, in
-          which case the partial volume class is considered separate from the tissue
-          classes. Alternatively, one can use the MRF only to handle partial volume in
-          which case, partial volume voxels are not considered as separate classes.
-
-     -p, --posterior-formulation Socrates[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
-                                 Plato[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
-                                 Aristotle[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
-                                 Sigmoid[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]]
-          Different posterior probability formulations are possible as are different
-          update options. To guarantee theoretical convergence properties, a proper
-          formulation of the well-known iterated conditional modes (ICM) uses an
-          asynchronous update step modulated by a specified annealing temperature. If one
-          sets the AnnealingTemperature > 1 in the posterior formulation a traditional
-          code set for a proper ICM update will be created. Otherwise, a synchronous
-          update step will take place at each iteration. The annealing temperature, T,
-          converts the posteriorProbability to posteriorProbability^(1/T) over the course
-          of optimization.
-
-     -x, --mask-image maskImageFilename
-          The image mask (which is required) defines the region which is to be labeled by
-          the Atropos algorithm.
-
-     -c, --convergence numberOfIterations
-                       [<numberOfIterations=5>,<convergenceThreshold=0.001>]
-          Convergence is determined by calculating the mean maximum posterior probability
-          over the region of interest at each iteration. When this value decreases or
-          increases less than the specified threshold from the previous iteration or the
-          maximum number of iterations is exceeded the program terminates.
-
-     -k, --likelihood-model Gaussian
-                            HistogramParzenWindows[<sigma=1.0>,<numberOfBins=32>]
-                            ManifoldParzenWindows[<pointSetSigma=1.0>,<evaluationKNeighborhood=50>,<CovarianceKNeighborhood=0>,<kernelSigma=0>]
-                            JointShapeAndOrientationProbability[<shapeSigma=1.0>,<numberOfShapeBins=64>, <orientationSigma=1.0>, <numberOfOrientationBins=32>]
-                            LogEuclideanGaussian
-          Both parametric and non-parametric options exist in Atropos. The Gaussian
-          parametric option is commonly used (e.g. SPM & FAST) where the mean and standard
-          deviation for the Gaussian of each class is calculated at each iteration. Other
-          groups use non-parametric approaches exemplified by option 2. We recommend using
-          options 1 or 2 as they are fairly standard and the default parameters work
-          adequately.
-
-     -m, --mrf [<smoothingFactor=0.3>,<radius=1x1x...>]
-               [<mrfCoefficientImage>,<radius=1x1x...>]
-          Markov random field (MRF) theory provides a general framework for enforcing
-          spatially contextual constraints on the segmentation solution. The default
-          smoothing factor of 0.3 provides a moderate amount of smoothing. Increasing this
-          number causes more smoothing whereas decreasing the number lessens the
-          smoothing. The radius parameter specifies the mrf neighborhood. Different update
-          schemes are possible but only the asynchronous updating has theoretical
-          convergence properties.
-
-     -g, --icm [<useAsynchronousUpdate=1>,<maximumNumberOfICMIterations=1>,<icmCodeImage=''>]
-          Asynchronous updating requires the construction of an ICM code image which is a
-          label image (with labels in the range {1,..,MaximumICMCode}) constructed such
-          that no MRF neighborhood has duplicate ICM code labels. Thus, to update the
-          voxel class labels we iterate through the code labels and, for each code label,
-          we iterate through the image and update the voxel class label that has the
-          corresponding ICM code label. One can print out the ICM code image by specifying
-          an ITK-compatible image filename.
-
-     -r, --use-random-seed 0/(1)
-          Initialize internal random number generator with a random seed. Otherwise,
-          initialize with a constant seed number.
-
-     -o, --output [classifiedImage,<posteriorProbabilityImageFileNameFormat>]
-          The output consists of a labeled image where each voxel in the masked region is
-          assigned a label from 1, 2, ..., N. Optionally, one can also output the
-          posterior probability images specified in the same format as the prior
-          probability images, e.g. posterior%02d.nii.gz (C-style file name formatting).
-
-     -u, --minimize-memory-usage (0)/1
-          By default, memory usage is not minimized, however, if this is needed, the
-          various probability and distance images are calculated on the fly instead of
-          being stored in memory at each iteration. Also, if prior probability images are
-          used, only the non-negligible pixel values are stored in memory.
-          <VALUES>: 0
-
-     -w, --winsorize-outliers BoxPlot[<lowerPercentile=0.25>,<upperPercentile=0.75>,<whiskerLength=1.5>]
-                              GrubbsRosner[<significanceLevel=0.05>,<winsorizingLevel=0.10>]
-          To remove the effects of outliers in calculating the weighted mean and weighted
-          covariance, the user can opt to remove the outliers through the options
-          specified below.
-
-     -e, --use-euclidean-distance (0)/1
-          Given prior label or probability images, the labels are propagated throughout
-          the masked region so that every voxel in the mask is labeled. Propagation is
-          done by using a signed distance transform of the label. Alternatively,
-          propagation of the labels with the fast marching filter respects the distance
-          along the shape of the mask (e.g. the sinuous sulci and gyri of the cortex.
-          <VALUES>: 0
-
-     -l, --label-propagation whichLabel[lambda=0.0,<boundaryProbability=1.0>]
-          The propagation of each prior label can be controlled by the lambda and boundary
-          probability parameters. The latter parameter is the probability (in the range
-          [0,1]) of the label on the boundary which increases linearly to a maximum value
-          of 1.0 in the interior of the labeled region. The former parameter dictates the
-          exponential decay of probability propagation outside the labeled region from the
-          boundary probability, i.e. boundaryProbability*exp( -lambda * distance ).
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-```
-
--->
-
-<!--
-
-## Atropos + N4 $\rightarrow$ `antsAtroposN4.sh`
-
-![](./tools/atropos/figures/atroposFlow.png)
-
-## ```DenoiseImage``` --- contribution from Jose Manjon
-
-![](./tools/figures/denoising.png)
-
--->
-
-<!--
-```bash
-$ DenoiseImage --help
-
-COMMAND:
-     DenoiseImage
-          Denoise an image using a spatially adaptive filter originally described in J. V.
-          Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive
-          Non-Local Means Denoising of MR Images With Spatially Varying Noise Levels,
-          Journal of Magnetic Resonance Imaging, 31:192-203, June 2010.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, the program tries to infer the dimensionality from the input
-          image.
-
-     -i, --input-image inputImageFilename
-          A scalar image is expected as input for noise correction.
-
-     -n, --noise-model Rician/(Gaussian)
-          Employ a Rician or Gaussian noise model.
-
-     -x, --mask-image maskImageFilename
-          If a mask image is specified, denoising is only performed in the mask region.
-
-     -s, --shrink-factor (1)/2/3/...
-          Running noise correction on large images can be time consuming. To lessen
-          computation time, the input image can be resampled. The shrink factor, specified
-          as a single integer, describes this resampling. Shrink factor = 1 is the
-          default.
-
-     -p, --patch-radius 1
-                        1x1x1
-          Patch radius. Default = 1x1x1
-
-     -r, --search-radius 3
-                         3x3x3
-          Search radius. Default = 3x3x3.
-
-     -o, --output correctedImage
-                  [correctedImage,<noiseImage>]
-          The output consists of the noise corrected version of the input image.
-          Optionally, one can also output the estimated noise image.
-
-     --version
-          Get Version Information.
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-
-```
--->
-
-## Multi-atlas segmentation
-
-![](./tools/jointfusion/figures/jointLabelFusion.png)
-
-## New work:  joint intensity fusion
-
-![](./tools/jointfusion/figures/jointIntensityFusion.png)
-
-## Possible uses
-
-* ``Correct'' images
-
-    * motion correction
-
-    * ``remove'' lesions
-
-* Project atlas set intensity signature
-
-* Use in ``corrective learning''
-
-<!--
-
-## ```antsJointFusion``` --- contribution from Hongzhi Wang (with some added features)
-
-```bash
-$ antsJointFusion --help
-
-COMMAND:
-     antsJointFusion
-          antsJointFusion is an image fusion algorithm developed by Hongzhi Wang and Paul
-          Yushkevich which won segmentation challenges at MICCAI 2012 and MICCAI 2013. The
-          original label fusion framework was extended to accommodate intensities by Brian
-          Avants. This implementation is based on Paul's original ITK-style implementation
-          and Brian's ANTsR implementation. References include 1) H. Wang, J. W. Suh, S.
-          Das, J. Pluta, C. Craige, P. Yushkevich, Multi-atlas segmentation with joint
-          label fusion IEEE Trans. on Pattern Analysis and Machine Intelligence, 35(3),
-          611-623, 2013. and 2) H. Wang and P. A. Yushkevich, Multi-atlas segmentation
-          with joint label fusion and corrective learning--an open source implementation,
-          Front. Neuroinform., 2013.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, the program tries to infer the dimensionality from the input
-          image.
-
-     -t, --target-image targetImage
-                        [targetImageModality0,targetImageModality1,...,targetImageModalityN]
-          The target image (or multimodal target images) assumed to be aligned to a common
-          image domain.
-
-     -g, --atlas-image atlasImage
-                       [atlasImageModality0,atlasImageModality1,...,atlasImageModalityN]
-          The atlas image (or multimodal atlas images) assumed to be aligned to a common
-          image domain.
-
-     -l, --atlas-segmentation atlasSegmentation
-          The atlas segmentation images. For performing label fusion the number of
-          specified segmentations should be identical to the number of atlas image sets.
-
-     -a, --alpha 0.1
-          Regularization term added to matrix Mx for calculating the inverse. Default =
-          0.1
-
-     -b, --beta 2.0
-          Exponent for mapping intensity difference to the joint error. Default = 2.0
-
-     -r, --retain-label-posterior-images (0)/1
-          Retain label posterior probability images. Requires atlas segmentations to be
-          specified. Default = false
-
-     -f, --retain-atlas-voting-images (0)/1
-          Retain atlas voting images. Default = false
-
-     -c, --constrain-nonnegative (0)/1
-          Constrain solution to non-negative weights.
-
-     -p, --patch-radius 2
-                        2x2x2
-          Patch radius for similarity measures. Default = 2x2x2
-
-     -m, --patch-metric (PC)/MSQ
-          Metric to be used in determining the most similar neighborhood patch. Options
-          include Pearson's correlation (PC) and mean squares (MSQ). Default = PC (Pearson
-          correlation).
-
-     -s, --search-radius 3
-                         3x3x3
-                         searchRadiusMap.nii.gz
-          Search radius for similarity measures. Default = 3x3x3. One can also specify an
-          image where the value at the voxel specifies the isotropic search radius at that
-          voxel.
-
-     -e, --exclusion-image label[exclusionImage]
-          Specify an exclusion region for the given label.
-
-     -x, --mask-image maskImageFilename
-          If a mask image is specified, fusion is only performed in the mask region.
-
-     -o, --output labelFusionImage
-                  intensityFusionImageFileNameFormat
-                  [labelFusionImage,intensityFusionImageFileNameFormat,<labelPosteriorProbabilityImageFileNameFormat>,<atlasVotingWeightImageFileNameFormat>]
-          The output is the intensity and/or label fusion image. Additional optional
-          outputs include the label posterior probability images and the atlas voting
-          weight images.
-
-     --version
-          Get version information.
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-
-```
-
--->
-
 # Putting it all together---the ANTs cortical thickness pipeline
@@
 ## Cortical thickness studies
+
+\scriptsize
 
@@
 
-![](./evaluation/figures/pipeline.png)
+\begin{centering}
+
+\includegraphics[width=4.5in]{./evaluation/figures/pipeline.png}
+
+\end{centering}
 
@@
 
-![](./evaluation/figures/templates.png)
+\begin{centering}
 
-<!--
+\includegraphics[width=3in]{./evaluation/figures/templates.png}
+
+\end{centering}
+
+\small
+
 * Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.  
 * Acquisition and anonymization (e.g. defacing) protocols are often different.
--->
 
@@
 
-![](./evaluation/figures/templatePriors.png)
+\begin{centering}
 
-<!--
+\includegraphics[width=2.5in]{./evaluation/figures/templatePriors.png}
+
+\end{centering}
+
+\small
+
 Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
 to produce auxiliary images which are used for brain extraction and brain segmentation.
--->
-
-<!--
 
@@
 
-![](./evaluation/figures/brainExtraction.png)
+\begin{centering}
+
+\includegraphics[width=3.5in]{./evaluation/figures/brainExtraction.png}
+
+\end{centering}
+
+\small
 
@@
 
-![](./evaluation/figures/brainSegmentation.png)
+\begin{centering}
+
+\includegraphics[width=3.5in]{./evaluation/figures/brainSegmentation.png}
+
+\end{centering}
+
+\small
 
 Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.
--->
 
@@
 
-![](./evaluation/figures/corticalThicknessEstimation.png)
+\begin{centering}
+
+\includegraphics[width=4in]{./evaluation/figures/corticalThicknessEstimation.png}
+
+\end{centering}
+
+\small
 
@@
 
-_But without ground truth, how does one evaluate the pipeline?_
+\begin{centering}
+
+\Large
+
+{\bf But without ground truth, how does one evaluate the pipeline?}
+
+\end{centering}
 
@@
 
+\begin{centering}
+
 $AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$
+
+\end{centering}
 
@@
 * $>$ 1200 subjects, age 4 to over 94 years old
+
 -->
@@
 
-![](./evaluation/figures/evaluation.png)
+\begin{centering}
+
+\includegraphics[width=4in]{./evaluation/figures/evaluation.png}
+
+\end{centering}
 
@@
 
-![](./evaluation/figures/agePredictionPerSite.png)
+\begin{centering}
+
+\includegraphics[width=4in]{./evaluation/figures/agePredictionPerSite.png}
+
+\end{centering}
+
+-->
 
@@
 
-![](./evaluation/figures/antsvfreesurfer_Importance.png)
+\begin{centering}
 
+\small
 ANTs (left) vs. FreeSurfer (right)
+
+\includegraphics[width=4in]{./evaluation/figures/antsvfreesurfer_Importance.png}
+
+\end{centering}
+
+<!--
 
@@
 
-![](./evaluation/figures/antsvfreesurfer_regionalPlots.png)
+\begin{centering}
+
+\includegraphics[width=4in]{./evaluation/figures/antsvfreesurfer_regionalPlots.png}
+
+\end{centering}
 
@@
 
-# Current work and Advanced Normalization Tools in R (ANTsR)
+# Advanced Normalization Tools in R (ANTsR)
 
@@
 
-![](./competitions/figures/brats2013results1.png)
+\begin{centering}
+
+\includegraphics[width=4.5in]{./competitions/figures/brats2013results1.png}
+
+\end{centering}
+
+\small
 
@@
 
-![](./wmhs/figures/wmhPipeline.png)
+\begin{centering}
+
+\includegraphics[width=4.5in]{./wmhs/figures/wmhPipeline.png}
+
+\end{centering}
 
@@
 
-![](./antsr/figures/filiano_rsfmri.png)
+\begin{centering}
 
-<!--
+\includegraphics[width=3in]{./antsr/figures/filiano_rsfmri.png}
+
+\end{centering}
 
@@
 
--->
+----
+
+## Open source
+
+* https://github.com/stnava/ANTs
+* https://github.com/stnava/ANTsR

### 2017-04-24 asnr2017.tex
ENH:  ASNR 2017

--- 2016-07-18 ibm.tex
@@
 \makeatother
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight0.8\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 
@@
 
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 
-\title{``Dr.~Tustison (UVA) presentation''}
+\title{Quantitative neuroimaging with ANTs}
 \author{Nick Tustison}
@@
 
-\section{Developers and
-collaborators}\label{developers-and-collaborators}
-
-\includegraphics{./figures/brian_and_nick.png}
-
 \begin{frame}
-
-\includegraphics{./figures/antsCollaborators2.png}
 
@@
 
-\section{Why would you care?}\label{why-would-you-care}
+\section{What is ANTs?}\label{what-is-ants}
 
-\begin{frame}{Software for medical image analysis}
+\begin{frame}{NLM's The Visible Human Project and The Insight Toolkit}
 
-\begin{itemize}
-\item
-  \href{http://fsl.fmrib.ox.ac.uk/fsldownloads/}{FSL}
-\item
-  \href{http://www.fil.ion.ucl.ac.uk/spm/software/}{SPM}
-\item
-  \href{http://www.fil.ion.ucl.ac.uk/spm/software/}{FreeSurfer}
-\item
-  \href{http://mipav.cit.nih.gov}{MIPAV}
-\item
-  \href{https://afni.nimh.nih.gov/afni}{AFNI}
-\item
-  Slicer, Elastix, SimpleITK, ANTs \(\longleftrightarrow\)
-  \href{http://www.itk.org}{Insight Toolkit}
-\item
-  Many more at \href{http://idoimaging.com}{idoimaging.com}
-\end{itemize}
+\begin{center}
+
+\includegraphics[width=4.75in]{./figures/VisibleHumanProject_ITK.pdf}
+
+\end{center}
+
+\end{frame}
+
+\begin{frame}{ANTs \emph{began with a clinical research need.}}
+
+\begin{center}
+
+\includegraphics[width=4.75in]{./figures/ANTsEvolutionarySummary.pdf}
+
+\end{center}
+
+\end{frame}
+
+\begin{frame}{Advanced Normalization Tools}
+
+\begin{center}
+
+\includegraphics[width=4.75in]{./tools/figures/coreANtsToolsNeuro.png}
+
+\end{center}
+
+\end{frame}
+
+\begin{frame}{Advanced Normalization Tools \(\rightarrow\) ``ITK-Lung''}
+
+\begin{center}
+
+\includegraphics[width=4.75in]{./tools/figures/coreANtsToolsLung.png}
+
+\end{center}
 
@@
 
-\section{Major ANTs utilities}\label{major-ants-utilities}
-
-\begin{frame}{Donoho?}
-
- \emph{``Papers are just advertisements for the science.''}
-
-\end{frame}
-
-\begin{frame}{Beyond original SyN}
-
-\small
-
-\includegraphics{./papers/figures/Frontiers_ITK.png}
-
-\includegraphics{./papers/figures/Frontiers_BSplineSyN.png}
-
-\end{frame}
-
-\begin{frame}{Template building: creating the average Joe}
-
-\includegraphics{./papers/figures/template0.jpg}
-
-\end{frame}
-
-\begin{frame}{``Attractiveness'' \(\rightarrow\) mental processing?}
-
-\includegraphics{./papers/figures/template1.jpg}
-
-\end{frame}
-
-\begin{frame}{What about brains?}
-
-\includegraphics{./papers/figures/template3.jpg}
-
-\end{frame}
-
-\begin{frame}{Templates facilitate computation}
-
-\includegraphics{./papers/figures/template4.jpg}
-
-\end{frame}
-
-\begin{frame}{Nonparametric nonuniform intensity normalization (N3)}
-
-\begin{itemize}
-\item
-  Developed at the Montreal Neurological Institute (John Sled, 1998)
-\item
-  Part of the standard preprocessing protocol in large scale projects
-  such as ADNI
-\item
-  The traditional de facto standard in MRI bias correction
-
-  \begin{itemize}
-  \tightlist
-  \item
-    good performance
-  \item
-    \emph{public availability}
-  \end{itemize}
-\item
-  Public availability --- set of perl scripts coordinating various C++
-  programs
-\item
-  ``\emph{Let's incorporate N3 into ANTs!}''
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}[fragile]{N4 (``Nick's N3'')}
-
-\begin{itemize}
-\item
-  comparative
-  \href{http://www.ncbi.nlm.nih.gov/pubmed/20378467}{evaluation}
-\item
-  small spline distances (useful for higher magnet strengths)
-\item
-  multiresolution
-\item
-  weighted regional mask (used in
-  \href{https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh}{\texttt{antsAtroposN4.sh}})
-\item
-  fast execution times
-\item
-  \emph{publicly available}
-\item
-  tested nightly within the ITK dashboard system
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Multi-atlas segmentation}
-
-\includegraphics{./tools/jointfusion/figures/jointLabelFusion.png}
-
-\end{frame}
-
-\begin{frame}{New work: joint intensity fusion}
-
-\includegraphics{./tools/jointfusion/figures/jointIntensityFusion.png}
-
-\end{frame}
-
-\begin{frame}{Possible uses}
-
-\begin{itemize}
-\item
-  ``Correct'' images
-
-  \begin{itemize}
-  \item
-    motion correction
-  \item
-    ``remove'' lesions
-  \end{itemize}
-\item
-  Project atlas set intensity signature
-\item
-  Use in ``corrective learning''
-\end{itemize}
-
-\end{frame}
-
 \section{Putting it all together---the ANTs cortical thickness
@@
 \begin{frame}{Cortical thickness studies}
+
+\scriptsize
 
@@
 
-\includegraphics{./evaluation/figures/pipeline.png}
+\begin{centering}
+
+\includegraphics[width=4.5in]{./evaluation/figures/pipeline.png}
+
+\end{centering}
 
@@
 
-\includegraphics{./evaluation/figures/templates.png}
+\begin{centering}
+
+\includegraphics[width=3in]{./evaluation/figures/templates.png}
+
+\end{centering}
+
+\small
+
+\begin{itemize}
+\tightlist
+\item
+  Templates representing the average mean shape and intensity are built
+  directly from the cohort to be analyzed, e.g.~pediatric
+  vs.~middle-aged brains.\\
+\item
+  Acquisition and anonymization (e.g.~defacing) protocols are often
+  different.
+\end{itemize}
 
@@
 
-\includegraphics{./evaluation/figures/templatePriors.png}
+\begin{centering}
+
+\includegraphics[width=2.5in]{./evaluation/figures/templatePriors.png}
+
+\end{centering}
+
+\small
+
+Each template is
+\href{https://github.com/ntustison/antsCookTemplatePriorsExample}{processed}
+to produce auxiliary images which are used for brain extraction and
+brain segmentation.
+
+\end{frame}
+
+\begin{frame}{Brain extraction comparison}
+
+\begin{centering}
+
+\includegraphics[width=3.5in]{./evaluation/figures/brainExtraction.png}
+
+\end{centering}
+
+\small
+
+Comparison with de facto standard FreeSurfer package. Note the
+difference in separation of the gray matter from the surrounding CSF. (0
+failures out of 1205 scans)
+
+\end{frame}
+
+\begin{frame}[fragile]{Brain segmentation}
+
+\begin{centering}
+
+\includegraphics[width=3.5in]{./evaluation/figures/brainSegmentation.png}
+
+\end{centering}
+
+\small
+
+Randomly selected healthy individuals. \texttt{Atropos} gets good
+performance across ages.
 
@@
 
-\includegraphics{./evaluation/figures/corticalThicknessEstimation.png}
+\begin{centering}
+
+\includegraphics[width=4in]{./evaluation/figures/corticalThicknessEstimation.png}
+
+\end{centering}
+
+\small
 
@@
 
-\emph{But without ground truth, how does one evaluate the pipeline?}
+\begin{centering}
+
+\Large
+
+{\bf But without ground truth, how does one evaluate the pipeline?}
+
+\end{centering}
 
@@
 
-\(AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)\)
+\begin{centering}
+
+$AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$
+
+\end{centering}
 
@@
 
-\includegraphics{./evaluation/figures/evaluation.png}
+\begin{centering}
+
+\includegraphics[width=4in]{./evaluation/figures/evaluation.png}
+
+\end{centering}
 
@@
 
-\section{Current work and Advanced Normalization Tools in R
-(ANTsR)}\label{current-work-and-advanced-normalization-tools-in-r-antsr}
+\begin{frame}{Regional importance comparison}
+
+\begin{centering}
+
+\small
+ANTs (left) vs. FreeSurfer (right)
+
+\includegraphics[width=4in]{./evaluation/figures/antsvfreesurfer_Importance.png}
+
+\end{centering}
+
+\end{frame}
+
+\section{Advanced Normalization Tools in R
+(ANTsR)}\label{advanced-normalization-tools-in-r-antsr}
 
@@
 
-\includegraphics{./competitions/figures/brats2013results1.png}
+\begin{centering}
+
+\includegraphics[width=4.5in]{./competitions/figures/brats2013results1.png}
+
+\end{centering}
+
+\small
 
@@
 
-\includegraphics{./wmhs/figures/wmhPipeline.png}
+\begin{centering}
+
+\includegraphics[width=4.5in]{./wmhs/figures/wmhPipeline.png}
+
+\end{centering}
 
@@
 
-\includegraphics{./antsr/figures/filiano_rsfmri.png}
+\begin{centering}
+
+\includegraphics[width=3in]{./antsr/figures/filiano_rsfmri.png}
+
+\end{centering}
+
+\end{frame}
+
+\begin{frame}{Other ANTsR work}
+
+\begin{itemize}
+\item
+  \href{http://www.nature.com/articles/sdata20153}{Pediatric template of
+  brain perfusion}
+\item
+  \href{http://www.ncbi.nlm.nih.gov/pubmed/26756101}{Automated
+  segmentation of chronic stroke lesions using LINDA: Lesion
+  identification with neighborhood data analysis}
+\item
+  \href{http://www.ncbi.nlm.nih.gov/pubmed/25448483}{Eigenanatomy}
+\item
+  Corrective learning for segmentation refinement
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Open source}
+
+\begin{itemize}
+\tightlist
+\item
+  \url{https://github.com/stnava/ANTs}
+\item
+  \url{https://github.com/stnava/ANTsR}
+\end{itemize}
 

### 2017-04-24 background/background3.Rmd
ENH:  ASNR 2017

--- 2017-04-24 asnr2017.Rmd
@@
----
-title: Quantitative neuroimaging with ANTs
-subtitle:
-author: Nick Tustison
-bibliography: REFERENCES.bib
-output:
-  beamer_presentation:
-    colortheme: dolphin
-    fonttheme:  professionalfonts
-    highlight: tango
-    incremental: false
-    theme:  AnnArbor
-    includes:
-      in_header: mystyle.tex
- #   toc: yes
-    keep_tex: yes
-    slide_level: 2
-    fig_width: 6
-    fig_height: 4.5
-    fig_caption: false
----
-
----
-
 # What is ANTs?
@@
 \end{center}
-
-<!--
-
-# Competitions
-
-## Algorithmic fight club
-
-![](./competitions/figures/fightclub.jpg)
-
--->
-
-## International competitions
-
-* [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496): MRI brain registration
-
-* [EMPIRE 2010](http://empire10.isi.uu.nl):  CT lung registration
-
-* [Multi-Atlas Label Challenge 2012](https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page):  MRI brain registration and segmentation
-
-* [SATA Challenge 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events): MRI cardiac and canine hind leg registration
-
-* [BRATS 2013](http://martinos.org/qtim/miccai2013/): Multi-modal MRI brain segmentation
-
-* [STACOM 2014 MoCo Challenge](http://www.cardiacatlas.org/web/stacom2014/moco-introduction):  MRI cardiac motion estimation
-
-<!--- ![](./evaluation/figures/evalhistory.png) -->
-
-<!--
-
-## Klein, NeuroImage 2009
-
-![](./competitions/figures/nihms-130679-f0001.jpg)
-
-* 14 algorithms
-* publicly available data
-* different labeling protocols
-* developers tune their own algorithms
-
-## Klein results
-
-![](./competitions/figures/KleinResults2009.png)
-
-## Take-away message
-
-_"One of the most significant findings of this study is that the relative performances of
-the registration methods under comparison appear to be little affected by the choice of
-subject population, labeling protocol, and type of overlap measure....  ART, SyN, IRTK, and
-SPM's DARTEL Toolbox gave the best results according to overlap and distance measures,
-with ART and SyN delivering the most consistently high accuracy across subjects and label sets."_
-
-## EMPIRE 2010
-
-![](./competitions/figures/EMPIRE10criteria.png)
-
-* Alignment of lung boundaries,
-
-* major fissures,
-
-* annotated landmark pairs, and
-
-* topology of displacement field.
-
-## EMPIRE 2010 results
-
-![](./competitions/figures/EMPIRE10Results.png)
-
-## Multi-atlas 2012
-
-![](./competitions/figures/NKI30_MALF.png)
-
-## Multi-atlas 2012 results
-
-![](./competitions/figures/MALF2012.png)
-
-## SATA 2013
-
-Three very different problem domains
-
-![](./competitions/figures/SATA_data.png)
-
-## BRATS 2013
-
-![](./competitions/figures/brats2013results1.png)
-
-## BRATS 2013 results
-
-![](./competitions/figures/brats2013results2.png)
-
-[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
-supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)
-
-## STACOM 2014
-
-![](./competitions/figures/image_gallery.jpg)
-
--->
-
-<!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->
-
-# Putting it all together---the ANTs cortical thickness pipeline
-
-## Cortical thickness studies
-
-\scriptsize
-
-```{r, results='asis', echo = FALSE}
-conditions <- c( "Tetris-playing ability", "Huntington’s disease", "schizophrenia", "bipolar disorder",
-                 "Alzheimer’s disease", "frontotemporal dementia", "Parkinson’s disease",
-                 "Williams syndrome", "multiple sclerosis", "autism", "migraines",
-                 "chronic smoking", "alcoholism", "cocaine addiction", "Tourette syndrome in children",
-                 "scoliosis in female adolescents", "early-onset blindness", "chronic pancreatitis",
-                 "obsessive-compulsive disorder", "ADHD", "obesity", "heritable depression",
-                 "elderly depression", "age", "gender",
-                 "handedness", "intelligence", "athletic ability", "meditative practices", "musical ability",
-                 "tendency toward criminality", "childhood sexual abuse in female adolescents",
-                  "traumatic brain injury", "untreated male-to-female transsexuality" )
-
-conditionsDF <- data.frame( Column1 = conditions[1:floor( 0.5*length(conditions) )], Column2 = conditions[( 1+floor( 0.5*length(conditions) ) ):length(conditions)] )
-knitr::kable( conditionsDF )
-```
-
-<!--
-
-## ANTs-related background
-
-* Sandy, Brian, and <span style="color:red;">DiReCT</span>
-    + used other tools such as FMRIB Automated Segmentation Tool (FAST)
-    + `KellySlater.cxx`
-* pipedream scripts "adequate for Penn data."
-* `KellyKapowski.cxx` and `antsCorticalThickness.sh`
-* _"Let's evaluate on open data."_
-* and, eventually, _"Let's compare with FreeSurfer."_
-
-## Basic components of the pipeline
-
-1. template building (offline)
-2. brain extraction
-3. cortical thickness estimation
-4. cortical parcellation
-
-## Sample results
-
-![](./evaluation/figures/components.png)
-
--->
-
-## The ANTs structural brain mapping workflow
-
-\begin{centering}
-
-\includegraphics[width=4.5in]{./evaluation/figures/pipeline.png}
-
-\end{centering}
-
-## Template building
-
-*Tailor data to your specific cohort*
-
-\begin{centering}
-
-\includegraphics[width=3in]{./evaluation/figures/templates.png}
-
-\end{centering}
-
-\small
-
-* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.  
-* Acquisition and anonymization (e.g. defacing) protocols are often different.
-
-## Template priors
-
-\begin{centering}
-
-\includegraphics[width=2.5in]{./evaluation/figures/templatePriors.png}
-
-\end{centering}
-
-\small
-
-Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
-to produce auxiliary images which are used for brain extraction and brain segmentation.
-
-## Brain extraction comparison
-
-\begin{centering}
-
-\includegraphics[width=3.5in]{./evaluation/figures/brainExtraction.png}
-
-\end{centering}
-
-\small
-
-Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
-the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
-
-## Brain segmentation
-
-\begin{centering}
-
-\includegraphics[width=3.5in]{./evaluation/figures/brainSegmentation.png}
-
-\end{centering}
-
-\small
-
-Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.
-
-## Cortical thickness maps
-
-\begin{centering}
-
-\includegraphics[width=4in]{./evaluation/figures/corticalThicknessEstimation.png}
-
-\end{centering}
-
-\small
-
-In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter,
-*ANTs* diffeomorphically registers the white matter to the combined gray/white matters
-while simultaneously estimating thickness.
-
-----
-
-\begin{centering}
-
-\Large
-
-{\bf But without ground truth, how does one evaluate the pipeline?}
-
-\end{centering}
-
-## Predict age and gender
-
-\begin{centering}
-
-$AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$
-
-\end{centering}
-
-<!--
-
-## Open science principles
-
-![](./evaluation/figures/ageDistribution.png)
-
-* Public data sets (IXI, NKI, OASIS, MMRR)
-* $>$ 1200 subjects, age 4 to over 94 years old
-
--->
-
-## Prediction from cortical thickness data
-
-\begin{centering}
-
-\includegraphics[width=4in]{./evaluation/figures/evaluation.png}
-
-\end{centering}
-
-<!--
-
-## Age prediction per site
-
-\begin{centering}
-
-\includegraphics[width=4in]{./evaluation/figures/agePredictionPerSite.png}
-
-\end{centering}
-
--->
-
-## Regional importance comparison
-
-\begin{centering}
-
-\small
-ANTs (left) vs. FreeSurfer (right)
-
-\includegraphics[width=4in]{./evaluation/figures/antsvfreesurfer_Importance.png}
-
-\end{centering}
-
-<!--
-
-## Regional measurements
-
-\begin{centering}
-
-\includegraphics[width=4in]{./evaluation/figures/antsvfreesurfer_regionalPlots.png}
-
-\end{centering}
-
--->
-
-# Advanced Normalization Tools in R (ANTsR)
-
-## Multimodal Brain Tumor Segmentation (BRATS 2013)
-
-\begin{centering}
-
-\includegraphics[width=4.5in]{./competitions/figures/brats2013results1.png}
-
-\end{centering}
-
-\small
-
-[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
-supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)
-
-## White matter hyperintensities in TBI
-
-\begin{centering}
-
-\includegraphics[width=4.5in]{./wmhs/figures/wmhPipeline.png}
-
-\end{centering}
-
-## Social behavior and immunity dysfunction in mice
-
-\begin{centering}
-
-\includegraphics[width=3in]{./antsr/figures/filiano_rsfmri.png}
-
-\end{centering}
-
-## Other ANTsR work
-
-* [Pediatric template of brain perfusion](http://www.nature.com/articles/sdata20153)
-
-* [Automated segmentation of chronic stroke lesions using LINDA: Lesion identification with neighborhood data analysis](http://www.ncbi.nlm.nih.gov/pubmed/26756101)
-
-* [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/25448483)
-
-* Corrective learning for segmentation refinement
-
-----
-
-## Open source
-
-* https://github.com/stnava/ANTs
-* https://github.com/stnava/ANTsR

### 2017-04-24 evaluation/antsvfreesurfer2.Rmd
ENH:  ASNR 2017

@@
 
-![](./evaluation/figures/templates.png)
+\begin{centering}
 
-* Templates representing the average mean shape and intensity are built directly from the
-* cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
+\includegraphics[width=3in]{./evaluation/figures/templates.png}
+
+\end{centering}
+
+\small
+
+* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.  
 * Acquisition and anonymization (e.g. defacing) protocols are often different.
@@
 
-![](./evaluation/figures/templatePriors.png)
+\begin{centering}
+
+\includegraphics[width=2.5in]{./evaluation/figures/templatePriors.png}
+
+\end{centering}
+
+\small
 
@@
 
-![](./evaluation/figures/brainSegmentation.png)
+\begin{centering}
+
+\includegraphics[width=3.5in]{./evaluation/figures/brainSegmentation.png}
+
+\end{centering}
+
+\small
 
@@
 
+\begin{centering}
+
 $AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$
+
+\end{centering}
+
+<!--
 
@@
 
+-->
+
 ## Prediction from cortical thickness data
 
-![](./evaluation/figures/evaluation.png)
+\begin{centering}
+
+\includegraphics[width=4in]{./evaluation/figures/evaluation.png}
+
+\end{centering}
+
+<!--
 
@@
 
-![](./evaluation/figures/antsvfreesurfer_regionalPlots.png)
+\begin{centering}
+
+\includegraphics[width=4in]{./evaluation/figures/antsvfreesurfer_regionalPlots.png}
+
+\end{centering}
+
+-->

### 2017-04-24 ibm.Rmd
ENH:  ASNR 2017

--- 2016-07-18 ibm.Rmd
@@
 ---
+# Background
 
-# Developers and collaborators
+## Founding developers
 
-<!--
-##  Founders:  Brian and Nick
--->
+<div align="center"><img width="1800" src="./figures/brian_and_nick.png" frameborder="0"></img></div>
 
-![](./figures/brian_and_nick.png)
+BBA & NJT
 
-<!--
-NOtes:
-* Worked together for almost 10 years
-* have learned tons
-* have written quite a bit of code together
--->
+## Long-term collaborators
 
-----
+![](./figures/antscollab.jpg)
 
-![](./figures/antsCollaborators2.png)
+$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
 
-<!--
-$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
--->
+##
 
-<!--
-NOtes:
-* However, it is not just us
-* Other people have done quite a bit
-* and others who are not shown such as Arman
--->
+![](./figures/lion.png)
 
-# Why would you care?
+a pride: common way of doing things
 
-<!--
+... in a competitive world ...
 
-## \`\`Free beer\'\'
+## Definitions
 
-![](./licenses/figures/freebeerfreespeech.jpg)
+* Registration $=$ estimate an "optimal" geometric mapping between image pairs or image sets (e.g. Affine)
 
--->
+*  Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)</span>
 
-## Software for medical image analysis
+* Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)
 
-* [FSL](http://fsl.fmrib.ox.ac.uk/fsldownloads/)
+* <span style="color:grey;">Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)</span>
 
-* [SPM](http://www.fil.ion.ucl.ac.uk/spm/software/)
+* Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>
 
-* [FreeSurfer](http://www.fil.ion.ucl.ac.uk/spm/software/)
+* <span style="color:grey;">Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)</span>
 
-* [MIPAV](http://mipav.cit.nih.gov)
+* MALF: multi-atlas label fusion - using anatomical dictionaries to label new data
 
-* [AFNI](https://afni.nimh.nih.gov/afni)
+* <span style="color:grey;">Solutions to challenging statistical image processing problems usually need elements from each of the above</span>
 
-* Slicer, Elastix, SimpleITK, ANTs $\longleftrightarrow$ [Insight Toolkit](http://www.itk.org)
+## Image mapping & perception: 1878
 
-* Many more at [idoimaging.com](http://idoimaging.com)
+![](./figures/galton.png)
 
-<!--
+* Francis Galton: Can we see criminality in the face?
 
-## [FSL](http://fsl.fmrib.ox.ac.uk/fsldownloads/)
+* (maybe he should have used *ANTs*?)
 
-> No part of the Software may be reproduced, modified, transmitted or
-> transferred in any form or by any means, electronic or mechanical,
-> without the express permission of the University. The permission of
-> the University is not required if the said reproduction, modification,
-> transmission or transference is done without financial return, ...
-> You may be held legally responsible for any copyright infringement
-> that is caused or encouraged by your failure to abide by these terms
-> and conditions.
->
-> __You are not permitted under this Licence to use this Software
-> commercially.__
+## Image mapping & biology: 1917
 
-## [SPM](http://www.fil.ion.ucl.ac.uk/spm/software/)
+![](./figures/dthompson.png)
 
-> SPM is free but copyright software, distributed under the terms of
-> the GNU General Public Licence as published by the Free Software
-> Foundation (either version 2, as given in file spm_LICENCE.man,
-> or at your option, any later version). Further details on "copyleft"
-> can be found at http://www.gnu.org/copyleft/. In particular, SPM is
-> supplied as is. No formal support or maintenance is provided or implied.
+D'Arcy Thompson
 
-> "Copyleft" says that anyone who redistributes the software, with or
-> without changes, must pass along the freedom to further copy and change
-> it. Copyleft guarantees that every user has freedom... __it is illegal to
-> distribute the improved version except as free software__...
+## Initial scope
 
-## [FreeSurfer](http://www.fil.ion.ucl.ac.uk/spm/software/)
+![](./figures/ants_initial_scope.png)
 
-> The license granted in this Software License includes without limitation
-> the right to (i) incorporate the Software into proprietary programs
-> (subject to any restrictions applicable to such programs), (ii) add
-> your own copyright statement to your modifications of the Software, and
-> (iii) provide additional or different license terms and conditions in your
-> sublicenses of modifications of the Software; provided that in each case your
-> use, reproduction or distribution of such modifications otherwise complies
-> with the conditions stated in this Software License.
+... just do a better registration (tell story) ...
 
-## [ANTs](https://github.com/stnava/ANTs/blob/master/ANTSCopyright.txt)
+## *ANTs* Lineage
 
-> Redistribution and use in source and binary forms, with or without
-> modification, are permitted provided that the following conditions
-> are met:
-> 1. _Redistributions of source code must retain the above copyright
->   notice, this list of conditions and the following disclaimer._
-> 2. _Redistributions in binary form must reproduce the above copyright
->   notice, this list of conditions and the following disclaimer in the
->   documentation and/or other materials provided with the distribution._
-> 3. _Neither the name of the consortium nor the names of its contributors
->  may be used to endorse or promote products derived from this software
->  without specific prior written permission._
+![](./figures/lineage.jpg)
 
-## [ITK](https://itk.org/ITK/project/licenseversion1.html)
+References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
 
-> The license of the Insight Toolkit is an open-source Apache 2.0 license. It
-> allows unrestricted use, including use in commercial products.
-> Starting with ITK 4.0, The Insight Toolkit is distributed under the Apache 2.0
-> license approved by the Open Source Initiative (OSI).
+## Diffeomorphisms
 
--->
+<div align="center"><img width="1433" src="./figures/sillyputty.png" frameborder="0"></img></div>
 
-<!--
-# Competitions
--->
+plausible physical modeling of large, invertible deformations
 
-<!--
+"differentiable map with differentiable inverse"
 
-## Algorithmic fight club
-
-![](./competitions/figures/fightclub.jpg)
-
--->
-
-## International competitions
-
-* [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496): MRI brain registration
-
-* [EMPIRE 2010](http://empire10.isi.uu.nl):  CT lung registration
-
-* [Multi-Atlas Label Challenge 2012](https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page):  MRI brain registration and segmentation
-
-* [SATA Challenge 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events): MRI cardiac and canine hind leg registration
-
-* [BRATS 2013](http://martinos.org/qtim/miccai2013/): Multi-modal MRI brain segmentation
-
-* [STACOM 2014 MoCo Challenge](http://www.cardiacatlas.org/web/stacom2014/moco-introduction):  MRI cardiac motion estimation
-
-<!--- ![](./evaluation/figures/evalhistory.png) -->
-
-<!--
-
-## Klein, NeuroImage 2009
-
-![](./competitions/figures/nihms-130679-f0001.jpg)
-
-* 14 algorithms
-* publicly available data
-* different labeling protocols
-* developers tune their own algorithms
-
-## Klein results
-
-![](./competitions/figures/KleinResults2009.png)
-
-## Take-away message
-
-_"One of the most significant findings of this study is that the relative performances of
-the registration methods under comparison appear to be little affected by the choice of
-subject population, labeling protocol, and type of overlap measure....  ART, SyN, IRTK, and
-SPM's DARTEL Toolbox gave the best results according to overlap and distance measures,
-with ART and SyN delivering the most consistently high accuracy across subjects and label sets."_
-
-## EMPIRE 2010
-
-![](./competitions/figures/EMPIRE10criteria.png)
-
-* Alignment of lung boundaries,
-
-* major fissures,
-
-* annotated landmark pairs, and
-
-* topology of displacement field.
-
-## EMPIRE 2010 results
-
-![](./competitions/figures/EMPIRE10Results.png)
-
-## Multi-atlas 2012
-
-![](./competitions/figures/NKI30_MALF.png)
-
-## Multi-atlas 2012 results
-
-![](./competitions/figures/MALF2012.png)
-
-## SATA 2013
-
-Three very different problem domains
-
-![](./competitions/figures/SATA_data.png)
-
-## BRATS 2013
-
-![](./competitions/figures/brats2013results1.png)
-
-## BRATS 2013 results
-
-![](./competitions/figures/brats2013results2.png)
-
-[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
-supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)
-
-## STACOM 2014
-
-![](./competitions/figures/image_gallery.jpg)
-
--->
-
-<!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->
-
-# Major ANTs utilities
-
-## Donoho?
-
-<BR><BR>
-_\`\`Papers are just advertisements for the science.\'\'_
-<BR>
-
-<!--
-
-## Neuro tools
-
-![](./tools/figures/coreANtsToolsNeuro.png)
-
-## Pulmonary tools
-
-![](./tools/figures/coreANtsToolsLung.png)
-
--->
-
-<!--
-
-## Symmetric Normalization (SyN)
-
-$\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt + \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2$
-
-![](./papers/figures/fishes.png)
-
-NOtes:
-* Previously discussed Brians work
-* The variant most widely used
--->
-
-<!--
-
-## Diffeomorphisms:  Occam's razor modeling
-
-![](./figures/sillyputty.png)
-
-_differentiable map with differentiable inverse_
-
-## Diffeomoprhisms:  differentiable map with diff. inverse
-
+## Fine-grained and flexible maps
 ![](./figures/highresdiffeos.jpg)
 
--->
-
-<!--
+... to correct a misconception about diffeomorphisms ...
 
@@
 ![](./figures/shape_appearance.png)
--->
 
-## Beyond original SyN
+## General purpose library for multivariate image registration, segmentation & statistical analysis tools
 
-\small
+* 170,000+ lines of C++, 6$+$ years of work, 15+ collaborators.
 
-![](./papers/figures/Frontiers_ITK.png)
+* Generic mathematical methods that are tunable for
+application specific domains:  no-free lunch
 
-![](./papers/figures/Frontiers_BSplineSyN.png)
+* Deep testing on multiple platforms ... osx, linux, windows.
 
-<!--
+* Several "wins" in public knock-abouts ( [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496), [Murphy 2011](http://www.ncbi.nlm.nih.gov/pubmed/21632295), [SATA 2012 and 2013](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/), [BRATS 2013](http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf), others )
 
-## ```antsRegistration```
-<BR><BR>
-
-```bash
-$ antsRegistration --help
-
-COMMAND:
-     antsRegistration
-          This program is a user-level registration application meant to utilize
-          ITKv4-only classes. The user can specify any number of "stages" where a stage
-          consists of a transform; an image metric; and iterations, shrink factors, and
-          smoothing sigmas for each level.Note that dimensionality, metric, transform,
-          output, convergence, shrink-factors and smoothing-sigmas parameters are
-          mandatory.
-
-OPTIONS:
-     --version
-          Get Version Information.
-
-     -d, --dimensionality 2/3
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, we try to infer the dimensionality from the input image.
-
-     -o, --output outputTransformPrefix
-                  [outputTransformPrefix,<outputWarpedImage>,<outputInverseWarpedImage>]
-          Specify the output transform prefix (output format is .nii.gz ). Optionally, one
-          can choose to warp the moving image to the fixed space and, if the inverse
-          transform exists, one can also output the warped fixed image. Note that only the
-          images specified in the first metric call are warped. Use antsApplyTransforms to
-          warp other images using the resultant transform(s).
-
-     -j, --save-state saveSateAsTransform
-          Specify the output file for the current state of the registration. The state
-          file is written to an hdf5 composite file. It is specially usefull if we want to
-          save the current state of a SyN registration to the disk, so we can load and
-          restore that later to continue the next registration process directly started
-          from the last saved state. The output file of this flag is the same as the
-          write-composite-transform, unless the last transform is a SyN transform. In that
-          case, the inverse displacement field of the SyN transform is also added to the
-          output composite transform. Again notice that this file cannot be treated as a
-          transform, and restore-state option must be used to load the written file by
-          this flag.
-
-     -k, --restore-state restoreStateAsATransform
-          Specify the initial state of the registration which get immediately used to
-          directly initialize the registration process. The flag is mutually exclusive
-          with other intialization flags.If this flag is used, none of the
-          initial-moving-transform and initial-fixed-transform cannot be used.
-
-     -a, --write-composite-transform 1/(0)
-          Boolean specifying whether or not the composite transform (and its inverse, if
-          it exists) should be written to an hdf5 composite file. This is false by default
-          so that only the transform for each stage is written to file.
-          <VALUES>: 0
-
-     -p, --print-similarity-measure-interval <unsignedIntegerValue>
-          Prints out the CC similarity metric measure between the full-size input fixed
-          and the transformed moving images at each iteration a value of 0 (the default)
-          indicates that the full scale computation should not take placeany value greater
-          than 0 represents the interval of full scale metric computation.
-          <VALUES>: 0
-
-     -v, --write-interval-volumes <unsignedIntegerValue>
-          Writes out the output volume at each iteration. It helps to present the
-          registration process as a short movie a value of 0 (the default) indicates that
-          this option should not take placeany value greater than 0 represents the
-          interval between the iterations which outputs are written to the disk.
-          <VALUES>: 0
-
-     -z, --collapse-output-transforms (1)/0
-          Collapse output transforms. Specifically, enabling this option combines all
-          adjacent transforms wherepossible. All adjacent linear transforms are written to
-          disk in the forman itk affine transform (called xxxGenericAffine.mat).
-          Similarly, all adjacent displacement field transforms are combined when written
-          to disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available)).Also, an
-          output composite transform including the collapsed transforms is written to the
-          disk (called outputCollapsed(Inverse)Composite).
-          <VALUES>: 1
-
-     -i, --initialize-transforms-per-stage (1)/0
-          Initialize linear transforms from the previous stage. By enabling this option,
-          the current linear stage transform is directly intialized from the previous
-          stage's linear transform; this allows multiple linear stages to be run where
-          each stage directly updates the estimated linear transform from the previous
-          stage. (e.g. Translation -> Rigid -> Affine).
-          <VALUES>: 0
-
-     -n, --interpolation Linear
-                         NearestNeighbor
-                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]
-                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]
-                         BSpline[<order=3>]
-                         CosineWindowedSinc
-                         WelchWindowedSinc
-                         HammingWindowedSinc
-                         LanczosWindowedSinc
-          Several interpolation options are available in ITK. These have all been made
-          available. Currently the interpolator choice is only used to warp (and possibly
-          inverse warp) the final output image(s).
-
-     -g, --restrict-deformation PxQxR
-          This option allows the user to restrict the optimization of the displacement
-          field, translation, rigid or affine transform on a per-component basis. For
-          example, if one wants to limit the deformation or rotation of 3-D volume to the
-          first two dimensions, this is possible by specifying a weight vector of '1x1x0'
-          for a deformation field or '1x1x0x1x1x0' for a rigid
-          transformation.Low-dimensional restriction only works if there are no preceding
-          transformations.
-
-     -q, --initial-fixed-transform initialTransform
-                                   [initialTransform,<useInverse>]
-                                   [fixedImage,movingImage,initializationFeature]
-          Specify the initial fixed transform(s) which get immediately incorporated into
-          the composite transform. The order of the transforms is stack-esque in that the
-          last transform specified on the command line is the first to be applied. In
-          addition to initialization with ITK transforms, the user can perform an initial
-          translation alignment by specifying the fixed and moving images and selecting an
-          initialization feature. These features include using the geometric center of the
-          images (=0), the image intensities (=1), or the origin of the images (=2).
-
-     -r, --initial-moving-transform initialTransform
-                                    [initialTransform,<useInverse>]
-                                    [fixedImage,movingImage,initializationFeature]
-          Specify the initial moving transform(s) which get immediately incorporated into
-          the composite transform. The order of the transforms is stack-esque in that the
-          last transform specified on the command line is the first to be applied. In
-          addition to initialization with ITK transforms, the user can perform an initial
-          translation alignment by specifying the fixed and moving images and selecting an
-          initialization feature. These features include using the geometric center of the
-          images (=0), the image intensities (=1), or the origin of the images (=2).
-
-     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]
-                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]
-                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]
-                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]
-          These image metrics are available--- CC: ANTS neighborhood cross correlation,
-          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global
-          Correlation. The "metricWeight" variable is used to modulate the per stage
-          weighting of the metrics. The metrics can also employ a sampling strategy
-          defined by a sampling percentage. The sampling strategy defaults to 'None' (aka
-          a dense sampling of one sample per voxel), otherwise it defines a point set over
-          which to optimize the metric. The point set can be on a regular lattice or a
-          random lattice of points slightly perturbed to minimize aliasing artifacts.
-          samplingPercentage defines the fraction of points to select from the domain. In
-          addition, three point set metrics are available: Euclidean (ICP), Point-set
-          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).
-
-     -t, --transform Rigid[gradientStep]
-                     Affine[gradientStep]
-                     CompositeAffine[gradientStep]
-                     Similarity[gradientStep]
-                     Translation[gradientStep]
-                     BSpline[gradientStep,meshSizeAtBaseLevel]
-                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
-                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
-                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]
-                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]
-                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
-                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
-                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]
-                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]
-          Several transform options are available. The gradientStep or learningRate
-          characterizes the gradient descent optimization and is scaled appropriately for
-          each transform using the shift scales estimator. Subsequent parameters are
-          transform-specific and can be determined from the usage. For the B-spline
-          transforms one can also specify the smoothing in terms of spline distance (i.e.
-          knot spacing).
-
-     -c, --convergence MxNxO
-                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]
-          Convergence is determined from the number of iterations per level and is
-          determined by fitting a line to the normalized energy profile of the last N
-          iterations (where N is specified by the window size) and determining the slope
-          which is then compared with the convergence threshold.
-
-     -s, --smoothing-sigmas MxNxO...
-          Specify the sigma of gaussian smoothing at each level. Units are given in terms
-          of voxels ('vox') or physical spacing ('mm'). Example usage is '4x2x1mm' and
-          '4x2x1vox' where no units implies voxel spacing.
-
-     -f, --shrink-factors MxNxO...
-          Specify the shrink factor for the virtual domain (typically the fixed image) at
-          each level.
-
-     -u, --use-histogram-matching
-          Histogram match the images before registration.
-
-     -l, --use-estimate-learning-rate-once
-          turn on the option that lets you estimate the learning rate step size only at
-          the beginning of each level. * useful as a second stage of fine-scale
-          registration.
-
-     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]
-          Winsorize data based on specified quantiles.
-
-     -x, --masks [fixedImageMask,movingImageMask]
-          Image masks to limit voxels considered by the metric.
-
-     --float
-          Use 'float' instead of 'double' for computations.
-          <VALUES>: 0
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu. Will also print values used on the current command line
-          call.
+```
+    An algorithm must use prior knowledge about a problem
+    to do well on that problem
 ```
 
--->
+## *ANTs*: Beyond Registration
 
-## Template building:  creating the average Joe
+![](./figures/antscapabilities.jpg)
 
-![](./papers/figures/template0.jpg)
+[Atropos](http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison) segmentation, [N4 inhomogeneity correction](http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison), [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants), [SCCAN](http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants), [Prior-constrained PCA](http://www.ncbi.nlm.nih.gov/pubmed/24852460), and [atlas-based label fusion](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/) and [MALF](http://www.ncbi.nlm.nih.gov/pubmed/21237273) (powerful expert systems for segmentation)
 
-## "Attractiveness" $\rightarrow$ mental processing?
+## On documentation
 
-![](./papers/figures/template1.jpg)
+![](figures/Chainsaw.jpg)
 
-##  What about brains?
+documentation is important
 
-![](./papers/figures/template3.jpg)
+## On documentation
 
-## Templates facilitate computation
+![](figures/blindmen.jpg)
 
-![](./papers/figures/template4.jpg)
+... developers can be blind to doc deficiencies
 
-<!--
-
-## Gender?
-
-![](./papers/figures/template5.jpg)
-
--->
-
-<!--
-
-## ```antsMultivariateTemplateConstruction.sh```
-
-```bash
-$ antsMultivariateTemplateConstruction.sh
-
-Usage:
-
-antsMultivariateTemplateConstruction.sh -d ImageDimension -o OUTPREFIX <other options> <images>
-
-Compulsory arguments (minimal command line requires SGE cluster, otherwise use -c & -j options):
-
-     -d:  ImageDimension: 2 or 3 (for 2 or 3 dimensional registration of single volume)
-   ImageDimension: 4 (for template generation of time-series data)
-
-     -o:  OUTPREFIX; A prefix that is prepended to all output files.
-
-<images>  List of images in the current directory, eg *_t1.nii.gz. Should be at the end
-          of the command.  Optionally, one can specify a .csv or .txt file where each
-          line is the location of the input image.  One can also specify more than
-          one file for each image for multi-modal template construction (e.g. t1 and t2).
-          For the multi-modal case, the templates will be consecutively numbered (e.g.
-          template0.nii.gz, template1.nii.gz, ...).
-
-NB: All images to be added to the template should be in the same directory, and this script
-should be invoked from that directory.
-
-Optional arguments:
-
-     -c:  Control for parallel computation (default 1) -- 0 == run serially,  1 == SGE qsub,
-          2 == use PEXEC (localhost), 3 == Apple XGrid, 4 == PBS qsub, 5 == SLURM
-
-     -g:  Gradient step size (default 0.25) -- smaller in magnitude results in more cautious steps
-
-     -i:  Iteration limit (default 4) -- iterations of the template construction (Iteration limit)*NumImages registrations.
-
-     -j:  Number of cpu cores to use (default 2; -- requires "-c 2")
-
-     -k:  Number of modalities used to construct the template (default 1)
-
-     -w:  Modality weights used in the similarity metric (default = 1) --- specified as e.g. 1x0.5x0.75
-
-     -m:  Max-iterations in each registration
-
-     -n:  N4BiasFieldCorrection of moving image (default 1) -- 0 == off, 1 == on
-
-     -p:  Commands to prepend to job scripts (e.g., change into appropriate directory, set paths, etc)
-
-     -r:  Do rigid-body registration of inputs before creating template (default 0) -- 0 == off 1 == on. Only useful when
-          you do not have an initial template
-
-     -s:  Type of similarity metric used for registration.
-
-     -t:  Type of transformation model used for registration.
-
-     -x:  XGrid arguments (e.g., -x "-p password -h controlhost")
-
-     -y:  Update the template with the full affine transform (default 1). If 0, the rigid
-          component of the affine transform will not be used to update the template. If your
-          template drifts in translation or orientation try -y 0.
-
-     -z:  Use this this volume as the target of all inputs. When not used, the script
-          will create an unbiased starting point by averaging all inputs. Use the full path!
-
-     -b:  Boolean for saving iteration output to directories (default = 0).
-
-Example:
-
-antsMultivariateTemplateConstruction.sh -d 3 -m 30x50x20 -t GR -s CC -c 1 -o MY -z InitialTemplate.nii.gz  *RF*T1x.nii.gz
-
-- In this example 30x50x20 iterations per registration are used for template creation (that is the default)
-- Greedy-SyN and CC are the metrics to guide the mapping.
-- Output is prepended with MY and the initial template is InitialTemplate.nii.gz (optional).
-- The -c option is set to 1, which will result in using the Sun Grid Engine (SGE) to distribute the computation.
-- if you do not have SGE, read the help for multi-core computation on the local machine, or Apple X-grid options.
-
---------------------------------------------------------------------------------------
-ANTS was created by:
---------------------------------------------------------------------------------------
-Brian B. Avants, Nick Tustison and Gang Song
-Penn Image Computing And Science Laboratory
-University of Pennsylvania
-
-Please reference http://www.ncbi.nlm.nih.gov/pubmed/20851191 when employing this script
-in your studies. A reproducible evaluation of ANTs similarity metric performance in
-brain image registration:
-
-* Avants BB, Tustison NJ, Song G, Cook PA, Klein A, Gee JC. Neuroimage, 2011.
-
-Also see http://www.ncbi.nlm.nih.gov/pubmed/19818860 for more details.
-
-The script has been updated and improved since this publication.
-
---------------------------------------------------------------------------------------
-script adapted by N.M. van Strien, http://www.mri-tutorial.com | NTNU MR-Center
-multivariate template adaption by Nick Tustison
---------------------------------------------------------------------------------------
-Apple XGrid support by Craig Stark
---------------------------------------------------------------------------------------
-```
-
--->
-
-## Nonparametric nonuniform intensity normalization (N3)
-
-* Developed at the Montreal Neurological Institute (John Sled, 1998)
-
-* Part of the standard preprocessing protocol in large scale projects such as ADNI
-
-* The traditional de facto standard in MRI bias correction
-    + good performance
-    + *public availability*
-
-* Public availability --- set of perl scripts coordinating various C++ programs
-
-* "*Let's incorporate N3 into ANTs!*"
-
-<!--
-## Nonparametric nonuniform intensity normalization (N3)
-
-![](./tools/n4/figures/whyN4.png)
-
-<div align="center"><img src="./tools/n4/figures/whyN4.png" frameborder="0"></img></div>
-
--->
-
-## N4 ("Nick's N3")
-
-* comparative [evaluation](http://www.ncbi.nlm.nih.gov/pubmed/20378467)
-
-* small spline distances (useful for higher magnet strengths)
-
-* multiresolution
-
-* weighted regional mask (used in [`antsAtroposN4.sh`](https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh))
-
-* fast execution times
-
-* _publicly available_
-
-* tested nightly within the ITK dashboard system
-
-<!--
-
-## ```N4BiasFieldCorrection```
-
-```bash
-$ N4BiasFieldCorrection --help
-
-COMMAND:
-     N4BiasFieldCorrection
-          N4 is a variant of the popular N3 (nonparameteric nonuniform normalization)
-          retrospective bias correction algorithm. Based on the assumption that the
-          corruption of the low frequency bias field can be modeled as a convolution of
-          the intensity histogram by a Gaussian, the basic algorithmic protocol is to
-          iterate between deconvolving the intensity histogram by a Gaussian, remapping
-          the intensities, and then spatially smoothing this result by a B-spline modeling
-          of the bias field itself. The modifications from and improvements obtained over
-          the original N3 algorithm are described in the following paper: N. Tustison et
-          al., N4ITK: Improved N3 Bias Correction, IEEE Transactions on Medical Imaging,
-          29(6):1310-1320, June 2010.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, N4 tries to infer the dimensionality from the input image.
-
-     -i, --input-image inputImageFilename
-          A scalar image is expected as input for bias correction. Since N4 log transforms
-          the intensities, negative values or values close to zero should be processed
-          prior to correction.
-
-     -x, --mask-image maskImageFilename
-          If a mask image is specified, the final bias correction is only performed in the
-          mask region. If a weight image is not specified, only intensity values inside
-          the masked region are used during the execution of the algorithm. If a weight
-          image is specified, only the non-zero weights are used in the execution of the
-          algorithm although the mask region defines where bias correction is performed in
-          the final output. Otherwise bias correction occurs over the entire image domain.
-          See also the option description for the weight image.
-
-     -r, --rescale-intensities 0/(1)
-          At each iteration, a new intensity mapping is calculated and applied but there
-          is nothing which constrains the new intensity range to be within certain values.
-          The result is that the range can "drift" from the original at each iteration.
-          This option rescales to the [min,max] range of the original image intensities
-          within the user-specified mask.
-
-     -w, --weight-image weightImageFilename
-          The weight image allows the user to perform a relative weighting of specific
-          voxels during the B-spline fitting. For example, some studies have shown that N3
-          performed on white matter segmentations improves performance. If one has a
-          spatial probability map of the white matter, one can use this map to weight the
-          b-spline fitting towards those voxels which are more probabilistically
-          classified as white matter. See also the option description for the mask image.
-
-     -s, --shrink-factor 1/2/3/4/...
-          Running N4 on large images can be time consuming. To lessen computation time,
-          the input image can be resampled. The shrink factor, specified as a single
-          integer, describes this resampling. Shrink factors <= 4 are commonly used.
-
-     -c, --convergence [<numberOfIterations=50x50x50x50>,<convergenceThreshold=0.0>]
-          Convergence is determined by calculating the coefficient of variation between
-          subsequent iterations. When this value is less than the specified threshold from
-          the previous iteration or the maximum number of iterations is exceeded the
-          program terminates. Multiple resolutions can be specified by using 'x' between
-          the number of iterations at each resolution, e.g. 100x50x50.
-
-     -b, --bspline-fitting [splineDistance,<splineOrder=3>]
-                           [initialMeshResolution,<splineOrder=3>]
-          These options describe the b-spline fitting parameters. The initial b-spline
-          mesh at the coarsest resolution is specified either as the number of elements in
-          each dimension, e.g. 2x2x3 for 3-D images, or it can be specified as a single
-          scalar parameter which describes the isotropic sizing of the mesh elements. The
-          latter option is typically preferred. For each subsequent level, the spline
-          distance decreases in half, or equivalently, the number of mesh elements doubles
-          Cubic splines (order = 3) are typically used.
-
-     -t, --histogram-sharpening [<FWHM=0.15>,<wienerNoise=0.01>,<numberOfHistogramBins=200>]
-          These options describe the histogram sharpening parameters, i.e. the
-          deconvolution step parameters described in the original N3 algorithm. The
-          default values have been shown to work fairly well.
-
-     -o, --output correctedImage
-                  [correctedImage,<biasField>]
-          The output consists of the bias corrected version of the input image.
-          Optionally, one can also output the estimated bias field.
-
-     --version
-          Get Version Information.
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-```
--->
-
-<!--
-##  Atropos -- cutting the threads of fate
-
-![](./papers/figures/Atropos_deGoya.jpg)
--->
-
-<!--
-Notes:
-* Can we use Suyash's code?
-* What about graph cuts?
--->
-
-<!--
-
-## Atropos:  flexible code base
-
-"20+ years of development.  <br>_Show me the code!_"
-
-![](./tools/atropos/figures/atropos.png)
-
--->
-
-<!--
-
-## ```Atropos```
-
-```bash
-$ Atropos --help
-
-COMMAND:
-     Atropos
-          A finite mixture modeling (FMM) segmentation approach with possibilities for
-          specifying prior constraints. These prior constraints include the specification
-          of a prior label image, prior probability images (one for each class), and/or an
-          MRF prior to enforce spatial smoothing of the labels. Similar algorithms include
-          FAST and SPM. Reference: Avants BB, Tustison NJ, Wu J, Cook PA, Gee JC. An open
-          source multivariate framework for n-tissue segmentation with evaluation on
-          public data. Neuroinformatics. 2011 Dec;9(4):381-400.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, Atropos tries to infer the dimensionality from the first input
-          image.
-
-     -a, --intensity-image [intensityImage,<adaptiveSmoothingWeight>]
-          One or more scalar images is specified for segmentation using the
-          -a/--intensity-image option. For segmentation scenarios with no prior
-          information, the first scalar image encountered on the command line is used to
-          order labelings such that the class with the smallest intensity signature is
-          class '1' through class 'N' which represents the voxels with the largest
-          intensity values. The optional adaptive smoothing weight parameter is applicable
-          only when using prior label or probability images. This scalar parameter is to
-          be specified between [0,1] which smooths each labeled region separately and
-          modulates the intensity measurement at each voxel in each intensity image
-          between the original intensity and its smoothed counterpart. The smoothness
-          parameters are governed by the -b/--bspline option.
-
-     -b, --bspline [<numberOfLevels=6>,<initialMeshResolution=1x1x...>,<splineOrder=3>]
-          If the adaptive smoothing weights are > 0, the intensity images are smoothed in
-          calculating the likelihood values. This is to account for subtle intensity
-          differences across the same tissue regions.
-
-     -i, --initialization Random[numberOfClasses]
-                          Otsu[numberOfTissueClasses]
-                          KMeans[numberOfTissueClasses,<clusterCenters(in ascending order and for first intensity image only)>]
-                          PriorProbabilityImages[numberOfTissueClasses,fileSeriesFormat(index=1 to numberOfClasses) or vectorImage,priorWeighting,<priorProbabilityThreshold>]
-                          PriorLabelImage[numberOfTissueClasses,labelImage,priorWeighting]
-          To initialize the FMM parameters, one of the following options must be
-          specified. If one does not have prior label or probability images we recommend
-          using kmeans as it is typically faster than otsu and can be used with
-          multivariate initialization. However, since a Euclidean distance on the inter
-          cluster distances is used, one might have to appropriately scale the additional
-          input images. Random initialization is meant purely for intellectual curiosity.
-          The prior weighting (specified in the range [0,1]) is used to modulate the
-          calculation of the posterior probabilities between the likelihood*mrfprior and
-          the likelihood*mrfprior*prior. For specifying many prior probability images for
-          a multi-label segmentation, we offer a minimize usage option (see -m). With that
-          option one can specify a prior probability threshold in which only those pixels
-          exceeding that threshold are stored in memory.
-
-     -s, --partial-volume-label-set label1xlabel2xlabel3
-          The partial volume estimation option allows one to modelmixtures of classes
-          within single voxels. Atropos currently allows the user to model two class
-          mixtures per partial volume class. The user specifies a set of class labels per
-          partial volume class requested. For example, suppose the user was performing a
-          classic 3-tissue segmentation (csf, gm, wm) using kmeans initialization. Suppose
-          the user also wanted to model the partial voluming effects between csf/gm and
-          gm/wm. The user would specify it using -i kmeans[3] and -s 1x2 -s 2x3. So, for
-          this example, there would be 3 tissue classes and 2 partial volume classes.
-          Optionally,the user can limit partial volume handling to mrf considerations only
-          whereby the output would only be the three tissues.
-
-     --use-partial-volume-likelihoods 1/(0)
-                                      true/(false)
-          The user can specify whether or not to use the partial volume likelihoods, in
-          which case the partial volume class is considered separate from the tissue
-          classes. Alternatively, one can use the MRF only to handle partial volume in
-          which case, partial volume voxels are not considered as separate classes.
-
-     -p, --posterior-formulation Socrates[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
-                                 Plato[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
-                                 Aristotle[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
-                                 Sigmoid[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]]
-          Different posterior probability formulations are possible as are different
-          update options. To guarantee theoretical convergence properties, a proper
-          formulation of the well-known iterated conditional modes (ICM) uses an
-          asynchronous update step modulated by a specified annealing temperature. If one
-          sets the AnnealingTemperature > 1 in the posterior formulation a traditional
-          code set for a proper ICM update will be created. Otherwise, a synchronous
-          update step will take place at each iteration. The annealing temperature, T,
-          converts the posteriorProbability to posteriorProbability^(1/T) over the course
-          of optimization.
-
-     -x, --mask-image maskImageFilename
-          The image mask (which is required) defines the region which is to be labeled by
-          the Atropos algorithm.
-
-     -c, --convergence numberOfIterations
-                       [<numberOfIterations=5>,<convergenceThreshold=0.001>]
-          Convergence is determined by calculating the mean maximum posterior probability
-          over the region of interest at each iteration. When this value decreases or
-          increases less than the specified threshold from the previous iteration or the
-          maximum number of iterations is exceeded the program terminates.
-
-     -k, --likelihood-model Gaussian
-                            HistogramParzenWindows[<sigma=1.0>,<numberOfBins=32>]
-                            ManifoldParzenWindows[<pointSetSigma=1.0>,<evaluationKNeighborhood=50>,<CovarianceKNeighborhood=0>,<kernelSigma=0>]
-                            JointShapeAndOrientationProbability[<shapeSigma=1.0>,<numberOfShapeBins=64>, <orientationSigma=1.0>, <numberOfOrientationBins=32>]
-                            LogEuclideanGaussian
-          Both parametric and non-parametric options exist in Atropos. The Gaussian
-          parametric option is commonly used (e.g. SPM & FAST) where the mean and standard
-          deviation for the Gaussian of each class is calculated at each iteration. Other
-          groups use non-parametric approaches exemplified by option 2. We recommend using
-          options 1 or 2 as they are fairly standard and the default parameters work
-          adequately.
-
-     -m, --mrf [<smoothingFactor=0.3>,<radius=1x1x...>]
-               [<mrfCoefficientImage>,<radius=1x1x...>]
-          Markov random field (MRF) theory provides a general framework for enforcing
-          spatially contextual constraints on the segmentation solution. The default
-          smoothing factor of 0.3 provides a moderate amount of smoothing. Increasing this
-          number causes more smoothing whereas decreasing the number lessens the
-          smoothing. The radius parameter specifies the mrf neighborhood. Different update
-          schemes are possible but only the asynchronous updating has theoretical
-          convergence properties.
-
-     -g, --icm [<useAsynchronousUpdate=1>,<maximumNumberOfICMIterations=1>,<icmCodeImage=''>]
-          Asynchronous updating requires the construction of an ICM code image which is a
-          label image (with labels in the range {1,..,MaximumICMCode}) constructed such
-          that no MRF neighborhood has duplicate ICM code labels. Thus, to update the
-          voxel class labels we iterate through the code labels and, for each code label,
-          we iterate through the image and update the voxel class label that has the
-          corresponding ICM code label. One can print out the ICM code image by specifying
-          an ITK-compatible image filename.
-
-     -r, --use-random-seed 0/(1)
-          Initialize internal random number generator with a random seed. Otherwise,
-          initialize with a constant seed number.
-
-     -o, --output [classifiedImage,<posteriorProbabilityImageFileNameFormat>]
-          The output consists of a labeled image where each voxel in the masked region is
-          assigned a label from 1, 2, ..., N. Optionally, one can also output the
-          posterior probability images specified in the same format as the prior
-          probability images, e.g. posterior%02d.nii.gz (C-style file name formatting).
-
-     -u, --minimize-memory-usage (0)/1
-          By default, memory usage is not minimized, however, if this is needed, the
-          various probability and distance images are calculated on the fly instead of
-          being stored in memory at each iteration. Also, if prior probability images are
-          used, only the non-negligible pixel values are stored in memory.
-          <VALUES>: 0
-
-     -w, --winsorize-outliers BoxPlot[<lowerPercentile=0.25>,<upperPercentile=0.75>,<whiskerLength=1.5>]
-                              GrubbsRosner[<significanceLevel=0.05>,<winsorizingLevel=0.10>]
-          To remove the effects of outliers in calculating the weighted mean and weighted
-          covariance, the user can opt to remove the outliers through the options
-          specified below.
-
-     -e, --use-euclidean-distance (0)/1
-          Given prior label or probability images, the labels are propagated throughout
-          the masked region so that every voxel in the mask is labeled. Propagation is
-          done by using a signed distance transform of the label. Alternatively,
-          propagation of the labels with the fast marching filter respects the distance
-          along the shape of the mask (e.g. the sinuous sulci and gyri of the cortex.
-          <VALUES>: 0
-
-     -l, --label-propagation whichLabel[lambda=0.0,<boundaryProbability=1.0>]
-          The propagation of each prior label can be controlled by the lambda and boundary
-          probability parameters. The latter parameter is the probability (in the range
-          [0,1]) of the label on the boundary which increases linearly to a maximum value
-          of 1.0 in the interior of the labeled region. The former parameter dictates the
-          exponential decay of probability propagation outside the labeled region from the
-          boundary probability, i.e. boundaryProbability*exp( -lambda * distance ).
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-```
-
--->
-
-<!--
-
-## Atropos + N4 $\rightarrow$ `antsAtroposN4.sh`
-
-![](./tools/atropos/figures/atroposFlow.png)
-
-## ```DenoiseImage``` --- contribution from Jose Manjon
-
-![](./tools/figures/denoising.png)
-
--->
-
-<!--
-```bash
-$ DenoiseImage --help
-
-COMMAND:
-     DenoiseImage
-          Denoise an image using a spatially adaptive filter originally described in J. V.
-          Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive
-          Non-Local Means Denoising of MR Images With Spatially Varying Noise Levels,
-          Journal of Magnetic Resonance Imaging, 31:192-203, June 2010.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, the program tries to infer the dimensionality from the input
-          image.
-
-     -i, --input-image inputImageFilename
-          A scalar image is expected as input for noise correction.
-
-     -n, --noise-model Rician/(Gaussian)
-          Employ a Rician or Gaussian noise model.
-
-     -x, --mask-image maskImageFilename
-          If a mask image is specified, denoising is only performed in the mask region.
-
-     -s, --shrink-factor (1)/2/3/...
-          Running noise correction on large images can be time consuming. To lessen
-          computation time, the input image can be resampled. The shrink factor, specified
-          as a single integer, describes this resampling. Shrink factor = 1 is the
-          default.
-
-     -p, --patch-radius 1
-                        1x1x1
-          Patch radius. Default = 1x1x1
-
-     -r, --search-radius 3
-                         3x3x3
-          Search radius. Default = 3x3x3.
-
-     -o, --output correctedImage
-                  [correctedImage,<noiseImage>]
-          The output consists of the noise corrected version of the input image.
-          Optionally, one can also output the estimated noise image.
-
-     --version
-          Get Version Information.
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-
-```
--->
-
-## Multi-atlas segmentation
-
-![](./tools/jointfusion/figures/jointLabelFusion.png)
-
-## New work:  joint intensity fusion
-
-![](./tools/jointfusion/figures/jointIntensityFusion.png)
-
-## Possible uses
-
-* ``Correct'' images
-
-    * motion correction
-
-    * ``remove'' lesions
-
-* Project atlas set intensity signature
-
-* Use in ``corrective learning''
-
-<!--
-
-## ```antsJointFusion``` --- contribution from Hongzhi Wang (with some added features)
-
-```bash
-$ antsJointFusion --help
-
-COMMAND:
-     antsJointFusion
-          antsJointFusion is an image fusion algorithm developed by Hongzhi Wang and Paul
-          Yushkevich which won segmentation challenges at MICCAI 2012 and MICCAI 2013. The
-          original label fusion framework was extended to accommodate intensities by Brian
-          Avants. This implementation is based on Paul's original ITK-style implementation
-          and Brian's ANTsR implementation. References include 1) H. Wang, J. W. Suh, S.
-          Das, J. Pluta, C. Craige, P. Yushkevich, Multi-atlas segmentation with joint
-          label fusion IEEE Trans. on Pattern Analysis and Machine Intelligence, 35(3),
-          611-623, 2013. and 2) H. Wang and P. A. Yushkevich, Multi-atlas segmentation
-          with joint label fusion and corrective learning--an open source implementation,
-          Front. Neuroinform., 2013.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, the program tries to infer the dimensionality from the input
-          image.
-
-     -t, --target-image targetImage
-                        [targetImageModality0,targetImageModality1,...,targetImageModalityN]
-          The target image (or multimodal target images) assumed to be aligned to a common
-          image domain.
-
-     -g, --atlas-image atlasImage
-                       [atlasImageModality0,atlasImageModality1,...,atlasImageModalityN]
-          The atlas image (or multimodal atlas images) assumed to be aligned to a common
-          image domain.
-
-     -l, --atlas-segmentation atlasSegmentation
-          The atlas segmentation images. For performing label fusion the number of
-          specified segmentations should be identical to the number of atlas image sets.
-
-     -a, --alpha 0.1
-          Regularization term added to matrix Mx for calculating the inverse. Default =
-          0.1
-
-     -b, --beta 2.0
-          Exponent for mapping intensity difference to the joint error. Default = 2.0
-
-     -r, --retain-label-posterior-images (0)/1
-          Retain label posterior probability images. Requires atlas segmentations to be
-          specified. Default = false
-
-     -f, --retain-atlas-voting-images (0)/1
-          Retain atlas voting images. Default = false
-
-     -c, --constrain-nonnegative (0)/1
-          Constrain solution to non-negative weights.
-
-     -p, --patch-radius 2
-                        2x2x2
-          Patch radius for similarity measures. Default = 2x2x2
-
-     -m, --patch-metric (PC)/MSQ
-          Metric to be used in determining the most similar neighborhood patch. Options
-          include Pearson's correlation (PC) and mean squares (MSQ). Default = PC (Pearson
-          correlation).
-
-     -s, --search-radius 3
-                         3x3x3
-                         searchRadiusMap.nii.gz
-          Search radius for similarity measures. Default = 3x3x3. One can also specify an
-          image where the value at the voxel specifies the isotropic search radius at that
-          voxel.
-
-     -e, --exclusion-image label[exclusionImage]
-          Specify an exclusion region for the given label.
-
-     -x, --mask-image maskImageFilename
-          If a mask image is specified, fusion is only performed in the mask region.
-
-     -o, --output labelFusionImage
-                  intensityFusionImageFileNameFormat
-                  [labelFusionImage,intensityFusionImageFileNameFormat,<labelPosteriorProbabilityImageFileNameFormat>,<atlasVotingWeightImageFileNameFormat>]
-          The output is the intensity and/or label fusion image. Additional optional
-          outputs include the label posterior probability images and the atlas voting
-          weight images.
-
-     --version
-          Get version information.
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-
-```
-
--->
-
-# Putting it all together---the ANTs cortical thickness pipeline
-
-## Cortical thickness studies
-
-```{r, results='asis', echo = FALSE}
-conditions <- c( "Tetris-playing ability", "Huntington’s disease", "schizophrenia", "bipolar disorder",
-                 "Alzheimer’s disease", "frontotemporal dementia", "Parkinson’s disease",
-                 "Williams syndrome", "multiple sclerosis", "autism", "migraines",
-                 "chronic smoking", "alcoholism", "cocaine addiction", "Tourette syndrome in children",
-                 "scoliosis in female adolescents", "early-onset blindness", "chronic pancreatitis",
-                 "obsessive-compulsive disorder", "ADHD", "obesity", "heritable depression",
-                 "elderly depression", "age", "gender",
-                 "handedness", "intelligence", "athletic ability", "meditative practices", "musical ability",
-                 "tendency toward criminality", "childhood sexual abuse in female adolescents",
-                  "traumatic brain injury", "untreated male-to-female transsexuality" )
-
-conditionsDF <- data.frame( Column1 = conditions[1:floor( 0.5*length(conditions) )], Column2 = conditions[( 1+floor( 0.5*length(conditions) ) ):length(conditions)] )
-knitr::kable( conditionsDF )
-```
-
-<!--
-
-## ANTs-related background
-
-* Sandy, Brian, and <span style="color:red;">DiReCT</span>
-    + used other tools such as FMRIB Automated Segmentation Tool (FAST)
-    + `KellySlater.cxx`
-* pipedream scripts "adequate for Penn data."
-* `KellyKapowski.cxx` and `antsCorticalThickness.sh`
-* _"Let's evaluate on open data."_
-* and, eventually, _"Let's compare with FreeSurfer."_
-
-## Basic components of the pipeline
-
-1. template building (offline)
-2. brain extraction
-3. cortical thickness estimation
-4. cortical parcellation
-
-## Sample results
-
-![](./evaluation/figures/components.png)
-
--->
-
-## The ANTs structural brain mapping workflow
-
-![](./evaluation/figures/pipeline.png)
-
-## Template building
-
-*Tailor data to your specific cohort*
-
-![](./evaluation/figures/templates.png)
-
-<!--
-* Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.
-* Acquisition and anonymization (e.g. defacing) protocols are often different.
--->
-
-## Template priors
-
-![](./evaluation/figures/templatePriors.png)
-
-<!--
-Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
-to produce auxiliary images which are used for brain extraction and brain segmentation.
--->
-
-<!--
-
-## Brain extraction comparison
-
-![](./evaluation/figures/brainExtraction.png)
-
-Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
-the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
--->
-
-<!--
-
-## Brain segmentation
-
-![](./evaluation/figures/brainSegmentation.png)
-
-Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.
--->
-
-## Cortical thickness maps
-
-![](./evaluation/figures/corticalThicknessEstimation.png)
-
-In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter,
-*ANTs* diffeomorphically registers the white matter to the combined gray/white matters
-while simultaneously estimating thickness.
-
-----
-
-_But without ground truth, how does one evaluate the pipeline?_
-
-## Predict age and gender
-
-$AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$
-
-<!--
-
-## Open science principles
-
-![](./evaluation/figures/ageDistribution.png)
-
-* Public data sets (IXI, NKI, OASIS, MMRR)
-* $>$ 1200 subjects, age 4 to over 94 years old
--->
-
-## Prediction from cortical thickness data
-
-![](./evaluation/figures/evaluation.png)
-
-<!--
-
-## Age prediction per site
-
-![](./evaluation/figures/agePredictionPerSite.png)
-
-## Regional importance comparison
-
-![](./evaluation/figures/antsvfreesurfer_Importance.png)
-
-ANTs (left) vs. FreeSurfer (right)
-
-## Regional measurements
-
-![](./evaluation/figures/antsvfreesurfer_regionalPlots.png)
-
--->
-
-# Current work and Advanced Normalization Tools in R (ANTsR)
-
-## Multimodal Brain Tumor Segmentation (BRATS 2013)
-
-![](./competitions/figures/brats2013results1.png)
-
-[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
-supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)
-
-## White matter hyperintensities in TBI
-
-![](./wmhs/figures/wmhPipeline.png)
-
-## Social behavior and immunity dysfunction in mice
-
-![](./antsr/figures/filiano_rsfmri.png)
-
-<!--
-
-## Other ANTsR work
-
-* [Pediatric template of brain perfusion](http://www.nature.com/articles/sdata20153)
-
-* [Automated segmentation of chronic stroke lesions using LINDA: Lesion identification with neighborhood data analysis](http://www.ncbi.nlm.nih.gov/pubmed/26756101)
-
-* [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/25448483)
-
-* Corrective learning for segmentation refinement
-
--->
+while users are blind to what we provide!

### 2017-04-24 ibm.tex
ENH:  ASNR 2017

--- 2016-07-18 ibm.tex
@@
 \newif\ifbibliography
-\usepackage{longtable,booktabs}
-\usepackage{caption}
-% These lines are needed to make table captions work with longtable:
-\makeatletter
-\def\fnum@table{\tablename~\thetable}
-\makeatother
 \usepackage{graphicx,grffile}
@@
 
-\section{Developers and
-collaborators}\label{developers-and-collaborators}
+\section{Background}\label{background}
 
-\includegraphics{./figures/brian_and_nick.png}
+\begin{frame}{Founding developers}
 
-\begin{frame}
-
-\includegraphics{./figures/antsCollaborators2.png}
+BBA \& NJT
 
@@
 
-\section{Why would you care?}\label{why-would-you-care}
+\begin{frame}{Long-term collaborators}
 
-\begin{frame}{Software for medical image analysis}
+\begin{figure}[htbp]
+\centering
+\includegraphics{./figures/antscollab.jpg}
+\caption{}
+\end{figure}
+
+\(+\) \href{http://neuro.debian.net/pkgs/ants.html}{neurodebian},
+\href{http://www.slicer.org/}{slicer},
+\href{https://github.com/BRAINSia/BRAINSTools}{brainsfit},
+\href{http://nipy.sourceforge.net/nipype/}{nipype},
+\href{http://www.itk.org}{itk} and more \ldots{}
+
+\end{frame}
+
+\begin{frame}{}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{./figures/lion.png}
+\caption{}
+\end{figure}
+
+a pride: common way of doing things
+
+\ldots{} in a competitive world \ldots{}
+
+\end{frame}
+
+\begin{frame}{Definitions}
 
@@
 \item
-  \href{http://fsl.fmrib.ox.ac.uk/fsldownloads/}{FSL}
+  Registration \(=\) estimate an ``optimal'' geometric mapping between
+  image pairs or image sets (e.g.~Affine)
 \item
-  \href{http://www.fil.ion.ucl.ac.uk/spm/software/}{SPM}
+  Similarity \(=\) a function relating one image to another, given a
+  transformation (e.g.~mutual information)
 \item
-  \href{http://www.fil.ion.ucl.ac.uk/spm/software/}{FreeSurfer}
+  Diffeomorphisms \(=\) differentiable map with differentiable inverse
+  (e.g. ``silly putty'', viscous fluid)
 \item
-  \href{http://mipav.cit.nih.gov}{MIPAV}
+  {Segmentation \(=\) labeling tissue or anatomy in images, usually
+  automated (e.g.~K-means)}
 \item
-  \href{https://afni.nimh.nih.gov/afni}{AFNI}
+  Multivariate \(=\) using many voxels or measurements at once
+  (e.g.~PCA, \(p >> n\) ridge regression)
 \item
-  Slicer, Elastix, SimpleITK, ANTs \(\longleftrightarrow\)
-  \href{http://www.itk.org}{Insight Toolkit}
+  {Multiple modality \(=\) using many modalities at once (e.g.~DTI and
+  T1 and BOLD)}
 \item
-  Many more at \href{http://idoimaging.com}{idoimaging.com}
+  MALF: multi-atlas label fusion - using anatomical dictionaries to
+  label new data
+\item
+  {Solutions to challenging statistical image processing problems
+  usually need elements from each of the above}
 \end{itemize}
@@
 
-\begin{frame}{International competitions}
+\begin{frame}{Image mapping \& perception: 1878}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{./figures/galton.png}
+\caption{}
+\end{figure}
 
@@
 \item
-  \href{http://www.ncbi.nlm.nih.gov/pubmed/19195496}{Klein 2009}: MRI
-  brain registration
+  Francis Galton: Can we see criminality in the face?
 \item
-  \href{http://empire10.isi.uu.nl}{EMPIRE 2010}: CT lung registration
-\item
-  \href{https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page}{Multi-Atlas
-  Label Challenge 2012}: MRI brain registration and segmentation
-\item
-  \href{https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events}{SATA
-  Challenge 2013}: MRI cardiac and canine hind leg registration
-\item
-  \href{http://martinos.org/qtim/miccai2013/}{BRATS 2013}: Multi-modal
-  MRI brain segmentation
-\item
-  \href{http://www.cardiacatlas.org/web/stacom2014/moco-introduction}{STACOM
-  2014 MoCo Challenge}: MRI cardiac motion estimation
+  (maybe he should have used \emph{ANTs}?)
 \end{itemize}
@@
 
-\section{Major ANTs utilities}\label{major-ants-utilities}
+\begin{frame}{Image mapping \& biology: 1917}
 
-\begin{frame}{Donoho?}
+\begin{figure}[htbp]
+\centering
+\includegraphics{./figures/dthompson.png}
+\caption{}
+\end{figure}
 
- \emph{``Papers are just advertisements for the science.''}
+D'Arcy Thompson
 
@@
 
-\begin{frame}{Beyond original SyN}
+\begin{frame}{Initial scope}
 
-\small
+\begin{figure}[htbp]
+\centering
+\includegraphics{./figures/ants_initial_scope.png}
+\caption{}
+\end{figure}
 
-\includegraphics{./papers/figures/Frontiers_ITK.png}
-
-\includegraphics{./papers/figures/Frontiers_BSplineSyN.png}
+\ldots{} just do a better registration (tell story) \ldots{}
 
@@
 
-\begin{frame}{Template building: creating the average Joe}
+\begin{frame}{\emph{ANTs} Lineage}
 
-\includegraphics{./papers/figures/template0.jpg}
+\begin{figure}[htbp]
+\centering
+\includegraphics{./figures/lineage.jpg}
+\caption{}
+\end{figure}
+
+References: Horn and Schunck (1981), Gee, Reivich, and Bajcsy (1993),
+Grenander (1993), Thompson et al. (2001), Miller, Trouve, and Younes
+(2002), Shen and Davatzikos (2002), Arnold (2014), Thirion (1998),
+Rueckert et al. (1999), Fischl (2012), Ashburner (2012)
 
@@
 
-\begin{frame}{``Attractiveness'' \(\rightarrow\) mental processing?}
+\begin{frame}{Diffeomorphisms}
 
-\includegraphics{./papers/figures/template1.jpg}
+plausible physical modeling of large, invertible deformations
+
+``differentiable map with differentiable inverse''
 
@@
 
-\begin{frame}{What about brains?}
+\begin{frame}{Fine-grained and flexible maps}
 
-\includegraphics{./papers/figures/template3.jpg}
+\begin{figure}[htbp]
+\centering
+\includegraphics{./figures/highresdiffeos.jpg}
+\caption{}
+\end{figure}
+
+\ldots{} to correct a misconception about diffeomorphisms \ldots{}
 
@@
 
-\begin{frame}{Templates facilitate computation}
+\begin{frame}{Diffeomorphisms: image parameterization in a metric space}
 
-\includegraphics{./papers/figures/template4.jpg}
+\begin{figure}[htbp]
+\centering
+\includegraphics{./figures/shape_appearance.png}
+\caption{}
+\end{figure}
 
@@
 
-\begin{frame}{Nonparametric nonuniform intensity normalization (N3)}
+\begin{frame}[fragile]{General purpose library for multivariate image
+registration, segmentation \& statistical analysis tools}
 
@@
 \item
-  Developed at the Montreal Neurological Institute (John Sled, 1998)
+  170,000+ lines of C++, 6\(+\) years of work, 15+ collaborators.
 \item
-  Part of the standard preprocessing protocol in large scale projects
-  such as ADNI
+  Generic mathematical methods that are tunable for application specific
+  domains: no-free lunch
 \item
-  The traditional de facto standard in MRI bias correction
+  Deep testing on multiple platforms \ldots{} osx, linux, windows.
+\item
+  Several ``wins'' in public knock-abouts (
+  \href{http://www.ncbi.nlm.nih.gov/pubmed/19195496}{Klein 2009},
+  \href{http://www.ncbi.nlm.nih.gov/pubmed/21632295}{Murphy 2011},
+  \href{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3837555/}{SATA 2012
+  and 2013},
+  \href{http://martinos.org/qtim/miccai2013/proc_brats_2013.pdf}{BRATS
+  2013}, others )
+\end{itemize}
 
-  \begin{itemize}
-  \tightlist
-  \item
-    good performance
-  \item
-    \emph{public availability}
-  \end{itemize}
-\item
-  Public availability --- set of perl scripts coordinating various C++
-  programs
-\item
-  ``\emph{Let's incorporate N3 into ANTs!}''
-\end{itemize}
+\begin{verbatim}
+    An algorithm must use prior knowledge about a problem
+    to do well on that problem
+\end{verbatim}
 
@@
 
-\begin{frame}[fragile]{N4 (``Nick's N3'')}
+\begin{frame}{\emph{ANTs}: Beyond Registration}
 
-\begin{itemize}
-\item
-  comparative
-  \href{http://www.ncbi.nlm.nih.gov/pubmed/20378467}{evaluation}
-\item
-  small spline distances (useful for higher magnet strengths)
-\item
-  multiresolution
-\item
-  weighted regional mask (used in
-  \href{https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh}{\texttt{antsAtroposN4.sh}})
-\item
-  fast execution times
-\item
-  \emph{publicly available}
-\item
-  tested nightly within the ITK dashboard system
-\end{itemize}
+\begin{figure}[htbp]
+\centering
+\includegraphics{./figures/antscapabilities.jpg}
+\caption{}
+\end{figure}
+
+\href{http://www.ncbi.nlm.nih.gov/pubmed/?term=atropos+tustison}{Atropos}
+segmentation,
+\href{http://www.ncbi.nlm.nih.gov/pubmed/?term=N4+tustison}{N4
+inhomogeneity correction},
+\href{http://www.ncbi.nlm.nih.gov/pubmed/?term=eigenanatomy+avants}{Eigenanatomy},
+\href{http://www.ncbi.nlm.nih.gov/pubmed/?term=sparse+canonical+avants}{SCCAN},
+\href{http://www.ncbi.nlm.nih.gov/pubmed/24852460}{Prior-constrained
+PCA}, and
+\href{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4009425/}{atlas-based
+label fusion} and
+\href{http://www.ncbi.nlm.nih.gov/pubmed/21237273}{MALF} (powerful
+expert systems for segmentation)
 
@@
 
-\begin{frame}{Multi-atlas segmentation}
+\begin{frame}{On documentation}
 
-\includegraphics{./tools/jointfusion/figures/jointLabelFusion.png}
+\begin{figure}[htbp]
+\centering
+\includegraphics{figures/Chainsaw.jpg}
+\caption{}
+\end{figure}
+
+documentation is important
 
@@
 
-\begin{frame}{New work: joint intensity fusion}
+\begin{frame}{On documentation}
 
-\includegraphics{./tools/jointfusion/figures/jointIntensityFusion.png}
+\begin{figure}[htbp]
+\centering
+\includegraphics{figures/blindmen.jpg}
+\caption{}
+\end{figure}
 
-\end{frame}
+\ldots{} developers can be blind to doc deficiencies
 
-\begin{frame}{Possible uses}
-
-\begin{itemize}
-\item
-  ``Correct'' images
-
-  \begin{itemize}
-  \item
-    motion correction
-  \item
-    ``remove'' lesions
-  \end{itemize}
-\item
-  Project atlas set intensity signature
-\item
-  Use in ``corrective learning''
-\end{itemize}
-
-\end{frame}
-
-\section{Putting it all together---the ANTs cortical thickness
-pipeline}\label{putting-it-all-togetherthe-ants-cortical-thickness-pipeline}
-
-\begin{frame}{Cortical thickness studies}
-
-\begin{longtable}[c]{@{}ll@{}}
-\toprule
-Column1 & Column2\tabularnewline
-\midrule
-\endhead
-Tetris-playing ability & chronic pancreatitis\tabularnewline
-Huntington's disease & obsessive-compulsive disorder\tabularnewline
-schizophrenia & ADHD\tabularnewline
-bipolar disorder & obesity\tabularnewline
-Alzheimer's disease & heritable depression\tabularnewline
-frontotemporal dementia & elderly depression\tabularnewline
-Parkinson's disease & age\tabularnewline
-Williams syndrome & gender\tabularnewline
-multiple sclerosis & handedness\tabularnewline
-autism & intelligence\tabularnewline
-migraines & athletic ability\tabularnewline
-chronic smoking & meditative practices\tabularnewline
-alcoholism & musical ability\tabularnewline
-cocaine addiction & tendency toward criminality\tabularnewline
-Tourette syndrome in children & childhood sexual abuse in female
-adolescents\tabularnewline
-scoliosis in female adolescents & traumatic brain injury\tabularnewline
-early-onset blindness & untreated male-to-female
-transsexuality\tabularnewline
-\bottomrule
-\end{longtable}
-
-\end{frame}
-
-\begin{frame}{The ANTs structural brain mapping workflow}
-
-\includegraphics{./evaluation/figures/pipeline.png}
-
-\end{frame}
-
-\begin{frame}{Template building}
-
-\emph{Tailor data to your specific cohort}
-
-\includegraphics{./evaluation/figures/templates.png}
-
-\end{frame}
-
-\begin{frame}{Template priors}
-
-\includegraphics{./evaluation/figures/templatePriors.png}
-
-\end{frame}
-
-\begin{frame}{Cortical thickness maps}
-
-\includegraphics{./evaluation/figures/corticalThicknessEstimation.png}
-
-In contrast to FreeSurfer which warps coupled surface meshes to segment
-the gray matter, \emph{ANTs} diffeomorphically registers the white
-matter to the combined gray/white matters while simultaneously
-estimating thickness.
-
-\end{frame}
-
-\begin{frame}
-
-\emph{But without ground truth, how does one evaluate the pipeline?}
-
-\end{frame}
-
-\begin{frame}{Predict age and gender}
-
-\(AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)\)
-
-\end{frame}
-
-\begin{frame}{Prediction from cortical thickness data}
-
-\includegraphics{./evaluation/figures/evaluation.png}
-
-\end{frame}
-
-\section{Current work and Advanced Normalization Tools in R
-(ANTsR)}\label{current-work-and-advanced-normalization-tools-in-r-antsr}
-
-\begin{frame}{Multimodal Brain Tumor Segmentation (BRATS 2013)}
-
-\includegraphics{./competitions/figures/brats2013results1.png}
-
-\href{http://www.ncbi.nlm.nih.gov/pubmed/25433513}{Tustison, et al.,
-Optimal symmetric multimodal templates and concatenated random forests
-for supervised brain tumor segmentation (simplified) with \emph{ANTsR},
-\emph{Neuroinformatics}.}
-
-\end{frame}
-
-\begin{frame}{White matter hyperintensities in TBI}
-
-\includegraphics{./wmhs/figures/wmhPipeline.png}
-
-\end{frame}
-
-\begin{frame}{Social behavior and immunity dysfunction in mice}
-
-\includegraphics{./antsr/figures/filiano_rsfmri.png}
+while users are blind to what we provide!
 
 \hypertarget{refs}{}
+\hypertarget{ref-Arnold2014}{}
+Arnold, Vladimir I. 2014. ``Topological Methods in Hydrodynamics.'' In
+\emph{Vladimir I. Arnold-Collected Works}, 433--54. Springer.
+\url{http://link.springer.com/chapter/10.1007/978-3-642-31031-7_42}.
+
+\hypertarget{ref-Ashburner2012}{}
+Ashburner, John. 2012. ``SPM: A History.'' \emph{Neuroimage} 62 (2).
+Wellcome Trust Centre for Neuroimaging, 12 Queen Square, London WC1N
+3BG, UK. john@fil.ion.ucl.ac.uk: 791--800.
+doi:\href{https://doi.org/10.1016/j.neuroimage.2011.10.025}{10.1016/j.neuroimage.2011.10.025}.
+
+\hypertarget{ref-Fischl2012}{}
+Fischl, Bruce. 2012. ``FreeSurfer.'' \emph{Neuroimage} 62 (2). Athinoula
+A Martinos Center, Dept. of Radiology, MGH, Harvard Medical School, MA
+fischl@nmr.mgh.harvard.edu, USA. fischl@nmr.mgh.harvard.edu: 774--81.
+doi:\href{https://doi.org/10.1016/j.neuroimage.2012.01.021}{10.1016/j.neuroimage.2012.01.021}.
+
+\hypertarget{ref-Gee1993}{}
+Gee, J. C., M. Reivich, and R. Bajcsy. 1993. ``Elastically Deforming 3D
+Atlas to Match Anatomical Brain Images.'' \emph{J Comput Assist Tomogr}
+17 (2). Department of Computer; Information Science, University of
+Pennsylvania, Philadelphia 19104.: 225--36.
+
+\hypertarget{ref-Grenander1993}{}
+Grenander, Ulf. 1993. \emph{General Pattern Theory-a Mathematical Study
+of Regular Structures}. Clarendon Press.
+
+\hypertarget{ref-Horn1981}{}
+Horn, Berthold K, and Brian G Schunck. 1981. ``Determining Optical
+Flow.'' In \emph{1981 Technical Symposium East}, 319--31. International
+Society for Optics; Photonics.
+\url{http://proceedings.spiedigitallibrary.org/proceeding.aspx?articleid=1231385}.
+
+\hypertarget{ref-Miller2002}{}
+Miller, Michael I., Alain Trouve, and Laurent Younes. 2002. ``On the
+Metrics and Euler-Lagrange Equations of Computational Anatomy.''
+\emph{Annu Rev Biomed Eng} 4. Center for Imaging Science, The Johns
+Hopkins University, Baltimore, Maryland 21218, USA. mim@cis.jhu.edu:
+375--405.
+doi:\href{https://doi.org/10.1146/annurev.bioeng.4.092101.125733}{10.1146/annurev.bioeng.4.092101.125733}.
+
+\hypertarget{ref-Rueckert1999}{}
+Rueckert, D., L. I. Sonoda, C. Hayes, D. L. Hill, M. O. Leach, and D. J.
+Hawkes. 1999. ``Nonrigid Registration Using Free-Form Deformations:
+Application to Breast MR Images.'' \emph{IEEE Trans Med Imaging} 18 (8).
+Division of Radiological Sciences; Medical Engineering, Guy's, King's,;
+St. Thomas' School of Medicine, King's College London, Guy's Hospital,
+London, UK. D.Rueckert@umds.ac.uk: 712--21.
+doi:\href{https://doi.org/10.1109/42.796284}{10.1109/42.796284}.
+
+\hypertarget{ref-Shen2002}{}
+Shen, Dinggang, and Christos Davatzikos. 2002. ``HAMMER: Hierarchical
+Attribute Matching Mechanism for Elastic Registration.'' \emph{IEEE
+Trans Med Imaging} 21 (11). Center for Biomedical Image Computing,
+Department of Radiology, The Johns Hopkins University School of
+Medicine, 601 N. Caroline Street, Baltimore, MD 21287, USA.
+dgshen@rad.upenn.edu: 1421--39.
+doi:\href{https://doi.org/10.1109/TMI.2002.803111}{10.1109/TMI.2002.803111}.
+
+\hypertarget{ref-Thirion1998}{}
+Thirion, J. P. 1998. ``Image Matching as a Diffusion Process: An Analogy
+with Maxwell's Demons.'' \emph{Med Image Anal} 2 (3). INRIA, Equipe
+Epidaure, Sophia-Antipolis, France. jean-philippe.thirion@inria.fr:
+243--60.
+
+\hypertarget{ref-Thompson2001}{}
+Thompson, Paul M., Michael S. Mega, Christine Vidal, Judith L. Rapoport,
+and Arthur W. Toga. 2001. ``Detecting Disease-Specific Patterns of Brain
+Structure Using Cortical Pattern Matching and a Population-Based
+Probabilistic Brain Atlas.'' \emph{Inf Process Med Imaging} 2082.
+Laboratory of Neuro Imaging, Division of Brain Mapping,; Alzheimer's
+Disease Center, Dept. of Neurology, UCLA School of Medicine, Los
+Angeles, CA, USA thompson@loni.ucla.edu.: 488--501.
+doi:\href{https://doi.org/10.1007/3-540-45729-1_52}{10.1007/3-540-45729-1\_52}.
 

### 2017-04-24 makePresentationASNR2017.R

@@ -1,0 +1,40 @@
+#!/usr/bin/env Rscript
+
+####################
+#
+#   July 19, 2016
+#
+#
+#
+#
+#####################
+
+library( ggplot2 )
+library( rmarkdown )
+
+srcDir <- "./"
+buildrmd <- 'asnr2017.Rmd'
+
+########   Morning    ##########
+
+# Retrospective
+
+rawrmds <- c( "format.Rmd",
+              "background/background3.Rmd",
+              "competitions/competitions.Rmd",
+              "evaluation/antsvfreesurfer2.Rmd",
+              "antsr/antsr.Rmd",
+              "finalSlide.Rmd"
+               )
+
+for ( x in 1:length(rawrmds) ) {
+  if ( x == 1 )
+    {
+    cmd<-paste( "cat ", rawrmds[x], " > ", buildrmd )
+    } else {
+      cmd<-paste( "cat ", rawrmds[x], " >> ", buildrmd )
+    }
+  system( cmd )
+  }
+
+render( buildrmd, clean = TRUE )

### 2017-04-24 makePresentationASNR2017.R
ENH:  More.

@@ -23,6 +23,7 @@ rawrmds <- c( "format.Rmd",
               "background/background3.Rmd",
               "competitions/competitions.Rmd",
               "evaluation/antsvfreesurfer2.Rmd",
+              "evaluation/antsvfreesurfer2_extra.Rmd",
               "antsr/antsr.Rmd",
               "finalSlide.Rmd"
                )

### 2018-02-15 antsr/antsr.Rmd
ENH:  Final commit.
ENH:  ASNR 2017
ENH:  Add Cohen presentation.

@@
-# Current work and Advanced Normalization Tools in R (ANTsR)
+# Advanced Normalization Tools in R (ANTsR)
 
@@
 
-![](./competitions/figures/brats2013results2.png)
+\begin{centering}
+
+\includegraphics[width=4.5in]{./competitions/figures/brats2013results1.png}
+
+\end{centering}
+
+\small
 
@@
 
-![](./antsr/figures/filiano_rsfmri.png)
+\begin{centering}
+
+\includegraphics[width=3in]{./antsr/figures/filiano_rsfmri.png}
+
+\end{centering}
 
@@
 
-* Corrective learning for segmentation refinement
+* [ANTsRNet](https://github.com/stnava/ANTsRNet): a growing collection of popular deep learning architectures

### 2018-02-15 cohen.Rmd
ENH:  Add Cohen presentation.

--- 2016-08-04 ants2015build.Rmd
@@
     slide_level: 2
+    fig_width: 6
+    fig_height: 4.5
+    fig_caption: false
 ---
 
-# Developers and collaborators
-
-##  Founders:  Brian and Nick
-
-![](./figures/brian_and_nick.png)
-
-<!--
-NOtes:
-* Worked together for almost 10 years
-* have learned tons
-* have written quite a bit of code together
--->
-
-----
-
-![](./figures/antsCollaborators2.png)
+---
+
+# What is ANTs?
+
+## NLM's The Visible Human Project and The Insight Toolkit
+
+\begin{center}
+
+\includegraphics[width=4.75in]{./figures/VisibleHumanProject_ITK.pdf}
+
+\end{center}
+
+## ANTs _began with a clinical research need._
+
+\begin{center}
+
+\includegraphics[width=4.75in]{./figures/ANTsEvolutionarySummary.pdf}
+
+\end{center}
+
+## Founding developers
+
+\begin{center}
+\includegraphics[width=4.75in]{./figures/brian_and_nick.png}
+\end{center}
+
+\begin{center}
+BBA \& NJT
+\end{center}
+
+## Collaborators
+
+\begin{center}
+
+\includegraphics[width=4.75in]{./figures/antsCollaborators2.png}
+
+\end{center}
 
@@
 
-<!--
-NOtes:
-* However, it is not just us
-* Other people have done quite a bit
-* and others who are not shown such as Arman
--->
-# ANTs lineage
-
-## Image mapping and perception: 1877
-
-Francis Galton: _Can we see criminality in the face?_
-
-![](./figures/galton.png)
-
-_What about syphilis, mental illness?_
-
-<!--
-Notes:
-* Use of "composite portraiture" and what he called "eugenics"
-* Can we see criminality, mental illness, syphilis, and others in facial features?
-* Despite the obvious prejudices driving his research, he was a pioneer.
--->
-
-<!--
-
-##
-
-![](./background/figures/FrancisGalton2.jpg)
--->
-
-<!--
-Notes:
-* Another example where he has manually categorized facial features and try to combine them
-* Did not find much---composite tends to blend away to normality.
--->
-
-##  Speaking of criminality...
-
-_Can we say anything about the U.S. Congress?_
-
-![](./background/figures/congressPersons.png)
-
-__Maybe they should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__
-
-<!--
-Notes:
--->
-
-##  Image mapping & biology:  1917
-
-D'Arcy Thompson: _Comparison of related forms_
-
-![](./figures/dthompson.png)
--->
-
-<!--
-Notes:
-* Book: On Growth and Form
-* Descriptive
-* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
--->
-
-## Image mapping & biology: Current
+## Advanced Normalization Tools
+
+\begin{center}
+
+\includegraphics[width=4.75in]{./tools/figures/coreANtsToolsNeuro.png}
+
+\end{center}
+
+## Advanced Normalization Tools $\rightarrow$ ``ITK-Lung''
+
+\begin{center}
+
+\includegraphics[width=4.75in]{./tools/figures/coreANtsToolsLung.png}
+
+\end{center}
+
+<!--
+
+# Competitions
+
+## Algorithmic fight club
+
+![](./competitions/figures/fightclub.jpg)
+
+-->
+
+## International competitions
+
+* [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496): MRI brain registration
+
+* [EMPIRE 2010](http://empire10.isi.uu.nl):  CT lung registration
+
+* [Multi-Atlas Label Challenge 2012](https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page):  MRI brain registration and segmentation
+
+* [SATA Challenge 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events): MRI cardiac and canine hind leg registration
+
+* [BRATS 2013](http://martinos.org/qtim/miccai2013/): Multi-modal MRI brain segmentation
+
+* [STACOM 2014 MoCo Challenge](http://www.cardiacatlas.org/web/stacom2014/moco-introduction):  MRI cardiac motion estimation
+
+<!--- ![](./evaluation/figures/evalhistory.png) -->
+
+<!--
+
+## Klein, NeuroImage 2009
+
+![](./competitions/figures/nihms-130679-f0001.jpg)
+
+* 14 algorithms
+* publicly available data
+* different labeling protocols
+* developers tune their own algorithms
+
+## Klein results
+
+![](./competitions/figures/KleinResults2009.png)
+
+## Take-away message
+
+_"One of the most significant findings of this study is that the relative performances of
+the registration methods under comparison appear to be little affected by the choice of
+subject population, labeling protocol, and type of overlap measure....  ART, SyN, IRTK, and
+SPM's DARTEL Toolbox gave the best results according to overlap and distance measures,
+with ART and SyN delivering the most consistently high accuracy across subjects and label sets."_
+
+## EMPIRE 2010
+
+![](./competitions/figures/EMPIRE10criteria.png)
+
+* Alignment of lung boundaries,
+
+* major fissures,
+
+* annotated landmark pairs, and
+
+* topology of displacement field.
+
+## EMPIRE 2010 results
+
+![](./competitions/figures/EMPIRE10Results.png)
+
+## Multi-atlas 2012
+
+![](./competitions/figures/NKI30_MALF.png)
+
+## Multi-atlas 2012 results
+
+![](./competitions/figures/MALF2012.png)
+
+## SATA 2013
+
+Three very different problem domains
+
+![](./competitions/figures/SATA_data.png)
+
+## BRATS 2013
+
+![](./competitions/figures/brats2013results1.png)
+
+## BRATS 2013 results
+
+![](./competitions/figures/brats2013results2.png)
+
+[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
+supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)
+
+## STACOM 2014
+
+![](./competitions/figures/image_gallery.jpg)
+
+-->
+
+<!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->
+
+<!--
+
+# Major ANTs utilities
+
+-->
+
+## Donoho?
+
+\centering
+
 <BR><BR>
-_Look where we are now!_
-<BR><BR>
-![](./background/figures/r16xr85.png)
-
-<!--
-## ANTs family tree
-
-![](./figures/lineage.jpg)
--->
-
-<!--
-References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
--->
-
-<!--
-## Initial scope
-
-![](./figures/ants_initial_scope.png)
--->
-
-<!--
-Notes:
-* Brian work with Murray Grossman
-* First registration paper
-  - WBIR submission
-  - FEM registraiton using B-spline basis functions.
-  - "yeah, that registration is not that good---Jim would not like it."
--->
-
-# Major ANTs utilities
-
-## Donoho?
-
-<BR><BR>
+
 _\`\`Papers are just advertisements for the science.\'\'_
@@
 * The variant most widely used
+
 -->
@@
 
+-->
+
+<!--
+
 ## Beyond original SyN
@@
 ![](./papers/figures/Frontiers_BSplineSyN.png)
+
+-->
 
@@
 <BR><BR>
+
+\scriptsize
 
@@
           the current linear stage transform is directly intialized from the previous
-          stage's linear transform; this allows multiple linear stages to be run where
+          stage\'s linear transform; this allows multiple linear stages to be run where
           each stage directly updates the estimated linear transform from the previous
@@
 
+<!--
 ## Template building:  creating the average Joe
@@
 
+<!--
+
 ## Nonparametric nonuniform intensity normalization (N3)
@@
 ![](./tools/atropos/figures/atropos.png)
+
+-->
 
@@
 
+<!--
 ## Atropos + N4 $\rightarrow$ `antsAtroposN4.sh`
@@
 ![](./tools/figures/denoising.png)
+
+-->
+
+<!--
+
+##
 
@@
 ```
-
+-->
+
+<!-- 
 ## Multi-atlas segmentation
@@
 
+-->
+
+<!--
 ## Possible uses
@@
 
+\scriptsize
+
 ```{r, results='asis', echo = FALSE}
@@
 
-![](./evaluation/figures/templates.png)
-
-<!--
+\begin{centering}
+
+\includegraphics[width=3in]{./evaluation/figures/templates.png}
+
+\end{centering}
+
+\small
+
 * Templates representing the average mean shape and intensity are built directly from the cohort to be analyzed, e.g. pediatric vs. middle-aged brains.  
 * Acquisition and anonymization (e.g. defacing) protocols are often different.
--->
 
@@
 
-![](./evaluation/figures/templatePriors.png)
-
-<!--
+\begin{centering}
+
+\includegraphics[width=2.5in]{./evaluation/figures/templatePriors.png}
+
+\end{centering}
+
+\small
+
 Each template is [processed](https://github.com/ntustison/antsCookTemplatePriorsExample)
 to produce auxiliary images which are used for brain extraction and brain segmentation.
--->
-
-<!--
 
@@
 
-![](./evaluation/figures/antsvfreesurfer_Importance.png)
-
+\begin{centering}
+
+\small
 ANTs (left) vs. FreeSurfer (right)
 
+\includegraphics[width=4in]{./evaluation/figures/antsvfreesurfer_Importance.png}
+
+\end{centering}
+
 ## Regional measurements
 
-![](./evaluation/figures/antsvfreesurfer_regionalPlots.png)
-
--->
+\begin{centering}
+
+\includegraphics[width=4in]{./evaluation/figures/antsvfreesurfer_regionalPlots.png}
+
+\end{centering}
+
+<!--
 
@@
 
-<!--
 ##  What about using both the T1 & T2?
--->
 
@@
 
-<!--
-
 ## Arno-thick-in-the-head (ATITH)
@@
 
--->
-
-<!--
 ----
@@
 
-# Joint label/intensity fusion
-
-## Multi-atlas labeling
-
-![](./competitions/figures/NKI30_MALF.png)
-
-## Multi-atlas segmentation
-
-![](./tools/jointfusion/figures/jointLabelFusion.png)
-
-## Multi-atlas 2012 results
-
-![](./competitions/figures/MALF2012.png)
-
-## New work:  joint intensity fusion
-
-![](./tools/jointfusion/figures/jointIntensityFusion.png)
-
-<!--
-
-## Possible uses
-
-* ``Correct'' images
-    * motion correction
-    * lesions
-* Project atlas set intensity signature
--->
+# Advanced Normalization Tools in R (ANTsR)
+
+## Multimodal Brain Tumor Segmentation (BRATS 2013)
+
+\begin{centering}
+
+\includegraphics[width=4.5in]{./competitions/figures/brats2013results1.png}
+
+\end{centering}
+
+\small
+
+[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
+supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)
+
+## White matter hyperintensities in TBI
+
+\begin{centering}
+
+\includegraphics[width=4.5in]{./wmhs/figures/wmhPipeline.png}
+
+\end{centering}
+
+## Social behavior and immunity dysfunction in mice
+
+\begin{centering}
+
+\includegraphics[width=3in]{./antsr/figures/filiano_rsfmri.png}
+
+\end{centering}
+
+## Other ANTsR work
+
+* [Pediatric template of brain perfusion](http://www.nature.com/articles/sdata20153)
+
+* [Automated segmentation of chronic stroke lesions using LINDA: Lesion identification with neighborhood data analysis](http://www.ncbi.nlm.nih.gov/pubmed/26756101)
+
+* [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/25448483)
+
+* [ANTsRNet](https://github.com/stnava/ANTsRNet): a growing collection of popular deep learning architectures
+
+----
+
+## Open source
+
+* https://github.com/stnava/ANTs
+
+* https://github.com/stnava/ANTsR
+
+* https://github.com/stnava/ANTsRNet

### 2018-02-15 cohen.tex
ENH:  Add Cohen presentation.

\documentclass[ignorenonframetext,]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usetheme[]{AnnArbor}
\usecolortheme{dolphin}
\usefonttheme{professionalfonts}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\newif\ifbibliography
\hypersetup{
            pdftitle={Quantitative neuroimaging with ANTs},
            pdfauthor={Nick Tustison},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\usepackage{longtable,booktabs}
\usepackage{caption}
% These lines are needed to make table captions work with longtable:
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight0.8\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

% Prevent slide breaks in the middle of a paragraph:
\widowpenalties 1 10000
\raggedbottom

\AtBeginPart{
  \let\insertpartnumber\relax
  \let\partname\relax
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \let\insertsectionnumber\relax
    \let\sectionname\relax
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \let\insertsubsectionnumber\relax
  \let\subsectionname\relax
  \frame{\subsectionpage}
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% \pgfdeclareimage[width=1cm]{logo}{./figures/monkeyTypewriter.png}
%\logo{\pgfuseimage{logo}}

\institute{University of Virginia}
\definecolor{links}{RGB}{42, 27, 129}
\definecolor{mypink2}{RGB}{219, 48, 122}
%\hypersetup{colorlinks,linkcolor=links,urlcolor=mypink2}
\usefonttheme{professionalfonts}

% \setbeamerfont{note page}{family*=pplx,size=\footnotesize} % Palatino for notes

\setbeamerfont{subtitle}{size=\small}

\definecolor{uvablue}{RGB}{0,85,150}
\definecolor{uvalibraryorange}{RGB}{252,175,23}
\definecolor{uvacream}{RGB}{241,229,199}
\definecolor{uvalightblue}{RGB}{163,220,230}

\setbeamercolor{block body}{bg=green,fg=green}
\setbeamercolor{block body alerted}{bg=green,fg=green}
\setbeamercolor{block body example}{bg=green,fg=green}

\setbeamercolor{caption name}{fg=uvablue}

\setbeamercolor{headline}{fg=uvacream,bg=uvacream}
\setbeamercolor{section}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{frametitle}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{palette primary}{bg=uvalibraryorange,fg=uvablue}
\setbeamercolor{palette secondary}{bg=uvablue,fg=uvablue}
\setbeamercolor{palette tertiary}{bg=uvalibraryorange,fg=uvablue}
\setbeamercolor{palette quarternary}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{palette sidebar primary}{bg=uvalibraryorange,fg=uvablue}
\setbeamercolor{palette sidebar secondary}{fg=uvablue,bg=uvablue}
\setbeamercolor{palette sidebar tertiary}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{palette sidebar quarternary}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{structure}{bg=uvablue}

\useinnertheme{rectangles}

\titlegraphic{\vspace{-7.5mm}\includegraphics[width=0.45\paperwidth]{./figures/monkeyTypewriter.png}}

\title{Quantitative neuroimaging with ANTs}
\author{Nick Tustison}
\date{}

\begin{document}
\frame{\titlepage}

\begin{frame}

\end{frame}

\section{What is ANTs?}\label{what-is-ants}

\begin{frame}{NLM's The Visible Human Project and The Insight Toolkit}

\begin{center}

\includegraphics[width=4.75in]{./figures/VisibleHumanProject_ITK.pdf}

\end{center}

\end{frame}

\begin{frame}{ANTs \emph{began with a clinical research need.}}

\begin{center}

\includegraphics[width=4.75in]{./figures/ANTsEvolutionarySummary.pdf}

\end{center}

\end{frame}

\begin{frame}{Founding developers}

\begin{center}
\includegraphics[width=4.75in]{./figures/brian_and_nick.png}
\end{center}

\begin{center}
BBA \& NJT
\end{center}

\end{frame}

\begin{frame}{Collaborators}

\begin{center}

\includegraphics[width=4.75in]{./figures/antsCollaborators2.png}

\end{center}

\(+\) \href{http://neuro.debian.net/pkgs/ants.html}{neurodebian},
\href{http://www.slicer.org/}{slicer},
\href{https://github.com/BRAINSia/BRAINSTools}{brainsfit},
\href{http://nipy.sourceforge.net/nipype/}{nipype},
\href{http://www.itk.org}{itk} and more \ldots{}

\end{frame}

\begin{frame}{Advanced Normalization Tools}

\begin{center}

\includegraphics[width=4.75in]{./tools/figures/coreANtsToolsNeuro.png}

\end{center}

\end{frame}

\begin{frame}{Advanced Normalization Tools \(\rightarrow\) ``ITK-Lung''}

\begin{center}

\includegraphics[width=4.75in]{./tools/figures/coreANtsToolsLung.png}

\end{center}

\end{frame}

\begin{frame}{International competitions}

\begin{itemize}
\item
  \href{http://www.ncbi.nlm.nih.gov/pubmed/19195496}{Klein 2009}: MRI
  brain registration
\item
  \href{http://empire10.isi.uu.nl}{EMPIRE 2010}: CT lung registration
\item
  \href{https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page}{Multi-Atlas
  Label Challenge 2012}: MRI brain registration and segmentation
\item
  \href{https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events}{SATA
  Challenge 2013}: MRI cardiac and canine hind leg registration
\item
  \href{http://martinos.org/qtim/miccai2013/}{BRATS 2013}: Multi-modal
  MRI brain segmentation
\item
  \href{http://www.cardiacatlas.org/web/stacom2014/moco-introduction}{STACOM
  2014 MoCo Challenge}: MRI cardiac motion estimation
\end{itemize}

\end{frame}

\begin{frame}{Donoho?}

\centering

\emph{``Papers are just advertisements for the science.''}

\end{frame}

\begin{frame}[fragile]{\texttt{antsRegistration}}

\scriptsize

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\ExtensionTok{antsRegistration}\NormalTok{ --help}

\ExtensionTok{COMMAND}\NormalTok{:}
     \ExtensionTok{antsRegistration}
          \ExtensionTok{This}\NormalTok{ program is a user-level registration application meant to utilize}
          \ExtensionTok{ITKv4-only}\NormalTok{ classes. The user can specify any number of }\StringTok{"stages"}\NormalTok{ where a stage}
          \ExtensionTok{consists}\NormalTok{ of a transform}\KeywordTok{;} \ExtensionTok{an}\NormalTok{ image metric}\KeywordTok{;} \ExtensionTok{and}\NormalTok{ iterations, shrink factors, and}
          \ExtensionTok{smoothing}\NormalTok{ sigmas for each level.Note that dimensionality, metric, transform,}
          \ExtensionTok{output}\NormalTok{, convergence, shrink-factors and smoothing-sigmas parameters are}
          \ExtensionTok{mandatory.}

\ExtensionTok{OPTIONS}\NormalTok{:}
     \ExtensionTok{--version}
          \ExtensionTok{Get}\NormalTok{ Version Information.}

     \ExtensionTok{-d}\NormalTok{, --dimensionality 2/3}
          \ExtensionTok{This}\NormalTok{ option forces the image to be treated as a specified-dimensional image. If}
          \ExtensionTok{not}\NormalTok{ specified, we try to infer the dimensionality from the input image.}

     \ExtensionTok{-o}\NormalTok{, --output outputTransformPrefix}
\NormalTok{                  [}\ExtensionTok{outputTransformPrefix}\NormalTok{,}\OperatorTok{<}\NormalTok{outputWarpedImage}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{outputInverseWarpedImage}\OperatorTok{>}\NormalTok{]}
          \ExtensionTok{Specify}\NormalTok{ the output transform prefix (output format is .nii.gz )}\BuiltInTok{.} \ExtensionTok{Optionally}\NormalTok{, one}
          \ExtensionTok{can}\NormalTok{ choose to warp the moving image to the fixed space and, if the inverse}
          \ExtensionTok{transform}\NormalTok{ exists, one can also output the warped fixed image. Note that only the}
          \ExtensionTok{images}\NormalTok{ specified in the first metric call are warped. Use antsApplyTransforms to}
          \ExtensionTok{warp}\NormalTok{ other images using the resultant transform(s)}\ExtensionTok{.}

     \ExtensionTok{-j}\NormalTok{, --save-state saveSateAsTransform}
          \ExtensionTok{Specify}\NormalTok{ the output file for the current state of the registration. The state}
          \FunctionTok{file}\NormalTok{ is written to an hdf5 composite file. It is specially usefull if we want to}
          \ExtensionTok{save}\NormalTok{ the current state of a SyN registration to the disk, so we can load and}
          \ExtensionTok{restore}\NormalTok{ that later to continue the next registration process directly started}
          \ExtensionTok{from}\NormalTok{ the last saved state. The output file of this flag is the same as the}
          \ExtensionTok{write-composite-transform}\NormalTok{, unless the last transform is a SyN transform. In that}
          \KeywordTok{case}\NormalTok{, the inverse displacement field of the SyN transform is also added to the}
\NormalTok{          output composite transform. Again notice that this file cannot be treated as a}
\NormalTok{          transform, and restore-state option must be used to load the written file by}
\NormalTok{          this flag.}

\NormalTok{     -k, --restore-state restoreStateAsATransform}
\NormalTok{          Specify the initial state of the registration which get immediately used to}
\NormalTok{          directly initialize the registration process. The flag is mutually exclusive}
\NormalTok{          with other intialization flags.If this flag is used, none of the}
\NormalTok{          initial-moving-transform and initial-fixed-transform cannot be used.}

\NormalTok{     -a, --write-composite-transform 1/(0)}
\NormalTok{          Boolean specifying whether or not the composite transform (and its inverse, if}
\NormalTok{          it exists) should be written to an hdf5 composite file. This is false by default}
\NormalTok{          so that only the transform for each stage is written to file.}
\NormalTok{          <VALUES>: 0}

\NormalTok{     -p, --print-similarity-measure-interval <unsignedIntegerValue>}
\NormalTok{          Prints out the CC similarity metric measure between the full-size input fixed}
\NormalTok{          and the transformed moving images at each iteration a value of 0 (the default)}
\NormalTok{          indicates that the full scale computation should not take placeany value greater}
\NormalTok{          than 0 represents the interval of full scale metric computation.}
\NormalTok{          <VALUES>: 0}

\NormalTok{     -v, --write-interval-volumes <unsignedIntegerValue>}
\NormalTok{          Writes out the output volume at each iteration. It helps to present the}
\NormalTok{          registration process as a short movie a value of 0 (the default) indicates that}
\NormalTok{          this option should not take placeany value greater than 0 represents the}
\NormalTok{          interval between the iterations which outputs are written to the disk.}
\NormalTok{          <VALUES>: 0}

\NormalTok{     -z, --collapse-output-transforms (1)/0}
\NormalTok{          Collapse output transforms. Specifically, enabling this option combines all}
\NormalTok{          adjacent transforms wherepossible. All adjacent linear transforms are written to}
\NormalTok{          disk}\KeywordTok{ in}\NormalTok{ the forman itk affine transform }\KeywordTok{(}\NormalTok{called xxxGenericAffine.mat}\KeywordTok{)}\ExtensionTok{.}
          \ExtensionTok{Similarly}\NormalTok{, all adjacent displacement field transforms are combined when written}
          \ExtensionTok{to}\NormalTok{ disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available))}\ExtensionTok{.Also}\NormalTok{, an}
          \ExtensionTok{output}\NormalTok{ composite transform including the collapsed transforms is written to the}
          \ExtensionTok{disk}\NormalTok{ (called outputCollapsed(Inverse)}\ExtensionTok{Composite}\NormalTok{)}\ExtensionTok{.}
          \OperatorTok{<}\ExtensionTok{VALUES}\OperatorTok{>}\NormalTok{: 1}

     \ExtensionTok{-i}\NormalTok{, --initialize-transforms-per-stage (1)}\ExtensionTok{/0}
          \ExtensionTok{Initialize}\NormalTok{ linear transforms from the previous stage. By enabling this option,}
          \ExtensionTok{the}\NormalTok{ current linear stage transform is directly intialized from the previous}
          \ExtensionTok{stage}\DataTypeTok{\textbackslash{}'}\NormalTok{s linear transform}\KeywordTok{;} \ExtensionTok{this}\NormalTok{ allows multiple linear stages to be run where}
          \ExtensionTok{each}\NormalTok{ stage directly updates the estimated linear transform from the previous}
          \ExtensionTok{stage.}\NormalTok{ (e.g. Translation -}\OperatorTok{>}\NormalTok{ Rigid -}\OperatorTok{>}\NormalTok{ Affine)}\ExtensionTok{.}
          \OperatorTok{<}\ExtensionTok{VALUES}\OperatorTok{>}\NormalTok{: 0}

     \ExtensionTok{-n}\NormalTok{, --interpolation Linear}
                         \ExtensionTok{NearestNeighbor}
                         \ExtensionTok{MultiLabel}\NormalTok{[}\OperatorTok{<}\NormalTok{sigma=imageSpacing}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{alpha=4.}\OperatorTok{0>}\NormalTok{]}
                         \ExtensionTok{Gaussian}\NormalTok{[}\OperatorTok{<}\NormalTok{sigma=imageSpacing}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{alpha=1.}\OperatorTok{0>}\NormalTok{]}
                         \ExtensionTok{BSpline}\NormalTok{[}\OperatorTok{<}\NormalTok{order=}\OperatorTok{3>}\NormalTok{]}
                         \ExtensionTok{CosineWindowedSinc}
                         \ExtensionTok{WelchWindowedSinc}
                         \ExtensionTok{HammingWindowedSinc}
                         \ExtensionTok{LanczosWindowedSinc}
          \ExtensionTok{Several}\NormalTok{ interpolation options are available in ITK. These have all been made}
          \ExtensionTok{available.}\NormalTok{ Currently the interpolator choice is only used to warp (and possibly}
          \ExtensionTok{inverse}\NormalTok{ warp) }\ExtensionTok{the}\NormalTok{ final output image(s)}\ExtensionTok{.}

     \ExtensionTok{-g}\NormalTok{, --restrict-deformation PxQxR}
          \ExtensionTok{This}\NormalTok{ option allows the user to restrict the optimization of the displacement}
          \ExtensionTok{field}\NormalTok{, translation, rigid or affine transform on a per-component basis. For}
          \ExtensionTok{example}\NormalTok{, if one wants to limit the deformation or rotation of 3-D volume to the}
          \ExtensionTok{first}\NormalTok{ two dimensions, this is possible by specifying a weight vector of }\StringTok{'1x1x0'}
          \KeywordTok{for} \ExtensionTok{a}\NormalTok{ deformation field or }\StringTok{'1x1x0x1x1x0'}\NormalTok{ for a rigid}
          \ExtensionTok{transformation.Low-dimensional}\NormalTok{ restriction only works if there are no preceding}
          \ExtensionTok{transformations.}

     \ExtensionTok{-q}\NormalTok{, --initial-fixed-transform initialTransform}
\NormalTok{                                   [}\ExtensionTok{initialTransform}\NormalTok{,}\OperatorTok{<}\NormalTok{useInverse}\OperatorTok{>}\NormalTok{]}
\NormalTok{                                   [}\ExtensionTok{fixedImage}\NormalTok{,movingImage,initializationFeature]}
          \ExtensionTok{Specify}\NormalTok{ the initial fixed transform(s) }\FunctionTok{which}\NormalTok{ get immediately incorporated into}
          \ExtensionTok{the}\NormalTok{ composite transform. The order of the transforms is stack-esque in that the}
          \FunctionTok{last}\NormalTok{ transform specified on the command line is the first to be applied. In}
          \ExtensionTok{addition}\NormalTok{ to initialization with ITK transforms, the user can perform an initial}
          \ExtensionTok{translation}\NormalTok{ alignment by specifying the fixed and moving images and selecting an}
          \ExtensionTok{initialization}\NormalTok{ feature. These features include using the geometric center of the}
          \ExtensionTok{images}\NormalTok{ (=0), }\ExtensionTok{the}\NormalTok{ image intensities (=1), }\ExtensionTok{or}\NormalTok{ the origin of the images (=2)}\ExtensionTok{.}

     \ExtensionTok{-r}\NormalTok{, --initial-moving-transform initialTransform}
\NormalTok{                                    [}\ExtensionTok{initialTransform}\NormalTok{,}\OperatorTok{<}\NormalTok{useInverse}\OperatorTok{>}\NormalTok{]}
\NormalTok{                                    [}\ExtensionTok{fixedImage}\NormalTok{,movingImage,initializationFeature]}
          \ExtensionTok{Specify}\NormalTok{ the initial moving transform(s) }\FunctionTok{which}\NormalTok{ get immediately incorporated into}
          \ExtensionTok{the}\NormalTok{ composite transform. The order of the transforms is stack-esque in that the}
          \FunctionTok{last}\NormalTok{ transform specified on the command line is the first to be applied. In}
          \ExtensionTok{addition}\NormalTok{ to initialization with ITK transforms, the user can perform an initial}
          \ExtensionTok{translation}\NormalTok{ alignment by specifying the fixed and moving images and selecting an}
          \ExtensionTok{initialization}\NormalTok{ feature. These features include using the geometric center of the}
          \ExtensionTok{images}\NormalTok{ (=0), }\ExtensionTok{the}\NormalTok{ image intensities (=1), }\ExtensionTok{or}\NormalTok{ the origin of the images (=2)}\ExtensionTok{.}

     \ExtensionTok{-m}\NormalTok{, --metric CC[fixedImage,movingImage,metricWeight,radius,}\OperatorTok{<}\NormalTok{samplingStrategy=}\DataTypeTok{\{None,Regular,Random\}}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{samplingPercentage=[0,1]}\OperatorTok{>}\NormalTok{]}
                  \ExtensionTok{MI}\NormalTok{[fixedImage,movingImage,metricWeight,numberOfBins,}\OperatorTok{<}\NormalTok{samplingStrategy=}\DataTypeTok{\{None,Regular,Random\}}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{samplingPercentage=[0,1]}\OperatorTok{>}\NormalTok{]}
                  \ExtensionTok{Mattes}\NormalTok{[fixedImage,movingImage,metricWeight,numberOfBins,}\OperatorTok{<}\NormalTok{samplingStrategy=}\DataTypeTok{\{None,Regular,Random\}}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{samplingPercentage=[0,1]}\OperatorTok{>}\NormalTok{]}
                  \ExtensionTok{MeanSquares}\NormalTok{[fixedImage,movingImage,metricWeight,radius=NA,}\OperatorTok{<}\NormalTok{samplingStrategy=}\DataTypeTok{\{None,Regular,Random\}}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{samplingPercentage=[0,1]}\OperatorTok{>}\NormalTok{]}
                  \ExtensionTok{Demons}\NormalTok{[fixedImage,movingImage,metricWeight,radius=NA,}\OperatorTok{<}\NormalTok{samplingStrategy=}\DataTypeTok{\{None,Regular,Random\}}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{samplingPercentage=[0,1]}\OperatorTok{>}\NormalTok{]}
                  \ExtensionTok{GC}\NormalTok{[fixedImage,movingImage,metricWeight,radius=NA,}\OperatorTok{<}\NormalTok{samplingStrategy=}\DataTypeTok{\{None,Regular,Random\}}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{samplingPercentage=[0,1]}\OperatorTok{>}\NormalTok{]}
                  \ExtensionTok{ICP}\NormalTok{[fixedPointSet,movingPointSet,metricWeight,}\OperatorTok{<}\NormalTok{samplingPercentage=[0,1]}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{boundaryPointsOnly=}\OperatorTok{0>}\NormalTok{]}
                  \ExtensionTok{PSE}\NormalTok{[fixedPointSet,movingPointSet,metricWeight,}\OperatorTok{<}\NormalTok{samplingPercentage=[0,1]}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{boundaryPointsOnly=}\OperatorTok{0>}\NormalTok{,}\OperatorTok{<}\NormalTok{pointSetSigma=}\OperatorTok{1>}\NormalTok{,}\OperatorTok{<}\NormalTok{kNeighborhood=}\OperatorTok{50>}\NormalTok{]}
                  \ExtensionTok{JHCT}\NormalTok{[fixedPointSet,movingPointSet,metricWeight,}\OperatorTok{<}\NormalTok{samplingPercentage=[0,1]}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{boundaryPointsOnly=}\OperatorTok{0>}\NormalTok{,}\OperatorTok{<}\NormalTok{pointSetSigma=}\OperatorTok{1>}\NormalTok{,}\OperatorTok{<}\NormalTok{kNeighborhood=}\OperatorTok{50>}\NormalTok{,}\OperatorTok{<}\NormalTok{alpha=1.}\OperatorTok{1>}\NormalTok{,}\OperatorTok{<}\NormalTok{useAnisotropicCovariances=}\OperatorTok{1>}\NormalTok{]}
                  \ExtensionTok{IGDM}\NormalTok{[fixedImage,movingImage,metricWeight,fixedMask,movingMask,}\OperatorTok{<}\NormalTok{neighborhoodRadius=0x0}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{intensitySigma=}\OperatorTok{0>}\NormalTok{,}\OperatorTok{<}\NormalTok{distanceSigma=}\OperatorTok{0>}\NormalTok{,}\OperatorTok{<}\NormalTok{kNeighborhood=}\OperatorTok{1>}\NormalTok{,}\OperatorTok{<}\NormalTok{gradientSigma=}\OperatorTok{1>}\NormalTok{]}
          \ExtensionTok{These}\NormalTok{ image metrics are available--- CC: ANTS neighborhood cross correlation,}
          \ExtensionTok{MI}\NormalTok{: Mutual information, Demons: (Thirion), }\ExtensionTok{MeanSquares}\NormalTok{, and GC: Global}
          \ExtensionTok{Correlation.}\NormalTok{ The }\StringTok{"metricWeight"}\NormalTok{ variable is used to modulate the per stage}
          \ExtensionTok{weighting}\NormalTok{ of the metrics. The metrics can also employ a sampling strategy}
          \ExtensionTok{defined}\NormalTok{ by a sampling percentage. The sampling strategy defaults to }\StringTok{'None'}\NormalTok{ (aka}
          \ExtensionTok{a}\NormalTok{ dense sampling of one sample per voxel), }\ExtensionTok{otherwise}\NormalTok{ it defines a point set over}
          \FunctionTok{which}\NormalTok{ to optimize the metric. The point set can be on a regular lattice or a}
          \ExtensionTok{random}\NormalTok{ lattice of points slightly perturbed to minimize aliasing artifacts.}
          \ExtensionTok{samplingPercentage}\NormalTok{ defines the fraction of points to select from the domain. In}
          \ExtensionTok{addition}\NormalTok{, three point set metrics are available: Euclidean (ICP), }\ExtensionTok{Point-set}
          \ExtensionTok{expectation}\NormalTok{ (PSE), }\ExtensionTok{and}\NormalTok{ Jensen-Havrda-Charvet-Tsallis (JHCT)}\ExtensionTok{.}

     \ExtensionTok{-t}\NormalTok{, --transform Rigid[gradientStep]}
                     \ExtensionTok{Affine}\NormalTok{[gradientStep]}
                     \ExtensionTok{CompositeAffine}\NormalTok{[gradientStep]}
                     \ExtensionTok{Similarity}\NormalTok{[gradientStep]}
                     \ExtensionTok{Translation}\NormalTok{[gradientStep]}
                     \ExtensionTok{BSpline}\NormalTok{[gradientStep,meshSizeAtBaseLevel]}
                     \ExtensionTok{GaussianDisplacementField}\NormalTok{[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]}
                     \ExtensionTok{BSplineDisplacementField}\NormalTok{[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,}\OperatorTok{<}\NormalTok{splineOrder=}\OperatorTok{3>}\NormalTok{]}
                     \ExtensionTok{TimeVaryingVelocityField}\NormalTok{[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]}
                     \ExtensionTok{TimeVaryingBSplineVelocityField}\NormalTok{[gradientStep,velocityFieldMeshSize,}\OperatorTok{<}\NormalTok{numberOfTimePointSamples=}\OperatorTok{4>}\NormalTok{,}\OperatorTok{<}\NormalTok{splineOrder=}\OperatorTok{3>}\NormalTok{]}
                     \ExtensionTok{SyN}\NormalTok{[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]}
                     \ExtensionTok{BSplineSyN}\NormalTok{[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,}\OperatorTok{<}\NormalTok{splineOrder=}\OperatorTok{3>}\NormalTok{]}
                     \ExtensionTok{Exponential}\NormalTok{[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,}\OperatorTok{<}\NormalTok{numberOfIntegrationSteps}\OperatorTok{>}\NormalTok{]}
                     \ExtensionTok{BSplineExponential}\NormalTok{[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,}\OperatorTok{<}\NormalTok{numberOfIntegrationSteps}\OperatorTok{>}\NormalTok{,}\OperatorTok{<}\NormalTok{splineOrder=}\OperatorTok{3>}\NormalTok{]}
          \ExtensionTok{Several}\NormalTok{ transform options are available. The gradientStep or learningRate}
          \ExtensionTok{characterizes}\NormalTok{ the gradient descent optimization and is scaled appropriately for}
          \ExtensionTok{each}\NormalTok{ transform using the shift scales estimator. Subsequent parameters are}
          \ExtensionTok{transform-specific}\NormalTok{ and can be determined from the usage. For the B-spline}
          \ExtensionTok{transforms}\NormalTok{ one can also specify the smoothing in terms of spline distance (i.e.}
          \ExtensionTok{knot}\NormalTok{ spacing)}\ExtensionTok{.}

     \ExtensionTok{-c}\NormalTok{, --convergence MxNxO}
\NormalTok{                       [}\ExtensionTok{MxNxO}\NormalTok{,}\OperatorTok{<}\NormalTok{convergenceThreshold=1e-}\OperatorTok{6>}\NormalTok{,}\OperatorTok{<}\NormalTok{convergenceWindowSize=}\OperatorTok{10>}\NormalTok{]}
          \ExtensionTok{Convergence}\NormalTok{ is determined from the number of iterations per level and is}
          \ExtensionTok{determined}\NormalTok{ by fitting a line to the normalized energy profile of the last N}
          \ExtensionTok{iterations}\NormalTok{ (where N is specified by the window size) }\ExtensionTok{and}\NormalTok{ determining the slope}
          \FunctionTok{which}\NormalTok{ is then compared with the convergence threshold.}

     \ExtensionTok{-s}\NormalTok{, --smoothing-sigmas MxNxO...}
          \ExtensionTok{Specify}\NormalTok{ the sigma of gaussian smoothing at each level. Units are given in terms}
          \ExtensionTok{of}\NormalTok{ voxels (}\StringTok{'vox'}\NormalTok{) }\ExtensionTok{or}\NormalTok{ physical spacing (}\StringTok{'mm'}\NormalTok{)}\BuiltInTok{.} \ExtensionTok{Example}\NormalTok{ usage is }\StringTok{'4x2x1mm'}\NormalTok{ and}
          \StringTok{'4x2x1vox'} \ExtensionTok{where}\NormalTok{ no units implies voxel spacing.}

     \ExtensionTok{-f}\NormalTok{, --shrink-factors MxNxO...}
          \ExtensionTok{Specify}\NormalTok{ the shrink factor for the virtual domain (typically the fixed image) }\ExtensionTok{at}
          \ExtensionTok{each}\NormalTok{ level.}

     \ExtensionTok{-u}\NormalTok{, --use-histogram-matching}
          \ExtensionTok{Histogram}\NormalTok{ match the images before registration.}

     \ExtensionTok{-l}\NormalTok{, --use-estimate-learning-rate-once}
          \ExtensionTok{turn}\NormalTok{ on the option that lets you estimate the learning rate step size only at}
          \ExtensionTok{the}\NormalTok{ beginning of each level. * useful as a second stage of fine-scale}
          \ExtensionTok{registration.}

     \ExtensionTok{-w}\NormalTok{, --winsorize-image-intensities [lowerQuantile,upperQuantile]}
          \ExtensionTok{Winsorize}\NormalTok{ data based on specified quantiles.}

     \ExtensionTok{-x}\NormalTok{, --masks [fixedImageMask,movingImageMask]}
          \ExtensionTok{Image}\NormalTok{ masks to limit voxels considered by the metric.}

     \ExtensionTok{--float}
          \ExtensionTok{Use} \StringTok{'float'}\NormalTok{ instead of }\StringTok{'double'}\NormalTok{ for computations.}
          \OperatorTok{<}\ExtensionTok{VALUES}\OperatorTok{>}\NormalTok{: 0}

     \ExtensionTok{-v}\NormalTok{, --verbose (0)}\ExtensionTok{/1}
          \ExtensionTok{Verbose}\NormalTok{ output.}

     \ExtensionTok{-h}
          \ExtensionTok{Print}\NormalTok{ the help menu (short version)}\ExtensionTok{.}

     \ExtensionTok{--help}
          \ExtensionTok{Print}\NormalTok{ the help menu. Will also print values used on the current command line}
          \ExtensionTok{call.}
\end{Highlighting}
\end{Shaded}

\end{frame}

\section{Putting it all together---the ANTs cortical thickness
pipeline}\label{putting-it-all-togetherthe-ants-cortical-thickness-pipeline}

\begin{frame}{Cortical thickness studies}

\scriptsize

\begin{longtable}[]{@{}ll@{}}
\toprule
Column1 & Column2\tabularnewline
\midrule
\endhead
Tetris-playing ability & chronic pancreatitis\tabularnewline
Huntington's disease & obsessive-compulsive disorder\tabularnewline
schizophrenia & ADHD\tabularnewline
bipolar disorder & obesity\tabularnewline
Alzheimer's disease & heritable depression\tabularnewline
frontotemporal dementia & elderly depression\tabularnewline
Parkinson's disease & age\tabularnewline
Williams syndrome & gender\tabularnewline
multiple sclerosis & handedness\tabularnewline
autism & intelligence\tabularnewline
migraines & athletic ability\tabularnewline
chronic smoking & meditative practices\tabularnewline
alcoholism & musical ability\tabularnewline
cocaine addiction & tendency toward criminality\tabularnewline
Tourette syndrome in children & childhood sexual abuse in female
adolescents\tabularnewline
scoliosis in female adolescents & traumatic brain injury\tabularnewline
early-onset blindness & untreated male-to-female
transsexuality\tabularnewline
\bottomrule
\end{longtable}

\end{frame}

\begin{frame}{The ANTs structural brain mapping workflow}

\begin{centering}

\includegraphics[width=4.5in]{./evaluation/figures/pipeline.png}

\end{centering}

\end{frame}

\begin{frame}{Template building}

\emph{Tailor data to your specific cohort}

\begin{centering}

\includegraphics[width=3in]{./evaluation/figures/templates.png}

\end{centering}

\small

\begin{itemize}
\tightlist
\item
  Templates representing the average mean shape and intensity are built
  directly from the cohort to be analyzed, e.g.~pediatric
  vs.~middle-aged brains.\\
\item
  Acquisition and anonymization (e.g.~defacing) protocols are often
  different.
\end{itemize}

\end{frame}

\begin{frame}{Template priors}

\begin{centering}

\includegraphics[width=2.5in]{./evaluation/figures/templatePriors.png}

\end{centering}

\small

Each template is
\href{https://github.com/ntustison/antsCookTemplatePriorsExample}{processed}
to produce auxiliary images which are used for brain extraction and
brain segmentation.

\end{frame}

\begin{frame}{Brain extraction comparison}

\begin{centering}

\includegraphics[width=3.5in]{./evaluation/figures/brainExtraction.png}

\end{centering}

\small

Comparison with de facto standard FreeSurfer package. Note the
difference in separation of the gray matter from the surrounding CSF. (0
failures out of 1205 scans)

\end{frame}

\begin{frame}[fragile]{Brain segmentation}

\begin{centering}

\includegraphics[width=3.5in]{./evaluation/figures/brainSegmentation.png}

\end{centering}

\small

Randomly selected healthy individuals. \texttt{Atropos} gets good
performance across ages.

\end{frame}

\begin{frame}{Cortical thickness maps}

\begin{centering}

\includegraphics[width=4in]{./evaluation/figures/corticalThicknessEstimation.png}

\end{centering}

\small

In contrast to FreeSurfer which warps coupled surface meshes to segment
the gray matter, \emph{ANTs} diffeomorphically registers the white
matter to the combined gray/white matters while simultaneously
estimating thickness.

\end{frame}

\begin{frame}

\begin{centering}

\Large

{\bf But without ground truth, how does one evaluate the pipeline?}

\end{centering}

\end{frame}

\begin{frame}{Predict age and gender}

\begin{centering}

$AGE \sim VOLUME + GENDER + \sum_{i=1}^{62} T(DKT_i)$

\end{centering}

\end{frame}

\begin{frame}{Prediction from cortical thickness data}

\begin{centering}

\includegraphics[width=4in]{./evaluation/figures/evaluation.png}

\end{centering}

\end{frame}

\begin{frame}{Regional importance comparison}

\begin{centering}

\small
ANTs (left) vs. FreeSurfer (right)

\includegraphics[width=4in]{./evaluation/figures/antsvfreesurfer_Importance.png}

\end{centering}

\end{frame}

\begin{frame}{Regional measurements}

\begin{centering}

\includegraphics[width=4in]{./evaluation/figures/antsvfreesurfer_regionalPlots.png}

\end{centering}

\end{frame}

\begin{frame}{Longitudinal processing}

\includegraphics{./longitudinal/figures/longitudinalPipeline.png}

\end{frame}

\section{Advanced Normalization Tools in R
(ANTsR)}\label{advanced-normalization-tools-in-r-antsr}

\begin{frame}{Multimodal Brain Tumor Segmentation (BRATS 2013)}

\begin{centering}

\includegraphics[width=4.5in]{./competitions/figures/brats2013results1.png}

\end{centering}

\small

\href{http://www.ncbi.nlm.nih.gov/pubmed/25433513}{Tustison, et al.,
Optimal symmetric multimodal templates and concatenated random forests
for supervised brain tumor segmentation (simplified) with \emph{ANTsR},
\emph{Neuroinformatics}.}

\end{frame}

\begin{frame}{White matter hyperintensities in TBI}

\begin{centering}

\includegraphics[width=4.5in]{./wmhs/figures/wmhPipeline.png}

\end{centering}

\end{frame}

\begin{frame}{Social behavior and immunity dysfunction in mice}

\begin{centering}

\includegraphics[width=3in]{./antsr/figures/filiano_rsfmri.png}

\end{centering}

\end{frame}

\begin{frame}{Other ANTsR work}

\begin{itemize}
\item
  \href{http://www.nature.com/articles/sdata20153}{Pediatric template of
  brain perfusion}
\item
  \href{http://www.ncbi.nlm.nih.gov/pubmed/26756101}{Automated
  segmentation of chronic stroke lesions using LINDA: Lesion
  identification with neighborhood data analysis}
\item
  \href{http://www.ncbi.nlm.nih.gov/pubmed/25448483}{Eigenanatomy}
\item
  \href{https://github.com/stnava/ANTsRNet}{ANTsRNet}: a growing
  collection of popular deep learning architectures
\end{itemize}

\end{frame}

\begin{frame}{Open source}

\begin{itemize}
\item
  \url{https://github.com/stnava/ANTs}
\item
  \url{https://github.com/stnava/ANTsR}
\item
  \url{https://github.com/stnava/ANTsRNet}
\end{itemize}

\end{frame}

\end{document}

### 2018-02-15 cohen2018.Rmd
ENH:  Add Cohen presentation.

--- 2018-02-15 cohen.Rmd
@@
 \end{center}
-
-## Founding developers
-
-\begin{center}
-\includegraphics[width=4.75in]{./figures/brian_and_nick.png}
-\end{center}
-
-\begin{center}
-BBA \& NJT
-\end{center}
-
-## Collaborators
-
-\begin{center}
-
-\includegraphics[width=4.75in]{./figures/antsCollaborators2.png}
-
-\end{center}
-
-$+$ [neurodebian](http://neuro.debian.net/pkgs/ants.html), [slicer](http://www.slicer.org/), [brainsfit](https://github.com/BRAINSia/BRAINSTools), [nipype](http://nipy.sourceforge.net/nipype/), [itk](http://www.itk.org) and more ...
 
@@
 <!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->
-
-<!--
-
-# Major ANTs utilities
-
--->
-
-## Donoho?
-
-\centering
-
-<BR><BR>
-
-_\`\`Papers are just advertisements for the science.\'\'_
-<BR>
-
-<!--
-
-## Neuro tools
-
-![](./tools/figures/coreANtsToolsNeuro.png)
-
-## Pulmonary tools
-
-![](./tools/figures/coreANtsToolsLung.png)
-
-## Symmetric Normalization (SyN)
-
-$\int_{t=0}^{0.5} \left(\|\mathbf{v}_1(x,t)\|_L^2 + \|\mathbf{v}_2(x,t)\|_L^2\right)dt + \|I\left(\phi_1(x,0.5)\right) - J_i\left(\phi_2(x,0.5)\right)\|^2$
-
-![](./papers/figures/fishes.png)
-
--->
-
-<!--
-
-NOtes:
-* Previously discussed Brians work
-* The variant most widely used
-
--->
-
-<!--
-
-## Diffeomorphisms:  Occam's razor modeling
-
-![](./figures/sillyputty.png)
-
-_differentiable map with differentiable inverse_
-
-## Diffeomoprhisms:  differentiable map with diff. inverse
-
-![](./figures/highresdiffeos.jpg)
-
-## Diffeomorphisms: image parameterization in a metric space
-
-![](./figures/shape_appearance.png)
-
--->
-
-<!--
-
-## Beyond original SyN
-
-\small
-
-![](./papers/figures/Frontiers_ITK.png)
-
-![](./papers/figures/Frontiers_BSplineSyN.png)
-
--->
-
-## ```antsRegistration```
-<BR><BR>
-
-\scriptsize
-
-```bash
-$ antsRegistration --help
-
-COMMAND:
-     antsRegistration
-          This program is a user-level registration application meant to utilize
-          ITKv4-only classes. The user can specify any number of "stages" where a stage
-          consists of a transform; an image metric; and iterations, shrink factors, and
-          smoothing sigmas for each level.Note that dimensionality, metric, transform,
-          output, convergence, shrink-factors and smoothing-sigmas parameters are
-          mandatory.
-
-OPTIONS:
-     --version
-          Get Version Information.
-
-     -d, --dimensionality 2/3
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, we try to infer the dimensionality from the input image.
-
-     -o, --output outputTransformPrefix
-                  [outputTransformPrefix,<outputWarpedImage>,<outputInverseWarpedImage>]
-          Specify the output transform prefix (output format is .nii.gz ). Optionally, one
-          can choose to warp the moving image to the fixed space and, if the inverse
-          transform exists, one can also output the warped fixed image. Note that only the
-          images specified in the first metric call are warped. Use antsApplyTransforms to
-          warp other images using the resultant transform(s).
-
-     -j, --save-state saveSateAsTransform
-          Specify the output file for the current state of the registration. The state
-          file is written to an hdf5 composite file. It is specially usefull if we want to
-          save the current state of a SyN registration to the disk, so we can load and
-          restore that later to continue the next registration process directly started
-          from the last saved state. The output file of this flag is the same as the
-          write-composite-transform, unless the last transform is a SyN transform. In that
-          case, the inverse displacement field of the SyN transform is also added to the
-          output composite transform. Again notice that this file cannot be treated as a
-          transform, and restore-state option must be used to load the written file by
-          this flag.
-
-     -k, --restore-state restoreStateAsATransform
-          Specify the initial state of the registration which get immediately used to
-          directly initialize the registration process. The flag is mutually exclusive
-          with other intialization flags.If this flag is used, none of the
-          initial-moving-transform and initial-fixed-transform cannot be used.
-
-     -a, --write-composite-transform 1/(0)
-          Boolean specifying whether or not the composite transform (and its inverse, if
-          it exists) should be written to an hdf5 composite file. This is false by default
-          so that only the transform for each stage is written to file.
-          <VALUES>: 0
-
-     -p, --print-similarity-measure-interval <unsignedIntegerValue>
-          Prints out the CC similarity metric measure between the full-size input fixed
-          and the transformed moving images at each iteration a value of 0 (the default)
-          indicates that the full scale computation should not take placeany value greater
-          than 0 represents the interval of full scale metric computation.
-          <VALUES>: 0
-
-     -v, --write-interval-volumes <unsignedIntegerValue>
-          Writes out the output volume at each iteration. It helps to present the
-          registration process as a short movie a value of 0 (the default) indicates that
-          this option should not take placeany value greater than 0 represents the
-          interval between the iterations which outputs are written to the disk.
-          <VALUES>: 0
-
-     -z, --collapse-output-transforms (1)/0
-          Collapse output transforms. Specifically, enabling this option combines all
-          adjacent transforms wherepossible. All adjacent linear transforms are written to
-          disk in the forman itk affine transform (called xxxGenericAffine.mat).
-          Similarly, all adjacent displacement field transforms are combined when written
-          to disk (e.g. xxxWarp.nii.gz and xxxInverseWarp.nii.gz (if available)).Also, an
-          output composite transform including the collapsed transforms is written to the
-          disk (called outputCollapsed(Inverse)Composite).
-          <VALUES>: 1
-
-     -i, --initialize-transforms-per-stage (1)/0
-          Initialize linear transforms from the previous stage. By enabling this option,
-          the current linear stage transform is directly intialized from the previous
-          stage\'s linear transform; this allows multiple linear stages to be run where
-          each stage directly updates the estimated linear transform from the previous
-          stage. (e.g. Translation -> Rigid -> Affine).
-          <VALUES>: 0
-
-     -n, --interpolation Linear
-                         NearestNeighbor
-                         MultiLabel[<sigma=imageSpacing>,<alpha=4.0>]
-                         Gaussian[<sigma=imageSpacing>,<alpha=1.0>]
-                         BSpline[<order=3>]
-                         CosineWindowedSinc
-                         WelchWindowedSinc
-                         HammingWindowedSinc
-                         LanczosWindowedSinc
-          Several interpolation options are available in ITK. These have all been made
-          available. Currently the interpolator choice is only used to warp (and possibly
-          inverse warp) the final output image(s).
-
-     -g, --restrict-deformation PxQxR
-          This option allows the user to restrict the optimization of the displacement
-          field, translation, rigid or affine transform on a per-component basis. For
-          example, if one wants to limit the deformation or rotation of 3-D volume to the
-          first two dimensions, this is possible by specifying a weight vector of '1x1x0'
-          for a deformation field or '1x1x0x1x1x0' for a rigid
-          transformation.Low-dimensional restriction only works if there are no preceding
-          transformations.
-
-     -q, --initial-fixed-transform initialTransform
-                                   [initialTransform,<useInverse>]
-                                   [fixedImage,movingImage,initializationFeature]
-          Specify the initial fixed transform(s) which get immediately incorporated into
-          the composite transform. The order of the transforms is stack-esque in that the
-          last transform specified on the command line is the first to be applied. In
-          addition to initialization with ITK transforms, the user can perform an initial
-          translation alignment by specifying the fixed and moving images and selecting an
-          initialization feature. These features include using the geometric center of the
-          images (=0), the image intensities (=1), or the origin of the images (=2).
-
-     -r, --initial-moving-transform initialTransform
-                                    [initialTransform,<useInverse>]
-                                    [fixedImage,movingImage,initializationFeature]
-          Specify the initial moving transform(s) which get immediately incorporated into
-          the composite transform. The order of the transforms is stack-esque in that the
-          last transform specified on the command line is the first to be applied. In
-          addition to initialization with ITK transforms, the user can perform an initial
-          translation alignment by specifying the fixed and moving images and selecting an
-          initialization feature. These features include using the geometric center of the
-          images (=0), the image intensities (=1), or the origin of the images (=2).
-
-     -m, --metric CC[fixedImage,movingImage,metricWeight,radius,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  MI[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  Mattes[fixedImage,movingImage,metricWeight,numberOfBins,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  MeanSquares[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  Demons[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  GC[fixedImage,movingImage,metricWeight,radius=NA,<samplingStrategy={None,Regular,Random}>,<samplingPercentage=[0,1]>]
-                  ICP[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>]
-                  PSE[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>]
-                  JHCT[fixedPointSet,movingPointSet,metricWeight,<samplingPercentage=[0,1]>,<boundaryPointsOnly=0>,<pointSetSigma=1>,<kNeighborhood=50>,<alpha=1.1>,<useAnisotropicCovariances=1>]
-                  IGDM[fixedImage,movingImage,metricWeight,fixedMask,movingMask,<neighborhoodRadius=0x0>,<intensitySigma=0>,<distanceSigma=0>,<kNeighborhood=1>,<gradientSigma=1>]
-          These image metrics are available--- CC: ANTS neighborhood cross correlation,
-          MI: Mutual information, Demons: (Thirion), MeanSquares, and GC: Global
-          Correlation. The "metricWeight" variable is used to modulate the per stage
-          weighting of the metrics. The metrics can also employ a sampling strategy
-          defined by a sampling percentage. The sampling strategy defaults to 'None' (aka
-          a dense sampling of one sample per voxel), otherwise it defines a point set over
-          which to optimize the metric. The point set can be on a regular lattice or a
-          random lattice of points slightly perturbed to minimize aliasing artifacts.
-          samplingPercentage defines the fraction of points to select from the domain. In
-          addition, three point set metrics are available: Euclidean (ICP), Point-set
-          expectation (PSE), and Jensen-Havrda-Charvet-Tsallis (JHCT).
-
-     -t, --transform Rigid[gradientStep]
-                     Affine[gradientStep]
-                     CompositeAffine[gradientStep]
-                     Similarity[gradientStep]
-                     Translation[gradientStep]
-                     BSpline[gradientStep,meshSizeAtBaseLevel]
-                     GaussianDisplacementField[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
-                     BSplineDisplacementField[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
-                     TimeVaryingVelocityField[gradientStep,numberOfTimeIndices,updateFieldVarianceInVoxelSpace,updateFieldTimeVariance,totalFieldVarianceInVoxelSpace,totalFieldTimeVariance]
-                     TimeVaryingBSplineVelocityField[gradientStep,velocityFieldMeshSize,<numberOfTimePointSamples=4>,<splineOrder=3>]
-                     SyN[gradientStep,updateFieldVarianceInVoxelSpace,totalFieldVarianceInVoxelSpace]
-                     BSplineSyN[gradientStep,updateFieldMeshSizeAtBaseLevel,totalFieldMeshSizeAtBaseLevel,<splineOrder=3>]
-                     Exponential[gradientStep,updateFieldVarianceInVoxelSpace,velocityFieldVarianceInVoxelSpace,<numberOfIntegrationSteps>]
-                     BSplineExponential[gradientStep,updateFieldMeshSizeAtBaseLevel,velocityFieldMeshSizeAtBaseLevel,<numberOfIntegrationSteps>,<splineOrder=3>]
-          Several transform options are available. The gradientStep or learningRate
-          characterizes the gradient descent optimization and is scaled appropriately for
-          each transform using the shift scales estimator. Subsequent parameters are
-          transform-specific and can be determined from the usage. For the B-spline
-          transforms one can also specify the smoothing in terms of spline distance (i.e.
-          knot spacing).
-
-     -c, --convergence MxNxO
-                       [MxNxO,<convergenceThreshold=1e-6>,<convergenceWindowSize=10>]
-          Convergence is determined from the number of iterations per level and is
-          determined by fitting a line to the normalized energy profile of the last N
-          iterations (where N is specified by the window size) and determining the slope
-          which is then compared with the convergence threshold.
-
-     -s, --smoothing-sigmas MxNxO...
-          Specify the sigma of gaussian smoothing at each level. Units are given in terms
-          of voxels ('vox') or physical spacing ('mm'). Example usage is '4x2x1mm' and
-          '4x2x1vox' where no units implies voxel spacing.
-
-     -f, --shrink-factors MxNxO...
-          Specify the shrink factor for the virtual domain (typically the fixed image) at
-          each level.
-
-     -u, --use-histogram-matching
-          Histogram match the images before registration.
-
-     -l, --use-estimate-learning-rate-once
-          turn on the option that lets you estimate the learning rate step size only at
-          the beginning of each level. * useful as a second stage of fine-scale
-          registration.
-
-     -w, --winsorize-image-intensities [lowerQuantile,upperQuantile]
-          Winsorize data based on specified quantiles.
-
-     -x, --masks [fixedImageMask,movingImageMask]
-          Image masks to limit voxels considered by the metric.
-
-     --float
-          Use 'float' instead of 'double' for computations.
-          <VALUES>: 0
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu. Will also print values used on the current command line
-          call.
-```
-
-<!--
-## Template building:  creating the average Joe
-
-![](./papers/figures/template0.jpg)
-
-## "Attractiveness" $\rightarrow$ mental processing?
-
-![](./papers/figures/template1.jpg)
-
-##  What about brains?
-
-![](./papers/figures/template3.jpg)
-
-## Templates facilitate computation
-
-![](./papers/figures/template4.jpg)
-
-## Gender?
-
-![](./papers/figures/template5.jpg)
-
--->
-
-<!--
-
-## ```antsMultivariateTemplateConstruction.sh```
-
-```bash
-$ antsMultivariateTemplateConstruction.sh
-
-Usage:
-
-antsMultivariateTemplateConstruction.sh -d ImageDimension -o OUTPREFIX <other options> <images>
-
-Compulsory arguments (minimal command line requires SGE cluster, otherwise use -c & -j options):
-
-     -d:  ImageDimension: 2 or 3 (for 2 or 3 dimensional registration of single volume)
-   ImageDimension: 4 (for template generation of time-series data)
-
-     -o:  OUTPREFIX; A prefix that is prepended to all output files.
-
-<images>  List of images in the current directory, eg *_t1.nii.gz. Should be at the end
-          of the command.  Optionally, one can specify a .csv or .txt file where each
-          line is the location of the input image.  One can also specify more than
-          one file for each image for multi-modal template construction (e.g. t1 and t2).
-          For the multi-modal case, the templates will be consecutively numbered (e.g.
-          template0.nii.gz, template1.nii.gz, ...).
-
-NB: All images to be added to the template should be in the same directory, and this script
-should be invoked from that directory.
-
-Optional arguments:
-
-     -c:  Control for parallel computation (default 1) -- 0 == run serially,  1 == SGE qsub,
-          2 == use PEXEC (localhost), 3 == Apple XGrid, 4 == PBS qsub, 5 == SLURM
-
-     -g:  Gradient step size (default 0.25) -- smaller in magnitude results in more cautious steps
-
-     -i:  Iteration limit (default 4) -- iterations of the template construction (Iteration limit)*NumImages registrations.
-
-     -j:  Number of cpu cores to use (default 2; -- requires "-c 2")
-
-     -k:  Number of modalities used to construct the template (default 1)
-
-     -w:  Modality weights used in the similarity metric (default = 1) --- specified as e.g. 1x0.5x0.75
-
-     -m:  Max-iterations in each registration
-
-     -n:  N4BiasFieldCorrection of moving image (default 1) -- 0 == off, 1 == on
-
-     -p:  Commands to prepend to job scripts (e.g., change into appropriate directory, set paths, etc)
-
-     -r:  Do rigid-body registration of inputs before creating template (default 0) -- 0 == off 1 == on. Only useful when
-          you do not have an initial template
-
-     -s:  Type of similarity metric used for registration.
-
-     -t:  Type of transformation model used for registration.
-
-     -x:  XGrid arguments (e.g., -x "-p password -h controlhost")
-
-     -y:  Update the template with the full affine transform (default 1). If 0, the rigid
-          component of the affine transform will not be used to update the template. If your
-          template drifts in translation or orientation try -y 0.
-
-     -z:  Use this this volume as the target of all inputs. When not used, the script
-          will create an unbiased starting point by averaging all inputs. Use the full path!
-
-     -b:  Boolean for saving iteration output to directories (default = 0).
-
-Example:
-
-antsMultivariateTemplateConstruction.sh -d 3 -m 30x50x20 -t GR -s CC -c 1 -o MY -z InitialTemplate.nii.gz  *RF*T1x.nii.gz
-
-- In this example 30x50x20 iterations per registration are used for template creation (that is the default)
-- Greedy-SyN and CC are the metrics to guide the mapping.
-- Output is prepended with MY and the initial template is InitialTemplate.nii.gz (optional).
-- The -c option is set to 1, which will result in using the Sun Grid Engine (SGE) to distribute the computation.
-- if you do not have SGE, read the help for multi-core computation on the local machine, or Apple X-grid options.
-
---------------------------------------------------------------------------------------
-ANTS was created by:
---------------------------------------------------------------------------------------
-Brian B. Avants, Nick Tustison and Gang Song
-Penn Image Computing And Science Laboratory
-University of Pennsylvania
-
-Please reference http://www.ncbi.nlm.nih.gov/pubmed/20851191 when employing this script
-in your studies. A reproducible evaluation of ANTs similarity metric performance in
-brain image registration:
-
-* Avants BB, Tustison NJ, Song G, Cook PA, Klein A, Gee JC. Neuroimage, 2011.
-
-Also see http://www.ncbi.nlm.nih.gov/pubmed/19818860 for more details.
-
-The script has been updated and improved since this publication.
-
---------------------------------------------------------------------------------------
-script adapted by N.M. van Strien, http://www.mri-tutorial.com | NTNU MR-Center
-multivariate template adaption by Nick Tustison
---------------------------------------------------------------------------------------
-Apple XGrid support by Craig Stark
---------------------------------------------------------------------------------------
-```
-
--->
-
-<!--
-
-## Nonparametric nonuniform intensity normalization (N3)
-
-* Developed at the Montreal Neurological Institute (John Sled, 1998)
-
-* Part of the standard preprocessing protocol in large scale projects such as ADNI
-
-* The traditional de facto standard in MRI bias correction
-    + good performance
-    + *public availability*
-
-* Public availability --- set of perl scripts coordinating various C++ programs
-
-* "*Let's incorporate N3 into ANTs!*"
-
-## Nonparametric nonuniform intensity normalization (N3)
-
-![](./tools/n4/figures/whyN4.png)
-
-<div align="center"><img src="./tools/n4/figures/whyN4.png" frameborder="0"></img></div>
-
-## N4 ("Nick's N3")
-
-* comparative [evaluation](http://www.ncbi.nlm.nih.gov/pubmed/20378467)
-
-* small spline distances (useful for higher magnet strengths)
-
-* multiresolution
-
-* weighted regional mask (used in [`antsAtroposN4.sh`](https://github.com/stnava/ANTs/blob/master/Scripts/antsAtroposN4.sh))
-
-* fast execution times
-
-* _publicly available_
-
-* tested nightly within the ITK dashboard system
-
--->
-
-<!--
-
-## ```N4BiasFieldCorrection```
-
-```bash
-$ N4BiasFieldCorrection --help
-
-COMMAND:
-     N4BiasFieldCorrection
-          N4 is a variant of the popular N3 (nonparameteric nonuniform normalization)
-          retrospective bias correction algorithm. Based on the assumption that the
-          corruption of the low frequency bias field can be modeled as a convolution of
-          the intensity histogram by a Gaussian, the basic algorithmic protocol is to
-          iterate between deconvolving the intensity histogram by a Gaussian, remapping
-          the intensities, and then spatially smoothing this result by a B-spline modeling
-          of the bias field itself. The modifications from and improvements obtained over
-          the original N3 algorithm are described in the following paper: N. Tustison et
-          al., N4ITK: Improved N3 Bias Correction, IEEE Transactions on Medical Imaging,
-          29(6):1310-1320, June 2010.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, N4 tries to infer the dimensionality from the input image.
-
-     -i, --input-image inputImageFilename
-          A scalar image is expected as input for bias correction. Since N4 log transforms
-          the intensities, negative values or values close to zero should be processed
-          prior to correction.
-
-     -x, --mask-image maskImageFilename
-          If a mask image is specified, the final bias correction is only performed in the
-          mask region. If a weight image is not specified, only intensity values inside
-          the masked region are used during the execution of the algorithm. If a weight
-          image is specified, only the non-zero weights are used in the execution of the
-          algorithm although the mask region defines where bias correction is performed in
-          the final output. Otherwise bias correction occurs over the entire image domain.
-          See also the option description for the weight image.
-
-     -r, --rescale-intensities 0/(1)
-          At each iteration, a new intensity mapping is calculated and applied but there
-          is nothing which constrains the new intensity range to be within certain values.
-          The result is that the range can "drift" from the original at each iteration.
-          This option rescales to the [min,max] range of the original image intensities
-          within the user-specified mask.
-
-     -w, --weight-image weightImageFilename
-          The weight image allows the user to perform a relative weighting of specific
-          voxels during the B-spline fitting. For example, some studies have shown that N3
-          performed on white matter segmentations improves performance. If one has a
-          spatial probability map of the white matter, one can use this map to weight the
-          b-spline fitting towards those voxels which are more probabilistically
-          classified as white matter. See also the option description for the mask image.
-
-     -s, --shrink-factor 1/2/3/4/...
-          Running N4 on large images can be time consuming. To lessen computation time,
-          the input image can be resampled. The shrink factor, specified as a single
-          integer, describes this resampling. Shrink factors <= 4 are commonly used.
-
-     -c, --convergence [<numberOfIterations=50x50x50x50>,<convergenceThreshold=0.0>]
-          Convergence is determined by calculating the coefficient of variation between
-          subsequent iterations. When this value is less than the specified threshold from
-          the previous iteration or the maximum number of iterations is exceeded the
-          program terminates. Multiple resolutions can be specified by using 'x' between
-          the number of iterations at each resolution, e.g. 100x50x50.
-
-     -b, --bspline-fitting [splineDistance,<splineOrder=3>]
-                           [initialMeshResolution,<splineOrder=3>]
-          These options describe the b-spline fitting parameters. The initial b-spline
-          mesh at the coarsest resolution is specified either as the number of elements in
-          each dimension, e.g. 2x2x3 for 3-D images, or it can be specified as a single
-          scalar parameter which describes the isotropic sizing of the mesh elements. The
-          latter option is typically preferred. For each subsequent level, the spline
-          distance decreases in half, or equivalently, the number of mesh elements doubles
-          Cubic splines (order = 3) are typically used.
-
-     -t, --histogram-sharpening [<FWHM=0.15>,<wienerNoise=0.01>,<numberOfHistogramBins=200>]
-          These options describe the histogram sharpening parameters, i.e. the
-          deconvolution step parameters described in the original N3 algorithm. The
-          default values have been shown to work fairly well.
-
-     -o, --output correctedImage
-                  [correctedImage,<biasField>]
-          The output consists of the bias corrected version of the input image.
-          Optionally, one can also output the estimated bias field.
-
-     --version
-          Get Version Information.
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-```
--->
-
-<!--
-##  Atropos -- cutting the threads of fate
-
-![](./papers/figures/Atropos_deGoya.jpg)
--->
-
-<!--
-Notes:
-* Can we use Suyash's code?
-* What about graph cuts?
--->
-
-<!--
-
-## Atropos:  flexible code base
-
-"20+ years of development.  <br>_Show me the code!_"
-
-![](./tools/atropos/figures/atropos.png)
-
--->
-
-<!--
-
-## ```Atropos```
-
-```bash
-$ Atropos --help
-
-COMMAND:
-     Atropos
-          A finite mixture modeling (FMM) segmentation approach with possibilities for
-          specifying prior constraints. These prior constraints include the specification
-          of a prior label image, prior probability images (one for each class), and/or an
-          MRF prior to enforce spatial smoothing of the labels. Similar algorithms include
-          FAST and SPM. Reference: Avants BB, Tustison NJ, Wu J, Cook PA, Gee JC. An open
-          source multivariate framework for n-tissue segmentation with evaluation on
-          public data. Neuroinformatics. 2011 Dec;9(4):381-400.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, Atropos tries to infer the dimensionality from the first input
-          image.
-
-     -a, --intensity-image [intensityImage,<adaptiveSmoothingWeight>]
-          One or more scalar images is specified for segmentation using the
-          -a/--intensity-image option. For segmentation scenarios with no prior
-          information, the first scalar image encountered on the command line is used to
-          order labelings such that the class with the smallest intensity signature is
-          class '1' through class 'N' which represents the voxels with the largest
-          intensity values. The optional adaptive smoothing weight parameter is applicable
-          only when using prior label or probability images. This scalar parameter is to
-          be specified between [0,1] which smooths each labeled region separately and
-          modulates the intensity measurement at each voxel in each intensity image
-          between the original intensity and its smoothed counterpart. The smoothness
-          parameters are governed by the -b/--bspline option.
-
-     -b, --bspline [<numberOfLevels=6>,<initialMeshResolution=1x1x...>,<splineOrder=3>]
-          If the adaptive smoothing weights are > 0, the intensity images are smoothed in
-          calculating the likelihood values. This is to account for subtle intensity
-          differences across the same tissue regions.
-
-     -i, --initialization Random[numberOfClasses]
-                          Otsu[numberOfTissueClasses]
-                          KMeans[numberOfTissueClasses,<clusterCenters(in ascending order and for first intensity image only)>]
-                          PriorProbabilityImages[numberOfTissueClasses,fileSeriesFormat(index=1 to numberOfClasses) or vectorImage,priorWeighting,<priorProbabilityThreshold>]
-                          PriorLabelImage[numberOfTissueClasses,labelImage,priorWeighting]
-          To initialize the FMM parameters, one of the following options must be
-          specified. If one does not have prior label or probability images we recommend
-          using kmeans as it is typically faster than otsu and can be used with
-          multivariate initialization. However, since a Euclidean distance on the inter
-          cluster distances is used, one might have to appropriately scale the additional
-          input images. Random initialization is meant purely for intellectual curiosity.
-          The prior weighting (specified in the range [0,1]) is used to modulate the
-          calculation of the posterior probabilities between the likelihood*mrfprior and
-          the likelihood*mrfprior*prior. For specifying many prior probability images for
-          a multi-label segmentation, we offer a minimize usage option (see -m). With that
-          option one can specify a prior probability threshold in which only those pixels
-          exceeding that threshold are stored in memory.
-
-     -s, --partial-volume-label-set label1xlabel2xlabel3
-          The partial volume estimation option allows one to modelmixtures of classes
-          within single voxels. Atropos currently allows the user to model two class
-          mixtures per partial volume class. The user specifies a set of class labels per
-          partial volume class requested. For example, suppose the user was performing a
-          classic 3-tissue segmentation (csf, gm, wm) using kmeans initialization. Suppose
-          the user also wanted to model the partial voluming effects between csf/gm and
-          gm/wm. The user would specify it using -i kmeans[3] and -s 1x2 -s 2x3. So, for
-          this example, there would be 3 tissue classes and 2 partial volume classes.
-          Optionally,the user can limit partial volume handling to mrf considerations only
-          whereby the output would only be the three tissues.
-
-     --use-partial-volume-likelihoods 1/(0)
-                                      true/(false)
-          The user can specify whether or not to use the partial volume likelihoods, in
-          which case the partial volume class is considered separate from the tissue
-          classes. Alternatively, one can use the MRF only to handle partial volume in
-          which case, partial volume voxels are not considered as separate classes.
-
-     -p, --posterior-formulation Socrates[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
-                                 Plato[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
-                                 Aristotle[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]
-                                 Sigmoid[<useMixtureModelProportions=1>,<initialAnnealingTemperature=1>,<annealingRate=1>,<minimumTemperature=0.1>]]
-          Different posterior probability formulations are possible as are different
-          update options. To guarantee theoretical convergence properties, a proper
-          formulation of the well-known iterated conditional modes (ICM) uses an
-          asynchronous update step modulated by a specified annealing temperature. If one
-          sets the AnnealingTemperature > 1 in the posterior formulation a traditional
-          code set for a proper ICM update will be created. Otherwise, a synchronous
-          update step will take place at each iteration. The annealing temperature, T,
-          converts the posteriorProbability to posteriorProbability^(1/T) over the course
-          of optimization.
-
-     -x, --mask-image maskImageFilename
-          The image mask (which is required) defines the region which is to be labeled by
-          the Atropos algorithm.
-
-     -c, --convergence numberOfIterations
-                       [<numberOfIterations=5>,<convergenceThreshold=0.001>]
-          Convergence is determined by calculating the mean maximum posterior probability
-          over the region of interest at each iteration. When this value decreases or
-          increases less than the specified threshold from the previous iteration or the
-          maximum number of iterations is exceeded the program terminates.
-
-     -k, --likelihood-model Gaussian
-                            HistogramParzenWindows[<sigma=1.0>,<numberOfBins=32>]
-                            ManifoldParzenWindows[<pointSetSigma=1.0>,<evaluationKNeighborhood=50>,<CovarianceKNeighborhood=0>,<kernelSigma=0>]
-                            JointShapeAndOrientationProbability[<shapeSigma=1.0>,<numberOfShapeBins=64>, <orientationSigma=1.0>, <numberOfOrientationBins=32>]
-                            LogEuclideanGaussian
-          Both parametric and non-parametric options exist in Atropos. The Gaussian
-          parametric option is commonly used (e.g. SPM & FAST) where the mean and standard
-          deviation for the Gaussian of each class is calculated at each iteration. Other
-          groups use non-parametric approaches exemplified by option 2. We recommend using
-          options 1 or 2 as they are fairly standard and the default parameters work
-          adequately.
-
-     -m, --mrf [<smoothingFactor=0.3>,<radius=1x1x...>]
-               [<mrfCoefficientImage>,<radius=1x1x...>]
-          Markov random field (MRF) theory provides a general framework for enforcing
-          spatially contextual constraints on the segmentation solution. The default
-          smoothing factor of 0.3 provides a moderate amount of smoothing. Increasing this
-          number causes more smoothing whereas decreasing the number lessens the
-          smoothing. The radius parameter specifies the mrf neighborhood. Different update
-          schemes are possible but only the asynchronous updating has theoretical
-          convergence properties.
-
-     -g, --icm [<useAsynchronousUpdate=1>,<maximumNumberOfICMIterations=1>,<icmCodeImage=''>]
-          Asynchronous updating requires the construction of an ICM code image which is a
-          label image (with labels in the range {1,..,MaximumICMCode}) constructed such
-          that no MRF neighborhood has duplicate ICM code labels. Thus, to update the
-          voxel class labels we iterate through the code labels and, for each code label,
-          we iterate through the image and update the voxel class label that has the
-          corresponding ICM code label. One can print out the ICM code image by specifying
-          an ITK-compatible image filename.
-
-     -r, --use-random-seed 0/(1)
-          Initialize internal random number generator with a random seed. Otherwise,
-          initialize with a constant seed number.
-
-     -o, --output [classifiedImage,<posteriorProbabilityImageFileNameFormat>]
-          The output consists of a labeled image where each voxel in the masked region is
-          assigned a label from 1, 2, ..., N. Optionally, one can also output the
-          posterior probability images specified in the same format as the prior
-          probability images, e.g. posterior%02d.nii.gz (C-style file name formatting).
-
-     -u, --minimize-memory-usage (0)/1
-          By default, memory usage is not minimized, however, if this is needed, the
-          various probability and distance images are calculated on the fly instead of
-          being stored in memory at each iteration. Also, if prior probability images are
-          used, only the non-negligible pixel values are stored in memory.
-          <VALUES>: 0
-
-     -w, --winsorize-outliers BoxPlot[<lowerPercentile=0.25>,<upperPercentile=0.75>,<whiskerLength=1.5>]
-                              GrubbsRosner[<significanceLevel=0.05>,<winsorizingLevel=0.10>]
-          To remove the effects of outliers in calculating the weighted mean and weighted
-          covariance, the user can opt to remove the outliers through the options
-          specified below.
-
-     -e, --use-euclidean-distance (0)/1
-          Given prior label or probability images, the labels are propagated throughout
-          the masked region so that every voxel in the mask is labeled. Propagation is
-          done by using a signed distance transform of the label. Alternatively,
-          propagation of the labels with the fast marching filter respects the distance
-          along the shape of the mask (e.g. the sinuous sulci and gyri of the cortex.
-          <VALUES>: 0
-
-     -l, --label-propagation whichLabel[lambda=0.0,<boundaryProbability=1.0>]
-          The propagation of each prior label can be controlled by the lambda and boundary
-          probability parameters. The latter parameter is the probability (in the range
-          [0,1]) of the label on the boundary which increases linearly to a maximum value
-          of 1.0 in the interior of the labeled region. The former parameter dictates the
-          exponential decay of probability propagation outside the labeled region from the
-          boundary probability, i.e. boundaryProbability*exp( -lambda * distance ).
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-```
-
--->
-
-<!--
-## Atropos + N4 $\rightarrow$ `antsAtroposN4.sh`
-
-![](./tools/atropos/figures/atroposFlow.png)
-
-## ```DenoiseImage``` --- contribution from Jose Manjon
-
-![](./tools/figures/denoising.png)
-
--->
-
-<!--
-
-##
-
-```bash
-$ DenoiseImage --help
-
-COMMAND:
-     DenoiseImage
-          Denoise an image using a spatially adaptive filter originally described in J. V.
-          Manjon, P. Coupe, Luis Marti-Bonmati, D. L. Collins, and M. Robles. Adaptive
-          Non-Local Means Denoising of MR Images With Spatially Varying Noise Levels,
-          Journal of Magnetic Resonance Imaging, 31:192-203, June 2010.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, the program tries to infer the dimensionality from the input
-          image.
-
-     -i, --input-image inputImageFilename
-          A scalar image is expected as input for noise correction.
-
-     -n, --noise-model Rician/(Gaussian)
-          Employ a Rician or Gaussian noise model.
-
-     -x, --mask-image maskImageFilename
-          If a mask image is specified, denoising is only performed in the mask region.
-
-     -s, --shrink-factor (1)/2/3/...
-          Running noise correction on large images can be time consuming. To lessen
-          computation time, the input image can be resampled. The shrink factor, specified
-          as a single integer, describes this resampling. Shrink factor = 1 is the
-          default.
-
-     -p, --patch-radius 1
-                        1x1x1
-          Patch radius. Default = 1x1x1
-
-     -r, --search-radius 3
-                         3x3x3
-          Search radius. Default = 3x3x3.
-
-     -o, --output correctedImage
-                  [correctedImage,<noiseImage>]
-          The output consists of the noise corrected version of the input image.
-          Optionally, one can also output the estimated noise image.
-
-     --version
-          Get Version Information.
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-
-```
--->
-
-<!-- 
-## Multi-atlas segmentation
-
-![](./tools/jointfusion/figures/jointLabelFusion.png)
-
-## New work:  joint intensity fusion
-
-![](./tools/jointfusion/figures/jointIntensityFusion.png)
-
--->
-
-<!--
-## Possible uses
-
-* ``Correct'' images
-
-    * motion correction
-
-    * ``remove'' lesions
-
-* Project atlas set intensity signature
-
-* Use in ``corrective learning''
-
--->
-
-<!--
-
-## ```antsJointFusion``` --- contribution from Hongzhi Wang (with some added features)
-
-```bash
-$ antsJointFusion --help
-
-COMMAND:
-     antsJointFusion
-          antsJointFusion is an image fusion algorithm developed by Hongzhi Wang and Paul
-          Yushkevich which won segmentation challenges at MICCAI 2012 and MICCAI 2013. The
-          original label fusion framework was extended to accommodate intensities by Brian
-          Avants. This implementation is based on Paul's original ITK-style implementation
-          and Brian's ANTsR implementation. References include 1) H. Wang, J. W. Suh, S.
-          Das, J. Pluta, C. Craige, P. Yushkevich, Multi-atlas segmentation with joint
-          label fusion IEEE Trans. on Pattern Analysis and Machine Intelligence, 35(3),
-          611-623, 2013. and 2) H. Wang and P. A. Yushkevich, Multi-atlas segmentation
-          with joint label fusion and corrective learning--an open source implementation,
-          Front. Neuroinform., 2013.
-
-OPTIONS:
-     -d, --image-dimensionality 2/3/4
-          This option forces the image to be treated as a specified-dimensional image. If
-          not specified, the program tries to infer the dimensionality from the input
-          image.
-
-     -t, --target-image targetImage
-                        [targetImageModality0,targetImageModality1,...,targetImageModalityN]
-          The target image (or multimodal target images) assumed to be aligned to a common
-          image domain.
-
-     -g, --atlas-image atlasImage
-                       [atlasImageModality0,atlasImageModality1,...,atlasImageModalityN]
-          The atlas image (or multimodal atlas images) assumed to be aligned to a common
-          image domain.
-
-     -l, --atlas-segmentation atlasSegmentation
-          The atlas segmentation images. For performing label fusion the number of
-          specified segmentations should be identical to the number of atlas image sets.
-
-     -a, --alpha 0.1
-          Regularization term added to matrix Mx for calculating the inverse. Default =
-          0.1
-
-     -b, --beta 2.0
-          Exponent for mapping intensity difference to the joint error. Default = 2.0
-
-     -r, --retain-label-posterior-images (0)/1
-          Retain label posterior probability images. Requires atlas segmentations to be
-          specified. Default = false
-
-     -f, --retain-atlas-voting-images (0)/1
-          Retain atlas voting images. Default = false
-
-     -c, --constrain-nonnegative (0)/1
-          Constrain solution to non-negative weights.
-
-     -p, --patch-radius 2
-                        2x2x2
-          Patch radius for similarity measures. Default = 2x2x2
-
-     -m, --patch-metric (PC)/MSQ
-          Metric to be used in determining the most similar neighborhood patch. Options
-          include Pearson's correlation (PC) and mean squares (MSQ). Default = PC (Pearson
-          correlation).
-
-     -s, --search-radius 3
-                         3x3x3
-                         searchRadiusMap.nii.gz
-          Search radius for similarity measures. Default = 3x3x3. One can also specify an
-          image where the value at the voxel specifies the isotropic search radius at that
-          voxel.
-
-     -e, --exclusion-image label[exclusionImage]
-          Specify an exclusion region for the given label.
-
-     -x, --mask-image maskImageFilename
-          If a mask image is specified, fusion is only performed in the mask region.
-
-     -o, --output labelFusionImage
-                  intensityFusionImageFileNameFormat
-                  [labelFusionImage,intensityFusionImageFileNameFormat,<labelPosteriorProbabilityImageFileNameFormat>,<atlasVotingWeightImageFileNameFormat>]
-          The output is the intensity and/or label fusion image. Additional optional
-          outputs include the label posterior probability images and the atlas voting
-          weight images.
-
-     --version
-          Get version information.
-
-     -v, --verbose (0)/1
-          Verbose output.
-
-     -h
-          Print the help menu (short version).
-
-     --help
-          Print the help menu.
-          <VALUES>: 1
-
-```
-
--->
 
@@
 
-* [ANTsRNet](https://github.com/stnava/ANTsRNet): a growing collection of popular deep learning architectures
+* Corrective learning for segmentation refinement
 
@@
 * https://github.com/stnava/ANTs
-
 * https://github.com/stnava/ANTsR
-
-* https://github.com/stnava/ANTsRNet

### 2018-02-15 papers/papers.Rmd
ENH:  Remove slides.
ENH:  Last minute refinements.
ENH:  Final commit.
ENH:  More.
ENH:  mdAnderson August 11 morning talk.
ENH:  Add Cohen presentation.

@@
+<!--
+
 # Major ANTs utilities
+
+-->
 
@@
 
+\centering
+
 <BR><BR>
+
 _\`\`Papers are just advertisements for the science.\'\'_
 <BR>
+
+<!--
 
@@
 
-<!--
-
 ## Symmetric Normalization (SyN)
@@
 
+-->
+
+<!--
+
 NOtes:
@@
 ![](./figures/shape_appearance.png)
+
 -->
+
+<!--
 
@@
 
+-->
+
 ## ```antsRegistration```
 <BR><BR>
+
+\scriptsize
 
@@
 
-## Gender discernibility?
+## Gender?
 
 ![](./papers/figures/template5.jpg)
+
+-->
+
+<!--
 
@@
 * "*Let's incorporate N3 into ANTs!*"
--->
 
-## N3 adoption issues
+## Nonparametric nonuniform intensity normalization (N3)
 
@@
 * tested nightly within the ITK dashboard system
+
 -->
+
+<!--
 
@@
 ```
+-->
 
-<--
+<!--
 ##  Atropos -- cutting the threads of fate
@@
 
+-->
+
 <!--
-
 ## Atropos + N4 $\rightarrow$ `antsAtroposN4.sh`
@@
 ![](./tools/atropos/figures/atroposFlow.png)
+
+## ```DenoiseImage``` --- contribution from Jose Manjon
+
+![](./tools/figures/denoising.png)
+
 -->
 
-## ```DenoiseImage``` --- contribution from Jose Manjon
+<!--
+
+##
 
@@
 ```
+-->
 
+<!-- 
 ## Multi-atlas segmentation
@@
 * Use in ``corrective learning''
+
+-->
+
+<!--
 
@@
 ```
+
+-->

### 2018-02-15 makePresentationCohen2018.R

@@ -1,0 +1,46 @@
+#!/usr/bin/env Rscript
+
+####################
+#
+#   Feb 15, 2018
+#
+#
+#
+#
+#####################
+
+library( ggplot2 )
+library( rmarkdown )
+
+srcDir <- "./"
+buildrmd <- 'cohen.Rmd'
+
+########   Morning    ##########
+
+# Retrospective
+
+#
+#  Should add
+#    fmri processing
+
+rawrmds <- c( "format.Rmd",
+              "background/background3.Rmd",
+              "competitions/competitions.Rmd",
+              "papers/papers.Rmd",
+              "evaluation/antsvfreesurfer2.Rmd",
+              "evaluation/antsvfreesurfer2_extra.Rmd",
+              "antsr/antsr.Rmd",
+              "finalSlide.Rmd"
+               )
+
+for ( x in 1:length(rawrmds) ) {
+  if ( x == 1 )
+    {
+    cmd<-paste( "cat ", rawrmds[x], " > ", buildrmd )
+    } else {
+      cmd<-paste( "cat ", rawrmds[x], " >> ", buildrmd )
+    }
+  system( cmd )
+  }
+
+render( buildrmd, clean = TRUE )
